% A Difference in the Family: The Snape Chronicles (Rannaro)
% The Seventh Year

\chapter{Bait, Hook, and Catch}

% \textbf{The Sixth Year - The Bait}

And so the sixth year at Hogwarts ended. Severus asked for and received permission to apparate home several times during the last week in order to clear out the things he'd left stored in Slytherin house over the years, and he took advantage of the trips to pay brief visits to Nana. Apparation was a wonderful thing, and he'd turned out to be quite good at it.

Now that he was allowed to perform magic outside of Hogwarts, Severus set about seriously remodeling his home. He lined the walls of the sitting room with bookcases, making it smaller and darker and more like a private study. Then he built a new staircase that ended behind one of the bookcases, a sort of secret passage. Upstairs in the now empty storage area he installed tables, cabinets, and a sink, turning it into a proper laboratory for both potions and chemistry.

With all finally prepared, Severus apparated to London. It was a heady thing to have money. He wasn't sure where to go, so he went to the Tower of London, where he was sure there was a tourist information desk. There he found that Charing Cross Road was the best place for books. He wandered in and out of rare book shops until he discovered his favorite building in the whole country, for it contained floor after floor after floor of books. Severus restricted himself to geometry, physics, astronomy, and chemistry, then apparated home, assuring himself there'd be many more visits.

Another day he went to Diagon Alley to buy books at Flourish and Blotts. While there Severus noticed a display of broomsticks, and paused to think. It'd been a while since his disastrous classes, and he was older and more self-assured. Maybe... After all, it might be wise to keep a broom at home. Just in case. He lied to the shop keeper about a younger brother and bought a lightweight beginner's broom to practice with on the moors outside town.

The broom turned out to be easier than Severus expected. He went out onto the moor in the evening when he was certain not to be seen, and tried to recall everything he'd ever been told about handling a broom. Whether it was his own greater maturity or the fact that the broom hadn't already been used by hundreds of other students, Severus found that he could rise and land without losing control and that he could navigate short distances without the ride becoming too bumpy. Not great, but serviceable, and so he was content.

Then there was Voyager. Not as glamorous as Apollo or Skylab, nor as immediate in its results as Viking and Venera, Voyager nonetheless was a scientist's dream. Severus practiced his geometry and physics calculating the trajectory that would take the twin probes to Jupiter, Saturn, Uranus and Neptune. The thought of seeing photographs of something more than two and a half billion miles away was intoxicating.

Severus was upstairs working in his laboratory one sunny day in the second half of July when a beautiful tawny owl flew up and beat her wings against the window. \emph{Who would send me an owl?} He opened the window to let her in, and tipped her a few knuts. He had the impression she would have preferred a live mouse, but he kept no live animals in the house, certainly not mice.

The letter was from Narcissa. Her whole future happiness was at stake. She was desperate. She was at her wits' end. She had no one to turn to except him. If he wouldn't help her, she would have no other recourse but to die.

\emph{Rich kid drama. No one falls for this stuff except people who really want to and people who watch too many movies. And people who have too few good memories.} The return owl assented to a meeting and gave instructions on how to find the house. The next afternoon, Severus heard the pop of Narcissa apparating into his kitchen.

Narcissa was clearly not prepared for Severus's house. She was uncomfortable with its smallness, its shabbiness, its uncared for look. He persuaded her to sit down on the tiny, worn sofa in the sitting room and prepared tea for her in a chipped cup. She sipped at it graciously.

"I can't stand it. I can't stand being without him. My parents are opposed. His parents are opposed. I'm at my wits' end. I need a spell; I need a potion. I need something that will turn them around and allow us to marry. You're the only spell maker I know. Can't you do something for us?"

"I might be able to do something in the spell way, though I'm not sure what, but I have no idea if there's a potion that will do what you want it to. My grandmother would know. She's made potions for the district all her life. If there's something that can help you, she'll know what it is."

"Oh... You have a grandmother?" was Narcissa's reply.

Nana's cottage was classic, small but perfect in its simple, neat way, and Narcissa loved the garden. She and Nana were polite to each other, and yet there was a distance of blood and heritage that both were intensely aware of that created a certain frostiness between them. It made Severus wonder if Narcissa had ever before been in the position of feeling inferior.

"I do not," Nana said as they inspected the black hellebore and aconite, "brew potions to deceive."

"Oh, no, Mrs. Prince. Not deceive. Just incline to our point of view."

"It would help if I knew why your points of view differ."

"Our fathers have different ideas on a... political issue. It has nothing to do with Lucius or myself, and everything to do with keeping the families apart. I hate politics so. I just want us to be happy."

Later they took tea on the lawn. Nana was using an elegant tea service that Severus had never seen before, and he suspected she kept it packed away, bringing it out for special occasions.

"There is a potion for the healing of psychic wounds that may help you. It dispels bitterness and resentment, and speeds recovery from spiritual injuries. It is a complex potion that will take about six weeks to make and is somewhat expensive. I could not guarantee that it will accomplish what you wish, but it may make your persuasion more successful."

"Oh, money is no problem. We're just so happy to have any help at all. You're too kind."

Narcissa arranged to return in August.

It was a terrible summer. Even in the backwater of eastern Lancashire, they learned of accidents and attacks all through the wizarding world. It was as if the whole country was under some kind of evil spell.

Homes were destroyed by lightning, or by the explosion of gas mains. Families drowned in freak boating accidents, or were buried in mudslides of huge coal slag mountains. Closer to home, mobs of muggles in villages of Yorkshire and Cumberland attacked wizards and witches, driving them from their houses or, in one instance, killing them. The Ministry of Magic was frantic, trying to contain both the disasters themselves and the spread of news. Muggles were being attacked as well, and here the cover-up was more difficult.

Severus increased the protective spells around his house, extending them to neighboring buildings. Most of the narrow street was now empty of inhabitants, and he was quite pleased to keep it that way. The only thing needed was to ensure that the local council ceased to notice that the end of the road existed. It was at the very edge of the village, and drew neither electricity nor gas, and so the spells, while complex, did not involve a large area. He urged Nana to guard her cottage as well, but she didn't see the need.

Voyager 2 launched on August 20. Severus thought it fascinating that the second probe would leave Earth before the first one, but the logic was unassailable. Voyager 1 would be on a faster trajectory, and would arrive first at Jupiter, assuming all the physics had been done properly. Severus had no doubts. He set himself to wait patiently for a year and a half until he could start seeing the pictures.

Narcissa, too, came in August. She went directly to Nana this time, and Severus wouldn't have known of her visit if he hadn't been visiting Nana at the same time. They had a pleasant luncheon on the lawn, the weather being beautiful that day, and Narcissa left with a precious vial of potion for the healing of psychic wounds.

The summer ended far too soon, and it was time to return to Hogwarts. Seventh year, last year. Severus was looking forward to being out of Hogwarts for good. Except for Lily, he had no happy memories of the place. He knew it would be busy, with classes and tutoring, and preparing for his NEWT exams, but he was much more interested in chemistry and calculus, and was already trying to figure out how one could be employed in a laboratory without having a university degree.

On September 1, for the first time, Severus apparated directly to King's Cross Station to take, for the last time, the Express to Hogwarts.

% \textbf{The Seventh Year - The Bait (continued)}

Severus made his way to the Slytherin club car and sat toward one corner. Rosier joined him after a moment. "Feels funny being the top class, doesn't it?"

"A bit," Severus answered. "How was your summer?"

"Terrible. Haven't you heard of all the attacks? No one's safe."

"We got some of the news. But it's pretty safe where we live."

"Really? I thought a couple of the worst incidents were near you."

Severus wondered how Rosier had any idea where he lived. "North of us," he said. "Quite a bit north of us. But I did fortify the house better. You can't take chances."

"The Ministry twiddles its thumbs and does nothing while our people are dying," Rosier continued in a low, tense voice. "We need leadership that really leads. Someone who'll help us fight back."

"Does someone like that exist?"

Rosier bent closer. "Not only exists, but is already doing something about the problem. You've heard of him. We've spoken of him before. You know... His followers don't speak his name. They call him the Dark Lord."

"I remember. I've only heard a little about him."

"They don't spread it around much. Only the most trustworthy. The Ministry is against him, of course."

Rosier talked about the Dark Lord for a good part of the trip.

Severus looked for Lily at the Sorting. He found her, too, sitting next to James Potter. He almost got away without being seen, but wasn't quite fast enough.

"Severus! It's good to see you. How was your summer?"

The odd thing was that for all those years they'd never spoken in front of other students, preferring to keep their friendship a secret, and now that the friendship was diminished Lily felt comfortable bringing it into the open.

"It was all right. A little dull. How was yours?" He nodded to James. "Potter."

"Snape," James replied with the same almost formal nod.

"It was all right. A little dull." She laughed. "See you in Potions, probably."

"Yeah, Potions." And that was the extent of the conversation. Severus sat with Rosier at the Slytherin table, thinking of his promise to Lily of the year before. There wasn't a lot to talk about.

Before the first month was over three students, one from Gryffindor and two from Ravenclaw, were called to Dumbledore's office because of attacks on their families. Endorpha Reedbinder's uncle was actually killed by crazed wizards in a rampage outside the Ministry of Magic itself. The whole school was on edge, and the seventh years in Slytherin house formed a special group to discuss the situation.

"We have to generate support for this Dark Lord who's actually doing something to halt these attacks," Wilkes insisted at one of the first meetings.

"But we don't really know who's behind it." This was from Mordechai Benedict, and several others agree with him.

"Muggles are behind it!" Wilkes insisted. "Muggles and muggle-borns. Do we have to wait until there's not an old pureblood family left before we recognize the danger? Even the half-bloods come from old families, and they're in danger, too."

Severus agreed that some action should be taken, though he stood with the group that felt caution was needed in assigning blame.

Then, as the October moon waned into nothing, Dumbledore called Severus into his office.

% \textbf{The Seventh Year: The Hook}

\subsection{Tuesday, October 11, 1977 (one day before the new moon)}

"Master Snape, you will not apparate!"

"She's my grandmother!"

"And she has died. And we will go to her as quickly as possible. But you will travel with me. You will not apparate alone. You will go with me by Portkey."

"You're trying to control what happens!"

"I am not ashamed to admit it. You will not apparate into the middle of a volatile situation without backup or without someone who can control you. We do not yet know the full extent of what has happened."

"No, an angry mob just burned my grandmother to death in her own home, but I guess that's not explicit enough for you!"

"You are going nowhere until you have better control of yourself." Dumbledore nodded to Hagrid, who stood guard by the door.

"Lad, ya got t' be calmer. Ya go running off halfcocked and y're just going t' make the thing worse. The first thing we got t' do is find out just what did happen. Then ya can decide the next step."

"They will pay. I swear, they will pay."

"That is not for you to decide."

"You don't understand, do you Headmaster! I don't have any family left! She was the last living relative I had!"

"And you will not dishonor her memory by randomly attacking the innocent."

"You are not going to stop me! You are not... going to... stop..." And then Severus was sobbing like a child, with Hagrid's arm around his shoulders as he was pulled down onto one of the chairs in Dumbledore's office. "Oh, Nana... Nana..."

The Portkey took them first to the hospital to talk to an earnest young physician. "You're the grandson, right. I know she lost her daughter in a car accident. A sorry business, sorry business. Matter for the police, of course. I can assure you she suffered little pain. She was asleep. They found her body, well what was left... I'm sorry. They found her body still in the bed... well as near as... I'm sorry. She appears to have been still asleep in bed when she died, which means she never realized what was happening..."

"How am I supposed to believe that?" Severus confronted Dumbledore outside. "A mob surrounds her house and sets fire to it and she doesn't even wake up? That's not my grandmother. That's not Nana."

The police had little more to add except that eleven people were in custody, all of them having admitted to setting the fire. Severus wanted their names, but that was against policy until he'd consulted a solicitor. Dumbledore steered him carefully towards the door.

Then, finally, they visited the house. Nothing was left except a charred shell. The plants that stood next the house were gone, though the rest of the garden was intact. More to the point, the whole village was silent. No one, not one person, dared approach Severus or the tall wizard with the long beard and pointed hat. If there was an image of an avenging angel, it was Dumbledore.

The funeral was yet another problem. The local pastor was not sure that Nana deserved to be buried in consecrated ground. There not being other ground in which she could be legally buried, Severus was understandably upset. Dumbledore undertook to mediate between the inflexible church and the distraught boy, and ended up making enemies on both sides. It turned out there was a small, freethinking columbarium in Clitheroe, and Nana's urn was placed there, she already having been `cremated.'

A week after having left, Dumbledore and Severus returned to Hogwarts. Dumbledore was conscious of a situation that had not been handled well. Severus went directly to Rosier to ask what he could do to assist the Dark Lord.

Severus had more or less called a truce with Remus Lupin and with James Potter, but that truce did not extend to Sirius Black. Nor did it extend to Peter Pettigrew, but since Peter was such a nonentity, no one cared. The basic bottom line was that in addition to everything else, Severus and Sirius were still at war.

Once again Severus found himself busy with requests from fifth year students for assistance in preparation for their OWLs. Now he was paying more attention to each student's potential usefulness in the coming muggle war, passing on names and information to Rosier in addition to simple tutoring. To one student in particular, however, Severus gave special attention, promising to help him not only pass his OWLs, but learn how to create spells and invent potions. That student was Regulus Black.

It was the end of October and the weekend of the first trip into Hogsmeade. Most of the students at breakfast were eagerly discussing their day's plans as Severus rose and walked over to his new protégé.

"Are you ready? The earlier we get started, the more you can work on."

The younger student, whose thick black hair and moody good looks unmistakably proclaimed his house and lineage, grinned and said, "Sure. Right now?"

"Why not?"

They walked past the Slytherin table and out the doors into the entrance hall. As expected, they were followed.

"Hey, Snivellus! Where are you going with my brother?"

"Your brother? Oh, of course, Black. Silly of me not to have noticed."

"You keep your greasy fingers and your dark magic away from Regulus or I'll pulverize you with my bare hands."

"The Headmaster will certain want to hear how a Gryffindor student is threatening Slytherin students. Especially considering the situation in the world at large. We don't want fighting in school."

"There'll be fighting if you keep corrupting my brother."

"Leave me alone, Sirius," interjected Regulus. "You don't even live at home any more. You don't have any authority over me."

"Here. What's going on here?" Hagrid stood in the doorway to the Great Hall. Now he advanced to plant himself between Sirius and Severus.

"This Gryffindor student was threatening and attempting to intimidate us when we were just looking for a quiet place to review Regulus's Charms and Potions work. We'd like him to be ordered not to follow us." By now James, Lily, Remus, and Peter also appeared. Severus glanced at them and a note of bitterness entered his voice that gave his words added sarcasm. "Maybe our Head Boy and Head Girl could exercise a little of their authority for the protection of the students at large, and keep this `person' from accosting us in the halls."

"We'll take care of this, Hagrid," said James quickly. "Come on, Padfoot. Let's go back to the common room and talk about this."

Reluctantly, Sirius allowed himself to be pulled away, while Severus and Regulus continued outside to work on spells.

"It's a trap, Prongs! You've been to our house in London. You've seen all that stuff we have. Regulus has always been interested in the dark side of magic. But it was just a kid's interest. Now Snivellus..." Sirius saw Lily's glare and met her eyes in defiance. "...Snivellus is trying to pull him down into this Death Eater business and make him a servant of their Dark Lord, too. And he doesn't even care about Regulus. He's doing it to get back at me!"

"Why, Padfoot," James said smoothly, "whatever would Snape want to get back at you for? It isn't like you ever did anything to him."

"But this isn't me! It's Regulus! He can come after me with any curse he's got and I'll take him on man to man. But if he hurts Regulus, I'll kill him!"

James watched Sirius, a worried frown between his eyebrows. "Man to man," he said. "I'm not sure. Sometimes I wonder, if we ever had taken him on one to one, who would've won."

"I can tell you that," said Lily quietly. "He would've won. He's that good. He never used all his spells on you. I can also tell you that he never wanted to fight. Everything he did was in response to something you started. So now, please, leave him alone. He's already had enough trouble for the whole year, and it isn't November yet."

James slid over on the sofa so he was closer to Lily. "I've already promised. No fighting. We can still talk to him, and to Regulus, but I've sworn off curses for good."

"I haven't," Sirius snarled. "If he doesn't leave my brother alone, he's going down."

The interviews with Dumbledore lasted most of the afternoon.

"Master Black, you stated within the hearing of Hagrid that you would pulverize another student with your bare hands. Do you not consider this a threat?"

"The slimy git..."

"You will not use such language in my presence."

"He's teaching my brother the Dark Arts. He's recruiting for this Dark Lord, this evil sorcerer. I'm not letting Regulus get caught in it."

"Would it not be more to the point to inform the teachers or me of this? Do you think we are incapable of handling this situation?"

"Professor, you don't know how sneaky he is. He was close to my cousin Bella for years. She's gone off and joined these Death Eaters, and they've got their sights set on Regulus. I'm not going to let it happen."

The next interview was easier, though no more successful. "You have been friends for many years. Do you not think, Master Potter, that you could speak rationally with Master Black and convince him not to take matters into his own hands. If the conflict on the outside comes into Hogwarts, we shall have trouble indeed."

"I've been trying, but when Sirius cares passionately about something it's hard to derail him. He's really worried about his brother, and it's against his nature to sit back passively and watch things happen."

The third held more promise. "You used to be quite close friends, Miss Evans. No, do not look shocked. We have known about it for years, and it has been an excellent association for both you and him. Now I understand that you have formed other emotional attachments, quite natural too, but it has removed a means of reaching Master Snape."

"I'm sorry, Professor. I don't think I ever had that much influence on Severus. We'd talk, and he'd listen, but generally he did what he wanted. If I'd had any effect on him, there wouldn't have been so much hexing and cursing."

"Ah, Miss Evans. I fear you seriously underestimate your own role in the past six years. Could I persuade you to talk to him and find out how seriously attached he is to this Dark Arts group?"

"I'll try. I don't think he'll tell me much, though."

And then the final one. "The accusation is a serious one, Master Snape, that you would teach Dark Arts to another student and actively recruit him into a group bent on guerilla warfare within our world."

"I don't know what they're talking about, Professor. I tutor the others in Slytherin for their OWLs, their NEWTs, and their regular exams. I've been doing it for years. No one's ever accused me of promoting the Dark Arts before. To tell the truth, I think he's upset because he doesn't want someone like me to be a friend of his brother's. They are an old pureblood family, and I am a half-blood. It's just that he can't admit that kind of prejudice to you, so he has to find some other reason. The Dark Arts business is just ridiculous."

At the end of the day, Dumbledore called on Hagrid.

"He frightens me, Hagrid. He truly frightens me. Of all of them, he was the one I had no feeling for. If I did not already know he was lying to me, I would not know he was lying to me. How can one so young be so accomplished at this kind of deception?"

"Seems you asked that question before, sir, and seems I gave you the same answer. Ain't that what you been teaching him to do?"

"Ah, yes. I do recall. And I also recall saying that I had not anticipated that he would be so good at it. Tangled webs, Hagrid. Tangled webs."

A December owl brought an invitation from Bella to spend Christmas in London. Severus's acceptance went out by return owl. Even if he was in a servant's room on the fifth floor, or ate all his meals alone, he would still be living in London near Charing Cross Road. There were many worse ways to spend the holidays.

He was in for the biggest surprise of his life. When Severus arrived at the Black mansion, he was greeted warmly by Bella's parents, and his meager belongings were taken to one of the guest bedrooms. It was so grand, he hardly dared touch anything. Even the house-elves were polite.

That evening he was asked down to before-dinner drinks, and Mr. Black insisted that he have a glass of sherry. Severus's initial awkwardness at having to come to dinner in his school robes was quickly dispelled by the kindness of the family, and his reticence at drinking alcohol was pooh-poohed as well. Mr. Black commented on the boredom of the school wardrobe and recommended a tailor. Mrs. Black assured him that sherry `doesn't really count.' By dinnertime Severus felt a relaxed sensation around his mouth and shoulders, and talking had become much easier. Which was good, because Mr. Black asked so many questions. Severus actually had answers for him.

"My mother's family? Landed gentry until 1485, when they chose the wrong side at Bosworth. That's how we ended up in Lancashire. There are some things magic can't fix. But they controlled the Pendle district for generations, Even now we're well-known, that is until the recent... unpleasantness...

"Making new spells isn't glamorous work. It takes painstaking research and hours of experimentation. You have to envision the spell, develop an incantation, adjust for variance in voice and delivery...

"I don't think I would call Dumbledore the greatest Headmaster Hogwarts has ever had. He's made some serious errors since I've been there, and his record regarding improvement of the curriculum is certainly eclipsed by that of Phineas Nigellus."

Severus went to bed that night thoroughly convinced that the Blacks were the most civilized, intelligent, and respectable family in Britain.

The Black evaluation took place between Bella and her parents after the rest of the household was asleep.

"He's more intelligent than I thought he would be," said Mr. Black. "You ask him for an opinion, and he actually has one, one that he can back up with evidence. And he thinks fast on his feet. Do you think he was telling the truth about the spells he created?"

"Rodolphus said he and Rabastan got caught in an earthquake spell when Snape was second year. I'd say anyone who could make an earthquake when he was twelve could do everything he talked about tonight." Bella was clearly proud of her own protégé, and wanted her parents to know it.

"I really think," interjected Mrs. Black, "that you should take him to be fit for some new clothes. He would be quite presentable if he had something decent to wear. I mean, he already knows something of how to behave, better than some of our acquaintances, and it's a shame that people would be judging him on his clothes."

Mr. Black did, in fact, take Severus around to his tailor to arrange for formal robes as well as formal and semiformal muggle dress suits. Severus was proud (and immensely relieved) that he had enough money to pay for the clothes himself, though he mentally calculated how much extra tutoring he would have to do to recoup the amount he was spending. It was more than made up for by a gala night at the ballet, to which he was permitted to escort Narcissa. That he helped arrange a tête-à-tête between her and Lucius was just icing on the cake.

At the ballet, at the theater, at dinners with the Blacks and their friends, Severus found that he was meeting more and more wizards who supported the Dark Lord and his agenda for wizarding Britain. He was moving in a rarified atmosphere, and the effects were heady.

The general consensus about Severus, never divulged to him, was that he was a remarkably talented young man, and something of a social climber. So unfortunate about his father's family, though. The reports back to the Dark Lord were universally favorable.

Severus and Lucius also got together several times over the Christmas holidays. Some of it was about Narcissa, but a lot of it was about spells. Lucius had focus and discipline, but he lacked any background in the sciences.

"I don't understand why we can't just make an eavesdropping spell."

"Sound waves. Sound is disturbances in the air that move in wave-motions. As they radiate outward from the source of the disturbance, they dissipate and weaken. You have to have a way to collect and funnel... Do you understand this?"

"No. But you do. That's all we need, isn't it?"

"I thought you wanted to learn how to do this."

"You handle the theory. Show me the practice."

After several tries with material that didn't work, wool being particularly bad, Severus hit on a spider web-like filament that could radiate out in a cone shape to channel sound waves to a point in space just in front of the caster. Since it was a delicate mesh, it was nearly invisible, and would collapse into a tiny ball in an instant. The incantation took awhile to devise as well, but ultimately Autiarachnon did the trick.

It had taken three days. Lucius went away from the experience with a valuable spell, a deep respect for the art of spell construction, and the wish that he'd been trained to do this when he was younger.

One day shortly after Christmas, Severus managed to escape the Black home and go to South Kensington, to Imperial College. Since it was the Christmas break, most of the buildings were closed. He did manage to get some information about submitting an application which, on the whole, was extremely depressing. He'd attended no accredited grammar school, had taken no math or science courses, had not passed his O-Levels and would not sit for A-Levels, and was in every sense not qualified for admission

\emph{Field work. I could volunteer for field work and get experience. I could get a job in a chemist's shop and prove how good I am at preparing medications.} Severus sat for a few hours in the Natural History Museum trying to figure out a way around the massive obstacle to his dreams. \emph{How can you be a scientist if you don't go to university, and how can you go to university if you've never been to a real school?} The doors to the future were closing, and he hated Hogwarts.

Severus returned to school with the knowledge that in six months he would leave Hogwarts for good, and he had nowhere to go. He could never work for the Ministry of Magic, a thought so distasteful that it made him ill just contemplating it. He could get a job in a shop, or deal in potions like Nana. Maybe, since he'd actually taught himself some real math, he could work in a bank... But he didn't want to work in the muggle world. Muggles were the problem, not the solution.

Regulus had no such concerns. He came from a rich family and assumed there would always be money. "You could buy a yacht and sail around the world."

"I hate water and can't swim."

"You could betray rich widows in Alpine ski resorts."

"Ditto mountains. Ditto skiing."

Their conversation solved no problems, but at least it lightened the mood.

"I," Regulus announced, "shall join the ranks of the Dark Lord and fight for the freedom of our people. Can there be any nobler occupation than the struggle against oppression? To avenge the injuries inflicted upon us by cruel tyrants?"

Severus fought to close out the image of Nana's burned cottage. \emph{Anger destroys concentration. Vengeance is a dish best served cold. They will pay for killing Nana. They will pay for trying to kill me. They will pay for cheating me of my dreams. They will pay...}

"Are you all right?"

Severus looked up at the castle that loomed above them. "Yes, I'm fine," he said. "I need to think about something. I'll catch you at supper." He stood and walked toward the lake, not caring that Regulus looked bewildered and offended.

Sitting on the narrow strip of sand by the lake, Severus tried to sort out the mass of contradictions that was himself and his life. \emph{Muggle or wizard? Scientist or potions master? I'm going to be on my own in six months, and I don't even know who or what I am.}

There were three main questions. \emph{What do I want? What do I need? What can I have?}

\emph{I want payback. From the people who killed Nana. From the people who tormented and tried to kill me. From the mine that fired my father, and the pub owners who kept selling alcohol to an already drunk man. From the people who start wars and the people who embargo oil. From a school that won't tell me what I need to learn until I'm too old to fix it. From... No. Anger destroys concentration. Vengeance is a dish...}

\emph{I want a clean laboratory and a white lab coat. I want banks of computers at Mission Control in Houston. I want the world of microscopes and telescopes. I want voodoo dolls and the Hand of Glory.}

\emph{I need safety. Physical safety and economic safety. Protection and a way to make a living.}

The muggle world provided neither. From airplane crashes to rampaging mobs, it was a world of sudden, violent death. A world where the food on your table depended on a war a thousand miles away. Where they didn't care what you knew, only whether you had the right piece of paper. The wizarding world was no better, full of prejudice and equal violence, where four boys could torment one, and no one cared.

Then he remembered. The one who had stepped forward to save him. The one who had protected him with something more effective than impotent moral indignation. The one who'd charged out of the castle, a small army at her back and wand ready, shouting, "Touch him again, Potter, and I'll..."

Bella.

With Bella he had a place, a place where he was known and accepted, with Rabastan, Rodolphus, and Avery, where Mulciber, Wilkes and Rosier would be, and Regulus Black, too, and eventually Lucius and Narcissa. What did it matter if they didn't really like him? At least they respected his work. And colleagues were always more dependable than friends. Colleagues and a job - it took care of what he needed.

\emph{And of what I want. They'll help me get the payback. Against the people who killed Nana and the people who hurt me.}

That left only `What can I have?' That was when he took the clean laboratory and the white lab coat, the slide rules and the Bunsen burners, the banks of computers and the voice, his favorite voice in the whole world, and packed them away in tightly sealed boxes in the storage room of his mind, toys that he was now too old to play with.

Severus rose from the little sandy area, more settled and focused than when he'd sat down, and went to look for Regulus in the Great Hall.

% \textbf{The Seventh Year: The Catch}

\subsection{Monday, January 9, 1978 (the new moon)}

Severus's eighteenth birthday was cold and clear. He spent the second half of the morning in the library looking up protection spells for buildings and for items left in the open. It was tedious work, and he wasn't sure who was going to get the information when it was done, but Rosier had asked him for it the evening before, and he was trying to finish as quickly as possible.

As he finished his list and gathered his books to go, Severus noticed that Peter Pettigrew was also in the library two tables over. Pettigrew hadn't been sent to watch him since fifth year. A quick glance told him that there were no other Slytherins in the room, not a good sign. He moved three rows closer to the windows, scanned a bookshelf over his head, and picked out a particular volume.

Pettigrew looked up as the book slid in front of him. "What do you want?" he asked.

"Did you know there were seven seduction spells in the Appendix of this book? One especially involves chocolate. Livilla Fairhall likes chocolate, doesn't she? A lot. Of course, if I take it out, then bring it back when you're not here, you'll never know which book it is. They all look so much alike and there are, what, two hundred thousand of them?"

"What do you want?" Pettigrew repeated, but there was a totally different note to his voice.

"Who made you guard dog this time?"

"Sirius."

"Where's he going to jump me?"

"Staircase behind the tapestry. "

"What spell?"

"Petrificus. He has a speech he wants to give you, but he was also talking about tying you to the railing and shaving your head."

"Such tender affection. What does he do to you?"

"Huh?"

"You hate him almost as much as I do. What does he do, insult and belittle you or practice his spells on you?"

Pettigrew didn't answer, his reddening face doing that for him.

"Ah," continued Severus, "he lets you know your place, like the good little dog you are. Here, take it. Good luck with Livilla. Now don't move, this is for your own good." He cast quick binding and silencing charms, then whispered, "Tell him I snuck up behind you. That's why you couldn't warn him."

Pettigrew nodded.

Severus edged towards the tapestry, wand in hand, hoping to surprise Sirius. It didn't work. Somehow Sirius knew he was there, for the tapestry was suddenly pushed aside. Severus got his spell in first, though, and a petrified Sirius fell backwards onto the stair landing.

"My, my. What do we have here? Frozen Gryffindor on a Stick?" Severus stepped over Sirius's body and sat on the step next to him, letting the tapestry fall into place and conceal them. "Such a convenient opportunity for us to have a chat, don't you think? What shall we talk about? I could hang you upside down right here. There's a girls' bathroom two floors down. They'd love to come up and check you out." Then he noticed the wad of parchment sticking out of Sirius's pocket.

"What else do we have? An unfinished homework assignment? A love letter?" He pulled it out, ignoring Sirius's furious glare, and glanced over it. He paused and looked at it more carefully. "My goodness! No wonder you always knew where I was. Here I am right here on the stair, and here you are next to me. And here's that wimp Pettigrew in the library. I didn't have to tie him up after all. You didn't need him to warn you." Severus looked at the front. "Moony, Wormtail, Padfoot, and Prongs. You're Padfoot. I heard Potter call you that. Moony must be Lupin. We all know why. I can't imagine Potter being called Wormtail, so that must be Pettigrew."

Severus stood and smirked down at Sirius. "I know just what I'm going to do. I'm going to give you your map back. Then I'm going to bring you company much more fascinating than I could ever be." He stepped over the supine Sirius again and slipped under the tapestry.

Five minutes later, Filch appeared. Filch's grin was positively evil. Ten minutes after that, and the map was in a cabinet in Filch's office, and Messrs. Moony et cetera were all on detention.

After that day, Severus began to get clandestine visits from Pettigrew, to whom he fed a slow but steady stream of small hexes and jinxes in exchange for information that Severus passed on to Rosier.

A few days later, Severus happened to see Lily and James talking together near the Quidditch field. He'd noticed since the beginning of the year how much closer the two were becoming, but this time they were talking earnestly rather than lovingly. For a moment, just a moment, Severus considered using his new Autiarachnon spell, then shook his head. Lily's conversations were private and none of his business. He turned and walked back towards the castle.

Lily found Severus in the fountain courtyard. "Can I talk to you for a few minutes?"

"Here? In public? That's a first, isn't it?"

"You're right. I think it is. I wonder if there's some special meaning to that, like we've matured and don't have to play games any more."

"Could be. The games were fun, though. There's something about clandestine meetings that adds spice to life."

They were silent. It was a comfortable silence. Friends don't always have to talk.

"James asked me to talk to you."

\emph{Thank goodness she isn't lying about it. I couldn't take that.} "What does he want you to say that he can't say himself? I can't get his map back. I'm not breaking into Filch's office for anything."

"That was quite a coup. You'd have loved listening in to Sirius's ranting after you caught him behind that tapestry. Did you know you had the heart and soul of a bloodsucking vampire?"

"Well I am impressed. I must've really gotten to him to have advanced so far beyond the bloodsucking leech stage."

Lily giggled. "I miss talking to you. "

"You have other things to think about."

"Seriously, though, we're worried about you. James says you're more involved with this junior Dark Lord group, and you're helping them with spells and information."

"Potter has big ears."

"It's like quicksand, Severus. You think it's just an innocent pool of water, and by the time you figure out how deadly it is, you've been sucked in so far you can't get out. This is so much bigger and more sinister than hexes and jinxes. It's dangerous. People are being killed."

"I know."

"Oh, I'm sorry. That's right, your grandmother. But you're in danger, too."

"No. I'm in danger when I'm by myself. That's when I get hit. All those years I never had anyone covering my back. You have no idea how much safer I feel now. And I have somewhere to go after Hogwarts. They're not evil, Lily. It's the world around us that's evil." He regarded her quizzically. "Why so solicitous now? As I recall, two years ago the same prospect made you ready to toss me in the dustbin. Now you..."

"Two years ago the world seemed simpler. Good and evil were clear opposites, black and white. It isn't that simple, though, and I realized how easy it is to set a snare. What about being a scientist?"

"A child's pipe dream. That was never really an option. Not for someone like us. I don't think about it anymore."

"That's sad. It was a good pipe dream."

"How are your dreams doing?" Severus asked, and watched how prettily she colored.

"Good. It's all so... I'm very happy."

"You tell him that if I ever hear you're not happy, I'll turn his tongue into corkboard."

"I will. And you'll think about what I said? And keep your heart open?"

"I will."

Rosier slipped onto the bench next to Severus during lunch in the Great Hall. It was more private there amid all the babble than in the relative quiet of the common room.

"Bella wants to see you."

"I'm flattered. I thought Bella was above Hogwarts now."

"Not where you're concerned. She has maternal feelings for you. You're her own private project."

Severus was not certain if he wanted to be Bella's pet project, but he nonetheless smiled his restrained, sardonic smile and let Rosier know he was pleased. "Where are we supposed to meet?"

"Hogsmeade. Next weekend."

"I'll be there."

\subsection{Sunday, February 5. 1978 (two days before the new moon)}

They met at the Hog's Head Inn, where Severus paid for their drinks.

"I see things are improving for you," Bella commented.

"In some respects."

Bella raised her glass, "Here's to more improvement in more respects."

"I can drink to that."

"You're becoming known in high places. And in a good way. The Dark Lord himself has heard that you're resourceful and a team player. So many are looking only for their own aggrandizement, but you're not one of them. Have you thought of what you'll do after you've sat for your NEWTs and you're finished with Hogwarts?"

"Not really. Not that there are a lot of positions available for someone like me."

"I can think of one."

"I'm all ears."

"Join us. Become one of the Death Eaters. It's a waste for you to sit on the sidelines when you have it in you to play such an important part. Our people have already been attacked in the north - I don't have to remind you of that, you've already lost so much - and the witch-hunting fever is moving into the west and the midlands. We need people to defend our communities, to strike back at our assailants. You could be part of that."

"What would joining entail?"

"You have to be sponsored. That's easy. Several of us could sponsor you. There's an initiation, too. It's an interview with the Dark Lord, and you get a tattoo that shows you're one of us."

"Interview?"

"The Dark Lord is probably the most accomplished Legilimens the wizarding world has ever seen. The interview takes place in the presence of a select group of followers, but it's silent, just you and the Dark Lord. It's minor. A demonstration of loyalty."

"I'll think about it."

"Let me know."

The next move was not long in coming, and it was Sirius's.

"They say you can help me with my OWL in Potions."

Severus looked up from his book. The library was practically empty since lunch had just been served in the Great Hall. The fifth year student in front of him was from Ravenclaw house.

"I usually only tutor inside Slytherin. Who told you to look for me?"

It was clearly an embarrassing question. After a pause the Ravenclaw admitted, "No one. I heard them talking in class and they said you were good."

"What are you weak in?"

"Blended potions."

"They can be tricky. Let me think about it and I'll get back to you. What's your name."

"Sigfried... Sigfried Thurifer. But you shouldn't contact me at our house. Maybe we could meet somewhere..."

"Don't want to be seen with a Slytherin? All right. Where?"

"By the Quidditch stands tomorrow at lunch?"

"Okay. But if I don't show up it means I decided not to tutor you."

Severus sought out Mulciber for advice.

"I don't want to, I've already got too much to do, but I thought you should know."

Mulciber frowned in thought. "You know, Snape, we don't have anyone in the other houses who can gather information for us. This Thurifer could be our toe in the Ravenclaw door, so to speak. Why don't you take him on and find out how useful he is?"

"All right, if you think it could help."

Regulus was in the common room, too. "Isn't the Quidditch field an odd place to meet a pupil?" he asked.

"Away from prying Ravenclaw eyes was the sense I got of it."

The next day at lunch, Thurifer was waiting by the Quidditch stands. As Severus approached, the other boy motioned him forward and moved behind the stands where he was shielded from the castle windows. Severus shrugged and followed, and suddenly found a hood pulled over his head, a cord binding its cloth into his mouth, and his arms pinned behind his back. He tried to throw himself forward and to the right, but was restrained by several pairs of hands. \emph{Not again.}

Behind him, Sirius's voice said, "Here's your money. Now get out. We don't need you anymore."

Severus started to kick, and one of his captors laughed. "We're going to have to tie his feet, too. He might hurt himself." It was a voice Severus didn't recognize.

Sirius laughed as well. "We certainly wouldn't want him to hurt himself. That's my job."

They put binding spells around Severus's arms and legs and carried him under the scaffolding of the bleachers, hidden by colorful cloth panels, where they dumped him unceremoniously on the dirt. Sirius knelt next to him.

"It isn't you personally, Snivellus," he said, in a friendly tone. "Well, yes it is personal because personally I consider you sneaky, slimy, and unwholesome. But things would never have to go this far if you'd just listen when I tell you not to mess around with my brother. Because if I ever find that Regulus has joined up with that Death Eater crowd, I'll kill you. Before I do that, I'll break your kneecaps, rip off your fingernails, and gouge your eyes out of their sockets, but the bottom line is that I'll kill you. Do we understand each other?"

Severus didn't move, so Sirius took the cord that gagged him and pulled, tightening it painfully and jerking Severus's head back. "Do we understand each other?" he repeated. Severus managed a nod, and the pressure was released.

"Now these friends of mine have been looking forward all week to beating the crap out of you, and I have no intention of disappointing them." They pulled Severus to his feet and held him upright. Sirius gave his cheek a gentle pat, then drove a fist into the pit of his stomach. Severus would have doubled over in pain if not for the hands that held him upright.

Then he heard Regulus's voice say, "Hit him again. Go on. Give me an excuse to break your nose against that post. Hit him again."

Regulus helped Severus back to the Slytherin common room, while Sirius returned to Gryffindor.

"What the hell were you thinking of! Hexes are one thing, and sometimes they got out of hand, but beating someone up! Are you insane?" James could not recall ever being so furious with Sirius in all the time they'd known each other. To make things worse, Lily was crying and not talking to either of them.

"He deserves it! I'm not going to stand by and watch him destroy Regulus's life!"

"And you think your own family doesn't have a lot to do with it! Did it ever occur to you that Regulus might be pulling Snape into this? Maybe you're beating up the wrong person!"

"Snivellus has been tight with Bella ever since second year!"

"And Regulus has been tight with Bella ever since he was born! You're cousins, you idiot!"

They both stood, breathing hard, staring each other down.

Lily spoke then, and her voice was very quiet. "He said he needed the protection. That he never had anyone covering his back before, and being with them made him feel safer. I think you just proved he was right. They were covering his back today. What would you've done to him if Regulus hadn't shown up with his friends? I hear that first punch was pretty hard."

"I was angry."

James shook his head. "That's not good enough. You get out of control when you're angry. I know you. You could've killed him. As it is, he'll probably never listen to us again. I mean, how does it look? Lily goes to talk to him about being careful of this Death Eater business and then you jump him? He must think we're the biggest hypocrites in the world. We may never be able to repair the damage you did today."

"If you scared him as badly as you claim," Lily added, "we won't have the chance. He'll never go anywhere alone again."

Severus was lying on one of the sofas in the Slytherin common room while the others did their best to make him comfortable. "How did you know?"

"I told you I thought the Quidditch field was a strange place to meet. I followed you. When I saw Thurifer leave by himself, I went for Mulciber. Luckily they were all together. I wish we'd gotten there sooner."

"Soon enough. That was scary, though. He's your brother. Does he often get that violent?"

"Yeah. Sometimes it's like he's going to explode. He never hides it, and he never tries to control it. On the good side, he never tries to hide his affections either. He can be really nice."

"A side of Sirius Black I have never been privileged to see. And won't if I can help it. I'm taking a bodyguard if I leave the castle again. Maybe even inside it. There're some fourth and fifth years who'd be happy to trade time for tutoring."

"We need to teach Ravenclaw a lesson."

"Agreed. But let me decide what to do. I don't want anyone out of control like your brother. The punishment has to fit the crime."

They waited a week, then four Slytherins jumped Sigfried Thurifer in the quiet fourth floor corridor as he was leaving the library. Hustling him down the stairs behind the tapestry, they suspended him upside down with a Levicorpus spell inside the girl's bathroom. Then they shook him a little to make his money fall out of his pockets onto the floor. Regulus scooped it up with a grin.

"For the Slytherin Defense League. Thanks for the contribution.," he sneered.

Back in the common room they chuckled over the scene. "We didn't hurt him, Snape, I swear, but he looks so stupid hanging there by the cubicles. I hope the girls wait awhile before getting someone to take him down."

"I almost wish I'd seen it," Severus said, "but discretion is more important than personal satisfaction."

"I wish you could teach my brother that."

The spring advanced with little disturbance. Either Severus was too well guarded or James managed to restrain Sirius, but there were no more incidents. Hagrid sent word that he'd have to see Severus one more time. Severus replied that he did not see the need, and was in any case too busy. Hagrid responded that it was purely administrative, a simple matter of closing the books. In late May, Severus appeared at the hut for his appointment. Dumbledore was already there.

"Headmaster, I'm honored," Severus said. "Does two for one mean I'm getting the discount rate?"

Dumbledore chuckled. "We thought you might be pleased. It saves you time this way. You do not have to keep two appointments."

Hagrid followed his usual routine. "Jaw getting bigger. Means the back teeth have lined up better."

"Can they do that?"

"Oh, teeth move around, lad." He checked Severus's ears and eyes, shoulders and spine, then pushed up his sleeves to check the wrists and elbow joints. Severus didn't resist, but his eyes narrowed as he glanced from Hagrid to Dumbledore. "Rickets all gone?" was all he said.

"Looks to be in excellent health, if a tad under weight," Hagrid said as he finished. "I'd say the medical aspect was a success."

"I am pleased to hear it. Sit down, Master Snape. I am sure we both know the drill by now."

Severus met Dumbledore's eyes calmly as he was asked about the last year. "No problems, sir. I assure you," was his answer to Dumbledore's questions.

"Well, that is it, then. I wish you good luck on your NEWTs, Master Snape, and a profitable and happy life after Hogwarts."

"Thank you, Professor. It's kind of you."

As Severus was following Dumbledore out, Hagrid put a hand on his shoulder. "You ever need somewhat, lad, you just come by here."

"Thank you, Hagrid. I will."

There is nothing that will help one better understand a subject than teaching it to others. Severus aced his NEWTs and then it was time to say goodbye. After clearing out all his belongings and apparating home with them, Severus spent hours in the library copying down titles of books he hoped to be able to buy one day.

James and Lily came together. Or rather, Lily came accompanied by James.

"Tell me again, when is this Jupiter fly-by?"

"Not for nearly two years, so don't hold your breath."

"You take care of yourself."

"You, too." On a whim, Severus turned to James. "And you..."

"I know. Corkboard."

The departing seventh years partied on the Express all the way back to London. There was, Severus found, the most intoxicating sense of liberation from time that he'd ever felt. Hogwarts was over and done, never to be returned to. The future had not yet begun. For those few hours the class of 1978 was totally free. It was a good thing the Express sold no alcohol, or half of them would have been drunk by the time they reached King's Cross Station, there was such a strong sense that rules no longer applied.

The farewells on the platform were short as students apparated to their homes. Severus went right to his own kitchen in his own house, registered the amount of accumulated soot from the colliery, and settled down to brew himself a cup of tea over a newly lit coal grate. He was looking forward to a few weeks of solitude.

He got two and a half. Then on July 18, Bella's owl came with the message: `Meet me in London tomorrow. Wonderful news. He'll see you on the 20th. Initiation at sunset. Bring dress robes.'


