% A Difference in the Family: The Snape Chronicles (Rannaro)
% A Tiny Bit About Dueling

\chapter{Gilderoy the Great}

\subsection{Wednesday, August 12, 1992 (the day before the full moon)}

Severus Snape was in his bedroom in the dungeon of Hogwarts castle putting the books in order in his small private bookcase. Professor Snape had a secret passion for murder mysteries, and every year brought a different set from his home in Lancashire to read during his free time at Hogwarts. For years he'd been interested in a series about a medieval monk who also happened to be a potions maker. Thoroughly enchanted with the book he read, he purchased the whole series, or at least as many as had been written and published, and planned to read them in sequence. Now he was fascinated by an English lord and the upper class world of the 1920s. There were enough books in the series to keep him busy and content all year.

That task done, Snape double-checked his room, then the supplies in his office and the orders he'd placed to replenish what was running low or had gotten old, and finally his classroom. All was in order and ready to begin classes in September. \emph{I don't know why we have to be here so early. It never takes me a month to prepare.}

A glance up at the slits that served for windows in the dungeons told Snape that it was probably around lunchtime. He locked up - something he was careful always to do because of the quantity of poisons in his rooms - and went to the Great Hall.

Only seventeen people were there, the Professors and the rest of the staff of the school. Snape sought out Professor McGonagall, who was reading \emph{The Daily Prophet} and sipping a cup of tea.

"Anything interesting?" Snape asked.

"I've located our missing Dark Arts teacher," she replied. "He's in London." She handed the newspaper to Snape and pointed to an advertisement for Flourish and Blotts bookstore. It announced that Gilderoy Lockhart, the celebrated author, would be signing copies of his books at the store that day between 12:30 and 4:30.

"He must be just about to start. Do you want to pop down to London, accost him at his book-signing, and ask him why he's not up here doing his job?"

"Humph. I don't think he'd care. Did you see his book list for the course?"

Snape shook his head.

"Every book he's ever written is on it. He's using this job to increase his book sales and his profits."

Snape shrugged. "Maybe I should write some books. \emph{Potions for the Ungifted}, or \emph{Seven Ways to Burn Your Hands Off While Mixing Floo Powder}."

"More useful than this rubbish. \emph{Gadding with Ghouls}. \emph{Voyages with Vampires}. The man has an alphabet fixation."

The two professors began inventing their own - \emph{Surfing with Succubi}, or \emph{Percolating with Pixies}. Snape's best was \emph{Fan Dancing with Faeries}, but McGonagall topped that with \emph{Grocery Shopping with Grindylows}, and he had to admit defeat.

Later Snape spied Professor Dumbledore down by the lake practicing fly-casting. He went down one of the side paths from the Castle and stood where Dumbledore could see him out of the corner of his eye, but where he wouldn't interfere with the fishing line.

"Ah, Severus, I see you are waiting to ask me something."

"Why Lockhart? Lockhart's a joke. Why not me?"

"I need you around for longer than a year."

"Quirrell was here for three."

"But not in succession. He had that year off. And the third year cannot really count as it was not really Quirrell."

"But Lockhart?"

"I will confess that after Quirrell's demise not that many people were interested in the job. You, of course, but I will not have you. Not yet, anyway. Lockhart seems to think it will improve book sales, but at least he is willing to come. And he has worked with vampires and werewolves, so how bad can he be? Give the poor man a chance, Severus."

"Yes, sir," said Snape, and went back up the hill to spend some time with the English lord.

\sbreak

It was the last weekend before the students arrived, and the teachers were taking advantage of being able to sleep late, linger at breakfast, and not look at a clock or listen to Hogwarts's bell all day. Snape and Flitwick were deep into their second cribbage game when Hagrid entered the Great Hall with a fuchsia vision in tow.

"Good morning, Professors," said Hagrid, and there was a fizzing undertone to his voice that Snape immediately recognized as either suppressed laughter or the onset of pneumonia. "I'd like you t' meet the newest member of the staff, Professor Lockhart. He's just been up t' see Professor Dumbledore. Professor, this is Professor Flitwick and Professor Snape."

`Pleased-to-meet-yous' and handshakes were exchanged, as Snape and Flitwick took in the exquisite coiffure and perfect tailoring that was Gilderoy Lockhart. Then Hagrid delivered his punch line.

"Professor Dumbledore says you're t' show him around."

Snape looked at Flitwick, and Flitwick looked at Snape. There was about to be a fight over seniority, which Flitwick, having been at Hogwarts fifty years longer, was sure to lose, when Hagrid spoke up again.

"That'd be you, Professor Snape. The Headmaster says y're t' settle Professor Lockhart into his room, office, an' classroom, an' show him around the Castle an' grounds."

Flitwick grinned and patted Snape on the elbow. "Have a wonderful day, youngster," he said, and walked out of the Hall laughing quietly.

"Well," said Lockhart brightly, "I must say you are certainly high in the Headmaster's estimation to be selected to escort me on my first day here. I fully intend to mention your kindness in my next book, Professor, uh, Shape."

"Snape. Your classroom is on the first floor. If you would follow me."

As they left the Great Hall, Snape chose not to pay any attention to Professor McGonagall, who had risen from the table and was doing a really superb imitation of Lockhart's stance and gait before an audience of totally silent, yet thoroughly convulsed teachers.

As the two professors left the Hall, Lockhart was remarking on his home schooling and education abroad. They paused at the foot of the marble staircase. "This is quite a large entry hall, isn't it? I say, there must be a zillion staircases here. Don't know that I'd want to climb them all in a day, what? I understand the Castle is... one or two hundred years old."

"Closer to a thousand. And your rooms are on the first and second floors. You should never have to climb higher than that unless you visit the headmaster."

"And that was quite a climb, I'm not ashamed to tell you. Fairly set my heart beating, don't you know, although I am really quite athletic. I won the \emph{Witch Weekly} triathlon competition two years ago. I'm sure you read about it in the papers."

"I fear I don't keep abreast of such things. Here is your classroom."

They entered the Dark Arts classroom, with its rows of desks and benches. Lockhart seemed taken aback. "My, look at the quantity of desks. There must be - six times three, carry the two - at least twenty-six desks here."

"Eighteen, actually. Though your classes generally never run over ten. You have twenty-two sections a week, which in your case is four on Mondays, Wednesdays, and Fridays, and five on Tuesdays and Thursdays."

"My that is a lot, isn't it. Though I'm sure you're used to such things. The packhorses of education. I am so proud to be able to immerse myself in the stultifying routine of your existence this year. I have so much admiration for those of you who do the same dreary thing, day after day, year after year, for the good of our children. I've already planned to immortalize you and your efforts in a new book, \emph{Plodding with Professors}. Once your friends and family see your name in a Gilderoy Lockhart book, you won't be able to keep the adoring worshipers away."

"I can hardly wait," replied Snape. "Your office and private rooms are on the next floor."

"Well, it certainly is old," was Lockhart's first comment after standing and looking around the office and private room for a minute or two. "Rather small and dim too, what? Still and all it is a place to hang one's hat, and we shall make the best of it."

"I am thrilled to hear you say so." Snape's own room was a quarter the size of Lockhart's, and his office smaller and, being in the dungeon, darker.

"Well we are all part of the same team, and I'm definitely a team player. Always something for my colleagues. Now you, for example, you teach what?"

"Potions."

"Ah, yes," and Lockhart nudged Snape with his elbow. "Love philters and tonics for indigestion. Wonderful stuff. Now if you wanted to expand your capabilities, I would be willing to show you a thing or two about the Dark Arts. What to do if you ever meet a werewolf, say, or even a curse or two."

"You're very kind."

"Not at all, not at all. Part of building collegiality and team spirit. And you could show me how to brew, well, whatever it is you brew."

"As you can see, your things have been brought up. Would you like to tour the grounds now, or would you rather settle in here first, and see the rest this afternoon?"

"I think I really ought to unpack here first. Get all the little homey effects out so our minds can focus on what's important. We can meet...?"

"Lunch is at noon."

"Excellent, excellent. That'll give me time to have everything in order. Oh, and Shape, old boy...?"

"Yes?"

"There wouldn't happen to be any extra wardrobes lying around, would there?"

McGonagall was still in the Great Hall when Snape returned. "So. What's our new celebrity really like?"

"He's offered to teach me something about the Dark Arts. Maybe even a curse or two."

"And you said...?"

"I told him he was kind."

"You wicked, wicked, naughty boy! You're going to lead him down the garden path, then turn and pounce on him like the cobra you are. Pomona! Come over here, dear. This is just too rich. Our Snape has finally agreed to accept instruction in the Dark Arts. He may even learn his first curse."

Professors Sprout and Sinistra both joined Snape and McGonagall. "What's this Minerva? I thought..."

"From Gilderoy Lockhart!" McGonagall shrieked with laughter.

"It's true. He offered. He wants to promote teamwork and collegiality, so he's going to immortalize us in a book called \emph{Plodding with Professors}." Snape looked around at the three faces, mouths open in shock. "It's true. Could I make up something like that?"

"Well, actually, you were doing a pretty good job of it a couple of weeks ago," said McGonagall, "but I believe you anyway. Now, are you going to take him on? About the Dark Arts lessons, I mean. I'd love to be a fly on the wall."

"You could be a cat in the corner. I'm not sure though. It might have been first day jitters had him talking like that. I think I'll wait and see if his attitude changes over the next week or so. If he turns out to be decent, no harm done."

"And if he turns out to be a pompous ass?"

"Why then, Minerva, our consciences are clear."

"Five sickles says that he's a pompous ass."

No one would take McGonagall's bet.

Teachers dispersed to work or relax as the mood seized them, then returned to the Hall for lunch. Snape at first hoped that Lockhart was busy with his room and office, but at precisely 12:15, the man walked in. As Defense against the Dark Arts teacher, his place was next to Snape, and he made his way across the Hall and sat down, nodding and smiling to the others as he did so.

"Is everything so far to your satisfaction," Snape inquired.

"Yes, lovely, but odd thing you know. There seem to be a lottish number of, well, heads of garlic here and there. What sort of chap was in the position before."

"Oh yes, Quirrell. You'd have liked him. Last summer he was zapping zombies along the Zambezi. The local prince presented him with a ceremonial turban to mark his status in the tribe. Just your sort of thing. It was purple."

"Really? How nice. Yes, a purple turban would be nice. What happened to him?"

"He died."

"Dear me. Rotten luck. Well, not for me, eh? Rather good luck for me. I say, this food is quite tasty. Who prepares it for you?"

"We have a whole crew of house elves that see to the proper running of the Castle."

"Excellent! I shall speak to them, of course, about the menu and the spicing of some of the dishes. When I was helping the \emph{École de Gastronomie} in Paris rid themselves of some pesky poltergeists, I astounded them with my gourmet dishes. Just a natural talent. It could put the finishing touches on the meals. Oh, and we are seeing the grounds after lunch, no?"

Snape smiled.

It never stopped.

At the Quidditch pitch: "I was asked to play for England, you know. I would have been their best Seeker yet, except I had the misfortune to sustain a minor injury in that spectacular duel with the Voodoo Chief of Pico Duarte and had to sit that season out. After that there were too many other demands on my time..."

At Hogsmeade: "Quaint little village. So charming. Needs a bit of life though, don't you think? I could take a room at the Three Broomsticks for readings of my books to the general populace. It would bring in oodles of people and help the local economy. Do you think once a week would be enough..."

At the Forbidden Forest: "Such a shame you can't use it for something. Nature hikes, camping, sell the timber for profit. If it's just a matter of clearing out the dark creatures, well I'm your man. I'm sure Professor Dumbledore would agree, now that he finally has someone on staff who really understands dark forces. I mean I know all you teachers are very good at the subjects you teach, but the Dark Arts, now that takes practical experience..."

By the lake: "Angling! Now there is a sport that requires a cool head and a gifted arm. I could write the definitive book on fishing if my fans didn't keep me occupied with public appearances, or the world at large with the dangerous task of protecting it from evil. The noble art of fly-casting is one at which I excel, and I hope to spend many pleasant afternoons out here demonstrating the techniques..."

Lockhart returned to his rooms while Snape went to the Great Hall. After the students arrived, the professors would seek more the privacy of the staff room, but for now they enjoyed the luxury of the extra space. Snape went to the table where McGonagall, Flitwick, Sprout, and Sinistra were playing whist, and sat watching them for a few moments. McGonagall caved first.

"Well," she snapped, "don't just sit there and make us suffer. What was it like?"

Snape grimaced. "What truly frightens me is that I'm going to have to sit next to that man at every meal, every day for the entire year. I'll probably restrain myself from killing him, but I may have to cut his tongue out."

"That bad."

"You don't know the half of it."

Flitwick chuckled as he played a jack. "Better you than me, boy. Better you than me."

"What are you going to do to him?" Sinistra asked.

"I don't know, Aurora. I can't just gratuitously strike him, much as I would like to. Something will have to come up that I can play on."

"Severus, that sounds ominous," Sprout said. "What did he say to you?"

"He told me Dumbledore was fortunate to finally have a teacher on the staff with practical experience of dark forces."

It was McGonagall's turn to chuckle. "He may have just pounded the first nail into his own coffin."

Snape gritted his teeth all through supper, then fled to the blissful solitude of his own rooms for the rest of the evening, leaving the other teachers the pleasure of experiencing Gilderoy Lockhart. Monday breakfast looked to be more of the same until Filch came into the hall. Filch normally ate in his own room, so his presence at breakfast was unusual.

"Begging your pardons, Professors," said the caretaker, "but Hagrid's needed down at the gate to admit a delivery."

"Can't ya take care of that yerself, Filch?" Hagrid grumbled.

"Not allowed to seeing as it's creatures. Gamekeeper's job."

To Snape's immense relief, Lockhart sprang from his seat. "They'll be mine, I'm sure. Got the order in just a tad late, but when I mentioned who it was for, the delivery company assured me they'd be here. One of the advantages of fame." He grabbed biscuits and sausages and abandoned the now thoroughly delighted Snape. "I'll just go down with you, my man, and take charge of them myself."

The dynamics of the situation shifted immediately, for Hagrid's authority was challenged. "No ya don't, sir," he said at once. "Living creatures is my responsibility, an' they doesn't come onto school grounds without I personally inspects them."

The outcome of the confrontation was that Hagrid and Lockhart went together down the hill to the Hogsmeade gate to bring in and pen Lockhart's living creatures.

Snape went down to Hagrid's hut later in the morning because curiosity was burning him like a consuming fire. He found the door open, Hagrid fuming over a pot on the hearth muttering into his beard, and a large crate in one corner of the room. The crate was emitting piercing squeaks and whistles.

Hagrid looked up at Snape standing on the threshold. "You got a brain between y'r ears. Bet ya know what's in there."

Snape crossed to the crate and listened to the piping and trilling. "Pixies?" he ventured. "Cornish pixies? Are you sure you want them in your hut?"

"There. There's still someone with an ounce of sense in the school. He wanted t' open the crate and look at 'em right there at the gate."

"How many are there?"

"A good dozen."

"And he was going to release them into the air on the grounds?"

"There ya go. But he's the professor with all the experience handling creatures, so I don't know nothing."

"He told you that?"

"He did. But I'm big as about ten of him, so it really weren't no argument."

"Whatever are they for?"

"His first class Wednesday afternoon. He's planning t' test the students' mettle."

"And I have a class then, too. Drat! I'd love to see it."

Word spread quickly about Lockhart's little surprise, primarily because Snape told almost everyone else in the school personally. His excuse was that he was looking for volunteers to help contain the pixies when they got out of Lockhart's control, but the truth was that he was turning into a terrible gossip where Lockhart was concerned.

It was McGonagall who revealed this unpleasant fact to him. "You're turning into a terrible gossip where Lockhart's concerned, you know," she told Snape after supper.

"No I'm not. I'm just relaying essential information in the hope of averting a catastrophe."

"I think you need a nice saucer of milk before you go to bed tonight."

"All right, all right. But you don't have to sit next to him all the time."

\sbreak

\subsection{Tuesday, September 1, 1992}

The day that the students were to arrive was an especially hectic one as every teacher made last minute checks of his or her classrooms and materials. In particular, the teachers who were heads of houses had to inspect the dormitories and common rooms.

Around noon, Snape finished with his checklist for Slytherin house and headed for the Great Hall and his last relatively peaceful meal until the Christmas break. \emph{And today I'm sitting at the other end of the Hall. There must be something I have to discuss with Professor Vector today. Then again, that would put me next to Professor Trelawney. Hardly a trade-up. Would Trelawney like Lockhart? I wonder.}

Professors Sprout and Flitwick were whispering together in one corner, and Sprout waved to him to join them. "The most distressing thing has happened. Two students refused to board the train!"

"That's impossible," replied Snape. "No one refuses to get on the train."

"These two did. They were at King's Cross, but wouldn't even go onto the platform."

"Who was it?"

"Two of Minerva's. The youngest Weasley boy and, you'd never guess it, Harry Potter. Dumbledore got a message from Arthur and Molly. It seems the two stole the family car as well. Poor Arthur's had to admit that the car does things it shouldn't. Like fly."

"It isn't hard to believe," said Snape. "It's the sort of stunt Potter's father would've pulled. Anything to stay in the limelight. And I was hoping this year would be relatively normal. How's Minerva taking it?"

"She's furious," said Flitwick. "Dumbledore's trying to calm her down. She still hasn't gotten over the hundred and fifty points she had to deduct from Gryffindor on Potter's account last year. I understand she'll be waiting on the lawn with a crossbow to shoot them down."

"Assuming they can get in." Snape thought for a moment. "Much as it would serve them right to hit the defenses in that car, it wouldn't do to have squashed student all over the place. Aside from unnecessarily irritating Filch, it would upset some of the parents. He'll have to let them land."

Late afternoon brought the owls with copies of \emph{The Evening Prophet}. Shock and anger swept through the ranks of the teachers as they read about the unforgivable carelessness of Weasley and Potter in allowing the magical car to be seen several times.

"Don't they understand what it means to have muggles aware of our world?" cried Professor Burbage as she threw the paper down on the table. "You'd at least think Arthur would teach his children some discretion."

"We are talking about the father of Fred and George, you know," commented Sprout. "I think the only child they have who doesn't get into trouble is Percy."

Snape was nodding agreement when Dumbledore strode into the Hall. Moving to a table in the corner, he motioned Snape to join him.

"I fear, Severus, that I must place a distasteful duty on you tonight. You have, of course, heard of our errant twosome. We do not know yet when they will arrive. I need someone outside patrolling the grounds during the feast..."

"I'll do it."

"Really, I do know how much you must be looking forward to the feast, and explaining the Sorting ceremony to our new Dark Arts teacher..."

"I'll do it. Just tell me what it is, and I'll do it."

And so it was that later that evening, as every other denizen of the castle was joyfully preparing for the arrival of the students, the Sorting, and the feast, Professor Snape was down by the Hogsmeade gate with a pair of binoculars, searching the sky for a turquoise Ford Anglia with two twelve-year-old boys in it and feeling himself very lucky indeed.

It was getting late. The train arrived, the thestral carriages climbed the hill, and the boats had crossed the lake with the first years before Snape heard the car's engine. He was, at that moment, near the Quidditch pitch, reasoning that it presented a large, clear area in which to land. The drivers of the car had other ideas.

The car came across the lake, and there was enough light from the setting quarter moon to glint off its windows and chrome. As Snape watched in growing horror, the car headed straight toward the hill and the wall of the Castle on its peak. \emph{They're going to crash the car into Hogwarts!}

The car disappeared from his view, yet there was no crash. \emph{They must have missed it on the other side, which means they're headed for the Forest}. The quicker way was along the narrow beach at the base of the hill, and Snape hurried as fast as he could in the moonlight. Shielded by the rock of the hill, he heard no sound.

Rounding the hill Snape could see the black line of the forest and the lighter shadow of the Whomping Willow, but nothing else. No car, no students, nothing. He strode forward until he was abreast of the willow, where he lit a Lumos spell.

The willow was in dreadful shape. Broken branches lay scattered about, and there were great tears and dents in its bark. One huge branch had split away from the trunk and hung mutilated, ready to fall onto the grass. Nearby were the marks of the car's tires ripping up the sod, leading into the forest. Snape followed them a short way under the trees, but saw no sign of the car.

Climbing back up to the Castle, Snape could see clearly the traces where Potter and Weasley had dragged their luggage. \emph{At least they're not in the forest. But what did they do with the car?} At that moment cold fury broke through Snape's barriers. \emph{Just like his father. Has to be special. Has to be noticed. Doesn't think about the consequences and doesn't care about the rules. And doesn't care who or what he hurts.}

As Snape reached the castle steps, his anger abated a bit. \emph{It's always possible they hit the tree by accident and are scared and contrite. I wouldn't mind seeing Potter contrite for once. Rare moment.} But it was not to be. From the steps leading into the entrance hall Snape saw both boys peering between the massive doors of the Great Hall at the feast, and as he approached silently, he overheard:

"Where's Snape?"

"Maybe he's ill!"

"Maybe he's left because he missed out on the Defense against Dark Arts job again!

"Or he might have been sacked! I mean, everyone hates him -"

Standing right at their backs, his voice as low and deadly as he could make it, Snape entered the exchange. "Or maybe he's waiting to hear why you two didn't arrive on the school train."

Although clearly not contrite, the boys had the sense to appear nervous, maybe even embarrassed. Snape led them down into the dungeon area to his office. The room was dark and cold. As he entered and closed the door, Snape turned with his back to it to face the shivering boys. He was fighting to control his anger. Dim moonlight still filtered in through the slits near the ceiling.

"So, the train isn't good enough for the famous Harry Potter and his faithful sidekick Weasley. Wanted to arrive with a bang, did we, boys?"

And of course, Potter tried to blame someone else. "No, sir, it was the barrier at King's Cross, it..."

"Silence!" Snape ordered, his voice still low. "What have you done with the car? You were seen." He snapped his fingers for light and showed the startled boys the headlines of \emph{The Evening Prophet}, then read part of the article to them. By this time he was calmer. He looked up at Weasley, "I believe your father works in the Misuse of Muggle Artifacts Office? Dear, dear... his own son..."

Potter seemed more upset about that than Weasley. Snape continued. "I noticed, in my search of the park, that considerable damage seems to have been done to a very valuable Whomping Willow."

Incredibly, they still tried to shift blame from themselves, for Weasley burst out, "That tree did more damage to us than we..."

"Silence!" Snape's anger flared again, and he no longer trusted himself to keep his voice low. "Most unfortunately, you are not in my house and the decision to expel you does not rest with me. I shall go and fetch the people who do have that happy power. You will wait here."

He left the boys in his office and went to find McGonagall.

The Sorting was finished and everyone concentrating on the food as Snape made his way along the edge of the Great Hall and slipped behind McGonagall's chair. He whispered so that both she and Dumbledore beside her could hear. "I've got the pair of them. They're in my office."

Dumbledore nodded, but McGonagall rose at once. As the two professors left the hall, McGonagall began to question Snape. "Are they hurt?"

"Not really. Weasley has a small cut over his eye. They don't even seem too shaken up, though Weasley will claim the Willow damaged them. They brought up their own things, and when I found them peeking into the Hall, they were speculating on whether or not I'd been sacked because they couldn't see me at the table."

"Dear, dear. That doesn't sound at all penitent. What happened to the Willow?"

"They drove the car right into it. It'll need major work in the morning. Poor Sprout. I haven't the heart to tell her now."

"Have you deducted points from Gryffindor?"

"No. I wasn't thinking about points."

They reached Snape's office door. "How do you stand the cold down here, Severus? My fingers are numb already." As she entered the room, McGonagall raised her wand and lit the fire. The boys cringed as if they thought she would curse them. "Sit," she commanded. "Explain."

It was as ridiculous a story as Snape had ever heard, about the King's Cross barrier not letting them through, and stealing a flying car that just happened to be parked in the center of London. Both Snape and McGonagall already knew about the car from the Weasleys. When McGonagall asked why they didn't send an owl, the pair blushed scarlet.

Then Dumbledore knocked and entered, and the whole tale was repeated. As Snape listened, he watched Dumbledore, and the realization slowly dawned that the Headmaster did not intend to punish the boys. Sure enough, all Dumbledore would do was write to their families. \emph{But Weasley's family already knows, and Potter's family doesn't care. So he's not punishing them at all!} Snape coughed slightly.

"Professor Dumbledore, these boys have flouted the \emph{Decree for the Restriction of Underage Wizardry}, caused serious damage to an old and valuable tree - surely acts of this nature..."

Dumbledore would not budge. Turning all responsibility for the matter over to McGonagall, he put an arm around Snape's shoulders and practically pushed him out of his own office. "Come, Severus, there's a delicious-looking custard tart I want to sample..."

Snape glanced back at McGonagall, yet had no choice but to accompany Dumbledore. Once in the corridor and out of earshot of any students, though, he refused to be silent.

"It isn't right, sir! It isn't fair! If it were any other student in this school you wouldn't leave it in the hands of the head of house. What they did happened outside and affected the whole school, not to mention the work it's created for Professor Sprout. And that story!"

Dumbledore stopped and, with both hands on Snape's shoulders, turned him so they faced each other. "Severus, look me in the eyes."

Snape glanced up into Dumbledore's blue eyes, then down again. His gaze darted from place to place in the corridor, then fixed on the floor.

"Do not worry, Severus, I am not going to try to read you. But do you remember how many times you lied to me when you were a student? Admittedly it was usually to conceal what someone else had done to you, but they were nonetheless lies. And I did not punish you for them. So in the broader picture of things, I do not think I am being unfair. Consider it payback."

"Yes, sir."

"I now have you in a most difficult position. You cannot go back to your office and rooms as they are currently being used by Professor McGonagall to discipline students. You are therefore constrained to go back with me to the Hall and get some of that wonderful food that you have not had a bite of yet. And you will sit with me in McGonagall's seat and not have to talk to Professor Lockhart all evening."

Snape agreed and went with Dumbledore to the feast. The only bad moment was when McGonagall returned and informed him that the boys were eating supper...

"In my office! You left those two hooligans alone in my office unsupervised!" Snape rose to go, but Dumbledore pushed him firmly back into the chair.

"You have to learn not to be so paranoid, Severus. Have some custard. It really is quite good."

\sbreak

Though he would never admit it to anyone, Snape had a certain respect for Molly Weasley, a woman he'd met on very rare occasions. She was the sister of the Prewett brothers who'd been murdered during the time Snape was a Death Eater, and despite the fact that he had nothing to do with their deaths, Snape always felt guilty about it. More importantly, Molly was ready to do something that few others had the courage or stamina to do - discipline her sons. It was a Herculean task, especially where Fred and George were concerned, but she never gave up.

That next morning, Snape had cause to bless Molly Weasley, for she sent her youngest son a Howler. "RONALD WEASLEY!" it thundered across the Great Hall at breakfast, silencing all conversation as heads snapped around to listen to Weasley's mother telling him he should be expelled, he had shamed the entire family, and he would be brought straight home if he put another toe out of line.

\emph{Thank goodness she sees the situation clearly. Too bad there's no one to send a Howler to Potter. Maybe I could speak to that uncle of his.}

Then, since the week was half gone and there was no extra day for interviews with new students, it was time to begin classes.

At lunch Snape noticed that Professor Sprout glared down the table from time to time at Lockhart. Lockhart was explaining how he managed to rid a Brazilian village of bewitched marsupial anteaters, but Snape finessed the conversation around to the Whomping Willow.

"Professor Sprout was most fortunate that I happened to be here to assist here with that fine specimen of a tree. I'm sure she's quite competent with her subject matter, vegetables and all, but a willow of that sort needs a specialist's care. Luckily I happened to have some experience with..."

Snape was thinking of a way to rent out Lockhart's services to people with chronic insomnia when he remembered - "Excuse me, Professor. I'm sorry I have to run, but I have interviews with some of my students before afternoon classes."

One student actually, Draco Malfoy, who was waiting outside Snape's office. He was there to show Snape the results of his summer homework, which was to create a spell to permit one to have a conversation that couldn't be overheard. Snape didn't expect him to have the spell, and he didn't, but he'd grasped the concept that silencing spells didn't create silence. Rather they targeted specific sound frequencies and either masked or augmented them. Snape gave the boy some pointers on how to proceed with the task.

"Sir," said Draco, when they were through, "could you teach me to defend myself?"

"Your Defense against the Dark Arts teacher is Professor Lockhart."

"I don't mean that, sir. I mean defend myself. Father says you used to be a defensive combat instructor for..."

"I don't discuss certain periods in my past, and I'd prefer you didn't either. What makes you think you're going to need self defense?"

"Well I don't know that I'm going to need it, but if you wait until you need it, it's too late, isn't it?"

"Good point. All right, I'll consider it if you accept that it isn't all magic. The first thing you'll have to learn to do is fall."

"Fall? Fall down? What would I want to fall down for?"

"If you don't know how to do a diving forward roll, you may not have the chance to get your spell off. You think about it, Malfoy, and let me know."

And then there was the news about Lockhart's pixie class. Snape was not among the lucky few to have a free hour that afternoon. Those who did regaled the others with their account of how Lockhart had been driven ignominiously from his own classroom, which now looked as if a bomb had exploded inside it. Kettleburn and Flitwick howled with laughter as they repeated the incantation \emph{Peskipiksi Pesternomi} to the delight of all listeners.

"Where are the pixies now?" asked Snape.

"About half a dozen broke through the windows and are being rounded up outside. A couple of students got the rest," answered Kettleburn.

"And which students might those have been?"

"Harry Potter. And Weasley and Granger, I understand."

\emph{My money says you should've named the Granger girl first. I'll wager Potter had a lot less to do with it.}

On his way back to his rooms to get ready for supper, Snape ran into Marcus Flint, the captain of Slytherin's Quidditch team. "Sir. Begging your pardon, sir. Could I have a word with you for just a minute. Something's come up."

"Certainly, Flint. Come on in. Is this about you or the team?"

"Team, sir. We got a chance to get something good for the team, but there's tit for tat involved."

"All right, what's the good?"

Flint held out a broomstick. Even Snape, who had about as little experience with brooms as was possible for an adult wizard, recognized the quality. It was sleek, streamlined, and obviously fast. "Nimbus 2001, sir, seven of them. Just out last month and a present to every team member. We could sure use them."

"I heartily agree. What's the catch?"

"They're from Malfoy's father. Draco's to be the new Seeker."

Snape sat on the edge of his desk to consider. "I see. On the one hand, Mr. Malfoy is on the Board of Governors of the School, and the team gets new brooms. Of course, Mr. Malfoy was in Slytherin, and it's not unusual for former house members to present gifts. In and of itself, that's not the problem. The problem is the other hand. It's odd that the gift would be directly connected to Draco's becoming Seeker. Mr. Malfoy is usually more subtle than that, and he would have come to me."

"I'm not sure how it's happened, sir. I got the feeling Draco told his dad that he already was Seeker, and his dad gave the brooms as a thank you. So it's Draco sort of controls the brooms. We could sure use them."

"But not at the expense of a good Seeker. Who else is in line for the position?"

"That's it. No one. Draco's good on a broom, he's quick, and he's hungry. He really is the best shot we got. It just doesn't look good. And Draco, well he can get cocky, if you get me."

"Got you. The insufferable arrogance of the rich. Look, Flint, why don't you make him try out? Even if no one else shows. Tell him if he can't make the grade then you or Derrick'll be Seeker, and brooms be damned. You know he'll make it, and I know he'll make it, but he doesn't have to know. Sound good?"

"Cracker Jack, sir. We'll have to train him up. Wood's booked the pitch solid. No one else's got a shot before next month, he got in so fast."

Snape reached for a small parchment roll. "Here. If Malfoy is satisfactory, take this to the pitch on Saturday. It gives you permission to use it together with Wood. It's a large area. Just keep out of each other's way."

"Thank you, sir. For this and for the advice."

On Friday Flint informed Snape that Malfoy had, indeed, been accepted on the Slytherin Quidditch team as the new Seeker.

\sbreak

"And what right did you have to take the pitch away from Gryffindor when it was already booked?"

Snape was taken aback at McGonagall's ire. "I didn't take it away. I allowed it to be used at the same time."

"Wood booked it in advance!"

"Wood booked it for four weekends in a row! You can't expect that no one else can train until October. Talk to Flitwick. Talk to Sprout. I'm sure they're not happy either."

"You're just afraid that we're finally going to take that cup away from you this year."

"I am afraid of a lot of things in this world, Minerva McGonagall, but that is not one of them."

The two professors glared at each other for a moment, then a spirit of Puckishness entered Snape. "I understand that rather than train at the same time, your team simply abandoned the pitch. Walked away. Gave up. Surrendered without a fight. Starting with your Seeker."

"Weasley was spitting up slugs. He needed help."

"I sympathize. Not a pleasant experience. But Weasley is not on your team. And Granger was there. And what's-his-name - Creevey - was there. There were others to help him. No, your Seeker just walked away from his team mates. If anyone wins the cup this year, it will be Slytherin."

"I will see you eat those words, Severus Snape, if it's the last thing I do!"

\sbreak

By October it was easy to see that Lockhart had alienated the entire faculty, except perhaps for Filch since Snape could find no one who'd ever heard Lockhart claim to be good at janitorial work. Snape still had to sit next to the man at meals, and had started refining sleeping and paralyzing draughts, and begun to practice using an Amazonian blow dart.

Malfoy was turning out to be better at hand-to-hand combat than at spell construction. At first he balked at learning the physical techniques until Snape challenged him to a personal duel by the lake during supper. Alone and unwatched, Snape allowed Malfoy any spell he could think of, while Snape promised not to hit Malfoy at all, and use only one defensive spell to every two of Malfoy's attacks. After ten minutes, the boy was ready to learn anything Snape could teach him.

This physical self defense had always been a strain for Snape to teach, since he had to analyze, for the instruction of others, body movements that for him were instinctive and adapt the analysis to fit uniquely different students. Then, while eager, Malfoy was not remotely athletic off a broom. Still, they slowly progressed, and it quickly became clear that Draco was immensely pleased to be learning something Lucius had not learned in his youth.

After much serious thought, Snape also sought out Dumbledore during the first week of October. Together in the quiet period before supper one evening, they walked down the hill and into the edge of the forest where the trees would frustrate listening spells.

"I think you were wrong about me," Snape said after a moment of silence.

"How so?"

"The first time I lied to you, when I told you we were just talking about summer vacation, you should have stopped me."

"Ah, yes. That little fight Professor McGonagall prevented between you and the Gang of Four. As I recall, you were restricted to your dormitories."

"It wasn't enough."

"What was I to do? I could not prove you were lying. I could not even tell that you were lying, and that disturbed me, I assure you. The only reason I knew it, was because Professor McGonagall witnessed the confrontation."

"You should have forced me to show you the truth. When you know you can get away with something, it tempts you to break more rules. It makes you arrogant."

"We are talking about Harry Potter, are we not?"

"I don't think you should let him lie to you and go unpunished. Or at least let him know that you know. Don't let him think he can deceive you."

"Severus, we do what we can, but we cannot see the future. Sometimes being too strict is not the answer. What would have happened to you if in school I had broken down those amazing defenses you have? You would never have been able to stand up to... him. And we very likely would not be here today to have this conversation."

"Are you honestly telling me that you're allowing Potter to break rules today in order to save the world tomorrow?"

"Well, not exactly. It might happen though. Especially since things have changed somewhat since last year. The boy needs to be strong, not timid. He has his special gifts, just as you have yours, and they must not be weakened in the exercise of misguided strictness."

"He is going to continue lying to you."

"As you did. But in the end you came around. And the strengths you had when you finally did come around served us well."

"I still don't agree with you."

"Then it is fortunate that I am the Headmaster, and not you. The boy has a good heart. He will not stray too far from what is right."

"Perhaps, Professor. I still think events could prove you wrong."


