% A Difference in the Family: The Snape Chronicles (Rannaro)
% The Fifth Year

\chapter{The Last Peace}

\subsection{Sunday, August 31, 1975 (2 days after the last quarter)}

Severus returned to Nana's house for the last few days of summer, packing and showing her how well he'd studied his lessons. On the last day of August he was taken to the train station at Colne by the parents of Bill, the young man who'd fallen from the roof. Nana and Gra teamed together to buy his ticket. Severus would have preferred to apparate to Hogwarts with Nana, but everyone else agreed the Express was the best way to arrive.

Truth be told, Severus didn't want to spend the night at St.~Pancras. The last time he'd been there was before his parents died and that, coupled with his physical growth, made the idea of hiding in church pews, well{\el} distasteful. On his arrival at Euston Station, he carried his things to King's Cross and left them to call for the next day. Then he checked a directory for youth hostels. There were several within walking distance.

Not being able to take economics at Hogwarts, Severus was unfamiliar with the term `opportunity cost,' but that day made him aware of the concept. Even the modest charge for a bed at a hostel would seriously deplete the small amount of money he'd managed to save over the summer and limit his choices for the future. Poverty in the countryside of eastern Lancashire was a gentle nudge. Here in London it was a sledge hammer. Severus spent the night at St.~Pancras.

The Express to Hogwarts was a different story. Here he could use the knuts and sickles he'd made tutoring other students the year before. In the Slytherin club car where Bella Black greeted him warmly, he was able to contribute to the refreshments. It was nice to be back with his classmates.

Bella was preening for everyone. She was now a seventh year, and whatever else happened, this would be her last trip on the Express to Hogwarts. She and Rodolphus Lestrange were not officially engaged, but they were so clearly an item that it was occasionally embarrassing. Those in Severus's class were already talking about their OWLs, and clearly many of them were already nervous. Severus found several classmates being conspicuously nice to him.

There was another topic of conversation, one discussed in muted tones at corner tables. For the first time in a couple of years, Severus again heard rumors of attacks on wizards and their families by a dark lord and his servants, a rising figure of power whose very name the students were afraid to say. He thought of all the whispered `you know' in his dormitory in previous years and made mental connections. It appeared that no Slytherin families had been directly harmed, but he got the impression the same could not be said about students in Ravenclaw, Hufflepuff, or especially Gryffindor. It was on this train ride north that Severus first heard the phrase `death eater,' without understanding what it meant.

\subsection{Thursday, September 4, 1975 (the day before the new moon)}

Severus and Lily exchanged glances in Potions class with the understanding that they would meet at the lake, but it was not to be. On his way to his Care of Magical Creatures class outside, Severus passed by a group of Gryffindors.

"Hey, Snivellus!"

Severus affected not to hear.

"Snivellus!" Sirius Black was suddenly in front of Severus, blocking his path. "You should stop and listen respectfully when your betters address you."

"If any did, I would." Severus knew the other three were moving behind him, but he doubted they would do anything here, in full view of the castle windows.

Sirius's eyes narrowed dangerously. "If I had a beak like yours I wouldn't show myself in public. It's so big it'd give my neck a permanent twist."

"That's only because your brain isn't big enough to balance the weight."

Sirius's fists came up, but James moved between the two to block the punch. "Did you hear how the Slytherin insulted a Gryffindor?" he said. "I think you should take five points from Slytherin, Remus."

Severus turned to look at Remus and saw the Prefect's badge. "So you and who else together make a whole prefect?" he asked. Remus blushed.

James thrust his face within inches of Severus's. "You're making it hard to give you friendly advice, Cursemaster, but I'll try. Stay away from Gryffindors. You think we're scared because a few of your coward friends ambushed people over the summer, but if you try to bring it into Hogwarts, I'll take you down myself."

Before Severus could think of a reply, Professor McGonagall was in their midst, and all five of them found themselves unceremoniously herded into Dumbledore's office.

"This is not," said Dumbledore, looking over his glasses at the five boys, "the first time that three of you have been brought here for disturbing the peace at Hogwarts. I understand that it is even further from the first time that you have all behaved in an unruly and potential dangerous manner towards one another, though on many of those occasions you were not apprehended. What have you to say for yourselves?"

"We were just talking," said James. "Having a discussion."

"And what might that discussion have been about? Master Snape?"

Severus looked Dumbledore straight in the eyes. "We were talking about the summer, and how we wanted this year to be a good one."

Sirius and James glanced at Severus, then at each other. Remus and Peter stared at the floor. Dumbledore's expression became even more grave.

"I know that you are all aware of incidents over the summer that have raised tensions in both the wizarding and muggle worlds. It is of vital importance that these incidents not spill over into Hogwarts. All of the staff have been advised to regard any incident of practical joking, hexing, or hazing as grounds for detention or more severe punishment. Do I make myself clear?"

All five boys nodded.

"Good. Now I should like to ask you to set an example of restraint. Although none of you is on detention, I should like you to voluntarily restrict yourselves to your own dormitories this evening as a sign of desiring peace between your houses. Is that agreeable to you?"

"Yes, sir," said James immediately, and one by one the other four consented as well.

James stopped Lily as she was leaving the Gryffindor common room to go to supper. "Your friend won't be meeting you tonight."

"I don't know what you're talking about."

"The funny looking one with the big nose and the greasy hair. He won't be meeting you tonight."

Lily turned and confronted him. Part of her was worried, but most of her was furious. "You nasty, arrogant, supercilious, obnoxious, arrogant pig! Why can't you just treat people normally?"

"Because I'm nasty, supercilious, and arrogant. But he still can't meet you. Dumbledore's restricted us to our dormitories. Him too."

Lily didn't know what to say. She knew James was telling the truth, so it was nice of him to warn her. At the same time he was so unpleasant about it that she wanted to shake him. "Thank you," was what she finally did say, and went to supper.

Dumbledore's evening walk managed to take him past Hagrid's hut. There he knocked and was welcomed in for tea.

"Hagrid, we have a problem. It is the Snape boy."

"I'm sorry t' hear that. I thought he were doing better."

"As did I, but there has been an unforeseen change. He and the Gryffindor four were brought up to my office today because Professor McGonagall thought they might come to blows."

"Well that's happened before, hasn't it? Did come t' blows once or twice as I recall. Creative blows, too."

"Ah, but this time I asked him what happened and he told me they were just talking about summer vacation."

"Well a boy's not s'pposed t' peach on his mates, even if they are enemies."

"That was not the problem. The problem was that I could not see it. They were confronting each other outside, but when he came into my office, he concealed it. And I could not see it. If Professor McGonagall had not told me the whole incident, I would not have known he was hiding something. I saw what he wanted me to see."

"Ain't that what you been training him t' do?"

"You are right, Hagrid. It is my fault. I just did not realize he would be so good at it."

\subsection{Tuesday, September 9, 1975 (3 days before the first quarter)}

Severus and Lily got together again as the moon waxed. Severus had to admit that he'd missed the Soyuz launch, but then he explained why. Lily was fascinated with Nana's healing powers, and wanted to learn some of them, too. She also seemed interested in Severus's family history, though she most emphatically did not want to touch the shrunken head.

Their new projects were Viking and Venera. The recent international cooperation had led to an indirect and potentially far more profitable development. The Americans were going to investigate Mars, while the Russians checked out Venus. Both programs consisted of two spacecraft working together, and Viking 1 had launched on August twentieth. Viking 2 was going up at 18:39 on Tuesday. They had completely missed the Venera launchings the previous June, but the two spacecraft would arrive at Venus in October. Viking would take nearly a year to reach Mars.

Severus planned to borrow a telescope from the Astronomy classroom so they could see Mars, and the two had a date for Tuesday.

Remus put the final touches of ink on the parchment and sat back. "There. Finished. Who'd have thought the school was so big. And with hidden passages."

James admired his handiwork. They'd been working on sections of the map for more than a year, but now it was complete in the sense that it was comprehensive. There were still details to be added. "A masterpiece. We need to commemorate the occasion by using it tonight. Where shall we go?"

"Hogsmeade," replied Sirius at once. He was idly spinning web traps between the posts of his bed.

"You bore more easily than any other human being I know. Let's take the map with us, get some supper, and go marauding."

Shortly before seven o'clock, the four friends left the Great Hall. Slipping into the waiting room, they took out the seemingly blank map, and James ceremoniously pronounced, "I solemnly swear that I am up to no good." All of Hogwarts and its grounds resolved itself before them, with little moving dots, each labeled with a name.

They studied the map for a while, arguing over where to go. Remus glanced at a corner, then quietly folded that section under, but not quietly enough to escape Sirius's notice.

"Anything interesting over there?" Sirius asked.

"No," replied Remus, but Sirius unfolded the map anyway.

"Hey, Prongs. Look at this. Evans and Snivellus are down by the lake together. That girl has a peculiar taste when it comes to boyfriends. Thought you told her to stay away from him."

James looked at the two dots. "I think we should pay a visit to the lake."

All the way down the hill, Remus tried to talk the others back into the castle. "They're not hurting anyone," he insisted.

"He's probably teaching her dark magic and recruiting her into the Death Eaters. Whatever they're doing, we're going to stop it."

"Either that or kissing," laughed Sirius, "and we'll stop that, too. Can you imagine any girl wanting to kiss him?" For some reason, James didn't laugh at the joke.

What they saw was neither Dark Arts nor romance, but something so totally unexpected that none of the four made a sound. A telescope on a tall tripod was set by the lakeshore, and Lily was peering into it. Severus stood to her right and a little forward. "Can you see the moons?" he was saying.

"One of them. It's pretty bright. Could it be reflecting sunlight that far out?"

"Probably. Even the tiniest light makes a difference in all that darkness."

"I think I see the other one now. It's a lot fainter."

For some reason that he couldn't explain, James was more disturbed by this scene than he would have been by any black magic or making out. He rose slowly from the bushes and stepped onto the narrow beach.

"Well, well," he said quietly as Lily and Severus turned at the sound, "two lovebirds stargazing. What'll we have to do about that?"

Severus could feel himself shutting down in preparation for battle. A part of his mind registered how automatic the reaction was, the rest of his mind was assessing the situation. It was like that winter day three years earlier against Rabastan and Rodolphus, except that today it was four to one, and he had Lily to take care of.

Lily didn't seem to think she needed taking care of. "What're you doing here bothering people?" she snapped. "I never met anybody who stuck his nose into other people's business as much as you."

Sirius stood now and joined James, Remus and Peter a pace behind in the darkness. "You have a peculiar taste in boyfriends," Sirius said.

"Boyfriend!" Lily paused, a sly look coming over her face. "And what if he is? What's it to you?" She moved closer to Severus.

"Don't get in the line of fire," Severus said quietly. "I need a clear shot."

"You can't fight all of them. It's four to one."

"Two and two halves to one. Maybe only a half and a quarter."

Sirius, wand in hand, was edging away from James, moving more to Severus's left side. "You've got a smart mouth, Snivellus. Did you hear that, Remus? Peter? Snivellus thinks you're not good enough to fight him."

"Remus!" Lily called. "You're not part of this. You're better than this."

Remus shuffled uncomfortably. "You don't know what he's mixed up in, Lily. He's dangerous. He's training people in the Dark Arts."

"That doesn't give you the right to gang up on someone four to one."

"Lily, move out of the way." Severus was icily calm.

"You can't fight all of them!"

"They're not giving me a choice."

Remus stepped past James, turning to face him, his back to Severus and Lily. "She's right," he said. "This is wrong. I'm not with you in this. You keep it up and it's three to three."

"I don't need your help," said Severus.

"I'm not helping you, Slytherin. I'm a prefect. This is my job." Remus turned back to James. "I'll turn you in, I swear. And I'll get ten points each off Gryffindor, including myself. Now back off."

James and Sirius both lowered their wands and backed away.

Remus spoke without looking back. "Get the telescope and go back to the castle, Lily. We'll follow."

Severus didn't argue. There was a fine line between courage and stupidity, and he was not about to cross it tonight. He stayed slightly behind Remus as Lily folded up the tripod, then let her go first up the hill. He followed, and Remus brought up the rear. The other three remained by the lake.

When they reached the castle, Lily threw her arms around Remus and hugged him. "I knew you were better than them," she said. Then she turned to Severus. "You could say something, you know."

Severus thought for a moment. "Thank you for changing your mind about beating me up," he said coldly.

"My pleasure," replied Remus, but there was no love lost there either.

Remus had to face an infuriated James and Sirius when he returned to the dormitory later that evening. He'd spent a lot of time thinking of what to say.

"You traitor! You back-stabber! Switching sides in the middle of a fight! We had him!"

"Calm down, Sirius. There'll be other times. We know where he is all the time now. We have the map. Next time she won't be there."

James was thoughtful. "So you think we should've waited 'til Evans wasn't there?"

"She won't let you push her around. The more you try to put her off him, the more she'll back him up."

"This requires a rethinking of strategy."

"Let us know when you've come up with something," said Sirius.

After that, it seemed as if Severus and Lily could never be alone. They tried meeting at the lake at different times of the day, but one of the four, usually James or Sirius, always managed to meet either Severus or Lily on the way and break up the rendezvous. Then they switched in succession to the edge of the Forbidden Forest, down the path near the gates that led to Hogsmeade, various rooms inside the castle{\el} It was always as if the four Gryffindors knew exactly where they were at any moment of the day. The only vigils they could keep for the Venera landings on Venus were behind Muffliato spells in classes they happened to share.

The last weekend in October was the first excursion into Hogsmeade for the year. Lily suggested they try meeting there, so Severus went to Professor Slughorn for permission.

"You never wanted to before," was Slughorn's first reaction.

I never had any money before. "My father wouldn't sign the paper. But my grandmother will if I send her a copy."

He sent the permission form with a school owl and got the signed paper back the next morning. Lily'd been to Hogsmeade in previous years and explained how to get to the edge of town.

Every student at Hogwarts who visited Hogsmeade had to see the Shrieking Shack, which was fast gaining the reputation of being the most haunted house in Britain. Having seen it, however, they seldom returned. The house shrieked every few weeks rather than daily, and then only at night. As a result, it was rather boring compared to Hogsmeade's other attractions. After the first hour of the first weekend visit, the area tended to be deserted.

Neither Severus nor Lily was followed to the Shack, and they spent a very pleasant afternoon on the edge of the nearby woods. Lily was still having trouble with nonverbal spells.

"Accio wand. Just think `Accio wand' and concentrate on the wand. Upper right side of the brain." The wand twitched, but otherwise refused to budge.

"I'm useless. Is there anything else I could try?"

"Let's go back to the Levicorpus spell. That has to be nonverbal. Maybe that'll be easier"

After a few minutes without success, Lily said, "Why don't you use it on me. Maybe if I know what the spell feels like, I can cast it better."

"I couldn't do that."

"Why not?"

Severus blushed. "You're wearing robes. The spell flips you over."

Lily laughed. "Not every boy would see that as a reason not to use the spell."

"I'm not every boy."

"That's true."

Lily went into town for some twine to tie her robes around her ankles while Severus chose a properly soft and mossy spot, the release spell tending not to let one down easily. Then, amid much giggling, Lily was suspended head down. It was a breakthrough moment, as Lily's thoughts coalesced on what she was trying to achieve. For a while they hung each other upside down, then turned to equally useful nonverbal spells. By the time they had to return to Hogwarts, Lily'd advanced considerably in her nonverbal skills.

"We lost them! How could we lose them?"

"Aren't you taking this a little harder than you have to?" Sirius didn't always appreciate James's dramatic streak, since it conflicted with his own.

"The fate of a Gryffindor girl hangs in the balance."

"Right. Like you cared for this girl before you found out she liked the Slytherin you love to hate."

"We're talking about a Dark Arts expert who's been tight with Bella and the Lestranges since second year. We're talking about a Death Eater in training. And she doesn't see it. She doesn't know how bad he is."

"The more you try to talk her out of it, the more she's going to fight you. You've got your work cut out for you, Prongs."

James could not find fault with Sirius's evaluation.

\subsection{Monday, November 17, 1975 (the day before the full moon)}

"You've never watched a Quidditch game? Where have you been for four and a half years?"

"Don't act so surprised. You've known me for ten years and we've hardly mentioned Quidditch once."

"Well you can't go to Hogwarts and not see at least one game. Come with me tomorrow."

"Who's playing? It'd be awkward if it was Slytherin and Gryffindor."

"It's Gryffindor and Ravenclaw. We're favored."

"I am not sitting in the Gryffindor stands."

"Then we'll both sneak into Hufflepuff. It'll be fun."

Severus agreed to go, and Lily borrowed the cloaks and the yellow and black scarves from a couple of her friends. They met near the fountain courtyard and changed, pulling the hoods over their heads as if for protection from the cold. Disguised as Hufflepuffs they set out to watch Severus's first Quidditch match. The Hufflepuffs who admitted them to the stands were the same boys who'd shared a train compartment with them three years earlier.

To his immense surprise, Severus enjoyed the game. This was partly because he was cheering for the Bludgers, a highly entertaining part of the action, especially when attacking Chasers. It took him half the game to understand the physical action, but he comprehended the scoring part at once.

"If either team had really good Seekers, this would be a boring game, wouldn't it?"

"What? What are you talking about?"

"It would be over too soon. No suspense. But as long as the two teams are within a hundred fifty points of each other, it's anyone's game. Bad Seekers, longer game, more action. Good one!" Severus's yell was for a Bludger that nearly knocked the Gryffindor Seeker off his broom.

Severus had no visions of himself playing Quidditch. Broom riding was the one course he'd failed dismally at Hogwarts. Brooms instinctively knew that he couldn't handle them and enjoyed trying to throw him. If he'd ever gotten more than six feet off the ground he'd have been killed, despite Lily's help.

Gryffindor won the Quidditch game, and for Lily's sake Severus hid his disgust at the abysmal Ravenclaw performance. Then he focused on the postgame activity and had a revelation.

Girls from all the houses were flocking to fawn over the Quidditch players. Even the losing players were surrounded by adoring fans attracted to them like flies to rancid meat. Severus's eyes swept the scene and located one of the Gryffindor Chasers, James Potter. \emph{If they push any more, they'll squish him. Trampled to death by girls. Pleasant thought.} Severus saw the broomstick, too. New, expensive, the best one there. James Potter was as rich as the Blacks.

\emph{A spoiled, arrogant rich kid who can have anything he wants and is popular to boot. Why does he care about me?}

"Look at him. Oozing money. No wonder he thinks he can boss everyone else around. People like that think they can buy anything." Severus and Lily were by the lake. For some reason they had not been stopped nor, apparently, followed.

"You don't know that he's like that. He can be quite nice."

"Both of them. Potter and Black. Rich and arrogant. Anyone not in their social class is scum."

"Haven't you met any nice rich people."

"Plenty if you have something they want. Otherwise, no. Well, maybe one."

"You still don't know them. Not well enough to judge."

"No? They've been pushing me around since second year. I think I've had a chance to see their dark side."

"You have a dark side, too, you know."

Severus wheeled in his pacing, anger seething, making it hard to breathe. She was belittling his opinions, trying to prove him wrong. She wasn't supposed to do that. She was supposed to support{\el}

Severus stopped. He knew from the expression on Lily's face that his own was cold and hard. Cold and dangerous. The demon was awake again and had almost taken control. Almost.

He closed his eyes and forced himself to breathe deeply. Forced himself to shut down, close off, seal the demon away where it couldn't hurt anybody.

"You're right," he said. "I do."

Hagrid took his time with the examination, but at the end was forced to admit that Severus was in reasonably good health and condition. "Eating good, seem t' get enough exercise. Been sleeping well? That's good. Any problems?"

"Problems? No. None to speak of. Why?"

"There's been a few times in the past. With other students. You know, problems."

"I've no idea what you're talking about."

"You got one of the worst cases of excessive pride I seen in all my years at Hogwarts."

"Pride? I'm not proud."

"Not proud? Goes up to hospital looking like Puss-in-Boots and says his wand slipped. Outnumbered and 'bout t' get his tailed whupped and tells Dumbledore bold as brass that they was discussing summer vacation. Won't ask for help nohow, and says he ain't proud."

"You've been talking about me behind my back."

"Hullo. This is a school. Happens t' be part of the job, taking care of students. Now, are you having problems."

"Nothing I can't handle."

"Ya see. Proud."

Everyone in fifth year was in the incipient stages of nervous breakdown because of their OWL exams in the spring. Severus found himself inundated just before Christmas with requests for tutoring. Enough Slytherin students approached him with the news that they were staying at Hogwarts over Christmas and begging for help with potions and charms that he floated the idea of having actual classes during the break. The response was overwhelming.

As the term wound down and the break neared, Severus tried to organize what he was going to do. He'd already tutored most of the students individually at one time or another, so he knew their relative strengths and weaknesses, easy to work with one on one, but harder to coordinate in a group. He was concerned to do it right, though, since he was going to get a considerable amount of money from the combined tutoring fees.

\emph{Is this what the teachers in our classes have to do all the time? I hope they get paid a lot.}

"Hi, Snape. How's the term been going?"

It'd been a while since Bella had talked to Severus, and he was surprised to have her sit next to him in the common room on the last day before Christmas break.

"Fine, I guess. Nothing to complain about."

"Any trouble with those thugs in Gryffindor?"

\emph{Do I have a black eye or something? Why is everyone asking me about problems with the Potter gang?} "Nothing serious. Actually milder than some years. Why?"

"I'm sure you've heard that there've been problems `outside' with wizards being attacked{\el}"

Severus nodded.

"What the Ministry isn't telling people is that we're in danger. And it's coming from the muggles. There's a witch hunt brewing, and some of our own are fueling it because they want more power."

"I heard it was the other way around, that it was more of a muggle hunt."

"That's what they want you to think. But muggles have always hated us and tried to get rid of us. Wasn't anyone in your family killed by muggles?"

Katherine Hewitt and the other Lancashire witches. Right in Pendle near where Nana lives. "Yes, a few. But that was a long time ago. Three hundred years."

"It's going to happen again. I don't want to scare you, but we have to be prepared. There's a new leader who's not afraid to speak up about the danger. He's looking for support so we can protect ourselves."

"It seems pretty improbable to me."

"Well, just think about it."

Christmas break passed quickly, probably because there was so much to do. Severus had classes for about half a dozen students at a time, trying to keep those with similar strengths and weaknesses together. One of the bonuses about being `the teacher,' was that sometimes the other students forgot that he was there as they worked on a potion. Severus got to overhear some interesting gossip.

He wasn't particularly fascinated by what Serendipida Corman was doing with Hengist Camberwell, but the knowledge that she was doing it with at least four other students added spice to an otherwise dull afternoon. Or the `true' source of the Paternoster's wealth, that was good for a smile or two. His ears did perk up a bit more at hearing the name `Black,' though. Which is how he was reminded that Bella and Narcissa had a sister. A sister who'd disgraced herself by marrying a muggle. \emph{Would you call her a `Black black sheep?' Maybe if Bella ever slips about my background, I can ask about Andromeda.}

Severus heard other things, too, ugly comments about mudbloods and mongrels. He should have been better prepared for the levels of blood snobbery he encountered, but somehow it still surprised him. One conversation in particular left him seething in silent impotence.

"{\el} didn't need him so much for OWLs, I'd teach him to remember his place."

"You're oversensitive. He's nothing more than a servant. Didn't your parents ever hire a tutor?"

"Yeah. It's not like he was trying to push his way into social things, except on the train. That would be stepping over the line."

"Well I suppose if you look at it like that{\el}"

What it boiled down to was money. You had to have money, or you were easy prey to every whim of fate, every twist and turn of economics. Severus swallowed the pride Hagrid said he had too much of and continued with his classes. He taught the rich kids, they paid him, but he no longer felt he had to be polite to them. Instead he began to vent his frustration with comments about their ineptitude and incompetence. It made him feel a little better.

Sirius Black spent Christmas at the Potters' home. It was in every way more pleasant than Christmas at home would've been, even with James rambling on and on about the girls in Gryffindor and what did Sirius think, anyway.

Christmas Day was especially fun.

"What in the world is this?" James asked, holding up a heavy, shimmering, multi-hued piece of cloth that looked like a cloak.

"A family heirloom you've grown into," replied Mrs.~Potter. "Put it on, dear. I think you'll look nice in it."

James wrinkled his nose at Sirius. He thought the cloak hideously ugly, but was not about to say so in his mother's hearing.

"Go on." Sirius was trying to contain his laughter. "Put it on. You'll look nice in it."

James put it on, and Sirius's laughter melted into awe. "It does make you look better! You've never looked so good in your life. It's an invisibility cloak."

The two boys took turns wearing James's cloak, and planning a wide series of escapades for their return to Hogwarts.

"You seem different," Lily said when she and Severus met after the Christmas break was over. "Did something happen?"

"No. I've just spent the last two weeks researching the inverse relationship between money and brains."

Lily laughed. "Rich kids are stupid, aren't they?"

"More than most. Maybe there's something about money that contaminates the gene pool. Wait{\el} If you can put chlorine into a swimming pool to disinfect it from germs, is there anything you can put into the gene pool to disinfect it from money?"

"Or could you say that someone comes from the shallow end of the gene pool?"

"Good one! I like that."

For a while they referred to the dumbest rich students as `shallow-enders.'

"Hey, Evans!"

Lily turned, her face blank, as James hurried over to her. "Going to Transfiguration?" he asked.

"You know where I'm going."

They walked together, since they were headed for the same class. "I've been wanting to talk to you{\el}"

"If it's about who I can and can't talk to, I don't want to hear it."

"I'm sorry about that. No, that's not true. I'm not sorry because he's not the kind of person you want for a friend, but I'm sorry I tried to pressure you."

"You don't know what kind of person he is."

"Look, Evans, we're living in really dangerous times. People are being attacked. Some of them are being killed. Not just wizards and witches, but muggles, too. One of the families that's deepest into this `Dark Lord' business is Sirius's family. They disown anyone who even associates with muggles, and they're part of the group that's heading the attacks. That's how I know so much. Do you think I'd care about some oddball Slytherin if he wasn't tight with the Blacks since second year? Do you know anyone at Hogwarts who knows more about the Dark Arts than he does? He walked into this school knowing more than anyone. His family has to be as dark as they come."

"That shows how much you know. He's a half-blood."

James stopped in his tracks, then hurried to catch up to her. "Really? That surprises me. He's been to Bella's house for Christmas break. Twice. I never thought they'd allow a half-blood under the roof for anything. That makes it worse."

"How?"

"Don't you see? If a family like the Blacks will tolerate a half-blood, even encourage him, then he must be{\el}"

"What?"

"Special. Valuable. More powerful than I thought."

Lily looked worried.

"Why do you associate with them?"

Severus paused, a rock that he'd been about to skip across the water still in his hand. "With who?"

"People like Bella Black. Like Evan Rosier. Like Aloysius Mulciber. Those people."

"I don't associate with them. They condescend to associate with me. I take their money. Besides, have you ever tried not associating with your dorm mates? It's kind of hard to do."

"You visit them during the breaks."

"So?"

"The Blacks don't like muggles and half-bloods. Why are you different?"

"You've been talking about me behind my back. Who with? Stuck-up Potter?"

"This is serious. People are getting hurt."

"Yes, witches and wizards."

"Muggles, too. And why didn't you answer my question?"

"What question?"

"Why are you different?"

"I'll answer your question if you'll answer mine."

"Okay. Potter wanted to talk to me. I told him he didn't know anything about you."

"I hope he still doesn't. Now your question. I'm useful. I was tutoring Bella in Potions so she could pass her OWLs. They put me in a servant's room on the top floor, and I got to eat all my meals by myself. Happy?"

"Yes, very. I'm so glad you're not one of them."

\subsection{Friday, January 9, 1976 (the first quarter)}

Severus was heading to a special Astronomy workshop just after lunch. He prided himself on his ability in astronomy and was thus in a state of perpetual frustration because of the course emphasis on the Zodiac and on astrology. There was nonetheless a certain amount of geometry involved, so it was not a total loss.

On a second floor staircase he happened to glance down and froze. Lily was leaving the Great Hall, James Potter was entering it, and the two paused to talk. Severus had a fairly good view of Lily's face, though not of James's, and was at first pleased to see that she wore a scornful expression. Pleasure turned to concern, however, as he began to note her mannerisms.

There was the little toss of her head, and the way she tucked a lock of hair behind her ear, the defiant way she tilted her chin, and the sidelong glance. Right hand on hip, a stamp with the left foot, then Lily walked proudly to the entrance doors while James, laughing, entered the Great Hall.

Severus sat back on the steps, stunned. Lily's face, and presumably her voice, radiated scorn, but every other part of her was flirting. Flirting with James Potter. Unconsciously, subconsciously flirting outrageously. \emph{Control yourself, idiot. Since when are you able to read girls' body language? Maybe she was restraining herself from attacking him and tearing his eyes out.} But of course that was wishful thinking.

Lily was attracted to Stuck-up Potter.

James was bored. Sirius had started an all-out campaign to regain the affections of Ariadne Musgrave, for which the presence of his good friend Potter was a hindrance. Remus was madly working on an Ancient Runes assignment, while Peter had disappeared. There was an unconfirmed suspicion that Pettigrew was taking advantage of his newfound small size to infiltrate the girls' dormitory, but there was as yet no proof. \emph{That's what you get when you have a rat for a friend.}

Getting out the Marauder's Map, James idly tapped it and said, "I solemnly swear that I am up to no good," but the effort was halfhearted. What good was it going out alone? He flipped through the different folds. Lily Evans was leaving Gryffindor Tower.

James looked quickly through the rest of the map. Sure enough, Severus Snape had just exited Slytherin house. As James watched, Lily headed for the lake, while Snivellus went down the path toward the gate to Hogsmeade. Then Lily turned left, while Snivellus turned right, and now both were going in the direction of the Forbidden Forest. At night. In the snow.

\emph{This evening isn't going to be so boring after all.} James hid his invisibility cloak under his school cloak and slipped out into the dark after his prey.

"Happy sixteenth birthday," Lily said as she gave Severus the traditional little cake. "I can't believe that next year we'll be of age. Are you looking forward to apparating?"

"Yes and no. Horribly uncomfortable experience, but much better than the train from Euston Station."

"When have you ever apparated?"

"With my grandmother, after my parents died. It wasn't the best of times."

"I am just dying to be able to do it. Think of the freedom!"

"Were you interested in learning other spells? Apparation isn't the only one with great advantages."

Lily giggled. "During vacation I tried some of the ones you taught me. I failed dismally. I don't know what I did wrong."

"Lucky it was wrong. The Ministry of Magic would've been on you for underage magic. In a muggle household, too. What do you think you did wrong?"

"I don't know. I tried the Leevicorpus{\el}"

"There's your problem right there. It may be nonverbal, but you still have to think the right sound. The first syllable's a shorter sound, more like `ay'. Levicorpus. Try it like that."

Lily tried it on a rock, and it worked. Then they went over the Liberacorpus spell as well, just to be sure it worked, too. By then it had gotten very cold, and they were both ready to return to the castle.

In the dark, they didn't notice the other set of footprints that came from the lake shore. The set of footprints that just ended there in the middle of the snow. Under his invisibility cloak, James Potter was thinking of a plan. 


