% A Difference in the Family: The Snape Chronicles (Rannaro)
% After Hogwarts

\chapter{The Spy}

\subsection{Thursday, November 13, 1980 (two days before the first quarter)}

"I'll be apparating to the Pendle area of Lancashire. There are herbs on the moors that I'll need. They have to be gathered at night." Severus's tone showed that he thought the questioning an unacceptable intrusion into the relationship between him and the Dark Lord. The administrative `assistant' recorded the request and went on to other things.

Severus didn't go home. He went straight to Pendle Hill where he could watch the countryside around him, and where there were indeed herbs that he could take back to London. \emph{If this plan fails, too.} He waited for a while, listening and scanning the area. No one followed him. Leaving his bag in the shelter of a rock so that it would look as if he'd just wandered away, he concentrated on the room at the base of the Shrieking Shack in Hogsmeade and apparated.

The shack was quiet, and Severus lit a Lumos spell. Through dust upon dust on the floor, through the overlay of Remus's own marks, human and lupine, he could still make out the traces of his and James's footprints, and the marks of the werewolf as it chased them back into the tunnel. No one but Remus had disturbed it since.

He eased himself into the tunnel and made his way to the willow. It was evening. Everyone should be at dinner. Pausing to look around to assure himself that nobody was there, Severus left the willow, skirted the edge of the forest and knocked on Hagrid's door. There was no answer.

\emph{Right. I get up this whole scheme, and then he's not in{\el} Why should I expect him to be in at dinner time?} He couldn't stand there in full view of the school, so he slipped the latch and entered. \emph{I'll sit here at the table 'til he gets back. What if he's not alone?} Severus looked around for someplace to hide, but there was none. \emph{It doesn't matter. Nothing matters anymore.}

Severus laid his head on his folded arms. After so many days and nights of worry he was exhausted, and he fell asleep at Hagrid's table.

Hagrid came in fifteen minutes later. He stopped in the doorway, then quietly closed the door and went up the hill to Dumbledore's office. There was no ceremony. "The Snape lad's come back. He's in my hut."

"Why is he here?"

"Didn't ask. Lad's asleep. Looking kind of pasty and washed out, you ask me. Not healthy at all. Thought you might want to know."

"Oh, yes, Hagrid, I do want to know. This must be handled carefully. Go back and find out what he wants. If it is to speak with me, tell him it cannot be here at Hogwarts. It must be somewhere, though, where I can first check to be sure we are alone. I shall let him choose the place."

Hagrid was gone for half an hour. When he returned, he looked worried. "It's got somewhat to do with James and Lily, but he wouldn't say more. He's agreed to meet you, wants to in fact. Said Pendle Hill in Lancashire since that's where his crowd thinks he's going anyway."

"Did he say when?"

"Soon as ya can. He's gone there now." Hagrid paused. "Professor, that lad's scared half out of his mind. I ain't never seen him so scared. What d' ya think it is?"

"I have a suspicion, Hagrid, but I shall keep it to myself for the moment. He is frightened, eh? If my suspicion is correct, his fear may not be entirely for himself. We may be able to use that. We may be able to convince him to change masters."

"I don't quite catch yer meaning. He's one o' them Death Eaters, is that it?"

"That is part of it. You know, it has often crossed my mind," said Dumbledore pensively, "that working for Voldemort may indeed be a frightening thing, and that the prospect of his anger and retaliation more frightening still. And yet Master Snape, terrified as he is, is facing that prospect now. The young man is worth saving, Hagrid, and the only way we can accomplish that is to turn him from this darkness and offer him a way back into the light. But he may be too frightened to accept the offer."

"So what can ya do?"

"Frighten him even more. If the prospect of staying with Voldemort is more terrifying than the prospect of leaving{\el} Hagrid, I am off to Pendle."

Cloaked against the cold, Dumbledore left Hogwarts and apparated to Lancashire.

Severus apparated onto the top of Pendle Hill with a storm brewing in the Pennines. Scudding clouds obscured the light of the crescent moon, and wind tore through the branches of the few trees that hugged Pendle's slopes. Severus shivered in the biting chill. It was a horrible night, a terrible night, a night of dark portent and fear, and suddenly, standing there alone, solitary in the vindictive presence of a tempest that howled with the bloodthirstiness of a wolf, suddenly Severus knew himself doomed. Two great wizards—and he'd betrayed them both. It was now only a matter of which descended on him first, the vengeance of the Dark Lord speeding north out of London, or the fury of the white one, reaching south from Hogwarts.

Wand in hand, ears straining for the dreaded crack of apparation, turning and looking every way at once because there was nothing to shield his back, Severus waited. He was trembling uncontrollably, his stomach twisted in knots, visions of Faustino Pembertine and Dorcas Meadows clawing at his mind, at that moment wishing himself dead that he might no longer be afraid{\el}

He came in a blinding flash of lightning, yet in that moment of stark terror and panic, Severus wasn't sure which one. He flung himself forward onto his knees, his wand already blasted from his hand, screaming "Don't kill me!" The apparition that towered over him was eerily illuminated in the darkness, and he realized it was Dumbledore.

"That was not my intention," said Dumbledore, his voice as frosty as the cutting air, his hair and robes swirling in the wind, the personification of the storm. "Well, Severus? What message does Lord Voldemort have for me?"

A sharp, unfamiliar pain shot through Severus's left arm, and he closed his eyes, both for the pain and for shame that Dumbledore would know so certainly who and what he was. He'd never been ashamed of being a Death Eater before. He'd been proud, loyal{\el} but that was before Pembertine and Meadows. Before the birth of Lily's son. The Wheel of Fortune was turning rapidly, and what had been, was no longer.

"No{\el} no message{\el}" he stammered. "I'm here on my own account. I{\el} I come with a warning{\el} no, a request{\el} please{\el}"

At his words, Dumbledore cast a silencing spell. "What request could a Death Eater make of me?"

"The{\el} the prophecy{\el} the prediction{\el} Trelawney{\el}" Severus's stammer was worse than it had ever been.

"Ah, yes. How much did you relay to Lord Voldemort?" And as the strange pain stabbed through his arm again, it seemed to Severus that Dumbledore was sneering.

"Everything{\el} everything I heard! That is why{\el} it is for that reason{\el} he thinks it means Lily Evans!" Even as he said the words, in that instant Severus understood that his bridges were burnt. He'd betrayed the Dark Lord, and his only hope lay in the man who stood before him. Lily's only hope as well. He did this for Lily.

It was the moment Severus had hoped for, the moment for Dumbledore to spring into action. But he did not. Instead he bandied words. "The prophecy did not refer to a woman. It spoke of a boy born at the end of July{\el}"

"You know what I mean!" Severus shrieked, not believing what was happening. "He thinks it means her son, he is going to hunt her down{\el}"—he thought suddenly of James and the unknown baby—"{\el} kill them all{\el}"

No sense of urgency tinged Dumbledore's voice. "If she means so much to you, surely Lord Voldemort will spare her? Could you not ask for mercy for the mother, in exchange for the son?"

"I have{\el} I have asked him{\el}" Severus began to explain, but Dumbledore cut him off.

"You disgust me." Severus knew the tone, knew it was his fault. He'd failed Dumbledore as he'd failed his father, as he'd failed the Dark Lord, as he'd failed Lily. Through the pain in his arm, he heard Dumbledore state his error{\el} "You do not care, then, about the deaths of her husband and child? They can die, as long as you have what you want?"

\emph{No! No! That isn't it at all!} Severus struggled to amend his error, to placate Dumbledore. "Hide them all," he begged. "Then{\el} keep her{\el} them{\el} safe. Please."

"And what will you give me in return, Severus?"

"In{\el} in return?" The impact of Dumbledore's callousness, his lack of concern for what became of Lily hit Severus like a physical blow. He couldn't speak for the shock of it. \emph{Pay? I have to pay for him to protect his own people? for him to protect Lily?} The enormity of his miscalculation swept over Severus—a tidal wave of renewed fear. He'd thrown everything away for this chance to save Lily, and now there was nothing left for him to cling to but the chance to save Lily. He groveled before Dumbledore. "Anything," he managed to whisper. "I'll give you anything."

There was a moment of silence, and then a deep sigh. "It is well," said Dumbledore gently. "You and I, Master Snape, need to talk. I believe your home is nearby. Shall we go there?"

\sbreak

"You have redecorated," was Dumbledore's only comment as Severus ushered him into the tiny sitting room, lodged him on the little sofa, and hurried to the kitchen to boil water on the grate for tea. After that, both were silent until Severus returned with the cups and Dumbledore motioned to him to pull a chair over so that they sat face to face.

"Now, if I may{\el}" Dumbledore held out his hand, his gesture clearly indicating that he wished to examine Severus's left arm. Severus turned his face away, but extended hand and arm, silent as Dumbledore pushed back the sleeve of the robe and unfastened the cuff of the shirt beneath, exposing the arm. The silence stretched out while Dumbledore's finger probed the mark.

"It is smaller than I anticipated," Dumbledore said at last. "And less detailed."

"It's not the full mark," Severus explained. "That's only for the inner circle. This one is for those of us who work at headquarters. The lower ranks have no mark at all."

"And where is headquarters?"

Severus opened his mouth to answer, but no sound came out. He tried to think the location, but no image entered his brain. He began to tremble again, for he'd said he would do anything for Lily, and was failing at Dumbledore's first request.

"It is no matter," said Dumbledore quietly. "There is a Fidelius Charm. How was the mark made, and what does it do?"

"It's burned on with green fire. It identifies us. It can summon us. It can punish us. It may be able to locate us—I'm not sure."

"Punish? Can you show me?"

Severus allowed Dumbledore to search his eyes, and let the images of Pembertine's last moments surface. Dumbledore watched, apparently unmoved, then sighed, rose, and stood for a moment by the window. "It has indeed burrowed its way deep into the flesh," he said at last. "I do not think it can ever be removed. I noticed that you flinched whenever I said{\el} his name." He paused. "You came to me after you witnessed this. Do you not fear him? Of course you do. When I first came to the hilltop, perhaps even then you thought it might be him. I was concerned that you had grown so distant that you would expect me to kill you. But if you were also expecting him{\el}" He returned to sit facing Severus. "Will you show me your own punishment?"

It was shorter and less painful to watch than the images of Pembertine. Knowing now how small his own torment had been compared with others, Severus was certain that Dumbledore would despise his weakness and his cowardice. He was wrong.

"So, you did not run to him in triumph, waving the prophecy like a banner of victory. You gave it to him only to escape further punishment. Tell me now of James and Lily's child."

Severus explained about the teams searching for reports of birth, and of finding the news about the Longbottoms and the Potters.

Dumbledore looked grave. "And you are certain which baby he is looking for?"

"Yes. The Potter baby. Lily's baby."

"Ah. I wish to ask you a question, Master Snape. If this were the other baby, any other baby, would you be here today?"

Severus closed his eyes and thought of the Aurors' child. "No," he said. "I wouldn't," and he was deeply ashamed of his own cowardice.

"Then perhaps we are fortunate that it is the Potter baby, for now we can take action. What is being planned?"

"Tonight. After midnight. Two teams of six. One to the Potter estate, the other to the Evans home in Surrey. There's something about getting information directly from the Ministry, but I don't know how that works."

Dumbledore again went to the window, but this time he opened it, pulled out his wand, and extended arm and wand outside. Something silver spurted from the end of the wand and vanished.

"We shall warn the Potter family and get a crew to Surrey," Dumbledore continued. "Now I fear you are going to have to prove yourself."

Severus was grilled on his spells and potions, his defense training, the layout of the interior of headquarters, other Death Eaters, and the fates of Benjy Fenwick and Caradoc Dearborn. The death of Dorcas Meadows was particularly difficult to relate, and Severus wished the earth would open and swallow him forever.

Then Dumbledore said, "Thank you, Master Snape. I believe you have answered all my questions. Now we must find a place where you will be safe."

"Oh, no. I have to go back. If he finds out I've spoken to you, he'll kill me."

"You would be safe at Hogwarts." Dumbledore said.

"I don't think so. I can't take that chance. If I don't report back, he'll know I betrayed him. Maybe he can't reach into Hogwarts, but I can't risk it. I'm not that brave. I have to go back."

"He will know when he looks at you."

"No, he won't. No more than you do unless I want you to. He didn't know anything about Lily until I asked him to spare her, and that's still all he knows."

Dumbledore smiled. "Well, if you are going back anyway, you did promise me anything I asked. I will ask you to consider helping me. Today will not be the end. If you hear more about attacks on the Potters, will you send me word? You do not need to decide now. Are you familiar with Hyde Park? Good. Magic can be sensed and traced, so we sometimes employ muggle techniques. There is a drop point near Marble Arch."

It was now nearly midnight. Dumbledore apparated to Hogwarts. Severus apparated back to Pendle Hill where he hurriedly collected as many herbs as he could, then spent the rest of the night sleepless at home. The following morning he returned to headquarters to report in. No one questioned the time he'd been gone, and no one inspected his herb bag. It looked as if he'd finally been successful at something after all.

The first raids to locate the Potters were glaring failures, and the Dark Lord was not pleased. His anger reverberated through headquarters, and everyone moved cautiously for a few days. Then at the beginning of December word came that the Dark Lord had inside information about the whereabouts of another of Dumbledore's people, one who might be able to tell them where the Potters were. Another raid was planned.

"When are you going out?" Severus asked Rosier with studied casualness.

"Tomorrow night. For some reason it has to be well before the full moon. Strange, but that's what he wants."

Rosier didn't understand, but Severus did. Now there were two in danger, Lily and Lupin. Severus knew Lupin would never betray Lily, but did he want Lupin captured and interrogated? How different might he feel if it were Sirius instead?

And then there was Dumbledore. Dumbledore had listened and trusted. Even knowing that Severus had betrayed him once before, Dumbledore had trusted and acted, and Lily was safe. He'd allowed Severus to go back to the Dark Lord without fearing further betrayal. \emph{I've disappointed him so much, and he still trusts me. Can I fail him again?}

That afternoon Severus left headquarters and, to avoid the traces of apparating, took the Underground to Hyde Park. A crowd was milling around Speaker's Corner listening to a political harangue, so it was easy to mingle and reach the drop point next to Marble Arch without seeming too conspicuous. There Severus left a note telling Dumbledore of the next day's raid to capture Remus Lupin. With a silent prayer that it be found in time, he returned by Underground to headquarters.

As Severus entered his training area, the impact of what he'd done hit him. \emph{I've just chosen sides. I work for Dumbledore, and I'm a spy.}

The raiding team ran into a group of Aurors, and Igor Karkaroff was captured. The Dark Lord was furious, and there were rumors that whoever his source of information was, was now in serious trouble. Severus's mood was much lighter. For the first time in a long time he felt as if he'd done something worthwhile, something that made a difference in the world. Lily was safe, Lupin was safe, and Dumbledore trusted him.

It was several days before Severus went back to Speaker's Corner. There, in the Marble Arch drop, he found instructions for a different drop and orders not to use Marble Arch for at least three months. The new drop was outside the zoo in Regent's Park, along the canal near Camden Town Underground station. \emph{How does Dumbledore know I take the Tube?}

When he returned to headquarters, Severus was hailed by a large Death Eater named Crabbe, one of his students who was particularly inept in learning defensive moves. "Hey, Snape," Crabbe called from the end of a corridor, "we need people on a job next week. You never go out. Want to join us?"

Severus was about to say that he had another assignment, then thought that this might be an opportunity to gather information. "What kind of job?" he called back.

"Muggle riot outside Shrewsbury. Interested?"

Severus started to ask what a muggle riot was when Rosier suddenly appeared at the door of one of the rooms. "Get inside here, you big idiot," he yelled at Crabbe, who instantly obeyed. "Sorry about that," Rosier said to Severus. "False alarm. We have a full crew, so you don't have to come."

"Okay."

His curiosity piqued, Severus moved closer to the door behind which Rosier and Crabbe disappeared. He could hear Rosier still yelling at Crabbe.

"How many times do I have to tell you, he doesn't go on jobs like this. He doesn't hear about jobs like this. He doesn't even know that jobs like this exist."

"But he'd be useful, wouldn't he?"

"Learning we set muggle mobs on wizards? If he ever finds out Wilkes and I lead raids like that, I'll nail your ears to the Ministry of Magic myself. Don't you know that's how we recruited him? That old lady in Lancashire?"

Severus listened no further. In a state bordering on shock, he made his way back to the workroom where he still occasionally made potions and spells. The old lady in Lancashire. That was Nana. Rosier and Wilkes, Death Eaters while still at Hogwarts, had led a muggle raid against Nana to recruit him. \emph{How could I be so blind? How could I be so naïve?} An icy, deadly fury enveloped him.

Vengeance is a dish best served cold. Severus waited three days before going to Camden Town. The message was short. `Sometime in the next week a mob of muggles will be incited to attack and possibly kill a wizard in the vicinity of Shrewsbury.' Discretion being more important than personal satisfaction, he then returned to headquarters to be the quiet, obedient little potions master who also taught defense. He asked no questions and made no outside excursions for several more days.

Both Rosier and Wilkes died in that raid, and another Death Eater named Antonin Dolohov was captured. The leader of the Ministry forces was an Auror named Alastor Moody, who was now singled out for the Dark Lord's wrath, especially as it was learned he'd also been the one to capture Karkaroff. With two major disasters in just a couple of weeks, the mood at headquarters became somber.

Then more shocking news came from above. The source that had provided so much success for nearly a year had informed the Dark Lord that there was a spy within the organization. Operations shut down, Death Eaters were forbidden to speak to each other, permission to return home in the evenings was denied, and everyone was required to be re-interviewed. The entry logs were picked up and movement in and out of headquarters for the last two months was carefully reviewed and analyzed.

As it turned out, Severus's precautions served him well. None of his exits from headquarters showed any deviation from his habits of previous months, and so gave no cause to suspect him. The interview was another matter. The time before, when his own mind independently concealed information, he'd intended to be open. Now he intended to deceive, and he couldn't rely on the automatic reflexes of his brain.

Severus's interview was an hour and a half ordeal. His sense of peril at a fever pitch, his nerves on a razor edge, he still had to appear calm and relaxed to the Dark Lord. Any image he'd shown during his first interview had to be available. Every moment of his life had to be accounted for. There could be no gaps, no omissions, no inconsistent images or emotions. And through it all he had to convey innocence and obedience. One slip meant a slow and painful death.

Just as he felt his will ebbing, as he was losing his focus and concentration, the Dark Lord ended the interview, pronouncing Severus a good and loyal servant, and not the spy being sought. Severus returned to his workroom and collapsed in a chair. \emph{I can't do this. I can't do this. I'm not strong enough.}

But he knew he was strong enough. The Dark Lord had ordered the deaths of both Nana and Lily, and the best way to avenge the first would be to prevent the second. He had so much to atone for. Severus closed his eyes and thought of Lily teaching him to skip stones. A pure thing, a clean thing, and he would stand between her and the darkness while there was still breath in his body, even if she never knew of it.

Now life had purpose. Life had meaning. All those long years of hiding, turning himself off, retreating from friendship, from involvement were gone. Severus was like a medieval knight. He burned with his mission to destroy the Dark Lord, and worshipped a lady unattainable and pure. He knew now he was no coward, for now he understood that life glows brighter when you live in the shadow of its ending, and he embraced that knowledge with the fervor of the newly converted. Never before had he felt so much alive as he did now, flirting with death.

All that he'd once loved came back to him, books, potions, and spells, mysteries and puzzles, the Pendle moors where he was now able to go only on weekends. Severus even spent a couple of evenings playing cribbage with himself, just to keep his hand in. He snuck back to South Kensington to pick up information on adult education classes and reinvestigate his chances of applying to Imperial College.

Then one cold December day in an Underground station he saw the magazine with the photos of Saturn. \emph{Saturn! How did I miss Jupiter?} The Jupiter fly-by had been more than a year earlier, before he'd gone to Hogsmeade to overhear a prophecy. He bought the magazine, which had pictures of both planets, and pored over the great red storm bigger than the whole earth, active volcanoes on moons large enough to have their own atmosphere, and crisp rings whose beauty and symmetry pierced his heart.

The warning messages continued to come to drop points all over London.

`Attack on Dedalus Diggle in Kent on the 13th.'

`Muggle riot in Lincoln on Thursday.'

`Explosion planned in St.~Paul's, London, Easter morning.'

And still the teams of the Dark Lord sought the hiding place of Lily and James Potter, and of the child that had been born as the seventh month died.

Then, at the beginning of August, Severus received a new assignment. Or rather, an old assignment revisited.

"It is our desire that you go to Hogsmeade to apply for a position as a teacher at Hogwarts. We need information about Dumbledore and his plans. As a member of the staff, you will be able to provide us with it. You failed two years ago. Do not fail this year. We must hunt down our nemesis, and we must destroy him. If you fail, you will die."

Once again Severus made the trip to Hogwarts and waited for Dumbledore at the Hog's Head, under the watchful eye of the bartender. This time, however, Severus was the one with the appointment.

% [\emph{Notice to Readers:}

% The original 2005 story \emph{A Difference in the Family} ended shortly after this with a brief account of Lily's death and Severus's despair at the thought of his own bleak future. Later, after I had reworked the first canon books from Snape's point of view, I went back and rewrote that part, expanding in into \emph{The Middle Years}, which continues in the next chapter.]


