% A Difference in the Family: The Snape Chronicles (Rannaro)
% Two More For Azkaban

\chapter{Treading Water}

Friday third year Potions class was always a torment.

\emph{One of these days I'm going to talk to Dumbledore again about changing the master schedule. It's insane to have Slytherin and Gryffindor students in the same classroom together for two hours. If I could just stand in one place and watch them, it would be one thing, but checking one student's progress means turning your back on another. The number of parchment pellets and paper airplanes I get from this class alone{\el} Not to mention the teasing{\el}}

Malfoy was being particularly obnoxious, as if he knew he could get away with anything. His bandages had come off a few days earlier, and he was strutting around like a bantam rooster, spoiling for a fight. And he was doing dementor imitations again for the benefit of Potter when Snape's back was turned.

\emph{At least he isn't doing it while I'm clearly watching him. Does he think I don't notice, or is he showing me he isn't afraid of me, or is he not thinking about it at all, just teasing out of habit?}

Snape walked over to Malfoy's table. The boy looked like a butcher, as did all the students, since he had a long apron over his robes and was holding a large bloody knife to cut up a crocodile heart. Snape leaned close to his ear. "Have you forgotten our conversation?"

Malfoy smiled up at him. Under other circumstances it might have been an angelic smile, if not for the glint in his eyes. "The investigation ends just before Christmas. Did you know, Professor? I'll be interested in what the panel decides."

"As will I. Keep your attention on your assignment."

A few minutes later the whole class was in an uproar, for Weasley 'd thrown a crocodile heart across the room straight into Malfoy's face. Malfoy's cauldron overturned, and there was blood on the floor and on Malfoy's face. \emph{Please let it be just crocodile blood}. Millicent Bulstrode was trying to pick up both Malfoy's and Weasley's hearts, but the things were slippery and slithered out of her hands.

Snape pulled Malfoy over to his desk and wiped blood off his face. Malfoy's nose was bleeding as well, so Snape had him tip his head back and gave him a cloth and an ice pack to try to staunch the bleeding. \emph{Why do Gryffindors always overreact? Why do they always overreact with physical violence? Why don't they just think up some creative little hex and get back at him that way? Outside my classroom.}

Turning to Weasley, Snape said coldly, "You attacked and injured a fellow student. Fifty points from Gryffindor."

McGonagall caught Snape at lunch, slipping into Hagrid's seat and generally forcing everyone to move one space down the table. "Fifty points, Severus? A little steep. I understand Malfoy was teasing."

Snape sighed. "It's more complex than that, Minerva. First, yes Malfoy was teasing, but you don't punch someone in the face for clowning around. That heart, well luckily it wasn't a whole one, but the piece he threw weighed about a pound and almost broke Malfoy's nose. In addition to the violence, you know the Board of Governors is going to hear about this. Second, have you any idea how hard it is to get fresh crocodile hearts? Most crocodiles are considered endangered species, so we have to buy them from zoos when the animals die or monitor them in the wild and harvest them from recently deceased specimens, then hold them in biosuspension until we need them for the class{\el}"

"All right, all right. It was more than just a spot of temper." McGonagall was laughing now. "I'll talk to Weasley."

"By the way, have you seen the list of people leaving for the Christmas break?"

"No, is it unusual?"

"Unusual! It's a mass desertion. Everybody is going. The only staff we'll have in the castle are Dumbledore, the heads of houses, Trelawney and{\el} Lupin. Plus Filch and Hagrid. It's worse with the students. I think out of the whole school we have about half a dozen."

"Do you blame them, with dementors stalking the perimeter? If I didn't have to stay as head of Gryffindor, I'd be leaving, too." McGonagall smiled. "I just realized. If we count Dumbledore, the teachers will outnumber the students. That should be fun. Speaking of which, are you going into Hogsmeade for the last weekend before break?"

"Can't. I have some special potions to work on. I'm excused." That weekend was one week before the full moon, and Lupin would have to start taking his calming potion. In a way, Snape would have preferred going into Hogsmeade, despite the supervisory duties. The castle was beginning to feel like a prison.

It turned cold after the beginning of December. The ground was covered in the mornings, not with snow, but with frost. The dungeon rooms turned icy, and for the first time since he started teaching, Snape was bothered by the winter cold. \emph{It can't be me. I'm not thirty-four yet. It's those dementors. Another thing Black's responsible for.} He put in an order for more firewood with Filch, enduring the caretaker's surprised look, because real fires warmed you better than magical ones.

Lupin's potions seemed to be taking up all of his time. They took several days to brew, had to be taken daily for at least a week before the full moon, and were followed up by the secondary potion to get Lupin back on his feet after the cycle was over. It seemed as if half of every month Snape was either brewing or administering the medication.

On the last Saturday before the break, the school had its pre-Christmas Hogsmeade trip. The castle was blessedly quiet as Snape brought the first dose of potion up to Lupin.

Lupin opened his office door at the first knock, his face settling at once into a cold mask that matched Snape's. "Aren't you a day early?" he asked.

"Last month you started feeling ill a day early. I thought we might forestall that by starting the doses early this month."

"You're the expert."

Snape set the small covered goblet on Lupin's desk. "It'd be best if you drank it now, while it's still warm. Then I could take the cup back with me."

Lupin sipped the mixture. "It tastes terrible," he said. "It always has. Does it have to be foul tasting to work properly?"

"I'll take it up personally with the wizard who discovered the potion."

Downing the contents without another word, Lupin handed the goblet back to Snape. "You didn't happen to see Potter on your way up, did you?" he asked as Snape turned to go.

"No. Were you expecting him?"

"After the dementor attack, I promised to work with him on something when the holidays were over. Since he can't go into Hogsmeade, I thought it might be an opportunity{\el}"

"I'll mention it if I see him."

"In a way that dementor attack was a lucky break for you, you know."

"Why would you think that?" Snape's hand was on the door handle, but he paused, puzzled.

"When Potter's broom was blown into the Whomping Willow it was smashed to pieces. They can't repair it. He told me. It's a good thing for Slytherin that he'll be on a Shooting Star instead of that Nimbus when Gryffindor plays against you."

"If you think it makes an ounce of difference to me what sort of broom Potter's flying{\el} "

"Just trying to have a conversation."

Glaring at Lupin, Snape turned and stalked out of the office.

\emph{What was that all about? How dare he imply that Slytherin can only beat Gryffindor if Potter is on an inferior broom! Make conversation indeed! Why doesn't he look for Potter himself anyway, or send a message to Gryffindor Tower? What does he think I am, his errand boy?}

Snape looked down at the goblet in his hands. \emph{I am an errand boy.}

Supper that evening was pandemonium. The fun of the day at Hogsmeade, coupled with the excitement of knowing that the next morning they would be on the Express back to London, spiced with every kind of joke Zonko's could provide, electrified the students. A food fight even broke out at the Hufflepuff table.

Snape was beginning to tire of having nearly every other teacher come over, wish him a happy holiday, and tell him how glad they were that they didn't have to spend the break at Hogwarts this year. \emph{One student. I'll be here to baby-sit one Slytherin student. Just like Sprout and Flitwick. McGonagall has the hardest job. She has three.} He looked over at the three: Potter, Weasley, and Granger.

Potter seemed withdrawn and upset about something. \emph{Not surprising if he couldn't go into Hogsmeade with the others. I wonder if Lupin ever had that chat with him. Someone else I have to baby-sit. One student and a werewolf.}

After supper, Snape went back to his cold office and room, stoked the fire, and checked Lupin's potion. Everything seemed in order. For some time he sat huddled in front of the fireplace, staring into the flames and wondering if he would ever feel warm again.

\subsection{Sunday, December 19, 1993}

Nobody was at breakfast the next morning. That is to say that Sprout and Flitwick were there, and a handful of students, but that was it. Most of the students were rushing to complete the packing for their holiday that they hadn't done the day before because of the Hogsmeade excursion. The teachers who were also leaving were helping supervise the boarding of the train before disapparating themselves. It was going to be a very quiet two weeks.

Snape sat next to Flitwick and started to help himself to eggs and toast.

"You didn't happen to bring the{\el} uh{\el}" Flitwick whispered.

"Didn't think of it, actually. Did you{\el} ?" Flitwick nodded so emphatically that Snape got up from his place. "I'll get it now, and we can have a game or two over breakfast." He headed back to the dungeon for the cribbage board.

In the entrance hall, Snape almost ran into McGonagall, who was hurrying in from outside. "Can't stop to chat," she called as she sailed past him. "Owl just came in from the Ministry, and Dumbledore wants to see me."

Wondering what that was all about, Snape retrieved the cribbage board and returned to the Great Hall, where he and Flitwick enjoyed a leisurely breakfast along with the cards.

It was some time later that McGonagall joined them, looking very sober indeed.

"So?" Snape asked, as she started loading a plate with toast and marmalade. Marmalade was a comfort food for McGonagall, and an excess of it tended to signify stress.

"The Ministry has issued its report on the hippogriff case. Dumbledore has just gone down to speak with Hagrid."

That did not sound good at all. Flitwick and Sprout were now both listening. "He hasn't lost his job, has he?" Snape asked, voicing the question that everyone was thinking.

"No, no. But for poor Hagrid it might be worse. They've decided to have a hearing to determine if the hippogriff is a dangerous creature that should be put down."

"That's terrible! When is the hearing to be, do you know?"

"On the twentieth of April next year."

Snape thought for a moment. "That's after the Easter break," he said. "If they really think the beast is so dangerous, why are they delaying the hearing until then? Why leave a dangerous animal around the students for four months?"

McGonagall looked at Snape shrewdly. "And what game do you think is afoot, Sherlock?"

"I wouldn't be surprised if Malfoy Sr. was using this as a hold on Dumbledore for most of the term. I wonder what they want."

"They?"

"Nobody in particular. The perennially amorphous `they.'" Snape got up, backing quickly away from the conversation. He certainly didn't want McGonagall to start thinking about the Dark Lord and Death Eaters at this time. He had no idea how much she already knew. "I may go down and see Hagrid later today."

% FIX
% \emph{[Note: Once again, JKR's time does not fit real time. Easter in 1994 was on April 3, but she has the Easter break come after April 20. At no time in the 1990s did this occur. Easter came after April 20 in 1984 and in 2000. I have chosen to stay with a real timeline for 1994.]}

\sbreak

In fact, he started out to see Hagrid almost immediately. Donning a warm cloak in his office, Snape returned to the entrance hall and went out the great oak doors into the world of frost and ice outside. Once there, however, his footsteps gradually slowed.

From the hill he could see the dark shapes of dementors clearly against the white frost and ice of the lake. They kept to the far shores, but they were hungry. Who knew what might draw them in.

Below, where Hagrid's hut stood, the Forbidden Forest crept disturbingly close. It, too, was a place where the dementors lurked, and the hut was too close to their threat for comfort.

Snape tried to force himself down the hill, but it was no use. Despising his own fear, he finally had to admit that the very memory of the dementor attack was enough to control his actions. \emph{Am I going to act like a coward for the rest of my life because of one incident on one morning in August? Moody would have a field day with that information.}

Reluctantly Snape reentered the castle and returned to his office. He promised himself that he'd speak to Hagrid later in the day, ashamed of the compromise, but at that moment powerless to do anything else.

One of the amazing things about Hogwarts was that so much preparation could go into a holiday that was shared by so few. Only fifteen people remained in the castle: Dumbledore, seven teachers (including Hagrid), Filch, and six students. Since Trelawney seldom left her tower, Lupin might be `sick' on Christmas, and Filch didn't care, it worked out to one Christmas tree per person. Truly extravagant.

It didn't take Hagrid long to recover from the Ministry's news about Buckbeak the hippogriff. On Monday he was at breakfast, and Snape asked if there was anything he could do.

"Nope, but thanks for the offer. I got me a team working on it already."

The team turned out to be Potter, Weasley, and Granger. \emph{Granger is certainly thorough and intelligent. The other two{\el} couldn't do any damage. Might do some good. It will keep them occupied and out of trouble. And it helps Hagrid. Worse could have happened.}

Christmas Day dawned bright and clear. Breakfast was very casual, with food laid out on one table for people to take when they wanted it. Snape went up to check on Lupin, and was disappointed to find that once again he was feeling `ill' a day earlier than he was supposed to.

"That clearly wasn't the right adjustment to that potion," said Snape, not bothering to hide his puzzlement. "Have you experienced any difficulties once the transformation starts?"

"No, that part's the same. I'm calm, I know who I am, I sleep a lot. Look, don't wear yourself out over this potion. Even with the extra day not feeling good, it's infinitely better than not having it. It isn't your fault I'm allergic to something in it."

Lupin stayed in his rooms, but Snape went down to the Great Hall to join the rest for Christmas lunch. To his surprise, there was only one table—staff and students were expected to dine together.

Dumbledore sat at the head of the table, with McGonagall at his right hand. Snape took the seat next to McGonagall, while Sprout sat on his other side, then Flitwick and Filch. Hagrid wasn't there, and Snape rather suspected he was celebrating Christmas with Buckbeak. The Slytherin, Ravenclaw, and Hufflepuff students were already seated on the other side of the table. The three seats across from Snape were empty.

Empty, that is, until the appearance of the Three Musketeers, Potter, Weasley, and Granger, who were forced to sit opposite. \emph{Wonderful. I have to look at them for the next half hour. I sincerely doubt they're pleased with the arrangement either. Let's restrict conversation, eat quickly, and leave.}

It was unfortunate that Dumbledore was in one of his more puckish moods. He insisted in handing out Christmas crackers to everyone and cheering as they popped open to reveal comical hats. Snape rather pointedly didn't take one.

"Come, come, Severus, you must have a hat, too!" cried Dumbledore, laughing, and held out a particularly large silver noisemaker. Left with no choice, Snape took the end proffered to him and pulled. A very large bang, a small puff of smoke, and there on the table lay a pointed witch's hat topped with a vulture.

This fit so perfectly the description Snape and the others had heard of Longbottom's boggart dressed in his grandmother's clothes that McGonagall immediately began fizzing with suppressed laughter. Snape didn't look at Sprout and Flitwick, not wanting to see the glee on their faces. Across from him the three Gryffindor students were trying their best not to giggle and succeeding very badly. Snape turned to the irrepressible Dumbledore, seething internally and pushing the hat toward the Headmaster. \emph{You did that on purpose.}

Dumbledore's eyes flickered in surprise, then he smiled and took the hat, removing his wizard's cap and putting the vulture on his own head. "Dig in !" he commanded, and they all began to eat.

Little happened during lunch except that they were joined by Sibyll Trelawney, an event welcomed by Snape since she and McGonagall never got along, and McGonagall baited the Divination teacher all the way through lunch. Aside from its being highly amusing, it caused everyone else to forget the vulture hat.

The students left as soon as it was polite for them to go, Potter and Weasley being the first. Granger for some reason wanted to confide in McGonagall, and the others drifted off to their rooms to relax. Dumbledore put a hand on Snape's sleeve.

"Stay for a moment, Severus."

"Yes, Professor?"

Dumbledore leaned closer, his elbows resting on the table, chin on hands. "Something happened earlier. Something that has not happened before. You spoke to me and told me that I planned that little hat trick. Which I did, of course, but that is not the point."

"I didn't speak to you. That's what I was thinking, but I didn't{\el}" Snape stopped as the full import hit him.

"I did not `read' your mind, Severus. You projected. You projected a clear, concisely worded message to me. Not a memory, not an emotional feeling—words. Words intended to tell me something specific."

"I don't know how I could've done that."

"It doesn't matter. What matters is that it can be done. Do not tell anyone else. I think that the fact that I can communicate silently with one of my teachers is not something that should be public knowledge. It may never be necessary. It is nonetheless good to know that it exists. Another weapon in the arsenal."

As Snape was leaving the table, McGonagall came over. "Sit down, Severus. We have another mystery that may be a problem. Potter has received a new broom to replace the broken Nimbus."

"That's wonderful!" exclaimed Dumbledore. "I had hoped he would still be able to play at top form."

"Where did he get it from?" was Snape's reaction. "Clearly it didn't come from either of you, and my understanding was that his aunt and uncle never bought him anything. "

"That is the problem, and the reason why Granger wanted to talk to me. Potter himself doesn't know who gave it to him."

Snape and Dumbledore exchanged a glance. "Quirrell once tried to get rid of Potter through a broom accident. What if Black intends the same? Maybe the broom is cursed," Snape suggested.

"That is what Granger is afraid of," replied McGonagall, and Snape's opinion of Granger went up a little. "I am going up to Gryffindor Tower now to confiscate the broom. I'd prefer to have Madam Hooch look at it, but she isn't here. Professor Flitwick can check it for charms. Maybe you can look at it, too, Severus."

"I don't know anything about brooms."

"You know as much about dark magic as anyone here. If the broom's been jinxed, you'd probably know it."

"Excuse me, Minerva, but Professor Lupin handles Dark Arts," Dumbledore interjected.

Snape and McGonagall looked at Dumbledore and then at each other. It was clear they agreed on this. "I'd rather not have Remus involved," said McGonagall. "He was one of Black's best friends, and it wouldn't be fair to put him into the position of investigating a friend."

"Besides," added Snape, "he's ill and won't be available for the next few days."

"Very well," conceded Dumbledore. "Have Flitwick look at the broom. If there is any indication that it has been jinxed, then you Severus should check it more thoroughly. I am sure, however, that you will find it is in perfect working order."

The question of the broom brought all of Snape's suspicions back to the fore. He was certain the gift came from Sirius Black. \emph{And how might Black have learned that Potter needed a new broom? Lupin told him.} Hadn't Lupin admitted earlier that he'd discussed the broom with Potter? Then he passed the information on to Black, who got Potter exactly what Potter wanted—a new broom, a wonderful broom. And Potter was just the type—his father's type—to take the gift without question, as something he deserved just by virtue of being Harry.

This was something Snape couldn't discuss with Dumbledore. The headmaster had made it abundantly clear that he wanted to hear nothing against Lupin. Lupin and Potter—two perfect people in Dumbledore's eyes. \emph{Why won't he listen? Black escapes from Azkaban, and suddenly Lupin is available for a job at Hogwarts. Someone has gotten Black past the dementors and into the castle. Someone is encouraging Potter to be careless of his own safety. Someone passed a message to Black that Potter would welcome a new broom. Who could it be but Lupin?}

They couldn't find anything wrong with the broom. Both Snape and Flitwick checked it for every charm, hex, jinx, curse, or enchantment they could think of, and the broom turned out clean every time. When the Christmas break ended, and students and teachers returned to Hogwarts, Madam Hooch was given the broom. She intended to strip it down completely and have the two professors individually check each part. She estimated this might take a month to accomplish. Neither Snape nor Flitwick grudged the time and effort.

The first Quidditch game of the year was between Slytherin and Ravenclaw. It was a hard fought battle, but Slytherin won by a narrow margin. At about the same time, news of Potter's new broom filtered through the ranks of the teachers. It was like a replay of the time two years earlier when Snape had asked to referee a Quidditch game in order to find out who was attacking Potter.

"So, you've confiscated Potter's new broomstick, eh," commented Sinistra at supper. "I suppose without that broom Gryffindor's chances of beating you get slimmer and slimmer."

"It wasn't my idea to check the broom," Snape protested. "McGonagall wanted me to go over it. And it's Hooch who's holding it back now, not me."

"Right. It's hard to miss how much it helps out Slytherin, though. I still think{\el}"

"It isn't my fault. I didn't make the decision."

"Professor Sprout! Severus here is trying to tell me that it's nothing to do with him that Potter can't use his new broomstick."

"A likely story, Snape. Anything to keep Slytherin on top, in my opinion."

Snape knew they were teasing, but he hoped Hooch would be finished with the broom soon.

Mid February was the Quidditch match between Gryffindor and Ravenclaw. Snape paid little attention during the weeks leading up to it except to note that immediately before the match McGonagall gave Potter back the new broomstick. At breakfast on the Saturday morning of the match, it seemed as if every boy in Gryffindor was escorting Potter to their table. The boy had actually brought the broom with him to breakfast.

Why soon became apparent. Gryffindor was not paying any attention to Ravenclaw. Gryffindor was taunting Slytherin.

After observing the interplay between the two houses for a few minutes, Snape got up and slipped into a seat next to McGonagall. "You know, they might have the courtesy to show some respect to the team they're actually playing today."

"Nervous, Severus? How does it feel to know you might soon be toppled off that throne of yours?"

"So that's where they get this cutthroat competitive streak. Direct from the Head of house herself. I should stop being surprised and go right to the source."

"You are going down in May. You are going to lose. You should practice living with the idea, laddie, so it's not so great a shock when it happens."

"Such an exemplar of kindness and consideration. Not to mention modesty."

"Do you want to back up your team with a wee wager?"

"Just exactly what do you consider a `wee wager?' I'd hate to end up penniless in the event of a Gryffindor win."

"Ten galleons."

"Not on your life. The gesture is purely symbolic in any case. One knut."

"As I recall, you've always been a bit of a penny-pincher. Weren't you the boy that tucked every sickle he made tutoring into a locked chest and would never even go into Hogsmeade for fear he might be tempted to buy one Jelly Slug?"

"I still haven't bought that Jelly Slug. One knut, take it or leave it."

"Deal."

Snape broke tradition by sitting with McGonagall that day. Flitwick was gracious enough to accept the explanation of the wager, knowing that all of Slytherin was cheering for Ravenclaw in any case. Lupin was in the Gryffindor box as well, sitting behind Snape and McGonagall.

Quidditch as purely a game was not something that Snape was particularly interested in. He'd been a student at Hogwarts for several years before he saw his first match, and that only because Lily'd insisted. He found the game somewhat boring. The better the seeker, the more boring the game. In fact, he had a tendency to cheer for the bludgers.

As the game progressed, even Snape had to admit that the Firebolt broom that Potter was riding was a technical marvel. Some of the dives were spectacular. Then, as both Potter and the Ravenclaw seeker closed in on the snitch, gasps came from the crowd. Three dementors were gliding onto the pitch.

Snape froze, his heart pounding and his breathing suddenly shallow. The spectators around him had risen to their feet, while he remained on the bench. Above the field, Potter suddenly pulled a wand from inside his robes and pointed it at the dementors.

Light sprang from the wand, light in the wispy, uncertain form of a deer. It radiated a powerful glow as it advanced on and struck the dementors, felling them to the ground. Then the stands erupted in wild cheering as Potter caught the snitch and ended the game.

McGonagall was already halfway to the dementors, Lupin not far behind her. Snape sat for a moment in the stands, eyes closed, then rose and joined the throng pouring out onto the pitch. Shakily he made his way to the crowd around McGonagall.

She was in a towering rage. "{\el} cowardly attempt to sabotage the Gryffindor seeker! Detention for all of you, and fifty points from Slytherin{\el}"

Fifty points! Snape suddenly began to push forward. There on the ground were Malfoy, Crabbe, Goyle, and Flint, still entangled in the black robes they'd used to impersonate dementors. Snape was furious, but said nothing, leaving the punishment of the four in McGonagall's very capable hands. Now that it was clear there had never been any dementors, he was beginning to calm down and focus on what had happened.

Harry Potter, a thirteen-year-old boy, had just produced a very impressive patronus.

\sbreak

\emph{A patronus! The boy can produce a patronus, and a good one. Is that what Lupin has been working with him about? Why? To use against dementors? But there are no dementors in the castle. All right, he was attacked by one on the train, and again at that first Quidditch match, so maybe there's some justification, but isn't it terribly risky as well?}

\emph{Lily's son is safest when he stays with other people. When he goes off by himself, he's vulnerable, a walking target. One of the things that keeps him from wandering off alone is his fear of the dementors. By giving him a reason not to fear the dementors, you increase the chance that he'll walk right into Black's hands. Now what will keep him inside the castle? Is that what Lupin wants? A reason for Potter not to be afraid of the dementors? Something that will make it easier for Black to reach him undetected?}

The whole castle knew that Gryffindor was partying with serious intent. It wasn't the first time that Snape was glad to be as far as possible from Gryffindor Tower. \emph{At least this will ensure that Potter stays where it's safe.}

Shut in the peace and quiet of his dungeon office, Snape pondered every angle of Lupin's possible involvement in the patronus and with Potter. There was no way around it. He found far more in it to worry him than not, and very little comfort.

The alarm jolted Snape out of sleep at two o'clock in the morning. All staff were being asked to report to the Great Hall at once. Dragging himself out of bed and throwing a dressing gown on over his nightclothes, Snape made his way through the dark corridor to the Hall. He was almost the first one there. The others were filtering in from the floors above.

McGonagall was already waiting, in a tartan dressing gown with her hair in a net.

"What's happening?" Snape asked, stifling a yawn.

"He's back. He was in Gryffindor, in the dormitories. In Potter's dormitory."

"Who?"

"Sirius Black. He went after young Weasley with a knife."

All sleepiness, all fatigue was instantly gone. "Is the boy all right? Was anyone injured? When did this happen?"

"Not ten minutes ago. The boys are fine, badly frightened is all. Weasley most of all. Black slashed through his bed curtains, but the boy woke and yelled, and he fled. The others were asleep when it happened."

"Then Black must still be in the castle."

"That's why you've been called out."

By this time the rest of the teachers had gathered. Quickly briefed by McGonagall, they split to search the castle from top to bottom, Snape once again taking the uninhabited towers and the upper floors. Once again the search proved fruitless.

By morning the story had leapt from Gryffindor to Ravenclaw, and from there to Hufflepuff and Slytherin. Everyone knew that Sirius Black had attacked Ron Weasley, and everyone also knew that he'd gotten the Gryffindor passwords from a crib list dropped by Neville Longbottom. Weasley was the hero of the school, and Longbottom the goat, and Snape was totally dissatisfied with the story.

"Listen, it doesn't make sense. You tell me that Longbottom lost the list some time before Friday afternoon. That means he lost it somewhere inside the castle. So for Sirius Black to find it, he would already have to be inside the castle, and no one could have found the list before him. Now, who helped Black into the castle, and where was the list of passwords that no one else found but Black did?"

"Well you know now that you put it that way, it does seem a bit suspicious. Are you saying that you think someone in the castle is helping Black enter, and that person found Longbottom's list on Friday and gave it to Black on Saturday?" McGonagall's face wore a puzzled look.

"Doesn't that fit the facts better? No mystery to that one."

"But who{\el}"

"Severus?" A benignly smiling Dumbledore interrupted the breakfast conversation. "I am sorry to spoil your little chat, Minerva, but I really must speak with Severus for a moment."

Snape followed Dumbledore to a corner of the Hall.

"Severus, you were about to voice to Professor McGonagall your suspicions about Professor Lupin. I really must insist that you do not talk of this with the other teachers."

"Headmaster, someone is helping Black enter the castle and someone gave him that list. The lives of our students are at stake. You have to at least consider the possibility{\el}"

"No, Severus. I am completely confident that no member of this staff is to blame for what happened. I forbid you to carry this any further. You will not speak of your suspicions, and you will not act on your suspicions. Do you understand?"

"Yes, Headmaster." Snape turned away from Dumbledore and strode angrily from the Hall.

\emph{Don't talk to the other teachers. Don't talk to the other teachers. I promise you this, Professor High-and-Mighty, I-know-what-everybody's-thinking Dumbledore—when Harry Potter is lying bleeding to death on the floor of the Gryffindor common room, I swear I'm going to mention it to someone!}

Furious now at Dumbledore's shortsightedness where Lupin was concerned, Snape decided to start checking and patrolling the whole castle himself. Black had to be getting in somewhere. Snape was going to find out where. All of his free time was now gone. When he was not teaching classes, or correcting papers, or mixing Lupin's potions, Snape was prowling the corridors of Hogwarts trying to find any place where Sirius Black might enter.

Shortly after, the school had another Hogsmeade excursion. Potter, luckily, was still unable to join the rest of the school because his aunt and uncle had not signed the form. In Snape's opinion this was a most sensible way to protect the boy, as long as he was smart enough to stay in the Gryffindor common room. Since the last incident when Black entered the castle, the entrance to Gryffindor was once again held by the Fat Lady, who knew Sirius Black, and she was protected by security trolls. It was unlikely that Black would ever get into Gryffindor again.

It was with some surprise, therefore, that on the morning of the excursion Snape saw both Potter and Longbottom standing together in front of the statue of the humpbacked witch on the third floor, far from Gryffindor, the library, or any place else they might be expected to be.

"And what are you two doing here?" he asked. "An odd place to meet{\el}" Snape suddenly had a feeling that the statue had something to do with Potter's actions. He wasn't certain why or how, but the feeling was there.

Potter was evasive. "We're not—meeting here. We just—met here."

\emph{It's still not someplace where you should be with a crazed killer after you.} "Indeed? You have a habit of turning up in unexpected places, Potter, and you are very rarely there for no good reason{\el} I suggest the pair of you return to Gryffindor Tower, where you belong." \emph{And where you'll be safe.}

As the boys obeyed, Snape stepped up to the statue of the witch. He touched it tentatively, wondering why he was getting such an odd feeling about it. There seemed to be nothing unusual, however, and he finished his rounds and returned to his office.

The afternoon was not far gone when there was a commotion outside Snape's office and then a banging on his door. Snape opened it to admit an extremely flustered Malfoy, who was babbling something about Potter's head. Malfoy's own head was spattered with mud. Crabbe and Goyle were in the corridor behind him, and they were muddy, too.

It took several minutes to calm Malfoy down to the point where he was coherent. Then Snape heard the unlikely story of mud hurtling out of empty space, and Potter's disembodied head floating near the Shrieking Shack. Malfoy was hysterical, but to Snape it all made perfect sense.

\emph{He has James's invisibility cloak. That little brat has been defying school rules and going into Hogsmeade without permission using that invisibility cloak. How{\el} ? Not by the gate, but maybe that's the purpose of the witch.} Sending the three Slytherin boys to the common room, Snape raced up the stairs to the third floor.

And there Potter was. Standing next to the witch, trying to hide the fact that he had mud on his hands. There was no sign of the cloak. \emph{And if you can get in and out of the castle that way, Potter, maybe Sirius Black can, too.}

"So. Come with me, Potter." Snape led the way back downstairs to his office in the dungeons, a rather subdued Potter right behind.

"Sit." Potter sat. Snape did not. "Mr.~Malfoy has just been to see me with a strange story, Potter. He tells me that he was up by the Shrieking Shack when he ran into Weasley—apparently alone. Mr.~Malfoy states that he was standing talking to Weasley, when a large amount of mud hit him in the back of the head. How do you think that could have happened?"

Potter was forced to answer the direct question. "I don't know, Professor," he said, his eyes wide.

"Mr.~Malfoy then saw an extraordinary apparition. Can you imagine what it might have been, Potter?"

"No."

"It was your head, Potter. Floating in midair."

Potter tried to pass it off as a joke, but Snape didn't let him finish. "What would your head have been doing in Hogsmeade, Potter? Your head is not allowed in Hogsmeade. No part of your body has permission to be in Hogsmeade."

\emph{You think you can brazen your way out of this, don't you? You don't realize that I know about James's cloak. I know you were in Hogsmeade, and I know how you managed it, you and that witch statue. Mocking all our attempts to keep you safe.}

"So. Everyone from the Minister of Magic downward has been trying to keep famous Harry Potter safe from Sirius Black. But famous Harry Potter is a law unto himself. Let the ordinary people worry about his safety! Famous Harry Potter goes where he wants to, with no thought for the consequences. How extraordinarily like your father you are, Potter."

That got a rise. The boy was not pretending innocence anymore. He was angry. Snape pushed it. Angry people say things without thinking. "He too was exceedingly arrogant{\el} Strutting around the place with his friends and admirers{\el}"

"My dad didn't strut. And neither do I."

"Your father didn't set much store by rules either{\el} His head was so swollen{\el}"

"SHUT UP!"

"What did you say to me, Potter?"

"I told you to shut up about my dad! I know the truth, all right? He saved your life! Dumbledore told me{\el}"

Locking down, shutting off, the cold moment before the volcano erupts. \emph{Bullied, threatened, intimidated, beaten up, nearly killed in front of a crowd of people, lost the only friend I ever had, and driven into Bella's waiting arms, and all he told you was that James saved my life! Am I nothing that he gives ammunition to this arrogant little imp who thumbs his nose at every rule Hogwarts has!}

"Have you been imagining some act of glorious heroism? Your saintly father and his friends played a highly amusing joke on me that would have resulted in my death if your father hadn't got cold feet at the last moment. There was nothing brave about what he did. Had their joke succeeded, he would have been expelled from Hogwarts. Turn out your pockets, Potter! Turn out your pockets, or we go straight to the headmaster!"

Potter hesitated, then produced a bag from Zonko's Joke Shop and a folded up piece of parchment. "Ron gave them to me," he said lamely.

"And you've been carrying them around ever since? How very touching." Snape took the bag automatically, but his attention was riveted on the parchment. Old parchment. "And what is this?" he said as he pulled it from the boy's hand, but he didn't need an answer. He'd seen it before.

\emph{This is the map Sirius had the day he tried to jump me outside the library. It's blank now, but I remember the look, the feel of it. The map Filch confiscated from him. The map they must have gotten back from Filch somehow. The map only Lupin could have given to Potter.}

Snape looked at Potter, who was pretending the parchment was unimportant. Moving closer the to fire, Snape said, "Why don't I just—throw this away?"

"No!" Potter cried.

"Or is it—instructions to get into Hogsmeade without passing the dementors?"

The look on Potter's face was all Snape needed. The boy was using the map. \emph{There is a passage behind the statue of the witch! Idiot child! Sirius Black helped make this map. Black knows where every passageway on it is. Lupin is sending you down where Black might be waiting for you. To kill you. And all you care about is buying tricks at Zonko's. Your mother died for this?}

Pulling out his wand, Snape unfolded the parchment on his desk and tried a few revealing spells to force the map to show itself. None worked, but the parchment began to form sentences, insulting sentences. Lupin, Potter, Black, and Pettigrew, each in turn taunted him—he could practically hear their voices in the mocking words. Potter looked as if he was going to be sick.

"So," and Snape's voice was icy. The cold calm before the nuclear blast. "We'll see about this{\el}" He strode to the fireplace, grabbed a fistful of floo powder, and flung it against the grate. "Lupin," he hissed, "I want a word!"

Lupin came at once. Stepping out from the hearth, he brushed the floo powder from his clothes. "You called, Severus?" he asked in a voice that oozed innocence.

"I certainly did," said Snape, barely able to keep his anger under control. "I have just asked Potter to empty his pockets. He was carrying this," and he pointed to the parchment.

There was no doubt. Lupin tried to control his expression, but Snape knew he recognized the map. "Well?" Snape insisted.

Lupin was silent. He was clearly trying to think of what to say. Snape pressed forward, his voice dripping with sarcasm. "Well? This parchment is plainly full of Dark Magic. This is supposed to be your area of expertise, Lupin. Where do you imagine Potter got such a thing?"

\emph{Did he just look at Potter? Warning him to be quiet? Warning him not to interrupt?}

"Full of Dark Magic? Do you really think so, Severus? It looks to me as though it is merely a piece of parchment that insults anybody who reads it. Childish, but surely not dangerous? I imagine Harry got it from a joke shop—"

\emph{Do you think I'm an idiot? Or didn't Sirius tell you how he lost the map. Do you think I don't know?} "Indeed. You think a joke shop could supply him with such a thing? You don't think it more likely that he got it directly from the manufacturers?"

Lupin had the gall to pretend he didn't understand. "You mean by Mr.~Wormtail or one of these people? Harry, do you know any of these men?"

"No," Potter replied, a little too quickly.

\emph{No, I don't mean Mr.~Wormtail. I mean Mr.~Moony, who's standing right in front of me this very moment pretending butter wouldn't melt in his mouth.}

"You see, Severus," Lupin continued. "It looks like a Zonko product to me—"

Then, as if part of the plot, Weasley came bursting into the office claiming to have bought everything and given it to Potter. At the sudden distraction, Lupin snatched the map off the desk, folded it, and put it in his robes.

"Well! That seems to clear that up! Severus, I'll take this back, shall I? Harry, Ron, come with me{\el}"

Snape stepped forward, but short of wrestling Lupin for the parchment, there was nothing he could do. Seething, his heart pounding and breathing like a winded runner, Snape watched Lupin slip away with Potter, Weasley, and the map.

Less than five minutes later, Hogwarts had lost another seventeen glass potions beakers.

\sbreak

"There is a passageway to Hogsmeade somewhere around that statue!" Snape knew his voice sounded wild and strident, but he couldn't control it. "Potter's been using it to go to Hogsmeade without permission, and he has his father's old invisibility cloak to hide him while he's there!"

"Severus, Severus, you must calm down. We have checked the statue and found no passageway. And an invisibility cloak, surely not."

"James. Had. An. Invisibility. Cloak. He told me about it himself when he was trying to patch things up with me so that he could have a chance at Lily. That obnoxious, arrogant little piece of owl dung has the cloak, and his disembodied head is appearing all over Hogsmeade! You have to do something about it!"

"We've looked through his things. There was nothing there. No invisibility cloak at all. You are overwrought, Severus, and you need to calm down or we'll be sending you to St.~Mungo's in a straitjacket."

"But Lupin is handing Potter to Black on a silver platter."

"Not silver. Not for a werewolf. And you seem to have forgotten that I told you not to speak of these suspicions. I have complete faith in all my teachers. I assure you that no one on the staff is doing anything to harm the boy."

The urge to strike Dumbledore was almost overpowering. \emph{The demon. I have to control the demon. So many years, so many years, and it's still there. Waiting to pounce. Waiting to leap out. Why won't he listen? Why won't he pay attention? Why won't he take me seriously?}

"Yes, Headmaster," was all that Snape said. He left Dumbledore's office feeling more alone than he'd felt in over twelve years.

And that was where things stood for weeks. Snape's days were filled with classes, homework, Lupin's potions, and patrolling the castle. At night he slept badly. He was noticeably even thinner than usual, and he had pretty much stopped talking to anyone. This was principally because there was no one he could talk to about what had become an obsession.

Dumbledore was out of the question, of course. It was Dumbledore who'd muzzled him. Hagrid was understandably preoccupied with Buckbeak and seldom came to the castle for meals anymore. He'd lost the case and was now preparing an appeal against the hippogriff's execution. Snape missed Hagrid, but he still couldn't bring himself to go near the forest where the dementors lurked.

Snape still had to see Lupin all the time about the calming potions, but now their conversation, which had never been extensive, was limited to commenting on the potion's efficacy. Snape was giving Lupin small doses of each ingredient one by one to see if he could isolate the particular herb that Lupin was allergic to. So far he'd had little success.

McGonagall and the others were a different matter. The whole school was talking about the upcoming Quidditch match between Slytherin and Gryffindor, and all McGonagall wanted to discuss were Gryffindor's chances of beating Slytherin for the Quidditch cup. It was all Flitwick and Sprout wanted to discuss, too, and they sided with McGonagall. \emph{It's apparently a tactical error to have the best Quidditch team every year. It promotes jealousy and ill feeling, especially against me.}

Monitoring the students became a major chore. Both Gryffindor and Slytherin students were harassing and jinxing each other in the corridors and in classrooms. A couple of small fights even broke out between classes. The only good thing about this was that the Gryffindor captain ordered Potter to be guarded everywhere he went, and the boy was effectively prevented from doing anything stupid because he was constantly surrounded by his teammates and housemates.

The Saturday morning of the match, Snape paused at the Slytherin breakfast table to wish Flint and the others good luck. The hall was packed, and the Gryffindor team chose that moment to enter, clearly playing for maximum effect.

The Great Hall erupted in cheering. Gryffindor, Ravenclaw, and Hufflepuff all joined in, as did the teachers at the high table, including Dumbledore, who enthusiastically applauded. The Slytherin table was booing and hissing, and Snape made no effort to stop them. He'd completely lost his appetite.

Rather than endure McGonagall's teasing at the teacher's table, Snape stayed with his own house, walking along the table and talking to the students, encouraging the team, and generally waiting until he could gracefully leave the hall, which only happened after the Gryffindor team departed, again to tumultuous applause.

Going back into the dungeon area, Snape was stopped by Marcus Flint. "Begging your pardon, sir, but the whole house is going out to the field together, and we were wondering if{\el} well{\el}" He pulled a small bundle from under his robes. It was another robe, a green one. Slytherin green with silver trim. "We were wondering if you wanted to be part of it, is all."

Snape took the robe. "I would be proud to be part of it, Mr.~Flint," he replied, and took the robe with him to his office, where he exchanged the usual academic black that he always wore for the brave green and silver.

Slytherin came last of all the houses down the hill, chanting their fighting song, emerald banners with their silver serpent waving in the breeze. Three quarters of the school stood against them, but they were not going to give up. Snape eschewed the VIP bleachers, and sat in the stands with his students.

From the beginning, the game went badly. The announcer was so clearly biased that the Slytherin team quickly lost all sense of proportion and concentrated on stopping Gryffindor either legally or by fouls. Gryffindor responded, but Madam Hooch noticed the Slytherin fouls and not those committed by Gryffindor. The score seesawed back and forth. Gryffindor needed a win of more than two hundred points to capture the Quidditch cup, and its team was doing all they could to keep Malfoy away from the Snitch until they were leading by sixty points.

In the end, the game was won by the Firebolt. Malfoy saw the Snitch before Potter did, and it was a race. The Slytherin stands were on their feet, Snape with them, as the more powerful broom swept down on Malfoy and edged him out. Potter struck Malfoy's arm away from the Snitch and reached for it himself, and the game was over. Gryffindor had won the Quidditch cup.

Snape joined his team on the field, congratulating them on a well-fought game. The green and silver crowd was quiet and dejected. Nobody else came to speak to them, for they were all concentrating on Gryffindor, and the Slytherin team couldn't get close to the Gryffindor team to congratulate them because of the throng. \emph{Not that they particularly want to. It would have been different if Gryffindor had been winning for ten years, and we were the underdog team.} He wasn't in the mood to remember that there'd been a time when that was true.

Depressed and dejected, Snape nonetheless swallowed his own feelings and went over to congratulate McGonagall on her win. "I owe you a knut," he said as they shook hands.

"And I'm going to see that you pay it," she answered. Then they were swept apart by cheering students and teachers, and Slytherin house made its way back up the hill to the castle, leaving the field to the victors.


