% A Difference in the Family: The Snape Chronicles (Rannaro)
% If You Are Ready{\el}

\chapter{The Tasks Begin}

Snape didn't follow Hagrid and Moody. If he had, Granger and the invisible Potter would have seen him and probably told either Hagrid, or Moody, or both. While he wasn't worried about Hagrid, Snape had no desire to let Moody know he'd witnessed the conversation in the Three Broomsticks.

At dinner that evening, Snape kept an eye on Hagrid, who was clearly keeping an eye on Madame Maxime. It didn't surprise Snape at all, for romantic possibilities were rare to nonexistent for Hagrid, and he imagined for Maxime, too. As soon as Hagrid made movements indicating he was about to rise from the table, Snape got up and quickly left the Great Hall. One cannot be accused of following another if one is first, after all.

In fact, Snape left the castle altogether and went out onto the lawn. The moon had not yet risen, since it was halfway between full and last quarter and the stars were glittering in a clear sky. Snape sincerely hoped that Hagrid and Madame Maxime were not intending to go strolling on the grounds because it would be awkward to interrupt such a tête-à-tête.

Fortunately, when Hagrid appeared he was alone.

Snape pretended he was walking back into the castle, stopped, and said, "Good evening, Hagrid. How are you enjoying all the excitement about the Tournament?"

"It's grand, Professor. And even better being smack in the middle of it."

"Smack in the middle? How is that?"

"Well, I'm gamekeeper. Magical creatures. They'd have to work with me, now wouldn't they?"

This was going much smoother than Snape had anticipated. He always preferred short conversations. "I imagine loads of people would like your viewpoint on what's happening."

"That's what Professor Moody was saying just this afternoon. Something about my `unique perspective.' I told him there weren't nothing unique about it, just a talent for handling dragons, but he went on like it were something special."

"So Moody knows about the dragons, too?"

"Well odd about that. I got the feeling at first that maybe he didn't, but nothing I said were no surprise to him, so I guess Dumbledore told him. Good thing, too, 'cause he warned me that something were afoot."

"Afoot? You shock me Hagrid. What could go wrong?"

"You wouldn't believe it to look at him, but seems Professor Karkaroff ain't above tipping the scales in his favor. Moody says he's planning to come down tonight to watch the shipment arrive. That'd give that Durmstrang school a big advantage. I thought I'd take Madame Maxime for a stroll."

"So you're planning to balance things out."

"Just leveling the playing field, Professor. Just leveling the playing field."

"Had you thought about leveling it Hogwarts' way?"

"Got that covered, too, Professor."

"I don't want to hear about it, Hagrid. I have an official position to protect."

"Mum's the word, sir."

Snape pondered this as he reentered the castle. On a whim he checked to see if Karkaroff was still in the Great Hall. Peeking in, he was surprised to see Karkaroff talking to Moody in a clearly animated fashion. Snape backed away and waited until Karkaroff came out.

"Good evening, Igor. You seem in quite a rush tonight."

"And why not? I have just found out about your little plot to shut Durmstrang out of the competition." He advanced on Snape, hands clenched into fists at his sides. "I thought we were friends as well as colleagues. I thought you would support me in this. But now I see where your loyalties lie. You abandon me when most I need help."

It was a godsend. Better than Snape could ever have planned. Thinking fast, he replied, "You know I'd help you in almost anything else, but I've been waiting and hoping for this for nearly a decade and a half, and you're not going to take it away from me. Don't count on my support. Not in this."

Karkaroff stopped dead, and stared at Snape as if he were a madman. "Are we talking about the same thing?"

"Maybe not," Snape said, and walked past him into the dungeons.

On the day of the first task of the tournament, it was impossible to get any work done. The morning classes were basically useless, and the afternoon classes were canceled. The four champions were taken away from the castle to a special holding area, and after lunch the rest of the school trooped down to a stadium area with a huge barrier fence that had been created during the night just for the competition.

Snape was not certain he wanted to attend. He was now one of only a few teachers (Hagrid and Moody being two others) who knew that the task involved dragons. Snape had never seen a dragon in his life, and honestly had no desire to. Once again the incongruity struck him that the weekend excursion to Hogsmeade required permission, but sitting only yards away from a dragon in an open air stadium did not. \emph{I need to study law and work on negligence suits. It would pay better.}

In the end, Snape had to go. Dumbledore asked the whole staff to be present, partly as a show of school spirit, and partly to have extra adults on hand to supervise in case of problems.

The competition turned out to be quite exciting, which was no more than Snape expected, and interesting as well. Diggory, Delacour, and Krum all tried various spells against their dragons, with various levels of success. Potter's trial, the last of the day, was different. Potter used his wand to summon his broomstick, and suddenly it was a match between a Seeker trying to catch a Golden Egg, and the biggest, baddest Bludger the world had ever seen.

Flitwick was sitting near Snape, and from the moment Potter cried, \emph{"Accio Firebolt!"} he was bouncing up and down in his seat trying to see. "A summoning charm! Potter used a summoning charm! I've been trying to teach him summoning charms since the semester started, and he finally got it!"

Spectators rose spontaneously to their feet as Potter and the dragon matched wits and flying speeds, until suddenly Potter had the egg, and the competition was over. Potter had the fastest time of any of the contestants.

The crowd in the stands began to break up. Snape noticed that Moody joined McGonagall in seeing that Potter was whisked off to the nurse to tend a few cuts. Everyone around him was discussing the last task, some even reenacting Potter's flight with arms and hands. Snape and the other teachers tried to keep the crowd orderly and steer everyone back to the castle for supper.

As he himself was finally walking up the hill back to the castle, part of a rearguard shepherding the students, Snape looked back and saw Moody heading for the gate into Hogsmeade.

A few minutes later, as he was going toward his dungeon office, Snape felt pain stab through his left arm. Frightened, he hurried into the office and locked the door, then rolled up the sleeve of his robe to check the Dark Mark. The pain was subsiding, but the mark was more clearly etched on his skin than it had been before.

\emph{Not a summons. Thank goodness, not a summons. I'm not ready yet. An urgent summons from the Dark Lord would have caused the mark to burn black with a fiery pain, and this was nowhere close to that.} It was bad enough, however, that it forced Snape to consider something he'd been trying to avoid, to ignore since August. It could be ignored no longer, and Snape left his office to find Dumbledore.

That took a while to do. Dumbledore was busy with Crouch and Bagman, with Madame Maxime and Karkaroff, with a horde of other visitors and with the press. Clearly it would be a couple of hours before he was free. Karkaroff saw Snape and waved to get his attention, then pointed to his arm. Snape nodded to confirm he'd felt it, too, but the two of them didn't talk.

Not until long after dinner, when most of the dignitaries had left and the students were in their common rooms, did Dumbledore receive Snape in his office.

Snape's request was an odd one. "I want you to cast a Cruciatus curse on me."

Dumbledore paused, a glass of mead held out in his hand for Snape. "I beg your pardon?"

"I want—no, I need—you to cast a Cruciatus curse on me."

"Severus, I have never cast a Cruciatus curse in my life. I have no intention of doing what you ask."

"I've never cast one either, though I've watched while others did. More important, I've never felt one."

"Why would you want to?"

Snape showed Dumbledore the mark on his arm, clear and bright now where before it had been faint. "It hurt. It made me think of the pain. Then I thought of what's going to happen when I face him. All this work preparing for his legilimency—what if it's all in vain because I'm not strong enough to stand up to the pain?"

"Severus, the casting of an Unforgivable curse{\el}"

"You let Moody use the Imperius curse on the students."

"That was in a controlled situation, with their consent{\el}"

"This would be a controlled situation."

"Let me consult Moody{\el}"

"No! I don't want Moody to know anything about this!"

Dumbledore gazed at Snape for a long moment. "All right, Severus. Let me think about it. I shall let you know when I have decided."

The following Saturday, Dumbledore asked Snape to come up to his office.

"Sit down, Severus, make yourself comfortable. Mead?"

"I'm not sure. This doesn't sound like good news." Snape didn't sit down.

"Am I so easy to read, then? Very well. I have thought long and hard, and I do not think that I can accede to your request. The Unforgivable curses harm both caster and victim in ways that no other spells can, and I fear{\el}"

"You want me to face him cold. Unprepared. No defenses at all."

"That is not what I said. I want to protect you from the effects of the Unforgivable{\el}"

"Who's going to protect me from the effects of his curses?" Snape started to pace, highly agitated now. "Will you be there with a shielding spell? Are you going to give me armor he can't detect? When I face him, I'll be alone in a circle of Death Eaters. I'm going to need all the preparation I can get. Why won't you help me?"

"I will give you all the help I can, but the Unforgivable curses are beyond the pale. You cannot ask me{\el}"

"No, but you can ask me. You can ask me to walk blindfolded into a mine field. Isn't it true the curses only hurt the caster if done with malice? This isn't malice, this is charity—\emph{caritas}."

"Severus{\el}"

"Headmaster, please!"

They faced each other across the silence, and it was Dumbledore who gave in. "Come tomorrow at lunch, Severus. I shall study until then on the best way to proceed in order to achieve the maximum benefit with the minimum damage."

"Thank you, Professor."

The first session was awkward in the extreme, since neither Snape nor Dumbledore had any idea what they were getting into.

"We do not need to recreate the whole experience, do we? Surely something of lesser intensity would serve equally."

"When you say the Cruciatus spell, you're supposed to mean it. It doesn't have the same effect if you don't mean it. It doesn't sound as if you{\el}"

"Well, it is very hard to mean to hurt someone you are trying to help. Excuse me if my heart is not in it. Now, where should you be for this? Sitting? Standing? Lying down?"

They settled on Snape sitting in the chair before the fireplace. Dumbledore stood a bit behind him and to the side, so that Snape couldn't see him. "I'd best start with something mild," Dumbledore said.

"It's hard to picture you doing anything else."

"Are you ready?"

"No, but go ahead anyway." Even so, it was a surprise.

\emph{"Crucio!"} cried Dumbledore, pointing his wand at Snape.

Pain that could not be ignored washed through every fiber of Snape's being. It wasn't that he could say, `My hand hurts' or `My stomach hurts' for he wasn't aware of hand or stomach or any other part of his body. It was as if his brain was disconnected from the rest of him, floating in a sea of pain, and that sea permeated everything, so that around him and in him and through him there was only pain. He had no sense of time or place, no sense of who was near, no memory of why this was happening. Only pain.

Then the pain was gone, and Dumbledore was sitting next to him, offering Snape a goblet of mead. "What happened?" Dumbledore asked.

Snape's hand trembled as he reached for the glass, then he shivered, took the mead, and drained the goblet. "I'm not sure. I thought this was going to be mild."

"I thought it was."

"Either you don't know your own strength, or this is going to be harder than I thought{\el} But there was something wrong." Snape waited for his head to clear a bit more. "When the Dark Lord uses this spell, he talks to the one being punished. Questions are asked and answered. I wasn't aware of you at all. Why not?"

"I do not know," said Dumbledore.

They thought to try at least once more that afternoon. This time Dumbledore would stand in front of Snape and attempt to establish eye contact, even ask questions. It was a good half hour before Snape was ready, but he agreed that if he couldn't do it in Dumbledore's office, then he couldn't do it anywhere.

\emph{"Crucio!"} cried Dumbledore again.

Again Snape's body vanished and he floated in the sea of pain, but this time he was aware of Dumbledore's eyes. The eyes promised release, and he longed for them to free him. A thought formed between his consciousness and the pain. `What is your name?' the thought said, and he knew release came with the answer.

"Severus," Snape gasped. "Severus Snape."

The pain was gone, and Dumbledore sat beside him. "Eye contact seems to be a key," Dumbledore said, and Snape agreed.

"Next," Snape said, "I have to try not to answer."

"Are you sure that is wise?"

"If I can't control it, then everything we're doing is useless."

Snape refused another glass of mead, wanting to be sharp and aware. Dumbledore spoke the Crucio spell, and the pain and eyes returned. `What is your name?' the eyes asked, and this time Snape clenched his whole being into one obstinate lump and withheld the answer. Pain washed him, but it didn't increase in intensity. `What is your name?' pressed into his brain more insistently this time, but still he fought the pain, and still the pain was static, unchanging. `What is your name?' came a third time, and this time Snape thought a conscious, independent thought. `Why are you doing this?' the thought said, and Snape answered, "Severus, Severus Snape."

"Now you have to tell me what happened," Dumbledore said in Snape's ear.

"The longer I held out, the more my own thoughts were able to come through," Snape panted, trying to control breath and heartbeat, both of which were racing. "The pain remained the same, but I was beginning to think again."

"That," said Dumbledore, "is a major piece of information."

They agreed to work on weekends, and the first half of December, as the school prepared for the Yule Ball, Snape and Dumbledore practiced with the Cruciatus curse. The second Sunday, Dumbledore increased the intensity of his curse, and Snape was dazzled with the pain, but by the third try, gasping and struggling with the agony of it, he was able to endure until his own thoughts began to break through. It seemed progress was being made.

The third Sunday, as Snape settled into the chair before the fire, he suddenly began to cry. "I can't do this," he wept. "I can't do this anymore."

Dumbledore couldn't hide the concern in his expression. "What will happen on that day if you can't do it anymore?"

"I'll tell him everything I know."

"What will he do then?"

Snape watched Dumbledore with tired eyes. "He'll punish me."

"Will he kill you?"

"Not for a long time."

"Then I cannot send you to him. It is too much to ask. I cannot do this to you."

"No, it's worse than that. I have to go. If I don't go when he summons me, then he'll hunt me down and kill me. You don't leave the Dark Lord's service."

They sat for a while, then Dumbledore said, "Shall we try it again? I shall keep it gentle."

Snape nodded and waited for the Crucio spell. Through the pain he felt the question `What is your name?' With all his strength he tried to resist, but knew he was weakening. Then, suddenly, there was a new question, or rather a new command.

`Tell me about Lily.'

The effect was electric. Every door in Snape's psyche began to shut down, and adrenaline poured into his system. He was alert, in terrible pain, but alert. Nothing about Lily, not the tiniest shred of information, was coming through. The probe came again, `Tell me about Lily,' and Snape's mind began to respond, "I don't know Lily. I know nothing about Lily. Who is Lily?"

The pain stopped, and Dumbledore was smiling. "That was the problem," he said. "We were just asking the wrong question."

The Sunday before Christmas was the last session. Neither Snape nor Dumbledore had any desire to continue beyond that. As Snape sat before the fire in Dumbledore's office, Dumbledore toyed with his wand.

"Are you sure you want to do this again?"

"Something different this time. I have to know it works."

"Very well. What do I do?"

"Read me. The first time, try to find if I'm hiding anything. Try hard."

The curse was cast, and Snape let the pain sweep through him. He had more control over it now, though he didn't know what would happen if it intensified further. He felt the legilimency probe enter his mind and registered that the pain made it harder to resist. \emph{I need to adjust, maybe through several stages.} Then Dumbledore backed away.

"Nothing. Clear, open, and honest. Where do you hide all the skeletons?"

"Professional secret. Now, try again."

"Are we expecting a different result?"

"Maybe."

The second time lasted longer, and when the pain stopped and Dumbledore stood, there was a curious expression on his face.

"I found a locked door. You're hiding something from me. Is that what you wanted?"

"Yes. If something like Moody's eye can see them, I want the Dark Lord to think he can find them, too. Unaided. Was it difficult?"

"A little. It was well hidden. Camouflaged behind something else."

"Perfect. Now, last time. Count how many doors you find, and try to open one."

Again the mind probe entered his brain, and Snape didn't resist until Dumbledore selected a group of thoughts and tried to force his way in. Then without warning the pain spiked, and Snape cried out with the agony of it. Dumbledore stopped immediately. When Snape could focus again, he found Dumbledore sitting beside him with a goblet of mead.

"Three. I found three doors, nothing else. What happened?"

"Three is good. Three is what I wanted you to find. But when you tried to break through, the pain got worse. It's a good thing I want to let him see what's in those boxes. What scares me is if he finds the ones I don't want him to see."

In the entrance hall on the way to Sunday supper, Snape ran into Moody.

"Good to see you back on solid ground, Snape old boy. That rarified atmosphere up in Dumbledore's office must make you giddy."

"Are you monitoring my movements?"

"I like to know where all my little Death Eaters are at any given moment. It makes me feel safer."

"I make Alastor Moody feel unsafe. I must be doing something right."

"Got a date for the Yule Ball? Or is it hard for an old man like yourself to find a date?"

"You must have one foot in the grave, Moody. You never used to fixate on my age before. You've been calling me `old man' and `old boy' since you got here. Maybe it's because you're in your second childhood now."

To Snape's great surprise, Moody didn't respond. Instead he stared at Snape for a few seconds, then turned and stumped in to supper. Snape watched him speculatively before following him into the Great Hall. They sat at the high table in silence, and all through supper Snape wondered what he'd said that shut Moody up so completely. He rather wanted to be able to repeat it.

The evening of the Yule Ball arrived, and all the students were making their way to the Great Hall dressed in their finest robes. The Hall was decorated in frosty white with green garlands, and instead of the long medieval tables with their benches, there were round banquet tables.

Snape was not wearing dress robes, nor did he take a seat in the Hall for the feast. The moon was in its last quarter again and wouldn't rise until midnight, the weather was surprisingly balmy, and Snape had managed to finagle the job of patrolling the grounds. He considered this a prize position since his student contact was minimal, he could stay out of the way of Moody and Karkaroff, and he didn't have to listen to the music of the Weird Sisters.

Instead, he stopped off at the kitchens to pick up a plate of food and, passing Professor Vector, who was on duty in the entrance hall, took it out onto the stairs to eat. The stars glittered overhead, and the world seemed at perfect peace. Snape felt Lily's presence, but that evening he had no need to talk to her. They had often sat by the lake as children, not talking but content just to be together and watch the sky.

From inside the castle, Snape could hear the music start and the beginning of the dancing. That meant that his own job was about to start, too. Not all of the students were interested in dancing, and it was Snape's duty to show them the error of their ways.

After the second dance, the first couple appeared on the steps, a seventh year boy and a sixth year girl. Both started when they saw Snape, then said, "Good evening, Professor." They were, they said, just going to stroll for a while to get away from the noise and the heat of the hall. Snape let them go, but noted the direction they'd gone.

A few minutes later, Karkaroff came out.

"Here you are, Severus. I need to talk to you someplace private. Come." He took Snape's arm and steered him across the lawn away from the light shining out from the castle. "I want to know what you're planning to do."

"Planning to do about what?"

"About what? About this!" And Karkaroff quickly touched his left arm.

\emph{I'm not talking to Karkaroff. I'm talking to the Dark Lord. Nothing I say to Karkaroff can be hidden. He'll want to see it all.} Snape look out across the lawn so that Karkaroff wouldn't be able to see his eyes. "Not everyone is panicked by this, Igor. A lot of people are waiting for it. You don't have to panic either."

Karkaroff stared at him. "You know what I did to get out of Azkaban. You know how many of our colleagues want me dead. I can't go back. And you! Go back? You betrayed them all before the Dark Lord fell. You were selling them out to Dumbledore while you were still training them in London. What they'll do to me is nothing compared to what they'll do to you. I heard Dumbledore say so in front of the tribunal. You sold them out before the Dark Lord's downfall, and you were Dumbledore's spy among us."

"I was where the Dark Lord told me to be, doing what the Dark Lord told me to do. Fooling Dumbledore was part of that. I have nothing to fear."

"No? Well maybe you have something to fear from Dumbledore, then. Or from Moody. Shall I tell them of this conversation? I spent time in Azkaban—maybe now it's your turn."

"Go ahead. Tell them. Dumbledore won't believe you, and Moody can't do anything." Snape turned back to Karkaroff. "I have a job to do out here. If you want to talk, you have to come with me." He headed for the garden area with Karkaroff in tow. "You aren't the only one he'll be angry with. He isn't going to kill everyone who tried to save his own skin. Besides, you might be reading the signs wrong. Do we know for certain he's coming back now?"

They reached the gardens and Snape listened carefully. Teenagers in the throes of a hormonal rush were seldom discreet. He pointed his wand at a tree and whispered, "Petrificus Totalis," then lit a Lumos spell. A second later he said, "Liberacorpus," and the two embarrassed students clambered to their feet. "I know, Hancock," Snape drawled sarcastically, "she fainted and you were giving her mouth-to-mouth-resuscitation. Ten points each from Slytherin. Get back into the Hall where you belong."

Karkaroff was still there. "I don't see how you can make light of this."

Snape continued through the garden. "I think you're overreacting. I really don't see what there is to fuss about, Igor."

"Severus, you cannot pretend this isn't happening! It's been getting clearer and clearer for months. I am becoming seriously concerned. I can't deny it{\el}"

"Then flee. Flee{\el}" Snape waved towards the castle. "I will make your excuses. I, however, am remaining at Hogwarts." He spotted another couple and sent a blast into the rosebush they were hiding behind, deducting ten points each from Ravenclaw and Hufflepuff as the students scurried to shelter. \emph{No real harm. The roses have to be pruned in January anyway.}

Potter and Weasley were in the garden, too, interestingly enough without their dates. Snape impatiently shooed them along. After a few more minutes of fruitless conversation, Igor returned to the castle and Snape to his job of frustrating adolescent love.

In the week between the Yule Ball and the beginning of the next term, Dumbledore asked Snape to come to his office again.

"Any news? Any change?"

Snape sighed. "Only what we expected would change. The mark is changing. It's becoming darker and clearer. Karkaroff's too. He's getting very worried about it, and I don't really blame him. I can find ways to justify the last thirteen years. He can't. He didn't just claim to be under an Imperius curse or to be coerced into the Death Eaters. He named names and sold people out. If we ever do get a summons, I'm afraid he's going to run."

"Ah, but where to? There are not a large number of safe places to go."

"I really think that's his main reason for keeping the location of Durmstrang a secret. I think he wants to be able to go there first. If no one knows where the school is, it'll give him time to get somewhere safer."

"No lion's den for Karkaroff, then." Dumbledore fingered his beard for a moment. "I did want to talk to you about something else. Have you been working on your Patronus?"

The question surprised Snape. "Not really. With the dementors gone, I didn't see the need."

"I hope you recall that I asked you to learn the Patronus charm before we had any dementors at Hogwarts. I hope you do not think I anticipated that little invasion."

"That's right. It was the year before, wasn't it? Why do you think I need it now? I'm not summoning a Patronus against the Dark Lord. I'm not that foolhardy."

"You can do other things with a Patronus that are very useful, such as send virtually undetectable messages."

"I didn't know you could project a Patronus to any distance."

"Oh, quite long distances. I have done it from here to London on many occasions. The Patronus does not allow itself to be intercepted, and cannot be overheard or detected like floo powder can."

"What situations are you envisioning here?"

"Well, I hate to bring it up, but the time might come when you need to get into Hogwarts very quickly. Let us say a situation involving hot pursuit. If you send the Patronus ahead, we can be at the gates to admit you and close them in the face of pursuers."

"Hot pursuit!" Snape rose from his chair and sloshed tea out of his cup before he managed to set it down. "Hunted down like a criminal! Like an animal! What kind of scenarios are you preparing for me?"

"Easy, Severus, easy. It is a worst-case scenario, but better to plan for any eventuality. Better to have it and not need it than to need it and not have it."

In the end, Snape agreed that Dumbledore had a point and began working on the Patronus. He was out of practice, and was therefore pleasantly surprised to find that the misty little fox with the sharp nose and black eyes was easy to conjure. Getting it to move from place to place on command was more difficult, but Snape persevered, working mostly in the evenings, and soon was able to send the Patronus to a specific spot along the lake bank at will.

A major obstacle was Moody, who continued to be fascinated by Snape's every movement. Most often Snape pretended to be working in his office, and slipped past Moody that way. Occasionally Dumbledore distracted Moody to enable Snape to escape undetected from the castle. One of the most intriguing things about the situation was the degree to which Dumbledore seemed to sympathize with Snape's desire to keep Moody entirely out of the picture.

Other things were happening to disrupt the routine at Hogwarts, however. One of the biggest came from outside in the form of an article in the Daily Prophet. It seemed a particularly obnoxious reporter by the name of Rita Skeeter had discovered a long concealed secret about Hogwarts. About Hogwarts, and about Hagrid.

It was shortly after the beginning of the term that several things seemed to happen at once. Returning to his office after practicing with the Patronus, Snape had a sudden sense that things were not quite right. Maybe it was the feel of the door as it opened, or an almost unnoticeable change in the air, but Snape knew that someone had been there. Since Snape's office was always locked with fairly strong spells, it had to be one of the teachers, or an unusually powerful student. Snape rather fancied he knew which.

Snape began a slow, methodical search of the office, checking his inventory lists against the vials and jars on the shelves. What was missing was powdered bicorn horn and shredded boomslang skin. \emph{Someone is making Polyjuice potion. The last time this happened was two years ago when Granger was in hospital, having semi-transformed herself into a cat.}

The problem was that Snape was reasonably sure this wasn't a student. He remembered all too well the incident of the firecracker in the cauldron that was the cover for the one who sneaked into the office for the potion ingredients. He really didn't believe that even Granger was capable of opening his office doors when they were locked.

\emph{Which left a short list of suspects. Why would Moody need Polyjuice potion? Who is he planning to transform himself into?}

The next day before breakfast, Snape was in Dumbledore's office.

"Polyjuice potion. The two ingredients are used together only for Polyjuice potion. Which means that whoever took them is planning to transform himself into someone else for an hour. How am I even supposed to know at this moment that you are you?"

Dumbledore did not seem concerned. "Because Polyjuice potion does not transfer memories, and anyone transforming himself—or herself—into me would still not know how to get into the office without the password. And I know that you are you because I can look into your eyes and see the Severus I have known these past two and a half decades. So we are reasonably sure of each other. Why do you suspect Moody?"

"Who else could it be? The only students are a couple of sixth and seventh years that I know quite well, and who wouldn't do it, and Granger for the pre-OWL crowd, but I don't think even she is that good. This happened between supper and ten o'clock, so that rather precludes outsiders, and who among the `regular' staff would you suspect? The only ringer is Moody. By the way, what's my patronus, and what major medical problem did I have as a child?"

"A fox, and you are assuming Hagrid told me, but it was rickets. You might want to know that I prefer raspberry jam."

They looked at each other for a moment. "Have you ever heard of James Bond?" Snape asked.

At breakfast, Snape could see from some distance that McGonagall was reading \emph{The Daily Prophet} and fuming. Not everyone had yet come down, so Snape slipped into the seat on her left.

"What's happening in the wide world?" he asked.

"Murder, if I can get my hands on her," replied McGonagall. She handed him the newspaper. There, under the byline `Rita Skeeter' was a story exposing the fact that Hagrid was half giant and speculating on the potential danger he posed for the students at Hogwarts and the wizarding world at large.

"The ugly old bat!" exclaimed Snape. Then he saw McGonagall's expression and backpedaled furiously. "You, on the other hand, are neither ugly nor a bat. And I can't help my age. Who does this `Skeeter' person think she is, anyway?"

"For your heart being in the right place, you're forgiven. Someone's got to talk to Hagrid."

The problem was that Hagrid wouldn't talk to anyone else. He'd already informed Dumbledore that he was sick and called in a substitute, a rather competent instructor named Grubbly-Plank. She was, in fact, far better at the professor business than Hagrid, and had only sentiment against her. Hagrid locked himself in his hut.

This presented a quandary for Snape. He had an enormous quantity of images of Hagrid that had to be sealed, double sealed, and triple blocked from the Dark Lord. At the same time, he wanted to let Hagrid know of his support. Dumbledore solved the problem by assuring Snape that he would pass along any messages to Hagrid.

It wasn't as if Hagrid didn't understand Snape's problem. After all, it was to Hagrid that Snape had gone for his defection. In terms of understanding the stakes, Hagrid came third. Right after Dumbledore and Snape himself.

The next Hogsmeade excursion was Saturday, January 14. This time Snape was excused any supervisory duty. Moody, on the other hand was assigned to keep an eye on the students and had to spend the entire day off the grounds. The reason for this arrangement became apparent after the older students left.

"Come with me, Severus. We are going out to the forest to practice something new. This should, quite frankly, be much easier for you than for most people, or I shall be very surprised."

They went only a little way in, more to be out of sight than anything. Then, with a flick of his wand, Dumbledore called \emph{"Expecto Patronum!"} Before Snape's astounded eyes there appeared a snow-white phoenix, a spectral bird of mist and ice. It was beautiful.

"Now this is the tricky part," Dumbledore was saying. "You are going to learn to send a message by Patronus. First get it to pause, like this, and be sure you know what you want to say. Then say, `Mitto nuntium' and tell it the message. I suppose you could project it nonverbally, but not everyone can do that. Then you tell it `Nuntius estis ad{\el}' and the name of the person you are sending the message to. Like owls, Patronuses always know where the person is."

"How do you receive the message?"

"Why do you not go across the clearing, and I shall send one to you. You try to send one in response."

Snape did as he was told, repeating over and over to himself Mitto nuntium and Nuntius estis ad{\el}, and wondering, not for the first time, why Latin wasn't taught as a subject at Hogwarts. When he was in position, he faced Dumbledore and waited.

Dumbledore spoke to his Patronus, then dispatched it towards Snape. It crossed the clearing in a microsecond, hovered before Snape, and suddenly his mind was receiving the words, \emph{`Is this not easier than floo powder?'} Immediately thereafter, the Patronus vanished.

\emph{Why can't it all be nonverbal?} On a sudden whim, Snape raised his own wand and summoned little Renard soundlessly. He was pleased to see that the fox was looking more and more cunning with each appearance. Silently Snape projected the words \emph{Mitto nuntium, Is there a limit to length?}, and \emph{Nuntius estis ad Dumbledore}.

The fox went instantly to Dumbledore, who conjured his phoenix and replied, \emph{`I do not know. I have never tried to send War and Peace.'}

Dumbledore returned to his office, and Snape practiced sending messages to him there for about an hour. It was clear from the first, however, that this was something Snape could do well. Very little practice was needed.

Later that afternoon, Dumbledore went to see Hagrid. Snape wasn't privy to that conversation, though he knew that Dumbledore carried with him a stack of letters from parents who had been students at Hogwarts and from the staff. All of them expressed confidence in Hagrid, and requested that Dumbledore keep Hagrid on. The meeting must have been successful, since Hagrid appeared at Monday morning breakfast and took up his classes again.

Things remained calm until the following Thursday night. To be more precise, it was one o'clock in the morning of Friday the twentieth.

That evening, Snape had stayed up reading until eleven, when he'd undressed for bed (it was cold, and a gray flannel nightshirt was in order) and, after some tossing and turning, fallen asleep. At about one in the morning, he was awakened by the most horrible shrieking and caterwauling he'd ever heard coming from the entrance hall.

Snape was awake immediately, and the first thing he noticed was a faint glow under the door to his office. Wand at the ready, he approached and opened the door. No one was there, though a torch had clearly been lit on the opposite wall to give light to whomever had been sneaking around.

\emph{Is this one mystery, or two? Did the shrieking that woke me have something to do with the person who broke into my office, or did it interrupt him in the middle of his search?}

Quickly throwing a dressing gown over his nightshirt, Snape made his way to the entrance hall. The disturbance, however, was farther up, and Snape climbed the stairs to the second floor where he could hear Filch raving:

"Hiding are you? I'm coming to get you, Peeves{\el} You've gone and stolen a Triwizard clue, Peeves{\el} Dumbledore'll have you out of here for this, you filthy, pilfering poltergeist{\el}"

Stepping out onto the second floor, Snape said, "Filch? What's going on?"

"It's Peeves, Professor. He threw this egg down the stairs." For some reason, Filch thought it necessary to whisper, even though they were nowhere near any dormitories or private rooms. Except Moody's.

Snape went further up to be able to talk to Filch without making any more noise. He looked at the egg curiously. It was from the first Triwizard task, and was supposed to contain clues to the second task. "Peeves? But Peeves couldn't get into my office."

Filch didn't understand what the egg had to do with Snape's office, but confirmed that the wailing and banging that awakened Snape had come from the egg. Snape alerted Filch to the fact that someone had been in his office.

"But Peeves couldn't{\el}"

"I know he couldn't. I seal my office with a spell none but a wizard could break!" Snape thought again of Moody and looked up the stairs and around the corridor, wondering why Moody hadn't come out to investigate the noise. \emph{It isn't as if he has a reputation for sleeping through odd occurrences, quite the contrary.} "I want you to come and help me search for the intruder, Filch."

Filch had other plans. He wanted to go to Dumbledore about the incident and get Peeves thrown from the castle once and for all.

"Filch," replied Snape, now exasperated, "I don't give a damn about that wretched poltergeist; it's my office that's{\el}" Then he heard the unmistakable sound of Moody's wooden leg and stopped. \emph{If there's anything I don't want, it's for Moody to hear this.}

But it was impossible to stop Filch. He immediately began telling Moody about the egg. "{\el} and then Professor Snape discovered that someone had broken into his off{\el}"

"Shut up!" Snape hissed, but the damage was done.

Moody moved closer and scanned Snape with his enchanted eye, then paused, mouth open in mock surprise at what he `found.' "Did I hear that correctly, Snape? Someone broke into your office?"

"It is unimportant." \emph{And since it was probably you, your little act is fooling no one.}

"On the contrary, it is very important. Who'd want to break into your office?" Moody was gazing into Snape's face with the enchanted eye.

He's trying to read me. Let's see you read a brick wall, you bastard. And Snape closed off every part of his mind to the probe, something he'd only done before in dueling situations. "A student, I dare say. It has happened before. Potion ingredients{\el} students attempting illicit mixtures, no doubt{\el}"

"Not hiding anything else in your office, are you?"

Only the presence of Filch was now keeping the exchange from turning into a fight. Snape wanted nothing more than to wipe the ugly grin off Moody's face. "You know I'm hiding nothing, as you've searched my office pretty thoroughly yourself."

"Auror's privilege, Snape. Dumbledore told me to keep an eye{\el}"

The baldness of the man's lie was breathtaking. "Dumbledore happens to trust me. I refuse to believe that he gave you orders to search my office!" \emph{Give me an excuse. Go for your wand and give me a reason{\el}}

A strange glint had come into Moody's real eye, as if he'd found something he'd been seeking for a long time. "'Course Dumbledore trusts you. He's a trusting man, isn't he? Believes in second chances. But me—I say there are spots that don't come off, Snape. Spots that never come off, d' you know what I mean?"

The stab of fire through the mark on Snape's left forearm was blinding. Snape gripped the arm in sudden, uncontrollable pain that was as instantly gone. Shocked to the core of his being, Snape stared at Moody. \emph{How did he do that? How could he do that? Aurors can't control the Dark Mark. Only the Dark Lord and his lieutenants{\el} Did he learn that from prisoners in Azkaban? Or{\el}}

Moody seemed quite pleased with the results of his action. He grinned. "Get back to bed, Snape," he said, like a parent commanding an errant child.

"You don't have the authority to send me anywhere! I have as much right to prowl this school after dark as you do!" That didn't come out quite the way Snape had intended, but he was so angry now that he was talking without thinking. Moody would get the gist of it.

Moody, in fact, seemed quite amused. "Prowl away. I look forward to meeting you in a dark corridor some time{\el}" The threat was implicit, and Snape was about to reply when Moody pointed past him. "You've dropped something, by the way{\el}"

Snape turned to look at the step Moody pointed to. He recognized the thing immediately. It was James and Sirius's map. The map he'd last seen in the possession of Lupin. The map that somehow still remained at Hogwarts{\el} And it was functioning, with the names of people moving over it! Snape reached for it only to have it fly past his fingers as Moody cried{\el}

\emph{"Accio Parchment!"} Then Moody grinned like a satyr. "My mistake. It's mine—must've dropped it earlier."

But now everything was clear. Moody had been working all the previous term to get Potter's confidence, starting with that little episode with the ferret. That was what Moody'd meant about `getting what he wanted.' What he wanted was Potter helping him. "Potter," Snape muttered aloud.

Moody's attention was drawn to the sound. "What's that?"

"Potter! That egg is Potter's egg. That piece of parchment belongs to Potter. I have seen it before, I recognize it! Potter is here! Potter, in his Invisibility Cloak!" \emph{On the stairs. He must be on the stairs, and Moody can see him with that damned eye.} Snape stretched out his hands and began moving upwards.

Clearly that was not what Moody wanted, for he snapped, "There's nothing there, Snape! But I'll be happy to tell the headmaster how quickly your mind jumped to Harry Potter!"

"Meaning what?" Snape's head turned to look down the stairs at Moody.

"Meaning that Dumbledore's very interested to know who's got it in for that boy! And so am I, Snape{\el} very interested{\el}" Moody moved closer as he spoke, demanding eye contact.

The image that entered Snape's mind was of the Dark Lord as he'd been fourteen years earlier, and himself kneeling to his lord in a circle of Death Eaters. A memory, perhaps, wrenched from the mind of a Death Eater in Azkaban and now brought forward to intimidate Snape. Placed in a pensieve for the perusal of Cornelius Fudge, it was damning. Snape began to retreat.

"I merely thought that if Potter was wandering around after hours again{\el} it's an unfortunate habit of his{\el} he should be stopped. For{\el} for his own safety."

"Ah, I see. Got Potter's best interests at heart, have you?"

"I think I will go back to bed," It was the order Moody had given him only minutes before. It was defeat. It was surrender. \emph{At least for now, until I have a chance to talk to Dumbledore and figure out what this all means.}

"Best idea you've had all night." As Snape passed him going down the stairs, Moody stopped him with a hand on his arm and whispered, too low for Filch to hear, "You and I may be having our little chat earlier than expected, and not in Azkaban."

Snape swept past Moody, along the corridor and down the stairs to the entrance hall without looking back. Once in his own office, however, he realized that he was near collapse. The disturbingly accurate image, the threats, the knowledge that the Marauder's map was now in Moody's possession and that he would never be alone—all of this was having a profound effect on the already distraught Snape's nerves.

\emph{I have to see Dumbledore tomorrow. He has to rein Moody in. I can't live like this.}

The next morning Snape was waiting for Dumbledore outside the latter's griffin statue staircase well before breakfast. "You have to talk to him! You have to do something about him! You have to make him leave me alone!"

"Let me see, Severus. `He' could be so many people. Are we discussing Professor Flitwick?"

Snape closed his eyes and took a deep breath. "Moody!" he spat out. "Keep him away from me!"

"Come, Severus. I am hungry. Could you entertain me at breakfast with what Alastor has done now?"

"You're not taking this seriously." Snape stopped in the corridor and waited until Dumbledore also stopped and turned to look at him.

"You must admit, Severus, that so far your charges against Professor Moody have been highly vague. Do you think you might calm down enough to explain in more detail what has upset you so?"

"He's been searching my office. I believe he's taken things. And he says he's doing it on your orders."

"My orders? Not my orders. No. Come, Severus, let us go to my office now. We can have breakfast there in private."

"He'll know."

"And how will he know?"

"He has the map. He can watch all of us from the comfort of his own rooms, and he'll know we're talking."

"And what map, pray tell, is this?"

"James's map. The one Filch took from Sirius. But Potter had it, and then Lupin took it from me. But I found it in Lupin's room, except when they knocked me out, I don't know what happened to it, but now Potter had it, and Moody's got it."

"I see. You really must come and have breakfast in my office, Severus. You will feel better. It is a blood sugar thing. What exactly does this map do besides show direction?"

"It shows where every person in Hogwarts is at any given moment."

"Do you mean it shows you and me talking together in this corridor?"

"It does. The first time I saw it was back in the old days. Sirius was using it to ambush me outside the library, but someone snitched and I caught him instead. I told Filch, who confiscated it. The next thing I know is it's about fifteen years later and Potter has the map. Except Lupin insisted on taking it—Dark Arts teacher and all. Last night Potter had it again, but Moody summoned it and now he's got it. He can monitor everything I do. Everything."

By this time Dumbledore had lured Snape up the spiral staircase, and they were in his office. Dumbledore contacted the kitchen, and breakfast was magically sent up for the both of them. Snape was, in fact, quite hungry, and began to eat automatically as he and Dumbledore discussed the situation.

"Now, the first complaint you have is that Alastor is in possession of an enchanted artifact that will allow him to monitor your movements every moment. What is your next complaint?"

"He's been searching my office. Someone broke into my office last night. When I accused him of it, instead of denying it he told me that you'd given him permission—no, orders—to keep an eye on me."

"You know that is not true."

"That's what I told him. I told him you trusted me, and you wouldn't allow it. Then he said you were a trusting person who believed in second chances, but he knew a leopard couldn't change its spots, and that's when he made the mark hurt."

"Tell me that again."

"The mark on my arm. He made it hurt. He made it burn almost as if I were being summoned. He enjoyed it, too. I could tell by the look on his face."

"Did he say anything else?"

"Well he's always talked about interrogating me in Azkaban, but last night he said we'd have our `little chat' soon, and not in Azkaban. I took it as a threat. That's what it felt like."

"I think I need to talk to Alastor. Thank you for advising me of all of this."

The next few weeks leading up to the second task in the Triwizard Tournament were a foretaste of eternal damnation. Moody was everywhere, ostentatiously letting Snape know that his movements were a matter of public record. Moody managed to meet Snape at the entrance to the Great Hall for every meal, to greet him and walk with him to the teachers' table. Moody popped out into the corridor at odd moments to almost bump into Snape and then, smiling, ask Snape's pardon for nearly running into him.

Snape was even unable to continue working with his Patronus. He went down to the lake shore one evening, only to glance up and see Moody watching him from the top of the hill. \emph{I can't do this with him as a spectator}. Snape reluctantly returned to his own rooms.

"Do something!" Snape screamed at Dumbledore midway through February. "That man is driving me crazy! Take that map away from him!"

"He denies that he has it. He denies any knowledge of it."

"He's lying. Read him—you'll see he's lying."

"You know I cannot read him without his permission. I do not read you without yours."

"Ask Potter. You don't have to read Potter. That boy's face is an open book."

"I would prefer not bothering Potter while he is immersed in preparing for the second task."

Snape examined his hands, his fingernails, then looked around at the walls, the ceiling, anywhere but at Dumbledore. He was trying to think of something to say that he hadn't already said.

It was Dumbledore who spoke first. "Maybe there is something I can do. The next time you wish to work with the Patronus, send it first to me. I shall come down."

That evening Snape summoned the Patronus in his own room and sent it with a message to Dumbledore. Going down the hill to the lake, he glanced behind him and saw Moody leave the castle. By the time Snape reached the lake shore, Moody was on the overlooking cliff, staring down at him. Snape waited.

A moment later Dumbledore appeared and greeted Moody on the cliff. They spoke for a few minutes, then Dumbledore took Moody's arm and steered him back toward the castle, talking in an animated fashion all the while.

Things got better after that, as Moody came to realize that Dumbledore was monitoring him with the same tenacity that he was monitoring Snape. Snape began to get some of his privacy back.

In the week before the second task, Snape was descending from the library using the stairway between the fourth and second floors, the same staircase where he'd encountered Moody before. Moody suddenly strode along the corridor, stopped at the foot of the stairs, and looked up.

"I'd like to see you in my office for a minute, Snape," he said curtly, then turned and walked away.

\emph{Don't kill him. Don't kill him. At least not here. Somewhere where it'll be harder to find the body, maybe.}

Following behind, Snape saw Moody enter his office. He arrived at the door a moment later and put his hand to the latch. It opened quietly. As Snape entered, he saw Moody step away from the wall. Moody was covering something that hung there, something that might be a mirror or a painting.

\emph{Curious. Why would he do that?}

"Hello, Snape. What can I do for you?"

"You just asked me to come here."

"I did? Odd. I can't imagine why I'd do that. Are you sure?"

Furious, but not knowing what to do short of physical violence, Snape turned and left, slamming Moody's door behind him. \emph{What was that all about? Why would he want me to come to his office just to dismiss me? And what was the thing on the wall that he was covering?}

By the time Snape got used to the fact that Moody was no longer hounding him, the second task of the Triwizard Tournament was on them. The morning of February 24, Snape stood on the hill looking down as the spectator stands were set up on the far side of the lake. He had absolutely no interest in the competition whatsoever.

What he did realize, had realized for several days, was that he hadn't done a thorough inventory of his office since before the last break-in. He didn't even know what Moody had taken. \emph{That's what happens when you let yourself be intimidated and manipulated by someone like Moody. And if Dumbledore had asked, you wouldn't have had an answer for him.}

Almost the whole school was now in the stands, the champions of the three schools were being briefed, and Snape left the cliff top to go back into the castle. At which point, he was nearly knocked down by a panicky Harry Potter, who shot out of the door of the castle and pelted downhill at full speed. The boy hadn't even noticed Snape.

\emph{Why is he late? You'd think he didn't care.} Snape reentered the castle and went directly to his office in the dungeon.

\emph{Boomslang skin and gillyweed? Who would possibly want both boomslang skin and gillyweed? The boomslang could be for more Polyjuice potion, and tie into the robbery at the beginning of the term. But gillyweed?} Then Snape made the connection and could have slapped himself for being so obtuse. \emph{The task today! It's underwater. One of the champions stole the gillyweed. Three guesses who!}

Snape settled himself to think it through. \emph{Potter was out the night that someone was in my office. And he was also on the staircase. But why didn't he just continue up to Gryffindor Tower? Why stop there? Filch wouldn't have known. I wouldn't have known. He probably wanted the egg back. But why have the egg with him to begin with?}

Then a thought occurred that almost made Snape laugh. \emph{What if high and mighty Potter got his foot stuck in the step that only catches first years? Made him drop his egg{\el} Probably not, though it's a sweet thought. Still doesn't explain why he had the egg with him, though.}

\emph{Or why Moody didn't come out right away. He should've been there before me, maybe before Filch. Perhaps he knew Potter was going after the gillyweed and wanted to stay clear in case of trouble. Does that mean Potter stole the Boomslang skin for Moody? Or is Potter planning his own little transformation?}

\emph{One thing's for certain. Moody 'd never seen the map before. Otherwise he wouldn't have drawn attention to it. But Moody kept it. Kept it to use against me. That must've upset Potter. What does Moody have over Potter to get Potter to give in like that? Of course, with a fourteen-year-old it doesn't take much.}

Noise in the corridor informed Snape that the competition was long over. He went out to mingle and hear what had happened. Potter, it seemed, had won and was now tied overall with Diggory. Good news for Hogwarts. What was far more interesting was that Potter'd been able to swim underwater because he managed to grow gills.

\emph{Did he now? That part's confirmed. Potter took the gillyweed. Next Potions class I'm going to have to find a way to talk to Potter and put the fear of God into him. How to do that?}

As Potions master, Snape was required to keep certain things on hand. Things like Veritaserum. Dumbledore had never used it, but since it took a month to make, it had to be ready for use at any time. Snape filled a tiny vial with the clear liquid and carried it with him for the next several days.

Snape got his opportunity during the next class with the fourth year Slytherins and Gryffindors. That horrid busybody Rita Skeeter had written a scathing indictment of Granger in the latest copy of Witch Weekly, and Granger had the misfortune to be reading it after the lesson started. To make matters worse—though for Snape at that moment it was better—the three musketeers were discussing the article as well. In audible voices. Snape crept up on them.

"Fascinating though your social life undoubtedly is, Miss Granger, I must ask you not to discuss it in my class." The sight of all three of them, Granger, Potter, and Weasley, jumping at the sound of his quiet voice was rather gratifying to Snape.

"Ah{\el} reading magazines under the table as well?" As he spoke it occurred to Snape that Potter, knowing nothing of legilimency or occlumency, would project thoughts much better if he were angry. "Oh, but of course{\el} Potter has to keep up with his press cuttings{\el}"

Now there is something about reading an article, any article, with a clinical tone lightly tinged with disbelief that renders that article highly amusing to the listeners and embarrassing to the subject. Snape picked up the magazine and started, "Harry Potter's Secret Heartache{\el}" and watched the faces of the trio grow more flushed and emotional as he continued to the end. "How very touching."

Then Snape separated the three, taking advantage of the opportunity to place Potter next to his own desk, where he could talk to the boy more privately.

Snape walked back to his desk, and Potter followed. As he watched Potter unload his cauldron and then sit, sullenly pounding his scarab beetles, Snape was able to focus on the fact that he absolutely loathed the boy.

\emph{You arrogant, puffed up little popularity hound. You don't care how many people you could injure in your desperate quest for fame and attention. You wouldn't confide in McGonagall, so instead of facing four adult wizards trained in combat, the weakened Dark Lord had to deal only with an eleven-year-old and was able to escape, and your friend Weasley's life was put in danger. Then, when you should have gone to Dumbledore with a suspicious enchanted object, you chose to play with it instead, and nearly got Miss Weasley and yourself killed. You walked starry-eyed into the trap of a killer and a werewolf because you chose to trust the judgment of a man who couldn't remember what phase of the moon it was. And now the hubris that brought you to tricking your way into a competition beyond your skills has got your sticky little fingers pawing through my office and my belongings.}

The rest of the class had quieted down and was concentrating on the assignment, and Snape leaned forward, whispering so that only Potter could hear. "All this press attention seems to have inflated your already overlarge head, Potter. You might be laboring under the delusion that the entire wizarding world is impressed with you, but I don't care how many times your picture appears in the papers. To me, Potter, you are nothing but a nasty little boy who considers rules to be beneath him."

Potter pretended not to hear, but the scarab beetles he was so obstinately pounding had long since turned to powder. Snape continued. "So I give you fair warning, Potter—pint-sized celebrity or not—if I catch you breaking into my office one more time{\el}"

Potter lashed out then. "I haven't been anywhere near your office!"

Snape and Potter sat, face to face and eye to eye. \emph{If I were a better legilimens, I'd try to read him.} "Don't lie to me. Boomslang skin. Gillyweed. Both come from my private stores, and I know who stole them." The flicker of guilt in Potter's eyes was unmistakable. \emph{Even if you didn't take the ingredients, you know who did, you sneaking little thief.}

Then Potter lied outright. "I don't know what you're talking about."

"You were out of bed on the night my office was broken into! I know it, Potter! Now, Mad-Eye Moody might have joined your fan club, but I will not tolerate your behavior! One more nighttime stroll into my office, Potter, and you will pay!"

Snape brought out the little vial he'd filled earlier. "Do you know what this is, Potter? It is Veritaserum—a Truth Potion so powerful that three drops would have you spilling your innermost secrets for this entire class to hear. Now, the use of this potion is controlled by very strict Ministry guidelines. But unless you watch your step, you might just find that my hand slips right over your evening pumpkin juice. And then, Potter{\el} then we'll find out whether you've been in my office or not."

Potter didn't respond. He couldn't look at Snape, but turned back to his class assignment and worked cutting up the second ingredient, ginger roots. The boy clearly had a lot to hide.

There was a knock on the door, and Snape called "Enter" automatically. The one who entered, to Snape's great annoyance, was Karkaroff. The man was twitching like a dog with fleas and talking through clenched teeth. \emph{Right, Igor. Let's hide from the whole school the fact that you're nervous as a cat on a hot griddle.}

"We need to talk," Karkaroff said.

It would never occur to this idiot that half of these students are children of Death Eaters. "I'll talk to you after my lesson, Karkaroff."

"I want to talk now, while you can't slip off, Severus. You've been avoiding me."

\emph{And you have just illustrated why. Do you see Potter sitting right next to this desk?} "After the lesson!"

But Karkaroff wouldn't leave. He hovered like a bat behind Snape's chair, a subject of intense curiosity for every student in the room. Snape wanted to hit the man. At last the class was over and the students filed out.

Rising and turning to face Karkaroff, Snape demanded, "What's so urgent?"

"This." And Karkaroff rolled up his sleeve to show Snape the mark on his arm. "Well? Do you see? It's never been this clear, never since{\el}"

Snape was horrified. Here, in an open, unsecured classroom, Karkaroff was talking about the Dark Lord and uncovering the mark. "Put it away!" he snapped, and looked around to see who might be watching. That was when Snape saw that Potter was still in the room, huddled on the floor listening.

"But you must have noticed{\el}"

"We can talk later, Karkaroff! Potter! What are you doing?"

Then Potter was talking about armadillo bile, and Karkaroff was stomping out of the room, and a furious Snape was trying to cope with the knowledge that Potter—arrogant, indiscreet, self-centered, undisciplined Potter—might now have something he could threaten Snape with.

The following Saturday was a Hogsmeade excursion, and this time Snape was on supervisory duty. Concerned about what Potter might guess after overhearing his conversation with Karkaroff, Snape planned to keep an eye on the boy. Potter, Weasley, and Granger left the castle together after lunch on a surprisingly warm day for the time of year, and they were carrying Potter's book bag filled with—Snape didn't know what it was filled with, but it filled him with curiosity.

He managed to keep an eye on the trio as far as Gladrags Wizardwear, which the three entered, then Snape was suddenly distracted by Karkaroff.

"We have to talk!" Karkaroff hissed.

"Are you following me? You know, the more you keep tagging after and accosting me in odd places, the more people are going to get the idea that you have a problem." Both were speaking quietly.

"You can't ignore this. You can't pretend it isn't happening. Look at your own mark. I swear it must be{\el}"

"If you think I'm rolling up my sleeve in the center of Hogsmeade, you're a bigger idiot than I imagined. What makes you think I'm ignoring it or pretending anything? You decide for yourself, Igor, and I decide for me. If you're going to run, I can't help you. And I'm certainly not joining you."

"Severus, you can't{\el}"

"Well, look who's here!" Moody's booming voice called from across the street. He walked over to Snape and Karkaroff, who were now silent, and lowered his voice. "Class reunion for the graduates of Death Eater secondary school? Aren't you being a bit obvious? Might as well hang up a sign as stand together in the middle of Hogsmeade."

"Not meaning to be rude or anything," replied Snape, "but I was just leaving. I need to step inside for a breath of fresher air." He walked back in the direction of the Hogwarts gate. After a moment, looking back, he saw Karkaroff leave Moody as well, and Moody went into the Three Broomsticks.

Snape returned as quickly as he could to the spot outside Gladrags, but the three students were gone. He didn't see them again until after four o'clock as they returned to Hogwarts. The book bag was now clearly empty.

The next morning after breakfast Snape went out onto the lawn. Glancing up by chance, he happened to see two owls leave the owlery together. They were carrying something heavy between them and flying in the direction of Hogsmeade. \emph{I wonder what that's about.}

Work increased as the Easter break approached and the spring term neared its end. Then they were in the summer term, and the year was flying quickly by. \emph{Funny how the beginning of the year seems to move so slowly and the end so fast.} Snape was busy with his own preparations.

Images were now in place, most openly accessible, others carefully placed behind hidden doors, others buried down so deep that Snape himself had trouble pulling them out. He was getting quite proficient with the Patronus as well. He now controlled it sufficiently so that he didn't need to summon it independently. Dumbledore showed him how to conjure it nonverbally as a messenger, complete with message, and the Patronus would shoot out of the end of his wand on its way, misty and distorted, but still recognizable to Snape as a fox. Finally, he'd figured out and practiced his story lines. He was fairly sure he had an answer for every question the Dark Lord might ask.

The only remaining problem was at Hogwarts, and the frustration of it was maddening. How had Moody caused the Dark Mark to burn? Why had he stolen ingredients for Polyjuice potion and who had he transformed himself into? Why had he summoned Snape into his office that day and then pretended he hadn't? Why was he now so vindictive when all those years before he'd seemed almost{\el} friendly?

It was nearing the end of May, and Snape still had no answers to these questions. 


