% A Difference in the Family: The Snape Chronicles (Rannaro)
% Yes, That Is My Job

\chapter{Operation Umbridge}

% \emph{[Note: In Order of the Phoenix, the students attend their first classes the day after they arrive, but in fact September 1, 1995 was a Friday. I have elected to utilize the weekend.]}
% FIX

Snape went down to his dungeon office where he spent the two hours before breakfast trying to reorder his thoughts and calm his nerves. Breakfast, however, brought a whole new range of speculation as he checked out the familiar and the new faces at the Slytherin table.

\emph{Dear Draco. I didn't see your father all day yesterday. Do you{\el} does he know I was hauled before the Dark Lord? Or was he kept out of the loop because he sponsors me and was in danger of being tarred with the same brush? You're certainly reporting back to him, so I'll have to watch my step. Especially now that I'm on probation, and Lucius is probably wanting to distance himself from me.}

McGonagall came and sat with him. "I was worried when you weren't back for the feast."

"I'm glad someone was."

"That bad a day?"

"I've had better." There was silence, and Snape glanced up at McGonagall. "Sorry. Shouldn't be flip about it. It was probably the worst it's ever been. I really thought for a while that he was going to{\el}"

"I take it you're Professor Snape."

Snape looked around, but didn't have to look up. Dolores Umbridge was at eye level from where he sat, even though she was standing. "I'm Snape," he replied. "Do I have the honor of addressing Professor Umbridge?"

"You do. And what was it that you really thought he was going to do?"

"Survive the night," said Snape without batting an eye. "Which is what made his passing right before dawn such a terrible shock. As I was just telling Professor McGonagall, my great-uncle Tiberius practically raised me from a boy. Hard to think he's no longer with us."

"That was why you weren't with us last evening. I wondered. I'd had such glowing reports of your dedication to the school and to sound teaching that it was something of a surprise to find you truant."

Snape looked away to hide the sudden emotion he felt at the too recent death of Great-uncle Tiberius. "Ah yes, the children," he said, with just a trace of noble melancholy. "They are, after all, the reason we go on."

McGonagall was pursing her mouth as if she'd just bitten into a very sour pickle, but she always looked like that when she was trying not to laugh.

Umbridge glanced from one to the other, opened her mouth, thought better of it, and cleared her throat with a little cough. "Hem, I'd like you to drop by my office this morning, say around ten o'clock. There are some things we need to discuss." She nodded to both of them and waddled off with a self-important air.

The two professors watched her go in shocked disbelief. "Who does she think she is—headmistress?" said McGonagall. "Ordering you around like that."

"Maybe she thinks she's the Special Assistant to the Minister of Magic."

"You mean you're going? Dancing to her tune?"

"I'm not sure what her tune is."

"She made a speech last night. She interrupted Dumbledore in the middle of a sentence and insisted on making a speech. A very boring speech."

"Oh, do tell. She must be planning to show us the error of our ways."

"She believes in preserving the time-honored traditions of our people, but throwing out what has not proven to pass the test of time, and yet she disapproves of progress for progress' sake."

"In other words, she gets to decide what stays and what goes."

"As bald-faced a threat as I have ever seen in my life. You're not going, are you."

"I have to. I can't afford to have more than one Dark Lord angry with me at the same time."

At precisely ten o'clock, as requested, Snape knocked on the door of the Dark Arts office on the second floor. Dolores Umbridge's voice responded, "Come in."

The room was flooded with light, for it seemed Umbridge had opened every curtain and drape in the room. \emph{I wonder if she's aware that the potions on the lower shelves need to be kept out of direct sunlight or they lose their potency? She'll find out, but not from me.}

"Ah, Professor. Hem, I've been looking forward to meeting you. Pity you couldn't be there at the feast."

"If it had been anything less serious, I wouldn't have allowed it to interfere with my duties at Hogwarts. I'm thankful I have the weekend to order things properly in Slytherin house." Umbridge was sitting at her desk, but had not invited Snape to sit, so he stood in front of her like an errant student. \emph{The analogy with the Dark Lord was more à propos than I'd thought. Like the interview chamber, only light instead of dark.}

"I've had excellent reports of you. You're one of the teachers who sticks to time-honored ways of doing things. No newfangled innovations."

"It's something of the nature of potions. If you must stir seven times anti-clockwise, changing it to six will not help you."

"Exactly! Change doesn't help."

Snape forbore to comment. After a moment of silence, Umbridge began to tap on the desk with her quill. "I hope," she said at last, "that there are other teachers here who share your dedication to our hallowed traditions."

"All of them, insofar as I am aware."

"What about Professor McGonagall?"

"A lady of incredible fortitude. I wouldn't take her job for all the tea in China."

"Is Transfiguration so hard?"

"No, but Head of Gryffindor house is. They're not chosen for intelligence, logic, diplomacy, or any other disciplined trait, but for bravery. They therefore tend en masse to opt for confrontation in any situation. If there's a fight, Gryffindor drew wands first. She keeps them under control. I'm not sure how she manages it."

"What about Professor Sprout?"

"An excellent herbologist. I depend upon her for much of my yearly supplies. Plants are something else that you can't overly innovate with."

"And Flitwick? I understand he's part{\el} goblin?"

Snape was bristling now. Flitwick had been his Charms teacher and his cribbage partner for many years now, and he was beginning to really resent Dolores Umbridge. "I believe that is correct. Goblins have a spectacular ability with charms that's lost on most other races. If we didn't have Flitwick, we'd have to settle for a mediocre wizard."

"I hear that you, too, are a half-breed{\el}"

"Half-blood. I am sure you're aware of the difference."

"Still, any pollution of the pure bloodlines{\el}"

"Strengthens the species. You have studied biology, have you not? Too pure a bloodline exaggerates undesirable traits{\el}"

"I'm sure I don't know what you mean."

"I'm sure you don't."

"I was hoping{\el} Lucius Malfoy led me to believe{\el} that you would be more cooperative."

"Not if it means the watering down and destruction of the traditional curriculum at Hogwarts. Professors McGonagall, Flitwick, and Sprout are key to this school. They teach nothing that you would object to, and replacing them in the short term is beyond the scope of imagination. There are no replacements available."

The quill resumed its tapping. \emph{Idiot, you have an assignment with this woman. You're supposed to support her. Remember yesterday.}

"What about Dumbledore?"

"What about Dumbledore?"

"Is he as dedicated to the traditions of Hogwarts as his teachers?"

"I would have thought so. Until{\el}"

"Ah! Until when?"

"The Headmaster seems somewhat preoccupied lately."

"Professor Snape, did you know you had a file at the Ministry? A rather thick file at that."

"No, I didn't."

"It seems that many years ago you were named as a Death Eater during the roundups and trials, but Dumbledore spoke up for you, and you were exonerated. You owe him quite a lot, don't you?"

\emph{The woman really does look like a toad. A squat, ugly toad with a long sticky tongue{\el}} "I suppose I do."

"Your perspective on this would be valuable to me. Since you were, hem, one of You-Know-Who's workers, you would certainly be in a position to give authoritative information about his return. Do you believe this story of Dumbledore's that You-Know-Who has come back?"

"The headmaster is deeply concerned about the safety of our world."

"Your loyalty is commendable, but you didn't answer the question."

Snape looked Umbridge in the eyes. \emph{Funny how so many people assume eye contact equates with honesty.} "I know of no evidence that would substantiate the headmaster's claim."

"Then you don't believe he's come back."

"No. I don't."

Umbridge leaned back in the chair, a smug look on her face. "That's what I was hoping to hear. This story is a concoction of Dumbledore's, using that poor deluded boy as a pawn, in order to take power in the wizarding world. He wants to control the Ministry, you know."

"That's not something I would expect from him."

"Oh, you don't know Dumbledore. He's crafty. Did you know he's already collecting a group of fanatic followers around him, dedicated to convincing the general populace of the truth of his sham threat?"

"No{\el} that's scarcely credible. People are surely not that gullible." Snape had trouble repressing the ghost of a grin at the thought of Molly Weasley being described as fanatic. Moody, yes, but Molly{\el}

"If Dumbledore manages to raise a force, an army, around him, he could become a bigger threat to the order and safety of our world than You-Know-Who ever was. He needs to be discredited and exposed for the ambitious, power-hungry manipulator he is. That boy Potter needs to be discredited as well. He's in it for the glory, and he's easily duped."

"I certainly agree with you about Potter, but I'd prefer to stay out of the conflict. My classes take up quite enough of my time."

"I know you don't like me, Professor Snape. You have to understand, however, that this is a matter of overriding importance. I'll expect your support in my work, even if it interferes with your daily tasks."

"Yes, ma'am."

"You may go."

Snape closed the office door before he let out a long breath. A line from an old movie came to him. `That girl, she's one.—A witch? You just never learned to spell.' It suited Dolores Umbridge—only a witch because of a slight spelling error.

\emph{Step one accomplished. She thinks she can manipulate me into helping her. She also knows about the Order, so maybe I can use her or the Ministry to accomplish another of the Dark Lord's tasks without anyone really getting hurt.}

The rest of the day was spent interviewing the first years, meeting with the Quidditch team, briefing the prefects, of whom Malfoy was now one (a ploy to placate Lucius), and addressing the entire house in the hour before dinner. It was then, his school duties completed, that Snape had to consider the next, bigger problem.

\emph{He said to come once a week on Saturday evenings. I was there Tuesday, and I was there Friday, but the probability is that he still expects me there tonight. Better to be overly zealous than lax, especially now.}

Going in to dinner, Snape decided to try something. Catching Dumbledore's eye, he projected a thought—\emph{Can we talk before I leave, not in your office?} Dumbledore dipped his head once in a nod and continued his conversation with McGonagall.

After eating, Snape rose and left the Great Hall. Dumbledore waited a few minutes, then followed, meeting Snape at the top of the path down the hill.

"So you're going again tonight?"

"He expects it."

"Have you decided on something to sell him?"

"Yes. You."

Dumbledore's eyes widened. "Are you sure that is wise?"

"Umbridge wants power. I'm going to advise him to get it for her."

"Ah. So I must play along."

"Or not. As you choose. But expect trouble from the Ministry if he heeds me."

"It is good of you to warn me."

"It's more than you deserve."

\sbreak

Snape stood alone in the presence of the Dark Lord. The fact that neither Malfoy nor Macnair was there seemed auspicious.

"You have made contact with Umbridge."

"Yes, Lord. She had Malfoy's recommendation and expected to speak with me. That happened this morning."

"She wishes to protect the Ministry by denying our return."

"Yes, Lord. She asked my opinion directly, and I told her that Dumbledore was mistaken and that you had not come back. She expects my help."

"And you agreed."

"I disputed her assessment of the instructors, insulted her intelligence, and then allowed her to blackmail me with the threat of using my past against me. She knows I was your servant fourteen years ago. At that point I agreed."

"Good. Good. And so the Ministry will continue to shield us. Good."

"Lord, there is more."

"Tell us."

"Lord, Umbridge believes that Dumbledore is using word of your return to acquire power. She knows he has loyal supporters helping him gather information, and she refers to them as a private army. She believes his target is the Ministry of Magic itself, and she believes that his ultimate goal is to rule the wizarding world. She would welcome any move on the part of the Ministry that would give her increased authority at Hogwarts, and correspondingly decrease Dumbledore's authority. She will not rest content until Dumbledore is removed from Hogwarts and entirely discredited."

"She supports a direct attack on Dumbledore himself. She will work to oust him."

"Lord, she does, and she will."

"This is useful information indeed. We will instruct our people to advise the Ministry to curtail Dumbledore's authority. Since Umbridge will support this from the other side, we are certain of success. You have done well."

"Thank you, Lord."

Sunday was quiet. There were a few more interviews left over from the day before, but basically it was the calm before the storm. Snape made the most of it, playing cribbage with Flitwick in the staff room despite Umbridge's scowl, and catching up on reading in his own rooms. No summons came from Croydon, and given the Dark Lord's attitude the day before, Snape accepted by dinner time that none would come. He went to bed early and slept reasonably well for the first time in weeks.

The second class Monday morning was double potions with the Slytherin and Gryffindor fifth years—for Snape the most trying group in the entire school. Worse, it was the one group where he was certain that his students were reporting back to the Dark Lord about him, because it contained Draco Malfoy, Vincent Crabbe, and Gregory Goyle. Not to mention Harry Potter.

Snape opened the dungeon classroom door after the morning break and quieted the class down. Fifth year was when he made his OWL speech, and this morning was no different.

"Before we begin today's lesson, I think it appropriate to remind you that next June you will be sitting an important examination, during which you will prove how much you have learned about the composition and use of magical potions. Moronic though some of this class undoubtedly are, I expect you to scrape an `acceptable' in your OWL, or suffer my displeasure. After this year, of course, many of you will cease studying with me. I take only the very best into my NEWT Potions class, which means that some of us will certainly be saying good-bye."

\emph{Good-bye to Potter, Weasley, Longbottom, Crabbe, Goyle, probably Malfoy. Granger might even be sufferable in a class where she has to compete with the best, many of them seventh years. I can hardly wait.}

"But we have another year to go before that happy moment of farewell, so whether you are intending to attempt NEWT level or not, I advise all of you to concentrate your efforts upon maintaining the high pass level I have come to expect from my OWL students."

The class started on their first potion of the year, the Draught of Peace, an extremely complex brew that required great care. For the first time, he hadn't set the ingredients out for them, but rather required them to get everything from the store cupboard. This forced the students to study the potion in its entirety before starting, since leaving it in the middle to get another ingredient would ruin the potion. Snape did, however, keep an extra-watchful eye on Longbottom, who'd been known to come up with strange ingredients even under the most controlled of situations.

Everything went surprisingly smoothly for almost the entire class period, so much so that Snape was beginning to get worried. Surely the gods only allowed such happiness right before they inflicted severe punishment. Ten minutes before the class ended, he called out, "A light silver vapor should now be rising from your potion."

That was when Potter, blessedly predictable Potter, gave the Death Eater children a show. \emph{There are times when it hurts me that Lily's son inherited none of her talent, and others when I am deeply grateful.} Walking over to where dark gray steam issued from Potter's cauldron, Snape said, "Potter, what is this supposed to be?"

"The Draught of Peace."

"Tell me, Potter, can you read?"

"Yes, I can." The boy faced him defiantly, ready for a fight.

"Read the third line of the instructions for me, Potter."

Potter had forgotten to add hellebore to his potion, and the deflated look on his face was more than enough to satisfy Snape. "This mess is utterly worthless," Snape said calmly. \emph{"Evanesco!"} And the contents of the cauldron disappeared, to the great delight of the Slytherins.

Class ended with no other hitch except that Goyle's potion set his robes on fire, a small emergency that made Snape think of his fire extinguishers in the lab at Croydon. As he finished assigning homework and collecting the flasks that the other students were presenting for a grade on their potions, he noticed the Three Musketeers in conference in the back of the room.

\emph{Probably upset that Potter got a zero on the class work, when everyone else received at least a little credit, even Goyle.} Then Snape was hit by another thought. \emph{Crawling with Weasleys. Grimmauld Place was crawling with Weasleys that day. Ron was undoubtedly there, too. Maybe Potter as well. Was that why so many of them arrived late at the same time? Escorting Potter? Do the three of them know I was making a report that evening to the Order of the Phoenix?}

It was a disturbing thought. Malfoy, et al. knew he was a Death Eater. Now Potter, et al. likely knew he was in the Order. Dumbledore and the Dark Lord knew both. \emph{But some day Malfoy and Potter may call on me to take sides, and that could cause trouble. Depending on the circumstances, it isn't always safe to show the world where one's true loyalties lie.}

The rest of the week passed smoothly. Snape was not surprised to hear from his Slytherin students that Professor Umbridge would not allow them to use magic in their Defense against the Dark Arts class. It struck him as entirely consistent with her attitude that Dumbledore might be trying to form a private army. He was also not surprised to learn that Umbridge had given Potter four nights of detention in his very first class with her. \emph{She's definitely not the one to be cheeky to. It would probably never occur to her to subtract points from a house. She'd go straight for the offender every time.}

Friday evening brought a little good news. The Gryffindor team, under its new captain Johnson, held tryouts for Keeper to replace Wood. Those competing for the spot were generally a sorry lot, the mediocre players having the best attitudes, and the good players suffering from an excess of whining or hubris. \emph{Slytherin may have a chance to win this year.}

Saturday was colored by anticipation of a meeting with the Dark Lord, and what had once been a relatively relaxed day was now tense and unpleasant. It was not helped by McGonagall showing him an article in \emph{The Daily Prophet.}

"Sturgis Podmore's been sent to Azkaban," she summarized as he read the short item. "Six months."

\emph{This was the incident that angered the Dark Lord so much. He told me of Podmore's arrest. What was Podmore doing outside a top-security door? Did the door have something to do with the prophecy? This is all so mysterious. And why did the Dark Lord say he knew I was interested in mysteries?}

Snape looked at McGonagall. "I thought he worked for the Ministry."

"He did. Though what he would be doing there at one in the morning trying to break down a door escapes me."

They stopped talking as Umbridge passed by. Then, as he turned the pages to keep Umbridge from seeing what they'd been looking at, another article caught Snape's eye. "Whoa! It says here that Sirius Black is hiding in London!"

"Let me see that." McGonagall snatched the paper from Snape and skimmed over the article herself. "Do you think someone saw him? It says a tip-off from a reliable source." She squinted suspiciously at Snape. "This wouldn't have something to do with you, would it?"

"Whatever do you mean?"

"Well you've got to give him something, don't you. Names, dates. Maybe one of your colleagues on the `other side' is the reliable source."

Snape was speechless. McGonagall regarded him pityingly. "I thought I told you."

"If you did, it didn't register completely."

"But you were telling me last week how difficult it'd been at your meeting on the first."

"I still don't think of it extending into Hogwarts."

"Get used to it. It's going to be extending into a lot of places we used to think immune."

That evening after dinner, Snape apparated to Croydon. He was called into the interview room to face the Dark Lord.

"Your idea of the last session was successful, Potions Master," said the Dark Lord. "The Ministry reached a decision yesterday evening. The Umbridge woman will be given power to interfere at Hogwarts. Have you any more to report?"

"No, Lord. Though I expect to have more after the news becomes public."

"That will be on Monday. \emph{The Daily Prophet} will announce it."

Snape spent the rest of the evening in the laboratory. He had more than a week's work to catch up on, and was glad to have some quiet time.

Malfoy looked in around nine o'clock. He seemed quite satisfied with events. "That was a good idea of yours. The Dark Lord is pleased with both of us. I owe you one."

"Consider it payback for last June, when you spoke up for me."

Malfoy smiled. "I like the way your mind works," he said.

Sunday was peaceful. Snape allowed himself the luxury of sleeping an hour later than usual, then lingered over breakfast. The calm before the storm. Things might not be so relaxed after Monday. Most of the rest of the day was spent correcting the previous week's homework. This was not normally something that Snape enjoyed, but now it was so far from the tensions of Croydon and Umbridge that he actually took pleasure in its mundane normalcy.

Monday hit with the force of a nuclear explosion.

"Look at this!" shrieked McGonagall, thrusting \emph{The Daily Prophet} under Snape's nose. "Look what those dunderheads at the Ministry have done! `Hogwarts High Inquisitor' my posterior! If I ever get my hands on the administrative nincompoop who orchestrated this, he'll be singing soprano for the rest of his life."

Snape nearly choked on his sausages. "You never know," he coughed into a table napkin, "it might have been a woman. After all, Umbridge herself is a woman."

"You don't have to be insulting."

"It's the archetype of ruthless ambition. Lady Macbeth. You can't expect us poor males to be able to compete with anyone as single-mindedly motivated as this, can you? For truly savage focus you have to have a woman."

McGonagall was mollified. "And just you remember it, too, laddie. A real woman will stomp you senseless into the ground as soon as look at you."

\emph{Dumbledore is missing something here. Let's chuck the Blacks, Lupins, Moodys, and Shacklebolts. Put together an army of Mollys, Minervas, Nymphadoras—that's where we win the wizard war. Who has the Dark Lord got? Just Bella, and she's in Azkaban.} There was Alecto, too, but Snape didn't include her. He figured if your IQ was smaller than your age, you didn't count.

Umbridge summoned, and Snape danced attendance.

"I now have the power to observe and evaluate all of you. It's Monday morning, Potions Master. Shall I evaluate you first?"

"Only if you want to give comfort to the friends of Dumbledore. It's well known that the two of us don't get along. If you were to delay my evaluation, it might make a point. Or not. It's entirely up to you. Shall I expect you later this morning?"

Umbridge paused and looked speculatively at Snape. "I wonder what's really going through your mind," she said.

"Nobody knows. Sometimes I don't know myself. Shall I expect you this morning? As it is, I'm about to be late for my first class, and the students will wonder why."

"No. I'll check the others first. Lucius Malfoy has spoken highly of you again, and I wouldn't want to upset Lucius by appearing not to take his advice seriously."

\emph{And you are a tactical idiot for telling me that piece of information.} "I am grateful for Mr.~Malfoy's good opinion. And when you do deem it the proper moment to inspect my classes, I shall receive you with all the respect commensurate with your position."

"I knew I could count on you."

Potions classes went extraordinarily well that day. Snape was able to put the fear of God into his students by grading their homework as if it were their OWL examinations. Most of them got D for Dreadful, which was not a passing grade. It inspired them for the class to come. Not even Potter—for heaven's sake, not even Longbottom—botched the class work. \emph{Why isn't my life always like this?}

Not everyone was as pleased as Snape. At supper that evening, Trelawney looked positively exhausted. Umbridge had been to evaluate her, and the encounter had evidently not been a pleasant one for Trelawney. Snape could hardly wait until Umbridge got to McGonagall.

The truly strange part of the day was that Dumbledore did not come down to dinner. In fact, it was to be some time before Snape saw Dumbledore again.

On Wednesday during the lunch break, McGonagall brushed past Snape in the Great Hall. "London this evening," she hissed. "Be ready."

Snape didn't react at all, which was wise since he noticed a moment later that Umbridge was watching him. The rest of the day he spent acting perfectly normal, and after supper retired to his rooms to work, something he was doing most evenings in any case. It was there that the misty little cat found him around nine-thirty and whispered, `now' into his brain.

\emph{Life would be so much easier if I had an invisibility cloak or were an animagus.} Snape stood just out of sight where the dungeon corridor flowed into the entrance hall, trying to determine if anyone anywhere was watching. Deciding it was safe, he darted out the main doors and scurried down the hill to the Hogsmeade gate, where McGonagall was waiting.

"What about Dumbledore?"

"Lying low for the time being. Something strategic, I understand. Trying to give that woman enough rope, just to see what she'll do with it."

"Maybe he doesn't want to give the Ministry an excuse to tighten the rules any further."

"Maybe." At a word from McGonagall the gate was unlocked and they slipped through. A quick agreement on location, and McGonagall said, "Now." An instant later they were in London, around the corner from Grimmauld Place.

Black opened the door and admitted them wordlessly into the house. The portrait of his mother seemed to be asleep, and Snape joined the general consensus to keep her that way. Silently they made their way to the parlor, where the others already waited. Greetings were quickly exchanged, and they sat down.

"All here now?" grunted Moody, who seemed to be in charge. "What's going on at Hogwarts?"

"The Ministry is trying to take over," replied McGonagall, and she explained Educational Decree Twenty-three and its immediate impact on the school. "It's blatant intimidation. Poor Trelawney was beside herself. At the moment it's just authority to inspect, but they could change it to authority to replace, and pack the school with their own people. Albus is staying out of it so as not to give them more reason to step further in. If he plays along, we may be able to defuse the situation. Especially since she told Severus they suspect him of planning an attack on the Ministry."

Snape wished McGonagall hadn't said that, as all eyes turned to him.

Black had an evil, speculative look on his face. "That's hardly the information that'd come up in casual conversation," he said. "Why would Umbridge confide in you? Or are you playing a three-way game now?"

There was a subtle shift in mood, and Snape was beginning to feel as if he were on trial. "She checked Ministry records on me. She knows I was a Death Eater. She thinks she can blackmail me into helping her. She has some information about the Order, which she regards as Dumbledore's private army."

"Have you been increasing the amount of information she has?"

"That's enough, Sirius," interjected Moody. "It'll be helpful to get inside news."

"Bet Umbridge likes inside news, too. And Voldemort. How long before you figure out how to sell everybody to everybody?"

"Enough!" Moody and McGonagall shouted at the same time, while the other members of the Order looked uncomfortable.

Snape, who'd winced at the Dark Lord's name, was now angry. "I noted that \emph{The Daily Prophet} has placed you in London," he said to the room in general. "That puts all of us in danger."

"We're protected by a Fidelius Charm."

"No, you're protected by a Fidelius Charm. We have to go out onto the street. How many people visited here socially while your parents were alive, and may pass by, knowing you're in London, and wonder why the house can't be seen anymore? And may want to watch and see who comes wandering through the square and then just disappears? While you sit inside, nice and safe."

Black was on his feet, lunging toward Snape as Lupin, Weasley, and Shacklebolt tried to restrain him. "It's hardly worth their effort, now is it? Since you've given them all our names anyway!" he yelled.

All the members of the Order were now on their feet except for Snape, who remained seated just out of Black's reach. It took Moody, McGonagall, and Molly Weasley several minutes to restore calm, and even then it was abundantly obvious that an explosion was brewing just under the surface.

"Is what he said true?" McGonagall asked Snape after the room had quieted.

"Of course it is," snarled Black. "Look at him. He'd sell{\el}"

"I didn't ask you!" McGonagall snapped. "I asked Severus."

"I gave the Dark Lord the names of all those who'd been members of the Order before, when Pettigrew was still part of it. He knows all those names anyway, and would already have given them to the Dark Lord. I told the others this at an earlier meeting."

"Well, that's logical at least. Now, the two of you have to stop bickering. It's bad enough we have to fight You-Know-Who without fighting each other as well."

Moody coughed, and the others turned to him, apparently thankful for the diversion. Snape and Black studiously avoided looking at each other.

"We also need to evaluate the incident involving Sturgis and the Department of Mysteries," Moody began.

Snape was alert at once. \emph{Department of Mysteries? Is this about the prophecy? Is this why the Dark Lord mentioned the word?}

"My understanding is that Sturgis was under an Imperius Curse," Moody continued. "That's why he was trying to break in. I also know that he was on guard there, protecting something because of information Dumbledore received." He turned to Snape. "Do you know anything about it?"

"Three weeks ago, I'd have said no. I didn't even know there was a Department of Mysteries until this moment. But if it contains things like prophecies, then Podmore was there because the Dark Lord is interested in a prophecy. One that talks about Potter."

"How do you know?"

"He mentioned it in a meeting." Snape had no desire to tell the Order the whole story of the prophecy or why the Dark Lord would be questioning him about it. "He was also furious when Podmore failed to get it and was arrested."

"And how did you learn that?"

"I was one of the people he suspected of passing the information to Dumbledore{\el}"

"Now we get to hear how dangerous your work is compared to everyone else." Black let his voice drip with sarcasm.

The memory of that day was too powerful, and Snape didn't trust himself to reply. Instead he closed his mouth and sat back in his chair, his arms folded across his chest. In the sudden silence, Moody snapped his fingers, and Snape glanced up automatically into Moody's eyes. Into the enchanted blue eye{\el}

"Who's guarding the place now?" asked Moody as he looked away.

"Several of us," Arthur Weasley said. "We have shifts and take turns. There's me, and{\el}"

"Better not give too many names," said Black. "The walls have ears."

Discussion continued for nearly twenty minutes more, but Snape took no part in it. Then Black went into the kitchen to see about refreshments, the others got up and began to mingle, and Moody crossed the room to sit by Snape.

"Was that it? Was that the day he was furious?"

Snape looked at his hands. "It isn't important," he said.

"I say it is important, boyo. Answer the question. Was that the day?"

"Yes. But I'd prefer not talking about it."

"Up to you, but if that's what you go through when he's ticked off, you've got a harder job than I thought."

"The Dark Lord is renowned for his temper. I wasn't the only one. I'm not supposed to mention it, though. Makes other people feel inadequate."

"Again, it's up to you. You ever want me to speak up for you, let me know."

Snape nodded, then rose and approached McGonagall. "Can we leave now?" he asked.

"We ought to socialize a little."

"Right. Me—socialize here. I'd go back alone, but you're the one who opens the gate. Can't we point out that we have classes tomorrow morning?"

"All right. I'll tell him we're leaving."

A few minutes later, Snape and McGonagall left 12 Grimmauld Place and apparated back to Hogwarts.

\sbreak

Things settled into a welcome routine. Weekdays were devoted to classes, grading papers, and other school duties. Snape gave up reading on the weekday evenings in order to finish all his duties during the week and save one day for complete relaxation. Saturday mornings were spent clearing up the last of the week's work and a thorough inspection of the classroom and stores. Saturday afternoons Snape tried to set aside to review the week and prepare for his trip to Croydon. The interview after the passing of Educational Decree Twenty-three was typical.

"Things are going according to plan at Hogwarts."

"Yes, Lord. Classes are being disrupted and teachers intimidated. Umbridge is acting as if she was already headmistress."

"And Dumbledore?"

"Has retreated. He hasn't appeared at meals or, so far as I can tell, spoken with any of the teachers."

"He is weaker than we realized. What further news do you anticipate?"

"More of the same for the next few weeks, unless Umbridge is suddenly given more authority."

"We shall work on that goal from this end. You need only report how successful our efforts have been on your side."

"Yes, Lord."

Both information gathering and potion making having faded into the background, Snape found himself assigned to teach classes in defensive techniques. Malfoy met with him on that same Saturday to work out a schedule. Basically Snape had two one-hour classes back to back each weekend. Malfoy had been thick enough to schedule the first one for that very evening.

"You know it's been over fourteen years since I taught this."

"Isn't it like riding a broomstick? You never forget?"

That class was held in a large basement room. The first five students were flippant and disrespectful, especially when he insisted they learn to fall before he would teach them anything else. They made it obvious that a potions brewer was not their idea of a qualified defense instructor.

"All right," said Snape, taking off his jacket and laying his wand aside. "You and you. Yes, you with the big mouth. You're wizards with wands and I'm a muggle with no magic. Go for me. Together."

He used defensive moves his mother had taught him years before he was old enough to go to Hogwarts. Even though he was rusty, Snape ducked, dodged, dropped, and rolled, and not only evaded every spell they threw at him, but was also able to knock one off his feet with a well-placed kick, and pin the other's arm behind his back to extract his wand.

Snape had no further problem with any of his defense classes.

Sundays were Snape's days of rest. One day a week he lay back and forgot potions, homework, or fighting. On Sundays he read, or played cribbage, or let McGonagall try to teach him chess. Life was, in fact, beginning to resolve itself into something pleasant. Pleasure is like pride, however. It never goes unpunished.

The first Saturday in October was a Hogsmeade excursion, the first of the year. Snape was assigned supervisory duties, and was almost looking forward to it. Usually the students were reasonably well behaved in Hogsmeade, knowing that any infraction of the rules would result in their losing the privilege. In addition, Snape had prepared a small gift—a selection of rare mulling spices—for Madam Rosmerta, to thank her for taking care of him the night of September first.

It was after presenting the spices, and then staying to savor a tankard of ale, that Snape noticed the unusual number of students turning down the lane that led to the Hog's Head Inn. \emph{Students don't frequent the Hog's Head. It isn't out of bounds, but it isn't savory either. Gryffindors, Ravenclaws, and Hufflepuffs, all going in the same direction. What could possibly lure Macmillan, Finch-Fletchley, and Goldstein into the Hog's Head?}

Snape didn't hurry, not wanting to startle any of the students, but after the rush seemed to have thinned out, he left the Three Broomsticks and approached the windows of the Hog's Head. The students were there, an uncommonly large number of them gathered in one place. At the center of attention were Potter, Granger, and Weasley.

Instinct told him he didn't want to know, and Snape beat a sudden and hasty retreat back towards the Three Broomsticks. On the way, by unhappy accident, he ran into Dolores Umbridge.

"Any problems down that way?" she asked, but he told her there were none, then invited her into the Three Broomsticks for a butterbeer.

Spending the rest of Saturday in the company of Umbridge ruined Hogsmeade for Snape. To crown his frustration, she didn't even have any good information to pass on to the Dark Lord. Just questions.

`Is McGonagall always so confrontational?'

`Has Flitwick ever talked about his goblin ancestors or tried to contact goblin relatives?'

`Why would Dumbledore hire as obvious a fraud as Trelawney?'

`Does Sinistra always keep her students up after midnight?'

`Why hasn't Grubbly-Plank been given a permanent position?'

`Has Sprout ever poisoned or caused permanent injury to a student?'

`When did Binns die?'

and

`Where is Hagrid?'

To which Snape replied:

`Yes,'

`No.'

`You'll have to ask him.'

`Usually.'

`We don't have one available.'

`Not that I know of.'

`I never asked. Before my time, certainly.'

and

`I haven't got a clue.'

The relentless woman did not give up until it was time for the students to return to the Castle. Snape, facing the window, noticed that the students from the Hog's Head were drifting out of the lane in carefully spaced groups of three and four. He kept Umbridge in conversation, determined that he would find out what was going on before she did.

Walking Umbridge back to the Hogwarts gate, Snape wished her a pleasant evening and turned back into Hogsmeade.

"Where are you going?"

"I had duty today. That means I have a free evening."

"Where are you going?"

"I haven't decided yet. I may stay at the Three Broomsticks. Or go to London to see a play. "The Hothouse" just opened at the Comedy Theatre, or I could catch "King Lear" in Leeds. It's supposed to be an interesting production."

"I didn't know you were interested in muggle theatrics."

"Now you know. Have a nice evening."

There was nothing Umbridge could do, and Snape whistled a little as he headed back to the Three Broomsticks. The only disappointing thing was that he wouldn't be seeing a play. He was going to Croydon.

The second self-defense class was tense. Snape didn't dare ask questions, but he kept his ears wide open. Something was happening in the next few days, and it would be inside a building. The two Death Eaters involved had to get in and out without raising an alarm, even if it meant failing in their mission. Since nothing but total success ever pleased the Dark Lord, even obeying orders could lead to a certain amount of punishment. Snape sympathized inwardly, though he made no outward sign that he realized what they were hinting at.

On arrival back at Hogwarts, Snape sent a patronus to McGonagall to admit him. She was patrolling the entrance hall when he walked in, and he quietly passed on the information. Then she asked about the play, and puzzled, he quickly invented something about the London comedy.

They wished each other good night. As he turned toward the dungeon corridor, Snape caught movement out of the corner of his eye. Umbridge had been watching them from a staircase.

On Sunday morning, after a leisurely breakfast, Snape and Flitwick started a game of cribbage in the Great Hall. They'd barely finished three hands when Filch came up to them—Snape later felt it had been timed to interrupt their game—with a message that was more of a command than a request.

"The Inquisitor wants to see you. She said now."

Flitwick's eyebrows lifted dramatically, and down the table McGonagall gave Snape a quizzical look.

"Tell her I'll be right up," said Snape.

"Tell her yourself. You'll make it up there as fast as me if you know what's what. She's in a foul mood."

Snape excused himself to Flitwick and went up to the second floor. Once again, Umbridge did not invite him to sit. Instead she kept him standing there for nearly three minutes while she finished writing something on a long scroll of parchment. It gave Snape a chance to look around the room, with its unusual dried flower arrangements and lacy frills.

Finally Umbridge seemed to notice he was there. She placed the quill feather to her lips and regarded him for a moment. "Interesting," she said, "how you can get entirely the wrong impression of someone at first. I would never have taken you for a shill."

"I beg your pardon."

"Yesterday. A shill for the students. You were coming up the lane from the Hog's Head and decoyed me into the Three Broomsticks. Do they buy you, or are you doing it for Dumbledore?"

"Oddly, it was for the pleasure of your company. Which I am beginning to regret."

"You're not good enough at flattery to be able to butter me up. Luckily I have other sources of information, so your little ruse didn't work. Where did you go yesterday evening?"

"Not that it's any of your business, but to London. To a play."

"Which one?"

"The Comedy Theatre. They're playing `The Hothouse.'"

"How did you get in? It was sold out."

Warning bells screamed trap, but Snape was not sure which way the pit lay. Locking himself down, he looked into Umbridge's round eyes, hoping she had no occlumency skill. "It would be a poor wizard who couldn't get admitted to a sold-out performance," he said, and saw the spark of triumph behind her eyes. "But it wasn't necessary. The show wasn't sold out."

"How did you like it?" Umbridge sounded petulant.

"It's always delightful when the author is one of the actors. You never miss the nuances."

"Favorite bit?"

"All of Act III."

Unable to trip him up, Umbridge changed her tactics. "I've been very nice to you so far," she said, "but now it's time for me to inspect your classes. I'll be at your morning Potions lesson tomorrow."

"I look forward to it."

"Just out of curiosity, Professor, about how many of your students know about your—shall we say `colorful'—past? More to the point, how many of their parents know? I for one might not be comfortable if a child of mine were under the tutelage of a former follower of You-Know-Who."

"I would say quite a few. Some of their parents had equally colorful experiences."

"But if there were to be a general protest at your continued employment here?"

\emph{A year ago you'd have had me. I'd dance to your tune or face Azkaban. You may still have that power, but at least now I have other places to go.} "It would be up to the Board of Governors."

"Maybe. Maybe not. Fascinating about Educational Decrees, how much they can change things in the course of a morning. There's a new one coming out tomorrow."

\emph{Time to give in.} "I understand, Ma'am. I hope you don't think I was being rude."

"Not at all, Professor," Umbridge replied, smiling with sickening sweetness. "I'm sure we'll work very well together. Now, what were the students doing in the Hog's Head?"

"I presumed they were planning something against Slytherin, since my house was the only one not represented. I didn't want them to be interrupted as they would then simply move somewhere else where I wouldn't be able to find out anything. As it is, I may be able to pick up some information from the staff or the other patrons. It would have to be done carefully."

"There's no need. They weren't plotting against Slytherin. It was against me. And henceforth you will allow me to make such decisions, instead of steering me away from the malefactors. Do you understand?"

"Yes, Ma'am," said Snape, and he was dismissed.

Most of the students had left the Great Hall for various intellectual and nonintellectual occupations appropriate to a Sunday morning, but most of the teachers were still there. At first Snape didn't think much of it until he returned to his seat next to Flitwick. Then he noticed that they seemed to be looking, not exactly at him, but in his direction.

McGonagall slipped over, her eyes on the doors. "What happened? Quick, before Filch comes in."

"Urge your students to be circumspect. She thinks they're plotting against her, and she already has a new Decree approved that'll be made public tomorrow. Do you talk regularly to Dumbledore?"

McGonagall nodded.

"She thinks he's the center and source of all plotting. No matter what happens, she'll try to pin it on him."

"That was Albus's own take on the situation."

"She's blackmailing me into helping her. It'll be easier if you all affect not to like me."

"In other words, behave normally."

"Cute."

"Anything else?"

"Walk softly. She'd dearly love to tighten the screws."

McGonagall left him and went to sit with Sprout and Vector. Flitwick moved down the table to speak to Sinistra and Pince. Snape was by himself sipping a last cup of tea when Filch looked into the Hall, then backed out again.

Snape rose to leave the Hall for his own rooms as Sprout joined Trelawney and Grubbly-Plank, Vector edged nearer to Futhark, Sinistra struck up a conversation with Hooch, and Pince went to find Madam Pomfrey.

\emph{A good thing no one was really watching this time, but if the network goes this smoothly from classroom to classroom, Umbridge has a fight on her hands.}

The next morning revealed the contents of Educational Decree Twenty-four. Every student organization, society, team, group, or club was summarily disbanded, and could only be reconstituted with the permission of the High Inquisitor. The Great Hall was frantic with little groups of students trying to find out if knitting circles and chess tournaments were now illegal.

Snape saw the word `team' and called the Slytherin Quidditch team together. "Draw up a petition. Make it very respectful, subservient even, but get the team approved. Tell the captains of the other houses." He then gathered his prefects. "Any club or society we have, petition for reconstitution. If you have a Transfiguration study group, petition for it to be approved. Anything where you meet regularly in a group of more than two, call it a club or society and petition. We don't want to be on the wrong side of this Decree."

After breakfast, in the staff room, Snape confessed to quite a different motivation. "I want to hit her with every little gathering of students I can think of. Heck, if I could invent new ones now, I would. I want that woman buried in paperwork up to her{\el}"

McGonagall and Grubbly-Plank, who like Snape didn't have classes that hour, were chuckling at the thought when there was a knock at the door. McGonagall opened it, and Snape could hear Potter talking outside. \emph{What is he doing here now? Doesn't the boy have a class?}

Grubbly-Plank was next to the door, and suddenly got up and joined McGonagall. A moment's more talking, and Grubbly-Plank reentered the room holding a beautiful snowy owl. She set her newspaper and pipe to one side in order to tend to the bird.

McGonagall came back in as well, having sent Potter on his way. "What do you think, Wilhelmina?" she asked.

"Looks like it was attacked. Takes a real villain to go after a beauty like this one. She's strong though, to make it here with her wing injured like that."

Snape edged closer. "You think the owl was attacked on purpose? To keep a message from getting through?"

"Maybe," said McGonagall. "Or maybe just to have the chance to read a message before it reached its destination. That's how traps are set."

"Who would Potter be exchanging messages with anyway? He hates his muggle family."

McGonagall stared at Snape over her glasses. "He has a godfather in London. Or had you forgotten?"

Snape wanted to throw a conniption fit. He could not, however, say anything because of the presence of Grubbly-Plank. He could think it, though. \emph{Potter's endangering every one of us by maintaining a direct, uncoded link with the headquarters of the Order in London. How many people don't know that the great snowy owl is Potter's bird? Azkaban must not be as terrible as they say. It didn't change Black at all. He's still reckless with other people's lives.}

The first bell sounded, and the morning break began. Grubbly-Plank took the owl and headed out toward Hagrid's hut for her morning lesson. Other teachers came into the staff room, and prevented Snape from discussing the matter with McGonagall. Then another thought hit him. \emph{How secure are the patronuses? Could Umbridge see me send the patronus to McGonagall to let me in every Saturday? How soon before she's wise to that?}

The bell rang signaling the end of the break, and Snape gathered his things, took his leave of the others, and made his way to the dungeon classroom. Umbridge was waiting for him with ill-concealed impatience, and he let her in, locking the door behind them.

"I expected you to be here to receive me," she snapped.

"Class hasn't started yet," he replied. "You will be able to observe from the corner without disrupting the dynamics of the class too much."

She sat where he pointed, and then Snape went to open the classroom door. What met him was totally unexpected. A line of Gryffindor students faced a line of Slytherin students, and in the middle were Malfoy and{\el} Longbottom? Neville Longbottom was struggling to get at Malfoy, and was being restrained by Potter and Weasley. \emph{I do not know what it is, and I do not care what it is, NOW is not the time!}

"Fighting, Potter, Weasley, Longbottom? Ten points from Gryffindor. Release Longbottom, Potter, or it will be detention. Inside, all of you."

The students filed into the room and to their seats. When most of them were settled, Snape announced, "You will notice that we have a guest with us today." All eyes turned to the corner where Umbridge sat, but after the short mention, Snape paid no further attention to her.

"We are continuing with our Strengthening Solutions today—you will find your mixtures as you left them last lesson. If correctly made, they should have matured well over the weekend. Instructions on the board." Snape waved his wand, and the instructions appeared. "Carry on."

Snape spend the next half hour moving around the room, checking as he normally did on the progress of the various students' potions. After half an hour, Umbridge got to her feet with an audible "Ha," and came over to him.

"Well, the class seems fairly advanced for their level, though I would question whether it is advisable to teach them a potion like the Strengthening Solution. I think the Ministry would prefer it if that was removed from the syllabus."

Snape forbore to comment, merely straightening from where he bent over a cauldron in order to look at her.

"Now{\el} how long have you been teaching at Hogwarts?"

\emph{I am sure that information is in my file, so your motive in asking would be{\el} ? To see if I remember? Or if I'm lying?} "Fourteen years." \emph{Two months and nine days.}

"You applied for the Defense Against the Dark Arts post, I believe?"

\emph{Why are you asking this?} "Yes."

"But you were unsuccessful?"

"Obviously."

"And you have applied regularly for the post since you joined the school, I believe?"

"Yes."

"Do you have any idea why Dumbledore has consistently refused to appoint you?"

\emph{As a matter of fact, I do. But I am not telling you.} "I suggest you ask him."

"Oh, I shall."

"I suppose this is relevant?"

"Oh yes. Yes, the Ministry wants a thorough understanding of teachers'—er—backgrounds."

\emph{You misspelled witch! Let's just scrawl `Death Eater' all over the walls.}

Umbridge ceased her questioning of Snape and began talking to one or two students about the class. Snape felt a prickle in the back of his head, and turned to find Potter staring at him. For just an instant, he was gazing into the green eyes, Lily's eyes, and he felt the same way he'd felt the first time he ever looked at Potter. \emph{I have to be careful. Luckily, Potter's no legilimens, but it wouldn't be safe to be surprised by Lily's eyes if one were in the same room.}

Then Potter looked away, and Snape noticed he'd botched his assignment. As usual.

"No marks again, then, Potter. You will write me an essay on the correct composition of this potion, indicating how and why you went wrong, to be handed in next lesson, do you understand?"

"Yes," Potter answered sullenly, and Snape could almost feel the anger. A glance over at Umbridge, however, showed that the exchange had pleased her.

The students cleaned up, the bell rang for lunch, and the room quickly emptied. Umbridge remained, and came nearer after they were alone.

"Fourteen years. I have to check your file again, but doesn't that mean you started teaching here before{\el}"

Snape turned and regarded her calmly. "I suppose it does," he replied.

"I didn't know You-Know-Who let his followers take other jobs."

"I'm sure I don't know what you mean."

"I'm sure you do. Dumbledore can be too trusting at times, no?" Without waiting for an answer, Umbridge left the room.

\emph{If that woman ever learns how to put two and two together to make four, I could be in trouble. As it is, she thinks she has an ironclad hold on me. But if we ever reach the day when I can tell her how I really feel{\el}}

Things at Hogwarts were quiet for the rest of the month. Part of this was because Umbridge had finished her interviews, and no longer interfered in classes. Part of it was because the weather was depressingly horrible, for it was a month of incessant wind and rain. And part of it was that for some reason many of the most active, irrepressible students seemed to be rather calmer than usual, as if they had found some outlet for their energy.

Snape and McGonagall were back to betting on Quidditch games, and the student body as a whole seemed more intense about Quidditch than usual.

"It's probably because there was no Quidditch last year," said McGonagall at supper near the end of October.

"That, and it's a relief to know Umbridge can't cancel it," added Sprout. "Is it true she tried to keep the Gryffindor team from being approved?"

"It is," said McGonagall. "I had to go to Dumbledore about it, and he overruled her. She was not happy about that, let me tell you."

Sprout nodded happily. "It's good to know Dumbledore still has a hand in things. He's been so quiet and retiring lately."

Snape was sitting a few seats away, listening to the conversation. Now he joined in. "How do we know Minerva doesn't have him locked up somewhere and is just pretending that instructions and intervention come from him? Maybe she's ruling Hogwarts now."

"You!" cried McGonagall. "I've been meaning to talk to you. What's this about allowing your students to hex mine and not stepping in to stop it?"

"Whatever are you talking about, my dear lady?"

"You know perfectly well that Bletchley hexed Johnson on Tuesday. There were witnesses."

"All of whom were Gryffindors conspiring to discredit the Slytherin Keeper. Besides, they've been hexing us, too, only they don't tell you about that. Bet they didn't say one word about the hex that Bletchley was retaliating for."

"You mean you knew all about this and didn't try to stop them?"

"About as much as you tried to stop a couple of Gryffindors from hexing me back when both of us were a lot younger than we are today. Consider it payback."

"You did look cute being carried up from Herbology with a Venus flytrap hanging onto your ear, and giggling like a lunatic. Even today I can look back and say honestly that it was the only time I ever saw you laugh."

Flitwick chuckled at the memory, too and Sprout, even though she'd heard the stories before, began begging for details. McGonagall settled herself to regale a growing audience with the legend of the famous Gryffindor-Slytherin hex wars of the '70s. Snape, knowing himself to be one of the stars of her story, stood and left the group to its fun.

"You be sure to get the story about Black's bats right," was all he said as he left the Hall.

Things were almost as calm in Croydon. The Dark Lord was displeased, but not with Snape. Whatever the two Death Eaters had tried to get, they'd not been successful. In the wake of two failures, the Dark Lord put in a series of requisitions for potions. Snape was interested in the combination.

There were Wit-Sharpening Potion, Unctuous Unction, various Sleeping Draughts, and Forgetfulness Potion, all of them very useful in situations where you did not want any fighting, or any traces left of your presence. Two items especially caught Snape's attention: Polyjuice Potion and Veritaserum.

It seems the Dark Lord was impressed by Barty Crouch's ability to fool the entire school, including Dumbledore, into believing he was Moody for over nine months. \emph{If one of our people takes the place of someone in the Ministry, it could wreak havoc.}

That was when Snape decided to use part of his time to tinker with the two most potentially dangerous potions. He asked for an interview with the Dark Lord.

"You wish extra funds to purchase ingredients for Veritaserum and Polyjuice Potion. You will explain why."

"It occurred to me that the Polyjuice Potion would be more useful to your operatives if its effects could be extended for longer than an hour. It may not be possible to accomplish this, but I should like to try. It would involve a large number of variant solutions, since I would have to test each ingredient separately in varying strengths and also the effects of different combinations of changes. I would also like to try producing Veritaserum in a gaseous form that could be sprayed in someone's face."

"Why is such extensive testing necessary? Is this normal in science?"

"No one knows what we are looking for. It has not been tried before. Edison tested over six thousand materials during a period of fourteen months before he found the right one for his incandescent electric light filament."

"We see. Very well, you have authorization to order materials and start your experiments."

Snape waited until he was back in his laboratory before he allowed himself a private thought. \emph{I'd be willing to bet he doesn't know who Thomas Edison was.}

\sbreak

Snape went out and bought a stack of notebooks, pens that wrote in different colors, rulers, markers, labels, filing cards, and a couple of calculators. The crates of ingredients arrived the third week in October, and he started setting up his experiments. By the weekend before Halloween, he had fifty different solutions brewing, each one a slightly changed version of either Veritaserum or Polyjuice Potion. Everything was meticulously labeled, and he was taking extensive notes.

The scope of the experiments was a bit different from what he'd told the Dark Lord, however. In fact, Snape was trying to find a way to shorten the amount of time Polyjuice Potion would be effective. \emph{Imagine someone infiltrating the Ministry in disguise changing back to his true form fifteen minutes before he thinks he will. The Dark Lord would think it was carelessness rather than the potion.}

In the case of the Veritaserum, he was trying to produce a weaker brew, one that would make the victim want to tell the truth, but which a strong person could fight successfully. \emph{If some people can fight Imperius Curses, they should be able to fight Veritaserum, too.}

Unfortunately, a complication was thrown into Snape's life just at the moment when he thought everything was under control. He apparated back to Hogsmeade that evening and sent his patronus to McGonagall. On reaching the entrance hall, however, he found Umbridge waiting for him.

"Where have you been?"

"Out."

"Where?"

"Some of the teachers commute, you know. They apparate home every night and return in the morning. Just because I'm the head of a house doesn't mean I'm chained to Hogwarts every minute of every day. I'm not on call for emergency duty until eleven o'clock, and until then my time is my own."

"Where did you go?"

"It's none of your business."

"I can make it my business."

"Very well. I moonlight as a referee for World Championship Wrestling. I was in Detroit, Michigan prepping for Halloween Havoc tomorrow. Want a tip? Don't bet on Hulk Hogan."

Umbridge glared at Snape for a moment, then stomped up the stairs to her office. \emph{She's going to check. Gad, I hope Hogan loses tomorrow, or I'm in trouble with her again.}

Hogan, as it turned out, was disqualified, leaving Umbridge to debate whether Snape had been bluffing or telling the truth. He was not about to say. The following week was taken up with two events, the Halloween feast and the first Quidditch match of the season—Slytherin against Gryffindor.

Dumbledore reappeared at breakfast on Monday. The teachers tripped over each other in their hurry to welcome him back and express their concern about his absence. He admitted only to having been `a little under the weather.'

"Severus," Dumbledore called down the table, "I understand that McGonagall has been showing you the fine points of chess. I am pleased that I might have an opponent who is at the beginning level, and therefore does not totally outclass me. Would you be interested in a game this evening?"

"It would be my pleasure, Headmaster."

And so that evening at the staff table, in full view of Umbridge, they set up a chess board, and Dumbledore and Snape played against each other. Dumbledore had not been lying about his abilities either, for Snape found himself playing an opponent at precisely his own level. Within minutes, all the other teachers were forbidden to comment or advise. Many of them left, bored by the amateurish game.

After several moments and the capture of Snape's second knight, Dumbledore looked up and smiled sweetly. As their eyes met, Snape heard in his head, \emph{What has been happening at Croydon?}

\emph{Not a lot. He wants something he can't get. I think it's in the Ministry. He's asked for potions that help get information or that conceal a person's presence.}

\emph{I hear you are still having problems with one of your colleagues.}

\emph{He thinks confronting the Dark Lord should be on a level with a Sunday picnic.}

\emph{You need to put it aside.}

\emph{I will if he will.}

\emph{What about the `Lady?'}

\emph{Fine until she thought I was helping the students skirt her rules.}

\emph{Were you?}

\emph{Not by intention, but that was the practical effect.}

\emph{Stay on her good side. We may reach a point where you are our only contact. }"Checkmate," said Dumbledore, moving his bishop to attack Snape's king. "Thank you for a most pleasant game."

"Any time," Snape replied.

Halloween was uncommonly low-key that year. There were a few jack o' lanterns, and the occasional picture of a black cat, but the food was normal supper fare, and there was really no sense of its being a feast.

Snape felt it was the perfect occasion for being a bit morose.

\emph{Doesn't anyone remember what day it is today? You'd think Potter would remember, but never once in his life have I seen him do anything to commemorate it. Neither does Dumbledore. I bet Black doesn't either. Lily died on this day fourteen years ago. The worst day in the whole year.}

Snape left the table at the earliest possible moment and spent the rest of the evening in his own rooms.


