% A Difference in the Family: The Snape Chronicles (Rannaro)
% Two More For Azkaban

\chapter{A Conspiracy of Marauders}

% \sbreak

There was a knock at the office door. "Go away!" Snape responded.

"I ain't going away. I'm staying here and if need be I'm breaking down the door."

"I don't need a nursemaid!"

"I ain't nursemaiding, I'm protecting school property."

"I'm not destroying school property."

"Prove it."

Snape opened the door, and Hagrid barged in with his plate of food. As he set it on the desk, Snape protested, "I'm not destroying school property. Look around you. What am I destroying?"

"A very valuable Potions master. Now sit and eat."

"I'll sit, but I can't guarantee eating. Hagrid, why would he do that?"

"I don't think he did. Not a-purpose, anyways. He lives in the moment, always has. In that moment he wanted Neville t' feel good about hisself, t' feel strong and in charge. I don't think it even entered his head that it 'd leave that room. He don't understand the cruel side of people."

"Then he's dimmer than I thought. He's seen enough, even participated in some of it, to know about cruelty. I still think that was on purpose." Snape speared a sausage and bit into it. "He's a lot sneakier than you give him credit for."

Hagrid didn't argue. He just let Snape talk, not even understanding all of it, because as long as Snape talked, Snape ate. That, after all, was the purpose of his visit.

Classes didn't improve, especially the third year double Potions with Slytherin and Gryffindor. Between them, Malfoy and Longbottom were enough to ruin Snape's sleep and appetite for a day and a half afterwards, and the others were a constant irritant. It didn't help that from their first year, this had been the thickest, most incompetent group of potions makers Snape had ever had to deal with. Malfoy was actually one of the better students. Granger would be tolerable if it weren't for her habit of constantly waving her hand in his face, but the rest were impossible.

In the middle of the second week of school, Lupin came to see Snape in his office. Snape was grading papers, and called "Come" at the knock without bothering to see who it was.

"I hope I'm not disturbing you too much," said Lupin.

"What do you need?" Snape didn't try to hide the sharpness in his tone.

Lupin pulled a folded-up square of parchment from his pocket. "Just this. I didn't want to push you, but I didn't want to leave it until too late either. I'm{\el} I hope it's not too inconvenient."

Snape took the parchment and glanced over it. "This isn't the standard potion," he said. "Why did you add betony and valerian?"

"I have a nervous reaction to the original formula. They counteract it without altering its potency."

"It'll take about ten days to make."

"That's fine. I need to start the doses on the twenty-first."

"You'll have it before then."

Snape set up the equipment that evening and started preparing the first of several decoctions. The brew didn't need constant attention, and much of the time necessary for its preparation was taken up by the distilling process. True to his word, Snape had the first doses bottled into flasks and in Lupin's hands two days before he had to start the treatment.

"I wasn't sure how much you would need, so there is extra."

"Thank you, Severus."

On September 28, 29, and 30, Professor Lupin was absent from his classes. He was replaced by those teachers who didn't have a class at the particular times of his courses. Snape's free afternoon was, unfortunately, at the same time as the class with the third year Gryffindors. Lupin had left them a writing assignment, and all Snape had to do was baby-sit. He had no problem with that arrangement at all.

On October first, Professor Lupin was back in his classes. He looked awful. His young-old face was gray and drawn, and he walked like an old man. The depth of his fatigue was so great that it was almost impossible for him to teach his classes, and all he wanted to do was sleep. It was the same as he'd been the day he arrived at Hogwarts on the train.

Pomfrey contacted Snape part way through the day, just at the end of morning double Potions. "He never used to be this weak when he was a student. Tired, yes, but not exhausted like this. Do you think it's the potion?"

"He did say he had a nervous reaction to the original one, and that the betony and valerian were meant to counter it."

It was a problem like any other potions problem, to be worked out with logic and experimentation. Snape took some of the pre-symptom potion and added vervain, hyssop, and pennyroyal to it. At lunchtime he stopped Lupin in the entrance hall and pulled him down to his dungeon office.

"Try this," Snape said, handing Lupin a smoking goblet of mint-scented potion.

Lupin took the goblet, glanced once at Snape, then drained the contents in three long swallows.

"You probably should lie down, though resting your head on the desk would have the same effect."

"You're the doctor," said Lupin, and did as he was told. About half an hour later he sat up again. "I feel very much better," he said. "I should get some lunch before the afternoon classes start."

And indeed, the supplemental potion seemed to work, for Lupin was back to normal in his afternoon classes, and had a good appetite for supper.

\sbreak

Quidditch practice was under way. The first match of the year was set for the last Saturday in November, and Slytherin was to play Gryffindor. Slytherin had a chance of winning, especially since team captain Marcus Flint was the oldest, largest, and most experienced Quidditch player in the school. This was due to his having to repeat seventh year, not having completed his classes or passed his NEWTs the year before.

Malfoy was causing trouble, though. He continued to insist that his injured arm was troubling him. He'd gone back to writing his own assignments and cutting up his own ingredients, but he complained that the arm was stiff, and he couldn't extend it fully.

Snape could understand Malfoy's milking his injury for all it was worth to get other students to do his work, or as a weapon against Hagrid, but not to keep him from playing Quidditch. He consulted Madam Pomfrey about the boy, and she was mystified as well.

"When I manipulate the arm, Severus, I can extend it to its full length. There doesn't seem to be any lasting damage to the muscles, cartilage, or bone. It's when he tries to do it himself that the arm won't extend."

"That sounds neurological to me. What do we have on the motor nervous system?" Pomfrey's expression told him `not much.'

In the middle of October, the notices were put up that the first Hogsmeade excursion would be on Sunday, October 31. Snape got his supervisory assignment the same day, looked at his calendar, and went to McGonagall, who was in charge of the supervision.

"I can't be in Hogsmeade on the thirty-first," he said. "I have to stay at the castle. At least part of the day, anyway."

"And why, pray tell, are you suddenly special and exempt from taking your turn watching the little darlings at play?"

Snape knew that McGonagall was only half joking. Hogsmeade duty could be strenuous, and few of the teachers enjoyed it. When a dozen teachers had to oversee more than seventy percent of the school in an uncontrolled situation, it was not easy. The only problem was that his reason had to do with Lupin and his werewolf potion. The thirty-first was the day after the full moon cycle, and Lupin would be weak and sick. Snape didn't know if McGonagall knew about Lupin.

"I have reason to suspect that one of the teachers will be ill around that time. It's a potions matter. I really can't say any more."

McGonagall looked at him shrewdly. "I see," she said. "Very well, Severus. I'll take your name off the list."

Snape was up before dawn on Halloween morning working on Lupin's morning-after werewolf potion. He was refining some of the ingredients and needed to work out a dosage schedule.

Shortly after sunrise, Snape waited in the entrance hall with the first of the doses smoking in a small goblet. He handed it to Lupin as soon as he entered the hall with the order "Don't drink it too quickly," then watched as Lupin downed the liquid without demure. \emph{I wonder if he's still staying in the Shrieking Shack during the full moon.} This thought brought back the memory of the time Lupin almost killed him, and he locked it up at once.

"The potion is a bit milder than last time. I'm hoping you don't need a stronger one, since we caught this at the first moment. You'll need more at noon and in the evening, though, and if it isn't strong enough, you'll have to tell me."

"Thank you, Severus. I can't express how much I appreciate your doing this for me."

Snape looked at Lupin blankly, honestly not comprehending.

"It's my job," he said.

The school was blessedly quiet with only the first and second years in the castle. As long as you weren't supervising, Hogsmeade days were delightful. Snape caught up on his grading, read a little, and then fixed Lupin's noontime potion. Carrying the goblet upstairs to the Dark Arts office would give him a chance to get out of the dungeon and stretch his legs.

He knocked at Lupin's office door, heard Lupin call "Come in," and entered the room. There, sitting at Lupin's desk drinking tea, was Harry Potter. Snape stopped. \emph{What's he doing here? Why isn't he in Hogsmeade? What does Lupin want with him?}

"Ah, Severus. Thanks very much. Could you leave it here on the desk for me? I was just showing Harry my grindylow."

Snape set the goblet on the desk, watching the interplay between Lupin and Potter. \emph{Interesting change in tone from the last two times I medicated him. He wants Potter to think he's in charge, and he doesn't want me to know what they were talking about.} "Fascinating," he said. "You should drink that directly, Lupin."

"Yes, yes, I will."

"I made an entire cauldronful. If you need more."

"I should probably take some again tomorrow. Thanks very much, Severus."

"Not at all." \emph{He doesn't want to drink my potion in front of Potter. Does he want Potter to think he doesn't trust me?} Snape backed out of the room, trying to see an explanation in Lupin's face. There wasn't one.

Back in his dungeon office, Snape paced. \emph{Am I reading too much into this? They were having a conference. A student-teacher conference that was private. So why not say so? Why the business about the grindylow? They weren't looking at the grindylow at all. They were talking about something that Lupin doesn't want anyone to know about. Talking with Lily's son about something.}

For the first time in quite awhile, Snape thought about Sirius Black again.

Everything seemed perfectly normal during the Halloween feast. Snape found himself watching Lupin more closely and worrying about Lily's son. The boy appeared all right, but kept looking up at Lupin at the teachers' table as if he expected something to happen.

Snape always expected something to happen on Halloween. It was, after all, the anniversary of Lily's death, and he'd been sitting in exactly the same spot when the news reached Hogwarts twelve years before that the Potters and the Dark Lord had all been destroyed. \emph{Nobody else seems to remember she died on this night. Potter doesn't. Lupin doesn't. Dumbledore doesn't. I hate Halloween.}

\emph{Ever since Potter came to Hogwarts, something has happened on Halloween. Last year the basilisk petrified its first victim on Halloween. The year before we had a troll. What's going to happen this year?}

It didn't take long after the feast to find out. Snape and his prefects were getting the Slytherins back to their common room when the word began buzzing through the hall—Gryffindor was locked out! The Fat Lady's portrait was slashed and she'd fled in terror! As Snape started making his way up the stairs to assist, more rumors met him. Peeves had identified the assailant.

It was Sirius Black.

Snape never actually reached Dumbledore. As he went up the stairs, Gryffindor and Ravenclaw students were coming down. McGonagall saw him and called down the staircase, "All students are to go at once to the Great Hall. Slytherin and Hufflepuff, too. Tell Sprout if you see her."

He started back down, herding students towards the Great Hall as he went. Reaching the entrance hall Snape hurried down the dungeon corridor to Slytherin house. To the surprised students in the common room he said, "Get everyone out of the dormitories. Take everything you'll need for the night. Everyone is to get into the Great Hall as quickly as possible. There may be a dangerous intruder in the castle. Prefects, start with the far rooms and work your way to the corridor wall. I don't want one student left here. Flint, you and the other Quidditch players check the whole dungeon and stand guard to keep people from going back once you've cleared them out."

In the entrance hall Snape met Dumbledore coming down. "Severus, how fortunate. Would you please go up and check the Astronomy tower, the north tower, and the Owlery tower? McGonagall is taking care of Gryffindor and Flitwick of Ravenclaw. That will take care of the highest points in the school. Then work your way down with the other teachers."

Dumbledore went into the Great Hall while Snape hurried up the stairs. It was logical that he take the towers because he and Lupin were the youngest teachers in the school, and Lupin was sick. As he reached the seventh floor, Snape opted to check the Astronomy tower first. Best to get it over with quickly.

At the top of the spiral staircase, Snape stepped out onto the flat top of the Astronomy tower and glanced around at the parapet and enclosed space. That other Halloween twelve years earlier he'd ended up here, too, though he'd not been hunting an intruder. \emph{Mightn't it have been better if Hagrid hadn't stopped me that night. How much good have my last twelve years done anyone?}

It was then that the full import of what was happening hit him. \emph{Twelve years ago tonight, Sirius Black betrayed Lily Potter to her death. Now tonight, twelve years later, we're hunting the same Sirius Black who's come into Hogwarts to complete the botched job. Tonight may be the night justice is finally served!} Snape returned down the spiral stairs with a renewed sense of purpose, pondering the quarry he was hunting.

\emph{He's been twelve years in Azkaban and a well-publicized fugitive for three months. He can't have a wand with him. So how did he get in? The castle's been locked tight every night against dementors. There's no way. Someone must have let him in. Who do we know in the castle who's a friend of Sirius?}

\emph{Equally to the point, how did he get onto the grounds, especially with dementors all around? I did it once, through the Shrieking Shack, but ever since then the Shack's been magically guarded. Who knows of the Shack and the passage to the Willow, can release the magic charm, and was actually using the Shack up until this morning?}

\emph{Odd how this keeps pointing to one person.}

As he searched the other towers, Snape could feel the volcanic pressure building inside him. \emph{Control. Control yourself. Need wit. Need logic. Need a cool head.}

\emph{He braved the dementors. He didn't even care about the dementors. All he wanted was to get here and kill a child. Right to Gryffindor, he went right to Gryffindor, where the students would be studying and talking and sleeping except tonight was Halloween. Did he remember it was Halloween? Did he expect to find Lily's son unsuspecting, sleeping, easy prey.}

\emph{He didn't escape Azkaban to flee dementors. He escaped Azkaban to kill a child. Kill children if the others got in his way. Kill his friend's son. My friend's son. Kill all that's left of Lily. Close the emerald eyes. Lily's eyes.}

Snape was in the entrance hall again, in front of the double doors. \emph{Quiet now. Children. Children sleeping behind the doors.} He paused and breathed deeply, then opened a door just enough to slip through, in control of himself and his thoughts once again.

Dumbledore was standing in the middle of the Great Hall surrounded by students sleeping peacefully in purple sleeping bags. He was talking to the Head Boy, a Gryffindor. One of the Weasleys. Percy.

Swiftly but quietly, Snape moved across the floor of the Great Hall until he was close enough to talk to Dumbledore without disturbing the sleeping children.

"Headmaster?" he said.

Dumbledore looked up as Snape approached.

Snape spoke in a low, quiet voice, less noticeable than a whisper. "The whole of the third floor has been searched. He's not there. And Filch has done the dungeons; nothing there either."

"What about the Astronomy tower? Professor Trelawney's room? The Owlery?"

"All searched{\el}"

"Very well, Severus. I didn't really expect Black to linger."

Snape was not about to let the conversation end there. \emph{Slowly. Go slowly. Stay in control.} "Have you any theory as to how he got in, Professor?"

"Many, Severus, each of them as unlikely as the next."

"You remember the conversation we had, Headmaster, just before{\el} the start of term?" \emph{He has to listen. There's too much at stake now.}

Dumbledore seemed to have other ideas, for his voice became cold. "I do, Severus."

\emph{He doesn't want to talk about it here in front of Weasley, but if I don't make the point now, it may be too late. Try to calm down and sound reasonable.} "It seems almost impossible that Black could have entered the school without inside help. I did express my concerns when you appointed{\el}"

"I do not believe a single person inside this castle would have helped Black enter it." And there it was. Dumbledore had cut off the subject, refused to listen, refused to even entertain the prospect. Then he sealed it completely. "I must go down to the dementors. I said I would inform them when our search was complete."

\emph{He knows I can't follow him{\el} can't go near the dementors.}

Dumbledore was talking to Weasley. "{\el}but I'm afraid no dementor will cross the threshold of this castle while I am headmaster." And then he was gone.

\emph{You won't listen to me. Will you listen to Lupin? Do you even know where Lupin is? He was sitting at the feast, and then he was gone. We never did see him while we were searching the castle. Maybe we didn't find Black because Lupin let him out again. What about that, Professor?}

One little, nagging voice at the back of Snape's skull did mention that Lupin could have told Black that Lily's son was at the feast that evening, but Snape was in no mood to listen to it at that moment.

Suddenly everyone was aware that Potter was in danger, and the boy was unable even to go between classes without an escort. He appeared to resent it, acting as if the rest of the school were fools and he an immortal god. McGonagall was beside herself.

"He's known since before school started that Black was after him, and he thinks it's not important. Certainly not as important as Quidditch practice. Black was in the castle. In the castle! He drove the Fat Lady away and had free run of the Gryffindor common room and dormitories, but Potter has to have his unencumbered Quidditch practice."

Snape agreed. "The Headmaster is equally stubborn, Minerva. It's impossible for Black to have gotten in without help, yet he refuses to investigate. How are we to do our jobs with no support?"

"Do you have anyone in particular in mind?"

"You know there's only one old friend of Sirius Black's in this building."

"Oh but Severus, I don't think Remus would let Sirius hurt anyone."

Snape folded his arms across his chest and narrowed his eyes. "Funny about that. My recollections seem to be just a tad different from yours."

"Oh," said McGonagall. "Yes. I see what you mean."

Then, just as the end-of-November Quidditch match was approaching, Malfoy announced that his arm had not improved enough to allow him to play. Gryffindor would meet Hufflepuff instead of Slytherin.

To make matters worse, Lupin came to Snape on the Friday before the match. "Could you take my classes this afternoon, Severus? I don't feel well. I'll be gone for a few days."

"I thought that started tomorrow night."

"I did, too, but it seems its coming earlier this time."

The sudden change of plans gave Snape an idea.

Snape did not go to lunch. Instead he went to his office and pulled out the paper that Lupin had given him with the werewolf-calming formula on it.

\emph{Why would he start feeling ill two days before the full moon when the cycle starts the day before{\el} Dumbledore should have investigated this before he ever took the post{\el} If the potion is too weak—no, then he'd just be more like a normal werewolf{\el} We already knew Black was loose before Dumbledore offered him the job. It was so obvious{\el} What if it's too strong? He has been having reactions, hence the betony and valerian{\el} He's got to be forced to investigate, or we'll have dead children, but he won't listen to me.}

Pulling jars and tins from the shelves around the office, Snape began going through his stores of calmatives, stimulants, and restoratives.

\emph{I can't force Dumbledore to investigate, but the Board of Governors could{\el} I wonder if it's the betony. It's an aperient as well as a nervine. It could be weakening him{\el} The parents could, too. If it comes from me, Dumbledore won't listen, but if it comes from the parents{\el}}

\emph{Potter doesn't have any parents. All because of Sirius Black. And that fool James Potter. Couldn't you see how unstable your `friend' was? The rest of us could. Crazy and unpredictable. You had the best secret-keeper in the world, and you turned to a madman out of `love.' Did you love Sirius more than Lily? Was that why you let him talk you into it? Sentimental idiot. Lost life, lost wife, lost one friend dead, two friends gone bad, son in danger{\el}}

Realizing that it was almost time for Lupin's class, Snape put all his potions material in order, locked the office, and went upstairs to the Dark Arts classroom.

Lupin's Friday afternoon class was Snape's least favorite group of Gryffindors. He allowed them a few moments of horrified realization that the class would be taught by their least favorite teacher, then proceeded to the formality of taking roll. It really was just a formality, as Snape already knew that only one student was missing—Harry Potter.

\emph{Just like Potter. A madman loose on the grounds who has access to the castle—a madman he knows to be intent on hurting him—and he's wandering around alone. And Lupin's out, too. Lupin suddenly gets `sick' and Potter's not in class{\el}} The knot was forming again in the pit of Snape's stomach.

"Now," Snape addressed the class, "as has, I am sure, become abundantly obvious to even the least cerebral of you, Professor Lupin is not here today. He feels `unwell.' He has, unfortunately, left no lesson plan nor any record of what you've covered so far{\el}"

Predictably, Granger's hand immediately shot into the air, and at the same time Potter burst through the door gasping, "Sorry I'm late, Professor Lupin, I—" then skidded to an abrupt halt as he recognized Snape.

\emph{Let's make sure he has reason not to wander alone during class time.} "This lesson began ten minutes ago, Potter, so I think we'll make it ten points from Gryffindor. Sit down."

"Where's Professor Lupin?"

No `Professor.' No `sir.' Just raw, blatant defiance. Snape closed down immediately and braced himself to meet the green eyes. Lily's eyes, now obscenely lit with James's arrogant sneer. A profanation, a blasphemy. Snape's voice was chill, "He says he is feeling too ill to teach today. I believe I told you to sit down."

"What's wrong with him?"

\emph{Don't fight me, Potter. You're making it very hard to want to save your life.} "Nothing life-threatening." \emph{Unlike the danger you face from Sirius Black.} "Five more points from Gryffindor, and if I have to ask you to sit down again, it will be fifty." \emph{And if you defy a teacher in front of a class again, you'll have detention for the rest of the year.}

Potter, however, took the hint and sat down.

The rest of the class, led by Granger, was equally rebellious, with even Thomas and Patil questioning the assignment he gave them. It was irritating, but he punished none except Granger and Weasley, both of whom went too far, since essentially the class was right. It was too early in the year for them to be studying werewolves. Werewolves, however, were what they needed to know about now, in the real world. \emph{Lupin has been working hard to be popular with this group. It won't be easy to get them to focus on the danger, especially since Dumbledore won't allow me to tell anyone about Lupin's `problem.' If just one or two notice and tell their parents, though{\el}}

While the class studied the werewolf section in the book, Snape looked at some of the papers. Lupin wasn't exacting enough, in Snape's opinion. But then he'd always been like that, always wanting to ease up on people he liked.

After taking five points from Granger and giving Weasley detention, Snape assigned the entire class an essay on how to recognize and destroy werewolves. \emph{At the very least, they have been forced to study what to do if they ever have to face Lupin in wolf form. May it never happen, but if it does they're better off prepared.}

At the end of the class, Snape returned to his office to continue puzzling over Lupin's potion.

It was well into supper time when there was a knock at Snape's office door. It was Hagrid. "I've got somewhat to say about this habit you're getting into of skipping meals," he said accusingly.

"Potions work. Medicinal," Snape responded.

"In that case, then, you'll let me bring you a plate."

"Of course." Snape absent-mindedly closed the door in Hagrid's face.

He needed pennyroyal and reached up to shift some tins in order to get it. Glancing at the tin in his hand, Snape paused. It was aconite{\el} monkshood{\el} wolfsbane{\el} \emph{Why did I pick up that one?} He rotated the tin in his hand, aware of the shadow thought forming in the recesses of his brain, but refusing to look at it. He listened instead to the voice of his witch grandmother, Nana. \emph{Potions are a sacred thing, for with them you hold life and death in your hands, and they are not toys to be treated lightly. You can care for the body, but you cannot probe the soul or part the curtain of the future to see if today's actions are good or evil. So above all, do no harm.}

Hagrid knocked again, bringing the food he'd promised. Snape carefully placed the tin of aconite back on its shelf and answered the door.

Noon is generally a good time to visit someone afflicted with Lycanthropy. While the rest of the school ate lunch and buzzed with anticipation about the day's Quidditch match between Gryffindor and Hufflepuff, Snape finished his potion. He then checked with Madam Pomfrey, who asked that he take Lupin some food as well, thus sparing her a trip in what was already looking like the biggest storm of the season.

It was a terrible day for Quidditch. Rain pelted down in blinding sheets while wind whipped the castle towers into aeolian pipes. Nothing short of lightning stopped a Quidditch game, however, and the school was prepared to troop en masse down to the pitch to watch as much of the action as they could see through the rain.

Snape took a flask of the modified werewolf draught and a dish of food, wrapped himself in a hooded cloak, and slipped out of the castle, taking care not to be seen, though in the torrential rain it was unlikely anyone would notice his dark figure walking down the hill.

He'd only used the passage under the Whomping Willow twice before in his life, but both occasions had been memorable ones, and Snape found the knot that froze the tree with no problem. Then ducking down between the great, overgrown roots, he entered the tunnel and made his way to the Shrieking Shack.

Lupin was in the upstairs room, sitting at a table with his head resting on his arms. He looked up as the door opened and Snape walked in. "Good morning, Severus. Or is it afternoon already? It's kind of you to call."

"I brought you something," said Snape, setting the plate of food on the table. "Did you change last night?"

"No, actually. I felt like I was going to, but in the end there was no transformation. It looks like I'm on schedule for tonight."

"Drink this, then." Snape handed Lupin the flask. "It's the same, except I replaced the betony with pennyroyal. It should be less enervating and relieve some of the muscle tension. If it isn't effective, we can try something else."

Lupin took the flask and downed its contents at once. Handing it back he said, "You wouldn't care to stay and talk, would you? It gets lonely here sometimes."

"No. I wouldn't."

"Back at the beginning of the term I asked you a question, whether you understood{\el}"

"I remember."

"I'd like to understand." Lupin spread his arms. "Is it because of what happened here?"

"That wasn't your fault."

"Then what{\el}?"

"Did you ever try to stop them? Did you ever once try to stop them?"

"That's unfair. There was that time by the lake."

"Lily was there. You did that because of Lily. No, I mean just because{\el}" Snape stopped. He was looking out the window of the Shack where they had a view of the area around the Quidditch pitch. "What's happening over there? It looks like more than the storm."

Lupin looked, too. "It's the dementors! They're being drawn to the Quidditch game!"

The two professors raced down the stairs, through the tunnel, and out into the rain as quickly as they could run, Snape ahead of Lupin, who was sick from his impending change. They slowed in the grass and mud at the base of the hill, where footing was less certain because of all the water.

Snape had reached the road that led up the hill when the cold hit him. He knew immediately what it was. Whatever may or may not have happened at the Quidditch game, his and Lupin's presence was now superfluous. The dementors had left the pitch and were returning to the perimeter, and there was at least one of them somewhere in front of him, invisible in the gusting sheets of rain.

Dementors felt and fed on emotions, and Snape began to back away and lock down simultaneously. No occlumens can fool a dementor for any length of time, but this one was far enough away that it might not have sensed him yet. He had no desire to feel its touch ever again in his life. Turning, he moved quickly up the hill, slipping slightly in the mud.

Lupin rushed up, as fast as he could go in the mud and the rain, his wand extended toward the source of the cold. \emph{"Expecto Patro{\el}"} he almost managed to shout, when Snape grabbed his arm, twisting the wand down, and clamped a hand over his mouth.

"Don't attract their attention!" he hissed.

Lupin glared at him, but did as he asked, the two of them now hurrying up into the castle, both drenched and bedraggled. Noting that Lupin's skin had a grayish color, and that his breathing was ragged, Snape took him by the arm and pulled him into the office in the dungeon where there was already a fire burning.

Tossing Lupin a couple of towels, Snape went into his bedroom to get a warm blanket. "Get out of that wet robe and dry off. I'll get you something to take the chill off and perk you up a bit. Then you'd best take a cloak and return to the shack before the change begins."

Lupin wrapped himself in the blanket and sat huddled by the fire, but when Snape gave him the warm potion he asked, "Why did you stop me? One of them was turning towards you."

"I was far enough away. It didn't have a strong feel for me. You'd have drawn it to us."

"No, it marked you. It was turning. I could see it turn."

"See? In that rain? I didn't know your condition improved your eyesight so spectacularly."

"Stop this!" Lupin snapped, and the tremor in his voice was not from the cold. "I was trying to help you. I wanted to protect you from that thing."

"I don't need protection."

"No? So you're here because you love to teach?" Lupin took a deep breath. "Severus, I know what you were. I know you changed before the end, and that Dumbledore valued you. I know that if you ever leave here, it's with a one-way ticket to Azkaban. But that's history. It's finished. You and I are colleagues now, can't we treat each other like colleagues? You made some choices in the past that turned out wrong, but{\el}"

Snape had gone icily cold, not the cold of the dementors but the cold that preceded an explosion. "Get out," he said, struggling to control his voice and his hands. "Get out of my office. Take your things and leave."

Lupin's anger was cold, too. "I can't believe that you'd allow schoolboy grudges to control your life all these years. Grow up, Severus. Let it go. Leave it behind you and grow up!" Then Lupin rose and walked out the door.

Close behind Lupin, Snape shut and locked the office door, his hands trembling as if with palsy. His body was wound so tight now that he was shaking all over. He could smash his fist into the leaded glass on a cabinet door. He could slam himself against the wall. Striding to the side of the room, he instead wrenched open the doors of a cupboard containing jars and beakers. In one long, fluid motion, he seized a beaker and flung it with deadly precision into the fireplace. Another beaker followed, and another, each shattering against stone with all the energy he could channel through nerve and muscle until the shards of twenty-seven covered the grate.

Drained, he let his legs buckle under him and collapsed beside the drawers at the base of the cupboard. There he sat as evening fell and darkness gathered, leaning against the knobs and drawer pulls, emptying his mind of thought and feeling, floating in a limbo of nervous exhaustion until, in the wee hours of the morning Snape finally dragged himself into the other room and lay on the bed.

That was a mistake, for that was when he drifted into restless sleep.

\sbreak

\emph{He stood on the grass facing Lily—her emerald eyes held him mesmerized—but the eyes were in a different face, and he knew he was in danger. The attack came from behind—he wheeled to face the great dog, the mastiff, with its bloody fangs. Around him a crowd was laughing at the sport—he was the sport—and the wolf with a prefect's badge pinned to its fur lolled on the grass grinning.}

\emph{Hit from behind again, he spun to face the new threat. But he never could face it because however he turned it was always behind him. He wanted to run, but he was lying on the ground, arms and legs strapped with iron bands. He wanted to scream, "I didn't do anything!" but harsh bristles tore at his tongue, and pink foam frothed in his mouth.}

\emph{The foam expanded, clogging his nasal passages, filling his throat, burning his lungs. He couldn't breathe—couldn't breathe—he was dying—and the crowd was laughing, for his fear, his pain, his death were all for their amusement{\el}}

\emph{Then foam was gone, bristles gone, iron bands gone, and Bella stood above him, pushing back the crowd. He crawled to her to lay his head on her feet, where she sat at the table. "Good dog," she crooned, "Good little puppy," as she fastened a collar around his neck, and he lay curled at her feet because that's what good dogs do.}

\emph{He woke in the dark alone. The collar was gone. Rejoicing in freedom, he went out into the sunlight. But the sun was dark, and the wolf and the mastiff attacked him, tearing at his throat, his limbs, his stomach. "Help!" he screamed, "Please help me!"}

\emph{"I can't," said Bella. "You're not wearing the collar."}

\emph{Frantically he searched the room as the mastiff rent his flesh. The collar was in his hands, and he fastened it around his own neck. Then the animals weren't there, only Bella, singing. "Now I can protect you—protect you—protect you—" And he lay at her feet and loved her.}

\emph{"Come with me," Bella said, fastening a steel chain to his iron collar. He trotted at heel beside her. Around them were wolves, hounds, lions, tigers{\el} but they couldn't touch him if he wore the collar.}

\emph{In the dark, dark room they faced a hooded spectre. Bella smiled. "I've brought you a pet{\el} a puppy{\el} a servant{\el} a slave{\el}" Red eyes burned into his mind, his heart, his soul, his arm, as the cold voice laughed, "I have a collar, too{\el}"}

Eyes suddenly opened wide in the darkness, Snape listened for the rustle of robes in the chamber. In the silence he raised a hand to his throat, expecting to feel the collar. There was no collar, no chamber, no rustle of robes. He was lying in bed, heart still racing from the nightmare.

He groped his way from the bed into the office, where embers glowed in the fireplace. There, in the lingering warmth, Snape stoked the fire and sat in front of it, wrapped in the blanket he'd brought out for Lupin, waiting for dawn and the coming of light.

As soon as it was time, Snape left his office to go to the Great Hall for Sunday breakfast. He was a little dizzy from lack of food, and once again he had a headache.

Lupin wasn't there. \emph{Of course not. He's a wolf lying in the upper room of the Shrieking Shack.} Hagrid was, though, and Hagrid was clearly relieved to see Snape walk into the Hall.

"Where was you last evening?" he muttered. "We was all riled up about the dementors at the Quidditch match, and Harry and all, and come round about ten I says to myself, `I ain't seen Professor Snape come in for supper,' but then it was too late."

"I was busy. What happened to Potter?"

"He's in the hospital wing, not bad hurt but Madam Pomfrey wants t' keep him there a while. Them dementors came right onto the Quidditch field. Seems they went for Harry most of all, and he fell off his broom about fifty feet up. Dumbledore was already on the field driving off the dementors and managed to slow Harry's fall. Had us all scared there for a bit."

Snape ate as Hagrid talked, asking a question from time to time, though there wasn't much more than that to tell. \emph{Potter has no luck with opening Quidditch games. First one his broom's jinxed, then its bludgers, now its dementors.}

As he finished his breakfast, Snape's attention was drawn to Malfoy at the Slytherin table. Draco was obviously doing imitations of dementors and of Potter falling off his broom. The little group around him was giggling. \emph{That boy and I are going to have a talk today.}

Breakfast over, Snape went up to the first floor, to the hospital wing. He spoke briefly with Madam Pomfrey, who'd taken Lupin his breakfast. All apparently well with his patient, Snape returned to his own rooms to clean up the broken glass and generally straighten everything from the episode of the evening before.

He was calm, but only because he'd locked everything, including the dream, away.

At midmorning there was a knock on the door.

"Come," Snape called. He was making samples of werewolf potion with different proportions of ingredients.

Dumbledore entered the room. "Ah, Severus," he said. "It is good to see you looking well."

"Did you expect that I wouldn't, Headmaster."

"Why so informal? Why do you not call me Professor, as you usually do?" Dumbledore moved around the table to a position where he could see Snape's eyes, and though Snape carefully avoided contact, Dumbledore soon nodded. "I take it that you and Remus had a{\el} difference of opinion."

"Am I that transparent."

"My boy, there are days when you are the purest of crystal. Others when you are as impenetrable as obsidian. And on the days when you close yourself down this tightly in the privacy of your own office, it is generally because what you are afraid of is inside you. The most obvious trigger for this is poor Remus. How is he doing, by the way?"

"He doesn't react well to the medication. It makes him sick both before and after the change. We're trying to adjust it to smooth out the transitions."

"If anyone can, it is you. Tell me now, what happened with Remus?"

"He wants to be friends."

"Defensive sarcasm, and therefore a slight exaggeration. Today is a crystal day. You see, it is not so hard. I take it Remus wishes to cease being enemies."

"He also wants to protect me from dementors and forgive me all my sins."

"Whose sins do you not want forgiven, his or yours?"

"He is going to forgive me for the wrong choices I made in the past."

Dumbledore's eyes widened slightly. "I am most gratified, Severus, that you have chosen to confide this in me. Things begin to get clearer. So the difference of opinion involved the nature of choices?"

"I would prefer not to talk about it."

"I am a patient man. It has taken me what, twelve years to get this piece of information. I shall treasure it and ponder it{\el}"

"Now you're being sarcastic."

"You are right. I beg your pardon. It troubles me, though, that you are so closed, that there is no one that you can open yourself to. That was what was so wonderful about you and Lily Evans. Just knowing that you had someone to talk to{\el} Severus?"

"It's nothing. I'm all right."

"Do you ever talk to her now?"

"You do watch me!"

"That was not an answer." Dumbledore waited as Snape turned away from him to the potions on the workbench.

"I did. I can't now. There are dementors around the lake."

"Is there any place else where she is?"

"The Astronomy tower."

"No, no. That would not do at all. Not at all." Dumbledore paused. "Remus is a good man, Severus. As are you. He may understand more than you think. It is an option you should consider. You think about it. And I shall see you at lunch."

Dumbledore left Snape to his potions and his thoughts.

\sbreak

"Malfoy, may I have a word with you?" Teachers and students were leaving the Great Hall after lunch, and Snape took advantage of the opportunity to call the boy aside.

"Certainly, Professor. What can I do for you?"

Malfoy's attitude was a bit cockier than Snape expected. "Perhaps in my office?" he said. Malfoy followed him into the dungeon.

Once inside, Malfoy immediately sat down in the chair next to the desk. "Haven't been here in a long time. Doesn't change much, does it?"

"Not all change is good. How is the arm?"

Malfoy flexed it a little. "Getting better, I think. Madam Pomfrey's been working at the scars. They're almost gone. I'll be happy to see the last of these bandages."

"Your parents are well?"

"They're fine. Father isn't any happier about the condition of this place, though. Thinks it's a disgrace Dumbledore hired that pathetic Lupin to teach Dark Arts. Odd, too, that you and he find so much to talk about. Is it true, Professor, that you were attacked by one of the dementors? Kind of like a tiny taste of what Azkaban is like."

\emph{This boy knows something. Is this a threat, or a warning? Whatever he's playing at, power in the hands of a thirteen-year-old is not a pretty sight.} "It's of dementors I wished to speak to you. You've been going around imitating them in front of people. Some members of this house have relatives in Azkaban. A couple of people, and yes the rumor about me is true, have been too close to them to find you amusing. One person on staff was in Azkaban for a few days. Your joke is in bad taste."

"They should've kept him in Azkaban. That's another decision of Dumbledore's Father isn't happy about. That oaf's no teacher. They're almost finished with the investigation of his attack on me, though, and that class 'll be history. They may even investigate old Dumbledore for hiring him in the first place. Wouldn't you like a change of headmaster, Professor?" The gleam in Malfoy's eyes was unmistakable gloating.

"What you change to is usually more important than what you change from. Until I know that, I'll reserve my judgment. Keep in mind what I said."

"Sure, Professor." Malfoy left the office.

That was impressive. \emph{He's better at this than his father. Now what? Do I take him on, or do I take the hint? If only I had a way to know how serious the threat to Hagrid and Dumbledore is.}

\sbreak

"Severus!" It was Tuesday afternoon, and Lupin was once again back teaching. "Severus, I'd like to talk to you."

"Certainly. Always at your disposal."

"Not here. My office, maybe."

Once inside the office, so much larger and brighter than Snape's, with its grindylow swimming peacefully in the large tank, Lupin turned to face Snape, clearly angry.

"What's this game you're playing with my students?"

"I'm sure I don't know what you're talking about."

"Do you think I'm an idiot? You gave them that werewolf assignment to try to expose me. I want to know why."

"Let me see. We have a werewolf with unpredictable reactions to a calming potion sleeping three nights a month in an unguarded shack, and we also have a madman running around with inexplicable access to a barricaded castle in which a friend of his resides. I would hazard a guess that student safety had something{\el}"

"I would never! never! do anything to endanger the students!"

"No? Your very presence is a danger. What happens if you get careless?"

"I'm not going to get careless."

"It only needs once, Lupin. Winter's on us. Long nights, a werewolf roaming the halls who forgot to take his medicine, unsuspecting children on their way to bed. You've never had any close calls?"

Lupin was silent, but the flicker in his eyes was all the answer Snape needed. "Do what you like about the assignment," he said. "They've looked at it. They don't need to write about it."

Snape walked out of the office, leaving Lupin standing there in thought.

\sbreak


