% A Difference in the Family: The Snape Chronicles (Rannaro)
% Two More For Azkaban

\chapter{Struck from Behind}

% \sbreak

By supper time, Snape was a bit more ready to deal with the situation.

"How does it feel not being on top anymore?" Sprout called from halfway across the Great Hall.

"Very comfortable, in fact. Much less like a moving target."

"Bit of a shocker for you today, wasn't it my boy?" commented Flitwick.

"We just couldn't bear to see you lose all that money you bet on Gryffindor. And don't say I never did you a favor."

Hagrid was almost contrite. "I sort of lost my head there, Professor. It's just that me and Harry, we've been like that since I first took him to Diagon Alley. Nothing against you, just that me and Harry, well you know."

"I know, Hagrid. No hard feelings."

Then there were final exams. Nothing special happened except that Potter, contrary to all expectations, was totally unable to pass the practical portion of the exam. His potion was a disaster.

\emph{If it weren't for your eyes and your nose I'd refuse to believe you were Lily's son at all. Is there nothing of her in you? You have money, you have fame, you're good at Quidditch, and you're a mediocre student. There is no doubt, even apart from your appearance, who your father was, but does your mother live in you at all? She was good at potions, and at charms, and at many things. Aside from broomsticks, what are you good at? Ah, one thing. Getting yourself out of the trouble that you got yourself into.}

Hagrid, too, was reaching crisis. On the Thursday that was the last day of exams in early June, Hagrid's hippogriff Buckbeak was scheduled for his appeal. The appeal was taking place at Hogwarts, and if lost would mean the execution of Buckbeak at sundown of the same day.

The Minister of Magic arrived that day at Hogwarts around noon. He was actually visiting in regard to the search for Sirius Black, but was doing double duty as a witness at the hippogriff's execution, should it come to that. With him were two representatives of the Committee for the Disposal of Dangerous Creatures.

Snape had been thinking of talking to the Minister, Cornelius Fudge, about Hagrid and the hippogriff, but on arriving in the entrance hall was arrested by the sight of the representatives of the Committee. The older wizard was unknown to him, but the younger was not, and he immediately recognized Snape.

"Well hello there, Snape old boy," he boomed, his black mustache quivering and the axe in his belt bobbing. "Fancy seeing you here."

"Hello yourself, Macnair. It has been ages, hasn't it. What brings you to Hogwarts?"

"Hippogriff to put down. Malfoy's keen on it. Looking forward to it myself. Hard to get a good job these days."

"I heard there was an appeal."

"Don't go placing bets. It's a done deal. When you get down to it, the beast attacked the boy. Enough said. And you don't want to go getting in the way of Lucius Malfoy. Better for me, too. And for you. You ever hear anything really good about a hippogriff? Best to chop 'em all, I say."

"You're probably right. I can't tell you how to do your job."

Macnair lowered his voice to a whisper. "You hear what's on the grapevine? They say he's coming back, that he's shown himself. I'm waiting for the summons. Is it true you saw him here at Hogwarts?"

Snape hesitated. Macnair was one of the more brutal Death Eaters, and Dumbledore considered it imperative that Snape's position regarding the Dark Lord remain ambiguous. "I stood as close to him as I am standing to you right now, but he felt that communication at that time was not wise. He's not yet regained bodily form."

"Lucky man, to have the chance to see and talk to him after all these years. When he returns{\el}"

The Minister called to Macnair, "We're ready to go up and see Dumbledore now. Best come along."

Snape watched them go. With Macnair standing by to see and hear everything, there was no way to speak to the Minister about Hagrid. At least Dumbledore would be able to intercede, and after all, Dumbledore's word carried far more weight than his own did.

Hagrid lost the appeal, and the hippogriff was sentenced to be executed at sundown the same day. Since it was June, that was well after dinner. Hagrid, naturally, was not in the Great Hall that evening, though the three from the Ministry were. Snape had the feeling that Macnair was watching him all during the meal.

There was no question of going to see Hagrid. Aside from the dementors, Macnair would be there. \emph{What has he heard that he's waiting for a summons from the Dark Lord? How many others know? How?} As soon as Dumbledore was finished with the `visitors,' Snape would have to tell him about Macnair's information.

Potter and his friends were at dinner, which was some relief. Snape had thought they might try to sneak out of the castle to see Hagrid. There was always that dratted invisibility cloak, but it didn't appear that Potter had it with him.

Snape returned to his own rooms after dinner to avoid Macnair. Shortly after sundown (the execution is over now, poor Hagrid), Snape suddenly thought of Lupin. It was an odd full moon that reached its full in the early hours of the morning. Lupin had not been certain whether he would transform that night or the next. He'd wanted to wait in his office rather than the shack, since other than the weakness, he'd had no problems with the potion.

Snape decided to check on him, and to take an extra dose of the calming potion just in case.

The corridors of the castle were deserted as Snape made his way to the second floor with a goblet of potion. He knocked at Lupin's office door, but there was no response. Fearing the transformation had happened, but knowing that Lupin had been taking his medicine, Snape opened the door and went into the office.

Lupin's office was empty. On the desk, untouched, was the goblet of potion that Snape had brought him earlier in the day. \emph{He's done it. He's been careless about his medication. He's going to transform into a full-blown, uncontrollable werewolf as soon as the moon rises.} It was then that Snape noticed the map.

He hated that map. Like the invisibility cloak, it had been used to separate him from Lily's friendship. Lupin was obviously using it to monitor the movements of everyone at Hogwarts because the whole castle was clearly visible with its little moving dots.

Snape paused for a moment in front of the parchment. Dumbledore and the Minister were coming up the hill by the road. Lupin's dot was moving down the hill, not by the road, but straight towards the Whomping Willow. Snape looked closer. There in the tunnel between the Willow and the Shrieking Shack were Potter and Granger, their dots almost off the edge of the map.

\emph{How does Potter know about the tunnel? Is Sirius Black already in the Shack waiting for him? Has Lupin gone to block his retreat?} Snape was out of Lupin's office and running down the stairs to the entrance hall as fast as he could go.

Dumbledore and the Minister had not progressed far enough to waste time hailing them. For all Snape knew, Potter was dead already. He followed the path of Lupin's dot, across the summit of the hill and down the side closest to the Willow.

Alarm bells were ringing in Snape's brain. \emph{Macnair is coming up the hill—he'll see me and be suspicious. There are dementors in the Forbidden Forest—I'll alert them by my movement. Lupin's about to transform into a werewolf—how do I handle him? Potter's heading for the Shrieking Shack where Black is probably waiting for him—I have to stop him.}

Approaching the Willow, Snape sensed two things: the Willow wasn't moving, and there were dementors nearby. He stopped. \emph{Slow down, Severus. How close are the dementors? Maybe they haven't marked you yet.} He had to force himself to take the next step. \emph{How close before they notice and attack? Don't think of that. Think of Lupin turning into a werewolf in the same room as two students. Stop him. Have to stop him.}

Step by forced step he edged closer to the Willow, which was starting to sway. There, on the ground by its roots, was the invisibility cloak. An evil thing. A wicked, filthy thing. And yet there was a homicidal maniac and a werewolf ahead of him. Up there in the Shack with Potter and Granger. \emph{Don't be a fool! You need all the help you can get.} Picking up the horrid, evil thing that had helped destroy his life, Snape put it on, took a deep breath, and entered the tunnel.

It was a long way from the Willow into Hogsmeade. Unable to use a Lumos spell for fear of alerting Lupin or Black, Snape stumbled along in the darkness. The end of the tunnel was not light, but rather a lessening of the dark. There Snape crawled up through the floor and groped his way to the stairs. Voices were coming from the room above.

Snape recognized Granger's voice. "{\el} there have been only seven Animagi this century, and Pettigrew's name wasn't on the list—"

Lupin laughed. "Right again, Hermione! But the Ministry never knew that there used to be three unregistered Animagi running around Hogwarts."

Light began to dawn for Snape. It came nearly twenty years too late, but it was light. \emph{That's how they tracked me! It wasn't just the map!} He edged nearer.

Another voice broke in, a well-hated voice. Sirius Black's voice. "If you're going to tell the story, get a move on Remus. I've waited twelve years, I'm not going to wait much longer."

There is no longer any doubt. \emph{Black and Lupin are working together to kill Potter!}

\emph{What am I facing? Lupin must have a wand. Does Black? Are the children free or bound? Do they have their wands? Let Lupin keep talking, let him brag if he wants. It'll give me more time.} Snape put his hand on the knob of the door that separated him from the voices. Gently, quietly, he opened it. At the moment he managed to slip into the room, the door creaked, attracting Black's and Lupin's attention, but Snape, under the invisibility cloak, was already inside.

"This place is haunted!"

Snape looked towards the voice. \emph{Why is Weasley here? What's wrong with his leg? Did they attack Weasley to lure Potter in? This complicates things if the boy can't walk. We can't retreat down the tunnel—I have to finish it with both Black and Lupin here. I can't see if they have their wands, but if I move they'll hear me.}

Lupin was telling the students how he became a werewolf and the history of the Shack. \emph{I need to watch him closely. The moon is rising. He may transform any moment. Does he want to attack them as a werewolf? Will Potter and Granger be able to react quickly? If they can, it'll be three to two instead of two to one.} Snape didn't dare shift his position for fear of creaking boards making his presence known. Yet as he listened, he found the focus of his anger changing.

"{\el} Finally, in our fifth year, they managed it. They could each turn into a different animal at will." \emph{In our fifth year they separated me and Lily. They used the map, the cloak, and the shape shifting—two of the most popular boys in the school, surrounded by girls everywhere they went, and she was the only friend I had{\el} That must be how he's been getting by the dementors, too. And into the castle. We were looking for Sirius Black, not an animal.}

"{\el} there were near misses, many of them. We laughed about them{\el}" \emph{Careless. Still careless. Still taking chances with people's lives. Like tonight. Can't be bothered to take his medicine. The most important thing he has to do, and he can't be bothered. Where is the moon? Steady{\el} watch for the change.}

"{\el} felt guilty about betraying Dumbledore's trust{\el} forget my guilty feelings every time we sat down to plan our next month's adventure. And I haven't changed{\el}" \emph{I know you haven't. Even you admit it. Still deceiving Dumbledore, still more concerned with yourself than the safety of others.}

"{\el} I convinced myself that Sirius was getting into the school using Dark Arts he learned from Voldemort{\el} Snape's been right about me all along." \emph{There! Black was in the service of the Dark Lord! Even Lupin knows about it! He destroyed Lily, and now he wants to kill Lily's son to finish his Lord's work!}

"Snape? What's Snape got to do with it?"

"He's here, Sirius. He's teaching here as well{\el} you see, Sirius here played a trick on him which nearly killed him{\el}"

"It served him right," Black sneered.

\emph{Served me right? Served me right! Black still thinks I deserved to be killed because I wouldn't give in to his intimidation and threats? After all these years he still wants me dead! Wants Potter dead. Wants anyone dead who doesn't agree with him. Of course, killing people who get in your way is just second nature to Black. Look what he's doing now.}

"{\el} Jealous, I think, of James's talent on the Quidditch field{\el}"

\emph{You filthy bastard. How dare you tell Lily's son I cared anything about puffed-up Potter or Quidditch. You know what went on between us, and you dare, you dare to trivialize it by pretending it had anything to do with Quidditch! You petty little sneak. It isn't enough for you to glorify yourself, you have to tear everyone else down. You're going to kill him, and you still can't tell him the truth.}

"So that's why Snape doesn't like you, because he though you were in on the joke?" Potter asked.

\emph{Joke? One student tries to kill another and he thinks it's a joke? My death is a joke?} Unable to take any more, his voice dripping with sarcasm, Snape hissed, "That's right" as he pulled of the invisibility cloak, his wand pointing straight at Lupin, his attention still partly on the window where he could see the light of the rising moon.

Snape could feel his heart pounding, and his breathing was uneven. He tossed the cloak disdainfully to one side, still hating the sight and feel of it. "I found this at the base of the Whomping Willow. Very useful, Potter, I thank you. You're wondering perhaps how I knew you were here. I've just been to your office, Lupin. You forgot to take your potion tonight, so I took a gobletful along."

\emph{He doesn't care. He knows he's going to transform into a wild killer in a few minutes, and he doesn't care. Black doesn't care either, but now I know why. But what is wrong with the children? Don't they realize{\el} ? Maybe they don't know tonight is the full moon. But Lupin does.}

"Lying on your desk was a certain map. One glance at it told me all I needed to know. I saw you running along this passageway and out of sight. I've told the headmaster again and again that you're helping your old friend Black into the castle, Lupin, and here's the proof."

"Severus, you're making a mistake. You haven't heard everything{\el}"

\emph{Don't try to wiggle out of this. If you're helping Black now, maybe you were helping him twelve years ago. Maybe you helped kill Lily.} "Two more for Azkaban tonight. I shall be interested to see how Dumbledore takes this{\el}" \emph{Refusing to listen, refusing to even consider the possibility. Insisting Lupin was safe when even now he's trying to buy time to allow the transformation{\el}}

"You fool. Is a schoolboy grudge worth putting an innocent man back into Azkaban?"

\emph{You filthy lying toad! Jealous about Quidditch and schoolboy grudges! Do you really not have a clue?} Then, suddenly, it was crystal clear. Every piece fell into place. Sirius Black and Bella Black—they were working together all along! Servants of the Dark Lord even in school. \emph{You were pushing me into her hands! You wanted me to be a Death Eater! You gave me to Bella!}

Cords leapt from Snape's wand at his unspoken command, binding the werewolf and pulling him to the floor. Lily's murderer charged, but Snape was faster, his wand now practically touching Black's forehead. Never in his life had he so much wanted to kill someone.

"Give me a reason," whispered Snape, cold fury now icing his voice. "Give me a reason to do it, and I swear I will."

A voice behind Snape filtered through his rage. "Professor{\el} ?" He didn't hear all the words, but twelve years of Hogwarts took hold, and he found himself shifting into automatic gear. "Miss Granger, you are already facing suspension from this school. You, Potter, and Weasley are out-of-bounds in the company of a convicted murderer and a werewolf. For once in your life, hold your tongue."

She would not, but kept pushing, pushing{\el} and he exploded. "Keep quiet you stupid girl!" \emph{This man will kill both of us given the smallest chance!} "Don't talk about what you don't understand!"

He concentrated on Black again. \emph{You gave me to Bella. Gave me{\el} sent me out to hear a prophecy and set the hunt afoot, then you sold her{\el} sold her{\el}} "Vengeance is very sweet. How I hoped I would be the one to catch you{\el}" \emph{For Lily. Vengeance for Lily.}

"{\el} I'll come quietly{\el}"

\emph{So you can go on deceiving Dumbledore. So Dumbledore will let you slip away again. }"Up to the castle? I don't think we need to go that far. All I have to do is call the dementors once we get out of the Willow{\el}" \emph{I can even face dementors for the satisfaction of knowing you're back in Azkaban.} "Come on, all of you."

Then, inexplicably, Lily's son was blocking the way. James was blocking the way. Standing up for his betrayer. Blind to the end. Sacrificing wife, child, to the sham friendship of a psychopathic killer{\el}

"Get out of the way, Potter."

"You're pathetic! Just because they made a fool of you at school{\el} !"

"I will not be spoken to like that!" \emph{Lupin's lies. Lupin's lies from Potter's mouth.} "Like father, like son{\el} You'd have died like your father, too arrogant to believe you might be mistaken in Black. Get out of the way!"

They took him the way Potter and Black had always taken him. While he faced one, the other hit him from behind. Snape's mind registered that Potter raised his wand, but even as the spell struck him, another slammed into his back, and the combined force flung him into the wall like a rag doll thrown by an angry child.

Blackness engulfed Snape before his body touched the floor.

\sbreak

Consciousness came gradually, and the first thing he was really aware of was a splitting headache. Slowly, Snape opened his eyes. Moonlit dark surrounded him and he was—suspended in midair like a broken marionette. \emph{Must be{\el} Mobilicorpus. Wand. No wand. Think. Concentrate.} Snape focused on his invisible bonds, thought the word Liberacorpus, and collapsed onto the grass.

His head was spinning. Cautiously lifting his hand to the side of his head, Snape found his hair matted with dried blood. His forehead, when he probed the skin with tentative fingers, felt tender and bruised, as if someone had been beating him on the head with a stick. Who? There were students. And Lupin. And{\el}

Adrenaline shot through him. Alert at once, Snape glanced around, but there was no one. No, there was someone. Someone lying on the grass near the Willow, unconscious. He crept to the other's side. Weasley. Immediately Snape checked the boy's breathing and pulse. A spell. \emph{Have to get him back to the castle. Madam Pomfrey.}

Snape stood somewhat groggily, shaking his head to clear his mind. He looked around and found three wands, his own, one he recognized as Lupin's, and one that must be Weasley's. He was about to conjure a stretcher when he saw the faint light from the lake. Someone was casting a spell—a patronus spell. Someone needed help. He started toward the lake.

The cold of the dementors was like a barrier. \emph{I can't fight them. I've never been able to produce a strong patronus. It won't do any good.} Still Snape forced himself forward. Potter and Granger were out there somewhere. Black, too, but as an animagus who could escape dementors. Lupin, but he was a werewolf. \emph{Potter and Granger. It must be Potter and Granger.}

Then, from across the water, there came another patronus. A patronus whose light grew and radiated in front of it like a beacon of strength. A patronus that lit the night and paled the moon. Below in the darkness the dementors hesitated, quailed, and at last fled. Snape stood, transfixed at the image of the radiant creature that paused, stamping its hooves, then returned to its creator across the water. \emph{A stag. Potter conjured a stag at the Quidditch match. Was that Potter?}

But it could not have been Potter, for Potter was lying unconscious near Black and Granger there where the dementors had attacked. Snape tried to puzzle it out, but his head was aching and he felt nauseous. Things seemed blurred and uncertain, and he wanted to lie down and sleep.

Instead he returned to Weasley, conjured the stretcher, and lifted Weasley onto it. Moving the stretcher in front of him, he then went down to the lake and conjured three more, one by one lifting Granger, Potter, and Black, the last of whom he bound to the stretcher with magical cords.

Four stretchers were a lot to handle, but Snape managed to maneuver them up the hill, into the castle, and to the hospital wing on the first floor. Madam Pomfrey went into a flurry of activity. She was asking him questions, questions he didn't totally understand because he was so sleepy, and feeling so sick{\el}

\sbreak

"He has a concussion. He's fine now, but it's a good thing he got up here to the infirmary. If he'd fallen asleep there{\el}"

"Thank you, Madam Pomfrey. I shall not keep you from your other patients." There was movement, and then Dumbledore's voice. "Severus? Are you awake?"

"Yes, Professor. I{\el} are the students all right?"

"Fine, fine."

"And Black?"

"He's in custody. You are not to fret about this. You have had quite enough trauma to the head this evening."

"Professor, there was someone else out there. Someone who conjured a powerful patronus to drive the dementors away. It looked{\el} it looked like the patronus that Potter conjured at the game against Ravenclaw."

"Indeed?"

"Do you know who's out there? Who might have done it?"

"Severus, listen carefully. I do not wish you to speak of this patronus to anyone. Not to anyone. It is very important that this remain a hidden thing. Like the mind speech."

"Yes, Professor."

Footsteps approached and Cornelius Fudge appeared. "Ah, excellent Professor Snape. You're awake and, I trust, well? Do you think, Albus, I might speak with Professor Snape for a few moments? It's about the children's story and this Black business."

"Black?" Snape sat up instantly. "Where's Black?"

"In custody in the West Tower. Interesting thing—the children insist he's innocent."

Dumbledore watched Snape with concern in his eyes. "Are you certain you feel all right, Severus? You do not need to discuss Sirius Black with the Minister right this minute."

"Where is Black?"

"He is in custody. That is what I mean, Cornelius. That is the third time he's asked that question. How does your head feel, Severus?"

"It hurts. Especially on this side." Snape touched the spot where his head had been bleeding.

"Still," said Fudge, "I do have to ask a couple of things. Professor Snape, during the time you were in the Shrieking Shack, did anyone talk about Peter Pettigrew?"

"Pettigrew? Yes, they talked about learning how to become animagi, and Pettigrew was Wormtail."

"Did they say anything about Pettigrew being the Potters' secret-keeper?"

"No. I don't think so. Why? Black was the secret-keeper." Some parts of the evening were very clear, others foggy. Snape was relieved the Minister was asking about the clear parts.

"The children are saying that Pettigrew betrayed the Potters to{\el} You-Know-Who."

"No, Black was the one. In fact, Lupin said that he assumed Black got into the castle using dark magic he learned from the Dark{\el} from You-Know-Who." Snape looked around in sudden agitation. "Where's Lupin? He didn't take his medicine today. He's out there, maybe attacking people."

"Do not worry about Professor Lupin," said Dumbledore quickly. "He will be all right."

"I'm not worried about Lupin!" Snape exploded, jumping to his feet. "You might try thinking of someone else for a change! Like the people in Hogsmeade who could be attacked by a rampaging werewolf. Or muggles in nearby towns. Do you know how far he could travel in a night?"

"Werewolf?" Fudge glanced at Dumbledore, clearly puzzled. "Do we have a werewolf to deal with, too?"

"Now, Cornelius, Severus is suffering from the effects of a blow to the head. I am sure that by tomorrow morning{\el}"

"I'm not crazy! Lupin is out there—dangerous to everyone around him—and Black{\el}"

"Sirius Black is going back to Azkaban tomorrow, Professor," said Fudge gently. "You captured him, you know."

"I did? No, I don't think{\el}"

"Indeed. Captured him and rescued all three children. Brought them up here on stretchers. An amazing piece of work." Fudge smiled benignly. "I think you should be commended. The children are confused. One was stupefied and the other two attacked by dementors. It's enough to confuse anyone."

Dumbledore raised a hand. "Would you be so kind as to stay with Professor Snape for a few minutes, Cornelius? I wish to speak with Black. Maybe you could walk around for a bit. A little air is good for clearing the head." He walked quietly out of the room.

The stroll with Fudge did help clear Snape's head somewhat, and the Minister was kind enough to help him with some of the points where his memory was still fuzzy.

"It's good to have you as a witness to all of this, especially with what the children are saying. After all, it really isn't possible that we would have incarcerated the wrong person all these years. You did say the children were placed under a Confundus Charm?"

"I did?"

"I'm sure that's what you said. And Black attacked you."

"No, I really think that was Potter."

Fudge changed the subject slightly. "Why was Black there at all?"

The fuzziness was instantly gone. "He was a servant of the Dark Lord. He betrayed the Potters twelve years ago, and came back to Hogwarts to finish the job. He and Lupin together. Lupin was working on Potter, trying to get him to trust{\el}"

"You said it was a Confundus Charm. You recognized it at once."

"I did?"

Slowly, with the Minister's help, the unclear parts were all coming back, clearer and more focused with each passing moment. Potter, Weasley, and Granger had been confounded by Black and Lupin, tricked into believing Black innocent and blaming the dead Pettigrew. It all made sense.

Only two things didn't fit. For some reason the Minister thought Black had knocked him out, and that he, Snape, had captured Black in a fight. Snape was fairly sure that wasn't true, but he wasn't sure where the truth was.

And of course the—thing—that Dumbledore had told him not to mention.

Someone was approaching from behind. Snape turned to face Macnair, whose black mustache bristled alarmingly. "How did the execution go?" Snape asked, trying to keep the bitterness out of his voice.

Macnair looked at him oddly. "Thought you'd heard. Wasn't one. Minister, did you need me for something?"

"Ah yes, Macnair," said Fudge. "Get down to the perimeter and bring back one of the dementors. We need a `kiss' performed tonight before we take our prisoner back to Azkaban."

"Kiss? You're doing that here? Dumbledore won't be pleased." That said, Macnair left on his task.

"Was he serious?" asked Snape. "There was no execution? I understood that the hippogriff lost the appeal."

"He did," replied Fudge, "but when we went down there to carry out the sentence, the beast had disappeared."

"Hagrid let him escape?"

"No, odd thing about that. The beast was chained up when we arrived, the three of us. And Dumbledore. We went into Hagrid's hut to finish the paperwork, and when we came out the beast was gone. Hagrid was with us the whole time. No one else was there."

"Potter," muttered Snape. "You didn't see{\el} No, of course you didn't see him. That's what they were doing down there."

"Come again?"

"No, it's nothing."

"Anyway, it's been a shocking business{\el} shocking{\el} miracle none of them died{\el} it was lucky you were there, Snape{\el}"

"Thank you, Minister."

"Order of Merlin, Second Class, I'd say. First Class, if I can wangle it."

\emph{For conjuring four stretchers? I'm sure I didn't{\el}} "Thank you very much indeed, Minister."

"That is a nasty cut you've got there{\el} Black's work, I suppose?"

\emph{We talked about this. I think we talked about this.} "As a matter of fact, it was Potter, Weasley, and Granger, Minister."

"No!"

Now Snape felt more sure of himself. He'd gone over the story with{\el} Fudge? "Black had bewitched them. I saw it immediately. A Confundus Charm, to judge by their behavior."

It was coming back now. Potter was getting too used to having the glory. First with the Stone and Quirrell, then with the basilisk in the Chamber of Secrets. This year it was going to be the single-handed capture of Sirius Black. He put everybody at risk with his thirst for fame. He needed to remember he was just another student in the school, not the center of the whole universe.

"What amazes me most," Fudge was saying, "is the behavior of the dementors{\el} you've really no idea what made them retreat, Snape?"

"No, Minister{\el}" \emph{That is most certainly the truth. The only patronus I've seen even remotely like that is Potter's, and he was unconscious. Dumbledore said{\el}} "by the time I had come 'round they were heading back to their positions at the entrance{\el}"

They talked a moment more, going back over the events that were now well fixed in Snape's mind. Suddenly there was a yell from inside the ward where the children were. Both men ran to the sound.

Potter was awake and raving that Black was innocent. Raving about seeing Peter Pettigrew. Raving that the Weasleys' rat—a longtime resident of Hogwarts—was somehow Peter Pettigrew. Snape's head was beginning to throb again.

Madam Pomfrey was trying to calm Potter with chocolate when Dumbledore returned and asked to speak with Potter in private. "I've just been talking to Sirius Black{\el}"

A terrible sense of foreboding was growing in Snape. Dumbledore had the air of a man about to turn the world on its head. "You surely don't believe a word of Black's story?" Snape whispered. He held Dumbledore's gaze. \emph{Don't do this. Don't let him go. He killed her. He'll kill again.}

Dumbledore's voice, faint and clear, sounded in Snape's head. \emph{I do not believe that Sirius is a killer, nor that he deserves the punishment he has received.}

Snape stepped closer to whisper, "Sirius Black showed he was capable of murder at the age of sixteen. You haven't forgotten that, Headmaster? You haven't forgotten that he once tried to kill me?"

"My memory is as good as it ever was, Severus."

It was like being slapped in the face. Raging inside, Snape turned and strode out of the ward, Fudge behind him.

"I don't know that it's good for you to be worked up like this," said Fudge as he caught up to Snape, "considering your injuries and all."

"I'll be fine once this headache goes away. I only hope Dumbledore's not going to make difficulties. The Kiss will be performed immediately?"

"As soon as Macnair returns with the dementors." Fudge rambled on, clearly reveling in the thought of the favorable publicity the Ministry was going to receive for the successful capture of Black.

Dumbledore joined them a few minutes later, as did Macnair, bringing a dementor with him. Snape moved quickly away from them, watching nervously as Fudge, Macnair, and the dementor followed Dumbledore upstairs.

It was almost over. \emph{When Dumbledore told me all those years ago that Black betrayed you, Lily, I promised that if he ever got out of Azkaban I would kill him myself. I didn't keep that promise—you don't kill an unconscious man—but at least we have the next best thing. We can close the book and write `finished' to the story. Black will never be part of my life again.} Snape walked over to the window and watched the full moon, Lily's moon, waiting for word from above.

Word came sooner than expected. Fudge came hurrying down the stairs, Macnair and Dumbledore behind him, hollering, "An owl! We send an owl to the Ministry at once! Macnair, round up some of the dementors! He can't have gotten far!"

Snape strode forward, blocking the Minister's path. "What happened? Black's escaped!" He looked past Fudge to Dumbledore. The Headmaster's expression was inscrutable. Things were clicking into place, and the volcano was nearing critical.

An invisibility cloak, an escaped hippogriff, and a prisoner who suddenly vanishes from a tower. "Potter!" Snape hissed, and headed back toward the hospital wing at a run. Fudge and Dumbledore caught up to him and tried to slow him, but Snape was beside himself. "Potter is responsible for this! He won't get away with it this time!"

Fudge was trying to be reasonable. "He must have disapparated, Severus. We should have left somebody in the room with him. When this gets out{\el}"

"He didn't disapparate! You can't apparate or disapparate inside this castle! This. Has. Something. To. Do. With. Potter!"

Dumbledore chimed in as they approached the door to the ward. "Severus—be reasonable—Harry has been locked up{\el}"

Snape's wand was out and pointed at the door with murderous fury. It crashed open in front of them to reveal a shocked Madam Pomfrey and the three students. "Out with it, Potter! What did you do?" Snape yelled at the mock-innocent face—James's face—that watched his approach with such evident satisfaction. "They helped him escape, I know it!" Snape continued in uncontrolled rage as both Madam Pomfrey and the Minister tried vainly to calm him down. "You don't know Potter! He did it, I know he did it{\el}"

Dumbledore's face was grave. "That will do, Severus. Think about what you are saying. This door has been locked since I left the ward ten minutes ago. Unless you are suggesting that Harry and Hermione are able to be in two places at once, I'm afraid I don't see any point in troubling them further."

It was like a bucket of cold water. Snape stared at Dumbledore in shock. \emph{Hermione? I never mentioned Granger. Potter yes, but Granger too? You lying, deceitful old man! You're laughing at me. The three of you are laughing at me.}

There was no recourse. There was no justice. Snape wheeled and stormed out of the room and down the stairs.

Out the great double doors into the dark, wand still in hand—Snape wasn't sure where he was going or what he wanted to do until he was halfway to Hagrid's hut. Then it obsessed him. He left the path and headed straight down the hill toward the Whomping Willow. As he neared the Forbidden Forest, he began to yell.

"Lupin! Lupin! You miserable son of a she-wolf! Come out and face me! For once in your life, face me!"

There was no answer—there couldn't be an answer. But somewhere in the forest there had to be a werewolf, and Snape had to do something or he would go insane. Unwary, uncaring of dementors or of anything else, Snape plunged into the forest. "Lupin!" he screamed, "Come on, Lupin! Come and get me, you cowardly cur!"

The pain in his head increased—it was pounding now like a second heartbeat, and Snape staggered a little, clutching at a tree for support. "Lupin!" he shouted again, and a shape loomed up to his left. It wasn't Lupin. It was Hagrid.

Snape spun at the sound of movement, his wand pointing at Hagrid's chest. "Don't stop me!" he hissed at Hagrid. "This has nothing to do with you. Get out. Leave me to my own business."

"Your business don't include hunting in the forest. Specially not what you're hunting. You come along with me now. You need rest and somewhat t' eat and drink."

"Stop nursemaiding me! There's a job to do. Nobody else 'll do it—nobody else cares—unfinished business—so I have to{\el}" Hagrid took a step closer and Snape screamed, \emph{"Stupefy!"}

The spell bounced off Hagrid's chest. "Now you know that won't work 'less ya can concentrate better 'n what ya can now." Snape stumbled forward, and Hagrid caught him around the waist to support him, taking his wand at the same time. "I ought t' pick ya up and carry ya, but I doubt ya'd thank me for it. Lets see if ya can walk t' my place."

They progressed slowly, and by the time they reached the hut Snape's breath was coming in gasping sobs. He was utterly exhausted, and the throbbing in his head overrode everything else. Hagrid wrapped him in a blanket and sat him in front of the fire supported by enormous pillows. After a few sips from a cup of warmed mead, Snape fell asleep.

When he woke around daybreak, Dumbledore was sitting at Hagrid's table drinking tea and chatting. "Ah, Severus. Good to see you awake. How are you feeling?"

"Terrible. Why are you here?"

"Hagrid sent word by Fang that you had turned up with him. I came to make certain you were all right."

"It's a little late to start caring, isn't it?"

"I suppose I deserve that. Now, I want you to consider that you might be wrong about Sirius."

"I knew you weren't here because you cared about me."

"This may end up being more about you than you realize. Tell me why you have trouble believing that Sirius may have been imprisoned unjustly."

Snape thought for a moment. It helped that he no longer had a headache. "It makes no sense. Not one iota of the story makes sense. First, who in his right mind would ever suggest Peter Pettigrew as a secret-keeper for anything? Pettigrew couldn't stand up to a large cat even before he became an animagus. Only someone who wanted a secret revealed would've made Pettigrew its keeper.

\textooquote Then there's the explosion that killed him. Black's magic was powerful enough to do that, but Pettigrew's? And why stay a rat for twelve years? A Weasley rat, at that? Who was he afraid of? Black was in prison, everyone else thought him dead, the Dark Lord was gone{\el} Why stay a rat at Hogwarts when he could go off and be a wizard in France, or America? Even Pettigrew wasn't that pitiful."

Dumbledore nodded. "All very logical. Yet the children saw Peter."

"And I could make them see a cow jump over the moon. Illusion isn't that hard."

"So you will not be convinced?"

"Headmaster, it isn't believable."

"Then we must leave it at that. I only ask that you keep your mind open to the possibility—in the future, of course—that the illogical and the unreasonable may sometimes be the truth."

Snape did not reply.

"Come then, Severus. It is time to be going. Breakfast will be served soon, and we do not want to be too late."

The three of them walked together up the hill to the Castle.

Cornelius Fudge was at breakfast that morning, seated next to Dumbledore. He came over to speak briefly to Snape during the meal.

"Well it's good to see you looking better than you did last night, Professor. We were worried about that bump on the head. Clearing up now, though? Good. You know, the Headmaster was explaining to me last night after you left us, about Professor Lupin and how he was probably trying to protect the children from Black as well. We're not planning to press charges."

"So the Ministry approves of uncontrolled werewolves roaming the grounds of a school?"

"Werewolf?" exclaimed Professor Flitwick, who couldn't help overhearing. "Is there a werewolf at Hogwarts?" Others nearby were now listening.

Before Dumbledore could stop him, Fudge was explaining. "We're just talking about Professor Lupin is all. Terrible to have a problem like that."

Snape glanced down the table. This time it was Dumbledore who was having trouble controlling his anger. Snape was not sympathetic.

Around noon, Snape took a gobletful of the calming potion up to Lupin, who was shut in his office. "I think I should stay to make sure you actually drink this one."

"Don't treat me like an irresponsible child."

"You were responsible yesterday? I recall that in the Shack both you and I mentioned this potion, and it didn't jog your memory at all that you still needed to take it. How many times have you transformed, Lupin? Well over three hundred, no? How could you not remember it was a full moon?"

"I'm sorry, Severus, that you missed your chance to get the Order of Merlin. I hear Fudge has withdrawn the offer since I'm not guilty and Sirius escaped."

"Typical. You told Potter I was jealous of his father's Quidditch skills. Are you now going to tell him I'm angry because I didn't get a medal? Is it because you're so petty yourself that you assign petty motives to others?"

"I'm not going to quarrel with you."

"I'm still going to wait here until you drink that."

\sbreak

It was a few more days until the end of the term. It couldn't come quickly enough for Snape. Even though Lupin left early and the dementors were gone, there was nothing at Hogwarts that could make Snape feel anything but depressed and bitter. There was some relief watching the train pull away in the distance—some, but not enough.

\emph{Last year this time I was telling myself that things couldn't get any worse. How is it possible to be so wrong? Ever since Potter came to this school, each year is worse than the one before. I hate to imagine what next year will bring.}

Dumbledore greeted him when Snape reentered the castle. They were on speaking terms again, though it was an effort for Snape, and he rather imagined it was an effort for the headmaster as well.

"Another year under our belts," said Dumbledore. "I am certain you are pleased to say goodbye to that one."

"Pleased hardly does justice to the feeling."

"What will you do during the summer holidays."

"Stay as far from here as I can."

"An excellent idea. That way you will be well rested for the autumn term." Dumbledore continued upstairs, leaving Snape in the entrance hall.

\emph{Do you know what really rankles, Headmaster? There are other prisons besides Azkaban. Other prisoners with life sentences. What really rankles is that Sirius Black escaped his prison. He's free.}

Snape walked quietly into the dungeon of the castle, to store his potions ingredients and to lock up his office and his rooms for the coming summer.


