% A Difference in the Family: The Snape Chronicles (Rannaro)
% Yes, That Is My Job

\chapter{Preparations}

\subsection{Saturday, November 4, 1995 (three days before the full moon)}

The following Saturday was the Quidditch match. The whole school was looking forward to it, and Snape was no exception.

Snape was up early on Saturday. It was cold and overcast, actually rather good Quidditch weather. There was a high level of excitement as Snape made his way to the Great Hall. Slytherin students were decked out in green and silver, while Gryffindor sported their own red and gold. Some of the Ravenclaw and Hufflepuff students wore red and gold, too, but most were less partisan for Gryffindor than they'd been in earlier years.

Little groups of Slytherins were laughing and talking around their table, and Snape noticed they were wearing badges. A little like last year when they got the badges supporting Diggory in the Triwizard Tournament. A close look showed him the badges carried a crown with the words `Weasley is our King' inscribed inside.

\emph{Weasley? He's the new Gryffindor Keeper, isn't he? I wonder what this is about.} A glance down the table made it clear that the source of the badges was Malfoy. Malfoy was the Slytherin Seeker, and his two goons Crabbe and Goyle had just been made Beaters. \emph{I need to check out the parents of Bletchley, Montague, Warrington, and Pucey. We may be approaching an all Death Eater Quidditch team here.}

Once the game got started, the meaning of the badges became clear. Weasley was nervous and intimidated by the Slytherin team and the chanting from the Slytherin crowd. `Weasley cannot save a thing, He cannot block a single thing{\el}' rose in a well-practiced roar from the green and silver stands.

Snape was astounded, and immensely gratified. The students had been working behind the scenes on their anti-Weasley performance, and it was a powerful and unified show of house spirit, with flags and banners waving and the song rising as if it was one huge voice. Slytherin house by itself overpowered in chants and cheers Gryffindor, Ravenclaw, and Hufflepuff put together. It was rousing.

And the game did not let them down. With well-practiced skill, the Slytherin team tore into Gryffindor's defense and landed score after score. The board rang up forty points for Slytherin before Gryffindor managed to score once. Slytherin was outflying, outplaying, outscoring Gryffindor in every part of the game and then{\el}

And then it was over. Both Seekers located the Snitch almost simultaneously, dove groundwards, and just before contact with the grass, Potter had the Snitch, with Malfoy so close to him that their hands were touching at the moment the Snitch was caught. The whole stadium rose to its feet in the last seconds, Snape with them, and then Gryffindor's stands erupted in cheers.

What happened next was not clear. It looked like an errant Bludger hit Potter, and Malfoy was saying something as the two teams converged on the Seekers, and then Potter and one of the Weasley twins charged Malfoy, Malfoy was on the ground clutching his stomach, and Potter was hitting him. Then Potter had been bowled over backwards by an Impedimenta charm cast by{\el} Madam Hooch?

Snape clambered down from the stands and ran to the center of the pitch where he knelt next to Malfoy. A quick look into the boy's eyes told Snape that he really was in pain. Potter had punched him in the stomach, hard, and in the nose as well. Snape had vivid memories of what that felt like, having been punched in the stomach himself. He conjured a stretcher and supervised the other members of his Quidditch team as they carefully lifted Malfoy onto the stretcher, and started moving him up the hill to the hospital wing and Madam Pomfrey.

It was only then that he looked around and noted that the Gryffindor team had disappeared from the pitch, as had McGonagall. \emph{She'll be angrier about this than I am. I would not like to be those students facing her wrath. I'll leave their punishment to her and find out about it at dinner.} As it was, he had to calm the team going up the hill, for Bletchley and Montague wanted to go after Potter and Weasley right then and there, and Snape had to talk them out of it.

\emph{Why does Gryffindor always have to react with physical violence?}

Supper was tense, and not just because of the animosity between the two houses. Gryffindor was somber, reacting to the news that their Seeker and Beaters had been banned from playing Quidditch for the rest of their lives. Slytherin was in an `it serves you right' mood, forcing Snape to threaten dire punishment to anyone who taunted Gryffindor. The other two houses were simply stunned.

And then there was McGonagall.

"Educational Decree Twenty-five! She's taking all authority out of our hands and giving it to herself! Not only does she have the power to determine punishments and sanctions, she has the authority to alter the punishments we determine for our students! If I ever get my hands on Fudge{\el}"

"I take it there's no process of review for her decisions."

"Review her decisions? Severus, the woman thinks she's infallible! Infallible and omniscient!"

"And now omnipotent by the sound of it."

Sprout and Flitwick nodded glumly. It was the four heads of houses who were most affected by the new decree, since they had the most control over the individual students. "What do we do now?" Sprout asked.

"Think about it very carefully. This requires gathering information and planning. We can't let that woman take over the school like this."

Then Umbridge entered the Great Hall for dinner, and the four teachers moved apart. Snape couldn't have continued the conversation for very long in any case. He had to go to Croydon, and this time he would have news to report.

Thus it was that Snape did not learn until nearly midnight that Hagrid had returned to Hogwarts.

\sbreak

Snape had no illusions about his meeting that night with the Dark Lord. He would have to be persuasive and be prepared to think fast.

On arrival at Croydon, Snape asked for an interview. It was granted an hour later. Once again, no one was there but Snape.

"Tell us of the situation at Hogwarts."

"The Lady is taking more power to herself."

"Describe that power."

"She has now been given the authority to determine all punishments for students, and to overrule the other teachers if she doesn't agree with what they have decided."

"This has little bearing on our main purpose."

"That is true, Lord, except that the other teachers are being pushed in the direction of rebellion. They resent her increased authority deeply."

"That is not what we wish. We wish you to explain why you think this was wisely done."

"It was not planned by our people, but it can rebound in our favor. The most important element of what is happening is that Dumbledore is not perceived as being part of it. The teachers wonder at his absence and his lack of action. They're beginning to doubt whether he has the will or the spirit to defend his own position. If they decide to act without consulting him, it means they've lost faith. Which also means they won't believe his stories about your return."

"We see. This is an interesting, even though unplanned development. Is there anything else?"

"Only that the students, too, seem to be rebelling against the Lady. Also without the assistance of Dumbledore."

"You will continue to keep us informed."

"Yes, Lord. Thank you, Lord."

Snape spent the rest of the evening with his self-defense classes and checking his simmering potions. It was too early to really tell with either the Polyjuice Potion or the Veritaserum, both of which took over a month to brew, but Snape had high hopes.

On his arrival back in Hogsmeade, Snape was met by an unseasonably early snowstorm and—Hagrid.

"What are you doing here? And more to the point, where have you been?"

"That's right Professor. Tell me how much ya missed me and were worried about me, and how ya couldn't live without my checking up on yer diet every two weeks. Go on. Tell me."

"I missed you and was worried about you. You can forget the diet part, though. I watch what I eat. Where were you?"

"We can talk about that later. Right now, I'm t' tell ya not t' send a patronus t' Dumbledore. Seems someone's watching. Seems someone's dying t' catch ya at something. Best not t' give them ammunition."

"Understood. Can you let me in the gate?"

"Well I'd be a poor groundskeeper an' I couldn't. What d' ya think Dumbledore sent me down here for?"

They walked to the gate, which Hagrid opened, then went their separate ways—Hagrid to his hut, and Snape to the castle. "Remember," Snape said as they parted. "You have to tell me everything."

A couple of inches of snow scrunched under Snape's feet as he climbed the hill, and his feet were soon wet and cold. \emph{Luckily the falling snow will cover my footprints.} No one was watching in the entrance hall. \emph{If she wanted to know whether or not I was in tonight, it wouldn't be so hard. All she had to do was knock on the office door to know I was out. Before I talk to her tomorrow, I need to establish an ironclad alibi.}

The alibi turned out to be easier than Snape had thought. Even as he approached the short, narrow flight of stairs that led to the dungeons, Sprout's voice spoke his name.

"Severus, what are you doing up so late?"

"Checking the snowfall. And I might ask you the same question."

"I'm going back out to the greenhouses. I've shut all the roof and wall ventilation ports, but it's still terribly cold in there, and the outdoor frames need insulation. There're also some annuals that'll be frostbitten and useless by tomorrow morning, and perennials that need tenting. I could use some help, and with your knowledge of plants, you'd know right away what needs doing."

"My pleasure. Just point me where you want me to go. When did the snow start?"

Sprout looked at him quizzically. "About ten o'clock. Where were you, that you don't know that? On second thought, don't tell me. I might not want to know."

"Best you don't. You could do me a favor though."

They were outside now and heading for the greenhouses. "What favor? I'm not promising until I know."

"If anyone asks, I went out to tend the plants with you as soon as the snow started. I was coming downstairs from the Astronomy tower, and you caught me in the entrance hall on your way out."

"Oooo{\el} deception. May I assume that `anyone' means a certain particular one?"

"I love the way you jump right to the crux of the matter."

"Well, since you've been here since the snow started, you already know what needs doing. You get out into the field on the east slope and gather up the plants that are dying in the frost so we can start preserving them tonight."

"Aye-aye, captain. I'll bring them to the greenhouses."

The two separated and went about the business of saving Hogwarts's herb crop. A job that would have been impossibly large for two muggles was difficult but doable for a witch and a wizard and a pair of wands. While Sprout warmed the greenhouses and piled straw around the frames, Snape bundled piles of annual plants, sending them up to the herbology workrooms, and brought more straw down to the planted areas to shield the perennials. Some he covered in paper tents as protection from the cold air, and others that could weather a snowstorm easily, he left alone.

The plants now safe, Snape and Sprout met in the workroom to begin the lengthy sorting, chopping, and boiling of the frostbitten harvest to preserve their essences for potion-making. Outside the snow continued falling—it was now a foot and a half deep, and the stars wheeled overhead on their way toward morning, but neither Sprout nor Snape had any intention of deserting their task. The cold had damaged the cellular structure of the cuttings, and any delay in processing them meant loss.

By dawn it seemed that every pot, pan, crock, cauldron, or kettle that Sprout had was cheerfully bubbling over one of several flames. The two professors sat back and surveyed the results of their industry, only just now realizing how tired they were. It was a contented tiredness, though, for they knew the job had been well done.

Carefully locking the door to the workroom, Sprout and Snape made their way together to the Great Hall where Sunday breakfast was just being laid out. "I'm famished!" Sprout cried, and made a beeline to the food. Snape followed, a bit more restrained, but he too was hungry, and the smell of the food was alluring.

"Whatever you two were doing, it's certainly given Sprout an appetite," commented McGonagall as Snape took his place at the table.

"Herbs," Snape explained through a mouthful of kipper. "Snow. Cold."

"Ah! I'd not thought of that. It takes a gardener to realize that there's more to snow than fun throwing snowballs. Were the two of you out all night?"

"Mmmm{\el}" Snape swallowed and was able to speak more coherently. "After covering the plants and bringing in the damaged ones, we had to start the preserving process or they'd have been ruined anyway. We just finished."

"Where were you last night?" asked an accusing voice next to Snape's ear. He turned to look Umbridge in the eyes.

"Saving Hogwarts's potions material," Snape replied. "We could have used some help, actually, Sprout and I."

"Why didn't you ask for it?"

"No one qualified enough. Except for us, of course."

"What about me."

"You never sat for a NEWT in either Potions or Herbology, much less passed one. That's definitely under-qualified."

"How do you know that?" Umbridge demanded, her face purpling.

"I checked. Hogwarts has files, too, you know." And Snape smiled sweetly at Umbridge.

After breakfast, since it was Sunday, Snape went to his own rooms, lay down on his bed, and fell quickly asleep. He woke again around one o'clock, which on Sundays was in the middle of the lunch period. He went to the Great Hall for a quick bite to eat, then decided to go down the hill to see Hagrid.

Hagrid at first didn't want to open the door. After several I-know-you're-in-theres, three open-this-door-nows, and a loud I-don't-need-a-key-to-bash-down-pine, the door opened and Snape was admitted.

"Tea?" said Hagrid, as if they'd not just had a confrontation about Snape's being allowed to visit at all.

"What the hell happened to you?" Snape countered.

Hagrid turned away, hiding his face in the ceremony of pouring tea. "It's nothing. We went up t' talk t', well, you know{\el} giants{\el} and they wasn't always so hospitable."

"No. You're lying. Some of those cuts and bruises are no more than thirty-six hours old. Some less. You got them shortly before you arrived here, and maybe{\el}"—Snape looked closely—"maybe even in the last hour or so. There's a slight swelling there that's going to be a bruise tomorrow."

"Can't hide things from you, can I? Ya read minds, ya do. Sneaky trick."

"I'm not reading your mind, Hagrid. I'm a healer. I know bruises and cuts. Something is beating on you, and you don't want to tell me what it is."

"Well then, maybe ya should go."

"Well then, maybe you should tell me what's happening."

"Well it ain't like anyone could stay up there with what was going on."

"Well that sounds like you brought one of them back with you."

"One o' them? Ya ain't getting racist too, are ya?"

"Progress! You brought a giant back with you and are now defensive about his presence. You're afraid others will reject him for what he is, and he is so close to what they think that even you're not sure he'll pass inspection. And you are the most obstinate, pigheaded, self-absorbed{\el}"

"Ya keep talking like that, and I'm going t' pound ya{\el}"

"Who is he, Hagrid?"

"How d' ya know it ain't a she?"

Snape paused. How did he know it wasn't a giantess? "Well{\el} I{\el} well{\el} She-giants don't beat you up like that!"

"A lot you know about she-giants! They ain't worth nothing if they don't beat ya up!"

This was incontrovertible. Snape retreated. "All right, you have a little friend hidden back there in the woods. Just as long as you're okay, I'll leave you alone. Forget I said anything."

"You just remember that, Mr.~Big Shot wants t' jump all over everyone else's fun."

"I'll leave you alone. I will, I swear I will. I just thought{\el}"

"Don't think. Ya think too much. So do them others. Ya just don't let them think for ya, see. You don't think, and they don't think, and we're all happy. I catch ya thinking, and I'll sit on ya 'til yer circulation stops and ya can't walk no more. Got me?"

By this time, Snape was backing quickly away. This was a Hagrid he'd never seen before. This was a Hagrid to set against Umbridge, and Snape was already trying to figure out how to do it. \emph{Not today, surely, and not tomorrow either. Not for many days. But someday, get Umbridge down here checking on this giant{\el}ess, and we're going to have the Donnybrook of all Donnybrooks.}

"Not to worry, Hagrid. I'm leaving, and I won't disturb you further. If you need anything, let me know."

Snape made his way back up the hill to his office and room. \emph{Too much in too short a time. I need some rest. I need to think this one through. I need to figure out how to get Umbridge and Hagrid in the ring together.}

The thought was a pleasant one, and comforted him all afternoon.

Umbridge sent for Snape later in the day.

"You weren't in your office last evening."

"I know."

Umbridge waited for a moment, until it was clear no more information was coming. "So you don't intend to answer my question?"

"You didn't ask one." \emph{Careful, Severus. You don't want her to get too impatient with you.}

Not having a quill in her hand to tap, Umbridge began drumming her fingers instead. "Where were you last evening?"

"I told you. Out saving the potions-grade plants from the frost. You can check the concoctions, decoctions, tisanes, effusions, tinctures, and other preparations that Professor Sprout and I worked on all night if you doubt me."

"I mean before that."

"I went up to the Astronomy tower."

"Why?"

"To observe cloud structure and take barometric readings."

"You're not the Astronomy teacher."

"That's not astronomy. That's meteorology." \emph{I could string her along like this forever, but do I really want to waste that much time?} "The study of weather," Snape continued, "Weather, especially humidity, affects potions-making, and I was also worried about the herbs. A potion is only as good as the ingredients that go into it. A sudden frost can be a disaster."

"No one saw you go up there?"

"I assure you, the next time I take barometric readings, I'll arrange for witnesses."

Umbridge seemed to debate with herself the value of continuing this unprofitable line of questioning, then suddenly changed the subject. "Tell me about Hagrid."

"I doubt I could add to what's already in his file."

"You went to see him this morning."

"I did. I've been acquainted with Hagrid for twenty-four years and wanted to say welcome back."

"He's been in some kind of fight, did you notice?"

"Hard not to. I even asked him about it."

"And?"

"He preferred not to tell me. Since it isn't really my business, I didn't press the issue."

"In your opinion, is he a good teacher."

"I've never watched him teach, and have no basis on which to form a judgment."

"It would be better for you if you cooperated a little more."

"I've answered your questions."

"I need a different kind of answer."

"I believe that's called suborning a witness."

The drumming stopped. Umbridge's eyes narrowed, and the corners of her mouth twitched in the crude imitation of a smile. "I can think of places much better suited for this kind of interview than Hogwarts. Tread carefully, Potions master, or you may find yourself in one of them."

"Is Educational Decree Twenty-Six going to give the High Inquisitor the authority to arrest and incarcerate the teachers?"

"Perhaps. I have a short list. You're on it. When the time comes, you may wish you'd kept on my good side. You may go now."

"Yes, Ma'am. Thank you, Ma'am."

On Monday morning, Hagrid was back at the staff table for breakfast. The teachers all came up to greet him, as did several of the students—mostly from Gryffindor. There was a certain tension, and the definite sense that many would miss Professor Grubbly-Plank.

Hagrid plunked his chair next to Snape's and began helping himself to an enormous plate of food. "Sorry 'bout the way I spoke t' ya yesterday, lad," he muttered. "I was a little testy."

"Understatement of the year," Snape replied, also in a low voice. "Snap my head off, was the way I regarded it. Have you met the Lady yet?"

"She sent me a message she would observe a class. Tomorrow."

"Who do you have?"

"Gryffindor and Slytherin, fifth years."

"Drat! She must have picked that one on purpose. You have to be careful."

"I thought it was pretty good." Hagrid sounded puzzled. "It's got the students as like me best."

"It's also got the student who dislikes you most, and Lucius Malfoy is hand in glove with the Lady."

"Well, that's all right, though. I got a powerhouse lesson planned. Knock her socks off."

"I'd rather see you have a nice, safe lesson. You can't afford to take chances."

"That's what Hermione said."

\emph{Point to Granger. The girl does have a head on her shoulders.} "You should listen to her. What's your lesson about, anyway?"

"Nothing out of the way. Animals we keep right here at Hogwarts."

"Sounds adequate{\el} Heads up! There's Umbridge. Pretend we're not talking."

Snape and Hagrid finished their breakfast in silence.

The morning Potions lesson was with the same students Hagrid would have for his inspection the next day. Malfoy, released from hospital the previous afternoon, was thirsting for revenge, while Gryffindor was still reeling from the shock of losing Seeker and Beaters at one blow.

It was a tinderbox waiting for a match.

The potion of the day, a rather complex one, was meant to stimulate the hippocampus, and was called the Elixir of Remembrance.

"Maybe it'll help Weasley remember which goals he's supposed to be defending," sneered Malfoy, loud enough so the Gryffindor students on the other side of the room could hear.

Snape weighed the relative merits of having a man who was both Dolores Umbridge's advisor and the Dark Lord's lieutenant angry with him, and allowed Malfoy to keep talking.

"Of course, first he'd have to remember that he plays Quidditch, and then he'd have to remember to take the potion."

Crabbe and Goyle laughed at Malfoy's witticism, but Snape cringed. Approaching Malfoy, Snape whispered quietly for his ear alone, "Your bon mot was lacking in literary quality. If I were you, I'd hold back until you had something of truly astounding wit to offer. Otherwise you might find yourself the butt of a few jokes."

"What do you mean?" Malfoy hissed.

"Your comment was on a twelve-year-old level. You can do better than that. Don't give them the chance to shoot your poorer efforts down when you can flatten them with your best."

The attempt to come up with something that was his `best' kept Malfoy quiet and occupied for the rest of the double lesson.

Hagrid's inspection by Umbridge was, by all accounts, a disaster. According to the Slytherin students, who were not at all sympathetic to Hagrid, Umbridge had treated him like an ignorant buffoon, pretended she couldn't understand what he was saying, accused him of exposing the students to vicious animals, and accepted at face value all the jokes they wanted to tell her. It was a while before Hagrid was ready to show his face to the staff.

Which was probably just as well, since his face continued to be cut and bruised with what were clearly fresh injuries, leading Snape to wonder if there wasn't after all a giantess somewhere in the background.

"Has he been to you for treatment?" Snape asked Madam Pomfrey on Thursday, two days after the inspection.

"I haven't seen him at all. If it weren't for the rest of you, I wouldn't know he'd been injured."

"Rest of us? Who else told you?"

"Who hasn't? Everyone who saw him on Monday and Tuesday at the staff table. McGonagall conveyed Dumbledore's concern, Flitwick and Sprout came together, Hooch was calling Trelawney a nervous old biddy for worrying that it might be contagious{\el} I may be the only one at Hogwarts who hasn't seen Hagrid's face."

"Could you go visit him?"

"Not without his asking. It doesn't seem life-threatening, or likely to cause permanent disability. I can't treat him without his permission."

\sbreak

November slipped away in relative quiet. The weather continued cold and snowy at Hogwarts, confining the students to the castle more than usual. This, oddly, did not increase the number of violent incidents, and Snape wondered again where some of his problems were channeling their energy.

The teachers had by now perfected the information chain, together with a series of coded messages, so in a way it was a disappointment that Umbridge gave them no opportunity to use it. The Lady once again appeared dormant, though the more rabid members of the staff were sure she was just waiting for the proper moment to spring her next surprise.

Things were happening at Croydon.

In the laboratory, the first experiments with Polyjuice Potion came up duds. Most of the alterations Snape had made merely rendered the potion completely ineffective. The only two ingredients that seemed to offer any hope for manipulation at all were the boomslang skin and the bicorn horn. At least when Snape adjusted them, the potion still brought about a transformation. He started several new batches brewing.

The Veritaserum gave more hope. It was harder to test, since Snape didn't want to use it on himself while he was at Croydon, so he brought a couple of samples with him to Hogwarts. Since he was absolutely certain that McGonagall would pump him for information if she were involved in the testing, Snape confided instead in Professor Flitwick. The results were, not surprisingly, mixed.

"I never knew you had{\el} dear me{\el} problems with your father," was Flitwick's response to testing with the first batch.

The second and the third, tested on different days, were similar, but the fourth batch showed promise.

In fact, it showed more than promise. Having drunk a dose of the potion, Snape found himself filled with unexpected feelings. He knew he'd been given Veritaserum, and he resented it. He wanted to resist, but that was not all. He wanted to deceive Flitwick. He began, in fact, to invent answers that were plausible but false.

"Now I am confused," said Flitwick at the end of that session. "How could \emph{Witch Weekly} name them couple of the year when you said before that they had so many problems?"

Snape explained, and the next time he was in Croydon, he made sure to bottle up several vials of the `adjusted' Veritaserum to keep with his supplies at Hogwarts.

Then, in December, Croydon was once again tense with activity. A new class came in for defensive training, and requisitions were made on the stores for potions of cooperation and forgetfulness. It appeared that everyone involved had been constrained by a need-to-know order, and the two times someone started to say something in Snape's presence, they were hushed immediately by their comrades.

Snape reported this to Dumbledore at once. Dumbledore called for a meeting of the Order for midnight Monday the ninth. Snape didn't usually leave Hogwarts during the week, and by midnight Umbridge would be convinced he was asleep. Long before breakfast Tuesday morning they would both be back.

Molly Weasley opened the door to them at Grimmauld Place, though Black came directly from the kitchen to the hallway at the sound of their voices. After a quick greeting to Dumbledore, he edged over to Snape and muttered, "I hear you're giving Harry a bad time."

"If you mean he's been producing inferior potions and receiving correspondingly low grades, you're quite right. Typical of him to go crying to you."

Dumbledore stepped between them, forcing the two apart. "No bickering!" he demanded in a menacing tone, then led the way into the parlor.

Snape's report was short and to the point. "Half a dozen Death Eaters, maybe more that don't need training. They have someone inside who'll admit them. They're carrying potions for interrogation and forgetfulness, so they're hoping to be in and out without being detected. They're not anticipating resistance or violence, but{\el}"

"But what?" prompted Moody.

"They're under a strict secrecy order—they won't talk in front of me—but they're nervous about something, something at headquarters, not the target building. A couple of them were projecting rather strongly. It seems someone important's going with them, and they're scared."

"Any idea who?"

"The highest ranking would be Malfoy or Macnair. If I were one of the ground troops, I'd be a lot more afraid of Macnair than of Malfoy."

"Understood," Moody said. "We have to set watchers again. We can rotate through the night hours like we did before." Tonks left right away, and the others stayed for refreshments.

Dumbledore followed the others into the dining room, but Snape hung back in the parlor. The rest affected not to notice, so Snape stayed there, lounging in a comfortable chair, ignoring the hum of conversation in the other room, and glancing around at the walls and the shelves of the parlor. Dark objects from every corner of the world were displayed there.

\emph{My great-grandfather would have loved this place. Great additions to his own collection. Pity they all belong to Black.}

A half an hour later, Dumbledore was ready to go. Snape rose and joined him on the way to the door, where Black let them out into the night. They exchanged no words.

Once in the street, Dumbledore turned to Snape. "One of these days, you will accept his hospitality." It was a command.

"I think he prefers that I don't. It would require his being hospitable to me."

"One of you is going to have to take the first step."

"Why? As it is now, we both know where we stand. No surprises."

"It is bad for the morale of the others. It impedes teamwork."

"The day I have to join the others as a member of a team is the day my usefulness to you as a spy is over. Better to keep things as they are."

"I want you to make peace with Sirius."

"Tell him to make peace with me. I wasn't the one who went around beating other people up."

Dumbledore looked puzzled. "Is this an incident I do not know about?"

"There were a lot of incidents you didn't know about."

"I would still like you to make the first move. Sirius spent twelve years in prison with little to do but brood. It is not surprising that he finds it hard to let things go."

Snape made eye contact with Dumbledore for several seconds. "Define prison," Snape said at last, and it was Dumbledore who looked away

Dumbledore said no more, and together they apparated back to Hogwarts. There were still a couple of hours left for sleep, but Snape was not able to avail himself of them, as his conversation with Dumbledore had revived too many bad memories. For the next few days, he was more bad-tempered than usual.

The situation between Croydon, Grimmauld Place, and Hogwarts remained unchanged for a week and a half. That was just enough time for it to begin to seem routine, even normal. Then, shortly after midnight the Thursday before the winter break was to begin, all hell broke loose.

Snape was driven from sleep by sudden searing pain in his left arm. He staggered from his bed in blind panic, the mind-numbing brutal insistence of the summons so intense that he was out of his rooms and halfway across the entrance hall before reality brought him to a wrenching halt.

\emph{I can't disapparate from Hogwarts. I can't even leave Hogwarts walking through the gate on my own feet. Someone has to open the defenses for me.}

Sprinting up the stairs to the gargoyle statue that was the entrance to Dumbledore's tower, Snape became aware that he was not the only person being summoned. The place was full of Weasleys of various ages, McGonagall apparently having just aroused them and brought them to Dumbledore. Snape hissed at her from a niche, and she came over after shooing the Weasley children up the spiral staircase.

"What are you doing here?" McGonagall asked, almost accusingly.

"I'm being summoned. Urgently. I need the gate opened."

McGonagall's look was almost fearful. "I think Albus will want to speak to you first."

Snape waited on tenterhooks while McGonagall brought Dumbledore down.

"He is calling you? When did it start?"

"Maybe fifteen minutes ago. Please, Headmaster, I have to go."

"Only a moment. We shall be leaving from here shortly, and you will be able to disapparate from this spot. Much faster than going to the gate. Do you have any idea what he wants?"

"No. There's no way to tell."

"We must assume that he knows, then. My concern is how much to give him. A little information will help you, and may also help us." Dumbledore thought for a moment. "Harry had a dream tonight, and in that dream he was present in the body of a huge snake that attacked Arthur Weasley. Only the snake really did attack Arthur. He is being taken now to St.~Mungo's. Riddle must be aware of the contact, or he would not be summoning you so urgently. You are authorized to tell him what I just told you. See if you can find out what the experience was like from the other side."

"Get the snake to talk, you mean? I thought you were going to give me a hard assignment."

"Do not be cheeky. Minerva will signal you when it is safe to disapparate."

Each second seemed like a minute as Snape waited for the signal to go. At last McGonagall appeared on the spiral staircase where he had a good view of her. She motioned to him to wait, paused, and then gave him a thumbs-up. Snape concentrated on Croydon and disapparated.

Malfoy was waiting when Snape walked into headquarters. "Thank goodness you're here. He's getting very impatient. What kept you?"

"Magical shields. He knows that."

"Just let what you have be valuable."

And yet, when they came to the interview room, it was only Malfoy and Snape before the Dark Lord, and they were not required to kneel.

"You did not come to us at once."

"It is impossible to leave Hogwarts without the assistance of the headmaster or deputy headmaster. Leaving at one in the morning is unusual."

Malfoy drew in a sharp breath, and pain tickled the corners of Snape's brain. \emph{Don't be flippant. Don't even approach being sarcastic. This man owns you, Severus. Be respectful.}

The Dark Lord allowed silence to fill the room. Then he spoke again.

"Who allowed you to leave, Dumbledore or McGonagall?"

"Dumbledore."

"Then he knows you have come here."

"Yes, Lord."

"What does he want?"

"He wishes to know of the snake."

"Tell us how he is aware of this snake."

"The Potter boy had a dream, and in the dream he was the snake. He saw himself attack Arthur Weasley, and upon awaking alerted Dumbledore that Weasley was injured. Weasley has been taken to St.~Mungo's."

"What else does Dumbledore know of the snake."

"Nothing, my Lord."

"So Dumbledore wishes to scan the mind of a snake. This amuses us. Has Potter had such dreams before?"

"None have been spoken of."

"So it begins. This is excellent news. We must study how this serpentine propensity of Potter's can be manipulated to our advantage. You may go."

Snape and Malfoy left together, each to apparate to a different part of Britain. Before they parted, Malfoy said, "You have no idea how relieved I was to hear you had something to tell him. I don't know what happened to him tonight, but it was as if someone had set him in a bed of nettles. He hated not knowing. I owe you another one."

In Dumbledore's office later, Snape tried to make sense of it all.

"Malfoy said something had happened to the Dark Lord himself. And the Dark Lord thought it funny that you wanted me to look for a snake. What are the chances that the Dark Lord was the snake?"

"You mean that Harry touched the mind of Riddle directly? That would explain how Riddle knew at once of his presence. You have a better feel for this than I do, Severus. What are the chances that Riddle, having already unconsciously influenced Harry's dreams, will now try consciously to influence those dreams further?"

"I think it's very possible."

"Will he start immediately?"

Snape thought for a while. "My sense was that he doesn't want to alarm Potter. Or you, for that matter. I don't think he has anything specific that he wants Potter to believe or do. When he comes up with something, he'll move. We may have some time to plan before he does."

"How would you feel if I asked you to teach Harry to block Riddle's thoughts?"

"You're joking. Please tell me you're joking."

"Why not? It seems a logical step."

"The Dark Lord nearly killed me last June because he thought I was teaching myself occlumency. Can you imagine how he'll react if he finds I'm teaching it to someone else?"

"How would he find out?"

"Through Potter. Once he tries contact with Potter's mind, unless Potter has already mastered occlumency, it's a direct link to me. Are you trying to kill me?"

"Not if I can avoid it. What makes you think Harry cannot master occlumency?"

"He's his father's son. There's nothing subtle about him. James was as transparent as the daylight, and his boy is no different. He'll sacrifice the thing he loves best to sentiment, and anything else that gets in the way. I prefer not being a sacrifice. At least not to his sentiment."

Thursday and Friday passed quickly, and suddenly the term was over and they were on Christmas break. Students and teachers deserted Hogwarts en masse, leaving the usual skeleton crew and stragglers. Even Umbridge left for the holidays, and Hogwarts was temporarily transformed into an island of peace in a tumultuous world.

Saturday found Snape back in Croydon.

Malfoy stuck his head in the door of the laboratory, but hardly glanced around. "He has a question for you. It'll take just a minute."

Snape went down to the interview room and stood before the Dark Lord.

"Has Potter had any more dreams?"

"I don't know. He left Hogwarts early Thursday morning and is in{\el} the south now. He won't be back at Hogwarts until next term."

"Do you know exactly where he is?"

"Yes, Lord."

"Tell us."

The safest thing at that moment was to honestly try to think and say the name, which Snape did, knowing full well that it wouldn't be possible. "He's in{\el} south{\el} at{\el} square{\el}"

"Look at us."

Legilimency revealed the shield of the Fidelius Charm. There was no way to break through it, and the Dark Lord was satisfied. "That is of no consequence. We have already received information from another source. We have sufficient weapons. You will attempt to discover if Potter has had more dreams. It is important."

Back with Malfoy, Snape confided his task. "He also said we had a new source of information."

Malfoy chuckled. "It came to me, totally unexpected. You might say it fell from the blue, but it gave us a tool to use against Potter when it comes to it. Enough said. The less you know, the safer."

Snape returned to his class and his potions, but on his return to Hogwarts he went straight to Dumbledore.

"He's trying to project dreams into Potter's head. He wants Potter to know something or do something to the Dark Lord's advantage. I'm to find out if the dream incursion has been successful, and what the dreams are."

"Harry has told no one of any dreams. I shall contact the members of the Order and have them watch out for any sign that he is connecting with Riddle."

"Why don't you just ask him?" When several seconds passed without an answer, Snape looked over at Dumbledore. "He wouldn't tell you, would he?"

"He would be more likely to tell Sirius. It is fortunate that he is spending the break at headquarters. With the two of them together, Sirius may be able to find out things that would be harder for us here at Hogwarts."

"I don't suppose we could just explain the situation to him."

"Unfortunately, that might make things worse. That would open the possibility that Riddle would find out the full extent of our knowledge of his actions, putting Potter and you into greater jeopardy."

"Now I see where this is going. You're making another case for occlumency lessons. If I don't teach him, he's likely to give everything he knows about me to the Dark Lord." Snape stood and walked over to the cabinet where Dumbledore kept his mead and poured himself a glass. "This is a damned if you do, damned if you don't situation, isn't it?"

"I fear so. You must weigh which action is likely to give you the most protection and place you under the least risk."

"Does that mean you're leaving the decision up to me?"

"It does."

"Then I would prefer not to."

"That quick a decision? May I ask why?"

"It's more personal than you realize. You can find someone else to teach him. You could do it yourself. I could teach any other student. I do not want to teach him."

Dumbledore remained silent, waiting.

\emph{I have to explain to him. He thinks I'm refusing because of some childhood feud involving James and Sirius. But Arthur Weasley's lying in St.~Mungo's—he could have been killed—and I can't let Dumbledore think that I'm being that petty at a time like this. I can do this if I just figure out how to start.}

The long, gentle silence helped. Snape knew Dumbledore would wait patiently until he was ready.

"It's instinctive. Shutting people out, I mean. I was shutting my father out before I was old enough to understand that I didn't have to—that he couldn't read me anyway. The first time I locked you out, I wasn't really intending to do it. It just happened. The same with the Dark Lord. I didn't want to shut him out. It just happened."

Snape took a deep breath. "Letting people in can be instinctive, too. I won't say I never shut my mother out, but the few times I did required conscious effort, hard effort, and she could sense the strain. There's one other person I was never able to lock out. She didn't know how to read me either, but that wouldn't have made a difference. Every time I looked into her eyes, I was an open book."

Dumbledore nodded. "And he has his mother's eyes."

"I felt it from the beginning. The day he was sorted. He touched his scar as if it hurt, and looked straight at me. It was like looking into her eyes again. If he'd known how to read that day, he'd have had me from that moment. But he didn't know. And now you want me to teach him that reading is possible. I'll never be able to let down my guard around him again."

"This is a serious issue for you, I see."

"It's worse. What if he can't learn occlumency? There are things{\el} The fastest way to get someone to want to hide his thoughts is to try to access the thoughts he most wants to hide—thoughts of humiliation, fear, intense or shameful emotion{\el} It can boomerang, and he could conceivably access my thoughts, and I might not be able to keep him out. Those thoughts would then be available for the Dark Lord to see every time Potter sleeps. Some of those thoughts, if the Dark Lord sees them through Potter, would let him know that I deceived him from the very first. They're a death sentence."

"I had not thought of that." Dumbledore rose now, too, and poured himself a glass of mead, refreshing Snape's glass as he did so. Then he asked a strange question. "How many of these thoughts are we talking about?"

"I don't know. I wasn't even considering the question before this little chat of ours. What difference does it make?"

"What if you could put those thoughts somewhere where Potter could never access them?"

"You can't just take thoughts out of your head."

"I have a pensieve."

"Oh."

This was not, truth be told, Snape's idea of an optimal solution. The optimal solution was for Dumbledore to teach Potter himself. That, however, could lead to the same worst-scenario situations that Snape foresaw for himself, except that having the Dark Lord access Dumbledore's thoughts was, over all, a greater disaster.

"Let me show you the pensieve," Dumbledore said. "Have you ever used one before?"

Learning to use the pensieve was easy. Deciding what to place in it was hard. The capacity of the basin was limited, so it could hold a large number of short memories, but only a few long ones. Snape sat in his office for hours, staring at the ancient symbols carved around the outside of the stone, reviewing all those thoughts he'd managed to keep hidden from the Dark Lord in June.

\emph{It really is a matter of what I can explain to the Dark Lord and what I can't. There's nothing about my family I have to worry about, except the moment I discovered that Death Eaters arranged Nana's death with an Imperius spell. That has to go into the pensieve.}

The memory swirled in the basin like a liquid mist, lightly coating the bottom with white silver. After that, Snape's choices revolved around three people—Dumbledore, Hagrid{\el} and Lily.

\emph{Thank goodness the Dark Lord knows that Dumbledore considers me his own spy. Almost all of our conversations can be explained. And since I'll be evoking unpleasant memories in Potter, that's what Potter'd be most likely to see in me. Most of my interactions with Hagrid were pleasant, and therefore unlikely to come out, or explainable if they do. The most dangerous memory is of the day I returned to Hogwarts and betrayed the Dark Lord to Dumbledore.}

That was a long memory. The pensieve was filling up, the silver clouds of his thoughts rippling as if disturbed by a breeze. Now there was the problem of Lily{\el} Lily, who'd brought about the destruction of the Dark Lord through the power of her love{\el} whose friendship would, in the Dark Lord's eyes, constitute the blackest of treasons.

\emph{I have never shown Lily to the Dark Lord. Anything he sees of her will tell him I've been hiding my thoughts, deceiving him. There's too much, and I can only fit two more long memories into the pensieve. Most of my memories of Lily are good, pleasant memories, though. Best to concentrate on the bad ones, the ones most likely to be pulled out during occlumency lessons.}

That narrowed the list down considerably. First and foremost was the day that Lily died. The whole episode—from the moment of hearing of the Dark Lord's demise, through the black despair of the Astronomy Tower, to waking up from sedation in the hospital—all had to go.

One other long memory remained—the day Sirius and James had humiliated him in front of the whole school, and Lily had come charging to his defense. \emph{If the Dark Lord sees that, he'll know there was something between us, will wonder why he never saw it before, and will look for more.}

Now there was room for only two short memories, and they were obvious. First was the day Snape had struck Lily, the day he'd realized that his father's demon lived in him and that he could never be close to anyone without hurting them. The other was the argument when he'd accused Lily of betraying him by teaching his spells to James. With that last memory, the pensieve was full.

\emph{Three long memories, and three short memories. The others either unlikely to be drawn out or something I can explain. Something I hope I can explain.}

\sbreak

"It will work, then?" Dumbledore smiled. "I am pleased."

"It'll work as far as past memories are concerned. At least the most dangerous things can be protected. There still remains the very act of teaching occlumency. He's not going to be happy about that."

"Will not the fact that I have ordered you to do it be of any help in deflecting his anger?"

"You haven't ordered me to do it."

Dumbledore turned his back on Snape, then wheeled suddenly, wrath blazing in his eyes. "Enough of your excuses and your petty scruples!" he snarled. "I will not tolerate your disobedience! You will teach this boy to hide his thoughts, or your tenure at this school is over. If you cannot be useful to me, you might as well be dementor fodder at Azkaban! Do you understand!"

"Yes, Headmaster," Snape whispered, hanging his head and allowing fear to wash through him.

After a pause, Dumbledore relaxed his pose. "Do you think that will assist you in making your case?"

"It's better than nothing. Have you ever considered a career in the theater?"

The Saturday before the new term, Snape left early for London. He had first to visit Grimmauld Place to let Potter know about the occlumency lessons, then go from there to Croydon. Dumbledore had covered one of Snape's problems by giving him a letter to let Black know he was to be allowed to speak privately to Potter. The second problem was trickier. Snape had to decide whether or not to tell the Dark Lord about the lessons.

"Come in, Professor. What a pleasant surprise," Molly Weasley smiled at him as she opened the door. "Will there be a meeting?"

"Good afternoon, Mrs.~Weasley," Snape replied. "No meeting today. At least no large one. I'm here at Professor Dumbledore's request to speak with Master Potter."

"In that case, you'll probably be most comfortable in the kitchen. I'll let Harry know you're here."

"Look what the cat dragged in," said a voice from the stairs, and Snape and Molly looked up to see Black descending towards them. "Or maybe it was a snake. Look what the snake dragged in."

"I've been instructed to speak with Potter," Snape said calmly, holding out the letter. "Professor Dumbledore{\el}"

Black seized the letter, tore it open, and read quickly. "Fine. You can talk. The kitchen's perfect. Molly, you can tell Harry to meet us there. Unless, of course," he sneered, "Mr.~High-and-Mighty also objects to smelling my food."

Snape ignored the jibe. "I believe you'll notice that the letter says a private conversation."

Gesturing Snape towards the kitchen, Black growled, "I'm not leaving Harry alone with you." The volume of his voice was rising, and Snape wondered suddenly if Black had been drinking. "I wouldn't trust a sneak like you alone with Harry. So you take me, or you get out of my house."

"Very well," Snape responded. "I suppose when one is truly bored, even eavesdropping provides entertainment."

"Get in the kitchen, Snivelly, before I decide to throw you out."

"Believe me, I have as great a desire to return to fresh air as you have to see me leave."

They sat for a moment in stony silence, the width of the kitchen table between them, staring at opposite sides of the room. Then the door opened, and Potter said, "Er{\el}" and entered.

Trying to act as if Black weren't there to threaten him, Snape motioned toward a chair. "Sit down, Potter{\el}"

"You know," Black interrupted, tipping his chair back and staring ceilingwards, "I think I'd prefer it if you didn't give orders here, Snape. It's my house, you see."

Potter took Black's cue and sat next to his godfather so that Snape was obliged to talk to both of them. Snape forced his anger down, and with an effort to be calm said, "I was supposed to see you alone, Potter, but Black{\el}"

"I'm his godfather!" Black was now close to shouting.

"I am here on Dumbledore's orders, but by all means stay, Black. I know you like to feel{\el} involved."

Black's chair slammed back into its place. "What's that supposed to mean?"

"Merely that I am sure you must feel{\el} frustrated by the fact that you can do nothing useful for the Order." Black was silent, and Snape continued. "The headmaster has sent me to tell you, Potter, that it is his wish for you to study Occlumency this term."

"Study what?" Potter said, and it was clear he'd never heard the word before.

"Occlumency, Potter. The magical defense of the mind against external penetration. An obscure branch of magic, but a highly useful one."

"Why do I have to study Occlu{\el} thing?" His obtuseness brought vivid images of Crabbe and Goyle into Snape's mind. \emph{How can you be Lily's son? If it weren't for the eyes{\el}}

"Because the headmaster thinks it a good idea. You will receive private lessons once a week, but you will not tell anybody what you are doing, least of all Dolores Umbridge. You understand?"

"Yes. Who's going to be teaching me?"

\emph{Do you honestly think that I came all the way here to play messenger boy for someone else? Or does the prospect distress you so much that you refuse to accept its reality?}

"I am," Snape replied.

Potter stared at Snape, the look on his face one of horror. Black thrust his own face forward intimidatingly. "Why can't Dumbledore teach Harry?" he demanded. "Why you?"

The angrier Black became, the more sharp and focused Snape felt himself growing. The conversation was nearing a point of actual battle, and Snape began automatically to shut down even as he prepared to leave the house. "I suppose because it is a headmaster's privilege to delegate less enjoyable tasks. I assure you I did not beg for the job."

Rising, Snape adjusted his cloak around his shoulders. It was nearly time for him to be at Croydon. He addressed Potter, turning slightly to shut Black out of his vision. "I will expect you at six o'clock on Monday evening, Potter. My office. If anybody asks, you are taking Remedial Potions. Nobody who has seen you in my classes could deny you need them."

As Snape turned to leave, Black snapped, "Wait a moment!"

"I am in rather a hurry, Black{\el} unlike you, I do not have unlimited leisure time{\el}" Snape was shut down completely now, sensing attack. His hand moved toward his wand. Just in case{\el}

"I'll get to the point then," snarled Black, rising. His height and bulk loomed forward over Snape, a clear physical menace, and the memory flashed into Snape's mind of Black's fist slamming into his stomach. He gripped his wand as Black continued. "If I hear you're using these Occlumency lessons to give Harry a hard time, you'll have me to answer to."

"How touching. But surely you have noticed that Potter is very like his father?"

"Yes, I have."

"Well then, you'll know he's so arrogant that criticism simply bounces off him."

Black charged around the table, his wand now out in his hand, but Snape drew his wand, too, and they faced each other, barely two feet apart, for the duel that had been set brewing twenty-three years earlier, the first time Black threatened Snape in the halls of Hogwarts. Potter was yelling Black's name, but Black paid him no attention, and Snape concentrated only on the coming fight. Black's voice rose in anger while Snape's sank to a controlled whisper.

"I've warned you, Snivellus, I don't care if Dumbledore thinks you've reformed, I know better{\el}"

"Oh, but why don't you tell him so? Or are you afraid he might not take the advice of a man who has been hiding inside his mother's house for six months very seriously?"

"Tell me, how is Lucius Malfoy these days? I expect he's delighted his lapdog's working at Hogwarts, isn't he?"

"Speaking of dogs, did you know that Lucius Malfoy recognized you last time you risked a little jaunt outside? Clever idea, Black, getting yourself seen on a safe station platform{\el} gave you a cast-iron excuse not to leave your hidey-hole in the future, didn't it?"

The goading worked. Black raised his wand. \emph{Now it begins. Watch his eyes. You'll see the spell in his mind before he can cast it.}

And then Potter was between them, screaming "NO!" and trying to stop Black. "Sirius, don't{\el}"

His spell casting blocked by Potter, Black still pushed forward. "Are you calling me a coward?" he roared, as Snape sidestepped Potter to get a clearer shot.

"Why, yes, I suppose I am."

"Harry. Get. Out. Of. It!" and Black broke loose, lunging at Snape while Potter scrambled to intervene again. The boy planted one hand firmly on Snape's chest as he blocked Black with the other, and the two stood, the distance between them that of Potter's outstretched arms, wands pointed at each other's head.

\emph{Come for me. Come for me. Make my day.}

And then the kitchen door banged open and the whole tribe of Weasleys burst into the kitchen, Arthur among them gleefully pronouncing, "Cured! Completely cured!"

The tableau froze for a moment as the Weasleys took in the strange scene and Snape and Black began to retreat from their confrontation.

"Merlin's beard," gasped Arthur Weasley, "what's going on here?"

It was over. The duel would wait for another time. Recovering faster, Snape pocketed his wand and strode to the kitchen door, still too focused on Black to speak to the Weasleys. His last words were for the boy. "Six o'clock Monday evening, Potter," he said, then turned and left the house.

Snape walked quickly away from number twelve. Even though he was late, he wandered the streets around King's Cross for a while. He couldn't apparate directly to Croydon because it would be noticed instantly by the Dark Lord that something had disturbed him. \emph{If he calls me in to report, he'll know.} In addition, he'd not yet decided what to do about the occlumency lessons.

\emph{If I tell him, he'll be angry. If I don't tell him and he finds out later, he'll be furious. Either way, I'm in for a rough ride. How can I explain teaching occlumency when I've told him my own is involuntary? How will he react if I'm successful with Potter? How much can I blame Dumbledore?} It helped that Dumbledore had given him permission to disclose the lessons, but it didn't make the decision easier. \emph{Fascinating that I am allowed to tell the Dark Lord, but Dumbledore absolutely does not want Umbridge to know. Sad, that we can't trust our own Ministry.}

When he was finally calm enough, Snape apparated to Croydon, where he left a request to speak with the Dark Lord, then went directly to his laboratory. The next batches of the Polyjuice Potion and the Veritaserum were nearing their completion, and he tended them. Within the hour, a messenger came to ask him about his interview request.

"He wants to know if it's urgent or routine. If it's urgent, he'll see you tonight. If it's routine, it can wait until next week."

Snape stared at the man. "The Dark Lord has always seen me before."

"Not tonight, Professor. Big things brewing in the next couple of days. Wouldn't be surprised if they locked some of us out. Security, you know."

"It's routine. It will wait."

Snape fretted for another half hour, then the word came down that all extraneous personnel were to leave the building for the weekend and return the following Tuesday. Snape walked out with the others, then apparated directly to Hogsmeade.

Fifteen minutes later, he was with Dumbledore.

"You decided not to tell him about the lessons," Dumbledore said as Snape walked into his office.

"I never had the chance. They sent us all home and locked the building down. Something big is happening this weekend, or Monday by the latest."

"How do you know?"

"They told us to return on Tuesday."

"We shall reposition our people on guard at the Ministry and double the number. Any more than that, and Fudge will get suspicious. What are the chances that it is a different target?"

"I don't know. I know I was denied an interview and sent back here for security reasons. And I wasn't alone or singled out. This one is top, top secret."

"So we can only watch and wait."

"What if the Ministry wasn't against us?"

"We would alert the muggle Prime Minister and put a watch around every important building or site. The guards at the Ministry and at Azkaban would be reinforced, and listening posts would be alerted to report any unusual increase in magical activity. If the Ministry was not against us."

Snape went to bed and slept fitfully. The next day the students returned from their break, and the day after was Monday, and the beginning of Potter's occlumency lessons.


