% A Difference in the Family: The Snape Chronicles (Rannaro)
% The Fifth Year

\chapter{Conflicting Evidence}

The next day, three Slytherins were hung upside down in the fourth floor boys lavatory, their robes and gowns falling around their waists, and Rosier, on finding them, ran to pull Severus out of the library.

\emph{It can't be. It can't be my spell. Only Lily and I know my spell.} Severus closed his eyes in foreboding, then instructed Rosier and the other boys who'd since gathered to be ready to catch the first victim as he fell. He took a deep breath and thought \emph{Liberacorpus}, and the suspension spell was released, dropping the boy to the floor. The other two quickly followed.

"Whoa! Cursemaster!" whooped Rosier. "How'd you know that?"

"First year stuff," muttered Severus as he stomped out of the lavatory. He needed to think.

It turned out he didn't have much time. Slytherin students were being attacked and hung up in every corner of the school where teachers were unlikely to go. So far it was just the boys, but the chance that it would soon extend to the girls could not be ignored. A war council was called in the common room.

Bella and Rodolphus led the meeting. It centered on Severus.

"How did you know what the spell was?" Bella demanded.

"I didn't. I'd just{\el} come across something similar before and thought I'd try the release spell to see if it worked. Turned out I was right."

"Lucky for us. Is this a spell we can all learn? It'd be best if we could turn the tables on them, so to speak. Make the field level." Rodolphus was clearly eager to get his revenge, even though he was not one of the victims.

"It'll be hard for most of you. It's a nonverbal spell. Knowing it doesn't mean you can cast it."

"So you teach us."

It was decided. The sixth and seventh year students already knew nonverbal skills, and Severus taught them the Levicorpus and Liberacorpus spells that evening. He began showing the lower level students how to do nonverbal spells the next day. While not everyone was good at it, enough were so that soon Gryffindors were hanging up in the most unlikely places.

Levicorpus was the fad spell of the year.

"How did they learn it if you didn't tell them?" Severus was trembling, he was so upset. "I certainly never told them. They're my enemies!"

"So you automatically assume it must be me. Wonderful. You don't trust me." Lily pursed her lips in anger.

"Who else is there? Do you think I went around showing my spells to the whole school? Do you think I have a whole crew of `friends' to choose from?"

"I'm surprised you have any friends at all!"

Severus went white. It was as if the breath had been slammed from his lungs. When he spoke it was in a cold, controlled voice. "You really don't understand, do you? You're the only one I ever taught those spells to. The only one. I guess I don't have any friends at all. But I know who your friends are."

"What's that supposed to mean?"

"You don't exactly hide it. Every time you talk to him you're batting your eyelashes. It's quite an exhibition."

"What are you talking about?"

"Stuck-up Potter. You fancy him. You want him to notice you. Is that why you taught him my spell?"

"I never taught him your spell. But maybe I should have. He seems nice. Not like some people."

"It's hard to be nice when you've been betrayed."

"Maybe I'll try Potter. It'll be a pleasant change."

"Along with all the other girls. Learn what it's like to be part of a harem."

"At least he never hit me!"

In icy silence and deadly calm, Severus turned and walked away.

Without Lily to talk to, there were now three areas of life left for Severus to concentrate on, his classes and preparation for OWLs, his tutoring and the growth of his small savings into a rather respectable sum, and the Dark Arts, which he continued to study passionately.

One of Severus's new spells was Phusalida. It created a protective bubble shield around him to help ward off his own Levicorpus. What good was it that the Hogwarts robes disguised his poverty if he was vulnerable to a very revealing attack? For days he'd kept to areas frequented by the school staff, since it was only in hidden spots that the students dared use the suspension spell.

Fortunately, knowing exactly how Levicorpus worked, Severus was able to make his Phusalida spell curse-specific. It kept him from being suspended upside down, but was otherwise undetectable. The problem with curses, though, was that it was possible to invent new ones. Who knew what spell masters were out there creating hexes and jinxes just as he did in Hogwarts? The Dark Arts were a constantly shifting, dangerous morass requiring eternal vigilance and adaptability.

That was why he loved them so.

\subsection{Thursday, February 12, 1976 (three days before the full moon)}

Although busy, Severus was also increasingly lonely. Then, just before Valentine's Day, that began to change.

He was heading downstairs from the library to Potions in the dungeons when the sound of running feet behind him made Severus spin to face a potential attack. It was Wilkes and Mulciber, and they were running in what appeared to be panic, except they were laughing. They would have turned to race down the stairs, but Mulciber saw Severus.

"Snape!" Mulciber hissed, pausing there at the head of the stairs. "Come with us! Quick!" Wilkes was pulling at his robes, trying to get him to move.

"Why?" Severus asked, suspicious.

"Never mind. Just do{\el}" A sound behind him alerted Mulciber to the presence of his pursuers, and he glanced around, then appeared to make a quick decision. Leaving the safe escape route of the stairs, he ran and seized Severus's robes. "Run, quick. You don't want them to see you."

"But{\el}"

"You're in Slytherin robes. They won't care that it wasn't you." Even as he spoke, Mulciber pushed Severus down the corridor and into an empty classroom, Wilkes right behind them. "We have to hide," Mulciber gasped, breathing hard. "If they catch us in here{\el}"

"In the corner, quick," said Severus, and as the three boys huddled by the windows, Severus twirled his wand and said, \emph{"Contego!"} Although nothing seemed to have changed, the other boys trusted him and remained crouched down. They could hear voices in the corridor.

"They didn't take the stairs or we'd 've seen them. They must be here somewhere. You look in there. I'll check this one." It was Sirius Black's voice.

"Right you are, Padfoot. Yell if you need me."

The door to the classroom burst open, and Black entered. At least Severus assumed from the voice that it was Black. He wouldn't have known otherwise, since Black's face was covered by a long, thick beard the same color as his name. Hair was sprouting out of his ears and nostrils, and his eyebrows were about six inches long. Severus clamped his hands over his own mouth to keep from laughing out loud.

Black scanned the classroom, saw nothing, and continued down the corridor opening doors and searching. After a couple of minutes, the three could tell from the sounds that Potter and Black had moved on.

Mulciber stood, and held out a hand to help Severus to his feet. "Contego," he said. "I'll have to remember that. Thanks." He laid a hand on Severus's shoulder. "We'd better get down to Potions. We're almost late."

Wilkes laughed. "I'm looking forward to seeing how Black can stir his cauldron with all that hair in the way."

"You could have been there already," Severus pointed out. "You didn't have to stop for me."

"And let them catch you!" exclaimed Mulciber. "Not on your life. No Gryffindor messes with a Slytherin while another Slytherin stands by and watches."

"I thought it was different with `half-breeds' and `mudbloods.'"

Mulciber tilted his head, cocky and arrogant. "You may be a half-breed, but you're a Slytherin half-breed, and that makes you one of us. Come on, let's get to Potions."

The three entered the Potions classroom together. Potter and Black weren't there yet, but Lily was, and she watched them with worried eyes.

\subsection{Saturday, February 14, 1976 (1 day before the full moon)}

At breakfast on Saturday morning everyone was talking about Hogsmeade. They tended to talk about Hogsmeade at least once per term, and Severus normally paid no attention. This time Mulciber asked him a direct question, though, so he had little choice.

"What's your favorite place in Hogsmeade?" was the question.

"I don't have one," Severus replied. "I don't generally go into Hogsmeade."

"You mean you've never been there?"

"Once in third year. I didn't think it was that interesting." He didn't think Mulciber needed to know about the last time with Lily.

Mulciber grinned. "I bet you'd find it more interesting now."

Severus shrugged and shook his head. "On Valentine's Day? I doubt it. Are you going with Wilhelmina?" It was a measure of the degree that hiding from Sirius Black and James Potter had altered their relationship that Severus was suddenly able to talk to Mulciber this way.

"No, that's over. I'm taking Doris to Madam Puddifoot's. You should come along."

"You never heard about the number three and its comparison to a crowd?"

That made Mulciber laugh. "One of the things I like about you, Half-Breed, is that you have a way of saying things that's different from everyone else." There was something about the way he said `half-breed' that made it sound more like a friendly nickname than like the insult it had been before. Severus had heard his dad and his dad's friends call each other names like that, and all it meant was that they were mates. It didn't bother him.

"So," Mulciber continued, "are you going to Hogsmeade?"

"What would I do there that's remotely interesting?"

"Maybe the Shack will shriek."

"What shack?" There was nothing wrong with pretending to be dumb if you were intentionally hiding knowledge.

"You never heard of the Shrieking Shack? They started talking about it when we were in first year. There's this old tumble-down house just outside Hogsmeade, and it got haunted by some ghoul or something about four years ago. Lots of nights you can hear it scream and wail, or so they say. I hope to hear it at least once before I leave Hogwarts."

That sounded more interesting, for previously unremarked time sequences began to click together. "When does it shriek?" Severus asked, feigning only mild interest.

"At night. That's what makes February such a great time to go. The sun sets around five o'clock, so we can still be in Hogsmeade after dark. We have a chance to hear it."

That was even more intriguing. Severus declined to spend the entire afternoon in Hogsmeade, but he promised Mulciber he'd try to make it to the village around sunset to see if he could hear the shrieking in the Shack.

That afternoon, as the sun sank below the ridge of hills that rimmed Hogwarts and the moon, at the beginning of its fullness, edged over the same ridge, Severus made his way down the hill to the main gate with its flanking boars. No students were climbing the hill in the other direction, and Severus expected this was because they were all doing the same as he was—taking advantage of the early sunset to listen for the shrieking.

Indeed, finding the shack was simply a matter of following the students. Everyone, it seemed, was moving toward a little hill just outside of the village, and there was already a substantial number of students there. Severus saw Mulciber and Doris Gamp, and moved toward them. Mulciber looked over and waved. With so many students around, it was impossible to get close even to the fence that kept people away from the Shack itself.

Sudden stillness descended as a low, penetrating moan cut through the icy air. Severus felt the hair on the back of his neck stand up, and the crowd of students swayed and sighed in anticipation. Then the Shack began to shriek.

Severus had never heard—no one had ever heard—anything like it. It rose from a low murmur to a shrill scream. It throbbed with a wild ululation, then broke into barking yells and spectral howls. It screech and roared, moaned and sobbed, and cackled with demonic laughter. After only a few moments, most of the students had their hands over their ears to block the worst of the wailing, and when the professors came to herd everyone back to the castle for the night, no one resisted.

Severus went back with the rest, pondering the demonic noises as he watched the brilliant orb of the moon mount the western sky.

The little group into which Severus was now admitted expanded to once again include Bella Black, who brought with her Rodolphus Lestrange, Kenneth Avery, and the third year student Regulus Black whom Severus had met at the Hand of Glory party, and whom he now knew was Sirius Black's brother. He didn't hold that against Regulus, who all in all was a decent chap.

Within his own dormitory, Severus would never wholly trust either Wilkes or Rosier, but Edison and Mulciber, who'd never been quite as mean to him, were fast becoming the closest thing to male friends that Severus had ever had in his life. For the first time he was admitted to a level of confidence and banter previously unknown.

"Yo!" cried Mulciber on their way to lunch one Monday in early March. "Muggle ship off the starboard bow! Now that one could make me change my opinion of mudbloods."

The `muggle ship' in question was Patience Ferguson of Ravenclaw, whose budding womanhood evoked the image of a figurehead from an old sailing ship, and who generally tended to leave young men in her wake with their hearts pounding and their tongues hanging out. Severus was able to watch her with a newfound aesthetic appreciation and with the opportunity to nudge another young man in the ribs in expression of that appreciation, even though he knew he would never be able to do anything about it. Not if he wanted to be free of the Demon.

Mulciber also turned out to be funny, in a crazy sort of way. He was taking Muggle Studies on the principle of `Know Thine Enemy,' and now frequently asked Severus to explain some arcane point. On having electricity and the electric light explained, he began hitting Severus with a series of jokes.

"How many purebloods does it take to change a light bulb?—None. It never occurred to them that the possibility existed."

"How many half-breeds does it take to change a light bulb?—Two. One to change the bulb and the other to keep the purebloods from getting in the way."

"How many mudbloods does it take to change a light bulb?—One if he's by himself, but if another joins him they need to canvass the neighborhood, hold a meeting, and vote."

"How can you tell the difference between a pureblood, a half-breed, and a mudblood?—Test them when they're eleven. The one who can't tie his shoes is the pureblood. The one who can't make change for a galleon is the mudblood. The one who dies laughing at the other two incompetents is the half-breed. Bury the half-breed. Never try that test again."

Severus rather liked Mulciber's jokes because they never made half-bloods seem dumber than purebloods or mudbloods. He completely forgot that he used to resent being called a half-breed, at least not when the word came from Mulciber. From Wilkes, it was a different matter.

When Wilkes used certain words, the very tone of his voice made them insults. When Mulciber used them, they were humorous and friendly. Severus wasn't sure exactly how it worked, but he knew that to Mulciber words were words, but to Wilkes they were weapons. Severus was careful how he used the same words, since he wasn't sure he could say them the way Mulciber did.

"Hey, Macdonald!" Mulciber called across the lawn one morning in mid March as the Slytherin fifth year students went out to the greenhouses while the Gryffindors returned to the castle from their earlier class. "Is it true mudblood girls{\el}\,?" and made reference in scientific terms to certain points of anatomy. Macdonald blushed furiously and ran over to her dorm mates, already in tears.

The group of Slytherin boys for whom Mulciber had been showing off included all four of his dorm mates as well as Avery and Regulus Black. Severus found the comment amusing, and was disappointed that Macdonald hadn't come back at Mulciber with something equally scathing.

"Isn't that your girlfriend, Sev?" said Rosier, pointing to the cluster of Gryffindor girls with Lily in the midst of them.

"What do you mean?" Severus was on guard at once, unsure of where this was leading.

"You know. The one you were meeting in the third floor corridor in first year. The one you kept on meeting{\el}"

"Yeah," chimed in Black. "On the Astronomy Tower, too!"

"You knew about that?" Severus said, wondering why, if it was true, no one had said anything.

"Sure," said Avery. "It wasn't hard, not when we really wanted to find out. But Bella said to leave you alone. She figured you'd eventually find out for yourself that the girl was bad news. I mean, why does she have to have her claws in you when she's got a whole stable of Gryffindors?"

Severus watched calmly, his mind closed and sealed, as Lily turned to regard his whole group with searing scorn. He thought of her meetings with Lupin, and her flirting with Potter, and wondered if Avery was right. After all, the times he'd seen her were scattered and short. He had no idea what she did the rest of the time, though apparently the rest of Slytherin house knew. And she had given the Gryffindor boys his spell{\el}

Yet even at that moment, Severus would have given anything to be able to go back to the way it had been before, to have at least one person he could trust completely, one person he could open up to. Part of him wanted to believe that Lily was honest and true, even though every piece of evidence he had said that Avery was right.

Lily accosted Severus in the fountain courtyard two days later, seized his arm, and marched him into the empty corridor on the other side of the cloistered walkway.

"What were you doing being so mean to Mary?" she demanded.

"I didn't say anything to Macdonald," replied Severus. "If you want to get upset with someone, get upset with Mulciber. Better yet, get upset with Less-than-Serious Black. He said just about the same thing to Alderton. I don't see you getting all righteous about that."

"I don't care about Sirius Black or about what he says and does. I do care about what you say and do. All of Gryffindor knows we've been seeing each other for years and{\el}"

"Aha! Worried about your reputation, are you?"

"You know perfectly well this isn't about my reputation!"

"And why would I know that? You've been sneaking around hiding our friendship for years, and now you tell{\el}"

"Me? Me hiding our friendship? I seem to recall it was you who were afraid of your `friends' from Slytherin finding out{\el}"

"They've known all along and never bothered me after first year. The ones who've harassed me are from Gryffindor. Now I find out it's because of you!"

"Because of me? I'll have you know{\el}\,!" Lily stopped, and Severus knew, knew as if he could see the image floating to the top of her brain, that she was remembering times when Potter warned her away from their friendship. She switched tactics. "Severus, you know they use dark magic."

Severus laughed out loud at this, actually enjoying the startled look on Lily's face. "You're going to have to do better than that if you want to pass your Dark Arts OWL," he chided her. "There are objects that are dark, but only three spells are classified as always dark. All the others depend on the intent of the spell caster. Even the simplest of spells. If I'm helping you clean the owlery, Scourgify's a cleaning spell. If I use it in anger to harm another person, it's dark magic. Even a{\el} someone like you should know that."

"Of course I know that! But your `friends,' people like Avery and that Bella Black, they're not trying to help people with their magic. It's dark."

"Do you think Stuck-Up Potter was trying to help Bertram Aubrey when he enlarged his head? Every hex and jinx and curse he uses to force people to do what he wants or just to show off, that's all dark magic because his intentions are selfish and mean. Just like that spell you stole."

"What are you talking about?"

"I made that for self protection. I intended to use it only if I was attacked. That's light magic. Then old Stuck-Up gets his hands on it, and uses it to attack and embarrass people. That's dark magic." Severus glanced around as if searching for Potter. "Do I see you talking to him about it? No. Clean up Gryffindor first. If we weren't attacked, we wouldn't have to defend ourselves."

"What happened the day before yesterday wasn't self defense."

"What happened the day before yesterday wasn't magic. It was a boy teasing a girl, and there wasn't any magic involved. Tell Macdonald she needs thicker skin. If she'd dinged him back, we'd all be laughing at him now."

"It was mean. You shouldn't hang around with him."

"I should hang around with spell thieves, I suppose. Those seem to be my only choices."

"I didn't give your spell to Potter!"

"No? Maybe you gave it to Lupin, and he gave it to Potter. One big happy family over there in Gryffindor, aren't you?"

Lily stamped her feet, quivering in frustrated rage. "You're making it awfully hard to like you!"

"Believe me, when I want you to like me, you'll know!"

The silence deepened, then Lily turned and, stiff-backed and struggling for dignity, walked away into the castle. Severus watched her go, feeling oddly empty and incomplete. Then he left the corridor and went down to Slytherin house.

One rite of passage for the fifth years was the mandatory meetings with Professor Slughorn in April, about preparing for the future and a career. Since nothing in his social position had changed, Severus expected his own interview to be a short one.

"Well, Snape, you seem to have good marks in all your classes. Doesn't look like you'll have too much trouble with the OWLs. Have you thought yet about what you want to do with yourself after leaving Hogwarts?"

"I'm torn between becoming a numismatist or a spelunker."

"Uh, yes. Well, um, you certainly have the grades for either one, but I, uh, am not certain that those would be the best career paths for someone in your, uh, position."

"Do you think my Herbology grades are too low for spelunking? I have excellent marks in Astronomy and Potions, though, so I was also considering Paleoanthropology."

"Well, you do seem to have given this considerable thought. I think we can leave it at that until you have to choose your sixth year classes."

"Thank you, Professor."

"Get along to class, now."

"Don't you ever go to Hogsmeade, Snape?" Bella was waiting for Rodolphus for the first excursion of the spring into town. "There's so much to do."

"Occasionally, but it's only fun if you're with someone or have money."

"You could be with us, and you have money."

Severus glanced up at Bella, caught the tail-end of a warning look on her face, and turned to the newly-arrived Rodolphus. There was no question what his expression had been at the prospect of Severus being the third member of their party. Severus didn't mind. He almost sympathized with poor Rodolphus, for this had nothing to do with money or status and everything to do with wanting to be alone with Bella.

"Not enough," he said. "Money's been tight since my father died, and when I go back this summer, I'll have to take care of the property. It needs some improvements." Not exactly a lie, but phrased so that Bella could exercise her imagination as to just what his `property' was.

"Suit yourself. Just remember that we'd love to have you."

They left, along with most of Slytherin house except the first and second years. Severus stayed in his dormitory with his mother's old Advanced Potions book. By now nearly every page was full of his small spidery handwriting, not only hexes and jinxes, but attack and defense spells, and notes on just about every potion in the book. He was going to go into his sixth year potions class knowing more than old Slughorn ever would in his entire life.

Hagrid spied Lily sitting on the low stone wall of the planted area in the fountain courtyard. "Morning, Lily. I hope everything's well with you."

"Good morning, Hagrid. I'm fine, thank you."

"I been looking for Severus. Ya wouldn't 've happened t' see him, would ya?"

Lily's face darkened. "Mr.~Snape does not entrust me with his schedule."

"Just thought I'd ask. You have a good day, now."

"Thank you, Hagrid."

On his way back to his hut, Hagrid thought he saw a familiar thin figure near the edge of the forest. Severus appeared not to notice as Hagrid lumbered over. "There ya are. Y're due for a checkup, ya know."

"Don't you think I'm a bit old for that now?"

"That may be, but that's for Professor Dumbledore t' say."

"Maybe I should talk to Professor Dumbledore."

"Maybe ya should. Meanwhile, I got my orders. Come along now."

Severus drew himself up to his full height, which was still somewhat short of Hagrid's chest. "I'm not your servant. You don't command me like one."

Hagrid was suddenly reminded of Professor McGonagall's old image of a dagger. A razor-sharp obsidian blade. "Suit yourself," he said casually, but his expression was worried as he returned to his hut.

First Lily, now Severus. Something had happened there, and Hagrid wished he knew what it was. What was most disturbing was the locked-down hardness, the frosty isolation he sensed in the boy, as if all his and Dumbledore's hard work had been in vain.

"Hi, Evans. What's the sad face?"

Lily looked up at James. Of all people, he was the one she probably least wanted to see that morning. "Nothing," she answered. "Classes. OWLs."

"You can't be worried about your OWLs. You're a top student in almost every class. Bet you breeze through and ace every one."

Lily shrugged.

"Look, Evans. I've been meaning to talk to you{\el} No, not about that; don't get huffy 'til you hear me out. I'm not as good at Potions as you are, and I was wondering if you could help me out on a couple of things I'm having trouble with. It's not a lot, but I'd really like to get an Outstanding in the subject. I know you will."

"I don't know. I've never tutored anyone."

"I'd really appreciate it."

"Let me think about it."

James insisted that he couldn't be tutored in the common room of Gryffindor house since he had a reputation to protect. He chose instead out-of-the-way places like behind the Quidditch field or in the Great Hall in the empty period between breakfast and lunch. He was very careful not to push things, keeping his meetings with Lily strictly to the business of tutoring. When she got really interested in the Potions work, some of the chill left her manner.

Sirius had finally realized that James's interest in Lily involved more than a concern with the Dark Arts. He acted as sentry for his friend, keeping others away from wherever they were working. He was most particularly concerned that Severus not see James and Lily together.

Spring progressed, and the OWL exams got nearer.

They were well into May before Lily made the next move. As she had so many times before, she slipped a note into one of Severus's books saying `Forest. Lunch. Please.' She got there as quickly as she could after class and waited, concealed behind bushes at the edge of the trees.

It was half an hour before Severus arrived. Looking around and seeing no one, he was about to leave when he heard a "Psst{\el}" from near by. Lily rose and beckoned him closer.

"I really want to talk to you," she said when he approached.

"So talk."

"Okay, first I'm really sorry about what I said, about you hitting me. That wasn't fair. It didn't have anything to do with what we were arguing about and it's way in the past. And I shouldn't have blamed you for what someone else did. I just wanted to tell you I was sorry and ask you to forgive me."

"That's first. What's second?" Severus regretted the words immediately, for it looked as if Lily might start crying. He looked at the ground, then at the lake in the distance. "I'm sorry. I shouldn't have said that. I guess we both say stupid things when we're angry. Of course I forgive you. Will you forgive me?"

"Sure. Water under the bridge."

They stood awkwardly for a couple of minutes, neither knowing what to do next. Lily got her nerve first. "I worry about you. The others in Slytherin—do they ever talk to you about Death Eaters?"

"Why?"

"Haven't you seen in \emph{The Daily Prophet} how people are being attacked, sometimes killed because of this dark wizard, this Lord{\el} you know."

"I know we're in danger, but a lot of the attacks are from mud{\el} muggles against our people, and the Ministry's doing nothing about it. Someone has to protect us."

"O Severus!" Lily sounded distraught. "You're even talking like them. Don't you know that's what they want you to think so they can get you to join them? Don't you know that all your friends in Slytherin work for him? Sirius says their fathers are all Death Eaters—Lestrange, Avery, Mulciber, Rosier{\el} You haven't joined them, have you?"

"Nobody's asked me to join anything, so if your beloved Sirius is telling you they have, then he's lying to you."

Lily sighed. "I'm glad about that. I'd feel better if you didn't hang around with them. I wish we hadn't quarreled. About that spell{\el}" Severus just watched her, neither helping nor stopping her.

"I really don't know how anyone found out about the spell," Lily continued. "I've been thinking and thinking. I know it wasn't you, because it was Gryffindor using it. You say you didn't tell anyone else. I know I didn't tell anyone else. But it did start with Gryffindor. I've been wondering if maybe I talk in my sleep or something. It's the only thing I can think of. If I did, it wasn't intentional. You believe me, don't you?"

"Yeah. I believe you," said Severus. "It's over now, anyway. It's out. Everyone knows. Water under the bridge. Pax?"

"Pax. Do you think we can get together again? Viking is getting near Mars."

"Hard to say. I'm awfully busy right now with tutoring and everything. I don't know how much free time I'll have before OWLs. Maybe afterwards."

"Okay. Maybe afterwards."

A shout interrupted them. "Hey, Evans! What're you doing out here?" They both looked in the direction of the castle to see James coming towards them, Sirius not far behind. "I thought we had an appointment for after lunch today. I've been waiting for you."

Severus glanced at Lily. "Tutoring," she mouthed and started for the castle before James could reach them.

"Hey, Snape!" James called as he stopped and waited for Lily. "Enjoy your afternoon. I will."

As the trio walked back up the hill to the castle, Severus began practicing Sectumsempra on the bushes.

"What do you see in him? He's weird, he's funny-looking, he's moody, he's up to his eyeballs in the Dark Arts{\el} Why do you care?"

"I don't think that's your business. Your business is learning Potions."

"Look, Evans, I know you know that I don't do this just for the Potions OWL. I'm sure it's occurred to you that there's more than that between us."

"That's it. This lesson is over."

"No, come on. I'd really like to do things with you. Go to Hogsmeade, have lunch together. I've been dying for a month to ask you on a date."

"I wouldn't date you if you were the last man on earth." Lily slammed her books shut and headed for the dormitories.

"Would you date him if he was the last man on earth," said James to no one in particular. "Would he date you if he knew{\el}" He was smiling.

Severus stopped as Sirius stepped out of the doorway from the boy's lavatory. The fourth floor corridor was empty of students, since most were enjoying a beautiful June afternoon, maybe the last before their tests.

"Someone wants to talk to you, Snivellus."

Severus turned to see Peter and Remus blocking his exit in the other direction. \emph{How do they always manage to get the drop on me?} "What do you want?"

"Not them. Me," said James to his right, from a statuary niche. "I just wanted to give you a little information."

"So." Severus inched to the left so that his back was to the wall.

"That spell of yours that lifts people up? I taught that to everyone. Just wanted you to know."

"No you didn't."

"Sure I did. You want to know where I got it? Evans told me."

Severus felt his insides go hollow. "That's a lie."

"Think so? She had some trouble with it. She was pronouncing it wrong. Leevicorpus she was saying. Once she corrected that, it was easy. That's all I wanted to say."

The four left, James and Sirius laughing together. Severus stood alone in the fourth floor corridor feeling as if his world had ended.

\subsection{Week of June 6—June 12, 1976 (moon waxing to full)}

There was no time left for friendship or enmity, for trust or betrayal, or even for the end of the world. There was nothing for it but for Severus to shut down and turn off everything inside himself but exams. It was a drill he knew well. For the second week of June, there was nothing in his life but OWLs. Theory in the morning, and practical application in the afternoon.

Charms on Monday went well, but that was only natural. Half the tricks he knew with a wand, and every trick he knew without one, Severus owed to his mother. Eileen had enticed him with baby games when he was little, schooled him in elementary magic as a boy, forced him to focus by teaching him to duel at age nine, and given him the discipline and power that no one his age could match. Severus had learned very little at Hogwarts except some incantations.

Tuesday's Transfiguration tests were harder. Toby Snape had spent almost all his adult life trying to transmute the lead of his mundane existence into the gold of the perfect family. That early on he had learned to use the Philosopher's Stone of alcohol was perhaps not entirely Toby's fault. Severus, as a result, had inherited a certain inability to change what was into what he wanted it to be.

On Wednesday, Severus dedicated his Herbology test to Nana. Dealing as it did with the idiosyncrasies of living things, Herbology was not Severus's best subject, but he had the necessary knowledge and skills, and knew Nana would never stop trying to make a healer of him—still the most intriguing, to Severus, of all the possible wizarding professions.

During all this time, Severus kept his head down, his eyes averted, every distraction locked out, and he never once saw or consciously thought of Lily.

Thursday morning's test in Defense against the Dark Arts took place in the Great Hall. All the tables usually in place for the daily meals were removed and replaced with individual desks. June sunlight streamed in through the high windows, tinting everything in chestnut, copper, and gold. Severus wasn't allowed to keep his wand near his hand for the test, so he tucked it into the folds of his robe. He contemplated hanging great-grandfather Wensley Snape's shrunken head around his neck as a talisman, but decided it would shock too many people. Besides, for this one he didn't need luck.

Severus found his place and carefully picked up and examined his ink bottle, quill, and roll of parchment. He knew that everything had been enchanted with anti-cheating spells, but whether or not they had been hexed with anti-success spells was another matter. Everything seemed in order. Professor Flitwick, the Charms teacher, was helping proctor the test. The question papers soared out over the students' heads, then settled simultaneously on their desks, and the test began.

From the moment Severus glanced over the questions, he knew his biggest problem was going to be time. \emph{How am I going to write down everything I know about these subjects in just a few hours? Just have to write fast and leave some of the fun things out, I guess.} He picked up his quill and began writing in his small, spidery script. He kept his head close to the paper so he could read the words easily.

Severus had barely finished when Professor Flitwick called, "Quills down, please! That means you, too, Stebbins! Please remain seated while I collect your parchment! \emph{Accio!}" Severus's parchment rolled itself up and joined the others sailing towards the tiny professor. There was a moment of mirth as the rolls knocked him off his feet, and a couple of students in the front had to help him up again. Then Flitwick announced, "Very well, everybody, you're free to go!"

Severus picked up the questions paper, but instead of putting it into his book bag, he started scanning it again. The whisper of a thought had appeared in his head as he wrote his answers, and he was trying to retrieve it. Somewhere in the middle, between questions 10 and 15.

Students spilled out into the sunshine from the Great Hall. Most of Slytherin house vanished quickly, either back into their dormitories or to other parts of the castle. Ravenclaw and Hufflepuff tended to side with Gryffindor in any confrontation, and the Slytherin students had grown wary of being outnumbered.

Severus didn't notice. It never occurred to him that anything would happen here on the front lawn anyway, in full view of the castle and all the teachers. He didn't want to walk and read at the same time, so he made his way down the grassy hill to a spot not far from the lake where he could settle in the shade of some bushes. There he continued his study of the questions, trying to remember what had set off those warning bells in his head.

Finally giving it up as a lost cause for the moment, Severus rose and folded the paper, tucking it into his bag. As he started down the lawn, a voice behind him said loudly, "All right, Snivellus?"

Severus wheeled to meet the threat, but his wand was not at his hand, and in the seconds it took him to pull it from his robes, James yelled \emph{"Expelliarmus!"} and Severus's wand flew a dozen feet behind him. Severus dove for the wand, but an Impedimenta from Sirius threw him to the ground and knocked the breath out of him. \emph{Two to one. Here in front of half the school it has to be an ambush and two to one.}

Severus felt as if heavy weights were holding him to the ground. As he fought to get air into his lungs, focus, and rise at the same time, he heard the other two approach. He was frantically trying to think of any wandless spell he knew that was of any use in a duel.

"How'd the exam go, Snivelly?"

"I was watching him, his nose was touching the parchment. There'll be great grease marks all over it, they won't be able to read a word."

Around him, Severus could hear the giggling and laughter. Gryffindor, Ravenclaw, Hufflepuff—probably not a Slytherin anywhere around. He managed to fight the spell enough to turn his head and look James in the face. "You{\el} wait," he gasped. "You{\el} wait{\el}"

"Wait for what?" came Sirius's cool voice from the side. "What're you going to do, Snivelly, wipe your nose on us?"

"Stu{\el} pefy{\el} Petri{\el} ficus To{\el} talus." The words wouldn't come out right with the magical bands constricting his chest. "You cow{\el} ardly bas{\el} tard. You can{\el} go to{\el} hell."

James was as cool as ice. "Wash out your mouth. \emph{Scourgify!}"

It was a spell meant for scrubbing floors and dirty dishes, not for use against another human being. Severus suddenly felt as if stiff-bristled brushes were scouring the inside of his mouth, and his throat and nasal passages began to clog with soap. He was coughing, gagging, choking, suffocating{\el} Above him as he struggled in panic, he heard a voice screaming as if from a great distance, "Leave him ALONE{\el}"

Lily advanced on the scene in a raging fury. "Leave him ALONE!"

"All right, Evans?" Incredibly, in the middle of everything, James was flirting, in a low, pleasant, come-hither voice.

It had no effect on Lily. "Leave him alone. What's he done to you?"

James pondered the question. "Well{\el} it's more the fact that he exists, if you know what I mean{\el}"

"You think you're funny, but you're just an arrogant, bullying toerag, Potter. Leave him alone."

"I will if you go out with me, Evans. Go on{\el} Go out with me, and I'll never lay a wand on old Snivelly again."

"I wouldn't go out with you if it was a choice between you and the giant squid," said Lily.

"Bad luck, Prongs," Sirius laughed.

The Impedimenta curse was wearing off, and Severus could finally move. Nauseous from the soap and groggy from lack of air, he began to vomit, filling his nose with suds and bile, but at least his throat was clear and he could breathe again. Realizing through his mental fog that James and Sirius had been distracted, Severus began to crawl toward his wand, still spitting out soap as he desperately inched his way forward. His fingers touched it, and he spun his arm around to point at James with a nonverbal Sectumsempra that gashed James's cheek and spattered blood on his robes.

The enraged James whirled and hit Severus with a Levicorpus, and Severus felt his legs pulled up into the air, his robes dangling about him. He heard laughter in the crowd of students and the voice he finally recognized as Lily's say, almost laughing, laughing at him{\el} "Let him down."

"Certainly."

Severus fell in a heap, and struggled to his feet, wand ready, only to be hit from the other side by Sirius with a Locomotor Mortis that knocked him to the ground as stiff as a board. It was a hopeless battle, for whichever one he faced, the other would take him from behind. Fear and frustration knotted his stomach as he waited helplessly for what they would do to him next. Through the haze of his panic he could hear Lily's voice talking to James. Lily, who had betrayed him, sold him, given him into the hands of his enemies to be shamed, humiliated, and tortured. The demon was loose, raging inside him, and he hated her with every fiber of his being.

Then he was free again, and James was smiling at him. The condescending rich boy deigning to notice the poor trash at his feet. "There you go," James smirked as Severus struggled to stand, "you're lucky Evans was here, Snivellus{\el}"

The demon lashed out in fury as he screamed at both of them, "I don't need help from filthy little mudbloods like her!"

Lily froze in shock. "Fine. I won't bother in the future. And I'd wash your pants if I were you, Snivellus."

James was clearly gloating as he threatened Severus from one side while Sirius covered him from the other. "Apologize to Evans!"

Lily spat like an angry cat. "I don't want you to make him apologize. You're as bad as he is{\el}"

"What! I'd NEVER call you a{\el}"

Severus only heard part of what followed for he was fighting to keep himself shut down and closed. He trembled with the effort to control himself, to lock down the rage, remembering this had happened once before, with Hagrid by to restrain him{\el}

"You make me SICK!" Lily shouted at James, turning briskly on her heel and walking away.

"Evans! Hey, Evans! What is it with her?"

"Reading between the lines, I'd say she thinks you're a bit conceited, mate," said Sirius.

"Right," said James, looking around for a way to vent his own frustration. "Right{\el}" and Severus was upside down again, held aloft by his own spell. "Who wants to see me take off Snivelly's pants?"

"Touch him again, Potter, and I turn your tongue into corkboard!"

James spun to face an infuriated Bella Black, who stood just above him on the grassy hillside, her wand pointed directly in his face and backed by a score of students from Slytherin house. "Oh look," he drawled. "The Wicked Witch of the West wants her little dog back." Casually he let Severus fall back to the ground. "I'd be happy to take you on, Bellatrix. Just you and me. Man to man."

The crowd of students was backing away from the line of fire, and some of the Gryffindors were edging around to support James and Sirius. A few students hurried up toward the castle, looking for teachers. The show had turned from amusing to dangerous.

"Funny how you want it one on one now that you're the one outnumbered, isn't it? Funny how that little fairness thing didn't concern you when you had the upper hand. You really are a bully, Potter, aren't you?" Bella advanced down the slope, wand still pointed at James. More students from Slytherin house were coming down to support her.

\emph{"Accio wands!"} Pushing her way through the crowd, Professors Flitwick and Slughorn behind her, Professor McGonagall advanced to the center of the ring of students. Wands flew from the hands of the confronting groups to fall in a great flock at her feet. She ignored them and addressed the crowd. "Every student involved in this display of hostility and violence is on detention. Any student who lifts a wand against another will be suspended from this school without delay. How dare you fight here! You and you," she pointed at James and Sirius, "go to my office immediately. You members of Slytherin house, you will go to Professor Slughorn's office. The rest of you will hold yourselves available as witnesses{\el}"

She never finished. Severus, having dropped exhausted to the grass, had staggered to his feet. The pressure that had been building inside him all term now exploded. Wandless once more, he launched himself at James, knocking him down with the force of the impact, and both boys were on the grass, rolling, punching, gouging, and kicking.

The rest of the students howled with glee and rushed to surround the combatants. More students poured from the castle and the surrounding grounds, the unerring radar of teenagers telling them a fight was in progress. The three professors struggled against the pressure of the crowd, but were unable to get close enough to immobilize either James or Severus. Though exercise gave James an advantage in muscle, the two were of roughly similar build, and Severus's single-minded fury evened the odds. Every blow of fist or knee that connected on either side was greeted with whoops and cheers from the eager watchers. When Sirius tried to intervene on James's behalf, he was jumped and held by half a dozen students from three houses.

From his hut nearby, Hagrid saw the crowd and knew what was happening. He ran grunting over to the lake to toss students from his path and force his way to the center of the milling, pushing throng. He grabbed both boys by the collars of their gowns and held them at arm's length. Both twisted and struggled, trying to continue the attack, so he shook them hard as the three professors finally made it to the center. Hagrid turned to speak to Professor McGonagall, and his hold loosened. Severus was on James like a wildcat. "Prefects!" McGonagall shouted.

Remus was a Gryffindor prefect and helped hold James back, together with a prefect from Hufflepuff. Severus was in the hands of Slytherin and Ravenclaw. They glared and challenged each other across the ring of students until McGonagall could get both of them hustled back up the steps into the castle. They were taken first to the hospital wing to be treated for bloody noses and numerous cuts and bruises, and then to Dumbledore's office to answer for causing mayhem on school grounds.

Saying that Dumbledore was angry would be like saying the Sears Tower in Chicago was tall—true as far as it went, but conveying no concept of the order of magnitude involved. James and Severus were isolated at opposite ends of the Defense against the Dark Arts classroom, each under separate guard, while Dumbledore interviewed students from all the houses. Then the two were brought into his presence, James first and Severus after him to avoid the possibility of a clash on the spiral staircase.

"Master Potter, Master Snape, you will both please sit down." Dumbledore indicated chairs at opposite ends of a substantial table. Hagrid took a seat near the center. "I have been speaking with students who witnessed the altercation between you two, and it would seem that in the matter of the fist fight you, Master Snape, physically attacked Master Potter. You will both refrain from comment, Master Snape. It appears, however, that you were provoked into this attack by a series of curses inflicted upon you by Master Potter and Master Black, who will be spoken to later. Master Potter, would you explain why you cursed Master Snape?"

"I greeted him after exams. He drew a wand on me. I had to protect myself."

"Master Snape?"

"He already had his wand out. He hit me before I could turn around."

"With an Expelliarmus. Then Master Black used an Impedimenta."

"That's right."

"Let us say for the moment that you were trying to protect yourself, Master Potter. Master Snape had just been immobilized by an Impedimenta. What was the justification for you to use a Scourgify on a fellow student?"

"He insulted us."

"So you used on a helpless opponent a spell generally reserved for cleaning the bottoms of owl cages? "

"Yes, sir."

"I see. Master Snape, you deliberately attacked another student and initiated a fist fight. You will receive two days' detention. Hagrid, would you take Master Snape to your abode, run a physical examination, and discuss with him the seriousness of his offense. Master Potter, you endangered the health and life of another student with your careless and malicious use of a dangerous spell. You will remain here while we discuss the gravity of your offense and the punishment it will entail. You are in serious danger of being expelled from this school. If you would, Hagrid."

Hagrid motioned to Severus, and the two left Dumbledore's office.

"So, ya went for James Potter and ya gave as good as ya got."

"I think so."

"That's going t' be a nasty black eye. Ya want me t' get rid of it."

"I don't know. I've never had a black eye before. It could be a badge of honor. I wish I'd broken his nose. He has a nose that deserves to be broken."

"I'll reserve judgment on that. Y're not supposed t' be fighting, after all."

"Do you think he'll be kicked out?"

"Doubt it. But he'll be cleaning a lot of classrooms."

"Good."

That night began the first of the three days of the full moon, yet Severus still could not recall what had set off the warning bells in his head during his Dark Arts examination. The OWL exams continued all the next week. On Friday of the second week, Viking 1 reached Mars, but Severus was not in good enough spirits to notice. Then came the last week and preparations for the end of year and summer holidays.

During all that time, Severus and Lily did not speak even once to each other.

It was, Severus figured, the last time he would return home with a next-day train ticket and an overnight at St.~Pancras church. He would turn seventeen before the end of sixth year, and then he could apparate. Once more. Once more at the beginning of sixth year, and he would be done with this drill for ever. This year, however, he decided to vary the routine.

Severus had never been to Diagon Alley, but he knew where it was and how to get there. The Underground took him to Charing Cross Road and the dingy little pub called the Leaky Cauldron. A passage through a wall, and he was in the crowded London marketplace of the wizarding world.

There was only one place he wanted to go—Flourish and Blotts. Severus spent a pleasant couple of hours going through dozens of books, finally picking out five that he thought he could afford. Four he deposited in King's Cross Station with the rest of his things, taking \emph{Witch Trials of the Seventeenth Century} with him to read that night and on the train.

Nana met Severus at Colne, and they slipped into an alley near the train station where she could apparate unseen to her cottage. Over tea he explained to her why he still had the traces of a black eye. "Good for you," was Nana's reaction. "You stick up for yourself."

A week later, Severus was back at his parents' house with a basket full of food that Nana prepared for him. He was planning to stay for several days, and maybe get some work done. After unpacking, he started to clean. The electricity and gas were off, but the water was still running, rusty at first from sitting so long in the pipes. Severus found a small supply of candles and decided that with coal and candles he didn't need electricity. He didn't really need candles if he rose and slept with the sun.

It was nearly two years since Eileen and Toby died, and now Severus was prepared to face the stain on the carpet at the foot of the stairs. He scrubbed it for half an hour, and it became fainter, but he couldn't get all of the blood out. As twilight sent long shadows through the house, he had a late supper and climbed the stairs to his little bedroom. It and everything else in the house seemed much smaller than he remembered.

\emph{Go back to bed, Toby. You've had too much. You're still drunk. Sleep it off before you go out again.—Leave me be, woman! A man's got the right to go where he will and no woman standing in the way!—I won't let you! You're in no condition to be on the street.—Get out of my way!}

There was a scream and the sound of something heavy falling on the stairs. Severus was awake at once, ready to help his mother. He burst onto the landing and{\el} there was nothing there. \emph{A dream. I was dreaming.} He went back to bed and lay awake for the rest of the night, but the sounds didn't recur.

The second day, Severus began clearing out the storage room and sorting everything into two groups. The things he thought he would use he moved downstairs. The things he knew he wouldn't need he shifted into his parents bedroom. He was thinking of converting the storage room into a workshop or laboratory. He couldn't use the front bedroom for anything, but it didn't bother him to store things there.

That night he had the same dream of his mother falling down the stairs. This time, after the shock of waking suddenly, he lay in bed and listened. The house was silent. Severus got up and went out onto the landing, but there was nothing there. \emph{A dream. Only a dream.}

The third day Severus was in the sitting room sorting books. He was trying to think of a way to make bookcases around the sides of the room. If he continued to make money tutoring, he could afford to buy a large number of books and wanted someplace to keep them.

There was a pop that he recognized as the sound of someone apparating into the kitchen. Puzzled, Severus started towards the back of the house to see who it might be, only to meet Nana coming out of the kitchen clearly looking for him.

"There you are child. I'm glad you look presentable. We need to leave right away."

"What's happened, Nana?"

"It's your grandmother. She's had a stroke."

Together Severus and Nana apparated to Gra's house.

It was over before they got there. The stroke was a massive one, and Gra lived for less than an hour after it happened. Severus and Nana went first to the hospital in Colne, then to Gra's house where they stayed while Severus took care of the administrative details of funeral, taxes, and inheritance. Gra's neighbors knew him from previous visits and came to offer their condolences together with gifts of food. Everyone was very kind, though they seemed wary of Nana.

The funeral was in the little vicarage church. There was a plot in the cemetery there where Severus's grandfather already lay, and Gra was placed beside him. Toby and Eileen were there, too. Nana took one of Edward Snape's three suits and altered it for Severus so that he looked quite distinguished as Gra's chief mourner. Severus was amazed at the number of people who were there to pay their last respects.

Nana hosted a reception at Gra's house afterwards, and people came up to Severus all afternoon with stories about his grandmother: how she had worked as a mechanic during `the War,' and brought trays of sandwiches to the men demonstrating during a strike at the mill, and delivered the Anderson baby when the midwife was sick with influenza. It saddened Severus to think how little he'd known about her.

For the next few weeks Severus and Nana went through the whole house. There were three basic categories—keep, sell, and give to charity. Most things went up for sale. Severus kept the books and those things that reminded him most of his grandmother, and anything that looked as if it might have belonged to Wensley.

Then the house was locked and put up for sale. Severus went back to Nana's for a few days, and finally returned to his work at his parents' home.

That night Severus dreamt again of Eileen falling down the stairs. The next morning he moved everything left upstairs that he would need into the lower part of the house. He looked through his father's meager tools and selected a heavy mallet and a crowbar.

The first swing of the mallet smashed into the stair railing and sent slivers of wood flying across the room. Carefully, methodically, Severus demolished the entire railing. Then, starting at the top, he used the crowbar to pry up every tread and riser, and finally took out the stringers with a combination of both tools.

With a pair of heavy shears, he cut away the section of carpet at the foot of the now destroyed staircase and burned it in the area yard.

After that, Severus slept without dreaming.

The debris from the staircase turned out to be very useful, for with it Severus began making the first of his bookcases. It took him six days because he had to keep undoing things that weren't fitting together right, but in the end he had a place for most of the books that had been in the upstairs storeroom. He decided that he could go through Gra's books the next summer, when the pain of her death had worn off a little.

It was then that Severus began to wander again. He spent whole days out on the moors rediscovering old haunts and the flat areas where he and his mum had dueled. He climbed the fence around the dilapidated old mill and prowled the huge workrooms with their dusty, silent machines. On the afternoon that he realized he hadn't opened his mouth to say a single word for three days, he decided to go around to Mrs.~Hanson's house, only to find she was visiting her sister in Manchester. From Mrs.~Hanson's, he went straight across the bridge, past the school, and to the playground where he'd first told Lily she was a witch. He sat there all afternoon and evening, until the late summer sunset tinged the northwestern sky with red. Then he went back to the empty house in the empty town where not one person knew who he was or cared. The next day he returned to Nana.

Severus spent the rest of August with Nana, working in her garden and brewing medicines. It was strange realizing that Nana was now the only member of his family left, and then it hit him that he'd been the only one left of her family for nearly two years. He started wheedling stories out of her, stories about her own parents and grandparents, and anything she knew about the Prince side of the family, too. He bought a notebook and jotted down every detail, worried that if Nana died suddenly all that information would be lost. Sudden death was a constant in life, always lurking in potential ambush.

The other thing Nana did for Severus was help him get his bearings again. After all, it was Nana who thought that `muggle' was an ugly word, and reminded him that they were all of them people. Out there in the calm countryside of eastern Lancashire, it was easier to see the bonds that held the community together, the shared hardships that made neighbors so important. School and house rivalry seemed distant, and the whispers of `you know{\el}' more distant still. Severus decided that `muggle' indeed was an ugly word, and `mudblood' therefore uglier still. He resolved to try to talk to Lily again.

It was the end of August, and time to return to Hogwarts.


