% A Difference in the Family: The Snape Chronicles (Rannaro)
% What Of My Soul, Dumbledore?

\chapter{The End of All Things}

With Snape away so much of the time taking care of Bella's business, the Carrows began to flex their muscles at Hogwarts. Amycus's plans to use students on detention as targets for curse casting was hampered by the fact that the other teachers suddenly stopped giving out detentions, and so the numbers were kept very small. Other students began getting in the way of the curses, and secret meetings were held to plan strategies.

Neville Longbottom was turning into a ringleader. Dumbledore's question to Snape - If you were one of those students? - was also being answered in the affirmative by Longbottom, who had uncovered an important weakness in the position of the Ministry and the Carrows - there were very few truly pureblood families left. Truly pureblood students were precious, and not to be placed in serious danger. And if any family was purest of the pure, it was the Longbottoms.

Longbottom was immune. Not immune from punishment, but immune from serious physical danger. He therefore took it upon himself to deflect punishment away from others onto himself, and at the same time encourage defiance. He challenged authority and insulted the Carrows in their classrooms. He helped hide students who were in trouble, and Snape had no idea where he was putting them. He was, truth be told, acting quite heroically, though Snape could never say so to anyone but the portraits.

It was the meetings that threatened to bring down everything. Students who met in twos and threes, then regrouped in other sets of twos and threes, were one thing. When they started coalescing into groups of six, ten, and fifteen, it was a problem.

The problem centered on Slytherin house. Larger than the others, Slytherin was also the Death Eater house. The parents, uncles, aunts, cousins, siblings of the Slytherin students were the operatives that Snape was making potions for in his laboratory. While opposition to Snape and the Ministry were covert, Slytherin was a minor problem. When it came out into the open, students began sending home owls with messages that the headmaster wasn't acting loyal enough.

Snape clamped down on the school again.

Then there was Hagrid. Snape, on his way to visit Hagrid the evening before Easter break began, was surprised when Hagrid met him halfway up the hill. "Tonight ain't a good night," Hagrid said. "I'm busy working on something."

Snape nodded and started to go back, when a burst of faint laughter erupted from the hut, then died away. "Hagrid," Snape asked, "why are there students in your hut?"

"Tain't nobody there, sir," Hagrid replied shiftily. "I'm just... eh... hatching golliwogs."

Snape found out about the golliwogs two days later when the first of the owls from irate Slytherin parents began coming in. It seemed that the story was the first thing out of the mouths of their sons and daughters as they stepped off the train.

"Support-Harry-Potter parties!" Snape screamed at Hagrid, waving the letters under his nose. "Do you want to go to Azkaban! Do you want me to go to Azkaban! I'm walking a bloody freaking tightrope here and you're holding Support-Harry-Potter parties!"

"I just wanted to give 'em a bit of a boost. Keep up their morale." Hagrid shifted uneasily in Snape's office, looking around at the slumbering portraits as if hoping for support.

"What about MY morale? I'm already being accused of lack of sufficient zeal in carrying out Ministry orders, and Bella Lestrange is breathing down my neck! Do you want Rabastan or Rodolphus in this office? Because you've been working at it pretty hard!"

"I'll stop 'em right away, Professor. No more parties."

But it was already too late. The next afternoon Snape got a Floo message from Law Enforcement at the Ministry. Headmaster Snape was requested to open the Hogwarts gates, as a special team was apparating into Hogsmeade to apprehend and arrest the dangerous dissident known as Rubeus Hagrid, who was also known to be on Hogwarts's grounds.

Snape stared at the fire. \emph{What am I going to do? I can't let Hagrid be arrested, but if I warn him, they'll know it had to be me. It's so obvious. They tell me they're coming and Hagrid immediately runs. They'd arrest me on their way out.}

And yet, he couldn't let them take Hagrid. Not Hagrid. Sending Filch down to the gate, Snape walked to the edge of the cliff and looked down at the lake. He had a little time before Filch reached the gate, and a minute or so after that before the Ministry team would be able to see the hut. With a whisper and a prayer, he sent the delicate, beautiful little doe down to Hagrid, then reentered the castle. He had to be far away when events unfolded. He watched from a first floor window.

At first Snape wondered if Hagrid had even understood the message. The doe was unfamiliar to him, and there was no movement around the hut. Then Hagrid appeared in the rear, sending Fang into the Forbidden Forest. Snape breathed a sigh of relief. Hagrid was going to pretend he saw the arresting team coming.

The drama was short, but well-played. Hagrid walked out of the hut, reacted in surprise to the advancing team, seized a log and, roaring defiance, hurled it at them to make them scatter, then raced toward the forest. Once he was inside, they would never find him.

It was a terrible thing to know that Hagrid was gone, that now nothing remained except the cold company of the portraits. For three and a half months, only the silent sympathy of Hagrid had stood like a wall between Snape and crushing loneliness. Now that was gone. Snape locked himself in his office, the stillness of the nearly empty school like a tomb around him.

For hours he stood at the window, looking down at the lake. Supper time came and went, but Snape didn't notice. He wasn't hungry, and now there was no Hagrid to see that he ate anything. The sun set shortly before eight o'clock, and the long northern twilight stretched out, and finally Snape went up the short spiral staircase from his office to his bedroom and lay there, facing the wall.

After a while, Snape slept.

The voice that woke him in the small hours of the morning was shrill, desperate, and panic-stricken. "Snape!" it screamed. "Snape! For God's sake, Snape! Please, come! Please, answer me! Please, Snape!"

Snape scrambled off the bed and rushed down the stairs to the fireplace. The pale green light of Floo communication illuminated the office, and even before he saw the heavy-lidded eyes, now wide with terror, and the mass of dark hair, Snape knew that it was Bella calling him, and that something was horribly, horribly wrong.

Dropping to his knees before the remains of the fire, Snape spoke quickly. "It's me, Bella. I'm here. What's happened? Bella, are you all right?"

Instead of answering, she screamed. Snape watched in horror as her face twisted and writhed before his eyes, and he knew she was being tortured with a Cruciatus curse. Then it stopped, and with a sob, she spoke.

"This is what happens to all who displease the Dark Lord. He will crush the proud and the ambitious and all who presume to substitute their will for his or detain him on the path he has chosen."

"Lord," Snape gasped, himself now terrified, too, "tell me what you wish, and I will do it!"

Bella paused, listening for instructions on her side of the fire, then she looked Snape in the eyes. "Would you execute this miserable slave who has failed me?" she asked.

"Yes," Snape replied at once, and Bella closed her eyes in fear.

A moment later she was speaking again. "Here are your instructions. The Dark Lord goes now to the gates of Hogwarts. You will let him in. You will speak no word, and you will cast no spell. You will return to the castle and await the Dark Lord's coming. The Dark Lord's business is not yours." Bella opened her eyes again. "He is on his way. Go now, Severus, quickly. Do not make him angrier than he is."

Snape was on his feet at once, racing for the door, the stairs, pausing only to grab a lantern in the entrance hall and then heading out onto the lawn. The quarter moon had set three hours earlier; the sun was not even a faint promise on the horizon. Snape had to slow his speed for fear of missing his step in the wavering light from the lantern, and it bobbed up and down in his hands as he moved down the hill toward the gate, his heart fluttering like a caged bird in his chest.

The Dark Lord was back, back and raging in anger. He'd tortured Bella... Bella and who else? And for what offense? And his first stop was Hogwarts. Why? Why?

Snape forced himself to act calmly, for the Dark Lord already stood cloaked at the gates. He fumbled a little as he opened them, and bowed the Dark Lord in, locking the gates again afterwards. The Dark Lord did not speak, and Snape, too, was silent as they moved along the path into the grounds. Then, where the path divided, one side up the hill to the castle, and the other around toward the lake, the Dark Lord turned the slits of his crimson eyes on his servant.

"We shall join you in the castle shortly. Leave us now." His voice was high and cold, and full of menace.

Snape bowed and walked up the hill, not once glancing back. The Dark Lord's business was not his business, and he still did not know if Bella's crime included some action of his own. He reached the great oak doors and stepped into the entrance hall. There he waited.

Minutes passed, a quarter of an hour, and then the Dark Lord glided into the entrance hall, and Snape once again bowed. "Your office," the Dark Lord said, and the two climbed the long staircases to the seventh floor and the gargoyle staircase.

Once inside, the Dark Lord looked around. "It is unchanged," he said, seating himself behind the headmaster's desk, "except for the new portrait of an old fool."

Not sure how to respond, Snape asked, "Does my Lord wish refreshment?"

The Dark Lord chuckled, and it might have been the pleasure of an event remembered, or anticipation of pleasure soon to come, still no clue to what Snape might face in the next hour. "Yes, Headmaster, we are pleased to accept refreshment. This night, that started in disappointment and anger, will end in victory and the destruction of those who oppose our will. You may pour us a glass of mead, and then you will stand before us and answer our questions."

Snape waited, as the Dark Lord sipped the mead in lingering appreciation, and watched his nervous servant. Finally tipping back his head, as if sniffing with his slits of nostrils, the Dark Lord said, "Tell us who among our servants is loyal."

Quicksand... gaping pits... an open mine field... "Lord, forgive me if in ignorance I displease you, but I know of no disloyal servants. All who..."

The Dark Lord raised his hand, and Snape stopped. "Wormtail is dead," the Dark Lord said with a sneer.

Snape said nothing.

"Does this news please or displease you?" the Dark Lord asked.

"I don't know, Lord," Snape answered. "If he died for transgressions against you, then I'm pleased. If he died in your service, I'm not pleased."

"He failed us," the Dark Lord said, "and his punishment was deserved."

"Then I am pleased," responded Snape. His defenses were going up, and his feelings were locking down.

"Bella, too, has failed us. This very night she called us, summoned us from our task to give to us the person of Harry Potter, but allowed Potter to slip through her fingers before we arrived. Summoned us in order to present us with failure. Not only that, but she has lost our other prisoner, too. She has lost us Ollivander. It matters not. He was of no further use to us, for we have progressed far beyond his poor knowledge, but the failure to guard was a grievous fault in Bella."

The pause seemed to await an answer. "Then she deserved her punishment, Lord," Snape said.

"And now, Severus, we will discuss your failure."

Snape slipped instantly to his knees, his heart in his throat. "Lord," he gasped, fighting to control his voice, "punish me for my failure, but I beg you also to enlighten my ignorance, for I do not know wherein I have failed."

The Dark Lord chuckled again. "You amuse us, Severus. So different from Bella. She tries to push blame and punishment onto others. You cry, `punish me, punish me.' Yet which of the two is more successful at avoiding punishment? Still, we must be fair to Bella, who at least did have the person of Harry Potter in her possession when she called us, whatever may have happened after that. What have you done to secure the person of Potter?"

Not waiting for an answer, the Dark Lord pointed his wand at Snape and said lazily, \emph{"Crucio."} Snape doubled over in pain and lay on the floor, clutching at the carpet. Yet he had endured far worse, and this was a mere game. Still, it did not do to spoil the Dark Lord's pleasure by self-indulgent courage and endurance. He cried, and kicked, and whimpered in agony until the pain abated.

"Stand up," said the Dark Lord, and Snape struggled to his feet, trembling. "Is the old fool of assistance to you in your labor here?"

Snape didn't look at the sleeping portrait. "They are only shadows of the people they represent. They can be amusing, but they're not as much help as their reputation would have us believe."

"Require it to speak to us."

"Headmaster Dumbledore," said Snape formally. "I want to talk to you."

The portrait coughed, and blinked, and looked around as if befuddled. "I beg your pardon," it said, "I seem to have been dozing. How may I be of service?"

Snape looked at the Dark Lord, who merely nodded to him. "Dumbledore," Snape said, "we have a guest."

The portrait looked down. "Goodness me, it is Tom Riddle. You will not know this, Headmaster, but Riddle here was one of the best, most successful students Hogwarts has ever known. Why I remember back in forty-three when he was first made a prefect..."

"Thank you, Dumbledore," said Snape. "Do you have the information I requested about the Astronomy class?"

"Yes, ahem. Hogwarts acquired its first telescopes in 1732. About 1860, we suffered a severe setback when Headmaster Burke mistakenly replaced them with prism binoculars under the impression they would see twice as far. I remember as a much younger teacher running across..."

The Dark Lord laughed. "An old fool indeed. You will see us out, Severus."

Snape returned to the office fifteen minutes later. He was still trembling. "I still don't know what I did to make him angry," he confessed to Dumbledore.

"You did not make him angry, Severus. He wanted an excuse to try out the wand, and I commend your acting ability. You were a bit preoccupied so you probably did not notice, but the wand he used to torment you with was mine."

\sbreak

"Where are they?" Snape demanded of Nigellus for about the hundredth time. "Something must be happening!"

"Albus," Nigellus said, pointedly bypassing Snape, "would you remind this importunate young man that I have told him repeatedly..."

"Phineas has told you repeatedly, Severus, that Miss Granger has not opened her bag in many days, and it has been a few weeks since she took the tent out. Since before they ran into Bella, in fact. We must only assume that they are staying with someone who is protected, probably by a Fidelius Charm. It could be anybody."

"Meanwhile, he gets stronger. Now that he's in Britain and has a new wand, he's getting stronger. And nobody knows where Potter is."

"I am certain someone knows, just not you. Now, Severus, if we could go over..."

"Why? We've done it so many times."

"Because you are the one who has to do it. You are the one who has to convince Harry that you really do work for me and that what you have to tell him is significant, of the utmost importance, in fact. Riddle's having the wand will play into our hands."

"How?"

"It will make him confident of success, and remove the last barrier to action."

Snape sighed and began to recite. "I tell Potter that you and he spent all last school year discussing Horcruxes. Horcruxes are items that contain a fragment of soul. Their function is to tie the soul to earth so that the person cannot be killed, as the Dark Lord was not killed by the ricocheting of his killing curse. I tell Potter that you showed him pensieve memories of the Dark Lord's acquiring of the Horcruxes. One commemorates his shrewdness as a student and the fact that he was Slytherin's heir - the diary that was already destroyed. Another commemorates the blood lineage of the Peverells, the one that somebody was stupid enough to try wearing - the ring of Marvolo Gaunt which has also been destroyed. Then there was something from each of the Founders - Slytherin's locket - destroyed, Hufflepuff's cup - not located yet, something of Ravenclaw's, but we don't know what it is..."

"Well that might also be Gryffindor's, Severus."

"I don't think so. I think it's Ravenclaw's"

"I would appreciate it if you would explain your logic."

"You told me that Potter is an unintentional Horcrux because the Killing Curse blasted away a fragment of the Dark Lord's soul and it attached itself to the only living soul left in the building - the child. But Horcruxes aren't usually living things. They're usually objects. Why couldn't that fragment attach itself to a chair, or a sliver of wood? I think it's because the Dark Lord intended to make a Horcrux of something belonging to Gryffindor, and a Gryffindor student belongs to Gryffindor, right?"

"Severus, I do not want to break this to you too harshly, but Harry was one year old. He was not yet a Gryffindor student."

"But his father was Gryffindor, and his mother was Gryffindor, and it was a foregone conclusion that he would be..."

"The Hat wanted to sort him into Slytherin, but he asked it not to."

Snape stared at Dumbledore in disbelief tinged with sarcasm. "I'll never believe that," he said at last.

"I fear you must. The Hat confirmed it to me."

"No. The Hat was fooled by the fragment of the Dark Lord's soul. That's the only reason it thought about Slytherin. That boy is no more a Slytherin than I am..."

"A Gryffindor? But if courage is the mark of Gryffindor, Severus, you really should..."

Snape slammed his hand down on the desk. "You keep this up, and I'm going to go into the lavatory and be sick to my stomach!"

"Shall we get back to the original topic, Severus? We have strayed somewhat."

"The point is, that when the Dark Lord realizes that the Horcruxes are in danger, he's going to become very protective of the snake. That's when things have to happen in the right order, and Potter has to know about it. The rest of the Horcruxes have to be destroyed, including the snake, and then Potter has to let the Dark Lord destroy him. After that, the Dark Lord can be killed. For the last two years the Dark Lord hasn't wanted to duel Potter because of what happened to his wand, but now he has a wand that gives him confidence that he'll win the duel, so he won't hesitate to kill Potter. He won't be expecting Potter to just let him do it - and that's what I have to get Potter to believe."

"Perfect, Severus. You always were a quick study."

"Yes, but I'm making book right now that Potter will kill me before I get to that part. And then where will we be?"

All through April the situation deteriorated. Bella and the Malfoys were under house arrest, and the Carrows became terrified that they weren't showing sufficient enthusiasm for their job. Their intimidation tactics against the students expanded to include incarceration and torture. Neville Longbottom disappeared, but from the reaction of the Carrows it had nothing to do with them. Other students began disappearing as well, and when Snape tried to rein the Carrows in, they threatened him.

"Can't you get it through your head, you fool," Amycus yelled at Snape in the headmaster's office, "that Potter got into the Malfoy mansion and helped prisoners escape! These little rats in this school will do anything to help him. We have to break them! crush the life out of them! or we'll end up like Bella and Lucius! Do you want to be screaming on the floor while he Cruciates you!"

"I thought I was here to protect Hogwarts!" Snape in his turn yelled at the portrait of Dumbledore. "To protect the students! How am I supposed to do that if I can't even control Amycus Carrow!"

"Easy, Severus. Easy. Your primary function is to make sure that Harry knows what he has to do when he meets Riddle. Everything else, yes including the temporary welfare of the students, is secondary. Riddle loved Hogwarts as much as he can be said to have loved anything, and I am sure one of the items is here. It may all come down to here, and here you must remain, even if sacrifices are made."

Snape was now sleepless most nights, rolling everything over and over in his head, trying to find an answer that would lead to success without at the same time destroying everything else. It was at this point that he became convinced that he was going to die.

\emph{A pig raised for slaughter. Dumbledore's known for years that Potter has to die; has he known about me equally long and with equal certainty? And what a death for Potter, the little hero, the pinup boy of half wizarding Britain. To be able to stand there and know - know - this is the moment of victory. This is the moment the Dark Lord falls. And then a painless Killing Curse. And my death? Tortured in a cellar? Killed by someone I used to think was a friend in the middle of a fight? And not one person will know. Not one will mourn me.} The nights filled with those thoughts were very bitter.

Worse, if anything could possibly be worse, was that more and more he was beginning to distrust Dumbledore. \emph{On the Astronomy tower, I did what he asked me to because I believed him. I trusted him that it was the right thing. But does he, in fact, want the right thing? Some of the things in that biography make him sound as bad as the Dark Lord. What if telling Potter to allow himself to be killed is the wrong thing, and only makes the Dark Lord stronger? Am I so sure that Dumbledore is right?}

A memory surfaced then, as disturbing as any thought Snape had ever harbored. It was the memory of the night that Dumbledore had told him that Potter himself was a Horcrux, that Potter had to die. They were sitting there in Dumbledore's office and... Dumbledore closed his eyes! Snape sat up in bed. He focused his thoughts and brought the image back. It couldn't be right. He hurried down into the office, though it was two in the morning, and opened the cabinet where Dumbledore kept his pensieve.

"What are you doing, Severus?" the portrait said, but Snape ignored it. Placing his wand to his temple, he pulled out a thin filament of thought and let it swirl in the bowl. He gazed at it for a long time. He had not been mistaken. All during the time that Dumbledore was talking about Potter being a Horcrux and having to be killed by the Dark Lord - his eyes had been closed.

Snape looked up at the portrait in horror. He was shaking like a leaf, and his breathing was shallow and fast. \emph{He didn't want me to read him. He didn't want me to see the thoughts behind the words. Because the words were lies. I'm supposed to tell Potter what to do, and I'll be telling him lies.}

The portrait continued to question, "Severus, what is wrong? What is upsetting you?" but Snape wouldn't answer. Carefully replacing the thought into his head, he put the pensieve back in its cabinet and went up to his bedroom. For three days he spoke to no one, no person, no portrait, and was utterly, utterly alone.

In the clear light of day, Snape could see that he was overreacting. There was no doubt that the Dark Lord was evil, and must be destroyed. There was no doubt that Dumbledore and the Dark Lord were enemies. There was no reason for Dumbledore to lie to him about the manner in which the Dark Lord had to be destroyed. But then why be so careful to shut him out? Why shield his thoughts?

In the clear light of day, Snape believed, but in the cold dark watches of the night, doubt and fear filled his soul, and Snape thought of all he'd been asked to do, and had done, for the man he'd once trusted so completely - of the murders of Dumbledore, Moody, Burbage, and Scrimgeour, of the students he could not help and the boy he would lead by the nose to his death, and Snape knew himself lost. Lost and damned. And he hated Dumbledore for what he had become. And he stopped eating altogether.

Then, at the beginning of May, the portrait of Nigellus brought news. "They took out the bottle of Polyjuice potion. Today. They're doing something today."

What that something was, neither Snape nor the portraits knew, and they could only watch and wait, and hope for the best.

That night, all hell broke loose.

It started at dinner, so Snape, who no longer sat in the Great Hall at mealtime, didn't hear it. What he heard was a nearly hysterical Alecto Carrow screaming at the gargoyle, "Let me in! Let me in, do you hear me! Snape! Snape!" He admitted her at once, and she crashed into his office in panic.

"Something's happened," Alecto shrieked. "Something terrible's happened! The kids are yelling it all over the Hall. Amycus shut up the Boot rat, but now the others are... They say Potter robbed Gringotts today!"

"Robbed Gringotts? Nobody robs Gringotts! Calm down Alecto. Tell me everything you heard."

"This little rat, Boot, comes running into the Hall just as dinner's started waving a piece of paper and yelling about Potter. He says Potter's robbed Gringotts Bank and that he and his friends got away on a dragon... and then Amycus got to Boot and slapped him silly, but now they're all yelling..."

"Shut up!" Snape yelled at her. "I don't care how many people are yelling! They were down where the dragon is?"

Alecto nodded, Snape's more focused fear affecting her now, too. "They unchained a dragon and rode it out of the bank."

"I saw that dragon in September," Snape said, feeling the adrenaline pour into his system. "That's where Bella Lestrange's vault is. That's where Gryffindor's sword is." \emph{But Potter wouldn't be after the fake sword because he has the real one. And Bella's been known to keep things for the Dark Lord before...}

Snape wheeled and grabbed Floo powder. "Headquarters!" he cried, "Infirmary!" and looked around for any of the healers. "This is Hogwarts school!" Snape called, aware that his voice was unusually loud. "Shane! Nugent! Is anyone there?"

A healer's face appeared in the flames. "Hogwarts," he said, "watch your back. He got bad news a few minutes ago. They're sending in the bodies now."

"Bodies? What bodies?" Snape called back. "What's happened?"

"Haven't you heard about Gringotts? They stole something of the Dark Lord's. He killed the goblin who brought the news, then started killing everyone in the room he could reach. They've already brought in Barrows and Quinley. Most of the dead were lower echelon. I have to go. There may be wounded as well."

Snape closed the connection and stared in shock at Alecto. A second later he was paying no attention to Alecto, for the Dark Lord was on the Floo network and asking for him, coldly and insistently. "I'm here, Lord," Snape stammered.

"Good. One at least is at his post. You must be alert this night. Potter will try to enter Hogwarts. He must be stopped. He must not be killed, but he must be stopped. He will go to Ravenclaw tower. Wait for him. Notify me when you have him."

"Yes, Lord," said Snape, but the Dark Lord was already gone.

Quickly Snape hurried down to the Great Hall. "Heads of houses!" he bellowed above the noise, and there was a lull. "Students will proceed at once to their houses. Prefects, see to it that there are no stragglers. Heads, I want a roll call and a report on anyone missing. If students didn't get a chance to eat, send up food from the kitchens. When all students are accounted for, I want all staff back here. Go! Now!" The fury, the urgency, radiating from his thin body was intimidating. Only McGonagall stood up to him.

"Ye'll not be punishing the whole school for a wee bit of gossip!"

Snape whirled on her, "Professor, you know nothing of what's happening. Do as I say, and do it now!"

"Ye'll not talk to me like that!"

"Woman! Look to your house!"

McGonagall paled, but held herself with great dignity and shepherded Gryffindor house from the Hall.

Snape waited until the teachers, with the Heads of houses, had reassembled. As the time passed, he began to calm down. The students were protected - it was the first, the most important concern, regardless of what Dumbledore thought. The next important thing was that Potter, Harry Potter, might be coming to Hogwarts, perhaps that very night. Snape's two masters both wanted him to meet Potter, the Dark Lord to take him prisoner, and Dumbledore to give him instructions. And if Dumbledore was right, both masters would get their wish. Snape longed to know how much of his mission Potter had already accomplished, but that might not ever be his to know. Now he could only do what was set before him to do.

It had been Snape's first intention to patrol the corridors and stop Potter. Now, on reflection, he did not want to do that. To the staff he said, "There is potential for trouble tonight. Students must stay in their houses. Teachers will walk their normal patrols. If anything unusual occurs, notify me at once. Professor Flitwick, it will be necessary for Professor Carrow" - he indicated Alecto - "to spend the night in Ravenclaw tower. You will admit her." He did not explain.

Then came the tense calm of waiting. Snape talked to the portraits for over an hour.

"Did he say anything about the snake, Severus. Has he started protecting Nagini?" It was not the first time the question had been asked.

"I don't know. It was short and concise. He would never tell me something like that anyway."

"It is vital that all the Horcruxes, Nagini included, be destroyed first. If that doesn't happen, all is in vain."

Snape looked at the portrait and sighed. "Did you tell him the snake was a Horcrux?"

"Yes, well that I thought it might be. Harry listens quite well."

"To you he listens. He's never listened to me. What if he won't listen, or won't believe. My telling him could cause him to do the opposite." Was that why you closed your eyes, Dumbledore, because you want him to do the opposite and do not want me to know?

"I wonder," said Dumbledore, "if Harry knows he is looking for something of Ravenclaw's."

"If he doesn't, I can tell him. I can at least tell him that the Dark Lord expects him to go to Ravenclaw tower and plans to capture him there."

"If Harry can get in, destroy the Ravenclaw Horcrux, and get out without being discovered," said Dumbledore, "it will be a good thing. We will have time to plan our next move."

Snape jumped then, shock adding to the violence of his reaction, and stared down at his left arm." She's called him," he gasped. "Alecto's called the Dark Lord. She has Potter. How did he..." He was on his feet at once, heading down the spiral stairs.

"Severus," Dumbledore called after him, "Severus, good luck," but by that time Snape was too far down the steps to hear.

He walked, as McGonagall had noted so many years ago, as quietly as a cat. There was nothing in the corridor near the gargoyle, but then Alecto was in Ravenclaw tower, so Snape made his way through the seventh floor corridors and was stopped by the sound of voices. He slid into shadow.

Amycus was talking. "Go and get Flitwick! Get him to open it now!"

"But isn't your sister in there?" came McGonagall's voice. \emph{Drat!} thought Snape. \emph{Trust her to be prowling around trying to find out what Alecto's doing.}

Snape listened to the two argue, then McGonagall agreed to open Ravenclaw door. Amycus's howl of shock and anger reverberated through the floor. "What've they done, the little whelps? What's the Dark Lord going to say? She's gone and sent for him, and we haven't got him!"

McGonagall's voice came again, calm but somewhat exasperated. "She'll be perfectly all right."

"Not after the Dark Lord gets hold of her! He thinks we've got Potter!"

"Got Potter?" Enlightenment swelled in McGonagall's voice.

"We was told he might come in here. We can push it off on the kids, say Alecto was ambushed..."

McGonagall was on her high horse again, talking of truth and lies, of courage and cowardice... "You are not going to pass off your many ineptitudes on the students of Hogwarts. I shall not permit it."

"It's not a case of what you'll permit. It's us what's in charge now."

Snape could not see what was happening, but what he heard next sent a tremor through him.

"You shouldn't have done that," and the voice was Harry Potter's. It was followed immediately by the shout, \emph{"Crucio!"} and the sound of a falling body.

Snape waited for McGonagall's explosion of righteous anger, but the ensuing exchange made it clear she only objected to Unforgivable Curses when they were cast by people she didn't like. She had no problem if it was Harry Potter. \emph{And I'll make sure she never forgets it,} Snape thought.

There was quieter talking, harder to hear, but Potter mentioned the Diadem of Ravenclaw. That was the Horcrux, but it was equally clear that Potter did not know where it was. Then McGonagall was talking about barricading the school against the Dark Lord while Potter searched for the Diadem.

\emph{No}, thought Snape. \emph{That puts everyone in danger. You have no idea of the forces he can move against the school. And what of the children? You may think it anathema to kill an eleven-year-old, but he wouldn't bat an eyelash}.

They were coming. Snape saw only McGonagall, who conjured three patronus cats to summon the other Heads, but he was sure Potter was under the Invisibility Cloak. He followed softly behind them until McGonagall heard his steps, turned, and said, "Who's there?"

McGonagall's wand was up, pointed chest high at her unseen opponent. Snape let his own slip from sleeve to hand, ready to use it if necessary, but still relaxed, pointed at the floor. He took a deep breath and stepped around a suit of armor that blocked her view.

"It is I," Snape said, but he wasn't paying as much attention to her as he was to the air around her. Potter was here. The primary reason for Snape's being at Hogwarts was standing in this corridor, and Snape couldn't see him because of the hated Invisibility Cloak. He couldn't speak to him either, or both Potter and McGonagall would know he was looking for Potter, and the way things stood now, that would guarantee her keeping Potter away from him. She had that fierce air of a lioness protecting her cubs. Snape stalled.

"Where are the Carrows?" His voice was calm, as if this were a perfectly normal situation, standing there with her wand pointed at his heart.

"Wherever you told them to be, I expect, Severus."

Slowly, not wanting to provoke a reaction, Snape eased forward, trying to identify the spot where something magic didn't block his view. He kept talking, distracting, "I was under the impression that Alecto had apprehended an intruder." I came because of that, not because I'm spying on you.

"Really? And what gave you that impression?"

The tingle from Alecto's call was still there, and Snape moved his left arm as an answer to McGonagall's question.

"Oh, but naturally. You Death Eaters have your own private means of communication. I forgot." There was scorn in her voice, and Snape registered that this was the first time she'd ever flatly called him a Death Eater. It was a wall between them when he needed a bridge. The air vibrated with the unseen presence of Potter.

Snape changed the subject. "I did not know that it was your night to patrol the corridors, Minerva."

"You have some objection?"

"I wonder what could have brought you out of your bed at this late hour?"

"I heard a disturbance."

It was good. She was defending her actions. He might yet talk the situation down to a lesser confrontation. "Really? But all seems calm."

And then, maybe because they were standing so close, and he needed the information so desperately, maybe because this might be the only chance he ever got, Snape made a fatal mistake. He looked into McGonagall's eyes and made a suggestion, hoping to see her response before she was aware of what he was doing. Ready now to take the chance of explaining to her, because Dumbledore required it, and he was running out of time. The Dark Lord was already on his way.

"Have you seen Harry Potter, Minerva? Because if you have, I must insist..."

The lioness attacked, and the only thing that saved Snape was that he saw the Stunning spell in her eyes before it reached her wand. He staggered back, his Shield Charm a reflex so automatic after all these years that he was hardly aware he'd cast it.

Snape didn't want to hurt her, but McGonagall had no such qualms about hurting him. She lashed out with a rope of fire that he transformed into a cool snake to avoid being burned. The snake dissolved and reformed into daggers and Snape, horrified now by the realization that McGonagall was actually trying to kill him, knowing himself outmatched in a battle of transfiguration, flung the suit of armor between them and let it absorb the force of the knives.

There was a clatter of feet on stone, and the three Heads of house that McGonagall had summoned rushed onto the scene. "Minerva! No!" Flitwick screamed, and Snape crouched behind the armor, making no attempt to use his wand, hoping Flitwick would reason with McGonagall. But that was not Flitwick's intent. As Flitwick yelled, "You'll do no more murder at Hogwarts," the armor came suddenly to life, throwing its heavy arms around Snape and squeezing the breath from his body. Frantic now, he flung it from him against an empty wall, dove for the floor to avoid the deadly spells shot at him by people who had once been his colleagues - his friends - scrambled to his feet, and ran.

There was an open classroom door, and Snape lunged for it, intending to seal the door behind him, but McGonagall and the others were too close. His task remained unaccomplished, and Snape was cornered. If they took him now, they might kill him. At the very least, he would never be allowed to speak to Potter. He saw one way out and, forgetting he was on the fifth floor, took it. Spells streaking past him, he leapt for the outer wall of the room, twisting to hit the leaded casements with his right shoulder. His body curled for the impact, arms wrapping his head, Snape crashed through the window in a shower of shattered glass and broken lead, then plunged a hundred and fifty feet to the ground below.

Suddenly, miraculously, the fall slowed, and Snape was drawn, pulled, summoned toward the gate and Hogsmeade. Powerful wizards cast powerful charms, and it does not do to allow a servant to fall to his death before you have the chance to extract information from him. The Dark Lord had arrived at Hogwarts.

\sbreak

Snape knelt, trembling, in the common room of the Three Broomsticks where the Dark Lord had temporary headquarters. Death Eaters were apparating in from all corners of Britain. Bella and Lucius were there - and Macnair, too, who had been given the privilege of reminding Snape of the consequences of abandoning his post. Now, waiting for the first of the Dark Lord's questions, Snape was unable to straighten his doubled-up body for the pain that cramped his stomach.

"We were summoned here," said the Dark Lord, and even in his torment, Snape noted the great snake that curled beside him.

"Alecto Carrow, Lord," Snape gasped. "She was stationed in Ravenclaw tower according to your will, and caught Potter as he entered, but was attacked by other students."

"So he is there."

"Yes, Lord."

"You have seen him?"

"No, Lord." Snape hurried his answer forward, to get past the renewed pain. "He wears an Invisibility Cloak, but I heard him speak and recognized his voice."

"Why has he come?"

"He seeks something of Ravenclaw's. He doesn't know where it is."

The Dark Lord smiled, a cruel smile. "He will never find it. Take us into the castle, and we shall dispose of the `Chosen One.'"

"Lord," Snape said, "they are already fortifying the castle against you. Amycus Carrow told McGonagall that you had been summoned. They are prepared for an attack."

This was not welcome news, and Snape collapsed as the Cruciatus curse hit him. When he was released, his brain was racing. For now, finally, all actions converged on the same consequences, and now, finally, there was a semblance of choice. Casting the fears and doubts of the last few months aside, Snape chose Dumbledore. \emph{How do I manage to contact Potter? How can I find a way to let him know? I can't go back in, but Potter can come out.}

"Lord," he said, "Potter has never been able to let others suffer for him. He can be persuaded." \emph{And I'll be there. I'll find some way to tell him and some way to get him back into the castle. I will. I'll think of something.}

"Yes," said the Dark Lord. He turned to his lieutenants. "Bring reinforcements. Everyone we can pull in. Our large friends from the north, the evil things of the forest. Everything that can break down the defenses and force Potter to be noble. Inform me when it is done."

The snake draped itself around the Dark Lord's shoulders and he left, going, as everyone knew, to gaze at the castle through the ironwork of the great gate. Snape remained kneeling in the circle of Death Eaters, for he'd not been given permission to stand. It was Bella who dragged him to his feet.

"You're on probation, puppy dog. Mr. I-stayed-at-my-post-through-thick-and-thin finally turned tail and cleared out as fast as he could go. But answer one question..." Bella's voice surprisingly held just a tiny note of admiration. "Whatever possessed you to jump out that window?"

"I don't know," Snape admitted. "At the time it seemed like the logical thing to do."

"You'd better get out there and dance for him. He's going to have questions."

Snape went out to the gate and stopped a respectful distance away. There he remained as the forces gathered, a roar far to the left indicating that there was even at least one giant. When the Dark Lord moved, Snape moved. When the Dark Lord stood, Snape stood. He was a shadow, a shackled slave, a dog on a leash, constrained to stay at his master's side in case he might be wanted.

At eleven o'clock, the Dark Lord was ready. His voice, when he spoke, was amplified, magnified, projecting everywhere and through everything so that Snape, standing so close, clapped his hands over his ears.

"I know that you are preparing to fight. Your efforts are futile. You cannot fight me. I do not want to kill you. I have great respect for the teachers of Hogwarts. I do not want to spill magical blood. Give me Harry Potter, and none shall be harmed. Give me Harry Potter, and I shall leave the school untouched. Give me Harry Potter, and you will be rewarded. You have until midnight."

\emph{An hour,} Snape thought. \emph{An hour to find a way to leave the Dark Lord's side. An hour to figure out which exit Potter will use. An hour to pass on Dumbledore's message.}

He didn't get the hour for, all that time, Snape remained tethered to the Dark Lord, desperate and anxious as the minutes ticked by and Dumbledore's task slipped through his fingers. But in the end he needn't have worried. For once, Harry Potter chose not to behave like an idiot Gryffindor. Potter did not come walking out of the castle, and the Dark Lord ordered the attack to begin.

Spells shot from the perimeter to shatter against the defenses of Hogwarts, and simultaneously Snape's very being was pierced by a scream, a wild, keening wail of rage and frustration. Snape dropped, shattered by the sound, then realized as he lay on the ground that it had come from the Dark Lord.

Hope leapt up and burned fiercely, for Snape knew at once what had happened. A Horcrux had just been destroyed and now, so close and so sensitive to his danger, the Dark Lord had felt it and recognized it. \emph{How many left?} Snape thought. \emph{Was that the fourth or the fifth? Was Dumbledore right? He was right! This is really going to happen!} He looked around. The Dark Lord was gone. He'd retreated into the night, and Snape was free, free to join the other Death Eaters and try to find a way into the castle.

All of McGonagall's and Flitwick's skill was no match for the Death Eaters. Protective spells were crumbling like ancient masonry, curses and hexes shooting into the castle through broken windows and cracked stone. Snape aimed his wand at the castle, too, striking out with nonverbal blasts of red and green light, sparks and blue flame, his spells doing surprisingly little damage, for in the confusion of battle, who would notice if the bolt of red was a stupefying spell or a charm to clean away mold?

The defenders did damage, too, and around Snape the explosions, bursts of roaring flame, crack of sundered trees, and the cries and screams of wounded Death Eaters was deafening. Eruptions of explosions lit up scenes out of a nightmare as a hooded figure staggered by clutching blackened hands to its hidden face, and another tried to staunch the flow of blood where an arm had once been.

And through it all, Snape was driven by one thought - Get into the castle. Get into the castle, find Potter, and give him Dumbledore's message.

They breached the doors and poured into the entrance hall. Far above Snape's head the giants battered the walls with enormous stones, huge spiders scurried by, and Snape elbowed his way through the press, shoving others aside, parrying blows, looking, always looking, for Potter.

Then he shuddered as the distant echo, faint and almost missed, of the Dark Lord's wail of fury lanced through him. No one else seemed to have noticed. \emph{Because it was so faint. Because they don't know what it means. Do I know what it means, or did I imagine it?} The thought that another Horcrux was gone blazed through him.

The world was shattered suddenly by an explosion of such force that the fighters in the entrance hall were knocked to the ground, great stones shook loose from the ceiling and walls and fell to crush those beneath. Dust from masonry and plaster rose in a billowing cloud, and Snape struggled back to his feet coughing and wheezing.

They were making no headway in the entrance hall. The defenders were shooting from doorways, behind pillars, shielded by the sweep of the great marble staircase, and the attackers were unprotected on the wide, open floor. Snape dodged spells and tripped over bodies, trying to find a way upstairs. A way to locate Potter.

Someone grabbed his arm and he spun, wand at the ready, to find himself facing Lucius Malfoy. Malfoy's mouth was moving, but in the din of battle Snape couldn't hear what he had to say. Malfoy leaned closer, his mouth next to Snape's ear. "He wants you!" Malfoy cried. "He wants you now. Go, please. He's in the Shrieking Shack."

Snape shook his head and tried to break away, pretending he hadn't understood, but Malfoy wouldn't let him go. "Severus, for God's sake, he's asking for you! Go to him! Go now!"

It was over. That bid to accomplish his task was over. Snape followed Malfoy out of the castle and began threading his way through the dead, the wounded, the still-arriving reinforcements that crowded on the lawn. He looked up at the castle and saw that part of one wall had been blasted away entirely - the effect, probably, of the Dark Lord's rage.

\emph{The snake}, Snape thought as he hurried down the hill, leaving Malfoy behind. \emph{If that was his anger at the destruction of the fifth Horcrux, then only the snake remains. I can't kill the snake. I have to give Potter his instructions, and I can't do that if he destroys me for killing the snake. Please let me have another chance to talk to Potter. Please...}

Snape made his way through the deserted streets of Hogsmeade. The Shack was oddly quiet, an island of calm after the storm of battle. Its enchantments had been removed, allowing Snape to walk to the door, lift the latch, and enter. The Dark Lord was in the room on the ground floor, the one where Snape and James Potter had managed to escape the werewolf Lupin.

"Severus," the Dark Lord said as Snape entered. "Has Hogwarts fallen?"

"No, Lord," Snape said, bowing. "When you summoned me, we had taken the doors and were inside. The entrance hall will soon be in our hands, and we'll be able to isolate pockets of them and defeat them piecemeal. I greatly desire to give you this victory, my Lord, if you will permit me to return to the battle."

"I think not, Severus. It is something else we need you for now."

Snape was shutting down, locking and sealing the doors of his mind. \emph{I can't let him see how much I need to go back, to find Potter. I can't let him suspect.}

"Lord..." Snape paused, not wanting his desire to be too strong, too suspicious. "I can still help in this battle. I am a good fighter. I wish to see your will accomplished in this, my Lord. Their resistance is crumbling..."

"...and it is doing so without your help. Skilled wizard though you are, Severus," and something in the cold, high voice turned Snape's veins to ice, "I do not think you will make much difference now. We are almost there... almost." The Dark Lord was not, Snape realized, talking about the battle. He noticed the snake, wrapped in a protective bubble, like a cage. He was slowly filling with a deep, nameless dread.

\emph{Potter. I have to tell Potter. It's the only thing left that matters.} "Let me find the boy," Snape tried to keep his voice low and calm, not to let the Dark Lord hear his fear. "Let me bring you Potter. I know I can find him, my Lord. Please."

The Dark Lord rose from the table where he had been sitting. He was fingering a wand. Dumbledore's wand. Pieces began to click into place in Snape's head. The Dark Lord's voice was gentle. Gentle and dangerous. "I have a problem, Severus."

"My Lord?" Snape said. He looked at the wand and thought of Dumbledore, eyes closed, telling a story that Snape had to believe because Harry had to believe, eyes closed to conceal the part that Harry couldn't know.

"Why doesn't it work for me, Severus?"

Snape's face was a blank, his mind closed tightly now to block the anger that sprang up inside him. "My Lord," he said, "I do not understand. You... have performed extraordinary things with that wand." The anger was building. Anger against Dumbledore. \emph{You knew. You knew it would come to this, this last step needed to give him the confidence to use the wand against Potter. You knew. All that talk about sparing an old man pain and humiliation - an act to trick me into doing your will. Another pig led to slaughter}.

"No, I have performed my usual magic. I am extraordinary, but this wand... no. I feel no difference between this wand and the one I procured from Ollivander all those year ago." The Dark Lord paused. "No difference."

There was nothing to say. Dumbledore had fooled him, and now Dumbledore would reap the penalty of his lies, because the crucial, vital task had not been accomplished. Snape knew that he was about to die, and Potter had not been told. Hatred flared against Dumbledore, and Snape felt a certain satisfaction that the old fake had failed. And yet...

The reality of the Dark Lord was inescapable. He was altogether evil. He had twisted and blighted Snape's life, destroyed everything that gave it meaning, brought cruelty and death, and turned Snape's friends into enemies. He had killed Lily, and now he would kill Lily's son - and suddenly Snape had a glimmer, an inkling, of why Dumbledore's eyes had been closed, and he knew that in a choice between the Dark Lord succeeding and Dumbledore succeeding, he would follow Dumbledore, because there are worse things than being led like a pig... no, like a lamb... to slaughter.

He had a task. "My Lord... I beg you will let me return. Let me find Potter. He might be killed accidentally by one other than yourself..."

The Dark Lord spoke of his wand, dragging out the moment, toying with Snape who saw where this was leading and could think of no way out. He couldn't even try to kill the Dark Lord, for the soul fragments in the snake and in Potter would anchor him, keep him alive. He could only wait and watch his own death approach. And still he tried, "My Lord... let me go to the boy..."

"The Elder Wand cannot serve me properly, Severus, because I am not its true master. The Elder Wand belongs to the wizard who killed its last owner. You killed Albus Dumbledore. While you live, Severus, the Elder Wand cannot be truly mine."

"My Lord!"

"It cannot be any other way." The Dark Lord moved the wand and hissed a command, and suddenly the meaning of the snake's bubble, its cage, became horrifyingly clear. It detached itself from its moorings and rolled across the room to encase Snape's head and shoulders. His hands were now helpless to defend himself from the great serpent.

Snape's fingers clawed desperately at the outside of the bubble, powerless to protect his neck, powerless to even touch the snake as Nagini's fangs sunk again and again into his throat. At first he screamed, but then his throat clogged with blood and the scream would not emerge. He fell to the floor, kicking against the boards, against the air, as he fought to break through the bubble.

The Dark Lord's last words to him were a mockery, something that Dumbledore would have said as well - "I regret it."

Through the transparency of the bubble, the still-conscious Snape watched as the Dark Lord moved the wand again and the bubble that supported his head and shoulders vanished. Snape slumped on his side, his hands finally able to reach his throat.

The Dark Lord looked down, and then his footsteps moved away, and the snake went with him, and Snape was left alone. Alone - pressing his hands against the gaping wounds in his neck.

At that moment there was total clarity. Life was neither love nor duty. Life was not friendship or loneliness, pleasure or pain. Life was red, liquid, and sticky, and it leaked through Snape's fingers as he struggled vainly to stem the exodus of life from his body.

But he had to stop it. He had to stay alive. Potter didn't yet know what he had to do when he met Voldemort. Until Potter knew that, the task was not fulfilled, the duty was not done. But life was slipping through his fingers, and with every passing second he became weaker, less able to concentrate, less able to fight for his own survival, less able to stop the outflow of life.

Light was fading, too. Around the edges of vision, darkness thrust its way forward, and Snape strove to stay conscious, to focus on the narrowing window of light - light hemmed now by a growing border of black - because if he gave in to the blackness, he would no longer be able to hold life in his body, and the task would be unfulfilled.

The task. He knew he had something to give, and someone to give it to, but as the red, viscous life leaked through his fingers, he found that words left him, and he could no longer recall what it was he had to give or who the gift was for. Only that he had to stay alive to finish it, and so he clutched his neck and willed life to stay, stay, until he did the thing he was supposed to do.

And then, in the collapsing frame of light, there was a face, and he knew the face, and he knew he had to give the face the thing he held, but he no longer remembered what he held. There were no more words, only images, and he couldn't remember which images he had to give to the face.

There was no other choice. In a life stripped of choices, in the end choice itself was stripped away. In the place of choice there was only need, and he began to claw at the doors that barricaded his mind. Something was in there that he had to give, and if he no longer knew what that was, then he had to give everything. The face drew him up into the light, and he ripped and shredded the locks and the seals because giving was all that was left, and he had to give - a rending every bit as painful as the rending of the fangs that had ripped open his neck.

Nothing was more important. The hands that blocked life from leaving left their struggle, and life poured forth even as the hands gripped fabric and the mouth found words "Take... it... take..." and the gushing forth of his soul, his very being, as fatal as the gushing forth of his blood, drowned the last of the words.

Then she came. He had missed her for so long. "Look... at... me..." he whispered through the blood in his throat. Her eyes smiled down into his, and he knew that he had done what he was supposed to do, that the task was accomplished, the duty fulfilled, and he was forgiven. He gazed into the peace of the well-loved eyes and relaxed, and let go, and let himself sink into the warm, welcoming darkness. And then...

...there was nothing.

\sbreak

McGonagall and Hagrid came for him after it was all over. She removed the barriers Voldemort had replaced around the Shack, and the two of them entered. Entered to clear away the cloying red blood that clotted in his dark hair, to straighten the contorted limbs, and to close the black eyes.

It was McGonagall who conjured the stretcher onto which they lifted his body, thin and scrawny, always off his feed, and small, the smallest ever sorted. And somehow he seemed younger, for he was only thirty-eight, and death had relaxed the tension in his face and let the youth shine through at last.

And McGonagall conjured the sheet, pure and white, that shielded the gaping snake wounds in his throat, and let this last public view be dignified and seemly.

They went through everything he left behind to see if there was a will, but there was nothing, for he was the last of his line, and there was no kin to be notified. His books and his papers went to Hogwarts, and it was fitting.

Thus it was that without warning there appeared at the modest home of Mrs. Hanson in a small mill town in the Pendle region of Lancashire, an aging, dignified witch and a huge shaggy man who might, in another age, have been called a giant. And they told her that Eileen's son was dead, and asked her help in arranging his last journey.

It wasn't a big funeral. Mrs. Hanson was the chief mourner. The lads from the pub were there, as well, to say farewell to Toby's boy, who never could learn how to play darts. The checking girls from the market where he bought the ingredients for beef stroganoff came, and Bill from the village over the hill, the one who'd fallen from the roof twenty years earlier, and now lived to have a wife and two sons.

There were others, too. The boy with the spiky dark hair and glasses, and the odd scar on his face. The little group of teenagers, awkward and shy in their strange clothes. The tiny, wizened dwarf, and the woman with the patched hat and flyaway hair. And, of course, the older woman and the giant who'd brought Russ Snape home.

It wasn't legal exactly, but they buried him in the lee of Pendle hill, there where he'd snagged conies and gathered herbs. There, where the sky stretched free over the moors from horizon to horizon, and at night you could see all the stars.

Because, for time out of mind, there have been witches in Pendle.

\sbreak

Here ends the story.
