% A Difference in the Family: The Snape Chronicles (Rannaro)
% The Third Year

\chapter{Highs and Lows}

\subsection{Sunday, December 23, 1973 (one day before the new moon)}

Severus regretted his decision almost at once. The world of Bellatrix Black and the world of Severus Snape were so far apart that it was hard to believe they even shared a common humanity. The London town house of the Blacks was a wealth of paneled walls, gilt molding, crystal chandeliers, and a marble staircase designed to make Severus feel small and poor in his Hogwarts robes, the only robes he owned.

Mr.~and Mrs.~Black were icily polite, and the house-elves (a pair of them) practically sneered. Bella took Severus to a room in the upper part of the house that he recognized at once as servant's quarters, but he didn't mind. He was far more comfortable there than he would have been in a grander room. He had a bed, a table, a chair, a wardrobe for his things, and his dormer window looked out over west end London. He realized that this was the first view he had of London that didn't include Euston Road.

The next couple of days were not so bad because Bella's parents ate out at the homes of friends, so he and Bella could share a simple supper after lessons. Bella wasn't always around either, but she showed him the library on the first floor and he was quite content to sit there and read, or watch upper class London go by the window.

Two days before Christmas, things changed. The Blacks were giving a dinner party to welcome Bella's sister home from France, and some of their well-to-do acquaintances would be there. Bella was given the task of telling `that little tutor boy' that the gathering was not for people of his `sort,' and that he would have to have supper in his room.

This seemed only fair to Severus, who spent the whole day in his little dormer room while the house-elves made things ready, the sister arrived, the decorations were put up, and the food prepared. Guests would come at seven, and the evening would be a formal one.

Shortly after six, Severus thought that there was a book in the library that he would like to read during his exile. He could use the servants' stairs and come out close by the door. If he was careful, he could get his book and be back in his room before he was seen. It was well before the arrival of the guests, so it shouldn't bother anyone.

His plan working well, he got the book, and then Severus hurried out of the library into the first floor hall where, to his great horror, he very nearly collided with a member of the family. He froze, his heart thumping, then looked up in the gathering silence, his mouth open in shock.

The Snow Queen herself stood before him, regally tall, gowned in iridescent blue and silver, her golden hair woven into a crown with one thick tress falling onto her shoulder. Ice-blue eyes smiled down in a face whose skin was the finest porcelain and whose mouth the delicate petals of a rose. Severus stood, rapt and dumbfounded, for he had never before seen anyone so beautiful.

"Well, hullo there. You must be Bella's friend from Hogwarts. Severus, isn't it?" and her smile was laughter and her voice the singing of birds. "I hope you're enjoying your stay at our home. I'm Narcissa."

It took a moment for Severus to recover and find his voice. "I'm{\el} sorry. I{\el} didn't mean{\el} to{\el}"

"That's all right. There's no damage done. I'm afraid I can't stay and chat right now as they're expecting me in the parlor, but since you're staying for the holidays, I'm sure we'll get to know each other." Then she smiled again and glided past him in a rustle of satin and the faint hint of jasmine perfume.

Severus watched her go, then started for the servant's stairs. By the time he reached the bottom step he was running, taking them two at a time up to the top floor. The book was thrown forgotten on the bed as he rushed to the window. His room faced the front of the house, and he hoped he could watch the guests arrive.

At precisely seven o'clock the chauffeured cars began to disgorge guests. Men in white tie and tails, women in tiaras and evening gowns. It was a fairytale world of color, richness, and beauty, of silk and lace, emeralds and sapphires, top hats and ebony walking sticks. Severus leaned as far out his dormer window as he dared, trying to catch all the details. Families were arriving together, older parents with sons or daughters the age of Narcissa. It looked as if Bella would be the youngest one there.

After the last guest was inside, Severus left the window. He had to see more. He put on his robe over his gown and took the biretta as well. If he were caught, he would at least be in his school uniform, and therefore respectable. Slowly and quietly he crept down the servants' stairs and along the hallway to the railing where he could look down on both the grand foyer that rose three stories to where he was, and on the doors to the dining room at the top of the marble staircase.

When the guests left the parlor to ascend the stairs for dinner, Severus peered through the rails to catch a glimpse of the Snow Queen. She went to dinner on the arm of a slender young man who matched her in height, but whose blond hair was so fair as to be almost white, a young man whom Severus recognized as the seventh year prefect when he himself was only in first year, Lucius Malfoy. They smiled and talked like old friends. The guests entered the dining room, and the doors were closed.

Severus couldn't move from his vantage point. He was certain that if he left for a moment he would miss something. After two hours, the doors opened again and remained open. The long table had vanished and music was playing—the dining room had become a ballroom. Glittering couples whirled past the open doors to the sound of enchanting music. It was a feast for eyes and ears, and Severus fed on it until the guests began to leave at two in the morning. Mrs.~Black stood at the head of the staircase to bid her guests good evening. Narcissa and her partner moved to one side, away from the others, in intimate and mutually pleasant conversation.

The last guest to go was an older man whose bearing and coloring proclaimed him the father of Lucius. The man was talking to Mr.~Black, and the argument had become heated, though Severus could only hear part of it.

"{\el} what your brother would say, Black, to abandon the traditions of your family like this{\el} toadying to an upstart of no background{\el}"

"{\el} has the best interests of the old stock in mind{\el} we have to do something to keep our position{\el} even at Hogwarts less than half are now pure{\el}"

"{\el} bring the product of miscegenation into your own house{\el}"

"{\el} only a tool that the Dark Lord may find useful{\el}"

"Dark Lord! Have you sunk so low? How can you think that I would allow my family to be so polluted{\el}" The man turned toward the younger couple. "Lucius! Attend me at once! We're leaving this place."

The blond young man stepped forward, dismay on his face. He turned to say goodbye to Narcissa, but his father's anger preempted him. "Lucius! At once! We no longer associate with such people." Torn between love and duty, Lucius threw one despairing glance back at Narcissa, then hurried after his father down the staircase and out the door. Narcissa followed him, one hand outstretched as if to seize him and draw him back to her, but she was stopped at the head of the stairs by her mother. The front door slammed. Narcissa hid her face against her mother's shoulder and began to weep.

Severus silently crept back up the stairs to his room. The tragedy of the situation overwhelmed him. She was so beautiful, so noble. She loved him, and he loved her, but the quarrels of their parents had torn them apart. It was heartbreaking. Severus hated both Narcissa's parents and Lucius's father. They had no right to stand in the way of true love! He only wished that there was something he could do to help, for his own young heart was firming in resolve.

If Narcissa Black wanted Lucius Malfoy, then Narcissa was going to have him.

"If we could get him over to Uncle's house to see all their things, it might make him more interested in the Dark Arts. He loves puzzles and mysteries and things like that." Bella was sitting on Narcissa's bed while Narcissa went through her clothes and jewelry deciding what to wear that evening.

"You know Auntie will never allow it. You know what she'll say."

Bella mugged. "Filthy blood traitors bringing a half-breed into my house{\el}" Both sisters laughed.

"Besides," continued Narcissa, "it would hurt him to meet someone like Auntie. He really is rather sweet, and so eager to please."

"Sweet?" Bella almost doubled over with laughter. "The one who dreamed up the bird-dung curse? The kid who had Sirius beating bats out of his hair? You have a twisted sense of `sweet.'"

"Bats! You must be joking!"

So Bella had to tell Narcissa all about the September war between Gryffindor and Slytherin. Then she had to tell about Rabastan and the earthquake. At that point Narcissa became very quiet.

"So the Dark Lord really is interested in him." She seemed suddenly sad.

"Why do you think he's here? You don't think I'd invite someone like him to our house just to be nice. Even if I do need the help with Potions."

"Oh, Bella. You can be so mean sometimes." Narcissa brightened suddenly. "I know what we can do. Let's invite Regulus for Boxing Day. He can bring some things from Uncle's house and we can all have fun just playing with them."

"And what good's that going to do?"

"Well first of all, it could be fun. Then for your scheming, it could help him see that the Dark Arts aren't so bad, nothing to be afraid of."

Bella looked at her older sister with renewed respect. "I think you may have a good idea."

\subsection{Boxing Day, Wednesday, December 26, 1973 \\ (two days after the new moon)}

The Hand of Glory was the hit of the evening. First of all, it was spooky and gruesome. Then they took turns seeing how it gave light to the holder and darkness to the beholders. Then Narcissa thought of the game.

She made everyone study the drawing room for five minutes. Then she took the Hand of Glory, and darkness descended on the others. A minute later it was light again. "All right," Narcissa asked, "what's changed?"

The other three glanced around the room, uncertain what they were looking for. Bella got it first, of course. "The candlesticks were at opposite sides of the mantle. Now they're in the middle." And it was Bella's turn.

Paintings reversed themselves, facing chairs turned their backs, lampshades switched, and the chandelier lost a third of its crystal baubles. The little group dissolved into laughter at every phase of the game, and yet Severus could detect an aura of melancholy that touched Narcissa from time to time, especially when Bella slipped and mentioned Lucius's name. Severus adored Narcissa's courage, the crystal sadness that she covered with consideration for others, the golden sorrow that tinged every action with romance. By the end of the evening he knew that he would lay down his life for her. For the love that she and Lucius shared.

Christmastide dissolved into the New Year, and it was time to return to Hogwarts. Severus carried back with him three defining concepts. First, that the life of the rich, while a source of pleasant fantasy, was as far above his day-to-day existence as the moon above the earth. Second, that the Dark Arts were nothing to fear, but merely an extension of the commonplace, something that he had already been playing with in his hexes and jinxes, and something that could be a source of amusement as well as power. Third, that there was no one in the world as kind, gentle, considerate, or worthy as Narcissa Black.

\subsection{Wednesday, January 9, 1974 (1 day after the full moon)}

Kohoutek was a disaster. The Skylab photos from December were great, but then the comet just seemed to fizzle out. Severus and Lily spent several evenings on the Astronomy Tower without a spectacular sighting in the bunch. Lily was great about it, saying that she had fun just watching the sky, but Severus knew that he'd failed to keep her interest.

Bella, on the other hand, was all attention. Not only was he teaching her potions, he was also fielding answers to other questions. Questions about cursing items and hexing people, and how to jinx the weather. Severus was spending more and more time in the library studying as much as he could about the Dark Arts, and his Defense against the Dark Arts class was quickly becoming his favorite.

More to the point, he was making a little cash. Bella's cousin Regulus started paying him for tutoring in Potions and Dark Arts. It wasn't much, but this time Severus might be able to buy something on the Express back to London. Though frankly he would have preferred muggle money.

Severus was doubly blessed on his fourteenth birthday, for Bella received an owl with a message for him. All it said was, `Best wishes for a Happy Birthday, Narcissa,' but that was all it had to say. Then that evening Lily met him by the lake in the ice and snow with another little cake for two. He thought as they ate it together that he'd never realized before how pretty she was.

"Ya seem to be doing well this term. Taller. Even putting on a little weight. Somewhat's agreeing with ya."

"I'm eating what you told me to. And drinking the milk. And classes are easy." Severus paused for a moment. "Hagrid?"

"Ask away, lad."

"Are girls really different from boys?"

Hagrid's face puckered in fruitless self-restraint, and then he burst into laughter. Severus blushed fiercely as he realized what he'd said. "I don't mean that. I mean{\el}" then he started laughing, too. It was a small, weak laugh, lacking experience and practice, but it was a laugh.

"What did ya mean, lad?"

"I mean do they think differently from boys. Do they like different things and look at the world differently?"

"The man that could answer that question would make hisself a fortune. 'T is my opinion they're a whole different breed. Ya got a girl you're interested in?"

"Don't know yet. Maybe."

Not everything was pleasant in Severus's garden, though. It manifested itself in the fountain courtyard.

"Hey, you! Snivellus! Turn around when you're spoken to, Snake!"

Severus turned, taking a couple of steps to his left as he did so to put a wall at his back. Sirius Black approached him in a tightly controlled rage, Potter and Pettigrew behind him.

"You're going to stay away from my brother, Snivellus. You start poisoning his mind and I'll crack your skull open."

"Brother? I didn't know Dr.~Frankenstein was still in business." \emph{Wasted effort. He hasn't got a clue.}

"I'll doctor you right into a hospital bed. You stay away from Regulus."

"Regulus is your brother? Mendel was right. Niceness is recessive."

Sirius advanced, and Severus pointed the wand that he still carried in his sleeve. \emph{"Toichos,"} he said calmly, and Sirius was blocked by an invisible wall that surrounded the spell caster. Severus backed away from the trio, as they pressed forward just beyond the limit of his wall.

"You okay, Snape?" Rabastan, Rodolphus behind, was standing in the cloistered walk that surrounded the garden.

"Fine, thanks. These gentlemen were just going."

Both sides backed away from the field, leaving the battle a draw.

"I'm warning you," was Sirius's parting shot.

\subsection{Friday, June 28 to Saturday, June 29, 1974 \\ (three days past the first quarter moon)}

Spring progressed with little change, and summer began to bloom around Hogwarts. Soon it was exams time again. Again Dumbledore called Severus to his office and gave him an envelope with a train ticket. Again students packed their belongings and said goodbye for the summer.

This time the train ride into King's Cross was much more enjoyable for Severus. He stayed with the other Slytherin students and bought some of the refreshments with his hard-earned coin. It was something of a farewell party for Rabastan, who'd finished his seventh year, sat for his NEWTs, and was now free of Hogwarts for good. Rodolphus was passing around a jug that Severus sniffed at and passed on, but by the time they got into King's Cross it was clear that some of the younger students were tipsy. In general, Slytherin house had a great time.

Exiting from King's Cross, Severus was aware of a change in London. It was hard to put a name to the feeling, but the area was different. There were a lot of bicycles in the traffic. Somewhat fewer cars, and a lot more bicycles. He crossed Euston Road to St.~Pancras for the night, wandered Euston Station the next morning, and boarded the train for Colne without problem. The trip to Lancashire was uneventful, and he arrived in Colne in the early evening.

Severus's parents were not there to meet him.

Severus sat on a bench in front of the train station for nearly two hours before he finally admitted to himself that his mum and dad were not coming. Four times the station master offered to phone his home, but they didn't have a telephone so Severus thanked him politely, but declined.

Finally he made up his mind that he'd have to walk. It was nearly ten miles to the village where he lived. The long northern twilight would make most of the trek bearable, and the waxing moon would give some light after the sun was gone. Still, it was more than a three-hour walk under the best of conditions.

At first Severus considered cutting across the moors, but quickly abandoned the idea. The gathering dusk wasn't the best time to be going over uneven land; he would probably make better time on the road. And if his parents were coming, he would have to be on the road to meet them. He hefted his Gladstone bag. Luckily it wasn't heavy.

The sun set, and the moon was near setting, too, before he reached his own town, tired, cold, and hungry. It was past `last call' at the boozers, and probably close to closing time. In all the hours he'd trudged along the road, though, he'd not seen a single car. It was as if all of eastern Lancashire was deserted, and he was getting nervous.

The sound of his shoes on the cobbles brought Eileen to the door well before Severus reached their gate. Her frightened expression turned to one of relief. "Russ! Thank God you're alright. I was that worried," but she wouldn't let him into the house. "You go over to Mrs.~Hanson's in Mule Lane. She's expecting you. Don't come back here 'til tomorrow morning."

"But Mum," Severus began, and Eileen turned on him in fury.

"You get to Mrs.~Hanson's and you get now! You're not spending the night in this house. I don't have time to argue with you. You obey! Now get!"

And Severus got. Mrs.~Hanson was a plump widow whose husband had worked in the mill. She was still up in her sitting room with the light on, waiting for him. She had a cold supper and a bed made up in the spare room, and she clucked over him as he ate, warming himself by her grate.

"It's those Arabs," she explained. "There was a war in the east and those Jews won. So those Arabs cut off our petrol. Isn't nobody can drive a car now, and the factories have it hard paying the extra for the power to keep them running. Prices are up everywhere. It's got near impossible to make ends meet. Your dad was on strike in February. They won, the miners, but everyone else is worse off, and your father's been drinking worse than ever. Your mum says he was getting to work late most every day. The mine says your dad's redundant, and he got laid off two days ago. Been drunk ever since. You go home tonight, boy, and he's like to kill you."

Severus lay awake all that night in the once familiar bed in the once familiar house, wondering what was happening at his own home. Laid off. No money. Like when he was nine. He didn't have to imagine what his dad would be like. He knew. And he was scared.

The sun was well risen the next morning before Mrs.~Hanson would let Severus leave her house. She fed him, too, not knowing what the boy might find at home. "Now you remember," she said as he walked to the gate, "you have any trouble over there, you just come here `til it cools off."

Severus's own house at the end of the street was quiet. The whole street was quiet, and Severus noticed that two more houses had boarded-up windows. As she had the night before, Eileen heard his footsteps before he reached the house and came out to meet him. She had a cut over the left cheekbone, and a bruise had formed around it.

"Shhh," she hissed, "he's asleep. Do you need breakfast?"

"Mrs.~Hanson gave me some. Supper, too."

"Good. Now, first things first. Wand."

"But Mum, I may need it. You never know what{\el}"

"Exactly. You'll go for it. You listen, Russ, and you listen good. Nothing—nothing—is going to keep you from going back to Hogwarts in September. Give me the wand."

Reluctantly he pulled the wand from his sleeve and handed it to her. Only then did she let him enter her house. Together they went back into the kitchen. Toby was snoring upstairs. Eileen opened the door into the area and picked up a glass jar full of a reddish-brown liquid, then took two cups from the cupboard.

"What's that?"

"Tea. Brewed it in the sun. It's lukewarm, and there's no milk or sugar, but at least we still have some tea. Enjoy it while it lasts."

"But what about{\el}" Severus glanced at the stove.

"Gas costs money. I have a job for you. Now drink your tea."

Dressed in his oldest, shabbiest clothes and carrying a large bag, Severus made his way to the local coal yard. It was Sunday, and the yard was shut down and quiet. He nimbly scaled the wall and began looking around for lumps of coal. Eileen's orders were clear. He was not to go into any trucks or open any bins. He could only pick up what had fallen loose and stray around the yard. That turned out to be quite a lot, and after a couple of hours he'd filled his bag. If they were careful, it would last a long time, for Eileen only intended to use the coal for cooking on the grate, a few lumps at a time.

Severus deposited his bag in the area yard and checked with his mother to find that Toby was still asleep. He then set out for the open moors, occasionally stooping to pick up a rock of exactly the right size and shape. He found a little outcropping and sat waiting, for patience was now his most important quality. After twenty minutes he saw a tentative movement of gray in the scrub. Easing himself up into position, he paused, then fired one of his rocks straight and true at the rabbit. He didn't move to collect the animal until he'd managed to kill another. A brace of rabbits would make a fine supper.

The kitchen was empty when Severus got home, but he could hear that his dad was being sick. He kicked off his muddy shoes in the area yard and went upstairs. Toby was in bed with a massive hangover, while Eileen held a bucket for him. The stairs squeaked, and both looked over at Severus.

"You!" Toby roared. "Where've you been? Come home from that fancy school to steal a man's food off his table, and not even here to help when he wakes up! Skulking around! Get over here! I'm going to beat the skin{\el}" He turned suddenly and vomited into the bucket again.

Severus waited quietly. When the spasms passed, and Toby was able to talk again, Severus moved his hand from behind his back and held the rabbits in front of him.

"I'll give you what for, skulking around like{\el}" Then Toby saw the rabbits. "How'd you get them?"

"Accident. They got in the way where I was pitching stones."

Toby grinned. "That's my boy. Ain't every boy can bring down a coney with a rock, is it Leen? Maybe you ain't more trouble 'n you're worth." Then he was sick into the bucket again.

Over her husband's bent head, Eileen and her son's eyes met. She smiled a tight, closed smile and nodded. He winked and went downstairs to leave the rabbits on the kitchen table.

A new routine settled into the Snape family.

Severus was now the primary food provider. On most days he managed to get a rabbit, or at least a couple of birds. It was closed season on moor hens, but pigeons were like rabbits, always fair game. Then, a few miles from home, he discovered a new source of food.

It was a small farm cottage with an extensive kitchen garden, and the woman was trying to repair a hinge on her gate. She was an older woman, in her sixties, and seemed to live alone. The garden was beginning to get overgrown with weeds.

"Could you use some help, ma'am," called Severus, standing in the road watching. "I could use the work."

"I've got the work, and I could use the help, but I can't pay you, so you'd be wasting your time." The woman looked tired and more than a little frustrated.

"I'd be willing to work for some potatoes, and maybe one of the new cabbages."

"Done," she said.

The first thing he did was hold the gate so she could finish the hinge, then she set him to picking things that were ripe and needed canning, while she stewed vegetables in the kitchen and sterilized jars. Severus had no trouble knowing what to do, reckoning that finally all that Herbology he'd studied was proving useful. Then, in the afternoon after a bite to eat, she had him start on the hoeing and weeding. There was more than enough work for the day, so he promised to return on the morrow. The woman sent him home with potatoes, carrots, onions, and a cabbage.

Severus spent a lot of that summer tramping around the district looking for work he could do in exchange for food.

Eileen was traveling farther to find jobs to do as well. Many of her old employers were also short of money, and she couldn't find the work near home that she used to do. She frequently brought tasks home with her to work on as long as she had any light. Most of her money went for things like bread that she couldn't make at home, or for petrol for the car. In addition, she always managed to put a few coins into a jar for the money to buy Severus's train ticket to London for the start of the next semester.

Toby was usually up before dawn, driving to nearby towns looking for day labor. If all went well, he would be home in the evening, ready to go to bed so he could get up and look for work the next day. If all didn't go well, he would come home late, drunk and frequently violent. Severus was helping his mother get his father to bed now, and was getting his own set of bruises as well.

One night at the end of July, Eileen wasn't there when Toby came home roaring drunk. Severus heard the unsteady steps on the walk and froze in the kitchen, listening. The door banged open, and his father yelled, "Eileen! Eileen! Get out here an' get me t' bed." Not knowing what else to do, Severus went into the hall to assist Toby.

"What're you doin' here? Where's your mum?" Toby muttered. "She oughta be here to tend me when I come home. Where's she got off to?"

"She's got a job. She'll be back soon. Just get up to bed, Dad{\el}" Severus tried to support his father to the stairs, but Toby had focused on one word.

"Job? She's not s'posed t' have a job. She's s'posed t' be here. Her place is here!"

"Come on, Dad, just get up the stairs."

"Where's your mother!" Toby rounded on his son with a fist to the jaw that sent Severus sprawling into the wall to then drop dazed to the floor. Staring madly around the room, Toby spied the umbrella stand with its one brolly. Seizing the heavy umbrella, he swung it like a club, the curved handle smashing into Severus's side as the boy tried vainly to ward off the blow with his hands. "I'm th' breadwinner in this house! I'm th' man in this house! No witch's brat's gonna make a fool of me!"

Another blow struck Severus in the leg, then he threw his arms around his head as the umbrella came down on his skull and everything became blurred. Suddenly Eileen was in the room screaming, "Toby! Stop, Toby! You'll kill him!" She flung her arms around the enraged man, but he pushed her back onto the stairs and advanced again on the boy whose presence in his house shamed him so.

Eileen flew up the stairs into the store room and from the upper landing aimed her wand at Toby, screeching \emph{"Stupefy!"} with all her strength. Toby buckled and fell to the floor, the umbrella clattering beside him, and lay still.

Without a glance at her husband, Eileen rushed to Severus. He was unconscious, and the hair on the crown of his head was sticky with blood. Cradling her son in her arms and crying uncontrollably, Eileen apparated.

Severus woke up at Nana's house. His grandmother was sitting in a wing-backed chair on the other side of the room. When he tried to move, he realized he had a splitting headache and that every bone in his body seemed to be protesting. "What happened?" he asked.

"You had a concussion. You've been lying unconscious in my guest bedroom for six hours, and I've had to sit here watching you to make sure you didn't die on us."

"I mean{\el}" Severus felt the bandages around his head, then realized others wrapped his chest and his left leg. "I mean what happened?"

"Oh, that. Your lout of a father came home drunk and nearly beat you to death. Your mother, finally using the common sense I've always hoped she was born with, hit him with a stupefying spell and brought you here to me. I've bandaged you and medicined you, and here you are. Awake and asking questions."

"Where's Mum?"

"The idiot girl has gone back to what she is content to call her `husband.' I offered to dispose of him, but she flew into one of her tempers and left in a huff. I assume you don't intend to do the same."

"But he could{\el}"

"Not if she stays at arm's distance. Which is what you should've done. Actually getting close enough so he could hit you. You ought to be ashamed of yourself."

Severus spent two weeks with his grandmother Prince. Then they shuffled the deck and he spent two weeks with his grandmother Snape. He got an owl from his mother almost every day telling him she was all right and asking about his health. He got nothing from his father.

Eileen came to visit him at grandmother Snape's about a week before the end of August. She brought with her the old robes that she had worn during her time at Hogwarts. "You're as tall as me now," she explained. "I can't buy you new robes, but maybe I can rework my old ones." She undid all the seams and reversed the fabric so that the faded side was now in, and the unfaded side out. She had to make some adjustments for the style changes since the beginning of the '50s, but it was minor, wizarding robes not have altered as much as muggle styles.

Severus returned to spend one last night with his parents before the trip back to London. His father was sober as a judge. There was a new reticence about Toby, who hardly dared look his son in the face. The awkwardness finally dissolved with the appearance of the cribbage board, and Severus won all three games. Severus was pretty sure that his father had miscounted his hands, but it was Toby's way of trying to make up.

The next morning they drove to Colne. There Severus bid his mum and dad goodbye and boarded the train for London. All went according to plan—Euston Station, St.~Pancras Church, King's Cross. At eleven o'clock on the morning of Sunday, September 1, 1974, the Hogwarts Express carried him back to school, lit as the day closed by a moon at the peak of its fullness.

Severus never saw his parents again.


