% A Difference in the Family: The Snape Chronicles (Rannaro)
% The Fourth Year

\chapter{Growing Pains}

\subsection{Thursday, January 9, 1975 (one day before the new moon)}

On his fifteenth birthday, Severus received the worst possible present . He woke up with a slight sense of pressure and pain at the right corner of his mouth. He touched it, and there was a bump there. A glance in the mirror confirmed it. He had a pimple.

"Lestrange knows a spell to clear that up," said Wilkes. He'd begun having similar problems around Halloween.

"I need to think about that. Maybe I don't want to get rid of it."

"Maybe you did it on purpose. Maybe you just fancy Wilhelmina," said Mulciber, coming up from behind them to check out the image of Severus's pimple in the mirror. "I heard she has a thing about pimples."

Wilkes laughed. "Maybe she just has good taste. Come on, Snape, go see Lestrange."

"I'm serious. I may keep it."

"You want something like that on your face? You're weird."

It wasn't just the pimple. Severus had noticed that his hair was oilier, and it was getting harder to keep clean. He still wouldn't join the other boys in the communal lavatories, but he was now reaching a point of major decision. Should he do anything to improve his appearance, or should he just let the changes happen?

Severus was aware that he would never be good-looking. He had his mother's thin face, pale skin, and stringy hair. He was clearly now developing his father's hooked nose and bony chin. His sharp black eyes were small and close together, and his teeth were crooked. In the black Hogwarts gown and robe he was a spectral study in light and dark. In the moonlight he could pass for a vampire. Severus rather liked that thought. He found vampires fascinating.

\emph{Why do the others care about their appearance, anyway? Isn't it girls? Aren't they all just interested in getting girls to notice them?} But Severus carried a demon inside him, and there was no point in wasting time caring about something you couldn't have. He would keep the pimple, and the oily hair. He would waste neither time nor energy on his outward self. Only the inner world, the mind, was important. That was where he would invest his energy.

Lily couldn't make it to the lake that evening, but she left him a note wishing him a happy birthday. Severus went by himself to skip stones and sit on Lily's rock for a while. He was still working on his Sectumsempra spell, and spent nearly an hour and a half trying to refine the slashing effect. It was supposed to be like a surgeon's scalpel, not a butcher knife.

By this time Severus was casting the spell non-verbally. He'd decided that he couldn't risk anyone overhearing the words, especially with something as dangerous as his new cutting spell. In the hands of the wrong person, it could kill with a terrifying ease.

He was working on another non-verbal spell, too, but one that could only work non-verbally. After a long period of reflection, Severus had worked out the basics of a self-protective spell to use if he were ever ambushed again. It was a spell to lift his attacker off the floor and hold him suspended upside down. He reasoned that the shock of suddenly being head down would make anyone let go of him and give him a chance to escape. The spell particularly had to be non-verbal in case he found himself again with a hand clamped over his mouth. The next step was working out the words.

No breeze stirred the crystal air of that dark winter night. Severus was utterly alone on the icy verge of the lake when he heard a faint{\el} sound. He glanced around, saw nothing, and became more nervous. There was something there, in the trees, he was sure.

Slowly, carefully, Severus began to inch his way toward the hill and the castle. As he shifted his position, he saw the eyes. Green eyes in the woods. Wand at the ready, he continued to back away. The eyes followed him until he reached the bottom of the hill, then they were gone. Severus hurried to the castle, breathing hard, for what he'd seen in the starlight frightened him, its unknown quality most of all.

The four students in the shelter of the trees were equally startled. "Who was that?" muttered Sirius listening to the muffled sound of retreating steps in the snow.

James lit his tiny green Lumos spell again and looked at the map the boys had been working on. The name `Severus Snape' was moving up the hill towards the castle. "I wonder what he was doing out here all alone in the dark?"

Sessions with Hagrid were back to normal.

"Yer weight's up. That's good. Didn't like seeing ya so skinny. Did ya want t' do anything 'bout that acne? No? Suit yourself. Mind, though. Y're getting t' be of an age where ya got t' take better care of yerself. I know ya don't want nobody seeing yer back, but ya got to find a better way t' wash up."

"I'm perfectly fine the way I am."

"Ah, but ya ain't fine for the people around ya. Face facts, lad. Teenage boys smell. Ya don't want t' make it worse 'n it has t' be." Hagrid got a sudden sly look around the eyes. "I mean, ya don't want t' be attracting more attention than what ya deserve."

"You think so?"

"I do so."

Severus thought about this while Hagrid went through the familiar checklist of his inspection. "And if I needed someplace different to wash up, where would I go?"

"Well, I got a pretty big washtub here. Ya could pop in from time t' time. Ya don't got t' be no prima donna, but a wee bit of a cleanup from time t' time 'll keep ya in the background, if ya get my meaning."

Severus got his meaning.

Lily brought news clippings from home. "They've actually been working on this for a couple of years.! I mean, who knew? The Russians and the Americans planning a joint program? Astronauts and cosmonauts together? The future of the space program is just getting bigger and bigger. You're sure to get into space!"

The Apollo-Soyuz launch wasn't scheduled until July, but Severus and Lily were studying the configuration of the docking capsules in February.

There were even a couple of sessions with Dumbledore.

"Now, I want you to think about your parents' deaths. I know it is hard. Please try not to close anything down. Good, but that is very graphic."

"I saw the blood. What do you want?"

"You saw the blood, but you did not see her fall. What you are showing me is your own reconstruction. Reconstructions are dangerous because they never represent the truth, only a personal interpretation."

"I thought legilimency saw the truth."

"It sees what you think the truth is. If you think that someone is a murderer, then the legilimens sees the murder. If you think the accused has been `framed', then the legilimens sees the `frame up'. You control what the legilimens sees."

"Then I can lie."

"No. The legilimens sees the truth. Your truth. It is just that sometimes you can chose which part of the truth you wish the legilimens to see. It lies in the selection of memories, not the falsification of them."

"So what was he doing there? Pitch black night. Cold to freeze your{\el} rear end off. And he's completely silent. Did you hear him? Did you?"

Sirius had to admit that he hadn't, as did Peter and Remus., "What if he's doing non-verbal spells," Remus suggested.

"Hello. Earth to Remus. He's fourth year, just like us. They won't us teach non-verbal until sixth year."

"Right. Like that ever stopped you. The man who's trying to become an animagus. Do they teach that at Hogwarts?"

"You think he's inventing non-verbal spells?"

"I'd stake my life on it."

"Then I think we're at war again."

The new war began in the stage of intelligence gathering and spying. For a few weeks, almost everywhere Severus went one of the four Gryffindors was nearby. The least obtrusive was Peter Pettigrew, and so he generally followed Severus into the library where Severus was spending more and more time studying every book that had a reference to the Dark Arts. Peter noted down for the record the titles of everything Severus read, and soon became curious about them himself. After a while he spent his time watching Severus by reading many of the same books.

Sirius took most of the outside watch, but was soon frustrated, for Severus had an uncanny ability to lose the person tailing him. If it weren't for his knowledge that no one could apparate inside Hogwarts, Sirius would have suspected Severus of doing just that.

"Maybe you're following him too closely," James said. "You're letting him see you're there."

"If I don't follow him close I'll lose him. Besides, I want him to know I'm there. I want him to worry."

"You have the subtlety of a bull elephant. What're we going to learn if he knows we're there? We're not just after him, remember. We're trying to stop them from recruiting any more."

"I'm after Bella's puppy dog. Regulus told me he was getting friendly with the Malfoys last Christmas."

"Regulus is delusional. The Malfoys get chummy with a half-blood upstart? Never."

Remus lounged against the pillows on his bed in the dormitory. "Would it interest you to know that he's tutoring half of Slytherin house?"

"Really?"

"Potions and Charms. Seems everyone's gotten real interested in their exams."

James thought for a minute. "Sirius, you take over the inside watch. I'm going to see if I can follow him outside."

Avery accosted Severus in the common room. "I need to get this work done tonight."

"You should have planned ahead. I'm busy tonight."

"I'm paying you to do this. You work for me. I need it tonight."

Severus's eyebrows shot up in mock surprise. "I work for you? For what you pay, I'm making a charity donation. You may not have noticed, but you're at the bottom of my `to do' list."

"You think you're so smart, but you're not so smart."

"I know. I have the 50p a pound brains and you have the 100 pound per ounce brains. That's why I'm tutoring you and not the other way around."

"So you're saying I have more expensive brains?"

"Of course. Supply and demand. Do you know how many purebloods you have to kill to get an ounce of brains?"

This was not the most diplomatic thing to say in the middle of the Slytherin common room, so it was a good thing that Severus had somewhere else to be that evening.

Severus was meeting Lily that evening because he was tutoring her, too. The difference was that he was teaching her his own spells. The first was the Muffliato spell that he'd made for Narcissa and Lucius. If they could use that in classes, they could talk without being overheard. It would be best if she knew how to cast the spell non-verbally, but that was harder to teach.

As he left the castle after supper, Severus kept a watch to the rear. For the last few weeks he'd been followed from the moment he went down the steps at the castle entrance. In response he'd devised a mental fog spell that cut off pursuit, but he preferred to use it only when necessary, not wanting to confuse the innocent by accident. Today it seemed that no one was behind him.

On the first floor, near the history classroom, James Potter was watching from one of the narrow windows. From the direction that Severus was going, James suspected he was going to the lake again. And right now, just before supper, was a time when he would be less likely to be disturbed. James left his vantage point and headed downstairs and out the entrance, then made his way stealthily toward the lake shore.

What James found there was the last thing he expected. Severus was with a girl. A girl whose robes were embroidered in Gryffindor red and gold. She was sitting on a rock, and Severus was on the grass at her feet. Severus stood and pointed at a dead branch nearby. Slowly it rose from the ground, though Severus had said nothing. James crept closer.

Then the girl stood, and James recognized her instantly. She was a fourth year, like him, and muggle-born. Her name was Lily Evans. She gazed fixedly at the branch, but nothing happened. Now snippets of conversation reached James.

"You have to focus the non-verbal part of your brain."

"I don't know where the non-verbal part of my brain is."

"I don't know where yours is either, but mine seems to be on the right side just above my ear."

"You're joking! Nobody can feel the part of their brain they're thinking with."

"I swear, it's over here on the right. Just focus on the branch, okay?"

James crept away again, not wanting to risk being seen.

The four friends met in the Great Hall and took seats separated from the rest of their house, shooing away anyone who tried to join them.

"He's meeting the Evans girl. He's teaching her dark magic."

Remus interrupted. "That's impossible. Lily's not interested in dark magic. She's one of the nicest people in our year."

"And you would know that because{\el} ?" James was beginning to feel that there were too many revelations for one evening.

"We talk. We've been talking since last year. She knows I have a `problem,' and she wants to help."

Sirius sneered. "Does she know what the problem is?"

"No. But it wouldn't matter. She's just nice. She likes to help people."

"If she likes both Moony and the Cursemaster, maybe she really is into the Dark Arts." Sirius seemed to think the whole situation amusing.

"Oh, shut up," replied James. "She probably doesn't know what she's getting into, how dangerous it could be. I should talk to her. Remus, could you get the two of us together for a private chat?"

"Of course I know you. Everyone knows you. You're a Quidditch chaser."

James preened a little, but got down to business quickly. "We need to talk to you about the company you keep. " Then he explained how he knew about her and Severus.

"You've been spying on me?"

"No. Not on you. I was spying on him."

"So that makes you what? A better kind of spy?"

"Look, I'm sorry about the spying, But there's this whole group in Slytherin that's into the Dark Arts, and their families are associated with this dark wizard who's been recruiting followers for the last four years. Your `friend' is one of the leaders of this group. He's dangerous."

"Severus? Dangerous? Now you're not even a good spy. And if you think you're going to dictate to me who my friends are, you{\el} better think again. And you!" She wheeled on Remus. "I'm ashamed of you!"

"You know," said James menacingly, "this means we're going to have to watch you, too."

"Well maybe I'm just going to have to study this dark magic to get rid of you."

"Well maybe you are."

The war entered its sniping phase.

Leaving `History of Magic' class, Severus was hit with a fur-growing spell that duplicated the coloration of a tortoiseshell cat. The worst part about it was that it itched, and took Miss Pomfrey two and a half hours to remove. Severus in turn placed a jinx on a third floor mirror where James liked to check the precisely tousled condition of his hair. Waiting to be sure he hit the right target, Severus then sealed the hex, leaving James with hideously crossed eyes.

A Rictusempra in Herbology sent Severus reeling backwards into a freshly transplanted stand of carnivorous plants which nibbled at his ears, nose, and fingers while he rolled on the floor giggling uncontrollably, and Wilkes and Rosier frantically helped Professor Mullein pry the fly-traps off him. Severus's retaliatory Arpague spell caused Sirius's hand to spasm at the very moment he was helping adjust Ariadne Musgrave's cloak, causing him to grab her in a way that led to a slapped face and the end of their budding relationship.

James and Sirius's next jinx backfired when Severus saw them coming and sidestepped the curse, which continued down the hall and struck the innocent Bertram Aubrey, inflating his head to twice normal size, for which both spell casters got detention. Severus decided not to respond to that one, except for the comment, "I thought you didn't use dark magic," as they were led past him to their punishment.

Things were quiet for a few days, but only because James and Sirius were trying to perfect their use of a babbling curse. This one was cast as Severus entered his Astronomy class, causing him to spew out the name of every constellation, star cluster, red giant, nebula, galaxy, and white dwarf on their charts, all 365,729 of them, until an exasperated Professor Sinistra hustled him out of the room and down into Slughorn's first year Potions class with the icy remark, "This, I think, is yours."

Stern times require stern measures. After letting things cool down for two days, Severus hit James and Sirius with matching Eros spells, carefully calibrated to go through a romantic phase, a courtship phase, a jealous phase, and a tender phase before reaching the full-blown love spell. Interestingly enough, it took twelve hours for any of their friends to notice a difference in their behavior, by which time the spells had become nearly impossible to remove.

Lily never told Severus that James had threatened her. Instead, she reacted by seeking out his company even more. They went for walks around the lake, and picnicked on weekends, and reminisced about muggle life. Severus finally confided to Lily the truth about his parents, and she in turn talked about her insecurity at Hogwarts, being muggle born. And they prepared for the Apollo-Soyuz launch.

They wouldn't be able to watch together on the day of the launch because it was scheduled for July, but they promised each other to keep separate vigils. Meanwhile they memorized every facet of the mission and even began learning a little Russian in honor of the historic cooperation. When they met they wished each other `Dobree dyen' and called each other `moy droog'. They said `spasibo' instead of `thank you'. Severus found out that in Russian his name looked like CEBEPYC, and he began writing that in his notebook.

It pleased both of them that none of the other students knew what was happening in the outside world, for it tinged their muggle heritage with romance and gave them a secret no one else could share.

And then it was final exams and the end of the term. Severus wondered if Dumbledore would call him to his office to give him a ticket, but he wasn't sure where any train ticket could take him. His whole summer was an unknown quantity. Then he got Dumbledore's summons and learned that he would have to leave almost everything at Hogwarts until he returned in September. Nana was apparating directly into Hogsmeade for him, but she wouldn't be able to carry much luggage out. Severus packed all his belongings in boxes for Slughorn to store over the summer.

The last test, the last packing, the last goodbye, and on Friday, June 27, 1975, Severus walked down the hill from the castle carrying his Gladstone bag. Nana was waiting for him, and they apparated together back to Lancashire.

It was a summer of real potions. As long as Severus was going to be living at Nana's expense for all of July, she was going to get work out of him. It started in the garden with foxglove, monkshood, and belladonna, comfrey, feverfew, and betony, and the symbiosis of bird, bee, and worm.

"You've left that too long, Russ. It should've been gathered last night."

"I'm hopeless at this. Why are living things so difficult to work with?"

"A talent for potions doesn't always go with a talent for herbs. A great potions master needs a great herbologist."

Potions. That was another matter. That was where Severus earned his keep. Infusions and decoctions, poultices, syrups, and lozenges, Nana's supply of medicines was kept stocked all during the summer. It was needed, too, for people in the surrounding villages seemed to be sick constantly. Some of them paid in kind, but others had coin, and for the first time Severus began to save a little of his own money.

\subsection{Tuesday, July 15, 1975 (the first quarter moon)}

Nana and Severus were in the garden the morning that Apollo-Soyuz was scheduled to go. The Russian rocket was set to launch twenty minutes after noon. Severus was trying to hurry with his work among the herbs so that he would be free to join Lily (in spirit at least) at the promised time. Suddenly his and Nana's heads swung to the sound of a car screeching to a halt by her gate. A women sprang from the passenger seat.

"Mrs.~Prince! Mrs.~Prince! My Bill! He's had a fall. You've got to come{\el}"

"Russ! The bag by the door! Run!"

Severus ran for the house to get the emergency bag that Nana kept filled with medicines by the front door while Nana hurried down the garden to the waiting car. Severus joined them and the car sped away. Severus closed his eyes. He hadn't been in a car since two summers before, and all he could think of was his father driving into that ditch{\el}

They reached the house in less than ten minutes. A little group of neighbors was gathered around the fallen Bill, who from the look of things had been repairing shingles on the roof. He lay now on his left side, his body at a strange angle. Someone had thrown a blanket over him. The people all moved respectfully aside at Nana's approach.

"Have you moved him at all?"

"Don't dare, ma'am. Looks like his back's messed up. We move him, who knows what we'll do."

"Probably for the best." Nana eased herself down next to Bill and felt the clamminess of his skin and the weakness of the pulse in throat and wrist. Her expression became grave. "He may be bleeding inside. Bleeding badly. He's dying. I don't have medicines for this." The woman choked on a sob, and Nana turned to speak to her. Behind her, holding the emergency bag, stood Severus. "Russ. Come over here. Now."

Severus knelt beside Nana. She spoke quickly and softly. "You have the gift of reading. Eileen told me. Read him. Find where the bleeding is."

"I don't{\el} I can't{\el}"

"Don't tell me you can't when a life is at stake. You try."

Severus looked into Bill's face; he was sixteen, maybe seventeen years old. \emph{Eye contact. I need eye contact.} Carefully Severus lifted Bill's eyelids so he could stare into the blank blue eyes. Nothing. A swirling fog. The rapid beat of heart and shallow breath. Then{\el} Severus doubled up in pain. Nana gripped his shoulders as he clutched the upper left side of his abdomen. "Here. It's here."

"Ruptured spleen. Get him away." The men pulled Severus back as Nana drew out her wand and took Bill's hand. She began a low, ancient spell like a chant, like a song, and the air around her grew chill. Time receded while Nana crooned to the injury, her body gently rocking back and forth. Then it was over. She beckoned to Severus again.

"Check his head for injuries, and find if there's a place in his back where the nerves are damaged." Again Severus looked into the blue eyes, and again Nana rocked and sang until finally she was able to tell the men to carry Bill into the house. He was breathing easily and color had returned to his skin.

Nana was too exhausted to stand. One of the men lifted her and carried her into the sitting room where they laid her on the sofa and brought her tea and biscuits. No one spoke of payment, knowing that for months to come Nana's wood would be chopped, her garden hoed, her screens patched, and that she wouldn't want for eggs or bread.

"How could you do that?" Severus asked after they got back home. "We aren't supposed to do magic in front of muggles."

"Muggles? What an ugly word. They're people. And for time out of mind there have been witches here in Pendle. What are we supposed to do? Just disappear because some newfangled Ministry decides to write a law?"

"Nana, will you teach me to be a healer, too?"

\subsection{Monday, July 21, 1975 (the full moon)}

Less than a week later, Severus finally got up the courage to visit his home. Nana packed up a lunch for him, as he'd be gone all day, and he set off across the moor country. He wasn't interested in having anyone see him, so he walked around the town to the side where the house was. More of the windows in the street were boarded up as neighbors left looking for work in larger towns. The coal mine in the neighboring town appeared to still be operating.

The yard was overgrown with weeds. Severus stood outside the house for a quarter of an hour before steeling himself to go inside. There everything was as it had been left, a cup whose tea evaporated long ago still on the kitchen table, the bed upstairs unmade, the stain at the foot of the staircase{\el}

Severus began to straighten up, suddenly wanting it to look as if his mother were still keeping house. He washed dishes, dusted, swept the floor, made the bed{\el} then shut himself into the back storeroom to go through boxes of things that he might need for Hogwarts. One small box contained photographs of his parents' wedding. He closed it immediately and shoved it into a corner. Another held baby clothes and toys he vaguely remembered from his childhood, and he stared at the ceiling for a while until he was certain he wasn't going to cry.

Then, under the suitcases and the boxes of chipped dishes and worn linens, he found the books. Six boxes of books. At the top of one box was a seaman's navigation manual, more than a hundred years old. Severus dragged all six boxes downstairs into the sitting room and unloaded them onto the sofa and chairs.

One group of them were school books bearing the names Tobias Snape, Edward Snape, and Leonora Smith. Books to teach arithmetic, English history, reading, penmanship, and French. It occurred to Severus that Leonora must be Gra, but he never knew she spoke or understood any French.

His mother's old schoolbooks were here, too, and he carefully separated them from the others, for he would need them at Hogwarts.

Another group were the professional books of a nineteenth century seaman, and Severus was particularly fascinated by the communication handbooks: the colored flags, semaphores, and Morse code.

One box contained just magazines, primarily a complete set of the Strand from 1890 to 1893. \emph{Why keep these?} Then he flipped through them and saw the Sherlock Holmes stories. One of Gra's parents had held onto an old friend.

Agatha Christie was a favorite, too, and Daphne du Maurier, and a host of lesser-known writers of the thirties and forties. Probably all Gra's.

The last box was different. The books inside had been carefully wrapped first in linen and then in oilcloth. The oilcloth was old, cracked, and very brittle. Severus unwrapped only two of the books. They were eighteenth century grimoires, the first on astrological correspondences, and the second on talismans. He wrapped them back in their linen and oilcloth and carried that box back upstairs, burying it under suitcases and old bedding. Dumbledore's spell should keep the house safe, but it was still not a good idea to leave things lying around.

Severus repacked the rest of the books, but left them downstairs in the boxes. He had an idea that he should bring in bookcases so that the books could be seen and read instead of hidden away. It was something to consider for the future. Taking with him those books he knew he would need for fifth year, Severus locked the house up and set off back to Nana's.

Halfway there, the irony of it hit him. During that whole last year when money got tight and his father was laid off, the solution had been in the storeroom all along. Those books would have fetched a great deal of money. Even the Strand magazines were probably worth something. His father had been sitting on a pile of cash, and had not known it.

"Mum had a box of old witchcraft books, really old books. Whose were they?" Severus asked Nana later that evening after supper.

"Old books? I don't remember any. What kind of books?"

"Astrology. Talismans. Stuff like that."

"That sounds more like your grandfather's family than mine. A couple of them were deeply interested in the hidden mysteries. I wonder how Eileen might have gotten their books."

There were thus no answers. Just more questions. Still it was something to have the beginnings of one's own private library.

At the beginning of August, Severus went to stay with Gra for three and a half weeks. By this time he had a supply of chants to practice, together with an old book on anatomy so that he could learn about things like spleens and kidneys.

At Gra's there was time to study and relax. She, too, had a garden, but it was for flowers and butterflies. Severus told her about his visit to his old home.

"Some of your schoolbooks are there. I didn't know you studied French."

Gra laughed. "Je m'appelle Leonora. Comment-allez vous? That's about all I remember. Was there anything else?" She was cutting up a stewing hen for supper.

"Seaman's stuff, navigation and all. Old Sherlock Holmes magazines. Lots of murder mysteries."

"That sounds like the books I gave Toby for you to read when you grew up. Except for your great-grandfather's seaman books. Those were for Toby."

"Some of grandfather Prince's books were there, too. Old books on magic and talismans."

Gra paused to face Severus instead of the chicken. "Child, I never knew the Princes to keep books. Those were your great-grandfather Snape's collection."

A tightness, an excitement, began to develop in the pit of Severus's stomach. "I remember his books on dark creatures and strange cultures. But why would he have such advanced books on magic?"

"From his travels. Did Wensley or Toby never tell you anything about the family?"

Severus shook his head. "I knew he was a sea captain, and that's where he got the shrunken heads and voodoo dolls. That was all."

Gra went back to cooking as she talked. "Constantina and I are from old Lancashire families, but the Princes and the Snapes came from Yorkshire, the Princes from Kippax just outside Leeds. I think they picked the wrong side in a civil war about five hundred years ago and had to remove to someplace safer. The wizard community here was a good place to hide. They got a bit of land and settled in.

\textooquote Snape's a village in the North Riding. I think that side worked their way south through Ripon, then came through here with the building of the Leeds and Liverpool Canal. Wensley Snape, your great-grandfather, shipped out of Liverpool.

\textooquote He went all over, and he learned things. Didn't have much schooling, but he knew more than any man I've met. And he got interested in all that magic stuff from his travels. I know you've got the voodoo dolls from the Caribbean, and the shrunken heads from New Guinea, and I'll bet you've got the poison darts from the Amazon{\el} That man had the scariest collection of things—used to give me nightmares every time I visited him. He managed to pick up books, too. Things in black leather bindings with pictures of witches on brooms that you saw when you were small, but also older things. Scarier things. That must be what you found.

\textooquote He was thrilled when he found out that Toby'd been seeing the daughter of Constantina Rossendale, she that married Richard Prince. Ned and I, that's your grandfather who died when you were young, we weren't that happy about it, but old Wensley wanted witch blood in the family. He kind of pushed Toby along, though Toby didn't need much pushing. And Eileen, she was willing, too.

\textooquote So Toby must've got those books along with the ones you inherited when Wensley Snape died." Gra put the stew pot on the stove, and her story was done.

Severus went back home the next day to search the house. He started in the storeroom, opening and rummaging through every case, box, and piece of furniture there. Then he went through his old room.

One box was in the bottom of the wardrobe in his parents' bedroom, another in a cabinet in the kitchen. The shrunken heads and dart blowers were there, just as he recalled them. There were the little statues of multi-armed gods and goddesses, and strange wand-like sticks with Chinese characters. It was a wealth of small artifacts from every continent, all of it very dark. Some of them were old, well-remembered friends. Others he'd never seen before.

This time Severus unwrapped all the books in the box upstairs. He was acquainted with only a few. Most of the rest were printed books from the seventeenth and eighteenth centuries, more than half of them in French. He could guess what they were about from the illustrations, but he couldn't read them.

Two of the books were smaller, older, handwritten on parchment that was still soft and supple, the ink as fresh as the day it was made. They appeared to be spell books, but like the others they were unreadable because they were in Latin. Something else to study.

Severus carefully packed everything back into its boxes and left it where it had lain for nearly fifteen years. He did pick one shrunken head, one voodoo doll, and the cribbage board to take with him to Hogwarts as a reminder of great-grandfather Wensley Snape.

He also took Gra's French schoolbook. At some point he wanted to be able to read the books that he'd inherited when Wenny died.


