% A Difference in the Family: The Snape Chronicles (Rannaro)
% Too Much For Granted

\chapter{Narrowing Options}

\subsection{Sunday, June 30, 1996 (the day before the full moon)}

Severus Snape sat comfortably in his own room in his own home sipping a cup of tea and poring over the stacks of personnel files he'd brought from Death Eater headquarters in Croydon. At first he was fascinated by the wealth of detail - personal histories, family members, habits, skills and observed talents, and current assignment. Then he became even more intrigued by what wasn't there, or rather who wasn't there.

There was no file on Lucius Malfoy. Neither was there a file on Bella Lestrange or, for that matter, on Snape himself. No first or second rank Death Eater, and few in the third rank, had a file. As near as he could tell, it was a question of access to the Dark Lord. Those who spoke directly to the Dark Lord retained their privacy. The rank and file were under the microscope.

A few, a very few, did not list a current assignment. The whereabouts of Fenrir Greyback, for example, was curiously unknown. The same for the Carrows, Gibbon, and Rowle. Several possible causes for this anomaly occurred to Snape, but his favorite theory was that they were on some sort of special assignment for the Dark Lord

Noise from downstairs brought Snape back to his immediate surroundings and to the hour. Poor Peter Pettigrew was about to learn that his holiday was over, and that the time for work had arrived. The most important commission that the Dark Lord had given Snape was the location of a new headquarters building, and he was due in Birmingham that morning to meet with Bella Lestrange and Nigel Yaxley on that very matter.

Descending the narrow staircase that replaced the original and opened through a moveable bookcase directly into the sitting room, Snape looked around for Pettigrew. The clatter of dishes led him into the kitchen in the rear of the house. Pettigrew looked up somewhat apologetically as Snape walked in.

"Breakfast is almost ready," he said. "I just have to get this thing working."

"I told you it doesn't work. There's no gas supplied to the house. No gas, no electricity... You have to cook it on the grate. Or use magic."

Pettigrew's talents as a cook made it easy to remember that he'd spent twelve years as a rat living in a student's pocket. Snape found a Victorian toast holder, placed a piece of bread in it and handed it to Pettigrew.

"Hold this near the coals, not too close or you'll burn it, and keep turning it until both sides are evenly toasted." Snape himself took a frying pan and set it heating on the grate to fry eggs. It was definitely not Hogwarts fare, but Snape usually didn't mind. Sharing it with Pettigrew was a bit of a burden, however, since Pettigrew tended to either grovel or whine about everything.

"I'm grateful that you're so knowledgeable about these muggle technologies. Toast in wire baskets, I wouldn't have guessed."

Snape shook his head, choosing not to reply. Instead he commented on the day's work. "We're going to meet Lestrange and Yaxley this morning. We have a headquarters to find. How much do you know about buying real estate?"

Not much, it appeared, so Snape tried to give Pettigrew a crash course on square footage, load-bearing walls, electrical wiring, and plumbing, but it was a lost cause. "Just be sure I get to see it before you sign a contract for anything," he said finally.

It was time. Leaving the small house for the area yard in the rear, Snape and Pettigrew looked around, then apparated to the side of the nursery in car park nine at Aston University. There Bella and Yaxley met them a few minutes later.

"Why here?" Bella asked, looking around.

"A place very few people are likely to be at midmorning on the last Sunday in June," replied Snape. "We didn't want to apparate into a crowd."

They found a coffee shop not far away, where Snape took out a map and a list of wards and street addresses.

"What we're looking for is an older building in one of the less prosperous wards where fewer people will pay attention to us. There's a lot of the old brick terraced housing left. The optimum would be an entire terrace. We could gut the interior and make one large office area, while it would still look like individual dwellings from the street. You can work together as a group, or you can split up and look individually. No strong-arm tactics, though. Subtle."

"What do you mean, `you?' Aren't you coming with us?" Bella asked, her eyes narrowing suspiciously.

"I have other work to do."

"How many masters do you serve?"

Yaxley and Pettigrew were suddenly still, watching Snape and Bella carefully, not about to take sides.

"Do you doubt my loyalty?" Snape asked quietly

"Maybe someone should."

"I'll tell the Dark Lord you question his judgment. I'm not the one who requested this position."

Bella was silent. The other two began to breathe again. Then Bella spoke up once more. "How do we know you aren't trying to manipulate us into moving where we can be attacked?"

Snape shut down, cold and dangerous. "If we weren't surrounded by muggles, I'd take you out right now. Say the word, and you and I can apparate to the Grampians for a little duel."

It was Bella who backed down. "I just meant that you're an unknown. We don't know how far we should follow you because you haven't proven yourself yet."

"Then let me reassure you. If I wanted to manipulate the location of headquarters, I wouldn't be leaving you here to do the choosing. I'd be selecting it myself. But I'm assuming you'll have found a place in the next few days, so I have to be organizing the moving in of equipment and personnel so the Dark Lord doesn't have to be kept waiting. Would you rather be doing that while I'm looking for the building?"

Bella shook her head, and the challenge was beaten back. After circling possibly fruitful locations on the map, Snape apparated back to his home.

That evening Pettigrew was tired and whining about the tribulations of the day. "...and she kept insisting that we could cast Imperius curses and force the estate agents to sell at a discount, and she wanted to turn a couple of tenants into cockroaches. If we have to work with her, we'll never find a new location."

"You can always work around her. It's a matter of negating her influence. You've done it before."

Pettigrew stared at Snape. "When did I ever...?"

"Oh, not with Lestrange. With her cousin Sirius. You had everyone believing for twelve years that he blew you up, not the other way around. You even fooled Dumbledore. Surely someone who could fool Dumbledore could handle Bella Lestrange."

"Well, maybe. That was a rather good setup."

"I've always wanted to ask - how did you do it?"

"It was really simple. Sirius didn't have the explosion spell, I did. Since I knew when it would go off, I could transform and get out at the right moment. I just had to cut off a finger and leave it there for everyone to believe I was dead. The biggest problem was the timing."

"I see. Ingenious."

The next day passed much the same, with Snape joining the other three from time to time to check out buildings that had some promise. That evening they found the perfect location, in a ward somewhat east of the city center. The next day they bought it.

The row of houses was in poor condition, its brick still obscured by more than half a century of coal smoke that all the intervening clean air acts couldn't wash away. The company that owned it was delighted to get such a high offer for the dilapidated buildings, since some meddling do-gooder had requested the property be given historical landmark status, and until the years of paperwork were gotten through it couldn't be sold to a modern developer.

Only two of the units were occupied - poor working families that were equally delighted to have their leases bought out for enough money to allow them to move somewhere better, something arranged that very day. Moving was handled by a local Death Eater crew that didn't have to disturb the neighborhood with things like vans. The rest of the units were in such poor condition that they'd been boarded up. The appropriate distribution of carefully selected mind spells and honest to goodness real muggle money allowed all the formalities of vacating and purchasing to be accomplished at once, since somehow everyone was under the impression that the deal had been in progress for weeks instead of being worked out in one day. The muggles were left with the memory that everything had proceeded quite normally.

Bella had to be banned from the negotiations, however, since she insisted on using words like squalor and hovel, and was generally not inclined to be diplomatic.

\subsection{Wednesday, July 3, 1996}

Snape was summoned the following morning to the Dark Lord. The place was a northern heath, vacant of everything for miles around except stone walls and sheep.

"You have found us a home."

"Yes, Lord. We await only your permission to perform the secrecy spells."

"You will not do so. We shall come ourself to attend to the spell. We shall be our own secret keeper."

"Yes, Lord. When that is done, we can begin the renovations." Snape paused. "Lord, if I may be bold..."

"Speak."

"Lord, the location takes up a significant amount of space, and there will be considerable movement in and out. I've been working on modifications to the spell that will allow an outer shell to remain visible at the lowest level of consciousness. People will know something is there but never have any reason to notice it." Snape took a folded piece of parchment from his robes. "If my Lord would condescend to..."

The Dark Lord received the parchment. "We will look at it," he said.

Bella had refused to set foot inside until the renovation was complete, so Snape, Yaxley, and Pettigrew cleaned things up in preparation for the Dark Lord. They couldn't begin any demolition or rebuilding until the property was shielded from notice by neighboring eyes.

An advance guard apparated in to the `new' headquarters building that evening to secure the place for the Dark Lord's arrival. Snape was a little surprised to see who accompanied the Dark Lord - Gibbon, Greyback, Amycus, Alecto, and Rowle. Snape was curious as to when they'd returned from wherever they'd been, but he was not to have his curiosity satisfied, since he and his two lieutenants were ordered out. They were not to observe either the arrival of the Dark Lord, or the spell that was performed.

It was quite late, and the area was quiet and sleeping, when suddenly the headquarters building disappeared. There was a sense of some kind of wall that concealed the end of the block - if pressed, Snape would have called it boardings around a construction site - but nothing that would allow entry. Gibbon appeared out of nowhere with a bundle of small, folded note papers, handing one each to Snape, Yaxley, and Pettigrew, and giving the rest of the bundle into Snape's keeping.

"Here's a list of the people you give them to. There's one each. One of them doesn't get a note, or the wrong person gets a note, and heads will roll. The Dark Lord has to approve everyone who gets access. No stray passes lying around. He wants to move in by noon tomorrow."

Snape nodded in understanding. They'd have to work all night. Gibbon disapparated. Snape and his lieutenants apparated to Snape's home where he gave them safe house locations of everyone on the Dark Lord's list with instructions to have them meet on the street outside headquarters in half an hour to start the rebuilding. Then Snape returned to Birmingham with blueprints. Opening and reading his own note, he watched as the building reformed, then he entered and began setting up for his work crews.

\subsection{Thursday, July 4, 1996}

By eleven o'clock the next morning, the work was done. The interior of the entire terrace had been gutted, except for the upper floor itself. Snape had been a little nervous about the load-bearing pillars and beams that replaced the walls, but careful monitoring had insured that they were properly placed. An underground area had been added as well, the excavated dirt being disposed of by sprinkling it over the Lake District and Snowdonia National Park.

Much of the underground area was taken up by an arena that could be used for conferences, demonstrations, combat training, or punishment. The interview chamber was on the other end of the building, connected to the entrance by a staircase. There were also several holding pens and cells. The ground floor was offices. Field Operations had the largest space, while smaller rooms were designated for Recruitment, Disinformation, Intelligence, Accounting, and so forth. The supplies that were used on a daily basis were also stored there, and there was a reference library.

The upper floor contained more storerooms, the clinic, a cafeteria (since the Dark Lord preferred his servants to eat and socialize on the premises rather than among the general population), and Snape's laboratory. Two of the original bedrooms were retained next to the cafeteria as small dormitories for Death Eaters who had to stay at headquarters longer than a day.

The Dark Lord arrived at noon, and entered for the first and only time through the front door. Snape, Yaxley, and Pettigrew gave him a tour of the premises, after which he retired to the interview chamber, where he would oversee the arrangement of his own personal space.

Shortly thereafter, Snape was summoned to the interview chamber. In the center was a small table, on which was a box filled with the folded pieces of note paper. Each note had the name of a Death Eater written on it.

"You have done well. Malfoy always praised your organizational skills, with some justification it appears. You will now start bringing our people and supplies in. You will be called again later in the afternoon. Act quickly. We begin operations as soon as possible."

Orders went out together with the individual notes, and soon Death Eaters were apparating in with boxes, crates, and furniture. The back area yards were designated as service entry points to keep the mass movement off the street. As each Death Eater arrived, he or she was told the office they were assigned to. Bella came in the middle of all the movement and was shown her new Field Operations office. She was less critical than Snape had dared hope for.

At two o'clock, Snape, Bella, Yaxley, and Pettigrew were in the interview chamber.

"Our first target is the Ministry of Magic. Tonight."

"Lord," said Snape, "we are not yet at full strength. Wouldn't it be wiser to wait?"

"Silence. What you offer would be good advice at another time, but for now you are too cautious. Listen... The Ministry served us well for a year, keeping our presence hidden while we regrouped. Now they think to weaken us by making our presence as public as they can. We shall teach them that they cannot control us this way. We shall control the Ministry, and if they resist, we shall make this confrontation so public that the Ministry will be overwhelmed by it. Tonight the Minister of Magic will be ordered to resign his position in my favor. He will, of course, refuse. Then we shall broadcast our presence in such a way that the whole of Britain, wizard and muggle alike, will tremble in fear of us. Fudge will be toppled, as will each of his successors, until the Ministry falls into our hands like ripe fruit."

"Lord," said Bella, "my department is ready to do your bidding."

"You will not be called on. The operation is already under way, and its coordination rests with another."

"Is it wise, Lord, to entrust too much to one pair of hands?"

"You are anxious, Bella, to redeem yourself. This is commendable, but the time is not yet ripe. Let others prove themselves; your opportunity will come later. Severus, you know what we shall need. Coordinate with the clinic, and be certain that all eventualities have been planned for. You may go."

In the corridor, Bella turned to confront Snape. "You think your star is going to eclipse mine, don't you? Well don't get too comfortable up there. I'm already climbing back, and my credentials are better than yours."

Snape didn't think it was necessary to inform Bella that he was not the one coordinating whatever it was. He checked the progress of the restaffing of headquarters, then apparated home and started ferrying in his lab equipment and Malfoy's files, which he stored in the laboratory.

Lancashire seemed a good place from which to send Dumbledore a patronus, it being out of the way and not watched, and on one of his trips Snape took a moment to do so. This was the first time he had conjured a patronus since contacting Sirius Black about Potter's vision, and when he went out onto the moors, he thought what he was doing would be fairly routine. It was not.

The incantation \emph{"Expecto Patronum!"} this time produced no silvery fox, but a delicate, prancing doe. Snape stared at it, dumbfounded. \emph{Where did that come from? What's happening to me if I can't even be consistent with a patronus?} The question of why the fox had metamorphosed into a doe was quickly shut behind a mental door, for there was a more urgent problem to deal with - that of getting word to Dumbledore. For some reason, Snape was reluctant to let the headmaster know of the change in his patronus.

In the end, though, there was no other course. Snape owned no owl, and there was no way he could communicate by floo network, for even had Pettigrew not been in his home, the house was not connected. Luckily the patronus carried his voice, which Dumbledore would recognize. Again conjuring the patronus, Snape sent the doe speeding northward. `Ministry being blackmailed. Highly public attack planned. No information yet on what, where, or when.'

That accomplished, Snape returned to the job of moving his equipment to Birmingham. At the end of the day, he apparated to his home and the unpleasant prospect of spending another evening with Pettigrew. Just before that last trip, however, he took a moment to review the day's surprise. \emph{Do I know anyone with a deer patronus?} he thought. \emph{Potter has a stag. Could that mean that his father's patronus was also a stag?}

The thoughts were quickly locked away again. It was best not to pursue that line of logic. Not if he still wanted to be able to maintain an impenetrable facade before the Dark Lord.

\subsection{Friday, July 5, 1996}

The next day around the lunch hour, Snape left setting up his laboratory to grab a bite to eat in the cafeteria. It was fairly full, but there were still a few small tables that were empty. Snape, preferring to eat alone anyway, chose one in a corner where few would see him. He was there when Greyback came in with Gibbon.

"Ah-ooo!" howled Greyback. "Set 'em up and let me knock 'em back. I felt it today! If you told me yesterday a bunch of steel girders and concrete pylons would hit my gut like tearing out a throat, I'd of thought you was crazy, but watching those cars hit the water... Blood rush!"

Gibbon tossed a couple of galleons to the servers. "Something a lot stronger than tea for everyone! We struck a blow for the Dark Lord today that they'll hear all over Britain. Let's see the Ministry hush this one up!"

People had left their tables and were crowding around the two, eager for information. Through the babble of voices punctuated by Greyback's howls, Snape realized they were talking about a catastrophe, a bridge that collapsed and spilled muggle cars into the river below. "Where?" he asked, and other voices picked up the question. "Where?"

"Brockdale! Broke apart like a house of cards! We'll teach those muggles to fear us!"

Snape toasted the success with the others, but left as soon as he could without being obvious. Leaving through the service entrance, he slipped out of the area yard and down the block to send a patronus. `Death Eaters claim to have brought down Brockdale Bridge. Do you have any news of bridge collapse? Do not reply, it could be dangerous.' Then he slipped back into headquarters.

The evening news was full of the Brockdale disaster. No one, from engineers to government officials, could explain how a bridge barely ten years old could suddenly part in the middle as if a giant had snapped it in two. Snape bought an evening newspaper and took it home with him to Lancashire.

"Do you think Fudge will step down?" Pettigrew asked as he glanced over Snape's paper. "Who would be Minister then?"

"I don't know. I doubt they'll ask Dumbledore again - he wouldn't take the post anyway. The only one I can thing of is Bones, head of Law Enforcement. I doubt the Dark Lord would like the trade. She'd be a lot harder to work with or around than Fudge."

It turned out the Dark Lord wouldn't have to face that prospect. The very next day, Amelia Bones was found murdered in her own home. The discovery was made by muggle police, and the rumor at headquarters was that the Dark Lord's squad had told them of the killing to ensure that it hit the muggle news before the Ministry could move to stop the story.

Dumbledore's patronus greeted Snape outside his home. `Come this evening. We need to talk.' Snape told Pettigrew he was going out, not particularly liking the little man's curious stare. There was nothing Pettigrew could discover in the house while he was gone, but Snape didn't like having his movements monitored.

\sbreak

"You've heard of the Bones murder?"

"It and the Brockdale Bridge are the talk of headquarters. There's a feeling of euphoria permeating the whole building."

Dumbledore poured the mead and handed a glass to Snape. "I have something for you to do. You have to arrange another murder."

Snape choked on the mead. When he stopped coughing, he said, "Why would you think I'd agree to something like that?"

"Hear me out. Things are changing fast. I have some tasks to perform that will be dangerous, even life threatening. The Order cannot afford to lose its secret keeper - it would place everyone in grave danger. I have to perform a spell to switch secret keepers."

"That wouldn't be safe either," Snape said. "Any other person would be vulnerable to attack and be forced to divulge the secret."

"Not if Riddle was convinced that the person was already dead."

"I see. This murder would be a cover story to protect the new secret keeper. Has someone already been chosen?"

"Yes. Emmeline Vance."

\subsection{Sunday, July 7, 1996}

Rain lashed the street outside Snape's home as he and Pettigrew prepared to apparate to Birmingham. It was no brief summer squall, but a driving downpour whose force would have been more appropriate in some southerly latitude.

Birmingham was being pounded by the same storm, only further south from Lancashire the wind was stronger. The two wizards hurried into headquarters where they found Bella and Yaxley waiting. All four had an interview that morning, and as they turned to the stairs leading down, Snape caught a glimpse of Bella raising her eyebrows in question, but not to him. To Pettigrew? It was one more thing to worry about.

"You see around you the labor of our servants," the Dark Lord informed them with some pride. "No action by the Ministry could conceal a work that spreads its force over all of England."

"Lord, where did it strike first?" Snape asked.

"Cornwall and Devon, where its effects are enhanced by some friends our servants brought with them from far northern lands. Friends our good servant Macnair enlisted to our cause. Our excellent servant Macnair, before the poor judgment of others took him from us."

"If my Lord will permit," Snape began diffidently, "I have acquired some information about that... incident."

"What information? Speak."

"The name of the enemy who witnessed the arrival of Potter and his friends at the Ministry of Magic, and who alerted the Order and Dumbledore to the presence of our people."

The Dark Lord looked coldly at Bella, Yaxley, and Pettigrew. "You will leave us, and wait to be called again." When they had left the room, he said to Snape, "Continue."

"Her name is Emmeline Vance, a witch who's basically a common errand runner for the Order. A person of little importance until she witnessed the arrival at the Ministry."

"She shall be punished for interfering. You may..."

"Lord, forgive me. May I speak?"

"You are not wont to be so forward. Speak then."

"It is your will that terror spread through Britain, among wizard and muggle alike, but after the execution of Amelia Bones, the Ministry might be more prepared than ever to hush something up. You have the opportunity to make this so public that the Ministry will be helpless to respond."

"You intrigue us. How?"

"Dumbledore is trying to establish contacts with the muggle government. Early tomorrow morning, Vance will be apparating into St. James Park near Birdcage Walk to meet with someone from the Home Office in Queen Anne's Gate. That's right by the Treasury, the Foreign Office, and Number Ten Downing Street. A public attack there, a bombing perhaps, would be impossible to conceal."

"Do you know the time of this meeting?"

"Very early, about five o'clock, before there are many people on the street to see her come in. There would be some, of course - London streets are never empty - so if they challenge her, everyone would know who it was. Everyone who matters, of course."

"Does your laboratory contain explosives?"

"I can prepare them this afternoon."

"Do so. Mention this to no one. Secrecy is of the utmost importance."

"Yes, Lord."

Snape was allowed to leave the Dark Lord's presence and return to the setting up of his laboratory. Around noon, he went to the cafeteria for a bite to eat and a moment's relaxation. He'd just taken his first sip of tea and was about to start on a chicken salad sandwich when the room was rocked by what felt like an explosion.

All around, Death Eaters leapt to their feet, crying out to each other, "What was that? What happened?" Snape was already across the room and heading down the stairs, knowing where his own place was in an emergency. On the way he ran into the messenger who was looking for him.

"He wants you, sir. He wants you now. You'd better hurry. He's furious."

"Furious at me?"

"No, sir. It happened shortly after Mrs. Malfoy was admitted."

Snape raced to the interview room where he was admitted to the terrible spectacle of both Bella and Narcissa being punished by a Dark Lord more wrathful than Snape had ever seen him. The sound of Narcissa's screams cut him deeply, and Snape needed all his strength to appear indifferent to her suffering.

Dropping to his knees at the edge of the circle of light that delineated the punishment area, Snape said, "Lord, you have sent for me." He, too, was hit instantly with a Cruciatus curse, and collapsed on the floor in pain. Luckily his was warning rather than punishment, and the curse was lifted almost immediately. Breathing heavily, Snape struggled back onto his knees.

"You will tell us," the Dark Lord shrieked in rage, "of the destruction of our property at Hogwarts! And you will answer for your failure to impart this information to us earlier! Speak at once, or join these two wretches!"

The images of the diary that Dumbledore suspected of being a horcrux lay buried deep in the recesses of Snape's brain and did not surface. "Lord," he gasped, "I know of no property of yours that was destroyed at the school. I never..." Pain hit again, and Snape was forced to stop.

"You know nothing of the opening of the Chamber of Secrets? Nothing of a enchanted object that completed this great work?" The Dark Lord's ire was so great that froth speckled his lips, and spat his words into the quivering air of the interview chamber.

"Lord, I understood there was a book, a sort of a journal, that was used, but that it was yours... It bore the name of a student..."

"And was it destroyed?"

"Yes, Lord."

"By whom?"

"By the Potter boy."

"How!"

"With the fang of a basilisk."

"Such would have indeed destroyed it." A wave of the Dark Lord's wand released the two women, who lay whimpering on the floor. "We are aware at whose door to place blame in this matter. You may go now, Severus. What follows here does not concern you. Yet."

Snape rose and hurriedly returned to his laboratory, all thought of tea and chicken salad erased from his mind.

Later, Snape was again summoned into the Dark Lord's presence. "Tell us of young Malfoy," was the command.

"He is both loyal and eager to prove himself," Snape responded. "That is how his parents have raised him."

The Dark Lord turned to contemplate Snape, the red eyes and slitted nostrils more serpentine than ever in the dimness of the interview chamber. Snape wondered briefly if bright light hurt the Dark Lord's eyes, for though he used it for the display of punishment and large meetings, individual consultations tended to be in semidarkness.

"Do you seek to shield those who betray us?" The question was a menacing hiss.

Snape dropped at once to his knees. "I know of no betrayal, Lord. Poor judgment, perhaps, in an overzealous attempt to serve your memory, but nothing..."

"You would do well to be more careful of your own position."

Snape was silent.

"We will assign the boy a task to demonstrate the dedication of his family to us. The task is to be accomplished at Hogwarts. The failure of the boy is the failure of the family. If you are right, he will be eager to prove himself. Yet payment must be exacted for the injury they have caused us. It will be amusing."

In the pause that followed, Snape ventured, "What must I do, Lord?"

"You are our eyes and ears at Hogwarts. Be aware that the boy will have a mission to fulfill. Do not stand in his way. Go so far as to remove obstacles if necessary," The red eyes narrowed to black slits. "He cannot succeed. Our great enemies do not fall so easily." The Dark Lord turned his back on Snape and moved away. "Still," he mused, "there is the possibility of luck which we cannot discount... You are dismissed, Severus."

Rising quickly, Snape left the interview chamber. He wanted to contact Dumbledore at once, but restrained himself. Whatever Draco had been given to do, would be done at Hogwarts. It was only the beginning of July. They had time. On his return to Lancashire that evening, Snape sent a patronus northward.

The following morning, shortly after five, a tall, older woman wearing a green cape was driven by a group of ruffians into Guards Road near Birdcage Walk. The early traffic screeched to a halt as the men surrounded her, taunting her. One of them yelled, "You'll never cross the Dark Lord again, Vance!" and then an explosion sent everyone scurrying for cover. When the dust settled, there was blood everywhere, a hole in the roadway, and the burning remnants of the green cape. The attackers were gone. Surprisingly, the force of the explosion had been narrow, and there were no other injuries.

\subsection{Tuesday, July 9, 1996}

The muggle government was under siege, not by the Dark Lord but by the muggle press. Four sensational stories in a row, culminating in a brutal attack around the corner from Number Ten with no suspects despite its having taken place in full view of commuters and security guards, were rocking the nation. Reporters vied with one another over the top spot in the headlines - new revelations about the construction of the Brockdale Bridge, calls for environmental commissions to revisit the repercussions of global warming, or speculations as to Emmeline Vance's terrorist connections.

The wizarding world was in an uproar as well, with \emph{The Daily Prophet} putting out extra editions on the tragedies and trying to tie every traffic accident in Britain to Death Eater activity. Pressure was mounting on the Ministry of Magic like a tidal wave, and on Tuesday, Cornelius Fudge resigned as Minister of Magic. His successor was Rufus Scrimgeour, Head of the Aurors and a subordinate of Amelia Bones until her murder. It was the death of Bones that had suddenly thrust Scrimgeour into the limelight.

Birmingham was electrified with a sense of importance and purpose. It was clear now that the yearlong wait was going to culminate in the triumph of the Dark Lord, and departments began to engage in a friendly competition to provide him with the next creative action against the stability and order of Britain.

Snape was hit with requisitions from all sides for Polyjuice Potion ("I don't care what your department head told you - it takes a month to make"), Veritaserum (ditto) and a wide variety of poisons and explosives. Starting Monday morning, he was in the laboratory for thirty-six hours straight just setting up the cauldrons and getting the brews started. Not until Tuesday evening was he able to apparate back to Lancashire in the hopes of getting a few hours rest.

He'd barely arrived outside his front door, however, when he was accosted by a glimmering little silver cloud - Dumbledore's phoenix. \emph{`Come at once. I need you'} was all it said. Since Dumbledore had promised he would not send a patronus to Birmingham, Snape had no way of knowing how long it had been waiting for him, or how urgent the matter was. Just as he apparated, he happened to glance at the window of his house. Pettigrew was peeking through the curtains.

Dumbledore sat collapsed in his office, his head resting on the desk, arms stretched in front of him, still conscious but sinking fast. Snape turned toward the door at once. "I'll get Madam Pomfrey," he said.

"No, Severus. Not Poppy. Should not be involved... You. You can treat it... hand."

Dumbledore's right hand was smoking, smoldering, the stench of burning flesh searing Snape's nostrils. The scorching was clearly moving into the wrist, slowly and inexorably, like a steady flow of lava, the black crust concealing but not blocking the progress of the fire within. Snape immediately began a low chant over Dumbledore's hand and arm, swelling the tissues in the still sound flesh to block the progress of the fiery poison. Then he rose, uncertain what he was dealing with, but able to focus first on the symptoms.

"Lower the shields," Snape said. "I'm apparating to my office." Once there, he began pulling jars and bottles from the shelves, returning to Dumbledore with an armload of equipment and ingredients,

\emph{Burning, like charring, rather than poison or an acid burn. And the necrosis is progressive, so it's virulent.} He put a small cup of potion to Dumbledore's lips, "This first one will induce your body to produce more blood." Another tiny cup followed. "Don't be alarmed. This will slow your heart. If the circulation is retarded a bit it may slow the process of consumption and give us more time."

Dumbledore was drifting into a comatose state, something that Snape desired. Pulling back the headmaster's sleeve, Snape made an incision around the lower arm, just above the wrist, cauterizing capillaries as he went. Here the flesh was still good, and Snape wanted to keep it that way. If it meant cutting off Dumbledore's hand, he would do it, though he hoped he wouldn't have to go that far.

Quickly, carefully, Snape began by clamping the vein, so that clean blood could go into the hand, but infected blood would not be taken into the healthy tissue. Then he started cutting away diseased tissue, making sure that no tiny trace of necrosis remained above his incision. He was relieved to see that the bone looked normal. The spell attacked flesh only. That meant that it might be contained if it was deprived of new flesh to attack.

Even as he worked to stem the corruption, Snape realized that Dumbledore could not have been waiting for him long. The speed with which the damage from the curse progressed was such that if Snape had not arrived when he did, it would have been impossible to save the headmaster. Now at least - now that the damage had been blocked, however temporarily - Snape had time to discover what he was dealing with. On Dumbledore's desk lay a golden ring with a heavy black stone, broken and disfigured, and the sword of Godric Gryffindor.

Snape approached the ring with intense curiosity. It was clearly the cursed item that had so badly injured Dumbledore, though whether the damage to it indicated that the curse was gone or not remained to be seen. He began a series of complex spells to determine what curse had enchanted the ring, and whether or not it remained.

In terms of medical skill, there was never any question but that Madam Pomfrey was by far a better healer than Snape was, but there were three things about Snape that Pomfrey prized as invaluable tools. The first was his modest but health-oriented legilimens ability. The second was his knowledge of muggle techniques. The third was his expertise in dark arts. Seldom were the talents of healing and dark arts combined in one person, but Snape combined them. Understanding lent efficacy to his spells and guided Pomfrey in hers.

Snape had never before seen the curse that empowered the ring, but he recognized its genetic trace. The dark arts were constantly evolving and shifting but, like organic evolution, each new development was the offspring of something that preceded it. This particular spell, powerful as it was, was the lineal descendant of a medieval scorching spell originally intended to render books unreadable. It had been adapted to flesh and enhanced over the centuries.

So now, knowing the composition of the spell, Snape began a frantic combination of different soothing and cooling medications, of purifying agents and restoratives. After what seemed hours, but was in fact a much shorter time, he could tell that the strength of the curse was no longer spreading. What remained of skin and flesh, rather than burning, was cooling and drying, withered and black, but now at least stable.

Snape took a needle and pierced the vein on the uninjured side of the clamp, then examined the blood he withdrew. It appeared whole and good. A similar sample from the damaged tissue was not good. The curse still operated, and though for the moment it was confined to the hand, it would eventually break forth again. The good news was that the ring had released its curse once for all and could now be handled safely by anyone.

Easing the clamp off Dumbledore's vein and making sure circulation was steady, Snape then set to medicating the open area with ointments that promoted healing and the regeneration of tissue. The hand would remain withered and black for the rest of Dumbledore's life. Unfortunately, though Dumbledore's body was, for the moment, essentially healthy, Snape feared that the `rest' of Dumbledore's life would not be long.

When the hand and arm were finally bandaged, Snape tipped a goblet of thick golden potion down Dumbledore's throat. After a moment the headmaster stirred. He blinked at Snape a couple of times, then smiled.

If it was meant to be a disarming smile, it didn't work. "Why did you put on that ring?" Snape demanded. "It carries a curse. Surely you realized that. Why even touch it?"

"I... was a fool. Sorely tempted..."

"Tempted by what?" It was insupportable. A few hours wait to have the ring tested and Dumbledore could have worn it with impunity. As it was, he'd jeopardized everything for... Snape didn't know what for. "It's a miracle you managed to return here! That ring... carried a curse of extraordinary power!"

Dumbledore smiled again, an embarrassed smile that asked for forgiveness, which Snape was not prepared to grant. "To contain it is all we can hope for!" Snape practically screamed in his frustration and fury. "I've trapped the curse in one hand for the time being..."

"You have done very well, Severus."

Dumbledore was looking into Snape's eyes, and Snape allowed the contact. \emph{Don't pat me on the head and patronize me! If I hadn't arrived when I did, you'd be dead by now! You're still going to die, you know!}

"How long do you think I have?"

"I can't tell. Maybe a year. There's no halting such a spell forever. It's the sort of curse that strengthens over time."

"I am fortunate that I have you, Severus. But really, this makes matters much more straightforward. I refer, of course, to the plan Riddle is revolving around me. His plan to have poor Draco murder me."

Snape sat in the chair on the other side of Dumbledore's desk, facing the headmaster. He was dumbfounded. As far as he was concerned, Dumbledore's recklessness had rendered Draco's task moot. A glimmering of the headmaster's meaning was beginning to form in his brain.

Since Dumbledore now made it very clear with a shake of his head and a raised hand that he would not discuss his transgressions with the ring any further, Snape let the topic shift. "I don't think the Dark Lord expects Draco to succeed. This is punishment for Lucius's `failures.' Slow torture for Draco's parents while they watch him fail and pay the price for their mistakes."

"A death sentence for both Draco and me," Dumbledore observed. "And you're the natural one to complete the job once Draco fails, no?"

The Dark Lord had not said so, nor had Snape left the interview chamber with that thought, but now Dumbledore's suggestion had, as it often did, planted a seed in Snape's brain. "That could be the Dark Lord's plan," he said.

"Riddle foresees a moment when he no longer needs a spy at Hogwarts."

It was hard to tell if this was a question or a statement. Snape looked into Dumbledore's eyes, and a previously unthought thought surfaced in his mind. "He hopes to take over soon at Hogwarts, I believe."

"If he does, you must promise to do all in your power to protect the students." At Snape's nod, Dumbledore continued. "Good. First, you must discover Draco's plans. He will be frightened and therefore dangerous. Guide him. He trusts you."

"Less now than before, I fear. He may blame me for taking his father's place."

"Still, we must try. He may accidentally strike at others while aiming at me. In the end, of course, there is only one possibility of saving him from Riddle's anger."

"You're going to let him kill you?"

"Of course not. I am going to let you kill me."

Over and above the quantity of arguments Snape wanted to muster against this insane idea there rose a deep and powerful anger that Dumbledore could have the arrogance and sense of domination over him to even suggest this plan. Snape's resentment spilled out in sarcasm. "Would you like me to do it now? Or would you like a few moments to compose an epitaph?"

Dumbledore smiled. "I can wait. I am certain we shall know when the time comes. It will, at any rate, be within the year." He contemplated his black, withered hand.

The words appeased none of Snape's anger. Dumbledore was still presuming too much, asking too much. "If that's the case, why not let Draco do it and gain favor with the Dark Lord?"

"No," Dumbledore shook his head sadly. "The boy's soul is still whole. I do not wish it ripped apart because of me."

"I see you have no such concern for my soul."

"Severus, we are talking about a difference in intent. Draco will be trying to murder me as Riddle's agent. You will be freeing me from pain and slow death. If, as we think likely, Riddle plans to attack Hogwarts soon, it may also be from possible torment and humiliation. Both Greyback and Bella like to play with their food before they eat it."

Their eyes met, Snape locking down automatically. He nodded as if in agreement, and Dumbledore took it as such, but the headmaster seemed to have seen something that disturbed him, for his countenance became sad. "Thank you, Severus. But tell me now, how have you felt about recent events?"

"Felt?" Snape asked, puzzled. "There's been nothing to feel."

"Surely the news about Amelia and Rufus must have touched you somewhere."

Dumbledore's words hit a wall. From the moment Snape had learned of the death of Amelia Bones, he had locked away every memory of the judge who had treated him with kindness and fairness during his trail as a Death Eater fifteen years earlier. There was no point in wallowing in sentiment. In Snape's position, such thoughts and feelings were dangerous. "I assure you, Headmaster," he said, rising now as if to leave, "there has been nothing to touch. Now, I really must return home. It's getting late."

"There were other things I wished to speak with you about," Dumbledore said, motioning for Snape to sit again. "The sudden alteration in the form of your patronus, for example. It did take me somewhat by surprise."

"I have no idea how or why that happened."

"You know of no one who has that patronus?"

"No. But then I haven't had the opportunity to see... Why do you think it reflects the patronus of someone else?"

"No reason." Dumbledore coughed slightly. "Do you think I might have some water?"

Snape stood and filled a glass from a pitcher in the office. He watched Dumbledore for a while, then said, "If I may ask, what were you...?"

"No, you may not. The fewer details you know, the better. Suffice it to say that we removed Emmeline from outside interference in time."

"Then you've already performed the new Fidelius spell?"

The silence stretched out. Then Dumbledore said, "Let me ask you a question. Did it ever occur to you to inform me of the whereabouts of your new headquarters before Riddle performed the Fidelius Charm there?"

Snape opened his mouth, closed it again, looked into the fireplace and then at his hands, then said, "It wouldn't have done any good. You couldn't have remembered."

"Not the exact location, no. But at least the general area. Even the city would have been helpful."

"You don't trust me."

"A man I have just summoned to my side in the last extremity to save me from imminent death. Severus, how can you think I do not trust you?"

"You don't want me to know..."

"It is just that in the last year I have become aware of a side of you I always subconsciously - well, consciously too - knew existed, but never had to take into account before. It appears that when you are focusing on a task that requires organization or analysis, well frankly Severus, you become so absorbed in the performance of the task that you tend to forget - let us be honest here - you tend to forget which side you are on."

"I know which side I'm on, sir."

"Yes, when faced with the direct choice. But really, if it had been Riddle who summoned you to care for a cursed hand, would your actions have been any different?"

"No, but that's not a fair example."

"Isn't it? This summer you were given a complex organizational task, on a far grander scale than you were given when you first came here to teach at the age of what? twenty-one? I would say that you devoted every ounce of your energy to the task, probably forgetting to eat or sleep, until it was accomplished - in about half the time that a normal person could reasonably have been expected to do the same thing. Your single-mindedness is astounding. It is that which inclines me to believe that you should know only what you have to know. Who knows what task Riddle may give you next?"

"You don't trust me."

"Not in everything, no. Only in what is most important."

It was late when Snape finally returned home. Apparating into the front yard, he was once again aware that Pettigrew was watching from behind a curtain.

\emph{I would do the same in his position, though I guarantee I would be more subtle about it. But he's playing me off against Bella. I can't let him get away with that.}

On Wednesday, when Snape and Pettigrew apparated to Birmingham, Bella was standing near the entrance looking her old self again. She once again raised her eyebrows, and then went upstairs toward the cafeteria. After a moment, Pettigrew followed. \emph{They don't even try to hide it. It's a bit like being hit with a sledgehammer.} Snape asked for a meeting with the Dark Lord.

"You have a request."

"Yes, Lord. Now that we have a headquarters building, would it be possible to allow Pettigrew to live here? That way he would always be where he could serve you."

"You will explain why you do not wish Wormtail to stay in your home."

"Lord, he is immensely irritating. He whines and complains and tries to ingratiate himself, and he has no conversational skills. I believe he's prying into my private affairs. He snores. And the house is very small."

The Dark Lord chuckled. It was a strange sound. "Yet I still wish him to assist you in one or two matters. Nonetheless, it would not be good for him to have free access to your home after you return full-time to Hogwarts. At the beginning of August, he will leave you."

"Thank you, Lord."

As Snape walked into the cafeteria, Pettigrew rose and left. Bella beckoned Snape over to the empty seat. A server brought more tea.

"Join me, please. We never have a chance just to chat."

"You're doing a lot of chatting this morning."

"I'm only just beginning to realize how much I missed during all those years in Azkaban. I've been so busy the last six months, I forgot that other people had fourteen years worth of living while I was gone. I mean, puppy dog, that's two-fifths of your whole life."

"And you've retained your math skills all this time."

"So sweet. So kind. Do you know what I learned this morning? I learned that rats have eyes, ears, and memories. Isn't that fun? And that rats who go to school with young wizards attend classes in their pockets. And run around at night."

"How fascinating for you, Bella. A rat's eye view of Hogwarts. You could sell tickets."

"I hear you and McGonagall bet on Quidditch matches. And you taught Flitwick some card game with a board and pegs. And you played jokes on a puffed-up idiot named Lockhart."

"Are you reaching a point, or do you just like to live vicariously through me?"

"How do you do it, puppy dog? How do you change your skin so easily? How do you live and work with those people, year after year, and then turn your back on them as if they're nothing more than strangers to you? Or do you?"

"Are you questioning my loyalty? Maybe we should take this conversation to the Dark Lord right now." Snape started to rise, but Bella put a hand on his arm.

"Don't run away. Is it true that the Dark Lord had to punish you last year for using occlumency against him?"

"If I had used occlumency against the Dark Lord, I wouldn't be sitting here talking to you right now."

"Then he did punish you."

"Didn't Macnair give you all the particulars?"

"Macnair didn't share all his tender moments with me, no. Do you miss her, puppy dog? No, I guess you wouldn't. I've learned other things, sad things. No wife, no children, no family... no special friends... I kidded you about being a monk back in January, but it turns out it was no more than the truth. You're like a machine. No skin to change. How easily would you sell me out?"

"Dearest Bella... I live for the day when the Dark Lord gives me that order. Now if you will excuse me. I think I've played pincushion quite enough for one morning."

Snape went immediately to his laboratory to work. There would be plenty of time later to discuss this matter with Pettigrew.

About half an hour later, Snape went to Accounting with a requisition for more supplies. It was a simple, routine matter, except that as he was returning to his laboratory, he ran into Pettigrew coming up from the subterranean area where the interview chamber was. Pettigrew avoided Snape's gaze and scurried down a corridor out of sight.

That evening, back at home, Snape hustled Pettigrew into the kitchen and shoved him into one of the chairs. "Sit down, Wormtail. We're going to have a little chat. You've been spying on me, haven't you, Wormtail. Telling tales out of school. You need to be taught not to do that, Wormtail."

"But... but the Dark Lord... he summoned..."

"I'm not talking about the Dark Lord. I'm talking about Lestrange. What have you told her? I hope nothing more interesting than the decor of the sitting room."

"She... wanted to know where you went."

"And you told her Birmingham like a good little rat, didn't you?" Snape was staring down into Pettigrew's eyes, and saw his mind suddenly shift to Hogwarts at the question. \emph{No discipline here at all. The demonstration mind for Legilimency 101.}

"Of course. Of course. Where else would you go?" Pettigrew was shaking now.

"You need to be taught not to meddle in my affairs. What are you afraid of, Wormtail?"

Pettigrew's mind flashed the picture, crisp and clear. Snape let a smile twist his mouth. "I heard your former master had the same little problem. So did one of my dorm mates back in first year. You remember the late lamented Evan Rosier. A positive phobia. Pity he had so much trouble with them."

Snape pulled Pettigrew to his feet and marched him through the sitting room, up the stairs, and into the usually locked front bedroom. "This was my parents' room. It's yours for the rest of your stay. Normally I would consider you unfit to pass the doorway, but I don't want to mess things up downstairs. And if anyone would appreciate the situation, it would be my father."

He bound Pettigrew to the bed and intoned \emph{"Petrificus Imperfectus,"} allowing small movements, but preventing Pettigrew from leaving the bed or even turning over. Just as he closed and locked the door, Snape pointed his wand at the ceiling. \emph{"Arachnes,"} he said calmly, then "Good night, Wormtail. Pleasant dreams. Your wakeup call will be at five."

The spiders were small and harmless, some of them web spinners and some burrowers. The burrowers had a fondness for nestling under clothing. The spinners found Pettigrew's nose and ears perfect anchor points for their threads.

Thursday, July 11, 1996

It was a very much subdued Pettigrew who apparated to Birmingham with Snape the following day. Snape kept him near, stirring potions in the laboratory. At noon they went together to the cafeteria for lunch. Glancing down the staircase towards the main entrance, Snape was not surprised to see Narcissa and Draco Malfoy follow Bella through the door. They took the stairs to the right and down to the interview chamber.

Until two days before, Snape hadn't seen Narcissa in years, and then it was hardly the same Narcissa. Looking down at her now, he was reminded of the first grand dinner party he'd ever seen, peeking through the railings at the color and wealth that swirled below him, and how enchanted he'd been by the Snow Queen, the only gentle person in the whole household. \emph{And was it you, sweet lady, who located my grandmother for the Death Eaters, visiting Nana's house with a request for potions so that they'd know where to set the attack?}

Angry with himself for his sudden suspicious bitterness, angry with Pettigrew and Bella for putting him in this position, Snape guided Pettigrew to a table and ordered a light lunch. They ate in silence. Snape hoped to see Narcissa on her way out, but was disappointed.

It was late when the two were finally able to apparate back to Snape's home. Wanting to relax a bit, Snape ordered Pettigrew to his new quarters upstairs, while he himself settled in the sitting room with a cup of tea to read. Around midnight he was surprised to hear a knock on the front door.

Crossing the room and opening the door just a crack, Snape found himself face to face with the shining radiance of Narcissa Malfoy, the shorter, darker Bellatrix a pace behind. "Narcissa! What a pleasant surprise!"

"Severus," she murmured, her voice tense, "May I speak to you? It's urgent."

"But of course." He opened the door wider to allow both of them inside.

Bella swept past Snape with only the most cursory of greetings, so clearly this was Narcissa's visit. Bella must have come under protest, or out of fear. He waved the two women to the sofa. Narcissa accepted his hospitality; Bella stood behind her sister like a bodyguard. Snape returned to the armchair where he'd been reading, Bella's attitude reminding him of his own in Sirius Black's house.

"So, what can I do for you?"

"We... we are alone, aren't we?" Both women were watching him, and so strong was Narcissa's anxiety that Snape could pick it up without trying. Bella's hostility radiated like a nuclear meltdown.

"Yes, of course. Well, Wormtail's here, but we're not counting vermin, are we?" With a lazy flick of his wand, Snape opened the stair panel behind which he knew Pettigrew was hiding. The one he watched was Bella. \emph{She doesn't want him here either. This isn't about me.} "As you have clearly realized, Wormtail, we have guests." Pettigrew started to greet the women, but Snape cut him off. "Wormtail will get us drinks if you'd like them, and then he will return to his bedroom."

"I am not your servant!"

"Really? I was under the impression that the Dark Lord placed you here to assist me."

Pettigrew tried to protest, and ended up bringing glasses and a bottle of wine, then retreating to the stairs. Snape poured, then raised his own glass in a toast to the Dark Lord. Bella was caught, forced to accept his hospitality and drink his wine. He refilled the glasses.

"Severus," Narcissa blurted out, "I'm sorry to come here like this, but I had to see you. I think you are the only one who can help me..."

Sensing rather than hearing Pettigrew's presence, Snape cast a percussive spell that sent him scurrying back upstairs. "My apologies. He has lately taken to listening at doors. I don't know what he means by it..." He was rewarded by the reddening of Bella's throat and face. "You were saying, Narcissa?"

"Severus, I know I ought not to be here, I have been told to say nothing to anyone, but..."

Bella interrupted abruptly, "Then you ought to hold your tongue! Particularly in present company!"

Snape realized he was closing down as if preparing for a fight. Whatever drove Narcissa Malfoy to his home after midnight, it frightened Bella Lestrange. There wasn't much that frightened Bella - she wasn't perceptive enough. \emph{I think I'm going to find out what this afternoon's interview was about without even trying.}

"Present company? And what am I to understand by that, Bellatrix?"

"That I don't trust you, Snape, as you very well know!" At Bella's words, Narcissa covered her face with her hands and began to sob.

The blatant, unqualified statement was a surprise, especially given the shift in their relative status over the last month. Either Bella was suddenly more confident, or she feared what Narcissa would say more than she feared a fight with Snape for the Dark Lord's favor. Bella's challenge allowed a brief moment of eye contact, during which Snape wished he was a more gifted legilimens. \emph{No, not so confident. This is for Narcissa.} He affected calm, leaning back in the chair.

"Narcissa, I think we ought to hear what Bellatrix is bursting to say; it will save tedious interruptions. Well, continue, Bellatrix. Why is it that you do not trust me?"

"A hundred reasons!" Bella's glass slammed down on the table as she moved to confront Snape. "Where to start! Where were you when the Dark Lord fell? Why did you never make any attempt to find him when he vanished? What have you been doing all these years that you've lived in Dumbledore's pocket? Why did you stop the Dark Lord procuring the Philosopher's Stone? Why did you not return at once when the Dark Lord was reborn? Where were you a few weeks ago when we battled to retrieve the prophecy for the Dark Lord? And why, Snape, is Harry Potter still alive, when you have had him at your mercy for five years?"

\emph{My, you have been busy in the last six months. Those questions didn't originate in Azkaban. The first two you'd ask of any Death Eater, but who told you about the Philosopher's Stone, Pettigrew, or the Dark Lord himself? And how many other Death Eaters are asking the same questions behind my back?}

Narcissa was unreadable, her eyes still covered by her hands. Bella broadcast defiance, anger, and suspicion. Whatever Snape answered would travel all through headquarters before noon. He settled more comfortably in the armchair and allowed a sarcastic smile to play around his mouth.

"Before I answer you... Do you really think that the Dark Lord has not asked me each and every one of those questions? And do you really think that, had I not been able to give satisfactory answers, I would be sitting here talking to you?"

"I know he believes you, but..." Uncertainty flickered in Bella's eyes. \emph{Good. Pettigrew hasn't told her everything - he may not realize it's important. Now if I can keep her off balance and him scared...}

"You think he is mistaken? Or that I have somehow hoodwinked him? Fooled the Dark Lord, the greatest wizard, the most accomplished legilimens the world has ever seen?"

Bella was retreating now - Snape could see it in her eyes - unprepared for the accusation that she herself was showing disloyalty. He began to recite the carefully prepared justifications he'd shown to the Dark Lord a year earlier, the night of his return to the Death Eaters, how he'd remained at his post gathering information.

"You ask why I did not attempt to find him when he vanished. For the same reason that Avery, Yaxley, the Carrows, Greyback, Lucius and may other did not attempt to find him..." Avery was to remind Bella that those who rose high could also fall through errors of judgment. The middle group now stood near the Dark Lord. To attack Snape was to attack them. And Lucius's name was for Narcissa, to remind her that what was good for Bella was not always good for her. Point by point, he went through Bella's list.

"But what use have you been? What useful information have we had from you?" Bella demanded.

\emph{Got you, Bella. Now we undermine Narcissa's faith in you.} "My information has been conveyed directly to the Dark Lord. If he chooses not to share it with you..."

"He shares everything with me! He calls me his most loyal, his most faithful..."

\emph{That's what Barty Crouch said. To how many has the Dark Lord said the same thing? He also called you a faithless servant, if I recall.} "Does he? Does he still, after the fiasco at the Ministry?"

"That was not my fault! The Dark Lord has, in the past, entrusted me with his most precious... if Lucius hadn't..."

Finally, Narcissa removed her hands from her face. "Don't you dare blame my husband!"

\emph{`In the past' is a telling phrase. It means `not now.' And I have separated Narcissa from you.} Snape was conciliatory, "There is no point apportioning blame. What is done, is done."

They sparred over his role with the Order of the Phoenix, then Bella turned to the issue of Potter.

"Have you discussed this matter with the Dark Lord?" Snape asked

"He... lately we... I am asking you, Snape!"

Another admission that Bella was not so high in the Dark Lord's favor as she pretended. Snape glanced at Narcissa, still glaring furiously at her sister. He then spoke of his disdain for Potter and the deep trust of Dumbledore - a bit of a fabrication, but Bella didn't need to know of Dumbledore's doubts. In the silence that followed, Snape turned to Narcissa.

"Now... you came to ask me for help?"

Narcissa's eyes welled with tears. "Yes, Severus. I think you are the only one who can help me, I have nowhere else to turn. Lucius is in jail and... the Dark Lord has forbidden me to speak of it. He wishes none to know of the plan. It is very... secret. But..."

Narcissa closed her eyes. Frustrated, Snape had to back down, wishing again that his legilimency skills were better. "If he has forbidden it, you ought not to speak. The Dark Lord's word is law."

It wasn't the response the sisters were expecting. Narcissa gasped in dismay, while Bella looked immensely pleased. "There!" she told Narcissa. "Even Snape says so. You were told not to talk, so hold your silence!"

Now, more than ever, Snape wanted to be sure of what drove Narcissa to his house in the dead of night - what he could do to help her that no one else could, not even Bella. So far as he knew, he had only one advantage in influence over the others - Hogwarts. The only connection she had with the school was Draco. This had to be about Draco's task, a chance to find out if Dumbledore's surmise was correct.

Snape rose and went to the window where his gaze was hidden from both sisters. He'd never had any indication that either one could read him, but he was taking no chances. Dumbledore had demanded a service of Snape, but only because of Draco's task. If the task was other than what Dumbledore suspected, the requested service did not have to be performed. The one way to get more information now was to play along, to divulge that the Dark Lord had confided in him.

\emph{If the Dark Lord hears of this... but I see no other way. Not if I'm to learn anything.} Lowering the curtain, Snape turned back to the sisters. It was a great risk, but Snape wagered that he knew enough about Bella's impetuousness and Cissa's sentimentality to know that this encounter was a family matter, and neither of them would breathe a word of it to anyone, not even the Dark Lord.

Taking a deep breath he said, "It so happens that I know of the plan. I am one of the few the Dark Lord has told. Nevertheless, had I not been in on the secret, Narcissa, you would have been guilty of great treachery to the Dark Lord." \emph{That should suffice to keep both of you quiet.}

Narcissa sighed with relief. "I thought you must know about it! He trusts you so, Severus..."

Bella was not so easy to convince. "You know about the plan? \emph{You} know?"

Ignoring the insulting tone of voice, Snape replied, "Certainly. But what help do you require, Narcissa? If you are imagining I can persuade the Dark Lord to change his mind, I am afraid there is no hope, none at all."

Narcissa began to weep. "Severus... my son... my only son." The childless Bella had no qualms about mentioning honor and duty, and Draco's eagerness to prove himself, while Narcissa thought only of his youth and of the danger. And of the fearful probability that Draco's death was a punishment for Lucius.

Snape remembered Draco's eager, desperate face in June as he as pleaded, "Can't we help? Can't we do something?" \emph{Why would the Dark Lord single out Malfoy for such punishment when Bella was there, too? I'd bet anything her vicious temper was more responsible for the disaster than Malfoy's poor planning... Unless Bella lied to the Dark Lord about her role, and now feels guilty for the repercussions Narcissa must face...} Then Snape recalled the Dark Lord's anger over the fate of the diary.

Narcissa's eyes showed only her terrible fear for her son. Unable to read deeper, Snape looked away, trying to decide the best course of action. To stall for time he said, "If Draco succeeds he will be honored above all others."

"But he won't succeed! How can he, when the Dark Lord himself..." Narcissa froze, realizing the enormity of her words. Snape shifted his gaze from woman to woman, knowing the apprehension on Bella's face was reflected in his own. They were talking treason.

Narcissa was babbling, "I only meant... nobody has yet... Severus, please... You are... always... Draco's favorite... Lucius's friend... the Dark Lord's favorite... speak to him... persuade him..."

Forcing himself to be calm and cold, Snape replied, "The Dark Lord will not be persuaded, and I am not stupid enough to attempt it... Yes, the Dark Lord is angry, Narcissa, very angry indeed."

"Then I am right... he wants him to be killed trying!" Narcissa flung herself at him, begging, pleading that he remove this cup from Draco, convince the Dark Lord, take the task onto himself... The power of her grief washed through Snape, and though he tried to talk to her reasonably, he was being overcome by memories - of Narcissa, distraught at the thought of being separated from Lucius, so joyful on the muggle underground because she was meeting him - of the baby in Snape's own arms, the tiny baby with the perfect fingernails - of Draco, raised in the Dark Lord's service, the heir to a dying world of blood status and privilege, so proud of being a Seeker, frantically trying to claw his way out from under the shadow of Harry Potter...

Narcissa collapsed, sobbing, "My only son... my only son..." while Bella screeched, "If I had sons..."

Silently cursing his own weakness, Snape dragged Narcissa to her feet and guided her to the sofa. He poured her another glass of wine, thinking all the while of the smile that would cross Dumbledore's face at the knowledge that Draco's mother was reinforcing Dumbledore's request. "Narcissa, that's enough. Drink this. Listen to me. It might be possible... for me to help Draco."

She held her breath, as if suspended between despair and joy. "Severus... oh, Severus... you would help him? Would you look after him, see he comes to no harm?"

"I can try." It was the only honest promise he could make.

Then she was on her knees to him, kissing his hand. "If you are there to protect him... Severus, will you swear it? Will you make the Unbreakable Vow?"

Snape stared down at her, not certain how he had reached this moment. His brain was screaming danger, but it battled against Narcissa's radiant hope. \emph{I can't do this. I can't bind myself to this. I have other promises to keep - not just to Dumbledore... to Lily...}

Bella's wild laughter broke through. "Aren't you listening, Narcissa? Oh, he'll try, I'm sure... The usual empty words, the usual slithering out of action... oh, on the Dark Lord's orders, of course!"

It was like cold water thrown in his face. Snape was suddenly keenly aware of the importance of learning exactly what Draco's task was. \emph{If I refuse the Vow and prove Bella right, I'll never again be in a position where Narcissa will confide in me. My only link to the Dark Lord's real plans for Draco - and Hogwarts - will be broken. I doubt I can find out tonight - they think I already know. But if Draco knows I'm sworn to protect him, I may be able to find out from him... I'm his head of house. Protecting him is no more than I would do anyway.}

His eyes never wavering from Narcissa's, Snape said, "Certainly. I shall make the Unbreakable Vow. Perhaps your sister will consent to be our Bonder."

They knelt facing each other, right hands joined. Bella stood gaping, as if she couldn't believe this was happening. "You will need your wand, Bellatrix. And you will need to move a little closer." Speechless, Bella obeyed.

Narcissa began the ritual. "Will you, Severus, watch over my son, Draco, as he attempts to fulfill the Dark Lord's wishes?"

"I will." The first red link of the binding chain spurted from Bella's wand.

"And will you, to the best of your ability, protect him from harm?"

"I will." Another fiery link formed around their hands.

"And should it prove necessary..." The first alarm went off in Snape's brain. The chasm was opening in front of him. "...if it seems Draco will fail..." He wanted to pull away, knowing before she said it what would be asked of him. Wanted to, but didn't. "...will you carry out the deed that the Dark Lord has ordered Draco to perform?"

The choice was clear - ignorance and safety, or knowledge and the possibility of death. \emph{But only if it's a task I can't perform. It may well be Dumbledore is wrong and I can do this thing. Oh, McGonagall, if you knew the wager I was making tonight!} The world was bright, the colors sharp and clear, and the Snow Queen's face glowed in the candlelight. Life burned more fiercely in the shadow of death, when you risked everything on one roll of the dice...

"I will," said Snape, and Bella sealed the vow with a third ribbon of fire. In the recesses of Snape's mind, Dumbledore face appeared, and he was laughing.

\sbreak

Dumbledore listened in silence to Snape's account of the event. When it was done, he shook his head sadly. "I would have wished that it had not reached so irrevocable a point. I cannot afford to lose you. Still, you were there, and no one is in a better position to evaluate the situation than you are."

"And here I thought you would be pleased." The irony in Snape's tone carried a note of humor. "If you're right about the task, you know, then Narcissa's practically guaranteed that you'll get your wish. If it was just you... but when it's a choice between your life and mine, you don't stand a chance."

"If I am right. But that raises another concern, Severus. What if I am wrong and Draco's mission involves something that I do not wish you to do? Was there no clue at all to confirm what this task is?"

"Plenty of clues, but none that give us definite answers. It has something to do with Hogwarts. That's the only place Draco and I have in common. Narcissa said nothing about going anywhere else. Then it's something the Dark Lord has tried to do and failed. That narrows it down considerably. And yet it's something that a sixteen-year-old boy thinks he can accomplish. Bella was clear, Draco's excited by the prospect, and Narcissa confirmed it. Granted Draco thinks he can do almost anything at first hearing. It's only later that his feet start getting cold. But it can't be an utter impossibility." Snape paused. "I did have one thought."

"Which was?"

"His task might be to kidnap Potter. Draco would most definitely enjoy the prospect of that one. And it's something the Dark Lord was ultimately unsuccessful at."

"It may be to kill him. Something else Riddle failed to do. The amount of protection surrounding Harry could explain Narcissa's fear for her son's life. But what would you do in that case if Draco fails?"

"I'm not going to speculate on `what ifs.' Everything depends on the precise nature of the task. The first thing I'll do, when I have time, is borrow that pensieve of yours again."

"Why Severus, whatever for?"

"To study the Vow. An Unbreakable Vow means exactly what the words say it means, no more and no less. What one party is thinking is irrelevant. If it isn't spoken, it isn't part of the Vow. If it is spoken, it is part. At one point Narcissa said, `to the best of your ability.' Now there's a loophole a mile wide. I need to know that Vow inside out and backwards."

Dumbledore smiled. "That's my Severus. No raging against fate, no wallowing in self-pity. Just work the problem."

Snape grimaced. "I wish you wouldn't use works like `wallow' when you're talking about me. There's a certain distastefulness..."

"Harry will be reasonably safe soon." Dumbledore continued. "That was arranged before this all happened. Which reminds me. There is another matter that you need to be aware of. I am in the process of recruiting and hiring a teacher to fill a vacant position. I hope to have accomplished it by tomorrow - no, it is nearly sunrise - by tonight."

"The Dark Arts professor? I already knew about that; it isn't news."

"Alas, no, Severus. I have a Dark Arts professor. It seems that what I am lacking is an instructor in Potions." Dumbledore's brow furrowed in concern. "Is something wrong, Severus? I thought you would be pleased."

Snape looked down at his hands. In any other year he would have been pleased, but now there was a dreadful sense of finality to the news, coming as it did with the increase in the Dark Lord's power, the Unbreakable Vow, and the certainty of Dumbledore's death through the action of the curse in any case. He looked up at Dumbledore with something close to a smile, rueful and ironic. "I guess that means I'm not going to last out the year either."

"I prefer to think that we shall finally break the jinx."

"The funny part is that a little over an hour ago I was telling Bella that one of the proofs of my loyalty to the Dark Lord was that you didn't quite trust me enough to give me the job. What am I going to tell her now?"

"You will have to be creative, I suppose."

"Who are you going to get for Potions?"

"For some time I have been toying with the idea of bringing Professor Slughorn out of retirement... Why Severus, do you not like Professor Slughorn?"

"You want the whole list?"

"Just the highlights."

"You're serious." Snape started numbering points on his fingers. "He never did anything about the hazing in Slytherin house. He never once acknowledged the quality of my Potions work..."

"He told me Lily was one of his best pupils."

"We used to study together. She was very good."

"But you helped her rather than the other way around."

Snape didn't respond, continuing instead with his list. "He never defended us to you or McGonagall when Gryffindor attacked us. He ignored everyone who was neither rich nor popular. He left a mess in his classroom and office. He left practically no stocks on the shelves, and no information about the curriculum..."

"In other words, he effectively destroyed your life."

"Now you're making fun of me."

"Would it be better if Slughorn did not use your office and private room? He would probably like the Dark Arts office. It is warmer and gets more light. I think I would prefer you away from the general population anyway, and it is closer to Slytherin house."

"That would be very nice, Headmaster. Thank you."

Dumbledore paused before speaking again. "There are one or two other points. I do not wish to alarm Horace by taking him into our confidence regarding Riddle, but his position at Hogwarts will be rather like Sibyll Trelawney's. That I wish to have you in Dark Arts assists me in this."

Snape waited for the rest, but it was not forthcoming. "So I'm to look out for him, but not know why. It's that old trust thing."

The comment was ignored. "The other point is that I may be calling on your expertise in dark magic again as I did on Tuesday. Should something occur involving curses or evil enchantments, there must be no confusion among the staff. The one in charge of the matter is the Dark Arts professor. They will have to rely on you."

The next couple of weeks were actually rather pleasant. The Dark Lord's squad continued its raids, though on a less spectacular scale, but that didn't directly affect Snape's life. Bella retreated from her attacks, adopting a policy of ignoring him altogether. Pettigrew stopped spying and tried to avoid Snape as much as possible. Snape was already organizing the Dark Arts curriculum, and was looking forward to returning to Hogwarts. Each of the key areas of concern in his life was locked into a separate compartment in his brain, and when he was focusing on the upcoming school year, no thought of Draco or of Death Eaters disturbed Snape's concentration.

Near the end of July, Dumbledore asked him to come to Hogwarts again.

"There have been two kidnappings, Severus. Do you know anything about them?"

The news was a surprise. "No. I'm not Field Operations. They don't discuss their business outside the department. Who was it?"

"Ollivander and Fortescue. Fortescue may have been taken from his shop. The place looks as if there had been a fight. Ollivander has simply vanished. No Dark Mark was placed over Diagon Alley, so it looks like kidnapping. I should like to know why."

"Ollivander for the wands, perhaps. I can't think of anything special about Fortescue. Except... My very first assignment, years ago, was to identify likely recruits among the students shopping in Diagon Alley. I pretended I was looking for tutoring work and used to spend a lot of time around the ice cream parlor. Did you know Fortescue was quite the expert on medieval history?"

"Indeed? I did not know. That is most interesting. I may need you to do some research for me."

"What sort of research, sir?"

Instead of answering, Dumbledore asked a question. "Did your parents tell you children's stories when you were a boy?"

"Do you mean like `Cinderella' and `The Ugly Duckling?' Storytelling was not something my father would have wanted for me."

"I was thinking more of the stories from your mother's side of the family. Beedle the Bard, for example."

"Never heard of him."

"Indeed? That may actually work in our favor, Severus. You will have no preconceptions." And that was all Dumbledore would say at that time. 


