% A Difference in the Family: The Snape Chronicles (Rannaro)
% The Middle Years (1982-83, Carmichael)

\chapter{The Barracuda}

\subsection{Summer 1982}

Cookbooks gave recipes for four, six, or eight people. Snape quickly got into a routine where he would cook once every two or three days, then eat the same thing for every meal until it was finished. That way he had more time for other things.

At first he was nervous about stepping outside his door, looking carefully down the street for anyone even remotely odd, but after a while going outside became more routine, and he began to explore. It had been years since he'd been out on the moors, and he'd never before gone out with the purpose of just collecting plants, having always relied on his grandmother's garden as a boy. Now the neighbors, many of whom remembered him and his parents, started to think of him as the resident naturalist.

Snape knew he was seen as more than a little eccentric. It didn't bother him in the slightest—in fact, it made things easier. People greeted him with a pleasant `Good morning' or asked if he'd had a profitable excursion, but recognized that he didn't want to socialize or visit, so the conversations were generally short. He could even pop into the local pub for a pint, sit for a while in a corner labeling the small clear bags that he put the leaves and flowers into, and not feel out of place.

True, the first time had been strange. When he'd walked in toward the beginning of July to get out of a sudden downpour on the way home, several of the men in the pub had stared at him as if he were from Mars, but he soon found out why.

"Afternoon," the barkeep said, ready to take an order. "Hope you don't mind my asking, but would you happen to be Toby Snape's boy Russ?" When Snape admitted that he was, men came over to shake his hand and tell him that they still missed his father. One or two even asked about `that fancy school' he'd gone to, which—to Snape's great surprise—Toby had apparently bragged about at some length. When he told them he was now a teacher at that same school, they agreed Toby'd have been proud, and pleased, too, that he would still condescend to come into a local pub to drink a pint with his dad's old mates.

They even tried once to get him into a game of darts, but it was soon clear that Russ Snape had inherited little or none of Toby Snape's instinctive skill, so they left him, for the most part, to his more academic pursuits.

Only Mrs.~Hanson treated him with the familiarity that one expects from close friends. She had the right, certainly, since she'd sheltered him many times when, as a boy, he'd needed protection from his father's rage, or just to give his parents time to be alone. Whenever they met in the market, she'd ramble on about her sister's family and her arthritis. Snape visited her once or twice for tea. He'd always thought of her as old, but really she was only about sixty now, and just ten or eleven years older than his mother would have been had she still been alive.

August came all too soon, and Snape let the neighbors know that he'd be gone for the school year, so they wouldn't think it odd that the house stood empty. They agreed that it would be nice if he managed to make it back for a few days at Christmas and Easter, and then it was the first of August, and he was walking out into his own back area yard with his Gladstone bag and a large parcel of books, sheltered from view by the brick wall and the gate, and apparating back to Hogwarts.

It was the longest Snape had spent in his own home since he'd graduated from Hogwarts four years earlier.

Hogsmeade appeared just as quiet when Snape arrived on the edge of the town. He was walking calmly down the empty street past the Hog's Head when an all-too-familiar voice made him spin around in sudden panic, expecting an ambush.

"There you are, right on time. I see Albus has you well trained already." Moody's scarred face and disconcerting eye leered at Snape from the alley next to the inn.

"You're not supposed to talk to me," said Snape, noting with some relief that Moody seemed to be alone.

"That order's expired. I can have a nice conversation with an old acquaintance in a public street now any time I like just as long as Judge Bones isn't shocked by my behavior. I've just come to let you know I still take a keen interest in your welfare, and that there's a place up north reserved with your name on it in case you decide to finally pay your debts."

"You can't threaten me."

"No? Think of it as advice. I'm watching. I'm waiting for you to make a mistake. The papers are all ready—just need a date and a signature." Moody advanced slowly until their faces were inches apart. "So you just keep your nose clean and your toes on the right side of the line, because you never know where I'll be or who on the street is working for me."

With that Moody backed away far enough so that he could apparate out, but near enough so that the percussion of his apparation pushed Severus back a couple of inches. When he was certain Moody was gone, Severus continued to the Hogwarts gate, wondering if he should tell Dumbledore what had just happened.

Many of the teachers were already in their rooms beginning to sort things out. They would all get together at breakfast for the welcome back and first staff meeting of the season. Snape decided that before anything he would go up and tell Dumbledore about Moody, mainly because he thought Dumbledore would want to know, Moody being a friend of his.

As he approached the spiral staircase to the headmaster's office, Professor McGonagall came down. She had a pinched I've-just-been-eating-lemons look on her face—more than usual—that made Snape quickly get out of her way. She glared at him as she flounced past, muttering "At least you knew something about potions!" and swept down the stairs to her own rooms.

Somewhat taken aback by the curtness of McGonagall's manner, Snape made his way up the stairs to Dumbledore's office. "Come in, Severus. Come in." Dumbledore called to him from across the room. "I trust the break was pleasant for you."

"Good morning, Headmaster. I{\el} Have I done something to upset Professor McGonagall? She seemed abrupt with me."

"With you? No, no, no. With me. Do not worry. You shall hear all about it, and in spades, at breakfast. I just hope Minerva has calmed down enough by then to let us attend to other business as well."

"Well, that's good, then{\el}" Snape caught himself. "No, it isn't good—it's unfortunate. I just meant that it's good for me that it isn't me{\el} That I'm not responsible."

"Do not apologize. It is, in fact, very good for you that you are not involved. You should try to stay that way. Did you wish to talk to me about something, or is this just a social call?"

"Yes. I mean, no. I mean, I did want to tell you something, it wasn't just a social call. I just bumped into Mr.~Moody. Not really bump, of course. We just met in Hogsmeade."

Dumbledore smiled as if gently amused by Snape's awkwardness. "What did Alastor have to say to you?"

"He wanted to remind me to stay out of trouble because I'm still on probation, he's watching, and Azkaban's waiting."

"He should not be doing that." Dumbledore was serious at once. "I shall speak with him and, if necessary, with Judge Bones."

"I don't want to cause trouble."

"I do not want you to have trouble. Thank you for bringing this to my attention."

Snape went to unlock his rooms and survey them for a bit, but he didn't immediately throw himself into doing things. He'd done so much the previous year, which he'd kept good records of, that much of his work was already done. Now he wanted to take his time, think carefully, and fine tune it.

Breakfast was better than he'd expected. During the school year, the teachers ate strung out along the high table, and many of them commuted to their homes in the evenings and on weekends, so they seldom had a chance to really talk to each other. August was the truly collegial time for the staff, when they sat around a lower table and talked without having to worry about the students.

Sprout was bubbling about Brazil, and Flitwick about Nubia. Sinistra had gone to the twenty-four hour darkness of the South Polar Plateau and the Amundsen-Scott Station to observe the stars of the Southern Hemisphere. Trelawney, with admirable restraint, simply `could not describe' her encounters with a renowned selection of medieval mystics, all deceased, while Dawson had taken up archery at the age of fifty-seven.

The better part of breakfast was passed in chitchat, and then Dumbledore called them to order. After the usual administrative announcements, he came to what Snape quickly realized was the crux of the matter.

"We have also," Dumbledore pronounced with some pleasure, "acquired a new Defense against the Dark Arts teacher. This is a lady of quite considerable qualifications whom I approached a couple of years ago, but who at that time was unable to accept because of the now recently ended `troubles.' She was, in fact, targeted by Voldemort for her knowledge and expertise, and has spent the last few years overseas{\el}"

There was a general gasp around the table. "You don't mean{\el} ?" cried Madam Pince.

"I do mean, ladies and gentlemen, that well-known author, scholar and adventurer, Val Carmichael."

Snape's eyes widened at that, for he knew the works of Dr. Carmichael. A muggle-born witch, she was famous in both worlds not only for her adventures (and her five husbands), but also for her academic merit, for she was a student of anthropology as well as of the development of primitive magic, and was considered one of the world experts on voodoo. Snape had read several of her works, though he owned none of them, and had found them well-researched and valuable.

This was clearly, however, the news that had upset McGonagall, for she remained frozen in her seat, an expression of great displeasure on her face.

Dr. Carmichael arrived on Sunday the fifteenth, intending to be a resident teacher ('Until the divorce is final, of course. Silly American laws. You'd think all fifty states would be the same, but no. If I'd been married in California, I wouldn't have to worry about this year of separation business.') Her entrance onto the Hogwarts stage was so eagerly anticipated that almost the whole staff stayed for supper that evening, and the reception afterwards, just to meet her.

Snape was shocked when he walked into the Great Hall. It was almost as packed as at the start of term banquet. This time, however, the seats were full of Ministry types, reporters, influential rich people, and members of the wizard publishing trade. The return of Val Carmichael to Britain was quite an event.

The staff, in fact, was relegated to the lower tables, in McGonagall's case by choice. From somewhere in the center of the hall, Snape regarded Hogwarts's newest celebrity. It was impressive and amusing at the same time.

Val Carmichael had clearly once been a very handsome woman. She was tall and athletically built, even muscular, but the deep tans of her youth had prematurely aged her skin, and there was a vague mummy-like quality to the leathery folds of her face. If she had left it there, it would have added character. Her attempts to defy aging had led her, however, to dye her hair a garish red, and to bury her wrinkles and creases under makeup. She dressed in clothes a hair too tight, and heels a centimeter too high. Her fingernails were sharp, clawlike, and scarlet, while her fingers were adorned with a variety of rings. She was almost a caricature of what she might have been.

During the reception following supper, Dumbledore pulled Snape over to introduce him in what must have been a long and boring line of Hogwarts teachers. Dr. Carmichael's acknowledgment was not routine.

"Well, I had begun to think Hogwarts was the male geriatric clinic of Northern Britain. I see I was mistaken. You must be the youngest teacher here."

"I was hired just last year to replace the retiring Potions professor."

"I love potions. I did a book on aphrodisiacs and other love potions. Not that I ever needed them. I must say it was a stroke of luck that other professor decided to retire."

Snape murmured an inaudible response and made way for Professor Vector, moving quickly himself to the outer areas of the Hall, where the refreshments were greater but the crowd less.

"What do you think?" Sprout gushed beside him. "Isn't it wonderful!"

"I don't know," said Snape. "She seemed a bit, well, over the top."

"Well of course, idiot. She's lived in America. She's a celebrity. That's what they're all like."

The clock ticked toward midnight, and the gathering thinned. All the aliens, from the Ministry, the media, and the mob, gradually left. Dr. Carmichael had been the sensation of the year, working the crowd like the professional she was, talking to everyone, stroking everyone.

"I need," she breathed in Snape's ear at about a quarter to midnight, "to get to know my colleagues better. I understand you are the absolute master of the dungeons. I love dungeons. All that writhing and screaming. Doesn't it keep you awake at night{\el} wondering{\el} longing{\el} ?"

"Good evening, Valeria dear," said McGonagall from Snape's elbow. "So sorry I didn't have a chance to welcome you earlier. You've met Professor Snape, of course. He was a bit after your time, though I believe you did share a year or two at Hogwarts with his mother. You do remember Eileen Prince? She'd have been right about the same time as you."

"Professor McGonagall. One of my best-remembered teachers. It's so good to see you've managed to hang on here. I suppose seniority can be a treasured commodity. You must be very proud of the niche you've carved out for yourself here at Hogwarts."

"I can treasure the fact that I, at least, have benefited the lives of those with whom I have come in contact. Self esteem. I am sure you join me in pitying those who do not have it."

"I was just suggesting to Professor Snape here that he might show me around the castle."

"And I was just about to see that he was able to relax from the tedium of the evening by being able to go to his quarters, alone, to get a good night's sleep. I'd be more than happy to show you to your own rooms, in case you'd forgotten the way."

"I'm still far too young for forgetfulness to hamper my lifestyle, though I can see why you might be concerned about its appearance in your contemporaries. I think I can{\el} get to bed on my own."

"See that you do, dear."

"Good night, Minerva."

"Good night, Valeria."

The entire encounter left Snape with a deep desire to set out saucers of milk for the night.

They had brunch the next day instead of breakfast, so many of the staff needing to sleep in from the late hours of the night before. Snape rather thought that he might be the first, but McGonagall was there before him. "Severus," she waved from the table, "come over here and join me. We need to decide on the Quidditch schedule. Last year was a bit unusual." Within five minutes, the heads of houses were all together at the deputy headmistress's end of the table, Snape at the corner on McGonagall's left, Flitwick on her right and Sprout, at McGonagall's insistence, next to Snape on the other side.

"Last year," McGonagall said, "we had to rearrange the Quidditch schedule due to{\el} well, you know{\el} and this year we need to decide whether to keep it that way or return it to the way it was before. I tend to think we should go back to the traditional schedule, but it is something requiring the consensus of the heads."

"I rather liked the Gryffindor—Slytherin match at the end," Sprout said. "It made things more exciting, more rivalry during the year."

"Because we dislike each other so much?" Snape asked cynically.

"Of course, dear," replied Sprout. "There's nothing like good, old-fashioned, I'm-going-to-kick-your-face-in hatred to spice up a Quidditch game."

Snape glanced to his right, but McGonagall wasn't listening. She had turned and was watching the entrance, a small smirk of triumph on her face. Following her gaze, Snape saw that Dr. Carmichael had entered the Hall. Her gaze went right to the group at the table's foot, and she seemed displeased. After a moment's hesitation, she came over to them. "Good morning. I take it this is the scintillating end of the table?"

"Good morning, Valeria," replied McGonagall. "I regret to say that this is the dull, house business end of the table. You might find conversation more to your liking with Albus, or some of the others. There's plenty of room along the table."

"But I love house business," said Carmichael, glancing pointedly at Sprout as if expecting her to slide over and make room for the newcomer on the bench. When Sprout didn't move, Carmichael went to the other side of the table to swing her legs over the bench and sit by Flitwick. It was McGonagall's turn to look displeased.

"We really do need to be informal," Carmichael gushed. "I want all of you to call me Val. That's what my friends do. I already know Minerva. You're{\el} ?"

"Pomona," said Sprout, a little waspishly, which Snape didn't quite understand since Sprout was usually so cheerful.

Carmichael looked to her right, and Flitwick replied, "Filius."

"Let me just jot this down in my notebook," said Carmichael, pulling a small spiral pad and a ball-point pen from her robes. "I swear sometimes, my head is like a sieve when it comes to names." Then she stretched her hand across the table so the tips of her fingernails were almost touching Snape's hand. "And you, the baby of the staff, what's your name, dear?"

"Severus."

"How sweet. I'm still looking forward to you showing me around the place." Snape noted that she did not jot his name down in her pad.

"I'm afraid that will have to wait," McGonagall said crisply. "Professor Snape and I need to go over the texts and coordinate our curriculum this morning. And I'm sure you'll want to work in your classroom and office. The last Dark Arts teacher left in the middle of the year, and you have quite a bit of work to do."

This took Snape by surprise, since McGonagall had never mentioned coordinating curriculum before, but Flitwick was acting as if it was perfectly normal, a tiny gleam of amusement in his eyes, while Sprout nodded affirmingly.

"Maybe later, then, Sevvy dear. We have the whole year ahead of us. Oh! There's Albus. Excuse me, I did want to ask him something." Carmichael was up off the bench and heading for the opposite end of the table before any of the other four could respond. They all turned to Snape.

"That woman," said Sprout solemnly, "is a barracuda. She's marked her prey, and she's circling in the water."

"Yes," said Flitwick. "I remembered last night. She's the former Valeria Aurifosser, isn't she, Minerva?" When McGonagall nodded grimly, Flitwick smiled at Snape. "She collects trophies. She had quite a string here at Hogwarts by her seventh year."

"You'd better be careful," said Sprout, "if you don't want your head on the wall."

"Wait a minute," said Snape, suddenly realizing what they were talking about. "She's old enough to be my mother!"

"I never knew that to stop her before," said McGonagall quietly.

Snape managed to get a quiet word in with Sprout before going up to McGonagall's office. "Is it my imagination, or is there something more between that woman and Professor McGonagall?"

"It isn't your imagination. They clearly hate each other. But I haven't a clue what it's about. Maybe Filius will know. Are you going to let her get away with calling you Sevvy?"

"What am I supposed to say? She's old enough to be my mother, and famous into the bargain. I can't just tell her not to use a nickname."

"She starts calling me Pommy or Mona and I'll tell her fast enough."

Upstairs in McGonagall's office, Snape got a bit more information as well as a lot of advice.

"What Filius said about trophies is true. Her affairs are legendary, as is her callousness when she decides it's over. "

"It sounded like she's about to divorce her fifth husband."

"Dear boy, she marries only the rich ones. I heard once that she'd bragged of making a conquest for every place she'd worked and every place she'd visited. I don't know if it's true, but I wouldn't be surprised. And she prefers them young. It's a bit like a game, a hunt. Your bad luck is that you're the only man here younger than she is."

"I could stay away from her."

"Will she stay away from you? Pomona, Filius, and I will help all we can, but it's going to be a long year."

Flitwick was a little more forthcoming. "She had quite the reputation in school for ruthlessness and vindictiveness. I always felt sorry for the young men she got her claws into. One in particular happened long after she left the school. She was twenty-three and already had her first husband, but she targeted a student who'd just turned eighteen, and he ended up dropping out of Hogwarts for her. There was quite a scandal, hushed up of course, but it ruined his chances for a career with the Ministry. Took the family years to recover."

"Is that why Professor McGonagall dislikes her so much, because she wrecked the life of one of her students?"

Flitwick looked embarrassed. "Listen, Severus, I would never breathe a word of this as gossip, but it looks like you're on her menu now, too, so you need to know exactly what you're up against. That young man{\el} was Professor McGonagall's son."

"Why then would Professor Dumbledore hire her? Surely he knows about it?" Then Snape remembered the first of August, and McGonagall's anger as she left Dumbledore's office. \emph{No wonder she was upset. How could Dumbledore have done this?}

Now Snape wanted more than ever to have nothing to do with Val Carmichael.

"So this is your little hideaway. How cozy! And so very private."

Snape looked up from his desk at the sound of Carmichael's voice, and immediately rose. "I'm sorry," he said, "I'm rather busy at the moment preparing the inventories for the things we just got in."

"Tut-tut, Sevvy dear. All work and no play can make Jack a very dull boy indeed. Come on, now. You have to give me the tour of the grounds. I need to refresh my memory of the place."

It occurred to Snape at that moment that they were isolated down in the dungeons and that Carmichael was blocking the door. And that she was bigger than he was. "You're right," he said, "now would be an excellent time, before the students arrive in September. If you'll wait for me in the entrance hall, I can be with you in five minutes."

She would clearly rather have gone to the entrance hall with Snape, but it was hard to refuse his request without being rude. Carmichael wiggled her fingers in goodbye. "See you in five minutes, then."

Quickly clearing the papers from his desk and locking the drawers, Snape followed, being sure to lock the office door securely as well. He jumped as he heard Carmichael's voice again.

"Whatever do you have to seal the place like that for? It's not like there are students here."

"Potions," Snape explained. "Some of what's in there is poisonous."

Carmichael nodded in understanding, and they made their way to the entrance hall and out onto the lawn.

It was actually a rather pleasant afternoon. Dr. Carmichael had both studied and traveled widely, and had a lot of interesting observations. It was clear that her knowledge of dark arts was extensive, and she might very well be an excellent teacher. She did, however, have a disconcerting habit of reaching out and touching him—his arm, his shoulder—that Snape didn't like, but he wasn't certain how to get her to stop it.

They saw the Willow, the forest, Hagrid's hut and then, at Carmichael's request, the grotto under the cliff where the boats docked with the first years. They went down to the boats from the top of the cliff, since Snape did not want to take her by Lily's rock. In the dark, narrow cavern she brushed against him once, only once, so he wasn't sure if it was intentional or accidental. Snape was beginning to get nervous, but then they were back in the sunshine.

Stables, hospital wing, library, it was a fairly full tour, and when it was over she thanked him very politely and went her way upstairs to her own rooms, leaving Snape wondering if she was really as dangerous as he'd been led to believe.

\subsection{Wednesday, September 1, 1982 (2 days before the full moon)}

Snape stood out on the lawn in the cool air of a September evening, the first in the month, and watched the rim of the moon peek over the low mountains. The day before the first day of a full moon cycle, almost werewolf time, and the arrival of a new group of first years. The thestral carriages had already left for the train station, and Snape was waiting for the sound of the incoming train whistle from across the lake as the Hogwarts Express pulled in from London.

Dumbledore stopped beside him. "Penny for your thoughts?" he said.

"I was just recalling a certain student who wouldn't have been able to come in on the train tomorrow night if he were starting now instead of eleven years ago. Have you ever tried that experiment since?"

"I have not yet had occasion to."

"You know, if you always had the train come in during a full moon cycle, you would always be sure there was no werewolf at Hogwarts. At least not at the beginning of the year."

"Interesting thought, Severus. And if I nailed up crucifixes and garlic, and insisted the train arrive before sunset, I would be certain there were no vampires."

"I stand rebuked and mocked," Snape sighed.

"Do not take it so to heart. It is only the mediocre who are never mocked, and the spiritless who are never rebuked."

"You are too kind, sir. What brings you out here on the first day, anyway? You weren't here last year."

"Tonight I anticipate the arrival of the eldest son of an old friend of mine. The boy's name is Bill. Bill Weasley."

"I'm not familiar with the name."

"You should be, though his parents were before your time. His father is Arthur Weasley, an employee of the Ministry, the one who managed to `weasel' his way into your cell block and then inform me that you'd been arrested back last Easter."

"Ah!" said Snape. "I shall keep that in mind."

"You are under no circumstances to treat the boy any differently than you would if he were not connected to you in any way."

"Yes, sir. No, sir."

Later, shepherding the students in from the thestral carriages, greeting students that he happened to come face to face with, and generally maintaining order, Snape noticed that Dr. Carmichael wasn't there. \emph{Pity. I'd have liked to find out if she can see the thestrals. Maybe no one warned her this was part of her job.}

When he entered the Hall, Snape was in for a shock, for Dr. Carmichael was sitting in what was supposed to be Kettleburn's chair which, since Snape sat at the end of the high table, made her his only dinner partner. Kettleburn, on her other side, raised his eyebrows in mock horror while she wasn't looking.

Trouble started even before the Hall settled or the first years entered for the Sorting, for Carmichael was definitely pressing her leg against his. After momentary panic, Snape rose, said, "Excuse me, Professor, I fear I am crowding you," and moved his chair six inches to the right. It allowed him to watch the Sorting in peace.

He didn't follow the Sorting as closely as the previous year, primarily interested in the student Dumbledore was interested in. As the list went through the alphabet and the number of unsorted students diminished, Snape began to wonder if it wasn't a tall, gangling redhead who, though quiet, seemed more confident of himself than most of the other eleven-year-olds. Sure enough, that year there were no Xes, Ys, or Zs, and the last name called was `Weasley, Bill.' The Hat cried, "Gryffindor!" and the Sorting was over.

Dumbledore then rose to welcome the students back to Hogwarts, and to introduce the new Professor, Dr. Carmichael. Val Carmichael was known by name to many of the students, and she got a warm round of applause. And then the feast began.

That was when the second stage started, for the tables were suddenly loaded with food. Carmichael observed the wide array of entrees and side dishes, and stage whispered, "They don't expect us to eat this, do they? Whatever is it?"

Snape looked around at the food. "It's the normal feast. The house-elves do somewhat lay it on, but it's all very good."

"I don't think so. What happened to the normal food we've been eating? The roast beef and roast chicken? The potatoes and Yorkshire pudding?"

"But when you were traveling all over the world, didn't you try new, exotic foods from different countries?"

"And end up with food poisoning? Or worse? Child, you have no idea of the bacteria and the bacilli, not to mention the viruses, running around in strange places and on strange food. You take your life in your hands every time you pick up a fork. Roast beef for me. Yorkshire pudding. You can't go wrong. What's that?"

The dish contained soft pieces of flesh in a savory sauce that was quite good. Snape had tried it once before. "I think it's sweetbreads."

"Sweetbreads! It's a gland! It's a calf's thymus gland. And if they ever serve you `fries' in the States, it's usually potatoes, but sometimes it's testicles. Now I have a great fondness for `fries,' but I'm not about to eat them. And those things. What are those?"

His face flaming scarlet, Snape struggled to explain. As he did, she leaned closer, and he felt her leg press against his once more. "Uh, scallops. I think they're called scallops. And those are shrimps."

"Sea vermin. I have never eaten a piece of sea vermin, and I never will. Stop fidgeting, boy." Her foot was now trying to wrap around his. "What's in this dish?"

"It's a paté, made from goose or chicken livers, I think{\el}"

"Organ meat! Where I come from we throw this in the garbage where it belongs. You know, I've traveled among tribes that tried to feed me snakes and locusts. And larvae! And brains! And I always fooled them. I always brought my own food and managed to magic it in. You can't even trust what's in sausages. I'll eat bacon, and roast pork and ham, a leg of lamb from time to time, but it's mostly roast beef and a chicken or two with me. None of those fancy foreign sauces."

Snape managed with some difficulty to unwind his leg from hers. "I hope you will excuse me," he said. "I am the head of a house, and I do have to greet my prefects, and my Quidditch team, and the other students. Please. Excuse me. I'll be right back."

The Slytherin students were happy to see him, and they appreciated his attention. As he made his way down the table, a little group of girls pulled him aside.

"We thought you could use some advice, Professor. About the situation."

"What situation?"

They glanced at each other. "Well," one ventured. "When a boy tries that with me, with the leg and everything, well I just find a way to `accidentally' step on his foot."

Snape looked up at the high table and realized the whole under-the-table business was clearly visible to all the students at the Slytherin table. He turned back to the girls. "How do you keep him from getting mad at you?"

"Sometimes you can't, but if you apologize enough, he can't say anything."

"Look, she can get me in real trouble." They, knowing his Death Eater past, nodded wisely. "She can't know that you know, and she can't be embarrassed."

The girls reassured him. "The whole table is mum, sir. We don't see anything."

Returning to his seat, Snape tried to steer the conversation away from unusual food. He himself took the plainest, most basic dishes there were, all three of them. Within minutes Carmichael's leg and ankle were working again.

"Look at that!" Snape said to her. "They may be starting a fight." He turned toward the Slytherin table, and as he turned his foot turned, his left heel coming down hard on her right big toe.

"You idiot!" Carmichael gasped.

"I am sorry, I am so sorry," Snape exclaimed. "I can't believe{\el} I am so mortified{\el} Please, do you want me to call Madam Pomfrey."

"I'll be fine," Carmichael hissed, and a few minutes later found a reason to speak to Professor Dumbledore, leaving Snape alone at the end of the table.

Snape looked over at the Slytherin table. A hefty percentage of the students had managed to get something stuck between their teeth, for they all had their faces buried in their table napkins. Severus flashed a `thumbs up' to the girls, and they responded in kind.

The feast ended without further incident, and all made it safely to their beds.

The next morning, Minerva McGonagall was making absolutely no headway with Maximilian Kettleburn at all. "I don't see why you can't make a small effort to be at meals on time so that you can sit in your usual place."

"And since I'm not a head of house, I don't see why it makes any difference where I sit." Kettleburn was, in fact, early in to breakfast since he'd spent the night at Hogwarts to make sure everything was going well for his first lessons, some of his instructional materials having minds of their own. The two were sitting in an otherwise empty Great Hall.

"If you prefer not helping a colleague in a difficult situation{\el}"

"Severus? He can take care of himself. And if he can't it's time he learned. He was doing pretty well last night."

"He has less experience with this sort of thing{\el}"

"He's twenty-two, Minerva. If he doesn't know yet how to escape the unwanted attentions of an older woman, it's about time he learned. And he'll only learn by doing. Don't wrap this one in cotton."

"It's just that I believe this to be more than simple flirting. The woman has a reputation{\el}"

Kettleburn began to laugh. "Well good for Severus! There are young men who'd give their eyeteeth to be trained up by an expert with no strings attached. He's not getting any younger, you know."

The innocent subject of their conversation walked into the Hall, which was now beginning to fill. McGonagall waved to him. "Severus! Come sit by me. We have business to discuss. And you, sir," she added, turning back to Kettleburn, "may take your crude ideas to your end of the table. Trained up indeed!"

His eyes twinkling merrily, Kettleburn rose to give his seat to Snape. As the younger man approached, Kettleburn leaned forward with a conspiratorial air. "As long as they're giving it away, lad, there's no harm in taking a free sample." Then he strode, still laughing, to the end of the high table.

"What was that all about?" Snape asked McGonagall.

"Best you not know, dear. Sit down."

By the time Carmichael made it down to the Hall, Snape was well protected on both sides, and she had to make do with Kettleburn's company. She kept her eyes on the center of the table, and they were filled with a cold calculation. It wasn't Snape she was watching, however. It was McGonagall.

When breakfast was over, and the students filing off to their houses for the opening talks and orientation, Carmichael managed to be beside McGonagall leaving the hall. "They're like birds," she said.

"I beg your pardon," McGonagall responded, puzzled.

"The harder you try to hold on to them, the more they struggle to be free. Hold too tight, and you kill them. I thought you'd learned that already."

"I have no idea what you're talking about."

"I think you do." With that, Carmichael swept from the Hall, up the stairs to her rooms.

McGonagall sought out Dumbledore, not waiting to get to his office before starting.

"You have to do something about that woman, Albus. She's up to her old tricks."

"And what tricks would those be, Minerva?" Dumbledore was patient, but only somewhat sympathetic.

"She's trying to get her claws into that poor innocent young boy{\el}"

"Last year he was that evil Death Eater who was going to bring Voldemort back."

"That was before. Now I know him better. You have to get rid of her for his sake. She'll ruin him."

By this time they were in the office. Dumbledore offered McGonagall a seat and sat himself at his desk. "Minerva, forgive me for being blunt, but we have had a similar conversation already. This time I believe that you are using Severus as a tool to attack Dr. Carmichael with. It is true that she has a somewhat overly physical lifestyle, but he is no child. He is an adult, and has been one for some years. He does not need my protection in this matter. Besides, I have seen no indication that he is even remotely attracted to her, and there is thus no problem."

"She is an evil, wicked woman who preys on{\el}"

"Minerva," said Dumbledore gently, "have you considered the possibility that in trying to atone for mistakes you made in the past, you are in fact about to repeat them?"

"Are you telling me, Albus, that you consider me responsible for what that woman did? She should have gone to jail for what she did, a woman of her age and a mere boy! And now she's after another boy who doesn't have the experience to see{\el}"

"May I remind you that she was, that other time, merely a year older than Severus is now."

"You can count age in more ways than by years! In terms of hardness and experience, the last time she was Severus's age she was thirteen."

"Now Minerva, you did not start teaching here until she was in her seventh year."

"I did the research twenty years ago. I know what happened. She should have gone to jail."

"But you cannot get around the fact that Severus is an adult. As Marcellus was an adult. They have and had the right to control their own lives. Holding a teenage boy is a little like holding a bird. Too tight{\el}"

"You're on her side, aren't you?" McGonagall screeched, springing from her seat in taut anger. "You've been conferring with her on how to dupe me! Well I won't let you! There is such a thing as justice, and justice is finally going to be done!" With that McGonagall stormed out of Dumbledore's office in a rage.

Snape gave his Start of Term speech, which was well received, in the common room. He talked about Slytherin's responsibility to the wizarding world to show you couldn't label a whole group of people because of the actions of a few, and that adherence to the rules was not only protection, but an actual weapon against the malice of enemies. He'd spoken of the possibility of winning the Quidditch Cup and the importance of the tryouts, and of the House Cup and the advantages Slytherin had both in terms of discipline and academic achievement.

"Doesn't Ravenclaw outdo us on both?" called a voice from the back.

"Yes," Snape answered. "But now we beat them in Quidditch. If we can match them in discipline and academics, we have a chance at the House Cup for the first time in more than five years."

"You mean we won the House Cup when you were a student?" cried someone on the side.

"Once or twice. But we had a particularly cooperative group of Gryffindors who were always losing points for their house. You can't count on that now. You have to do it yourselves."

Tryout days for Quidditch were announced, along with preliminary plans for in-house tutoring and Death Eater family support groups.

Snape went to his office to go over the last of the files of those students newly sorted into his house. He'd start the interviews in the afternoon.

Lunch was made less tense by the fact that McGonagall was not there. In addition, Dr. Carmichael seemed to have decided to leave Snape alone, for she sat further down the table talking with Professor Futhark. This did mean that she was facing Snape the whole time, and he had the distinct impression she was observing him, but it was better than playing footsie.

For the next two days, Snape had no contact with Carmichael at all, and on Sunday she merely asked him a question about the Dark Arts curriculum, an easy question that he knew the answer to and enjoyed talking about, though he rather had the feeling that she had already known the answer as well.

Gradually, over the next few weeks, Carmichael found more occasions to talk to Snape, and the conversations became longer and more involved. Snape found himself enjoying her company, even looking forward to it. There was no one else at Hogwarts he could talk to about the Dark Arts, and her knowledge was a gold mine.

Sprout and Flitwick relaxed their guard, certain that Carmichael realized now how unwanted her earlier attentions had been. Carmichael even found reasons to seek their advice, and had more than one long chat with Sprout about dangerous and poisonous plants, and with Flitwick about the nature of hexes and jinxes.

This new, more professional relationship with Dr. Carmichael seemed to bother Professor McGonagall even more than before, and she became irritable and withdrawn, her temper less under control, even shouting at her students during classes. She constantly warned Snape not to let down his guard, and had long meetings with Dumbledore that didn't seem to help at all.

September wore into October, and life at Hogwarts settled into a routine. Most of Snape's time was spent in his classes or in his office, but he was spending more time at meals in the Great Hall or in the staff room in the evening than he had the previous year. Hagrid was pleased because Snape was eating. Flitwick was pleased because it meant more card games. Even McGonagall accepted the arrangement since while Snape was talking to Carmichael in the staffroom, McGonagall could keep an eye on them. The world seemed a calm and pleasant place.

\subsection{Saturday, October 23, 1982 (2 days before the first quarter)}

The first Hogsmeade excursion of the year was the Saturday a week before Halloween. They had brunch instead of breakfast and lunch that day so that the students who could go into Hogsmeade would be ready and able to leave around noon (and so they would be inclined to buy more in the village).

For the first time since the beginning of the term, Dr. Carmichael sat next to Snape at brunch. Once again she was commenting on the food.

"What in the world is that disgusting mess?"

"Stewed kidneys. They're part of the old, traditional English breakfast. Or what they used to call a hunt breakfast. At least that's what I understand. We never had them for breakfast at home." Snape's mother had cooked kidneys from time to time because they were cheaper, and steak and kidney pie was frequently served as pub food where he lived, but he didn't tell Dr. Carmichael that.

"Organ meat. How can you eat it? Do you know what kidneys do while they're alive?"

"Doesn't bother me a bit. They have a strong taste, and you do have to prepare them properly so they're not too strong, but I like them. I wouldn't recommend them to you, though. I don't think you'd like them at all."

"I'll make a deal with you. I'll try the kidneys if you'll take tea with me in Hogsmeade."

Snape thought about this for a moment. Hogsmeade would be crowded, so it would be impossible for anything serious to occur. "All right," he said. "You have a deal."

Taking a teaspoon, Dr. Carmichael filled half of it with a tiny bit of kidney and a little sauce, grimaced, and put it into her mouth. After a thoughtful pause, she said, "It's milder than I thought it would be."

"That's because they were cut up properly before they were cooked."

"How do you know that?"

"My mum used to make them. The house-elves here do a good job."

Carmichael had a few more bites of the dish to prove she really did like it, then rose, saying as she left, "I'll see you in Hogsmeade around tea time. At the Three Broomsticks."

Snape went at once to the Three Broomsticks, since it was a place from whose windows he could conveniently keep an eye on the largest number of students at once. He'd hardly sat down when he was joined at the table by Alastor Moody.

"Thought I might find you out here today. Lovely day, isn't it? We've missed you in London." Moody greeted him heartily.

"I'm afraid you're going to have to go on missing me. I haven't done anything wrong."

"I can keep hoping. How's the new professor doing?"

"Well enough. She has a good grasp of the subject, and the students are in awe of her."

"I hear she's a man hunter and a cradle robber. Is she working on getting you into trouble?"

"No."

"Pity. I could use the help. I'm not letting that little room up north go to waste. There's things that have to be paid for and a person who has to pay. It's just a matter of time."

"Mr.~Moody, I understand that you consider me responsible for certain things that have gone wrong in your life, but I assure you that I never intended to cause harm, and certainly not to you."

"And yet look what happened. Somebody helped them out. Somebody's paying." With that, Moody rose and left the room, calling out, "See you in December," just before he disappeared through the door.

Snape sat quietly for a long time, staring out the window at the students with their bags of sweets, toys from the joke shop, new robes, and wondered how life could be so carefree for some and not for others. He couldn't remember any time when his world had been like that.

"You're pensive," said Carmichael as she settled into the chair opposite him. "Penny for your thoughts."

"I was envying their ability to relax and enjoy themselves."

"You need to regress, return to your youth—or in your case, your school days—pretend you're fifteen again."

"That wouldn't work. It might make things worse."

"Then get away from here now and again. I notice you don't take your nights off. Isn't there some young lady you're courting who can help you relax and forget this place for a few hours?"

Snape reddened and looked down at his hands.

"You've got to learn to control that. No sooner do I bring up sex but you blush like a girl. It gives you away every time." Carmichael leaned across the table and patted Snape's hand maternally. "Don't worry, I won't tell your secret. But you've got to find a way to get past that, or each year it'll get worse. Now I know a few{\el}"

"I'd rather not talk about this," said Snape suddenly, and stood to leave, but her chair blocked his way.

"You promised to have tea with me. I'll drop the subject and we'll sit and talk about voodoo." Which is what they did until it was time to return to the castle.

After the Hogsmeade gates had closed on the last of the students trudging up the hill to the castle, Snape went directly to Hagrid.

"How is it I can close my mind off to the Dark Lord and Dumbledore, but people like her know what I'm thinking? I don't want her to know the intimate details of my life, but she does! She doesn't need legilimency, she knows! And not just her. Everybody knows!"

"Can't say as I know, so it can't be everybody. What kinds of things do all these people know about ya?" Hagrid was boiling something in a huge cauldron, probably laundry, and had his back to Snape.

"In school—they could always tell when I was scared, Rabastan, Sirius, it didn't matter. They could always tell, and they knew when to jump me."

"And this `her' y're on about, that's riled ya. That wouldn't be Professor Carmichael now, would it?"

"See? Even you can do it. What good is occlumency if everyone knows what you're thinking? I may as well hang up a sign—Open brain. Feel free to walk around as much as you like."

"What does Professor Carmichael read in ya? If ya don't mind?"

Snape hesitated, but if anyone would lend a sympathetic ear, it would be Hagrid. "Every now and again she brings up the subject of{\el} well{\el} sex. And she knows that I{\el} haven't." Hagrid was silent, kept his face carefully averted, and waited for Snape to continue. "This afternoon she told me I blushed like a girl."

"Ya do tend t' get a mite flustered when the subject comes up," Hagrid observed. When Snape's only reply was a sigh, Hagrid went on. "They ain't reading yer thoughts, lad. They're reading yer feelings. And it ain't coming out through yer brain, it's coming out through yer body. It's blushing, and looking away, and the sudden sharp way ya glance for the exits. Yer body speaks a language. Fang can read it easy. So can the thestrals. I bet You-Know-Who couldn't read it at all."

"Is there any way to control my body's language? I really don't want the whole world to know about my personal life." Or lack of it.

"Practice, I suppose. If y're used enough to a subject, bringing it up in conversation won't make ya blush. If ya know yer eyes give ya away when y're scared, ya can control what ya look at."

"I don't understand."

It was Hagrid's turn to sigh. He pulled over a stool and sat facing Snape, black eyes to black eyes. "I been caring for yer scrawny little carcass since ya was nigh thirteen, diet and rickets and bad teeth, and you ain't never realized what a friend it is. Ya need t' move, it runs. Ya need t' climb, it climbs. It's a better weapon than a wand, and ya ain't never learned how t' use it 'cept to roll out of the way when someone aims a curse at ya. Ya want t' learn not t' blush? It's easy. Whatever embarrasses ya{\el} study it. Learn every twist and turn of it. Get so ya can explain it all in loving detail, and when someone starts talking t' ya, ya won't care. It'll be old hat. Yer eyes go t' exits when y're scared. Check the way out every time ya enter a room so when trouble stirs ya already know which way y're jumping. Then turn t' ice and stare them down."

Snape had never before thought of training himself physically—the same way he might train a dog, or a horse—to conceal emotional responses as well as perform actions. He and Hagrid talked for a while, then Snape went to his own rooms to plan.

The following Thursday, Snape did take his day off. He went to his London bookstore to buy a book on sex and sexual customs. It was probably the most embarrassing book he'd ever read in his life, but it was invaluable. Sunday was Halloween, and by Halloween he'd read and reread enough so that he doubted if any casual remark could cause him any embarrassment at all.

\subsection{Halloween, Sunday, October 31, 1982 (the day before the full moon)}

The Halloween feast was set to begin at eight o'clock and last for two hours. The only other meal of the day was brunch, but an hors d'oeuvres table was set up at six. At the request of several of the teachers, who had enjoyed the welcoming feast, the six o'clock table concentrated on seafood.

Dr. Carmichael approached Snape. "The kidney experiment was relatively successful. Which of these little sea vermin should I try?"

"I'm not sure. I haven't eaten all of them. Those round things are scallops, and the curled pink ones are shrimps. The ones on the strange gray shells are oysters, and the ones in the narrow black shells are mussels."

"If you eat an oyster, I'll eat an oyster," said Carmichael. Snape agreed, though immediately after he swallowed his first oyster she whispered, "They're aphrodisiacs, you know."

\emph{Blest be Hagrid and blest be books}, thought Snape as the dictionary definition of `aphrodisiac' skidded across his brain. He picked up another. "They have that reputation, but it's more for shape and texture than any actual effect they have. The power of suggestion may be involved, however. I suppose if you thought Yorkshire pudding was an aphrodisiac, it would become one." He ate the second oyster.

Carmichael regarded Snape with narrowed eyes. "Are you sure you haven't kidnapped Professor Snape and insinuated yourself into his place cleverly disguised? Where's the sweet, innocent boy I had tea with last week?"

"Dr. Carmichael, I have been called some rather unpleasant names in my life, but you are the first person to have the temerity to use the words `sweet' and `innocent' to my face."

She laughed, but to Snape's great relief did not respond with more banter. He wasn't sure if he could think of anything else to say that wouldn't come out wrong. Instead Carmichael clapped him on the shoulder and said, "Round one to you, Sevvy. But I'm going to put your theory to the test. I'm going to eat a few more of these, and if you're wrong, I may be hunting for you later—for dessert." She turned away from him then and struck up a conversation with Professor Futhark.

McGonagall appeared at Snape's elbow. "Thank goodness you were able to keep your distance. You have to be careful about that woman, Severus. She'll probe for every crack in your armor, and just when you think you're well defended, she'll strike again."

"Please don't worry about me, Professor McGonagall. I'm really not attracted to her. She rather frightens me sometimes."

"Good boy. But just to be on the safe side, you probably shouldn't eat any more of those." She steered Snape away from the oysters.

The Great Hall was festooned with jack-o'-lanterns, black cats, skeletons, and bats. Most of them were purely decorative, but one or two real bats did have to be ejected from the party after they made nuisances of themselves.

Many of the students had purchased costumes in Hogsmeade the weekend before, which caused a bit of a problem since, after about half an hour, it became apparent that some of them were trying to infiltrate the tables of the other houses behind the anonymity of masks for the purpose of gathering information to be used as weapons later on. This only came to the attention of the staff when Gryffindor started the first round of `Hunt the Spy' and chased an unlucky Hufflepuff boy halfway around the Hall before his mates came to his rescue.

At that point, all four tables began a spy search, which quickly escalated to a food fight. The staff sprang to do its duty, with about as much success as one usually has with two hundred eighty teenagers at a party, while Dumbledore watched from the dais with a beatific smile on his face.

After savoring the chaos for all of five minutes, Dumbledore rose. "Enough!" he thundered, stopping the trajectory of mashed potatoes and gelatin salad in mid flight. "Everyone will kindly sit down and resume the feast, or there will be no dessert." The students obeyed, returning demurely to their benches as the teachers went back to the high table and Dumbledore removed the mess with a wave of his wand.

Snape got back to his chair to find that Dr. Carmichael had moved next to him. She patted the seat of his chair with her heavily ringed hand. "Come sit beside me, Sevvy." He had the impression she may have had a glass or two too many. He took his seat, afraid that if he refused she might cause a scene, and fairly sure of Kettleburn's support on her other side if she got too much out of line.

"I'm sorry if I offended you earlier, dear," Carmichael whispered, leaning towards Snape and slipping her arm into his. "But you really are a sweet boy, and I really would like to know you better. It must be such a strain for you, surrounded by all this temptation, forced to stay aloof, alone. I can help you, make it easier for you{\el}"

She had to be tipsy. Snape glanced over at Kettleburn, who was also looking worried. Just as Snape was thinking that the two of them should get Dr. Carmichael out of the Hall, McGonagall came and stood behind them.

"What do you think you're doing," she hissed quietly at Carmichael. "exhibiting your brazenness in front of the whole school? It's bad enough you behave like a hussy when the students aren't present, but on display like this?"

"Dear Minerva," replied Carmichael, turning slowly to face McGonagall, her voice also low so that the student tables couldn't hear, "there isn't a student here who doesn't do the same or worse behind the sofas in the common rooms after midnight. Believe me, they are not shocked."

"How dare you assume that these children are like you. Just because you were a wanton doesn't mean the rest of the world follows your example."

Snape, his arm firmly gripped by Carmichael, couldn't move, but Kettleburn was on his feet heading for Dumbledore, knowing that an explosion was coming and coming soon.

"Wanton, am I?" Carmichael started to rise but, not relinquishing her hold on Snape, found it difficult to do. "At least I don't chase them away by dying my nose indigo. You stifle them, and they run{\el}"

"Professor McGonagall, if you would kindly step into the side chamber, I would be obliged," said Dumbledore, who now joined the fray. "And Professor Carmichael as well. Severus, would you assist Professor Carmichael. She may be unfamiliar with the room."

McGonagall glared at Dumbledore, her temper already flaring, but turned and stalked to the side chamber with great dignity. Snape rose, bringing Carmichael to her feet with him, Kettleburn helping on the other side. Carmichael was quite capable of standing and walking by herself, but both men wanted her restrained in case she decided to lash out.

They managed to make it to the side chamber without the students being aware that anything was happening. Once they were inside, Dumbledore had each of the ladies sit on opposite sides of the room while Kettleburn returned to his seat. Snape was sent for coffee for Dr. Carmichael. He could hear Dumbledore's voice as he opened the chamber door on his return.

"{\el} last year because of the lack of a Dark Arts professor for the second and third terms." Dumbledore turn at the sound of the door. "Thank you, Severus. Dr. Carmichael, I strongly advise you to drink the coffee. Severus, you should stay since it seems, will you nill you, you are part of this. Now, Minerva, as I told you earlier, we were able to avoid disaster last June by concentrating all our efforts on the fifth and seventh years so that they could pass their OWLs and NEWTs, but the other years were seriously neglected and far behind where they should have been. The school needs—I need—a Dark Arts expert. Dr. Carmichael has already been able to make up most of the deficit in just two months. By June all of the classes should be well prepared for their exams."

"Does the moral character of this school stand for nothing! That woman is a disgrace—"

"Minerva!"

"A bad example to our students. She practically encourages lewd and immoral behavior."

"Have you ever seen her behave in anything but a professional way with the students."

"No, but at the welcoming feast and this evening she was exhibiting a level of inappropriateness that was unacceptable."

"She called me names, Albus," said Carmichael menacingly. "Unpleasant names."

"You were crawling all over a male professor in full view{\el}"

"Linking arms doesn't constitute crawling{\el}"

"Ladies!" The room was silent. Then Dumbledore turned toward the door. "Severus, public demonstrations aside, are Dr. Carmichael's attentions in any way disagreeable to you?"

Snape was taken aback by the question. He thought for a moment. "I would rather it were kept on a professional basis," he said, noting both McGonagall's smugness and Carmichael's anger.

"Very well. Professor McGonagall, I expect you to behave professionally when you come into contact with Dr. Carmichael. You should stay separated from each other at meals and exchange as few remarks as possible at official occasions."

"Sir, I want to register my opinion that this woman is not fit to teach children and should not remain."

"Opinion registered. Now you will follow my instructions."

"Yes, sir."

"Dr. Carmichael, the same. And you will not initiate any kind of flirtation with Professor Snape."

"Just keep her away from me, Albus. That woman is vindictive and dangerous."

"Enough from both of you! Now, we must maintain appearances. Severus, you will leave first and go to your place at the far side of the table. Then, Minerva, you will take your seat at the center. Valeria, you will follow me out and remain at this end. None of you should look at each other for the remainder of the feast. We do not want the students to know there is discord among the staff. The rest of the staff should not be forced to deal with it either. Is that understood?"

They all agreed and went to their separate places without comment. The rest of the Halloween feast passed in apparent calm and good cheer.

After the students had retired to their dormitories, the teachers collected in the staffroom for a final round of drinks and a little friendly chatting. McGonagall went immediately to the far corner to help Sinistra fill the little goblets with sherry, and to stay as far as possible from the general crowd.

Most of them had been served when, a few minutes later, Carmichael walked in. She stayed near the door and carefully kept her face turned away from the other side of the room so that she and McGonagall wouldn't look at each other. Most of the teachers didn't notice.

"Is it all right if I ask you to get me a glass, too?" Carmichael asked Snape, and there was a bitter note in her voice. "You wouldn't interpret it as an attack or anything like that?"

"Of course not," Snape answered. "What would you like? Sherry? Port? Mead?"

"A glass of sherry would be nice."

Snape made his way to the other end of the room. "Could I have a goblet of sherry for Professor Carmichael," he asked Sinistra.

"Let me get that for you," said McGonagall, turning to pour the glass from a bottle on the counter and handing it to Snape who took it to Carmichael.

Carmichael received the goblet with thanks and returned to her conversation with Futhark, drinking the sherry in a couple of mouthfuls. A moment later a funny look came across her face. "Dear," she said turning to Sprout. "Is there a ladies room on this floor? I think I'm going to be sick."

Sprout went with Carmichael to be sure she found the way, and the rest of the teachers began clearing up, as it was after eleven o'clock. No one thought much of it until fifteen minutes later when Sprout came running into the staffroom in great agitation.

"Madam Pomfrey!" Sprout called. "Is Madam Pomfrey here?"

"Over here, Pomona," said the nurse. "What's wrong?"

"It's Dr. Carmichael! She's terribly sick, Poppy. I've never seen anything like it."

Sprout and Pomfrey hurried out of the room, while the rest of the staff exchanged concerned glances. McGonagall went over to Snape. "You've got the youngest legs. Go up and let Albus know. He'll want to be with her."

Snape sprinted up the stairs to the seventh floor, and was admitted to the spiral staircase. A few words, and Dumbledore was speeding down to the first floor staff bathroom to find out what was happening. The teachers hovered around the entrance hall and the staffroom, worried and wanting to help.

Sprout appeared among them and was inundated with questions.

"The poor woman," she said. "It's like her system is trying to purge everything inside her. Diarrhea, vomiting, it won't stop. And in between bouts she just keeps pacing, waiting for the next one. Her skin's all clammy, and she's shaking like a leaf."

Dumbledore came to the staffroom. "What was she doing just before she took ill?" he asked.

"She walked in fine," said Futhark, "and we got to talking. There was nothing wrong. And then like that—suddenly she got all queer in the face and said she was going to be sick. Just one second to the next."

"Did she eat or drink anything?"

"I think she had a glass of{\el} what was it?"

"Sherry," said Snape. "I gave it to her."

"And where did you get it from?"

"Over there. Professor Sinistra{\el} no, Professor McGonagall poured it for me."

"Where is the glass now?"

The glass had been cleared away and cleaned, and placed with the others in the cupboard. There was no way to tell which it had been, or if found, what it had contained. Meanwhile, Madam Pomfrey stayed by Dr. Carmichael's side, unable even to take her to the hospital wing until the purging was finished.

"Right now," Pomfrey told Dumbledore, "I'm most concerned about dehydration. She's losing too much fluid, and her stomach won't hold anything that I give her."

After two hours, the strength and frequency of the bouts of purging seemed to abate to the point where Pomfrey was ready to take Carmichael to the hospital wing on a stretcher. By this time Carmichael was beset by chills, shivering with cold even though wrapped in a blanket.

Dumbledore sent the rest of the staff, including McGonagall, to bed, but asked Sprout and Snape to stay with him in the hospital wing. He had need of their expertise.

"What could cause this?" he asked them.

Pomfrey joined them. "It's over," she said. "Dr. Carmichael is fine. Vomiting, diarrhea, chills, all gone. It's as if she was never sick. First she's shivering in one of my beds, then she's fit as a fiddle. I've told her she has to stay here until morning, and she's agreed."

"Diagnosis?" Dumbledore asked.

"No disease that I know of. Pharmacological."

"Which means?"

Snape answered. "It may be a result of poisoning."

"What could cause this?" Dumbledore repeated.

"It could be something that's both cathartic and emetic. Blue flag{\el} May apple{\el}" Snape said. "Or a combination of a cathartic with an emetic."

"Do we have these things at Hogwarts?" Dumbledore asked.

"Headmaster," said Sprout, "there are poisons all around us. The bulb of a daffodil could have caused vomiting like that{\el} though at that strength it would have killed her hours ago. Finding them isn't difficult if you know what to look for."

"All right," Dumbledore sighed. "We must consider ourselves in the midst of a full investigation. Severus, have you been within view of someone else at all times tonight?"

"Yes, sir. Except when I went upstairs to get you."

"Will it be possible to confirm by witnesses that from a certain time you have not gone back to your own rooms?"

Seeing where the questions led, Snape paused, trying to fight the surge of bitterness that rose in him. "Yes, sir. I've been visible since this afternoon."

"Good. I need to go down and seal your rooms, and you need to sleep somewhere else for the rest of the night. Pomona, how secure are the greenhouses?"

"Ordinary locking, but I shut them down Saturday morning, and I could tell if anyone had opened them."

"I shall seal them tonight as well. As for the more available poisons, we shall have to try to account for as much as we may. I fear classes must be suspended tomorrow while I talk to the staff and the Ministry."

Snape went with Sprout and Dumbledore first to his own rooms, which were sealed against him, and then to the greenhouses, which were sealed against Sprout. That they were also sealed against everyone else seemed irrelevant.

"Where am I to sleep tonight, sir," Snape asked Dumbledore. By this time it was nearly four in the morning. Notices had been placed that there would be brunch instead of breakfast, and that classes would not be held.

"The house-elves have prepared one of the guest rooms on the sixth floor. You should be comfortable there for a day or two. Until we see how serious the situation really is."

Snape went to the sixth floor, immensely tired and more than ready to sleep. The guest quarters turned out to be far more spacious and comfortable than his own rooms, if a bit sparsely supplied with things like books. He had, in any case, no need of books that night—or rather that morning—and could remedy the lack if he had to stay longer than a night.

It was easier to get to sleep than he thought. Random speculation about who might be responsible for the attack on Dr. Carmichael succumbed to exhaustion, and he was asleep very quickly, dreaming of clams and mussels having an obstacle race past the Whomping Willow while Lily cheered `Mudbloods! Mudbloods! Go{\el} mudbloods!'

When Snape woke the next morning, it was nearly nine o'clock. It took him a moment to remember where he was and why, then he dressed quickly and went downstairs. Most of the staff was filing into the Great Hall for brunch along with a highly elated group of students who were ecstatic to find their classes canceled for the day. McGonagall wasn't there.

"I hear she's still in the hospital," said Kettleburn, not having to explain who `she' was.

"I think it's just a precaution. She was feeling better around three o'clock."

"You were up that late? Guess it goes with the potions job. My wife wasn't happy with the hour I got in, even if it was Halloween, but when I told her what happened she was as concerned as I was. What did they find out?"

"I'm not sure I'm supposed to talk about it," said Snape, and left it at that.

At ten o'clock, the team from the Ministry arrived. By this time, most of the students had finished in the Great Hall and gone outside or to the library to study. After inviting the Ministry team to join the staff at brunch, Dumbledore turned the Great Hall into an interview room. The team spoke to the teachers one by one, cautioning each not to reveal anything of the session to the others.

McGonagall had finally come downstairs. "Is all this really necessary?" she asked Dumbledore, waving toward the Hall. "It is a serious disruption of the school's routine."

"I fear it is necessary, Minerva. Yesterday's episode is unprecedented in Hogwarts history, at least since the end of the Middle Ages, and Val Carmichael is a very well-known person. We must see that all procedures are correctly followed."

Snape, since he was one of the principal witnesses, was one of the last called. Sitting before the investigators reminded him of his trial nearly a year earlier.

"Did you get Dr. Carmichael a glass of sherry?"

"I did."

"Why did you do that?"

"Because she asked me to."

The investigation droned on in a dull litany of seemingly pointless questions.

"Where was the sherry?"

"In the far corner of the room."

"And the glasses?"

"The same."

"Did you ask Professor McGonagall for the sherry?"

"No, I asked Professor Sinistra."

"Did Professor Sinistra give you the sherry?"

"No, Professor McGonagall did."

"Did she know it was for Dr. Carmichael?"

"Yes."

On and on, for over two hours, the Ministry team questioned Snape, while he locked and sealed every feeling he had under double doors and hatches in order to remain calm. They reviewed the timing of the glass of sherry repeatedly, then extended the questioning to earlier occasions, including a detailed account of Carmichael's `attentions' to him. Fortunately, his study on the subject had its continued good effect in making him impervious to both the questions and their implications, and at no point did Snape become embarrassed or blush.

"Are you certain that you never encouraged Dr. Carmichael?"

"I don't understand what you mean."

"Did you ever do anything to make her feel that you took pleasure in her company?"

"I did take pleasure in her company. She has a excellent understanding of her subject, and I enjoyed talking to her."

"So Dr. Carmichael had some grounds for feeling that you might be attracted to her?"

"I have no way of knowing what Dr. Carmichael felt. For that you should ask her."

"But Professor McGonagall tried to discourage you from association with Dr. Carmichael?"

"On several occasions, yes."

When the questioning was over, Snape was asked to take the team to his office. There, in the presence and with the help of Professor Dumbledore, they broke the seals on the door and entered.

"Are these the only rooms over which you have control, Professor Snape?"

"There's also the classroom."

"We'll check that, too. Do you have an inventory of everything in this room?"

Enormously grateful now for all the meticulous work he'd done since taking the potions job, Snape pulled the inventory files from their cabinet and gave them to the inspectors.

"Is this the only place where you keep poisons?"

"Yes."

"You may go for the moment. We may have more questions after we finish here. Don't discuss this with anyone."

Snape left them reluctantly, knowing they were about to sort through everything he had at Hogwarts. \emph{That's what I get for being the only one here who regularly deals with poisons.} He went to the staff room. It was still only mid afternoon, but since the investigating team had taken over the Great Hall, dinner would be served to the students in their dormitories and to the staff in the staffroom. Meanwhile, a refreshment table had been set up.

"Good Lord, Severus," Sprout exclaimed when she saw him, "we thought they were never going to let you come up for air. Here, have a bite to eat and something to drink. You must be exhausted."

"Just pumpkin juice, Pomona, thank you. I'm supposed to hold myself available for further questioning. They're searching my rooms now."

"Whatever for?"

"I'm not supposed to discuss it."

"If this is how they treat you," said Flitwick gravely, "what do you suppose they'll do to Minerva?"

"Have they inspected the greenhouses?" Snape asked Sprout.

"Not yet, though I'm sure they will. They're not going to find anything there but plants, though."

"Right," said Snape. "Perfectly harmless things like mandragora, henbane, and monkshood. Nothing suspicious there at all." Sprout looked suddenly nervous.

Flopping into one of the leather chairs, Snape sipped his pumpkin juice and let the conversation flow around him, feeling no desire whatever to join in. It would have been pleasant just to relax for an hour in the staffroom were it not for the certainty that his interrogation wasn't over yet. Sure enough, the hour had barely passed when he was called back into the Great Hall.

"Professor Snape, we wish to thank you for making our job so easy. Have you always kept such detailed accounts of your inventory?"

"This is my second year at Hogwarts. Last year I had to start everything with no prior records. The detailed inventories were necessary."

"And before that?"

"I beg your pardon."

"Is it true, Professor Snape that you were a Death Eater?"

"Yes."

"What were your duties?"

"Making potions, inventing a few spells, teaching basic self-defense{\el}"

"Did you keep such detailed accounts in your potions work there?"

"Of course."

"Were you ever asked to brew poisons?"

Three heartbeats. "A couple of times."

"Define `couple.'"

"Four."

"Is there any reason why you tried to minimize the quantity by using an ambiguous word?"

"No."

"Were you ever asked to produce a poison to be used specifically against Val Carmichael?"

"No."

"Are you certain."

"Positive. I was never told what things were used for."

"So they might have been used against her without your knowledge."

"It is a possibility."

"Professor Snape, who are these people?" The photos from the lararium were pushed across the table.

"That's me with my parents at Blackpool."

"Muggle pictures?"

"My father was a muggle. This was my witch grandmother, Constantina Rossendale, and this my muggle grandmother, Leonora Smith."

"And this?" It was the framed scrap of paper from Lily.

"A classmate who died during the troubles. I didn't have a photograph."

"Who was it?"

"I would prefer not to say."

There was a pause as they noted that he would not answer the question. Then they started up again. "It seems, Professor, that you have some unusual reading material in your room." The book about sexual practices was placed in front of Snape on the table.

"I got that at the suggestion of a colleague. I was unfamiliar with some of Dr. Carmichael's references, and he suggested I learn more about the subject."

"You bought a book like this to understand flirtatious nuances?"

"Dr. Carmichael has extensive experience."

That silenced them for a moment as each member of the team apparently tried to imagine what Carmichael may have said to Snape. Then they resumed.

"Who was the colleague?"

Two more heartbeats. "Hagrid. But he will not want to say so if he feels he is violating my confidence."

"You also have a set of murder mysteries in your private collection."

"Yes."

"The third volume in the series deals with deadly poison put into food that will only be consumed by one person."

"I believe it does. The poison involved is aconite."

"Is there any aconite at Hogwarts?"

"Yes, the monkshood plant grows in the greenhouses, and I have aconite in my stores. But you are not looking for that."

"Why not, Professor?"

"Aconite poisoning affects the heart. Whatever was used on Dr. Carmichael affected the digestive tract, both upper and lower."

"You know a lot about poisons."

"I'm the potions master. It's my job."

The interrogation of Professor McGonagall was widely anticipated and even wagered on, this last inspired and encouraged by Kettleburn. The entire staff watched from doorways and behind pillars as McGonagall marched proudly down the marble staircase and into the Great Hall, the massive doors closing behind her.

No one overheard the interview, and the Ministry never made it public, but the Hogwarts staff witnessed the faces of the investigative team as they left the Great Hall several hours later. They were all in shock. McGonagall had, of course, taught them all in Transfiguration, and had been head of house to two of the three. She knew their deepest secrets, and was not a woman to forego the use of ammunition when the situation required it.

"They had the nerve," McGonagall told the rest of the teachers later in the staffroom, "to suggest that I might want to poison the woman! As if I would waste good poison on her! What did they ask you, Severus?"

"They instructed me not to talk about it," Snape replied. When the others pressured him, he continued, "And I am sure that in light of my experiences of last year, you can all understand why I am reluctant to defy their orders."

That silenced them all, even McGonagall, though she did whisper, "If there was something I really needed to know, you would hint{\el} ?" He assured her that he would, if there were.

The only other worry was that the team called Hagrid late into the evening. Snape had his fingers crossed that Hagrid would, in fact, tell them the truth, and was on pins and needles until the session ended.

"They told me ya said ya'd talked t' me," Hagrid admitted to Snape later. "Now how would they know that unless ya really told them? So I told them 'bout our chat."

"The whole thing?" Snape asked, cringing inside, though careful reflection had already told him that no amount of embarrassment about his sexual innocence could ever compare to being suspected of attempted murder.

"Well, how was I supposed t' know what was important and what was not? Sure I told them the whole thing."

"And you did well, Hagrid. You probably helped me a lot. Thank you."

"Glad I could, too. You been known t' get yerself into the strangest of scrapes."

"I know, Hagrid. Thank you again. I appreciate it."

The investigative team stayed on for a few more days, then returned to the Ministry in London. Classes had begun to resume even while they were still on the grounds and, except for Dark Arts, were in full swing before the end of the week. And then—the remedy for all ills—the first Quidditch game of the season was upon them.

\subsection{Saturday, November 6, 1982 (two days before the last quarter)}

It was Slytherin versus Gryffindor, the heads having decided to return to the traditional schedule. Snape was sorry that Algie and Chris were gone, both having graduated, but eager to test the talents of the new team. Lionel Atherton, a sixth year now, continued as seeker. Rhonda Shoemaker, David Commyns, and Saffron Magee were the chasers. The two new beaters were Sergey Duval and Josh Van Zandt, while the new keeper was Richie Gamp.

Snape was a little concerned about Richie's safety, since his father was known to have been a Death Eater, now in Azkaban. What was not known, not even to the Ministry, was that both Beaters and the youngest Chaser, Saffron, also came from Death Eater families. Snape had warned them all that he did not want the game to get too interesting.

Val Carmichael made her first public appearance at brunch on Saturday, the sixth of November, sitting next to Dumbledore while McGonagall sat at the far end of the high table from Snape, closer to her own house table. The atmosphere was deceptively calm.

"How does it look?" Kettleburn had stayed the night just to be on the grounds early for the game. "Are they in fighting shape?"

"It depends on what kind of fight you're looking for."

"Are you serious?"

"Professor Kettleburn, do you see that tall, blond Beater over there at the Gryffindor table?"

"Peterson? He's in one of my classes."

"He dropped out for a couple of months last year over the Death Eater business."

"I remember. Tried to take on one of your boys, didn't he?"

"Exactly. The boy he attacked is now our Keeper."

Kettleburn's eyes widened. "Thanks for the tip," he said, and moved off to make a side bet or two.

In the early afternoon, the whole school trooped down to the Quidditch field. Snape was surprised to see that a large number of spectators were coming through the gates from Hogsmeade. Many of them were total strangers to him.

"First opening game at Hogwarts since the whole You-Know-Who business ended," McGonagall whispered. "Last year they were still hunting Death Eaters. This year everyone feels safe."

Extra viewing stands had been set up to accommodate the visitors, among whom Snape recognized Alastor Moody, who waved at him but did not approach. Students were leaving the school groups to greet their parents, and Snape noted that the first year boy, Bill Weasley, ran over to a tall, thin man and a short plump woman, both with red hair, who must be Arthur Weasley and his wife. They were surrounded by a horde of young children, the youngest of whom seemed to be still a baby, though Snape was not good at judging children's ages. All of them had red hair, and most of them were distressingly active and noisy.

Dumbledore went over to speak with the Weasleys, and Mrs.~Weasley glanced at Snape, then rather pointedly turned her back to tend the children. Arthur Weasley, however, followed Dumbledore to where Snape stood next to McGonagall.

"Minerva," Dumbledore said, "I am sure you remember Arthur. Arthur, this is our newest teacher, Professor Severus Snape."

Weasley stuck out his right hand. "Pleased to meet you, Professor."

Snape shook hands. "The honor is mine, sir. I understand that you did me a kindness earlier this year, and I welcome the opportunity to tell you how grateful I am."

"Not at all, not at all. I hear you're taking good care of Bill."

"Your son is quite competent at Potions,"—an overstatement—"but I understand he excels at Charms and Defense against the Dark Arts."

"Yes, yes. We're quite pleased with his marks."

They parted then, McGonagall and Snape to sit with Flitwick and Sprout between them while Dumbledore joined some of the people from the Ministry.

Snape was not pleased to note that Val Carmichael had attached herself to Alastor Moody, and that the two of them were deep in conversation.

Madam Hooch started the game, and from the beginning it was apparent that Gryffindor's main tactic was to score by taking out the Slytherin Keeper. The first Bludger hit Richie in the shoulder, and the second was going for his head when Sergey managed to beat it back in time. In a way this was not a bad thing for Slytherin as long as they could protect Richie. It meant that Gryffindor, would rather narrow-mindedly keep the Bludgers around the Slytherin goal hoops where they were convenient to use against any Gryffindor Chasers who might approach, while the Slytherin Chasers were free from having to worry about Bludgers. It was a bit of a strain on Richie, though, who was the principal target.

Things began to heat up when a Gryffindor Beater ran his broom into Richie's. Madam Hooch's whistle stopped the action. "Foul!" she called. The Quaffle went to the Slytherin Chasers. Saffron made a pass at the right-hand hoop, suddenly dove out of the scoring area as she passed the Quaffle laterally to Rhonda, and Slytherin scored the first goal.

Cheers from Slytherin. Boos from Gryffindor. Snape was growing aware that the visiting crowd was mainly pro-Gryffindor, with the entire Weasley clan at its center. Mrs.~Weasley, in particular, was loud and passionate not only in her support of Gryffindor, but also in her opposition to Slytherin.

"Isn't Mrs.~Weasley taking this game a bit too seriously?" Snape whispered to Flitwick.

"Don't mind her. It's probably good for her. She was always an emotional student, and it's been hard the last couple of years having to hold everything in for her family's sake."

"I don't understand."

"Did you ever hear the names Gideon and Fabian Prewett?"

Snape remembered the day the squad of Death Eaters returned to headquarters with the news that they'd killed the Prewett brothers. There had been something of a celebration. All he said to Flitwick was, "Yes."

"She's their sister. Molly Prewett."

That explained her coldness and turning her back when Dumbledore wanted to introduce Snape to them. She probably knew about Richie's father, too. Snape tried to ignore the screaming visitor stands.

The game had become a war. Normally Quidditch was a highly physical game, but this one was a running battle that was now racking up more fouls than clean scores. Chasers were wrestling the Quaffle from each other's grasp, and two of them even locked brooms, bringing both crashing to the ground, still fighting for the Quaffle, and earning simultaneous fouls against both teams.

Richie was slammed against a goal post, removing him from the game for fifteen minutes. Slytherin made the foul shot, but Gryffindor began rushing the hoops and scored five times while there was no Keeper to defend them. Josh and a rival Beater got into a fist fight as both the Gryffindor and Slytherin stands screamed for blood, and Madam Hooch had to pull the two out of the game until they cooled off a little. Then Sergey's club hit the end of a Chaser's broom, knocking it and her to the ground and the Gryffindor stands began to empty onto the field ready to riot.

The game was stopped as the teachers struggled to get the students back into the stands. Dumbledore placed a barrier down the middle of the pitch at ground level to be sure no one could cross, and the game resumed. It was 90--70 in favor of Gryffindor, and after nearly an hour of play, no one had seen the Snitch.

Still the battle raged. The noise from the stands drowned out any possibility of conversation; the air around the pitch was pulsing and throbbing with the sound, the wooden stands vibrating from the stomping and pounding. Then a Gryffindor Beater hit a Bludger into the Hufflepuff stands forcing students to dive for cover, and Hufflepuff spilled onto the pitch, certain it was in retaliation for their support of Slytherin.

The sun was low in the sky and the score stood 140--130 when the Snitch finally appeared. Both Seekers saw it at the same time and plunged toward the earth, jostling and shoving each other while the electrified stands urged them on. The Snitch won, eluding both Seekers and streaking around the pitch with a whining hum. But now it was only a matter of who would get it first, and the scoring at the hoops became secondary as Beaters tried to break the concentration of Seekers and Chasers tried to throw them off course.

The end was a neck-and-neck race as the Snitch soared high into the air, both Seekers leaving the rest of their teams far below, and then the Gryffindor Seeker was chasing Lionel with murderous intent as he streaked back toward the ground with the Snitch firmly clasped in his right hand.

Slytherin had won, and all Gryffindor wanted was revenge.

Getting the students back into the castle was an exercise in riot control. Gryffindor and Ravenclaw went first, directly to the Great Hall for supper. Another barrier was placed down the middle of the hall to prevent projectile contact between the two sides as Hufflepuff and Slytherin followed them in. The teachers postponed their own meals to patrol the aisles, allowing the noise to continue, but silencing any attempts by either side to insult the other. By the end of supper, the mood had calmed considerably, Ravenclaw and Hufflepuff were no longer enemies, and everybody was ready for the common rooms and bed. 


