% A Difference in the Family: The Snape Chronicles (Rannaro)
% Yes, That Is My Job

\chapter{Wheels of Fortune}

Dumbledore sighed. "I am, of course, disappointed that you have reached this decision, but I shall respect it."

"It isn't as if you have much choice. What about the others? Potter has lethal information on them, too. Shouldn't they be warned?"

"Would it do any good? Is our cause served by making people unnecessarily cautious?"

"I'll remember you said that in case anyone asks. Now, how am I to get back to Hogwarts?"

Dumbledore sent a patronus to McGonagall, and Snape found the gate open on his arrival. He made his way wearily to his own room and sank onto the bed, not even bothering to undress. His conversation with Dumbledore had left him intensely depressed.

\emph{He has no idea what it's like to go to Croydon every week not knowing if I'm going to return. And he doesn't care. Last year, when I asked him to cast the Cruciatus Curse, I'm sure he was more concerned about his having to cause pain than about my having to feel it. If he thought it was necessary, would he throw me to the wolves? In a heartbeat. Would he throw Potter to the wolves{\el} a totally different question. Am I jealous of Potter?}

It was a new idea, and one Snape didn't like. Did he, in fact, resent Potter's position in Dumbledore's regard? \emph{Has Jacob stolen Isaac's blessing, and am I Esau? Am I angry because Dumbledore never kills the fatted calf for me, but welcomes prodigal Potter with open arms?}

Yet the Easter break seemed to pass without incident, and midway Snape made another routine visit to Croydon.

"Long time, no see," stage-whispered Phina as she vamped in the laboratory doorway.

"I was here last week."

"True, but I wasn't. The Wheel of Fortune sent Lucius up and Bella down, so you and I had to suffer. Did you suffer the lack of me? Really suffer?"

"Maybe. Is there a reward for saying `yes'?"

"I thought tonight we might go somewhere of my choosing."

"Am I going to be mugged and left bleeding by the side of the road?"

"Actually, it's been a while since I've seduced anyone, and I'm a little rusty. I was hoping to get in a little training time."

"Where were you thinking of going?"

"I sublet a little flat in the West End. It's cozy. We'd have to apparate together, of course."

"Let me finish these potions. It'll take about half an hour."

It took forty-five minutes, and then Phina clasped Snape to apparate to a flat that was the entire third floor of a nineteenth century town house. Snape took in Phina's version of Art Deco decor as she lowered the lights, put on some mood music, and opened a bottle of Sauvignon Blanc.

Handing him a glass of the wine, Phina pulled Snape down onto a cherry-red loveseat with rounded back and arms. "Kiss me, dahling," she intoned in a neoclassical '30s drawl, and encircled his neck with her arms, still holding the wineglass.

Trying not to laugh, Snape did as he was told, and the first touch of their lips reminded him why he enjoyed her company so much. He managed to deftly remove the glass from her hand, and they kissed lingeringly, lost in the moment of intimacy. All was going excellently until Phina destroyed the night with four words.

Looking up at Snape with wide eyes, she asked, "Do you love me?"

Snape pushed himself to a sitting position on the edge of the loveseat. "What do you want?" he asked.

Phina stared at him. "I thought that was obvious."

"People who ask that question do so because they want something."

"Well about a hundred years ago I wanted you. Now I'm not so sure." Snape didn't look at her, and a moment later she added, "I guess the answer was `no.' If you're not opposed to talking, I could make some coffee."

Phina got up and went to the kitchen where she ran water into an hourglass-shaped espresso maker and lit the stove. Snape followed her as far as the kitchen door. She looked over as he watched her. "Coffee only comes with conversation. No conversation, no coffee, you go back to wherever you want to go back to. \emph{Capisci}?"

"I understand."

Mutual silence accentuated the bubbling of the coffee maker, then Phina poured two demitasses and they sat facing each other across the kitchen table. "So," she challenged, "is it the fact that I'm ugly and repulsive?"

"No! Gad, if there's anyone neither ugly nor repulsive, it's you. It's just that this was all going so{\el} well, so{\el} , and then you had to make it personal."

"It has a tendency to be personal. Sort of the nature of the beast."

"I don't mean{\el} I mean—you were doing a job, and I was playing along, and it was{\el} uncomplicated{\el} lighthearted even{\el} and we didn't have to think about{\el} I don't even believe{\el} Drat! I had this conversation just a few weeks ago."

"Really? With whom?"

"Dumbledore."

Phina locked her mouth shut and looked for a moment as if she was about to explode. Then she burst out laughing. "You and Albus Dumbledore! I can't even picture it—if I tried, I'd just die! Which of you{\el}"

"I didn't mean that! You know perfectly well I didn't mean that! For crying out loud, Phina, stop laughing. I'm walking out now. You can just tell Bella you failed miserably and I don't care what excuse you give{\el}"

"No{\el} no{\el}" she gasped, waving him back into the chair. "I'm sorry. You took me by surprise. I didn't{\el} I don't{\el} Oh, Lord!" When the giggling fit calmed down, Phina took a deep breath, placed both hands squarely on the table, and looked Snape in the eye. "I take it this was a philosophical discussion."

"Well, yes. Of course." Then Snape began to chuckle, too. "The problem is{\el} Well, Dumbledore knows about you—not you specifically, but a{\el} a woman. He could sense a presence in my life, and he asked if I loved{\el} you. I have to tell you honestly, I don't believe there is such a thing. I think part of the population uses the word in order to manipulate another part of the population. `Love' is a con game."

"You've never loved anyone?"

"Don't use that tone of voice. I've felt affection for people, and I've been jealous, and I've felt{\el}" Snape paused, not used to any kind of admission of emotions. He knew he was blushing, and he knew that Phina could read this part of him like a book.

"Now we come to the heart of the matter. Semantics!"

"It isn't that simple!"

"Of course it is! You're afraid of the word `love.' You're willing to admit to anything else, just not the L word. Well come on, Cursemaster! I hate you, I loathe you, I abominate you. Let's just have fun!"

The incredible thing was that Snape still wanted to debate the issue, but Phina was having none of it. She seized his wrist, dragged him out of the chair, and pulled him into an embrace. It was a couple of hours before Snape even began to wonder what time it was.

The time window was a narrow one, and Snape didn't make it. At 11:06 he arrived in Hogsmeade. Barred from the grounds, he was forced to send a patronus. At 11:08 he walked through the gate. McGonagall had ample reason to complain now. Complaining was, however, not the only thing on McGonagall's mind.

Only moments after arriving in his office, Snape answered a knock at his door. It was McGonagall in nightgown, tartan plaid robe, and hair net. "Who is she?" McGonagall demanded.

"Minerva, do you really think this is the time to{\el}"

"Don't you dare try to wriggle out of this one! That patronus was practically{\el} well, it was. There's not much will affect a patronus like that, and so I'm asking. Who is she?"

"Mata Hari."

"Not the slightest bit funny, young man. If you are jeopardizing the lives and safety of colleagues of mine for purely personal reasons, I'll{\el}"

The accusation stung deeply. "No, no there's no one in danger. It isn't like that."

"You're dancing attendance on a Death Eater. You'll explain to me what it's like."

"She's just{\el}"

"Well?"

"She's Bellatrix Lestrange's cousin, and{\el} well{\el} she's{\el}"

"Assigned to lead you by the nose and diddle you into spilling everything you know about all of us."

"No! It has nothing to do with you."

"How do you know?"

"She's{\el} well{\el} she's{\el}"

"You've said that before, laddie. Now explain to me why I shouldna be worrit."

"She doesn't really want to do what Bella tells her to. She's more independent, more{\el}"

"And that's what she told you. How do ye know she's telling the truth?"

And there it was. Snape didn't know. He had no idea at all what Phina did when they weren't together, what she divulged to Bella, whether or not she was playing the same game with different men several times a week. Was he giving Phina secrets of the Order? He didn't think they'd ever discussed the Order when they were together, but what did they talk about? Snape wasn't sure. And therefore it might have been the Order.

"Minerva, I'm sorry. I've been{\el} how do I explain?"

"Ye've been traipsing after a skirt, that's what ye've been doing. And at any other time I'd be saying good on ye. But now's no' the time, and this girl's no' the one. Does Dumbledore know?"

"Yes. He asked me if I loved her."

"Well, do ye?"

"I don't accept the concept. There's no such thing."

"'T is a good sign that in the throes of passion ye can still debate a philosophical point. She's no' got her claws into ye so far as ye cannit get out. Ye stay away from that girl, Severus. She's no good for you. And she's no good for me and the others either. Ye need to think of someone besides yourself from time to time."

McGonagall returned to her rooms, and Snape to his bed, but not to sleep. What McGonagall had said revolved in his mind endlessly all that night, as he weighed the relative merits of trusting someone like Phina.

There was no doubt that McGonagall was upset; she would never have reverted to a burr otherwise\emph{. Can't she understand that I know Phina well enough to know that she wouldn't betray me? I've known her for months. She came to me for defense training.} Snape recalled the first lesson in the training room{\el} but that wasn't right—the first time he'd seen her was with Bella. Being introduced by Bella{\el} \emph{But Bella didn't escape from Azkaban until January, so that was only the beginning of February, just over two month's ago! Have I only known Phina for two months?}

It was a distressing thought, for seeing Phina was fast becoming the most important thing about Croydon. Snape forced himself to reconstruct the relationship, but sometimes the sequence of events was fuzzy. I took her to the theater, then to dinner{\el} no, she asked me to take her to dinner{\el} was that before or after Bella caught us together? Slowly—slowly because he really didn't want to see it—slowly a pattern emerged.

\emph{Whenever Bella hits a low point with the Dark Lord, Phina disappears for a week. Then when she comes back, the stakes get higher, the meetings become more intimate. It's as if every time Bella is insecure, Phina takes greater measures to move me into Bella's camp. Was she following orders tonight?}

But McGonagall was wrong if she thought Phina's goal was to learn about the Order. Phina was there because of Bella's rivalry with Malfoy. It was a purely internal matter, nothing to affect Hogwarts or Grimmauld Place at all. \emph{Everyone at Croydon knows I spy for the Dark Lord at Hogwarts, yet Phina has never once asked about it.}

Could that possibility arise? \emph{What did we talk about tonight?} Snape had to admit he didn't remember. Not that there was all that much talking. \emph{Could I lower my guard and say something without realizing it? If that could happen, then McGonagall's right. I would be putting the others in danger.}

The last week of Easter break went smoothly and quietly. There were no disruptions to spark Umbridge's anger, diligent students sought out professors for help studying for their OWL and NEWT exams, and Snape never once asked McGonagall for special permission to leave in the middle of the week, so by Wednesday she was speaking to him again.

"That woman is hinting that she'd like to observe all of my classes, as she did with Trelawney. Can you imagine the nerve of the creature! Has she nothing to do as headmistress that she can waste time with such tripe?"

"I take it you still haven't given her the `keys' to the castle."

"And let her control all our comings and our goings? You'd better hope I don't laddie, or you're going to be between a rock and a hard place."

"Are you going to let her observe you?"

"If it comes to that, I have no choice. But she's making a major tactical error."

"Which is?"

"You're supposed to be clever. You figure it out."

Snape thought for a moment. "She's trying to pressure you into giving her the spells. But if you do, then she can dismiss you any time she likes. As long as you keep the spells secret, she has to keep you here at Hogwarts. She's treating you like she treated Trelawney before she sacked her, thereby encouraging you to withhold what she wants."

"There. You are clever. The problem is that the woman has no subtlety."

"Good thing for us."

Saturday came, the last free day before the returning students raised havoc in the Hall and classes resumed on Monday. Snape ate supper as usual and then made his routine trip to Croydon.

Phina was in the laboratory almost as soon as Snape arrived, sidling close and beginning to tease him with her fingers. Since Snape was trying to measure out the ingredients for a metal-dissolving potion and was about to pour acid, this was decidedly not the time.

"Stop that!" he snapped at her. "You shouldn't be here bothering me."

"Did you hear that, young lady?" drawled a voice from the doorway. "You shouldn't be here bothering him."

Phina stepped away quickly as Malfoy walked into the lab.

Phina stomped out of the laboratory, not attempting to hide her disappointment. Malfoy stepped aside to allow her to pass.

"You'd better watch out for that one," he said calmly to Snape. "She's a man-eater."

"Bella set her on me."

"She's trotted out the big guns, then. Miss Vaughn only hunts serious game."

"Do you know her?"

Malfoy smirked. "Well, I don't exactly `know' her, if you take my meaning. She didn't frequent headquarters until Bella returned. The family depends on her more in financial deals and bla{\el} persuasion."

"I see. I'll be careful. Was there something you wanted to discuss?"

"Just to inquire if you had any opportunity to observe Potter and find out if he's responding to the Dark Lord's projections."

"No, I haven't. Most of the students have been studying for exams and generally locking themselves in their houses. Not to complain or anything, but Draco is part of the problem."

"Really? How so?"

"The Inquisitorial Squad is a masterful idea—it has totally hoodwinked Umbridge—but the squad members are sometimes over enthusiastic. The students of the other houses, especially Gryffindor, tend to stay away from the common areas where they might be observed."

"I hadn't thought of that. I'll send word to Draco."

"Would it be appropriate to tell me if the Dark Lord has made further progress? If not{\el}"

"Not a problem. He has, in fact, been able to catch more glimpses of things through Potter's eyes. This happens most often if Potter's upset about something. He seems, for example, to be having some disagreements with his friends. The Dark Lord would be interested in learning more details about this, which is the main reason I've come to talk to you. He still can't hear what's said, and he has no access to Potter's mind yet outside the direct visual connection. He was rather hoping you could provide context to help him expand the connection. It may prove to be as valuable as the dream link."

"Tell the Dark Lord I am ready to do as he wishes. I'll note down anything I observe."

"I know you have the Dark Lord's best interests at heart." Malfoy left the lab then, turning at the door to say, "Watch out for that girl."

Phina didn't return that night, Malfoy's attention having rendered any contact dangerous, thereby giving Snape time and opportunity to ponder their relationship and her motivation. He finished his work and apparated to Hogsmeade at precisely 11:00, presenting McGonagall with no reason to complain.

The next morning Snape and McGonagall spoke over breakfast.

"Was all calm in the south?"

"Dead and dull. Nothing to not report home to mother about."

"I'm pleased to hear it. I sympathize if this puts a damper on your social life."

"Unavoidable. You did give me a lot to think about."

"There's a good boy."

Later Snape tried to analyze why he was reluctant to tell McGonagall about the Dark Lord's attempts to see through Potter's eyes. His justification was that Dumbledore already knew. And there was also the chance that knowing would cause McGonagall to alter her behavior, thus making the Dark Lord suspicious. Snape rather thought, however, that the real reason was that he didn't want to confide in anyone but Dumbledore. Then he'll remember that I'm important, too.

Monday was the first day that Snape would come into contact with Potter since he'd pulled the boy out of the pensieve. \emph{Who has he told? How many Gryffindors have been regaled with the image of me suspended upside down by Potter's father?} It was a whole different problem from that of the Dark Lord seeing Lily.

It was also a whole different problem from the possibility of the Dark Lord watching him through Potter's eyes. \emph{I don't want Potter to think about me more than he has to. Below the radar{\el}} During Monday morning potions, Snape acted as if Potter didn't exist. Potter did the same regarding Snape. Everything was going smoothly until Potter brought a sample of his potion to Snape's desk for evaluation.

Snape wasn't sure what it was—James arrogant grin and air of superiority or Sirius's strut and defiant tilt of the head—but Potter deposited the flask of potion on his desk, then turned away, and without conscious thought Snape's hand brushed forward and the flask lay broken on the floor. At the sound of shattered glass, Potter spun around.

"Whoops. Another zero, then, Potter," Snape said quietly. Off to one side he could hear Draco Malfoy laughing at Potter's discomfiture. The icing on the cake was that Granger, in an effort to be helpful, had cleaned out Potter's cauldron, and Potter had no more potion to turn in for the assignment. It was a satisfying moment.

As the afternoon wore on, however, the memory of the incident became less and less satisfying. \emph{Childish! Foolhardy! Malfoy told me that the Dark Lord can see through Potter more easily if he's angry or upset. So what do I do? I make him angry. And why do I take the chance of both Potter and the Dark Lord focusing on me? A petty impulse. Severus, you're an idiot.}

Monday afternoon double Potions had just ended, and Snape was beginning to set the room up for the following morning, when there was a sudden commotion in the corridor. Slytherin students were running for the entrance hall, and the air was charged with excitement. Wishing he had the same instinct for a fight or a prank that a fourteen-year-old had, Snape quickly locked the classroom door and joined the crowd.

Students were streaming down the stairs, some holding their noses or gagging, some trying to wipe slime off their clothes or out of their hair, others just moving with the flow of bodies. In their midst, pushing to get ahead before the entrance hall became too crowded with Hufflepuff and Slytherin students pouring out from their respective dungeons, were Fred and George Weasley.

\emph{Aha! We know who's in the center of whatever the problem is!}

Fred and George didn't make it. Their path to the great doors and freedom was blocked by both students and teachers, some of whom had come from the Great Hall where supper was almost ready. The wall of bodies forced the two pranksters to turn at bay in the center of a ring of students, professors, and ghosts, Peeves hovering protectively above them. Umbridge, too, came charging down from the upper floors, out of breath but menacing.

"So!" crowed Umbridge at realizing the twins were trapped. "So{\el} you think it amusing to turn a school corridor into a swamp, do you?"

Snape looked over at Fred and George in shocked admiration. He himself had cast some inventive curses, hexes, and jinxes in his day, but a swamp inside a building was a stroke of genius. Ordinarily he would be incensed at the rule breaking. Seeing as it was Umbridge's problem, however, he decided to keep his mouth shut and enjoy the scene.

Filch pushed his way down from the second floor, Potter right behind him, croaking something about approval for whipping. Umbridge gloated. "You two are about to learn what happens to wrongdoers in my school."

The Weasleys defied her, defied her in front of everyone, then raised their wands and cried in unison, \emph{"Accio Brooms!}" The crash that echoed down the staircase reminded Snape that Umbridge had confiscated the broomsticks, but that made no difference. The brooms were loose and joining Fred and George.

Mounting the brooms, the twins informed the whole crowd that they were leaving Hogwarts and setting up a joke shop. "Special discounts to Hogwarts students who swear they're going to use our products to get rid of this old bat!"

As Umbridge screamed "STOP THEM!" the pair rose above the crowd. "Give her hell from us, Peeves!" was their parting shot, then returning the poltergeist's salute, they were gone.

The students were jumping up and down and cheering. Umbridge was livid and apoplectic. Snape was watching McGonagall, who was moving her lips silently. Fred and George Weasley were escaping from Hogwarts, and McGonagall had just opened the defenses to set them free.

It took an hour and a half to get the majority of the students into the Great Hall and settled for supper. As Snape was setting the Inquisitorial Squad to round up Slytherin students first, the mark on his arm began to itch. \emph{Not now. Please not now. She'll be watching all of us like a hawk.} The summons didn't increase in intensity, however, so Snape was able to plan his departure.

"He sends for you quite a bit, doesn't he?" was McGonagall's comment when Snape made the request.

"This is the first non-routine trip since Dumbledore left, and that one was on my initiative."

"Well, if you weren't working for us, I'd be keeping a record of when he had these little crises. It might show a pattern."

"May I tell him you said so?"

"Will you make me sound fierce and menacing?"

"Like a tigress."

"There's a sweet lad. Leave at 10:45. Back at 11:30. Don't be late."

"But that's hardly enough time if he wants me to do something special."

"Tell him I'm getting suspicious."

\sbreak

"You like to live dangerously," whispered Malfoy as he joined Snape in the interview room. "He isn't pleased about the delay."

"You did remind him that things aren't quite `normal' at Hogwarts, right?"

The Dark Lord appeared. "You did not come when we summoned."

"Lord, forgive me, but the school was in an uproar, and departure wasn't possible."

"Tell us."

"Two students, children of Arthur Weasley, changed a wing of the fifth floor into a swamp, defied Umbridge in front of the whole school, destroyed her office door in order to retrieve their brooms, and fled Hogwarts. The school has not yet quieted down."

"How is it these children were able to escape, and you are not?"

Snape opened his mouth, closed it again, and swallowed. "They had the connivance of Professor McGonagall."

"We would not have expected it of her. You get no such cooperation."

"She is looking for patterns in my trips here. She wishes to link the times you summon me to identifiable events. Tonight I told her that I needed something from my home in Lancashire. She gave me half an hour, but I managed to persuade her to increase it to forty-five minutes."

"You did well. We do not wish her to become too suspicious. Now, tell us what Potter was doing at about four-thirty this afternoon."

"I don't know. No, wait. He was watching the disturbance caused by the Weasleys."

"You are sure that was all?"

"No, Lord. I was not near him. I saw him on the stairs just before the Weasleys left the school."

"Perhaps you can explain why at about that time I saw him in conversation with Sirius Black. It appeared to be a floo-powder connection."

"No, Lord, I can't." Pain nudged him then, and Snape searched the memory for a clue. "He was on the second floor. That's where Umbridge's office is. Maybe he{\el}"

"Why her office and not some other hearth?"

"Hers is the only one not monitored by the Ministry. That was revealed when Fudge came to arrest Dumbledore, and McGonagall told the rest of us."

"So Potter took advantage of the disruption. Lucius, it would appear that your information was quite correct concerning Potter's ties. Unable to confide in Dumbledore, he turned to Sirius Black."

\sbreak

In a normal year, the school would settle down after the Easter break, fifth and seventh year students now studying frantically for their OWL and NEWT tests, and the rest almost equally concerned about exams. This was, however, no normal year. The example of Fred and George had touched off an epidemic of dungbombs and stinksap so fierce that students were walking through the upper corridors with bubble charms protecting their heads. Never before had Snape been so grateful that his rooms were in the dungeons.

The worst hit of all was Umbridge. In addition to having to deal with the pranks, she could not get rid of the swamp in the fifth floor corridor, and neither Flitwick nor McGonagall would admit to being able to do so. Snape was relieved that he wasn't asked. Somehow a large number of the employees of the Ministry seemed to think that Professors were as compartmentalized as their subjects, and never suspected a Potions teacher of being an expert spell caster as well.

The next weekend was the last in April, and Snape once again apparated into Croydon. He was taken directly to the Dark Lord where Malfoy and Bella were already in conference. The air seemed charged, and Bella looked murderous.

"Stand before us, Severus," said the Dark Lord. "We wish you to reach into your memory once more for the benefit of these two servants."

Snape relaxed at the speaking of his name, a clear indication that whatever was happening, the Dark Lord was not angry with him. "Yes, Lord," he replied.

"Speak again the words of the prophecy which you overheard."

Ignoring the intake of Bella's breath, Snape recited, "The one with the power to vanquish the Dark Lord approaches{\el} Born to those who have thrice defied him, born as the seventh month dies{\el}"

"Is this the whole prophecy?"

"No, Lord. The speaker was in a room on the other side of a door. I was interrupted and pulled away from the door, and so did not hear the entire prophecy."

"Who was in the room?"

"Professor Dumbledore and Professor Trelawney."

The Dark Lord's red eyes turned to fix on Bella. "You will speak again your advice to us."

"It's too dangerous to try to penetrate the Department of Mysteries. If our people are discovered, our secrecy is compromised. And in any case, only three people can take the sphere. I say we send our operatives against those who heard it and force the information from them."

"Severus?"

"We're speaking of three people who heard the prophecy. I'm one, but I didn't hear the whole thing. Another is Trelawney, but she remembers nothing of it, and in any case won't leave Hogwarts, and we can't enter to pull her out. The only other is Dumbledore, and I doubt he could be taken without exposing our whole operation, and even if it were possible, he could not be forced to talk."

"Do you see, Bella? Severus shares Lucius's view of this matter." The Dark Lord now turned to Malfoy. "You will speak again your advice to us."

"Entering the Department of Mysteries requires more patience and better preparation, but in the long run it is safer and less liable to be detected. Since the prophecy concerns Potter, he could be induced to enter the Department and take it. We could then take it from him."

"Severus?"

"It is the same problem as with Trelawney. Potter cannot leave, and we cannot get in."

"You can get in."

"Only with the permission of the headmaster or deputy headmistress. And I could not get out again without the same permission."

"Lord," said Malfoy, "my son Draco has told me there is another way to get Potter out."

Puzzled, Snape turned to stare at Malfoy, not understanding what he was talking about. "No, Severus," said the Dark Lord, "look at me now."

Eye contact firmly established with the Dark Lord, Snape listened as Malfoy explained. He knew he was being tested, and let some of his nervousness show.

"Two years ago, there was an incident in Hogsmeade. Potter didn't have permission from his guardians to go into the town, but he managed to make it anyway using some kind of invisibility charm. He attacked Draco. Draco knew it was Potter, however, because he saw Potter's head. He reported this to Professor Snape."

At Malfoy's first sentence, Snape remembered the incident and himself chastising Potter for taking chances with his life at a time when Sirius Black was loose. He allowed this memory to surface as he listened, letting the Dark Lord see it in its entirety before Malfoy finished.

"So, Lucius, it appears that once again your information is correct."

"Lord," Malfoy continued, "I again advise that we continue with the dream contacts, trying to make Potter desire to find what's in the Department of Mysteries. If that continues to be unsuccessful, we've lost nothing except a small amount of time. Then we can try to lure him out by other means."

"What other means, Lord?" asked Bella.

"Lucius has received information from a source that we do not wish known that the person most precious to Potter is your cousin, Sirius Black. We shall use this cousin of yours as bait."

"How do we find him, Lord? Sirius has been in hiding since he escaped from Azkaban."

"Tell Bella and Lucius, Severus. For whom does Sirius work now?"

"For Dumbledore."

"And where can he be found?"

"Lord, you know I can't say. I can't even think it."

"Forgive me, Lord, but if we can't get our hands on Sirius, what good is Lucius's plan to us?" Bella was sneering at Lucius in ill-hidden triumph.

Malfoy broke in. "Even without his person, we can still project an image. The image may be enough."

"Lord," cried Bella. "What if I can bring you the person of Sirius Black? Wouldn't that be better?"

"Then, Bellatrix, you would be most dear to us."

The session with the Dark Lord was a long one, though for most of the time Bella and Malfoy argued the same points again and again while Snape kept quiet. By the time they were released it was clear that the Dark Lord supported Malfoy. It was also clear that both Bella and Malfoy were upset that Snape hadn't taken sides more strongly, and that both believed he could be persuaded to.

Malfoy was first, as he walked with Snape up to the laboratory. "Thank you for agreeing with me that Bella's plan was foolish."

"I wasn't agreeing with you. I was stating my own opinion. It happened to coincide."

"Thank you, anyway. Bella can get a little crazy sometimes. She seems to think kidnapping and torturing half of England can be done without calling attention to ourselves. I keep advocating a more subtle approach, but Bella keeps insisting that her way is quicker."

"I'm the slow but steady type myself. But that's also a coincidence."

After Malfoy left, Bella arrived.

"You didn't play nicely this evening, puppy dog. Mommy's not happy."

"We've had this conversation before. I have one master here."

"And you want to serve that master to your best ability. So you should see that my way is best."

"Your way has a tendency to be reckless. Sometimes you go too far and your efforts become counterproductive."

"When has that happened. Name one occasion."

"The Longbottoms."

"That's ancient history. How about something more recent?"

"There isn't anything more recent. You've been out of Azkaban for less than four months, and you've been kept on a tight leash. It isn't like you've had the opportunity to get into a lot of trouble."

"You don't trust me, do you, puppy dog? After all I've done for you."

"Believe me, I remember everything you ever did for me. Or to me."

"And it will keep getting better. Phina sends her love."

"Now you're lying."

Bella pouted, then left, her eyes cold and calculating, leaving Snape with the feeling that she would like to see him on a platter with an apple in his mouth. \emph{Steady, Severus. Stay on her good side. You don't want her for an enemy if her star starts to rise.}

Phina didn't come that evening, though Snape hadn't really expected her to. He wasn't worried. If the pattern held true, the next weekend would be a very pleasant one. Right now he wanted some time to himself to decide how best to impart all this new information to Dumbledore.

At breakfast the next morning, Snape passed McGonagall on the way to his own seat, whispering as he did so, "I need to talk to Dumbledore." McGonagall replied at the end of breakfast, walking openly to Snape's chair.

"I have a job for you, Professor."

"On a Sunday?" Snape asked, pretending to be offended.

"There's a shipment of \emph{Bombyx mori} corpses due in today at Hogsmeade. The shipper can't guarantee the exact time since they're coming in from China. You ordered them, you receive them. Sometime between one and four o'clock this afternoon."

"But Professor! I have work{\el}"

"You ordered them, you be there to receive them."

Umbridge scurried over a moment later. "\emph{Bombyx mori}," she asked, "what's that?"

"Silkworms. They boil the cocoons to use the threads for silk. The boiled larvae are used in potions."

"Oh. I guess you have to be there."

"Of course. And I was going to use the afternoon for reviewing student files. Of all the rotten luck."

\sbreak

"They're talking about kidnapping Black to lure Potter to the Department of Mysteries. I think you should tell Potter."

"Who will tell him? You? He would never believe you." Dumbledore peered at Snape over the top of his glasses. "None of the rest of us can enter Hogwarts."

"McGonagall can tell him."

"Let me be more explicit. I do not think it is wise to let Potter know. We know that he has not yet learned occlumency. We know that you, for whatever reason, will not instruct him further, though even that might not affect the outcome. We must suspect that soon, if not already, Riddle will access Potter's mind and learn these things from him. Potter must be kept in ignorance for all our sakes. I shall alert Sirius and the others. Going into Grimmauld Place may become dangerous for a few weeks."

After his conversation with Dumbledore, Snape also alerted the Inquisitorial Squad to keep their eyes on Potter's comings and goings. One could never be too sure.

The next Saturday was the first in May. It was important for two reasons, first because Snape expected to see Phina again, but earlier and also important, because Slytherin was playing its last Quidditch match of the season against Hufflepuff.

Since the beginning of April, the Slytherin team had been searching for substitutes. First Montague was put out of action by the toilet thing—an incident that left him confused for weeks—then Warrington broke out in hives that resembled breakfast flakes. The other team members were scrambling for replacements.

In the end it was close. Hufflepuff won by only a few points, and Snape cheerfully paid off his bet to Sprout. Only one game was left, Ravenclaw v. Gryffindor, and Slytherin still had a chance to win the cup.

And then there was Croydon. It was Saturday, it was May first, and Snape was looking forward to Phina walking into his laboratory. She did not disappoint.

"Hi there, short dark and sexy. Long time no see."

"And where have you been?"

"You mean we still have illusions? Let me dispel them. Last week you were radioactive. The Malfoy isotope has a half-life of{\el}"

"You're not supposed to understand any of that."

"Because I work for Bella, I'm supposed to be stupid?"

They apparated to Phina's flat in the West End. Once again she opened and poured a bottle of wine. Once again she pulled Snape to her as they played the little kissing game. This time Snape, with the wisdom that comes of no longer being a novice, was able to anticipate some of her moves.

This time, however, the fact that Phina was out for big game could not be lost on anyone. To say that the first encounters of the evening were highly satisfactory was an understatement.

"I have to be back at Hogwarts before eleven."

"That gives us a few hours. Want me to show you something even more fun?"

"Let's wait on that. You may be trying to set a personal record, but I'm not."

She filled the glasses again, letting him watch her. "What are you feeling for me now?"

"Longing."

"At least it begins with an L. Didn't you ever love anything in your life? What about your parents?"

"What about them?"

"Your mother. You must have had some feeling for her."

"She was a strong woman and a creative witch. I depended on her and respected her. And I was a little frightened of her." \emph{And I was closed off so completely sometimes even she couldn't read me, but you, dear Phina, will never hear the word `occlumency' from me.}

"And your father? Oh, sorry. He was a muggle, wasn't he?"

"Don't be embarrassed. I'm not. Besides, I'm beginning to suspect you're not a pureblood either."

"How dare you! I'm a member of the Black family! We're all purebloods."

"Not all. There are a few cousins I've heard of{\el}"

"Wait now. What makes you think I'm not a pureblood?"

"I can't imagine any pureblood witch or wizard mentioning the half-life of radioactive isotopes. Most of them can't use a telephone. Do you know about Albert Einstein, too?"

"Is that a name? Seriously though, I think I just like things that are destructive. Radioactivity and atomic bombs and missiles with nuclear warheads."

She started tickling then, and the conversation about science was submerged in more important things. Later, they resumed talking.

"How about affection or tenderness? Or jealousy? Do you feel jealousy? Protectiveness?"

"No, you're too strong and{\el} dominating. About everything. I admire the way you just reach out and grab what you want, and your enthusiasm."

"Then why don't you like cousin Bella? She's like that. She throws herself totally into everything she does. I'd think you'd want someone strong and decisive advising the Dark Lord. Not like that weak, waffling Malfoy."

"I knew we'd come around to Bella and Malfoy eventually. Strong and dominating isn't always wise."

"I'm just going to have to work harder with you, aren't I?"

"I'm looking forward to it."

Snape made it back to Hogwarts on time to enter without a problem. He found himself musing about the future and wondering if, after everything was over, there could still be a place in his life for Phina.

May brought a lessening of pranks and more serious study. Snape was very pleased with his seventh year Advanced Potions class. Every student was certain to achieve an Outstanding or an Exceeds Expectations on their NEWTs. Snape's classes had a reputation for scoring above average, even on the OWLs, and the sixth and seventh years were introduced to the fine art of modifying and improving potions, having the benefit of their professor's long experience doing both. This was one of the reasons Snape would only accept into those classes students who scored an Outstanding on their OWLs.

Which, along with memories of his evenings with Phina, was one of the things putting Snape into a relatively good mood. It was absolutely certain that he would not be seeing a large number of his least favorite students next year. Potter, Weasley, and Longbottom would be gone, as well as Crabbe, Goyle, and possibly even Malfoy, though that was less certain. Granger would certainly continue, but might be easier to work with in a group where she was more challenged and faced stiffer competition.

Snape continued to stay away from Potter as much as possible. He did not want to be at the forefront of Potter's mind on the day the Dark Lord was finally able to see Potter's thoughts as well as the scene before his eyes. Interestingly enough, Potter seemed to be doing better in his potions work, though nowhere near good enough to hope for an Outstanding on his OWL.

On the Saturday just before the middle of May, Snape was again called into the interview chamber. He entered in the middle of Bella's report.

"{\el}was there. Completely gone."

"You are certain of the location."

"I've known it all my life."

"You have our authorization to assign observers to the place. Do not act without express permission. There are other things being planned of which you are not aware."

"Yes, Lord." Bella turned, nodded to Snape, and left.

"Potions master."

"Yes, Lord."

"We shall need new stocks of medicines and healing potions. Especially those for injuries caused by spells. You will start at once."

"Yes, Lord."

Snape checked first with the clinic to find out what was most lacking, then went to his laboratory and began laying out the necessary ingredients for about a dozen different potions. It was the part of his work he could take the most pride in—the part that healed rather than harming.

Phina looked in, but seemed already to know that they would have very little time together. "Will you be finished before eleven?" she asked.

"If all goes well, by ten."

"I wanted to ask you a favor."

"Depends on what it is."

"We started out with self-defense classes. I could use a refresher course."

"You have a desk job."

"Now why are you so sure of that? Just because I didn't go out into the field last time?"

"Admit it. The lessons were a ruse to get close to me."

"Right you are, Sherlock. And it worked."

"Now you're doing that half-blood thing again. When did you ever read Sherlock Holmes?"

"Oh, that's what it means! I just heard people say it. I never read anything. So, how about a refresher? We won't have time to go to my place."

They spent the last hour in the training room, reviewing the falls, the holds, and the defensive spells. Phina was still in excellent form, and initiated a game in which every time she blocked a spell, she got to steal a kiss. Snape was conscientious enough about his work to give her a hard spell to block from time to time. He didn't want her to get sloppy.

On arrival back at Hogwarts, Snape sent Dumbledore a patronus telling him that Bella and her Death Eaters were planning some surveillance and possible action that might center on Grimmauld Place. He advised extra caution for the next few weeks.

The third weekend in May, Malfoy came to the laboratory.

"Want some advice? Stay as clear of that woman as you can."

"Which woman are we talking about now?"

"That Lestrange woman. She's dangerous to everyone around her."

"Lestrange woman? Do I sense a shift{\el} an emotional distancing? She is, after all, your sister-in-law."

"Cissa won't see her. They spoke once after the Azkaban breakout, and now they won't have anything to do with each other."

"I think I'll forbear comment."

"Sometimes I think she won't even obey{\el} him. He's warned her not to act without orders, but she's straining at the leash, and we can't trust her to be sensible."

"I'll be careful."

Malfoy left, and Phina came in. "How late will you be tonight, Severus?"

"Another hour or so. Were you planning something?"

"That would give us a little time to pop over to my place. I was hoping to spend a while together."

They apparated to the West End around nine o'clock, but this time Phina put on music and they tried a little dancing, with considerable success. Phina was quieter and gentler than before, and for the first time Snape began to feel that this was indeed someone he wanted to protect. His gratitude for what she'd done for him was melting into a sense of tenderness, even affection, and it was no longer possible to imagine not seeing her every Saturday. They spent the last few minutes together in contented companionship, and then he apparated back to Hogsmeade.

The following Thursday, McGonagall received an urgent summons from Dumbledore. "We're leaving for London right away," she whispered to Snape at supper. "Something's happened."

Members of the Order guarded all the streets entering into Grimmauld Place. It was as if the small square was a fortress. Everyone who entered was watched carefully, so carefully that Snape was afraid the local muggles might call the police.

"Most of us," said Dumbledore when all had arrived, "already know what has happened. For those coming in from Hogwarts and the Ministry, we have had a little excitement here today. An attempt was made by a squad of Death Eaters to attack and kidnap Remus Lupin. We believe that the real goal was to lure Sirius Black out of this house so that they could capture him."

After waiting a moment for the babble of rising concern to calm down, Dumbledore continued. "Fortunately, we were forewarned of the possibility that this might happen, which is why all of you were cautioned to exercise extreme care in arriving and departing from this place. We had sentries stationed and were able to call in reinforcements before the Death Eaters could accomplish their purpose. For this advance notice we all owe thanks to Severus."

The others nodded, and Shacklebolt and Weasley stepped across the room to shake Snape's hand.

"Now," Dumbledore went on, "we must redouble our guard. We have escaped this first attempt unscathed. There may well be another. This is particularly true since apparently we inflicted some damage. At least two of their operatives fell during the fight, though as they were carried out by their colleagues, we have no way of knowing the full extent of the damage we caused. There was, however, blood on the pavement. This could well make them both more intent on striking us, and more careful in how they perform it."

At that moment, the mark began to burn. Severus's arm jerked at the sudden pain, causing the others to shift their attention to him.

"I thought that might happen," said Dumbledore quietly. "You had best go."

Croydon was in an uproar. Malfoy himself met Snape at the entrance. "You don't have to go to him, he doesn't want you. He's with Bella now, and he's furious. There's been a fight, entirely against orders. She'll be lucky if she makes it out of this one."

"Why was I sent for?"

"You need to go to the clinic. There've been injuries, bad ones, and the medics need more help. You're to see what potions they need and to assist in the healing. You are something of a healer, aren't you?"

Snape raced upstairs to the clinic, and was met at the door by one of the healers. "Good! You're here! We have one damage to a skull, still unconscious, and another severe blood loss. Can you get{\el}"

Another healer came over. "We'll only need the medicine for the concussion—the blood loss patient just died."

With a nod of understanding, Snape was out the door and headed for the lab. Unconsciousness for this long meant almost certain neurological damage and required special regenerating potions. Luckily they probably had a lot of time. It was not the sort of injury that killed quickly, not like losing large amounts of blood.

Malfoy came up to the laboratory while Snape was working. "Are you all right? I just came from the clinic. This must be a rough night for you."

"People get injured. Healers heal them. It's a job."

"You scare me sometimes, you know."

Snape paused in the decanting of a nerve regenerator. "Why would I scare you?" he asked finally.

"You can be so deadly cool about things that would floor other people. Almost as if it didn't mean anything to you. Would you be this calm if something happened to me?"

"Maybe. Probably not. But then, I know you."

Malfoy was silent. Too silent. Snape stoppered the flask of potion with exquisite care and checked the others, already finished and waiting to be taken to the clinic. The lucidity of the moment was breathtaking, and he marveled at the sharpness of the colors and the clarity of the light, and the revelation that hovered between them in Malfoy's silence.

"I'm sorry, Severus. Didn't they tell you?"

"Why should they? They weren't aware that I knew her." Inside he was locking down, closing up, every door slamming shut.

"Then you did know."

"Not until this moment, no. What happened?"

"They're not sure. A cutting spell, but no one knows where it came from. She was in the front, doing all right, and then she started moving forward. It got her in the throat. Sliced the artery. She never had a chance. She may have been dead before they got her to the clinic."

"I need to get these medicines over there."

"Can I help?"

"Yes, if you would take those four. They're for the confusion cases. I'll get the rest."

Both men were quiet on the way to the clinic. There Malfoy drew one of the healers aside and whispered quickly. The woman nodded.

"Would you like to see her?" Malfoy asked. "I told them you were a friend."

They had cleaned up the blood and wrapped a cloth around her neck, so she looked quite peaceful, except that her skin was very pale and waxy looking. Serene. It was a good word. She looked serene.

Snape glanced over at the medics and waited until they noticed him. "Do you need any more potions this evening?"

"No, this will do very well. I think he's responding already. Thanks."

It wasn't eleven yet, still several hours to go. Come to think of it, Snape wasn't sure what time McGonagall would have the shields down for him. She might even be with Dumbledore. Snape wanted some time to think, but first there were one or two things{\el}

"Lucius?"

"Yes, tell me what I can do."

"You said earlier that the action was against orders. What did you mean?"

"The Dark Lord told Bella to set a surveillance team, but not to move in unless she got the word from him. He didn't want other plans disrupted by badly timed action."

"So he didn't order it."

"No. This was all Bella's doing. She'll be `discussing' it with him for a long time tonight."

"Who else was there?"

"A very motley crew. Amycus and Alecto, Fenrir, Gibbon, some people from the branch offices I don't know. About ten in all."

"The spell that hit her, was it enemy fire or friendly fire?"

Now Malfoy looked uncomfortable. "We don't know. Things were pretty confused at that point, and I've gotten conflicting reports. We may learn more after Bella's able to talk again."

"Let me know what you hear."

"I will."

Snape went back to the laboratory where he turned out the lights and sat by the windows, watching the muggle trains speeding past in the darkness. Just before eleven he apparated to Hogsmeade. McGonagall must have assumed the same as he did, for the shields went down at precisely eleven, and Snape went to his rooms without having to speak to anyone.

The next morning Snape didn't go to breakfast. Instead he paid an inordinate amount of attention to setting up his classroom for his Potions lessons. They were almost at the end of the term, only one week of classes to go, then a week of review, and then exams. The routine was a help, and he'd locked himself down so tightly that he wasn't thinking of anything else.

The morning went smoothly, and Snape was spending the lunch hour in his classroom as well, setting up for the afternoon lessons when McGonagall appeared in the doorway. Snape continued his work without looking at her.

"Are you going to eat at all?"

"I wasn't hungry."

"Dumbledore said to watch your eating habits. No food is a bad sign."

"Dumbledore should mind his own business. As should you."

"Either they're feeding you very well at the `other place,' or something happened last night. And it is my business, and Dumbledore's. You're on staff here, remember."

"Maybe it has nothing to do with the `other place.' Maybe it's a Hogwarts problem."

"So you admit there's a problem. Dumbledore was concerned about the fight yesterday. One of the `problems' about your kind of work is that you know people on both sides. Do you know who was injured yesterday?"

"Yes."

"And?"

"It isn't important."

"Now you've got me worried. You need to go out tonight and talk to Dumbledore."

"No."

"Why not?"

"There's only one place where we can talk, and I'm not going there. Not now."

McGonagall watched him for another minute, then turned and left. Snape was relieved to see her go. Having her ask questions was forcing him to look at things he didn't want to look at.

The afternoon also went smoothly. Everything was blessedly uncomplicated routine. Snape stayed in the classroom clearing everything up, cleaning, straightening{\el} Supper was half over when a silver shadow slipped under the door. For just an instant the ghostly phoenix hovered before Snape's face, and then Dumbledore's voice spoke in his brain.

\emph{Something has happened. You may want to talk about it. I am in the Shack, and am quite prepared to wait here all night.}

The phoenix vanished, leaving Snape with a decision, but not one that he had to make right away. He continued to straighten, arrange, put away, and clean for over an hour, while the image of Dumbledore in the Shrieking Shack brooded on the edge of his consciousness.

The long northern sunset was beginning to alter the light when Snape eased open the great front door of the castle and hurried across the lawn. Once on the path down the hill, he was sheltered by bushes. There he slowed his pace, still uncertain if this was what he wanted to do. The nearer he got to the Whomping Willow, the slower he walked.

A long stick sufficed to press the knot that froze the tree, then Snape ducked into the tunnel and paused. There was a sense of inevitability about his movements, however, and he was soon wending his way along the uneven stone floor, a Lumos spell lighting the passage.

The basement room was empty, but so still was the air in the Shack that the marks of the feet from the last time he'd been here were visible in the dust—the students, Lupin, Black, his own footprints, and the little rat feet of Peter Pettigrew. It seemed a century ago.

He climbed the staircase softly, making almost no sound. As his hand reached out to push open the door of the upper floor room, Dumbledore's voice spoke from the other side.

"Oh, excellent, Severus. I was hoping you would come."

Snape stepped into the room and looked around. The ancient bed with its hangings was still there, and Dumbledore had found or conjured a couple of armchairs and a small table which now held a tea service for two and a bottle of mead with the appropriate cups and glasses for both.

"Sit, if you feel like it, Severus," Dumbledore said, and gestured toward the empty chair.

"I think I'd prefer to stand."

"As you wish." There was an awkward silence. "I did rather hope you could fill in the gaps in our information about yesterday."

"That? You got eight of them. Only Bella and Fenrir escaped unscathed. The others were hit by confusion, stunning, and cutting spells. And one backwards spell that's driving the healers crazy."

Dumbledore chuckled. "It looks as if we did quite well. Odd thing, though. I do not recall that any of our people used a cutting spell."

"Maybe you just didn't see it. It was very effective."

"The Death Eater is badly injured?"

"The Death Eater is dead."

"Ah. I am sorry to hear that."

"Sorry to hear of the death of an enemy?"

"Sorry to hear of the death of any wizard. Or witch. It was a woman who died. A woman you knew."

"You didn't read that."

"Dear me, no. I am reading an obsidian wall. I do not want to get analytical where your private life is concerned, but only something really powerful could make you shut down like that. I might even hazard a guess as to who it was."

"Don't bother. I'm sure you're right, though I would argue that `powerful' isn't the correct word."

"No? Would `personal' be a better word?"

"Perhaps. I'll have to think about it."

"What happened?"

"There was a surveillance ordered at Bella's request. She—her name was Delphina Vaughn, did I tell you?—she went out as part of the team. Bella got impatient and sent them into action without authorization. There was a skirmish. You know the rest."

"Riddle did not order the attack?"

"No. He's still preferring Malfoy's advice over Bella's."

"Poor Bella. She will not have spent a comfortable night." Dumbledore seemed genuinely saddened. "And you. This must have been difficult for you."

"Define difficult."

Dumbledore sat back, his fingers steepled in front of his glasses. "She was a colleague of yours. You will forgive me, Severus, but one of the things that has always disturbed me is that you did not enter this business as a double agent. These people were once your friends, your coworkers. You have never had the chance to be impersonal where they are concerned. Did you not assist in the engagement of Lucius Malfoy and Narcissa Black? You cannot pretend to be indifferent."

Snape turned away, suddenly fascinated by the simple workmanship of the solid paneled door.

"Severus{\el}" Though Snape did not face him, Dumbledore continued. "You shared something with this{\el} with Delphina. Do not deny it, you were{\el} close to her. You must feel something. Please, consider what that something is, for her sake."

Snape didn't speak, so Dumbledore shifted the focus of his question.

"What was she like? I never met her. How would you describe her?"

The answer was a while coming. "Pleasant to be with. Never demanding. Never judging{\el}"

Dumbledore didn't respond, and Snape was drawn to fill in the silence. "She was independent, intelligent{\el} kind and gentle{\el} understanding{\el} silly sometimes{\el}"

"Did she ask about us?"

"Not once. She was there to woo me away from Malfoy."

"You question her motives."

"There was no question about her motives. She was doing a job. The odd thing was that sometimes I got the feeling that even in spite of the job{\el} she may actually have liked me. Especially the last time."

"Which was{\el}"

"Last Saturday. It was like she was trying to show me something{\el} what she was really like, or what she could be like{\el} I'm not sure." Snape suddenly walked over to the table and poured himself a glass of the mead. "Could she have been saying goodbye?"

"Possibly, though that would require a high level of premonition."

They were silent again, and Snape tossed back what was left of his mead, pouring another glass which he sipped thoughtfully.

Dumbledore broke the silence. "What do you feel now?"

"Empty."

"Do not be angry{\el} but what would you feel if you lowered some of those barriers?" Again the silence spread. "There, I apologize. I have gone too far."

When Snape still didn't respond, Dumbledore poured himself a cup of tea. He wasn't looking at Snape when he asked, "Who else among your colleagues in London will remember her fondly?"

"I don't know. No one that I can think of. I don't know anything about her immediate family. To Bella she was a tool, as least that was the impression I got. To Malfoy she was an enemy. The healers didn't even know her name, so I don't think she had much to do with the others."

"Then insofar as we know, you are the place where the memory of her true self resides. What, if you will pardon me, will you remember about her?"

"She was one of the best self defense pupils I ever had. It doesn't seem to have done her much good. We went to the theater once—`Macbeth.' And to dinner." As Snape named the occasions, images floated up into his conscious mind of Phina's intent face as she watched Shakespeare's witches, and her laughter trying to block his view of the belly dancer. And the feel of her hands{\el} "She had very gentle{\el}" He turned to look through the curtains at the houses of the village, not wanting Dumbledore to see his face.

Dumbledore came to stand beside him, a hand resting lightly on Snape's shoulder. "It does not have to be all at once. Let the memories surface a little at a time, as you are ready for them. Sorrow is our best way of honoring the dead." They stood quietly for a few minutes. Then, "Will you try to find out why she died?"

"Does it matter? She was a soldier in a war. That's what happens in wars."

"What if you found that I had killed her?"

"You didn't. You'd never use that kind of spell. But it wouldn't matter. It isn't like a battle gives you a lot of time to make a decision."

"Then maybe you should find out. For your own peace of mind."

After awhile, Snape glanced over at Dumbledore. "I have another question. It's on a different subject, though."

Dumbledore looked down at Snape. "Very well. Ask."

"The defenses controlling access to this shack, are they part of the defenses that surround the grounds of the school?"

Now Dumbledore was silent for a moment. "I am not certain that I wish to answer this question," he said finally.

"They're not, are they? Look, I know I was the reason you put in these defenses. I got onto the grounds too easily back{\el} then. But I have a real problem now. Before you left I had a backup way of getting out at need. If I couldn't ask you, I could ask McGonagall. Now you're gone and Umbridge keeps watching McGonagall. What happens if I'm summoned, really summoned, and I can't get out?"

"I see. That would indeed be a difficult position to be in. You would, of course, never reveal it to anyone else. Who knows of it? Me, you, Madam Pomfrey, Lupin, Black, Potter, Granger, Ron Weasley, Pettigrew I am afraid{\el} Who can get in and out from this side? Me. Very well, Severus. I shall give you the codes. Do not use them except at great need. To open the shack to enter or leave, you say \emph{Patefacio tugurium}. To close it again, you say \emph{Claudo tugurium}."

"Thank you, Professor."

"Well, I suppose I should be off now. It is getting quite late, and we do all need our beauty sleep. You will take care of yourself, will you not, Severus?"

"Yes, sir. And thank you for that, too."

Climbing to the top of the hill, Snape turned south and searched the starry sky. It took only a moment to locate the constellation Delphinus, and for a while he contemplated the diamond formation of the dolphin's body and its tail of stars before entering the castle.

He started to cross the entrance hall to the dungeon stairs, but was stopped by McGonagall's voice calling from the Great Hall.

"There you are, Severus. Have you a moment?"

She was sitting at the foot of the Gryffindor table, and Snape was surprised to see that she'd saved a quantity of food from supper. Suddenly he was ravenously hungry, and immensely grateful for the late-night feast. He walked over to the table and sat facing her.

"Will you join me?"

"Well, unlike you laddie, I've actually been eating my regularly scheduled meals. But I'll have a bite and a sip of wine to keep you company. Go ahead now. Eat."

Snape did, and the food was delicious. Neither of the two talked for several minutes, but when Snape glanced up at McGonagall, she seemed quite pleased that her offering was being accepted with such relish.

"Have you given any thought to tomorrow, Severus?"

A piece of chicken stopped halfway to Snape's mouth, and he said with foreboding, "What happens tomorrow?"

"Final Quidditch match of the season. Us against Ravenclaw. Who d' ye favor?"

"You have a Keeper and two Beaters culled from the ranks of the Keystone Cops, and you want to know who I favor?"

"I take it your money's on Ravenclaw."

"Usual bet?"

"Usual bet."

The usual bet between them was a knut, but it was the principle of the thing. Snape and McGonagall wished each other a good night, and he went to his rooms. Before going to bed, however, Snape brought to mind the first time he'd seen Phina, the day Bella brought her to the lab and demanded defense training. Then he slept soundly for the rest of the night.

By long tradition, Snape sat with Flitwick during the match, while Sprout supported McGonagall. The fate of the Quidditch Cup hung in the balance, for if Ravenclaw won, the cup would return to Slytherin. The Slytherin stands vibrated with excitement, `King Weasley' buttons glittering on their robes, ready to burst into song at the first sign of trouble for the Gryffindor Keeper.

And at first it went predictably well, Ravenclaw scoring an easy goal that Gryffindor was unable to block. Then, out of nowhere, something seemed to electrify Gryffindor's Keeper, another easy one was suddenly deflected from the ring, and Flitwick was dancing up and down on the bench screaming with frustration, "Feint right, you fool, right! He saw that coming a mile away! You miss another goal and your broomstick will be supplying BOAC with toothpicks!'

Resolving to discuss the history of British Airways at another time, Snape focused on the match. The Snitch flickered here and there, but was mostly in hiding. Bludgers were ahead of Beaters by a seven point margin, and while Ravenclaw easily kept Gryffindor from scoring, the game was now being played at the Gryffindor rings. Attack after Ravenclaw attack was set up and run down the pitch to be deflected by the Gryffindor Keeper.

The red and gold stands erupted in small outbursts of cheers that quickly merged into one gigantic roar, drowning Slytherin's well-rehearsed `Weasley is our king' in a tidal wave of `WEAS-LEY! WEAS-LEY! WEAS-LEY!' McGonagall rose to her feet, fists raised over her head, arms pumping to the rhythm of her house's chant while Sprout brandished a red and gold pennant above them. Snape watched the whole scene in awe. \emph{Whoever would have thought a purely defensive game could be so exciting? Phina would love it.}

Then, in a twinkling of speckled light, the Snitch was there. Blue and red Seekers spun towards it like hawks after the same rabbit, surging up and diving down in pursuit of the precious shimmering orb, fingers outstretched in desperate longing until{\el} in a day of perfect triumph for the House of Weasley, the Gryffindor Seeker shot upwards, the Snitch held aloft in her hand. Gryffindor house exploded.

The players settled groundwards as the stands spilled Gryffindor and Hufflepuff students onto the grass, while Slytherin and Ravenclaw exhibited a more decorous behavior. McGonagall was gracious enough to advance halfway, then waited for Flitwick and Snape to approach her. "You owe me a knut," she said, after accepting Flitwick's congratulations.

"The show was well worth it," Snape replied as he handed over her winnings.

Supper was marred only by the general disappointment of the Slytherin students, sympathy with whom prevented Snape from sharing McGonagall's joy, by Umbridge's clear disapproval of the raucousness that followed the game, and by Snape's own anticipation of his impending trip to Croydon. That night he did not want to leave Hogwarts.

Croydon, however, was peaceful. Bella was nowhere around—recuperating, it was said, from her interviews with the Dark Lord. Malfoy was closeted with their master discussing ongoing plans. Snape spent a few hours in the clinic with the medics, evaluating the injured who were not responding well to treatment, and speculating on the spells used against them and the possible adjustments to the potions used to heal them.

And somewhere, on a level that was neither conscious nor subconscious, Snape kept expecting to see Phina, and was repeatedly disappointed when he remembered that he could not.


