% A Difference in the Family: The Snape Chronicles (Rannaro)
% If You Are Ready{\el}

\chapter{Masks and Unmaskings}

\emph{It was dark{\el} dark{\el} and the floor beneath his knees was cold. Hooded figures stood around him, hemming him in, menacing{\el} Red eyes bored into his own, dead eyes, eyes that steal your soul.}

\emph{"Read him!" the red eyes cried, and Moody stepped forward, grinning lasciviously. The blue enchanted eye began to rotate like a drill. "You be sure to tell me if you ever decide to retire. The guest room's been ready for some time," the eye sneered at him as it drilled into his brain. Then the eye grinned and bared its teeth. He looked to the Dark Lord for help, but the Dark Lord was aging, growing a beard, becoming Dumbledore, who shrank and got younger and became Potter, and it was Potter drilling into his brain.}

\emph{"Tea?" Potter said, and handed him a cup, but Bella held the cup, and they were sitting in a comfortable room with soft chairs and a fire.}

\emph{An angry young man with blond hair and freckles sat opposite him. "Whoever is giving them information should be punished. Whoever tries to leave{\el} punished. Whoever isn't punished{\el} punished." The young man leered at him. "I thought I might interest you in that vacation I'm always on about. Right now it's a bargain."}

\emph{He looked at his tea, which was a gray-colored sludge. "I can't drink this," he said.}

\emph{"Of course you can, dear," said Bella, "we got it from your office. You can be Potter."}

\emph{"I don't want to be Potter. I want to be me."}

\emph{"Don't be silly. Everyone knows you have to be Potter."}

\emph{They gave him a huge water skin full of the gray sludge, and he had to drag it around with him, drinking from it all the time to stay Potter. Moody held the neck of the skin to his mouth, cackling "You never know. You never know. Look for me in the gloamin'"}

\emph{Then he was looking—in a mirror. Potter's face looked back at him. "Mirror, Mirror on the wall, who does the Dark Lord fear most of all?" Potter's face began to narrow, and hair to grow, and he was looking at himself in the mirror. The Dark Lord watched him from behind, saying, "He will be killed, of course."}

\sbreak

Snape's eyes opened wide in the darkness. Killed{\el} of course. He listened for sounds of them coming for him, hearing nothing but silence. Slowly he remembered. \emph{I'm in bed. In my own room. It was a dream.}

It was about four o'clock. Unable to go back to sleep, Snape got up and fixed a cup of tea, then sat in his office by the fire. It wasn't a real fire, since it was getting too warm during the day to have one, but staring into flames, even magical ones, now helped Snape think. He was trying to recall the ephemeral, wispy strands of the dream that had wakened him.

\emph{Potter was in it. I had to be Potter by drinking{\el}} Pieces began to click into place. \emph{What if all my problems with Moody are caused by the fact that it isn't Moody? Maybe he doesn't need Polyjuice potion to turn into someone else. Maybe he needs it to stay Moody! Moody was attacked the night before he was supposed to come here. What if the attack was successful?}

Of course, that raised two more problems. Where was the real Moody, and who was impersonating him? \emph{Who's been missing since before Christmas? Who went missing just before someone started stealing boomslang skin and bicorn horn from me? Bartemius Crouch.} Except that Crouch and Moody had both been at the ceremony welcoming Beauxbatons and Durmstrang, and choosing the champions. \emph{Okay, so there are holes in the theory.}

Still, it explained so much. Crouch had always been a fanatic hunter of Death Eaters. He'd sent many to Azkaban without trial including, now that Snape thought about it, Sirius Black. He'd gotten Karkaroff, but Karkaroff managed to be released shortly after. He'd tried to get Snape, but Dumbledore had stood in his way. He did get his own son, who died in Azkaban, and he'd been more than a little disturbed ever since.

\emph{What if the Death Eater demonstration at the Quidditch World Cup pushed him too far? Didn't Percy Weasley say at the Yule Ball that he hadn't been right since then? What if he finally went off the deep end, knowing the Dark Lord is getting stronger, and Karkaroff and I would be in the same place at the same time? That would mean `Moody's' threats aren't idle—he really is after us.}

It still left the problem of Crouch and Moody being in the Great Hall together for the Goblet of Fire's decision, and later in November for the first task. Crouch and Moody had both been there for the first task. \emph{But if Crouch can become Moody, so can someone else. Maybe someone else became `Moody' at the beginning, and Crouch took over later. Which means instead of accounting for the actions of one crazy person, I have to explain two. More holes—can this theory really fly?}

\emph{I need to talk to Dumbledore.}

Dumbledore was not at breakfast, and the reason was soon apparent. Preparations were going forward for the third and final task of the Triwizard Tournament. Ludo Bagman was in and out between Hogwarts and the Ministry of Magic, and he seemed always to be closeted with Dumbledore during those times when Snape didn't have classes to teach. As the day wore on, Snape became more and more frustrated.

One of the problems was that he couldn't pin down his new theory. At times it seemed so clear and obvious that he couldn't imagine why he hadn't thought of it before. At other times he could see nothing but the holes and contradictions, and started to wonder if he should even mention it to Dumbledore. Snape was becoming so obsessed with the idea that Moody was Bartemius Crouch that he was having trouble concentrating on his classes.

Moody wasn't at breakfast, and Snape wondered if he was with Dumbledore and Bagman. He did show up just before lunch, and Snape on a sudden whim greeted him, "Top o' the morning to you, Moody me boy."

"You're cheerful today."

"It's a nice day."

"I've seen worse and will again. So will you."

"Pleasant thought. It just cheers a body up to talk to you."

Moody stared at Snape thoughtfully. "Insanity doesn't keep you out of Azkaban."

"Nor does innocence I understand. Have a nice lunch."

"You're not staying?"

"Not this time. But I'll be looking for you in the gloamin'."

Moody didn't reply. Shaking his head, he stumped off toward the high table.

\emph{Now, does that mean that he just doesn't remember, or that he doesn't want to banter, or that he's not the same person I had that conversation with back in August? Would Moody forget calling me `boyo'?} There was no definitive answer to that question

After supper, Bagman disappeared with a work crew from the Ministry in the direction of the Quidditch field. They were preparing something there for the Tournament. At that point, Snape started trying to see Dumbledore in earnest. He had no success whatsoever, since he kept running into Moody.

Going from the Great Hall upstairs, Snape was hailed from behind. "Aren't you going in the wrong direction?" Moody was grinning on the steps below him.

"I depends on where I'm going," Snape replied, and on the first floor turned towards the hospital wing. Once Moody continued upstairs to his office, Snape took another staircase, only to be met at the landing.

"We do seem to be running into each other tonight," Moody chuckled.

"Interesting coincidence," Snape answered.

Snape returned downstairs to think for a while then, around nine o'clock, started back up to the headmaster's tower. Moody wasn't waiting for him. \emph{Odd for him to give up so easily. Unless he was just trying to irritate me, or has something more important to do.}

The interview with Dumbledore didn't go well.

"I understand your concern, Severus, but really the only evidence you have is a dream, and the fact that a retired auror doesn't remember snippets of a casual conversation you had ten months ago. It is hardly a case. And since both Moody and Crouch were here together twice, you need to account for that. If you cannot, I can hardly accuse anyone based on what you have so far."

"But Headmaster, what about the missing ingredients? What about his sudden change in behavior towards me?"

"All explainable in less{\el} unusual ways."

"What about his ability to control the dark mark?"

"I will admit that is disturbing, but might be explained in some other fashion. Now if you will excuse me, I am busy with another matter."

Exasperated and deeply disappointed, Snape went to the door. As his hand touched the latch, he turned back to Dumbledore. Dumbledore stood in front of a black cabinet. Snape glimpsed the edge of what looked like a shallow stone basin, then left the office.

At the foot of the staircase, the hidden door slid open just in time to let Snape see Potter running hard in the other direction.

"Potter!" he shouted, and the boy skidded to a halt, then faced him. "What are you doing here, Potter?"

Potter came running back. "I need to see Professor Dumbledore! It's Mr.~Crouch{\el} he's just turned up{\el} he's in the forest{\el} he's asking{\el}"

\emph{How does he know about Crouch? Can he{\el} ?} "What is this rubbish? What are you talking about?"

"Mr.~Crouch! From the Ministry! He's ill or something—he's in the forest, he wants to see Dumbledore!"

The information, if true, shattered Snape's own theory. If Crouch were in the forest, ill, looking for Dumbledore, then he couldn't be Moody. Snape suddenly wanted the chance to check this before Dumbledore found out.

"The headmaster is busy, Potter."

Potter's voice rose to a scream, "I've got to tell Dumbledore!"

"Didn't you hear me, Potter?"

The boy was beside himself. "Look, Crouch isn't right{\el} he's{\el} he's out of his mind{\el} he says he wants to warn{\el}"

Behind Snape the door to the hidden staircase slid open , and Dumbledore stood watching the two. "Is there a problem?" he asked.

Potter immediately blurted out his story, and Dumbledore exchanged a quick, sharp glance with Snape. Snape looked down.

"Lead the way," Dumbledore told Potter, and the two were gone.

Snape was furious. Furious at Potter, furious at Dumbledore, furious at himself for being such a fool, and furious at fate for delivering Crouch to Hogwarts's doorstep at precisely this moment. Then, as he made his way down the staircases, Snape suddenly had another thought.

\emph{Was that why Moody didn't follow me that last time? Maybe something went wrong with the Polyjuice potion and he turned back into Crouch. Maybe that's Moody and Crouch out there in the forest, half crazy.}

Snape ran down the rest of the stairs and out onto the lawn. It was dark. There was no moon, and the stars were half obscured by clouds. Snape looked down from the top of the hill toward the forest. He had no idea where Potter and Dumbledore had gone. Then suddenly a streak of silver light left the trees and sped straight towards Hagrid's hut.

\emph{They've found something. That was Dumbledore's patronus. Whatever it is, they need Hagrid's help.}

Snape debated with himself a moment, then returned to the castle. It was too dark to see anything, and he couldn't go down. After their heated conversation earlier, he was sure Dumbledore would get the wrong impression if it appeared Snape was trying to interfere. \emph{If he wants or needs me, he can send for me.}

The next morning it was as if nothing had happened. Moody was at breakfast, Karkaroff and Madam Maxime were angry about something, and there was no sign of the mysterious Crouch. It was as if the previous night hadn't happened.

Snape was going toward his classroom after breakfast when Dumbledore came from behind and walked with him.

"I understand you had a conversation with Moody last night after I left with Potter."

Snape stopped to stare at Dumbledore, but Dumbledore took his elbow and steered him across the entrance hall toward the dungeon. "I take it that comes as a complete surprise to you."

"I didn't see Moody at all, and I certainly didn't speak to him."

"He met us down in the forest. Crouch had been there—both Potter and Krum saw him—but he has now vanished. Moody arrived very quickly after, and said you had told him about Crouch being in the forest. Now why would he say that if it was not true?"

"Headmaster, I have no idea."

"Thank you, Severus. All of the events of last night have given me quite a bit to think about."

Whether it was Dumbledore's doing, or mere coincidence, or nothing more than Snape's subjective perception, but the next few weeks went very smoothly and quietly. To begin with, of course, everyone was preparing for exams. Teachers were racing through the curriculum, students were studying frantically, and the whole school was like a string of racehorses in the stretch. \emph{Interesting how frantic intensity can have a pacifying effect.}

The second element contributing to calm was that Dumbledore seemed to have replaced Snape with Moody in the Triwizard Tournament. Snape was no longer called in on planning sessions, but Moody seemed to be spending large parts of his free time in Dumbledore's office.

Snape did not mind this in the least. Firstly, it gave him more time for his classes and the upcoming exams. Secondly, it was an indication that Dumbledore wanted to keep Moody on a close leash. The missing Crouch had not yet turned up, and Snape was pleased to see that Dumbledore was not going to let Moody prowl around on his own.

The third thing was quite unexpected. For reasons unknown to Snape, Potter decided to spend the last weeks virtually locked inside the castle and surrounded by friends who doubled as guards. The vast difference between this and his behavior the year before made Snape almost believe that the transition through puberty actually brought a minutely measurable increase in common sense. Almost.

All through June, the Quidditch field was changing. Hedges planted there at the end of May towered yards above the head by the time of the third challenge. Snape was at a loss to understand why the maze had to be so tall, unless it was meant to keep the spectators from seeing anything of the progress of the champions within.

\emph{That's even more boring than a game of Quidditch with a good seeker. At least the suspense will last longer.}

Hogwarts had been invaded by Ministry types over the Crouch business, and now, exams over and at the very end of the term, they were back for the third task of the Tournament. The families of the champions were invited to the school for the event. Snape was looking forward to meeting the Dursleys until he found out that the Weasleys had substituted for Potter's family instead. Though he did not know them well, he had considerable respect for any parents that had managed to survive Bill, Charlie, Fred, George, and Ron. Still, he wasn't sure they would have anything in common for the conducting of a conversation.

The dinner at the start of the third task was a gala banquet. Many of the teachers gave up their seats at the high table to accommodate dignitaries and families, and Snape was one of them. Sitting at Slytherin's table, it took Snape a half hour to realize that Moody was not in the hall.

Snape looked around, started eating, lost track, looked again a half hour later, and Moody was there at the Gryffindor table as if he'd been there all evening. \emph{When did he come in? I should have brickbats dropped on my head for a month of Sundays for not noticing!}

\sbreak

Potter and Diggory entered the maze. Then Krum, and then Delacour. The suspense was{\el} boring. Not for everyone, of course. Family members who watched the seconds tick endlessly by on a clock, while they were reduced to staring at an overgrown hedge, might nonetheless feel the tension, but Snape sincerely wished he were elsewhere. He rather thought a large number of the spectators agreed. Minutes grew into a quarter of an hour with no change.

Then there were muffled shrieks, the Beauxbatons girl crying out, and sparks in the air. Wizards went into the maze to assist her. A little later, another voice that sounded like Diggory, but the wizards that followed the sparks brought out Krum instead. And then for a long while there was nothing.

Suddenly, with the terrible fury of a bolt of lightning, Snape was summoned! From ease to searing pain, from calm to mind-numbing panic, was but an instant of time. The mark on his arm flamed with the intensity of volcanic lava. \emph{I must go! I must go! I must go to the Dark Lord{\el} I must surrender myself to him{\el} I must leave{\el} now{\el} NOW!}

The knowledge of his other duties stopped Snape and, pain notwithstanding, he hunkered down to wait. A glance at Karkaroff across the stands told him instantly that Igor had felt the beckoning, too. \emph{Run, Igor! Run now! Safety comes only with a strong heart and a good story. You have neither. I hope to God I have at least one of the two. I wish you all the luck I can spare.}

It was then, and only then, that the drama of the maze touched Snape. For it was then that he realized how the maze was the center of everything. It was then that he realized why Potter's name had been drawn from the Goblet of Fire. \emph{The Dark Lord is summoning Potter—has summoned Potter—Potter is with the Dark Lord and we are all, all of us, in danger.}

Snape staggered to his feet in the face of the blinding pain and tried to find Dumbledore.

Around Snape the eager spectators were still waiting for the outcome of the competition, and few even noticed him as he groped his way past them. Dumbledore knew, however, that something was wrong. He was already moving in Snape's direction.

"What has happened?" he whispered urgently as he helped support Snape toward the judging box.

"He has{\el} summoned{\el} us{\el} I{\el} have to{\el} go{\el}"

"Can you tell me where?"

"South{\el} a ways, but{\el} not too far{\el} probably{\el} Yorkshire{\el}"

"Try to locate the spot. It is important. Lives are at stake."

Snape nodded and allowed Dumbledore to guide him to a seat. The pain and urgency of the mark was beginning to abate, and fear was taking its place. \emph{I didn't answer the summons. Even if he didn't suspect me before, he will now.}

Dumbledore left to consult with Ludo Bagman and Cornelius Fudge, the Minister of Magic. Snape was trying to focus his thoughts and pinpoint the location he might apparate to if he responded to the summons. Everything else was a surreal background of normalcy, as if two separate worlds were cohabiting the same space.

Then, after what seemed an eternity, people began to scream and shout. Potter had suddenly appeared at the edge of the maze, though the circumstances of his arrival were hidden from Snape. There was an electric pause, and then the tone of the screams changed from excitement to fear. Something was wrong. Something was terribly wrong.

Snape struggled to his feet again and moved toward the front of the stands. People pushed forward to surround Potter. Through the pandemonium it slowly began to dawn on Snape that Cedric Diggory was dead, that somehow both Potter and Diggory had been transported to the Dark Lord, and that Potter had returned alive, but Diggory was dead.

Trying to cope with the magnitude of the thought, that a Hogwarts student had died, Snape sat down on the bleachers. His arm was throbbing and his head spinning. A form hovered over him.

"Are you all right?" McGonagall asked.

"I've been better. What's happening?"

"Albus is with Cedric's parents."

"Where's Potter?"

"Don't worry. He's in good hands. Alastor's taken him up to the castle."

It was the shot of pure adrenaline he needed. Snape rose quickly, seizing McGonagall's arm. "Get Dumbledore. Tell him Moody has Potter. He'll understand. I'm starting up to the castle now."

"But Severus{\el}"

"Move, woman!" An instant of shock on McGonagall's face, then she spun around to search for Dumbledore while Snape pushed his way through the crowd toward Hogwarts hill.

Fighting his way upward through gradually diminishing waves of dizziness, Snape reached the castle just as Dumbledore and McGonagall caught up to him. Dumbledore now in the lead, the three raced up the stairs to the second floor, to Moody's office. At Dumbledore's command, the door crashed open, and Dumbledore's cry of \emph{"Stupefy!"} sent Moody hurtling against the far wall to slump to the floor, unmoving. Snape took in the picture of Potter sitting in a chair and Moody lying on the floor, but his attention was immediately drawn to something else.

There on the wall was the mirror from his dream. Only it wasn't a mirror, it was a Foe-Glass. \emph{He's known all along that I was his enemy. He called me to his office that day to confirm it. But I work for Dumbledore. Why would the Foe-Glass think me the enemy of either Alastor Moody or Bartemius Crouch?}

McGonagall was trying to get Potter to his feet to go to the hospital wing, but Dumbledore wouldn't allow it. "{\el} he needs to understand{\el} He needs to know who has put him through the ordeal he has suffered tonight, and why. This is not Alastor Moody{\el}"

Turning to Snape and McGonagall, Dumbledore gave each a task. McGonagall was to fetch a dog from Hagrid's hut, Snape to bring Veritaserum and a house-elf. Neither questioned the orders. They were off at once down the stairs.

In his office, Snape quickly seized the small bottle of Veritaserum. Dumbledore would decide how much to use. Then he headed out of the dungeon and into the passage leading to the kitchens. The house-elves were bustling around, cleaning up the last of the dinner and beginning the preparations for breakfast.

Snape paused, then said to the crew in general, "The headmaster would like to speak to an elf named Winky."

The disgusted looks told him that Winky was not in good favor with the rest. After some consultation and with considerable effort, they pushed forward a slovenly, untidy elf who appeared to be{\el} tipsy? Snape was shocked, but decided Dumbledore must know what he was doing. "Come with me," he said to the unsteady elf. "You're not in any trouble, but the headmaster needs you."

They went more slowly than Snape would have wished as she followed him up the stairs to the second floor. McGonagall was coming down from Dumbledore's office at the same time. Snape suddenly remembered McGonagall's assignment. \emph{She went to get a dog, a `black' dog?} Connections formed in his brain, but their import eluded him.

The dog was forgotten when he entered the office. On the floor where Moody should have been was a much younger man with blond hair and freckles. Also from the dream. And though fourteen years had passed since Snape last saw him, he recognized him immediately. "Crouch?" he gasped, stopping dead in the doorway. "Barty Crouch?"

"Good heavens," was all McGonagall could say, but the elf darted forward at once.

"Master Barty, Master Barty, what is you doing here! You is killed him! You is killed him! You is killed Master's son!"

"He is simply stunned, Winky. Step aside please. Severus, you have the potion?"

As Snape handed Dumbledore the bottle, their eyes met for an instant. \emph{He has been reporting on me.} Dumbledore's voice in his head replied, \emph{I fear it may be so.} Then Dumbledore gave Crouch the Veritaserum and said, \emph{"Ennervate."}

And so the story came out. How Mr.~and Mrs.~Crouch had saved their son from Azkaban to condemn him to a prison of another kind. How Bertha Jorkins had learned the family secret and revealed it to the Dark Lord. How Barty had conjured the Dark Mark at the Quidditch World Cup, and how he'd been rescued by the Dark Lord and Wormtail. How he'd taken Moody's place to guide Potter through the Triwizard Tournament, and how he'd killed his own father when Bartemius Crouch escaped from the Dark Lord.

When the tale was told, Dumbledore sent Snape out to find Cornelius Fudge and bring him up to hear Barty Crouch's confession. McGonagall stood guard over Crouch while Dumbledore took Potter up to his office.

It took little time to find Fudge, but considerably more to attract his attention. Snape at first merely told the Minister that Professor Dumbledore wished to see him in the castle.

"A little busy now, Professor. We have to keep order down here first."

"With all due respect, Minister, the matter is rather urgent."

Fudge pulled Snape to one side. "Give me the gist of it. What's bothering Dumbledore?"

"He's discovered that You-Know-Who has had an agent at Hogwarts. The man is in custody now, and the headmaster would like you to interview him."

Fudge looked shocked, then worried. "An agent of You-Know-Who? Where is he?"

"The Defense against the Dark Arts office."

"Are you sure it's safe to go up there?"

"Perfectly, sir. The man is more than adequately restrained."

"I shall be the judge of my own safety. Go wait for me on the hill. I'll get a guard and join you."

Snape did as he was told. Fudge took somewhat longer than he expected, but when the Minister approached, Snape understood why. The deadly, soul-freezing cold of a dementor preceded the Minister, and Snape shrank from it as one already familiar with a dementor's touch must.

"Minister, the headmaster does not wish dementors inside the castle. He doesn't want them on the grounds."

"My personal safety requires the presence of a guard. I'm sure Dumbledore will see that. If I remember, the Dark Arts office is on the second floor."

Snape tried to stop Fudge, but he was unable to face the dementor. Instead he followed the Minister and his guard, still insisting that the dementor should not be in the building. When they reached the office, Fudge didn't even knock. He raised the latch and walked in to confront a surprised McGonagall.

The dementor moved fastest. At the first sniff of Barty Crouch, the thing sped across the room and attached itself to him. An instant later it had sucked out his soul, leaving a living but useless shell of a man sitting on the office floor.

McGonagall exploded. "How dare you allow that{\el} thing into Hogwarts!" she screamed. "You have no right to come in here with it! You've ruined everything! Have you any idea how much damage you've done!" She wheeled on Snape. "And you! You couldn't stop him from bringing it into the castle? You didn't have the nerve to stand up to him? What use are you, anyway!"

Snape couldn't respond, but Fudge tried to. "Now Minerva, you know I have no intention of getting in Dumbledore's way{\el}"

"You do a fine job of it for someone with good intentions! Get that thing out of here!"

Fudge hurriedly left the office, went with the dementor downstairs, and returned shortly thereafter, having sent it out of the grounds. The furious McGonagall continued berating Snape. "Why Dumbledore thinks he can depend on you is beyond me. I thought you had more backbone than that."

"It was a dementor, Minerva. You don't understand."

McGonagall paused in her tirade. "I'd forgotten. One of them went for you last year didn't it? Well, Dumbledore is going to hear about Fudge. He must be in the hospital. We're going down there now."

On their way down to the first floor they met Fudge coming up from the entrance hall. "Out of my way, you poor excuse for a{\el}"

"Please try to calm down, Minerva."

With McGonagall in the lead, and Snape bringing up the rear, they headed for the hospital wing. By the time they got there, though, Fudge had moved ahead.

"I agree it was regrettable, but all the same, Minerva{\el}" he said.

"You should never have brought it inside the castle! When Dumbledore finds out{\el} !"

Then they were in the hospital wing, facing an irate Molly Weasley with members of her family around Potter's bed. "Where's Dumbledore?" Fudge demanded.

As Mrs.~Weasley was protesting, Dumbledore entered behind them. At his question, McGonagall tried to explain, but she was too upset to be fully coherent.

"When we told Mr.~Fudge{\el}" and Snape quietly described what had happened, punctuated by McGonagall's furious additions and Fudge's protests.

"By all accounts he is no loss!"

"But he cannot now give testimony, Cornelius{\el}"

And there began a scene that to Snape seemed like something out of a bad dream, for Dumbledore tried calmly to explain that the events of the evening had been arranged by a Dark Lord now fully returned to his body, while Fudge was determined not to believe that it was anything except the hysterical ravings of a delusional boy. Eventually Potter joined in and shouted at the Minister, "I saw the Death Eaters! I can give you their names! Lucius Malfoy{\el} !"

Snape started. \emph{Lucius was there? Who else do I have to face?} He noticed Potter glanced at him strangely and turned back to Fudge. Potter kept blurting out names. "Macnair! Avery{\el} Nott{\el} Crabbe{\el} Goyle{\el}" It was useful information.

And still Fudge refused to accept, refused to consider making changes to adjust to the new, dangerous situation, refused to believe there was any danger at all. Clearly Dumbledore and Fudge were at a parting of their ways. Fudge had to be convinced, and Snape did something he'd been trying to avoid for fifteen years. He pulled back the sleeve of his robe, knowing that every person in the room would now share his secret, and held his arm, with its hideous skull and serpent tattoo, in front of Fudge's face.

"There. There. The Dark Mark. It's not as clear as it was an hour or so ago, when it burned black, but you can still see it. Every Death Eater had the sign burned into him by the Dark Lord. It was a means of distinguishing one another, and his means of summoning us to him{\el} Why do you think Karkaroff fled tonight? We both felt the Mark burn. We both knew he had returned{\el}"

It was too much for Fudge. "I don't know what you and your staff are playing at{\el} I will be in touch tomorrow{\el}" and he left Potter's winnings and strode from the room.

As Fudge disappeared from sight, Snape knew that others in the room were now staring at him. McGonagall and Pomfrey, Molly, Bill and Ron Weasley, Granger, Potter. All those years of living a relatively normal life were gone. Even if the Dark Lord were destroyed, nothing would ever be the same.

Dumbledore lost no time. Bill Weasley was sent at once to his father in the Ministry of Magic to try to organize opposition to the Dark Lord despite the attitude of Cornelius Fudge. McGonagall was sent to bring both Hagrid and Madame Maxime to Dumbledore's office. Madame Pomfrey was dispatched to the Dark Arts office to look after the house-elf Winky. When they had left, Dumbledore checked the door to be sure the remaining people were not disturbed. These were himself, Snape, Molly Weasley, Potter, Ron Weasley, and Granger.

"Now," said Dumbledore, "it is time for two of our number to recognize each other for what they are. Sirius{\el} if you could resume your usual form."

Snape turned, horrified, in the direction Dumbledore was looking. A great black dog stood in the corner, a dog who suddenly was Sirius Black. Molly screamed and was silenced by her son. Snape could only stare at the man in disbelief.

\emph{So now even Sirius Black has proof that I was a Death Eater. Why did Dumbledore bring him here? Why, with everything else there is to endure, do I have to endure this, too?} "Him! What is he doing here?" The words nearly choked him. It was clear that Sirius felt no love either.

"He is here at my invitation, as are you, Severus. I trust you both. It is time for you to lay aside your old differences and trust each other."

\emph{Trust him? Trust the man that was willing—eager—to throw me to a werewolf? Trust the man that lured me into a trap so he could beat me senseless? Trust the man that betrayed Lily?} A little voice in the back of his head was whispering `Wormtail, Wormtail' but for the moment he wasn't paying attention. Snape made no movement, but eyed Black as if he were expecting the treachery of a dagger at any moment. Black's face showed a similar expression.

Dumbledore broke up the mutual loathing society. "I will settle, in the short term, for a lack of open hostility. You will shake hands. You are on the same side now. Time is short, and unless the few of us who know the truth stand united, there is no hope for any of us."

It was an order. Warily, like two duelists who suspect a trap, Snape and Black approached each other . They never broke eye contact as they touched hands briefly—one could hardly call it a shake. Snape was shut down against legilimency as if it were, in fact, a duel. \emph{Don't look at his hands, look at his eyes. You'll see his attack there before his hands can move.} It seemed Black was thinking the same.

Dumbledore was quick to step between them. "That will do to be going on with. Now I have work for each of you. Fudge's attitude, though not unexpected, changes everything. Sirius, I need you to set off at once. You are to alert Remus Lupin{\el}—the old crowd. Lie low at Lupin's{\el}"

"You'll see me very soon, Harry," Black said, and then he was a dog again, and gone.

Dumbledore turned to Snape, and now there was concern in his eyes. They had reached the point toward which they'd been planning for so long, but now Dumbledore could only wait and hope. For what came next, he was unable to help. Snape could feel his apprehension, the worry that looked out at him from the usually calm blue eyes.

"Severus, you know what I must ask you to do. If you are ready{\el} if you are prepared{\el}"

The intervening years were gone. Snape had gone once before into the secret war, where no one watched your back, and you were always alone. Then he'd thought of himself as a knight errant, serving his lady, pure and untouchable. The lady was gone, but her murderer lived again. Now it was revenge he sought, revenge for the lady he would have died to save, and suddenly Snape felt alive again, alive in the face of death in a way he could never be alive anywhere else.

"I am," he said.

"Then good luck," said Dumbledore, and Snape swept wordlessly from the room.


