% A Difference in the Family: The Snape Chronicles (Rannaro)
% The Middle Years

\chapter{Trials}

\subsection{Tuesday, December 22, 1981 (midway between the last quarter and the new moon)}

The depth of Snape's self-loathing was boundless, a black pit into which he sank with no hope of ever climbing back again. He no longer cared what happened, not to his future, not to his freedom, not to his health. He refused to leave his bedroom and, with the terrible passiveness that always accompanied his intense depressions, he lay hour after hour staring at the wall. Hagrid brought food, finding more cause for worry in the fact that, rather than refusing the spoonfuls Hagrid presented to him, Snape ate them mechanically, like a robot.

Dumbledore was in immediate contact with the Ministry, and owls flew back and forth almost hourly for three days. Then, very early in the morning on Tuesday, Dumbledore and Hagrid came to Snape's room.

"On yer feet, lad," Hagrid said cheerfully. "We got to clean ya up and make ya presentable. Y're going to London today."

"No," Snape said, bewildered, "I'm not going anywhere. I can't leave."

"You are going, and you are going this morning," Dumbledore said. "I have moved heaven and earth. What is more difficult, I have moved the Ministry of Magic. Your pretrial hearing and judge's review have been combined and rescheduled for today, and the trial itself for next week."

"No. That's impossible. That's not until February. It can't be today. I can't go today. I don't feel well."

"And ya ain't never going to feel better lying there moping," said Hagrid. "So ya may as well get this over and done with. Now get out o' those things ya been lying in for the past four days and let me wash ya up and get{\el}"

Dumbledore left the rooms to allow Hagrid to work with Snape as he'd been doing since the boy was nearly thirteen. If anyone could put a spark of life back into Snape{\el}

There was the sudden sharp mosquito-like whine of a stinging hex, a yelp from Hagrid, and Snape's voice raised in anger. "Get your hands off of me! I'm not a baby! I'm perfectly capable of washing and dressing myself!"

"Well, then," Hagrid roared, "the rest of us would appreciate ya getting to it! Clear up the atmosphere a bit, I might add."

"I'm not bothering anyone!"

"Oh, no? I got t' come in here three times a day with yer food, and it ain't getting pleasanter. Now ya just clean yerself up and put on some decent clothes or I'm gonna haul ya buck naked down t' the lake and do a proper job!"

"Get out! Get out of my room!" And Hagrid was out, standing in the corridor next to Dumbledore as something heavy made of glass shattered against the inside of the office door.

"I suppose that is one way to do it," said Dumbledore.

Half an hour later, Snape was ready - washed, shaven, his long lank hair still damp - dressed in somber black frock coat and trousers rather than robes. Hagrid inspected him and pronounced him fit to stand trial, then the three went out of the dungeons and to the Great Hall for breakfast.

For a moment, Snape was surprised at the emptiness of the place, then remembered it was the second week of the Christmas break. The other teachers were scattered around in their usual holiday places as Snape followed Hagrid to a table, like a prisoner in the custody of a jailer. Dumbledore went to join McGonagall.

"Here," said Hagrid, sitting him down and filling a plate with Snape's favorite kipper and toast, "ya got to keep yer strength up for the day."

"I'm not hungry."

Hagrid's fist came down on the table like a sledgehammer, sending dishes flying. "Eat!" he shouted, and Snape grabbed a fork and began eating. "There now," Hagrid continued calmly, helping himself to some of the food. "Ain't that better now, us sharing a fine meal, all friendly like?"

Flitwick was the first to come over. "Important day today, we hear. Just wanted to wish you good luck with the Ministry."

"Thank you," Snape said, and smiled. A weak smile, but a smile.

Sprout came, too, and then Kettleburn, and soon all the others, even McGonagall, were wishing him luck for the day. Snape finished breakfast, said goodbye to everyone, then left the castle and walked down the hill with Dumbledore and Hagrid, all three apparating to London as soon as they were outside the gate.

The atmosphere at the Ministry of Magic, chilly to begin with, became positively frosty as the three descended towards the offices and chambers of the Department of Magical Law Enforcement. In the corridors, wizards and witches paused as Dumbledore passed, muttering imprecations and following his progress with angry looks. The aurors at Hogwarts had been right. Dumbledore was being blamed for what had happened to the Longbottoms.

Snape's preliminary hearing was held in a moderate sized room with the judge's desk raised slightly above the level of their heads, a clerk's desk to one side, a railed dock for the accused to stand in, and benches for prosecutors, aurors, and observers. Today observers had been banned, as Dumbledore would present evidence supporting a closed hearing.

Scrimgeour and Moody arrived shortly after Dumbledore, Snape, and Hagrid. They nodded curtly to Dumbledore in greeting, then waited in silence for the judge to arrive. Her clerk entered first and, as the little group rose, Judge Bones walked into the chamber. She was a dignified witch with a determined square jaw, graying hair, and glasses. She greeted them in turn.

"Mr. Scrimgeour, Mr. Moody, thank you for coming. I realize this hearing was rescheduled rather abruptly, and it was good of you to make adjustments in your busy schedules. Professor Dumbledore, you see we have made every effort to accommodate your requests. You will provide evidence supporting your claims today, however, or this case moves to a more open venue. Mr. Hagrid, it is pleasant to see you again. And this, I take it, is the accused." She checked the docket. "Mr. {\el}Snape, is it? If you will all take your seats, please, I'll review the case."

They waited in silence for nearly twenty minutes as the Judge checked documents, asked the clerk for files, and took notes. Then she called Snape forward to stand in the dock for the rest of the proceedings.

"Mr. Snape, my name is Amelia Bones, and I am reviewing the charges against you prior to their being presented in court. Are you aware of the nature of these charges?"

Snape looked over at Dumbledore, who nodded and smiled gently, then back at the Judge. "No, ma'am," he said.

"Very well, first you are charged with treason in that you willfully and voluntarily became a participating member of a group actively engaged in the overthrow of the Ministry and the setting up of another government in its place."

"No, ma'am, I didn't{\el}"

"Mr. Snape, I take it you are unfamiliar with the rules. You'll have a chance to respond later. Right now, you just listen."

"Yes, ma'am."

"Next, you are charged with conspiracy to commit treason in that you actively recruited or attempted to recruit others to join this same group. You are charged with using Unforgivable Curses. You are charged with several counts of murder, of inciting to commit murder, of conspiracy to commit murder, and of aiding and abetting others in the commission of murder both before and after the fact. I have a list of similar charges relating to grievous bodily harm, public disorder, and vandalism." She looked over her glasses at the now thoroughly shaken Snape and said, "You seem rather young to have accomplished all of this in{\el} three years, I believe it says."

"Your Honor, if I may{\el}" Dumbledore began, rising.

"Sit down, Albus, and wait your turn. I need to talk to these two gentlemen first. Which of you two is presenting the case, Alastor? You or Rufus?"

"I am, Your Honor," said Moody, stepping forward next to Snape.

"Either I am missing a large number of papers, Alastor, or you're getting sloppy with your homework. Or is this maybe because you weren't expecting me to review the files until a week after the original hearing?"

Moody glanced back at Scrimgeour, who shrugged. Turning back to the Judge, he said, "I may need to check with our office. What are you missing?"

"I've been going through all these papers since I got here this morning, and I can't find a single statement from a single witness placing this young man at the scene of any crime except the murder of Dorcas Meadows, and then only as a witness himself. How can you charge him with commission or inciting to commit if he wasn't there?"

Moody was now beginning to turn red in the face, but it seemed his anger was directed at Scrimgeour. "Permission to discuss this matter with my colleague for five minutes, ma'am?" he asked.

"Granted," the Judge replied, and Moody and Scrimgeour stepped out of the chamber.

A few minutes later, the two returned. "Your Honor," Moody said, "our office would like to withdraw all charges relating to commission or inciting to commit on the murder, bodily harm, public disorder, and vandalism counts."

"Noted," said the Judge. "Now, the Unforgivable Curses. I see no eyewitness testimony to the acts, nor any firsthand report of statements made by the accused. Everything is hearsay. What do you want to do with those?"

Moody turned to Scrimgeour and mouthed the words `not one?' then addressed the Judge. "We'd like to withdraw those charges, Your Honor, as they're still under investigation. We thought to have them done by February, but with the case moved forward{\el} If we collect enough evidence, we will be revisiting the charges."

"Are there any other changes you'd like to make, as long as we've gotten this far?"

"No, Your Honor." Moody didn't look happy.

"All right, Mr. Snape. Now we've gotten to the point where you hear the specific charges and enter a plea of either guilty or not guilty. If you want to tell the court that you did one of these things, you say `guilty'. If not, you say `not guilty.' Do you understand?"

"I think so, ma'am{\el} Your Honor."

"First the treason charge. The group you're accused of being a member of is the organization known as the Death Eaters, who followed the orders of the wizard who called himself Lord Voldemort."

Snape winced at the name, but didn't say anything. He looked around the court, then back at the Judge. "Do you mean that if I was a member of that{\el} group, I'm supposed to say, guilty?"

Dumbledore was on his feet, but the Judge stopped him with a gesture. "You have to be very careful about this, Mr. Snape. If you say `guilty,' it doesn't go to a trial. You just get sentenced. If you want the chance to defend or explain your actions to the court, you say `not guilty.' Do you have a lawyer? Is Professor Dumbledore your lawyer?"

"I don't know."

"Albus Dumbledore, front and center."

"Yes, Your Honor?"

"What do you mean bringing this young man here without briefing him first on what's going to happen?"

"I am very sorry, Your Honor. Unfortunately Mr. Snape has been suffering from acute clinical depression, and we were not certain he would make it to February. I believe Your Honor has transcripts of the correspondence."

"Did we get those?" the Judge asked the clerk, who sorted through a stack of files and brought one over. "Give me a moment, Albus. You may sit down."

Dumbledore sat, and when the Judge had scanned the papers, she called him back together with Moody. "I'd like you both to approach the bench." She handed Moody a paper and said quietly, "Did you know about this?"

Moody read it quickly, then looked at Dumbledore. "You're sure he drank it?"

"Yes. It turned out to be reasonably harmless, but he did not anticipate that."

"He certainly didn't think so on the tenth. Your Honor, we were not aware of this."

The Judge looked grim. "Can you guarantee to me, Albus, that neither of these actions of apparent desperation was connected with the charges before us? The timing of the first in particular bothers me."

"I assure you, Your Honor, that the charges are so far from being the source of his depression that I believe focusing on them will help him recover. This is why I requested they be moved up."

"And is he really that naive?"

"About some things, Your Honor. About others, alas, the depth of his experience is heartbreaking."

Sending Dumbledore and Moody back to their places, the Judge addressed Snape again. "Mr. Snape, it is my opinion that you would be well advised to have a lawyer. If you wish, Professor Dumbledore could fill that position, or you could choose someone else, or the court could appoint someone."

"I'd like Professor Dumbledore, ma'am."

"Do you need to confer?" Snape shook his head. "Very well, Albus, we'll proceed with the charges, beginning with treason."

"Thank you, Your Honor. Mr. Snape pleads not guilty to the charge." One by one the Judge read each individual charge, and Dumbledore responded, "Not guilty" to each.

When they had finished, the Judge reached for another folder. "Now," she said, "about your petition to have the trial conducted behind closed doors{\el}"

"Thank you, Your Honor. First, since we are no longer discussing charges, would it be acceptable for Severus to sit with Hagrid?" The Judge nodded and waved Snape from the dock. "Thank you. And now, Severus, as I am your lawyer, you must let me do the talking. If you wish to add or change anything, say `Your Honor' and ask to confer with me."

"Yes, sir," Snape said.

"Good. Your Honor, we have requested that the trial be held behind closed doors because we, well I actually, believe that Mr. Snape's life would be in danger if certain aspects of it were to become public. In danger from those who were also Death Eaters and former colleagues of his."

"Albus, I've just noticed that you've admitted your client's guilt on the first charge. Watch your step here."

"I realize that. We will argue extenuating circumstances. However, understanding that he was once a Death Eater is vital to understanding why his trial must be kept secret. About a year and two months ago, Mr. Snape came to me clandestinely at Hogwarts to divulge to me Voldemort's plans to attack two of his enemies. These two people were known to Mr. Snape from his school days, and he did not wish them harmed. I was skeptical of his motives and questioned him extensively. The information he gave me that day proved very useful to us later. I offered him asylum, but he feared Voldemort's wrath if he deserted the Death Eaters. I was mercenary enough to give him instructions on how to contact me if he wished to give me more information."

Everyone in the room, the Judge, Moody, Scrimgeour, and the clerk, were listening attentively.

"I was both surprised and pleased to receive from him some time later information that saved the life of yet another of my people. Then something happened, particulars of which I will reserve for the trial if you do not mind, that turned Mr. Snape against Voldemort completely. We began to receive information that enabled us to eliminate many Death Eaters and foil their plans. Many of our successes of the past year were, in fact, due to him. Since this is information that must be used in his defense at his trial, the trial cannot be public. Any Death Eaters still at large who learned of it might mark him for execution."

"Your Honor," exclaimed Scrimgeour, "we'd like to point out on the other side that as late as twelve days ago Mr. Snape was still withholding information from the Ministry in order to protect some of these same Death Eaters. Four of those he was protecting were responsible for the brutal attack on Frank and Alice Longbottom."

"Your Honor{\el}" Dumbledore began, but the Judge raised her hand.

"This dispute can be argued at the trial. I've heard enough to reach a decision. This case is hereby covered by a gag order and secrecy provisions. Except for client\slash lawyer privilege, it may only be discussed in secure areas of the Ministry. Any violation will result in both contempt and criminal charges. Anything else, gentlemen? No? You are dismissed." The Judge rose and left the chamber, accompanied by the clerk.

Scrimgeour followed her out, clearly angry at the outcome of the proceedings.

Moody came over to Dumbledore, not looking at Snape at all. "That was a nice little surprise you threw at us there, Albus. I don't deny it's going to change the mood at the trial. It makes it harder to explain his silence in the last month and a half, though. They're going to hit you hard on that."

"They are? Should you not be saying `we are?'"

"I'm torn. I will admit I'm torn. Well, I'm back off to work. Enough lazing around for one morning. Catch you later."

"Good-bye, Alastor."

It was lunchtime when they returned to Hogwarts. The teachers came over for news only to be told sternly by Dumbledore that the case could not be discussed outside the Ministry.

"Are you that important now?" cried McGonagall with a laugh. "Whoever would have thought."

Before leaving the Ministry, Dumbledore had checked the docket; Snape's trial was firmly set to begin on Wednesday the thirtieth. Since the Council of Magical Law did not involve anything so mundane as juries, and members of the Council were free to ask questions during the trial, it was not expected to last more than a day, two at most.

One of the best things about the hearing was that it restored Snape's appetite and general interest in life. He was always at his best when focusing on a well-defined problem, and at his weakest when dealing with the vague or formless. The charges, while detailed and complex, were nonetheless direct and specific. Snape sat down first to a hearty lunch, and then to trying to organize his memories of his activities at the time of the events mentioned in the charges.

\subsection{Wednesday, December 30, 1981 (four days after the new moon)}

On the day of Snape's trial, he, Dumbledore, and Hagrid returned to London and entered the Ministry of Magic. Their progress through the building was about as it had been the previous week, except this time Hagrid was not allowed into the chamber. That alone made Snape feel uneasy, but nowhere near as uneasy as he felt when he entered the chamber itself.

Banks of benches for the council members rose like the bleachers in a stadium around a central circular area. In the middle of the circle was a chair. A heavy chair with straight arms, and with chains to bind its occupant in place. Snape shrank against Dumbledore, for being bound, unable to move, was one of the things that frightened him most.

The members of the Council of Magical Law had been moving around, greeting each other and conversing in small groups, but when Dumbledore and Snape entered, they moved quickly to their places in the stadium-like chambers. A few greeted Dumbledore in a friendly manner, but most did not. Two clerks came up to Dumbledore.

"Is this the defendant?" one said.

"It is," Dumbledore replied.

"Come with us."

Dumbledore laid his hand on Snape's shoulder. "Do not be afraid. No one is ever harmed in this chamber. These are not aurors, but council members, and they have seen far worse than you."

Snape followed the two clerks meekly and sat when he was told. The chains were enchanted and wrapped around his arms like snakes (very odd under the circumstances, he thought) binding Snape to the chair. The chamber became quiet.

The clerk then unrolled a parchment and read: "Ladies and gentlemen, you have before you the case of one Severus Snape, wizard, accused of various crimes against our world which are detailed in the docket books in front of you. They are one count of treason, one count of conspiracy to commit treason, six counts of conspiracy to commit murder, and fifty-two counts of aiding and abetting others before the fact in commissions of felonies, including murder, attacks causing or intending to cause grievous bodily harm, incidents of civil disorder, and vandalism or other damage to property. Counsel for the prosecution may proceed."

"Objection," said Dumbledore, rising. "The defendant was not informed of fifty-two counts of aiding and abetting. Only of ten. We request that the others not be laid before this council until we have had time to research them and prepare a defense."

The head of the council, an old wizened wizard with curiously long ears, made a note. "We'll keep your objection under advisement, Albus. Prosecution may continue."

The auror leading the prosecution was Gawain Robards. He approached Snape in a very businesslike way.

"State your full name."

"Severus Snape."

"Date and county of birth."

"Nine January 1960, Lancashire."

"Names and blood status of parents."

"My father was a muggle, Tobias Snape, my mother a pureblood witch, Eileen Prince."

"The council will note that we intend to return to this matter of blood status. Occupation, Mr. Snape, and for how long?"

"Instructor at Hogwarts school, in Potions, since this last August."

"And before then?"

"I was a private tutor."

"Anything else?"

Snape didn't answer.

"Note that the defendant did not respond to the question. Now Mr. Snape, let's get right to the meat of the first charge. Were you at any time a member of the organization known as the Death Eaters under the control of the self-styled Lord Voldemort?"

"Yes. I became a{\el}"

"Just answer the question, Mr. Snape. In this case a simple `yes' suffices."

"Yes, sir."

"When did you become a Death Eater?" Robards continued.

"The twentieth of July, 1978."

"Describe your initiation."

"I was invited to London by one of my sponsors{\el}"

"You had sponsors? Please give their surnames."

"The Lestranges, Rosier, Wilkes, Avery."

"All three Lestranges? Rabastan, Rodolphus, and Bella?"

"Yes, sir."

"I ask the council to note that three of the defendant's sponsors were among those who attacked and tortured Frank and{\el}"

"Objection!" cried Dumbledore. "The defendant has not been charged in connection with the attack on the Longbottoms."

"On the contrary, Professor Dumbledore, that is count number fifty-two of the aiding and abetting charge{\el}"

"Of which the defendant was not informed until this moment, and which should therefore not be considered at this session{\el}"

The head of the council banged his gavel. "That matter is still under advisement. The prosecution may proceed." Dumbledore resumed his seat.

Robards returned to his questions. "Now, Mr. Snape, how did you come to be acquainted with these sponsors?"

"I knew them from Hogwarts. Rosier and Wilkes were two of my dormitory mates, and the others were in classes ahead of mine."

"Were you all in the same house?"

"Yes, Slytherin." The answer caused a little ripple of murmurs.

"How did you become familiar with these older classmates?"

"They hired me to tutor them in their Potions work."

"Come, Mr. Snape, you can be more honest than that. This is a court, after all."

"Objection! Counsel is badgering the defendant." Dumbledore had risen again.

The gavel banged. "Overruled, Albus. We want to see where this is going."

Snape watched Robards, wary and apprehensive. "I don't know what you mean."

"With the council's permission, I'll refresh your memory. Isn't it true that you became involved with these upper level students when you became part of a conspiracy to hex and jinx members of Gryffindor house in retaliation for a harmless prank they pulled at the 1973 Welcoming Feast?"

"No, they attacked us first{\el}"

"First? Then you did hex them?"

"Yes, but only because{\el}"

"Wasn't your nickname in Slytherin house `Cursemaster?'"

"Objection!"

"Counsel for the defense has a point, Mr. Robards. How does this relate to the charge?" The old wizard looked a bit impatient.

"I'm getting to that right now, sir, if the defendant will answer the question." Robards turned back to Snape. "Was it `Cursemaster?'"

There was no advantage in denying it. "Yes," Snape said.

"Ladies and gentlemen, the organization of Death Eaters was well known for its value of blood purity. Every one of the defendant's sponsors was a pureblood witch or wizard of impeccable ancestry. And yet they united in sponsoring into their midst a younger half-blood wizard of no social background. I submit that the reason for this sponsorship was the defendant's well-known, I might call it notorious, expertise in the Dark Arts, in hexes, jinxes, and yes curses, which by the time he was thirteen, thirteen, had earned him the name `Cursemaster.' Mr. Snape, is this not true?"

The silence stretched as Snape stared at the floor. "Let it be noted," continued Robards, "that the defendant refuses to answer the question."

There was no trace of triumph or malice in Robards's manner or voice. He continued to be very businesslike. "Let's return to your initiation. You met with your sponsors. What then?"

Snape tried to collect his thoughts. "I was blindfolded and taken to their headquarters."

"How?"

"Side by side apparation. They took me into a chamber and had me kneel, then they removed the blindfold. I was face to face with the Dark Lord{\el}"

"Lord? You still call him Lord?"

"No!" Snape cried. "It's just habit!" Robards didn't pursue the issue. "He examined me with legilimency, welcomed me to the group, and gave me the mark."

"Legilimency. So if you'd had any reservations, he would have known." Robards waited. "The defendant does not answer. Do you still bear the mark? May we see it?"

"Yes, sir."

Robards stepped forward and gently unbuttoned and pushed up the sleeve of Snape's jacket, showing the council members the skull and snake brand. "Now, Mr. Snape, did you enter into this association with `Lord' Voldemort freely and of your own will."

"Yes, sir."

"Thank you. The prosecution yields for the moment to the defense."

Robards sat and Dumbledore rose. Gently he asked, "Severus, what happens when someone says the name Voldemort in your presence?"

"It hurts. The mark hurts. It's like a jolt of electricity."

"Is this why Death Eaters employ the phrase `Dark Lord?'"

"Yes."

"Thank you. I shall try not to cause you further pain. Now, are you a talented spell caster?"

"Sir?"

"Does the casting of spells come easy to you? Have you been using a wide range of spells from childhood?"

"Yes, sir."

"Who taught you those spells?"

"My mother."

"Are you able to create new, previously unknown spells?"

"Yes, sir." The answer caused another murmur, this time of surprise.

"Describe your first encounters with the other members of Slytherin house, including your dormitory mates."

"They teased me and insulted me. They called me a mongrel and a cur. They bullied me{\el}"

"How did you respond?"

"I hexed them. Spiders and lice. I made Rabastan Lestrange smell like a wet dog."

"What is the most powerful spell you used against them?"

"I created a small earthquake." More murmurs, louder now.

"How old were you?"

"Twelve." The head of the council had to use his gavel for silence.

"And this was against your own housemates, other Slytherins, who were teasing and tormenting you?"

"Yes, sir."

"And what did Bella Lestrange do?"

"She offered to help me. She said if I stayed with her, she'd make the others leave me alone."

"So you went with her for protection?"

"Yes, sir."

Dumbledore continued, quiet and gentle. "Did you become a Death Eater of your own free will?"

"Yes."

"Why?"

"I was afraid. Wizards were being attacked by muggles, and no one seemed to be doing anything about it."

"Did this affect you personally?"

"My grandmother, a witch, was attacked and killed by a muggle mob."

"I see. Who of your family remained after this attack?"

"No one. She was my last living relative."

"How old were you when this happened?"

"Seventeen."

"An adult by wizard law, but how many of us could say we endured such great loss at such a tender age?"

"Objection," said Robards. "Counsel is editorializing."

"Sustained."

"Very well," said Dumbledore, "I shall summarize this point. The defendant has admitted to becoming a Death Eater of his own free will, out of fear of muggle violence and the desire for protection, something he had been seeking since entering Hogwarts. Now, Severus, what did you subsequently discover about the death of your grandmother?"

"By chance I overheard a conversation between two other wizards in which one told the other that my grandmother had been murdered by Death Eaters. They had placed muggles under an Imperius curse to attack my grandmother, and the reason for the attack was to recruit me, to push me into becoming a Death Eater."

"When did you overhear this conversation?"

"After the beginning of December of 1980."

"When did your grandmother die?"

"October 1977."

"So for three years, from October 1977 to December 1980, you believed your grandmother to have been the victim of random muggle violence, and your fear of this violence was a major factor in your becoming a Death Eater?"

"Objection!" cried Robards. "Counsel is leading the witness."

"I believe," said Dumbledore, "that my summary can be supported by the defendant's previous testimony and is therefore not leading."

"Overruled," said the head of the council.

"Answer the question, Severus."

"Yes, sir. I mean that's my answer. Yes. Sir."

"Good. Now Severus, when did you first come to me with information against this `Dark Lord?'"

"The thirteenth of November, 1980."

"Before you discovered the truth about the attack on your grandmother?"

"Yes, sir."

"Why did you decide to turn against your master?"

The answer to this question was the only one that had been prepared and rehearsed, since Snape adamantly refused to compromise Lily's memory through any connection to him. It was a masterpiece of precise truths and careful omissions.

"By the end of the summer, the Dark Lord - excuse me, I don't know what else to say - he'd gotten it into his head that some newborn baby was a threat to him. The baby and his parents. He had us all looking for them, James and Lily Potter and their son. I didn't like James, but we'd patched up the worst of our differences before we graduated, and besides it wasn't him, it was the baby. You don't go after a baby. I couldn't think of where else to go for help, so I went to Professor Dumbledore and told him what was happening."

"Thank you. We will return to this later. Now, Severus, what kind of work were you given to do as a Death Eater?"

"I was asked to create spells. To mix potions and to create spells. He would give me a message telling me what he wanted the spell to do, and my job was to create the spell."

"What kinds of spells? Combat spells? Interrogation spells?"

"No, sir. I've always had a{\el} kind of talent for sound spells and other sensory spells. He wanted things like covering conversations, hearing conversations at a distance, muffling movement, avoiding detection."

"Were you ever sent out as part of a group that attacked a person or a home or anything else?"

"No, sir."

"Were you ever involved in planning such an attack?"

"No, sir."

"Were you ever invited to join such an attack?"

"Yes, sir, on a couple of occasions by members of the squads, but the squad leaders always told me I couldn't go."

"Why was that?"

"They wouldn't tell me. But the last time, in December 1980, I overheard them say that they didn't want me to find out that my grandmother's death had been arranged in order to recruit me."

Dumbledore then addressed the council. "What we have here, ladies and gentlemen, is a young wizard of extraordinary talent in the invention of spells. This talent was noticed quite early by students associated with the Death Eaters. Please note that the Avery and Rosier mentioned by the defendant, were the sons of men who were among the original Death Eater cadre. This group over a period of several years carefully manipulated the defendant into believing that he was threatened, looking to them for protection, and finding among them respect and appreciation for his talents. Once recruited, he was carefully prevented from discovering the true nature of Death Eater operations. When he did learn of an operation that crossed a moral boundary - the hunt for a baby - even before learning about operations that affected him personally, he took steps to leave the Death Eater organization by coming to me. I now yield to counsel for the prosecution."

Dumbledore sat down, and Robards stepped into the center. "You've forgotten one or two things, haven't you, Mr. Snape?"

"Sir?"

"In August 1978, weren't you a frequent visitor to Fortescue's ice cream parlor in Diagon Alley?"

"Yes."

"What was your assignment there?"

"Make contacts, arrange future contacts through tutoring connections, gather information{\el}" Snape could not move, bound by the chains, but his fingers were beginning to twitch uncontrollably.

"Talk to students about becoming Death Eaters?"

"Yes."

"Do you recognize the name Marcus Abernathy? Did you talk to him about joining the Death Eaters? And did he join?"

"Yes."

"For the information of the council," Robards stated, "Marcus Abernathy has confessed to being a member of the squads that attacked and killed Edgar Bones and his family, killed Gideon and Fabian Prewett, and kidnapped Dorcas Meadows. Mr. Snape, did you create a spell that would allow a person to walk across dead leaves in silence, and another that would prevent a dog from noticing an intruder, and another that would locate and turn off burglar alarms?"

"Yes." The answer was mechanical. Snape was wrestling with the thought that Marcus had killed, that he had brought a killer to the Dark Lord, that he had recruited a killer.

"Would you say you were a reasonably intelligent person? At least at the same level as any average person?"

"I suppose so."

"As a reasonably intelligent person, Mr. Snape, what did you consider that these spells were being used for?"

Snape closed his eyes, his heart had begun pounding in his ears. "I{\el} didn't think about it."

"Didn't think about it. Let me show you a picture, Mr. Snape."

Snape opened his eyes. The picture was of a room in a house, and there were five people in the room, a man, a woman, two young boys, and a little girl. It was a wizard photograph but the people weren't moving. They weren't moving because they couldn't move. They were dead, and there was blood everywhere. And the little girl was staring up at the ceiling with wide, frightened eyes, unseeing eyes for her throat was cut. Staring at him with wide, unseeing, accusing eyes{\el}

Robards was talking. "This is the family of Edgar Bones, Mr. Snape. The members of the squad that attacked them, we have been told, were Abernathy, Rosier, Wilkes, Dolohov, Lestrange and his wife{\el} Curious thing, that Edgar seems to have been taken completely by surprise. You see, he had a dog that he expected to warn him of intruders{\el}"

Snape closed his eyes again, his body rigid, his face drained of all color, the image of the little girl floating in the front of his brain - closing down, locking, shutting all the doors, all the barriers{\el}

Somewhere in the distance Dumbledore was speaking, his voice muffled but urgent. "May I call a recess? A recess, please. My client is not well." The chains unwound, and Snape rose and was led to a small antechamber where he sat staring at the wall while Dumbledore got water.

"I don't want to do this anymore," Snape said quietly.

"I am afraid you have no choice," Dumbledore replied.

"Can't we just tell them I'm guilty? I mean, they're right, aren't they? I did all those things. I was stupid and blind, and I gave them the tools to kill people. Why don't we just say so, and stop this?"

"Are you sure?"

Snape nodded, and Dumbledore left the room to fetch Robards and the head of the council. When they were assembled, Dumbledore explained, "Mr. Snape wishes to change his plea to guilty."

"On all counts?" asked Robards.

"Yes," said Snape.

"No," said Dumbledore. "Not the conspiracy charges. He was never involved in any planning, and if he insists on pleading guilty to those, I'll request a hearing to find him psychologically incompetent to make his own legal decisions."

"All right. The evidence was circumstantial on those anyway. What about his giving evidence in other cases?"

"No," Snape said suddenly. "No more names."

"I believe he gave you a large number of names on the tenth, and I doubt he has more definite information than that. Could we not leave it there?"

Robards looked at Dumbledore for a moment. "All right. We'll amend the charges."

"Good." Dumbledore turned to the head of the council. "Faustinus, I should like to address the council on the defendant's behalf, but I think it best that he remain here. Could Hagrid come in and sit with him?"

"I'm afraid not, Albus. Hagrid's general public. No exceptions."

"Rufus is outside," said Robards. "He could{\el}"

"Absolutely not! That man will not come within{\el}"

"Calm down, Albus. What about Alastor? He won't speak, won't move, just make sure Mr. Snape{\el}"

They left and Moody entered, to sit unmoving and unspeaking in a corner while in the chamber Dumbledore's voice could be heard. "I should like to take a few minutes to speak on behalf of the defendant, especially concerning events that occurred between November thirteenth, nineteen eighty, and August first, nineteen eighty-one which I believe should be taken into account{\el}"

Over an hour later, Snape again entered the council chamber, this time to stand before the assembled wizards. The clerk read from a roll of parchment: "Severus Snape, hear the decision of the Council of Magical Law concerning the charges brought against you. In the matter of treason - guilty. In the matter of conspiracy to commit treason - guilty. In the matter of aiding and abetting the murder of Marlene McKinnon - guilty. In the matter of aiding and abetting the murder of Benjy Fenwick - guilty. In the matter of aiding and abetting the murder of Edgar Bones and his family - guilty. In the matter{\el}"

Snape hung his head and stared at the floor as the list droned on and on.

"{\el}and in the matter of aiding and abetting the felonious assault against Frank and Alice Longbottom - guilty. This completes the charges. And for these crimes for which you have been found guilty, Severus Snape, this Council sentences you to a term of fifty-five years in Azkaban prison with opportunity for parole following a period of good behavior of twenty years. The Council of Magical Law has spoken."

The head of the council then rose in the ensuing silence. "Mr. Snape," he said, and when there was no reply, he repeated, "Mr. Snape? Please look at me." Snape looked up, his eyes vacant. "Mr. Snape, I am Faustinus Oglethorpe and I am pro tempore head of this council in the temporary absence of Bartemius Crouch. There are several things we still have to cover, but I first need to ask you. Have you heard the verdict and sentence, and do you have anything to say at this time?"

"I heard, sir. I have nothing to say."

"Very well. You are clearly unfamiliar with this type of proceeding, so I would like you to notice that you are standing freely in front of this council rather than sitting bound in the accused's chair. This is highly unusual for a person who has just been found guilty on all counts, and you should take it as a favorable sign. You are not going to Azkaban, at least not yet."

Snape looked at him in earnest then, and glanced over at Dumbledore, who appeared hopeful. A glance in the other direction showed him that Rufus Scrimgeour was not happy, and that both Robards and Moody seemed displeased.

"Professor Dumbledore," continued Oglethorpe, "has given this council detailed information about your activities over the last year and two months which I won't go into in detail, but let me highlight a couple of points. First, of your own initiative and volition, you approached Professor Dumbledore with information that thwarted the plans of Lord Voldemort, even though you were one of his servants. You then returned to your position with Voldemort, placing yourself in considerable danger, and continued to supply Dumbledore with information that was instrumental in saving the lives of our people and even resulted in the capture or death of Voldemort's people. Most impressively, you've never asked for any kind of reward for these actions, not even now at your trial and sentencing."

Oglethorpe paused and glanced through his papers. "This would speak most highly in your favor were it not for some very disturbing aspects of your behavior. We have also been informed, and Dumbledore admits to the truth of the accusations, that you continue to show support, if not for Voldemort, then for Death Eaters who were Voldemort's operatives. This support extends to Death Eaters whom you know to have committed crimes, serious crimes. Not an hour and a half ago, in my presence, you continued to refuse to cooperate with our law enforcement people, even though your own freedom was at stake.

"Because of your service to us, this council is inclined to be lenient. Because of your contradictory and ambiguous behavior, we hesitate. Hear now the decision of the council. You have been found guilty and sentenced. Your service to us does not earn you a pardon, but we will grant you a suspension of that sentence. You are hereby remanded into the custody of Albus Dumbledore during the time of your good behavior. So long as your record remains clear, you will be free to come and go as long as you remain under Dumbledore's authority. Should you ever be found guilty of a future offense, however, the sentence here and now passed on you will be put into effect. Do you understand?"

"Yes, sir."

"Do you have anything to say?"

"No, sir. Thank you, sir."

"Then you are free to go. Albus Dumbledore, I remit Severus Snape into your custody. You may take him back to Hogwarts. See that he doesn't get into any more trouble."

The council began to break up into groups that filtered out the doors. Robards came over to shake Dumbledore's hand and offer congratulations. He didn't speak to Snape, which was probably just as well since Snape didn't want to speak to him. Scrimgeour stomped off, but Moody hung around to exchange a few words with Dumbledore.

"Guess that was about as good as you could expect, all told," Moody said. "You have a happy New Year, Albus." Then he looked at Snape and said, not unkindly, "Good behavior. You remember that. We'd hate to see the clemency of the court wasted." And then he left.

Outside, Hagrid was on pins and needles. When he saw Dumbledore and Snape together, he beamed. "Figured it had t' be pretty good 'cause of the scowl on old Scrimgeour's face when he come out, and if ya was going to Azkaban, ya wouldn't be standing here now. But it did take a long time, didn't it? So they found ya innocent?"

"Guilty with extenuating circumstances, I fear," said Dumbledore, "but that should be kept between the three of us. As far as anyone else knows, he is free. Now, shall we get back to Hogwarts?"

The reception at Hogwarts was gratifying, for the other teachers had prepared a small party, in the event that Snape came back to them, and they ended up laughing and joking, and playing silly parlor games like charades. Snape got tipsy enough to justify Hagrid's seeing him to bed, which gave Hagrid the opportunity to be sure his door was left unlocked during the night - just in case.

\subsection{Thursday, December 31, 1981}

It was dark and snowing the next morning when Snape awoke, and the dungeon rooms felt icy and damp. Snape lay in bed for a while, fighting a desire to simply roll onto his side and sleep again - sleep for hours - sleep forever. He couldn't see the future. It was as if there were no future. Just today, and the struggle to get out of bed.

Lying there was easy. It was warm and dark and quiet. He didn't have to think because there was nothing to think about. Nothing important in the world ever again, with the warm blankets wrapped around him like a cocoon. Like a shroud. Nothing at all{\el}

Except Hagrid.

Snape's eyes snapped open. \emph{What time is it? It's winter. It's always dark in the morning. Hagrid might be coming soon to haul me out of bed, force me into some clothes, and drag me to breakfast. And tell me how lazy I am, and how disgusting and careless.}

He didn't want that. He wanted to show Hagrid how wrong he was, how mistaken in his opinions. Snape checked the clock. Six-thirty. Half an hour before the house-elves would start putting food on the table. Full of resentment against Hagrid and his bullying, Snape threw back the blankets and stepped onto the cold stone floor.

For some reason, as he poured water into a basin for his morning ablutions, Snape thought of the magnificent teachers' bathroom on the third floor. His mouth tightened in scorn. Decadence and luxury were for those still under the illusion that life was good, life could be pleasant. At that moment, Snape was quite proud of the uncomfortable, Spartan arrangements of his own life.

In his wardrobe, all the clothes were black. As a boy he'd worn whatever muggle clothes his parents could get for him, but he'd loved the black of Hogwarts's uniforms and the contrast with his own, spectral features. It had been dramatic. Now the black had other meanings - mourning, death, and funerals. Black was also the color of priests and Dominican monks, of Jesuits, people bound within a life of physical austerity and dedication, finding a measure of freedom only in the mind and the world of the intellect.

Dressed and ready, Snape caught a glimpse of himself in the small mirror. Never handsome, his mother's lank, dark hair and long thin face highlighted by his father's aquiline nose and strong chin, the youth of skin and flesh contrasting sharply with the cold, hostile, intelligent eyes, eyes so dark they looked black. A face that eminently suited the way he felt.

Seven o'clock. He would show Hagrid. He was no weak baby to be coddled and coaxed. He'd go right into the Great Hall and eat his breakfast of kipper, toast, and coffee, and maybe even play a game of cribbage with Flitwick, so no one could say he was cowed by the events of yesterday, that he was weak or beaten.

Erect and defiant, Snape stepped into the corridor.

The problem, of course, was that no one expected him to be cowed by the events of the previous day. Since the only one who'd actually witnessed his ordeal was Dumbledore, everyone else thought he should be pleased and relieved by the outcome. It's particularly hard to be solemn, somber, and aggrieved when others insist on congratulating you on your good fortune.

Dumbledore understood. He rescued Snape from the heartiness of Kettleburn and the maternal clucking of Sprout to eat with him undisturbed in a corner of the hall. "I am pleased to see that you have the fortitude to face the world today," Dumbledore said after they'd sat down. "You have been through quite a lot."

"Truth? I couldn't bear the thought of Hagrid banging on the door to get me up. Coming myself was easier than facing him."

"Hagrid does serve some amazingly useful purposes. I shall have to remember that one. Do you mind if we talk here and now, or would you rather go later to my office?"

"Here and now is fine, sir."

"Excellent. I should first like to hear from you your impression of what is required of you from this point."

"I belong to you, don't I? I stay at Hogwarts teaching, and if I ever do anything wrong again in my whole life, I spend the rest of it in Azkaban."

"You do not belong to me, I do not own people. The phrase about being under my authority does seem to imply that you are expected to remain here, at least for the time being. I hope that you might come to enjoy it, or at least to accept it. I fear I must warn you, however, that your tribulations are not entirely over."

Snape raised his eyebrows. "What else is going to happen?"

"I have been in contact with the Ministry, trying to cancel Rufus Scrimgeour's contract to teach Dark Arts here. I have not been successful. It would seem that the Department of Magical Law Enforcement is sufficiently discontent with me that they will not give up an opportunity to keep me under surveillance."

"Or me either," said Snape with a sigh.

Dumbledore left the Great Hall to attend to business, but Snape decided to stay. He conjured parchment, ink, and quill, and poured himself another cup of coffee. Instead of writing, however, he sat in thought.

"What are you doing?" Sprout asked as she came to sit opposite him.

"It's New Year's Eve," Snape responded.

Sprout regarded him for a moment. "That seems to be the answer to a whole different question. Let's try this again. What are you doing?"

"Sorry. Muggle tradition. My dad used to do it all the time. New Year's Day is a time of new beginnings, clean slates. So you make yourself promises of what you're going to do and not going to do in the coming year to make your life better. They're called resolutions. New Year's resolutions."

"Did they make his life better?"

"Not really. He could never keep them longer than a day or two, then he slipped right back into the old habits. Still, it's a time to review your life and see if you approve of the direction it's going in."

They sat for a moment, Snape neither writing nor elaborating. Sprout began to fidget. "Right," she said, "I take it this is a personal and private ritual, so I'll be talking to you later. Do you expect it to take the whole day?"

"I don't know yet."

Snape sat thinking for a long time, then gathered his parchment and quill and, as the morning progressed, moved from place to place in the castle seeking inspiration. His father's resolutions had always been very specific, very drastic, and very easy to break. Resolutions like, `only one drink at the pub on the way home from work.' Impossible for a man like Toby to keep, and bound to be broken the first time he set foot in a boozer. Resolutions needed to be broad principles of life, not specific behavior modifiers.

In the end, Snape came up with three.

First: Be Prepared. He had walked into that trial knowing nothing about the wizard legal system, nothing about his opponents, and unready for the questions they would ask. Once in his life he'd truly prepared for something, and that was his interview after the Dark Lord realized there was a spy at headquarters. Then he'd known his life was on the line. Now he knew that his life was on the line every day. Every chance question, every casual observation, might hide a potential threat.

Second: Trust No One. He'd trusted Bella, who hadn't really wanted to protect him, just use him. He'd trusted appearances in the death of his grandmother, when it was part of a plot to trap him. He'd trusted Dumbledore to get him through the trial, not realizing there were some things Dumbledore couldn't do. Nothing is what it pretends to be. Everyone is looking out for his own interests first. No one takes care of you but yourself.

Third: Reveal Nothing. How many comments made lightheartedly to how many people in passing could be dragged up later to use against him? Even this morning, talking to Sprout. There were people who hated muggle-borns and half-bloods, and he'd let slip that his family had followed muggle New Year's traditions. Sprout would probably never use the information against him, but what guarantee did he have that she wouldn't casually pass it to someone else until it fell into the hands of the wrong person?

Three New Year's Resolutions

1. Be Prepared.

2. Trust No One.

3. Reveal Nothing.

Snape wrote them carefully on a fresh piece of parchment and tucked it into a pocket of his jacket. He would think about them all day, and look at them again at midnight.

Most of the staff stayed up that night waiting for the New Year, because after all it was a new year - 1982. There were refreshments and conversation, and games as well. Snape didn't talk much, though the fact that he was playing cribbage with Flitwick was taken as sufficient reason, and the others saw nothing odd about it.

Sprout came over just before midnight with a glass of mead for him. Snape looked at it, thought about how talkative he got if he'd had a glass or two, and said, "I think I'll have pumpkin juice, thank you."

At midnight they toasted the New Year, then went to bed. Before going to sleep, Snape looked at his resolutions again, guideposts for the rest of his life: Be prepared, trust no one, reveal nothing.

The students began arriving at school on the second of January, and by the evening of Sunday the third, they had all returned. Snape made a brief appearance in the Slytherin common room to welcome everyone back and wish them a happy new year and a successful term before they went to the Great Hall for supper.

There Snape had a most unpleasant shock, for Professor Scrimgeour was sitting next to Professor Dumbledore, and Alastor Moody was in a chair next to the place where Snape usually sat.

His first instinct was to turn and leave, but that course of action was already too late, for Moody had been watching for him and half rose from his chair to beckon. Snape steeled himself for this new ordeal and walked across the Hall with apparent calm to take his seat at the high table.

"Hope you don't mind my dropping in and disrupting your seating arrangements. Rufus wanted to come down early and check his room and all the plans for tomorrow. I thought I'd pop along and make sure Albus knew we didn't harbor any unnecessary grudges."

"What would you consider a necessary grudge?" Snape asked, knowing Moody was playing with him, a little cat and mouse game.

Moody grinned. "Right to the chase. Spirit coming back now that the worst is over? I'm sure Dumbledore's pleased. Don't you fret. I'm only here for dinner, then I'm going home. It's just Rufus who's staying the night."

"I'm devastated."

"Thought you would be. You won't believe what I've been doing the last couple of days. Checking up on old, old laws. Things that've been on the books for ages, nobody remembers them, but they've never been repealed. Did you know, for example, that after Cyprian Youdle was killed by a curse during a Quidditch match, a law was passed making it illegal to move widdershins around a Quidditch pitch?"

An open, undisguised threat. "Are you planning to observe our next Quidditch game?"

"I might. And I've presented you with a puzzle. Do you dance to my tune and carefully walk clockwise the whole afternoon, or defy me and risk being arrested for breaking a six hundred twenty-four year old law?"

"I see you've thought this out very carefully." Snape was now beginning to imagine all the other laws he didn't know about that could trap him.

"It's the ones that get away that keep you awake at night."

A very large chair banged against the stones between them. "Sorry 'bout that," Hagrid said genially. "I just noticed ya was occupying all Mr. Moody's attention, and I thought I'd come down and socialize a mite. Shove over there, Professor, so 's I can get me chair in."

Snape moved quickly to his left to allow room for Hagrid between him and Moody. \emph{That's another one I owe you, Hagrid. Maybe getting dragged out of bed from time to time is a small price to pay.}

Hagrid proceeded to entertain Moody with tales of famous dragons, the disadvantages of trying to control gnomes with jarveys, and methods for removing chizpurfles from the fur of crups, which led to a heated discussion about the need for licensing crups and docking their tails, a practice Hagrid considered cruel.

Dinner over, Moody took his leave of Dumbledore and Scrimgeour, saving his parting shot for Snape. "I'm looking forward to being able to welcome you back to London. Got a reception all planned. Don't be a stranger, now." Then he was down the hill and gone.

Snape didn't go to the staffroom that evening after supper, preferring to stay in his rooms trying to calm down and prepare for classes.

Things got worse in Potions the following day, for after Snape spent fifteen minutes explaining and demonstrating to a fourth year class the proper way to decant armadillo bile for a Wit-Sharpening potion so as not to injure skin or damage furniture, a Gryffindor student named Miss Kestrel did exactly the opposite, causing second-degree burns on her partner's hands and leaving a turnip-shaped mark etched into the tabletop.

For the first time in a long time, Toby's demon flared, and Snape's hand was halfway to Miss Kestrel's face before he realized what he was doing. He jerked the hand back with an almost superhuman effort, shaking with fury and a pent-up anger that found release through his tongue.

"Do you take notes so that you can study how to do things wrong, Miss Kestrel? Because an error so glaring and counter-intelligent could hardly occur by accident."

Miss Kestrel returned to her Potion, contrite and frightened, while Snape went to his desk to try to still the pulsing rage. \emph{I almost hit a student. Thank goodness I was able to control it. Striking a student - it's the worst thing you could do. Never touch a student. Never. Never. At least I was able to control it. Dumbledore knows about the time I hit Lily. I need to tell him about this. Thank goodness I was able to stop myself.}

"I want to be certain I understand this correctly. You wished to strike her, raised your hand to strike her, and then did not?" Dumbledore sat at his desk, calmly observing Snape's tense figure as he stood by the fireplace staring into the flames.

"That's right."

"Why did you wish to do that?"

"I was nervous. I was upset. I'd just spent all that time showing them what to do. It was like she was mocking all my efforts. Students are supposed to listen and follow instructions."

"Fist or open hand?"

That got a surprised reaction, then Snape relaxed. "You asked that question the first time, with Lily. Open hand."

"How did your father used to hit your mother?"

"Does it matter?"

"It might."

"Back of the hand. Fist if he was really drunk."

"And you?"

"I never hit my mother."

"I mean how did your father hit you?"

"Backhanded. Or he used something, like a belt."

"Why?"

"We would make him angry. There were things we were supposed to do, and{\el} how we were supposed to talk to him{\el} We never seemed to get it right."

"Like Miss Kestrel."

"You're trying to tell me that I'm like my father. I know that. I've known it for a long time."

"What made you stop?"

Snape stared into the flames again. "There are things you don't do. You don't use magic against muggles. You don't hit students."

"Did you have any of these impulses before the{\el} events{\el} of the Christmas break?"

"No."

"Let us hope, then, that this was an isolated incident. I would not dwell on it excessively if I were you. Should there be a recurrence, you will, of course, inform me."

"Yes, headmaster."

On his way downstairs for a quick bite of lunch before the afternoon classes started, Snape was surprised by the sudden appearance of Rufus Scrimgeour just leaving the Dark Arts classroom, apparently heading in the same direction. \emph{Does he watch me? Has he been waiting for me?} Snape hurried past as if he hadn't seen the auror, slipped quickly into the Hall for a small plate of food, and went to his own rooms.

\emph{They're controlling my life. They control where I eat. They control where I relax. They affect my relations with the other teachers and the students{\el} How can I allow them to do this?}

For the rest of the lunch hour, and during his free time over the next few days, Snape pondered what he could do to escape from the tyranny, real or apparent, of Rufus Scrimgeour and Alastor Moody.

Thursday night was clear and cold, and Snape slipped out of the school after ten o'clock to finish his rounds and look at the sky. The moon was nearly full. \emph{In fact, if I were a werewolf, the metamorphosis would start tomorrow. Saturday night it will be at its peak. }Which was the precise moment that he realized that tomorrow night at midnight would begin his twenty-second birthday.

\emph{Another new beginning? Another clean slate? Or will the coming year be as horrible as the last year was? If tomorrow night is as clear as tonight, maybe I'll come out at midnight to greet my birthday with the full moon. At least I'll be reasonably sure not to meet Scrimgeour.}

\subsection{Saturday, January 9, 1982 (the full moon)}

Late the following night, Snape threw his cloak over his robes and went out into the dazzling midnight world of full moon and white snow. It was beautiful, silent and serene, cold, pristine, and peaceful. Snape drew the frosty air into his lungs, aware only now that for the past few weeks he'd not been able to breathe in the castle.

The light snow on the lawn was marked with paths trodden by students during the day, and Snape followed the widest of them to the edge of the hill where the road led down to the Hogsmeade gate, the Quidditch pitch, and Hagrid's hut. There was a light in Hagrid's window, and Snape could see him moving around inside the hut. \emph{I wonder what he's doing up? Probably helping some creature hatch, or caring for the sick and injured. It would be wonderful to have a life so relatively uncomplicated.}

Turning back, Snape retraced his steps, but instead of going into the castle, he veered left toward the cliff face. There was a path here that led down to the lake, the light of the moon making it clear and easy to follow. Snape wound his way down to the narrow lake shore and the rock where Lily used to sit and talk to him.

And bring him cake on his birthday. Little cakes, just right for two people, cajoled out of the elves in the kitchens. There had been three people in his life who remembered his birthday - his mother, his father when he was sober, and Lily. All three were dead, but tonight under the full moon he could feel their presence as if they were still with him.

Snape walked to the edge of the frozen lake. The ice was crossed and swirled with the tracks of skates, moonlight glinting from crystals strewn up when the students raced and glided over its surface in their free periods during the day.

It was very cold, but Snape didn't want to leave. He wanted to hold the sparkling magical moment forever. Glancing around, he focused on the rock. \emph{I'll sit by Lily's rock for a few minutes and pretend it's nine years ago, and Lily's just brought me cake for my thirteenth birthday.}

He brushed the snow away from a patch of dead grass so that it wouldn't grow damp under him, and sat huddled next to the rock, his cloak pulled around him, his fingers tucked under his arms to protect them from the biting cold. Then he thought, \emph{This is crazy. I could at least make a little fire and be more comfortable.} A wave of his wand, a spoken word, and the fire glowed near his feet, very brightly at first, then subsiding into soft flickers. Flickering. Dancing against the backdrop of white and moonlight, entrancing in its constantly changing changelessness. Severus dozed, and eventually the fire died.

\emph{He was warm, warm and comfortable, his limbs relaxed in pleasant drowsiness and the comfort of knowing he didn't have to wake up, not today. `Come on, Russ,' his mother called, `you can't stay there forever, sleepyhead.' - `It's all right, mum,' he answered. `It's Saturday, and it's my birthday. On your birthday you can stay forever anywhere you want.'}

\emph{`Do you miss me?' Lily asked. `I'm sorry I didn't miss you as much as I should have, but husbands and babies keep you very busy, you know.'}

\emph{`Yes,' he answered. `That's what I heard. I thought about you a lot, especially that last year. I wanted to do so much.'}

\emph{`There's still so much to do. Don't let them beat you down. You're a fighter. You've always been a fighter. I told James. He wouldn't believe me, but he found out.' She laughed, then she touched his arm. `Don't let this make you stop fighting.'}

\emph{`I'm scared, Lily, and I'm tired.'}

\emph{`I know. Lovely, dark, and deep. Promises. Miles to go{\el}'}

\emph{`Before you sleep, Russ,' his mother called. `Chores to do before you sleep. You can't lie there forever, even if it is your birthday.'}

\emph{And then Toby was yelling at him. `What're you doing here, lad? You can't sit out here all night! Wake up!'} He threw his hand up to protect his head from his father's blow, but the blow never landed. Instead, Toby was shaking him, rubbing his wrists and hands, pulling him up out of the warmth into the cold, frosty night{\el}

"What the blame-all are ya doing out here?" Hagrid roared. "You start moving around, now, get that blood pumping!" Then Hagrid pulled off his own great coat and wrapped it around Snape's shoulders, its warmth battling the biting cold that weighed Snape's hands and feet. "Now move! Walk! I'm right beside ya. We're just going t' my place where there's a good fire and hot tea. I thought I saw ya up there on the hill a bit ago, then the flash when ya lit yer fire. Then when the fire died, I says, `Well, he's gone back inside t' bed', but something nagged at me and I says, `It won't hurt checking. No, ya can't sit down. Not yet. Ya just keep moving there."

Then Snape was staggering up the steps into Hagrid's hut, and was set before the fire, wrapped in warm blankets with a cup of hot tea in his hands while Hagrid pulled off his shoes to check his feet for frostbite.

"I was not trying to kill myself! I swear, I went out just to look at the moon, and it was so{\el} beautiful{\el} that I just wanted to stay awhile. I even made a fire. Ask Hagrid."

"That there is true, Professor. He did make a fire. That's what let me know he was out there to begin with. Well, that and seeing him on the hill."

"You saw me there?"

"It were a dandy silhouette 'gainst the moon, lad. No mistaking who it was neither."

"Still," said Dumbledore, "it is the third time in fewer months. Many would find a sinister meaning in the sequence of events. Do you promise me, Severus, that this time it was not deliberate?"

Snape looked directly into Dumbledore's eyes. "I swear, this time I was not trying to kill myself."

"I am content," said Dumbledore. "Now perhaps we should discuss the foolishness of falling asleep outside on a night as cold as this one."

"I didn't mean to do that either," said Snape ruefully, then added, "I saw Lily."

That attracted the instant attention of both Dumbledore and Hagrid. "Saw Lily?" Dumbledore asked, "Actually saw her?"

"Not actually. It was more like a dream. I saw my mother and father, too. Lily told me not to stop fighting, not to let them beat me down." Snape touched his left arm, the cloth of his robes under which lurked the skull and snake. "She said not to let this make me stop fighting. And she said something I didn't understand."

"Which was?"

"She said, `Lovely, dark, deep. Promises. Miles to go.' I don't know what it meant."

Dumbledore smiled. "It is the intrusion of the inexplicable into an otherwise easily explained occurrence that promotes in us the belief in the supernatural."

"Sir?"

"Last night's experience, Severus. You dozed off and, as you were succumbing to the cold, you had a dream. That dream expressed certain desires of your heart - that you would see your parents and Lily again, and that you would find some way to fight back against the forces that are trying to push you down. All of them the simple wishes of your subconscious mind expressing itself in a dream - until we get to the inexplicable. Are you certain you do not recognize the words?"

"I don't think so."

"They are from a poem about a man who also stops to contemplate the beauty of snow falling at night. The last lines are thought by many to expressing a longing similar to Hamlet's - "The woods are lovely, dark and deep, but I have promises to keep, and miles to go before I sleep."

"I'm sorry, sir. I don't understand about Hamlet either."

"Ah! One of Shakespeare's most famous. `{\el}to sleep, - no more; and by a sleep to say we end the heartache and the thousand natural shocks that flesh is heir to, - 'tis a consummation devoutly to be wished. To die, - to sleep{\el}'"

"I didn't realize you knew so much about Shakespeare."

"I do not. I am merely intrigued by this muggle attitude toward death and dying, the acceptance of it as a natural, gentle, and even desirable thing. Something Moriarty would not have understood."

Snape thought for a moment. "If this dream came from my own mind, how could it tell me part of a poem I don't remember reading? Could that be proof it was really Lily speaking to me?"

Dumbledore reached forward to lay a finger over Snape's heart. "Part of Lily lives right in here," he said, "and will continue to live here as long as you yourself are alive. As long as you do not force that part to change into something she was not, she will continue to speak to you. The Lily of your dream, is that how she would have talked to you?"

"Yes, very much so."

"Then do not be distressed if you find that at some time in the past you read or heard that poem. It was still Lily talking to you. Perhaps at this point it would be well to think of your school days and remember that you had a reputation for refusing to be cowed."

"Thank you, sir. I'll do that, sir." Snape left Dumbledore's office somewhat more optimistic than he'd been for several weeks.

The first problem, of course, was defining the problem. \emph{Who is my enemy? Is the Ministry of Magic my enemy? I would say not, because Judge Bones didn't act like an enemy, and Faustinus Oglethorpe didn't really act like an enemy. So far the only people who've acted like enemies are the aurors. And that's because of the Longbottoms.}

\emph{The Longbottoms. Pureblood aurors. They were the real threat to the Dark Lord. When their son was born as the seventh month died, the Dark Lord should have recognized the true chosen one of the prophecy, and not gone after Lily.} It was the Dark Lord's error, his blindness, that had killed Lily, and Snape wasn't going to let any more aurors push him into feeling guilty about the Longbottoms. Their fate had been prophesied. It wasn't Snape's fault.

It then occurred to Snape that the family whose picture he'd seen at the trial had been named Bones. Edgar Bones and his family. Remembering the picture made him feel sick again, but he had to think about it because the judge's name was Bones, and he wondered if they were related. She knew whose deaths he'd been accused of, yet she'd been kind and fair. No, it was just the aurors. Maybe their job made them cruel and suspicious, but they were the ones who wanted people to be guilty, wanted them to be punished. Not the whole Ministry, just the aurors. Like Scrimgeour and Moody. And Robards.

\emph{They're going to keep pushing, trying to make me crack. What are some of the things they might bring up? If they do, what can I say that will show them I'm not afraid and at the same time not get me into more trouble?} Snape began to think of sentences, lines, remarks, and commit them to memory.

\subsection{Friday, January 15, 1982}

Defense against the Dark Arts classes were canceled the following Friday because Scrimgeour was not coming up from London. Something was happening, something special enough that Dumbledore was going down to London to observe.

"Normally, I am part of the Council that conducted your trial. I could not sit with them that day, since I was acting as your lawyer. Today I go as myself. If anything happens that you need to know about, I shall tell you on my return."

It was a very pleasant day at Hogwarts for Snape, knowing he would not have to see Scrimgeour until the following Monday, but Dumbledore had given him something else to think about.

\emph{Maybe it wasn't so smart letting Professor Dumbledore act as my lawyer. He's wise, and he knows the law, and he was on my side, but what I needed then was someone who knew all the twists and turns and tricks. Someone who understood how they can lead you from question to question until you're in the trap before you see it. Not someone wise, or even clever, but someone just as sneaky as they are.}

Dumbledore returned from London late in the afternoon and sent a message to Snape to come to his office after the last Potions class. When he got there, Dumbledore offered him a glass of elf wine, but Snape turned it down, preferring tea or pumpkin juice. Dumbledore eyed him quizzically.

"Are you embarking on a change of diet? I was under the impression that you enjoyed an occasional glass of wine."

"I did. But if I drink it, I start talking too much. I have to watch what I say."

"Loose lips sink ships. Muggles used to put that on signs. I think it was during one of their wars. By the way, have you been taking your evenings off?"

"No. I don't think it's wise to leave Hogwarts."

"I hate to have to say it, but that is probably an excellent idea. They're bringing people out of Azkaban to give further evidence in exchange for lightening their sentences. One of the ones they questioned today was Igor Karkaroff. He named you."

"Karkaroff knew me. Not well, but he knew who I was."

"I was glad I was there. I spoke for you and reminded the council that you had been released because of your actions against Moriarty, but you could tell by the faces that not all of them were convinced. Scrimgeour and Moody were particularly skeptical."

"I think I could have guessed that."

"There was something else. They have statements from the Lestranges and Master Crouch about the attack on the Longbottoms. The four of them were trying to extract information about the whereabouts of Moriarty. They want to locate him."

"Whereabouts? He's dead!"

"That was my impression, but it is not the opinion of Bellatrix Lestrange. She, it would appear, is firmly convinced that Moriarty survives, and that the aurors somehow know where he is. More than that, she believes that he will return and be restored to power. It is a disturbing thought."


