% A Difference in the Family: The Snape Chronicles (Rannaro)
% The Third Year

\chapter{Battles}

\subsection{Saturday, September 1, 1973 (3 days before the first quarter)}

Students in various stages of semi-Muggle dress wended their way through King's Cross Station trying not to be too noticeable. It was actually amusing watching how hard they and their parents worked at being invisible. Severus got his trolley and retrieved his meager packages from the locker, then made his way to Platform 9. He stood there as if waiting on the platform until there was a lull in the Hogwarts traffic, then calmly slipped through to Platform 9 3/4. As he pushed the trolley to the baggage area, he overheard snippets of conversation.

"{\el} have to pass as many OWLs as possible or that new broomstick I want{\el}"

"{\el} and then we spent another two weeks on the Riviera{\el}"

"{\el} I heard the whole house just burned down, with them{\el}"

"{\el} fairly reeks of mudbloods and mongrels this year{\el}"

"{\el} tons of extra galleons because I'm so looking forward to Hogsmeade{\el}"

Leaving his baggage with the handlers and carrying only the Gladstone bag with his robes, Severus headed for the rear of the train where he hoped to meet and talk with Lily. He was surprised to hear his own name called from behind him.

"Snape! Wait. Hold on a moment."

Severus turned and waited as Bella Black hurried up. She smiled winningly at him as if they had been lifelong bosom friends. "I'm so glad I caught you here. Some of us Slytherins are getting together in the first cars, and you should join us. It's like a back-to-school House party. Come on. It'll be fun."

"I'm always{\el} dull at{\el} parties," Severus replied. "Not my favorite{\el} thing."

"You'll be fine. We have too many clowns as it is. We can use quieter ones to tone things down." She hooked her arm in his and steered him back along the platform to the front of the train where a crowd of familiar faces was milling around prior to boarding.

"Look who I found!" Bella called, and others came up to greet him and shake hands. Severus felt very out-of-place in his working-class clothes among all the children of rich old families, but everyone seemed truly pleased to see him. Then they boarded, and Severus found himself in a kind of club car with little tables. He was sitting with Evan Rosier, who started talking about his summer like an old friend. Tea, coffee, and various juices were brought to the tables along with an assortment of sweets. Severus was amazed at the variety.

At the other end of the room, out of earshot, Bella was in conversation with Rabastan. "I've done my part. He's here. Are you sure He's interested?"

"Are you joking? A second year who can conjure up an earthquake? Father was practically salivating when I told him. He told{\el} you know, and he's interested. He's just a kid now, but with the proper training he could be a powerful spell caster. We're supposed to take it easy, be sure he stays with us, not scare him away. We've got five years before he'll be ready, but{\el} you know who is willing to wait."

"What if Stumbledore is still hanging around him?"

"We back off. I told you. We have time. We can afford to do this slowly. We just be sure he develops in the right direction."

After an hour of listening to Rosier and to Wilkes who had joined them, Severus left the club car. He needed someplace quiet where he could think. Bella tried to stop him and lure him back, but Rabastan restrained her, mouthing the word `slowly' as he did so.

Severus met Lily near the other end of the train as she was making her way back from the baggage car. "What happened," she whispered, so that no one in the compartments could hear. "I was waiting for you."

"I was kidnapped," Severus replied, smiling slightly as their eyes met. He could feel the doors sliding gently open in his mind, and relaxed with a sense of homecoming that he didn't feel even in his parents' house. At her look of surprise, he added, "Bella Black wanted me to come into one of the front cars for a bit. They're having a Slytherin reunion." The two moved back to the area in front of the baggage car where they could talk freely.

"I thought they teased you all the time. Isn't that what you said last year?"

"Yeah, but Bella's in fifth year now, and she has her OWLs at the end of the year. I think she's already worrying about them and wants to be sure I'll tutor her in Potions. I'm not going to complain. Whenever she shows an interest in me, everyone else leaves me alone. It's almost pleasant."

Lily look puzzled. "That's not how her cousin talks about her in our common room. But he hates everything about his family and Slytherin, so maybe he's not exactly objective."

They chatted for a while, then Lily returned to her mates.

The sorting that evening was a revelation. Severus suddenly realized that he was no longer the smallest student at Hogwarts. Almost all of the new first years were shorter than he was. Nothing else about the sorting was remotely important. He didn't pay attention to a single name.

Lily sat, as usual, at the foot of the Gryffindor table. She and Severus exchanged `thumbs up' and smiled at each other. Further contact could wait until a safe and opportune moment. The feast was sumptuous, and this time Severus stayed to eat his fill. After all, the shock of his growth was now history, and his mum had figured out how to handle it. And the students around him seemed prepared to tolerate his presence.

At the moment when the sweets were served, there was a sudden interruption in the festivities. An explosion stopped the talking, and a huge smoky banner began to form in the middle of the hall. The banner carried a representation of a human hand balled in a fist with one finger extended and the legend, "Slytherin Sucks, Gryffindor Rules" emblazoned across it.

The entire Gryffindor table was stricken by sudden giggles. The Slytherin table expressed requisite rage. Severus thought it was mildly amusing. Only a few seconds passed before Headmaster Dumbledore rose and dispersed the banner, with a gentle admonition about courtesy and school unity. No one could identify who had perpetrated the dastardly act.

The feast being over, the four houses repaired to their respective dormitories.

The tenor of the term was set the next day as Slytherin house left its under-lake dormitories for a relaxed Sunday breakfast. The first out slipped and slid on a slime of seaweed that coated the floors. Rotting fish hung from the stone walls, and the stench of aged shellfish permeated the air. The members of Slytherin house gagged and retched, and swore vengeance on Gryffindor, for all were convinced that Gryffindor it must be.

War had been declared. Slytherin was in a state of siege.

Rabastan sat as head of the war council. "We can't let them get away with this. The honor of Slytherin is at stake. We stand now against our enemies, or we go down to glorious ruin in a blaze of vengeance!" (Rabastan was always in his element where drama was concerned. A pity that Hogwarts had no drama department.)

"Yes, but what're we going to do that'll half make up for what they did to us?" Avery had more of a talent for cutting to the quick of things.

"We could move the seaweed and stuff to their tower." Wilkes was roundly cuffed for his total lack of imagination.

"Let's make badges that say `Gryffindor is garbage'."

"We can wrap toilet paper around their tower."

Severus spoke up then in a quiet but confident voice. Curses always made him feel secure. "The fish and seaweed was because we're under the lake. They're up in the air. We have to do something with birds."

"But they're lions. That's not birds," Wilkes sneered.

Severus waved a hand in disgust. "And we're snakes, not fish. They didn't care. Why should we?"

"Go on, Cursemaster," cried Rabastan. "How can we destroy them?"

"Bird dung, feathers, and eggs. Tar and feathers. Rotten eggs. Not when they come out by the Fat Lady where they're expecting it, but dropping on them from the ceiling later as they come down to supper. Hitting them from the air outside during broom practice. And I would suggest{\el}" they all paused to listen, "the ones who hit us were the boys. Target only the boys. Let their own girls laugh at them. Let them be shamed by their own house. Divide them against each other and make them weaker against us!"

They cheered him then, and formed into groups to learn the Koutsoulia, Phtero, and Augo spells. Severus was mostly glad that Lily would not be a target, although the thought of a real fight against an open enemy was more exhilarating than he would have imagined.

By supper time it was understood that no quarter would be given by either side.

"It wasn't very nice," Lily said as they huddled in a niche along the north wall watching it rain. They'd brought lunch from the Great Hall and found a sheltered place. No one else was out in the cold and wet, and they didn't fear being disturbed.

"What they did to us wasn't very nice." Severus pulled a little vial of slime from his robes. "Smell that." Lily backed away in disgust from the stench. "That was all over the corridor. People were slipping and falling in it. It was almost impossible to get out of the robes." He'd been lucky. By the time he was leaving the common room, the corridor problem had been discovered. How he would have paid for new robes, he didn't know. "And we could've done worse. Someone suggested tar with the feathers, but we kept it to eggs. That washes." He didn't think she needed to know that the tar had been his idea.

"But a lot of the boys that were hit with that stuff had nothing to do with the first prank."

"And none of us had done anything at all to Gryffindor. We were all innocent."

Lily frowned. It was true. "It'd be better, though, if the only ones attacked were the ones who started it."

"Do you know who started it?"

"There's a group that loves practical jokes, but I'm not sure it was them." And that was all she would say, so Severus let the matter drop.

"How is Arithmancy?" Lily asked after a few minutes.

"It's all right. I wish it was something harder, though."

"Harder? You must the only student at Hogwarts who wants the classes to get harder."

"Yes, but the classes we have here aren't going to help me. I need physics, and chemistry, and algebra, and calculus{\el}"

"Why?"

"I'm going to be a scientist." The look on Lily's face said she thought it was a stupid idea. Severus wasn't sure he could explain it to her. He loved the pictures of laboratories in the magazines he'd gotten from Gra. They were so clean and orderly. And when you worked out a math equation, you didn't have to worry about nuances, or how someone felt. The answer was there in front of you on the paper. Severus's favorite voice in the world was the voice of the man counting down the rocket launches: "Six{\el} five{\el} we have ignition{\el} three{\el}" Total and perfect calm while doing something truly interesting and important. That was what it was like in a laboratory.

Severus showed Lily the double helixes he'd been doodling in his notebook. He tried explaining about them, but Lily seemed mostly impressed with how pretty they were. Severus realized she was bored. Something had changed between them, and he wasn't sure what it was. When they parted, both were thinking of other friends and things to do, not of the next time they would meet.

"Hey, Cursemaster!"

Severus paused on the steps outside the entrance to the Castle. He was on his way to Professor Kettleburn's class on magical creatures. Rabastan joined him and walked with him down the hill.

"I wanted to ask you about your hex work." Severus didn't reply. "I mean, you know, you're really good at little baby stuff, but did you ever try anything bigger?"

"Baby stuff?"

"Yeah. You know. Spiders and snowballs. I mean, Wilkes told me about the lice, and that was truly brilliant, but all you do is throw things and do hexes with small animals and insects."

"I seem to recall an earthshaking moment."

"Now that's what I mean. Something big. Something, well, dangerous. Ever invent a spell for something like that? Besides the earthquake."

"Not really. I never needed one."

"Well you should think about it. This thing with Gryffindor is getting bigger, and some of them are nasty and mean. I don't think they've realized yet that you're the source of the new hexes, but if they do, you're a target. You should have some good defense ready."

Rabastan returned to the castle while Severus continued on to his class. He didn't pay much attention to the magical creatures (in this case glumbumbles) because he had other things on his mind.

Back in his dormitory before supper, Severus dug into his footlocker and took out the Advanced Potions book. His mother had used it during her sixth year, and had taken notes in it on various potions. Nana, too, had added an occasional note when she saw place for improvement. But most of the copious annotations on many of the pages were in Severus's own cramped, spidery, almost illegible handwriting. His mother had given him the book when he was nine, and he'd spent the next years trying out the potions.

There were many that he couldn't do because he couldn't get all the ingredients, but where he could, he did. Things like gnat wings and dried lizard eyes were easy, as were most of the herbs. He'd nearly gotten the skin clawed off his right arm trying to get badger nose-hair, and shavings from the wooden leg of a one-eyed seaman had turned out to be more trouble than it was worth, yet overall the experience had been invaluable.

Here and there among the potions, though, he had experimented with charms. This book was the intellectual godparent of all the little hexes he'd used at Hogwarts. Many of them were accidents. Next to a potion requiring louse legs was the hex he'd stumbled on that later produced Wilkes's fine crop. Severus began to turn the pages, studying each note carefully. Rabastan was right. They were all simple hexes involving bugs and rocks.

But what if Rabastan was right about having to protect himself? He forced himself to remember the fight with the Lestranges on the hill, and how it had felt to realize that they were going to take him. The two Gryffindors—well, they had been two as well. Face to face was one thing. What if he was face to one and the other coming behind his back?

The first step was to decide what kind of spell might be useful, then try to make it. Severus went to the Great Hall for supper, grabbed a few things to take with him, and returned to Slytherin to work. It was just like first and second year all over again, but with a bigger enemy.

The short pudgy boy with the watery eyes and colorless hair glanced around the Great Hall. The two he was looking for were right in the center of the Gryffindor table, holding court as usual. Jokes, judging from the laughter around them. Moving sideways between the benches, the boy edged nearer until he caught the eye of the slender, dark-haired boy with glasses. He touched the side of his nose, and the boy nodded and whispered something to his companion. The taller, stockier boy looked over, gave a `thumbs up' sign, and continued his conversation.

After supper, they met in a corner of the Gryffindor common room. "{\el} and then Rabastan ran out and down the steps. He was calling somebody. `Cursemaster' was what he said."

The two others exchanged a significant look. "Cursemaster. Now that sounds like exactly what we're looking for, don't you think, James?" said Sirius Black.

James Potter, the boy with the glasses was grinning. "Got to be. Peter, did you get close enough to hear what they were saying?"

"Whoa. First things first," said Sirius. "Who was this spell caster so powerful that Rabastan lord-love-you Lestrange, for crying out loud, calls him `Cursemaster?'"

Peter chuckled. "You won't believe. He's the same year we are. The little pasty-faced one with the long black hair. The one that's so good in Potions."

James pursed his lips and made an I'm-trying-to-remember face. "Sirius, didn't we warn him last year about being your cousin Bella's lapdog?"

Sirius barked a loud laugh. "Sounds like the lesson didn't take. Sounds like he's moved up to Rabastan. Sounds like we're going to have to get our pretty little hands dirty."

James turned back to Peter. "Did you get close enough?"

Peter had to admit he didn't, but he'd remember one piece of information. "Snape," he said. "His name's Severus Snape."

"That's his name all right," said Sirius. "Snivellus Snake. There's a proper Slytherin name for you. Maybe we can rechristen him. Shiverus Shake sounds better, don't you think." Sirius jabbed an elbow into James's ribs and grinned.

This time it was four to one, Sirius, James, and Peter being joined by a thin boy with light brown hair named Remus. The whole school was in the Great Hall for supper the next day, and Severus had grabbed his handful of food to return to his dormitory when Sirius stepped out from behind a staircase right in front of him. James and Remus moved in from the sides to hold his arms, and James clamped a hand over his mouth. Together they hustled him into the chamber where first years generally waited before the sorting, then Remus and Peter stood guard outside.

"Cute," said James as he extracted Severus's wand from its loop in his right sleeve. "I'll have to remember that one. Must save a lot of time." He tossed the wand into the far corner. "Now, Cursemaster, you will sit, and we will talk." They pushed Severus into a chair and used rope spells to bind his wrists and ankles to the arms and legs.

Severus was thinking feverishly. He couldn't plead ignorance, since they'd overheard Rabastan. "I'm sorry{\el}"he started, but Sirius didn't let him finish.

"Apology? We don't want an apology. You got bird poop and eggs in my hair. We want payback."

"Rules first," said James. "We told you this last year, but you didn't want to listen. Now we have to slap you around a bit. You don't help Bella, or Rabastan, or Rodolphus. You don't attack Gryffindor students. You don't dabble in dark arts."

Sirius pulled out a tiny vial. "This is for you. Who knows what it'll do. You're a slimy Slytherin slug, and you're going to drink it." He pulled Severus's head back while James pinched his nose, forcing him to open his mouth to breathe. They tipped the contents of the vial down his throat.

Untying the ropes, they pulled him along the underground corridor to the entrance to Slytherin house. Severus's stomach was swelling, and he realized with horror that things were moving inside him. Depositing Severus on the floor in front of Slytherin, and setting a body-bind curse on him, they left, laughing. The things in his stomach were crawling into his throat, and Severus began to retch, vomiting up a huge slimy slug. Slug after slug spewed out of him as he lay helpless and mortified until Bella and Rodolphus found him twenty minutes later. They released the binding curse and helped him expel the slugs, assuring him that they would never again leave him to face enemies alone.

Severus was not cowed, however. A cold, murderous fury had settled in him, and he set his whole heart on vengeance.

Bella went back to the waiting chamber to get his wand, and then Severus sat up all that night in bed, analyzing what had happened to him. He was singled out. Why? Because Rabastan had called him `Cursemaster' for all to hear. What was the worst part of what they did? That was easy. It was being forced to swallow the liquid in the vial. He could still hear Black's voice, `Who knows what it'll do.' As it was, it was an uncomfortable and unpleasant prank, but the liquid could have been anything. Fear. Vulnerability. That was the worst part. Public humiliation and physical discomfort were important, too, but the sense of helplessness would stay with him the longest.

\emph{So. I make them feel helpless, too. Uncomfortable and publicly humiliated would also be nice, but fear is the most important.} All night he thought, but no plan would come, and finally Severus understood that his fear had nothing to do with magic. Brute physical force could not be met with hexes and jinxes. \emph{I have friends now. I can use them.} But that wasn't the answer either.

\emph{Never trust others for your safety. Just when you need them most, they desert you. If you can't take care of yourself by yourself, then you've been beaten.} In the end Severus settled for public humiliation, leaving the intimidation for a later time.

The next day both Sirius and James were hit by tripping jinxes and stinging hexes. Neither did them any damage, and they laughed and slapped each other on the back. "Is that Slytherin's best? Come on back, Cursemaster, we'll even give you the first two jinxes free." The retaliatory attack had been so pathetic that neither boy even considered a response. They assumed they had won.

Two days later, Nelson brought a small package. In it were homemade candies from Nana. Severus opened it at the table in the Great Hall, extracted one particularly tasty-looking one, and ate it with obvious relish. Then he tucked the box under his arm and returned to Slytherin house.

That afternoon Black and Potter found him in the fountain courtyard with his box from home. "Little Slytherins should share with their friends."

Severus sprang up, closing the box and taking out his wand. "They're mine. Leave me alone." He tried to leave, but they split to take him from both sides. Gryffindor was victorious while Slytherin fled ignominiously from the field of battle.

The box of sweets was small, but delicious, and Sirius and James finished them together in their room. Just before climbing into bed, James leaned forward, his hand on the bedpost. "Somehow I didn't think he'd be so easy to push around. I'm a little disappointed."

Sirius laughed. "You just like a fight. Go to sleep."

Severus, meanwhile, was not in bed. He was creeping past the Hufflepuff dormitories to the kitchens in the lower levels of the castle. A touch of his wand, a whispered, "Alohomora," and the doors opened. He had no trouble finding the great vat of pumpkin juice and emptying the contents of a small flask into it. The liquid was colorless, odorless, and harmless. Unless one had eaten certain candies the day before.

Morning dawned without incident, and all was well with Gryffindor. James stretched luxuriously in bed, then decided he was hungry. Together he and Sirius went to the Great Hall and sat down for breakfast.

A few minutes later, the giggling started. Sirius glanced around to see half his table staring at him. He turned to James and choked on his toast. James's hair was mottled with green and silver. From the shocked look in James's eyes, Sirius knew his hair must be blazoned with the Slytherin colors, too. In the minute that followed, the stares and giggling spread to Ravenclaw and Hufflepuff. The Slytherin students were less restrained. En masse, they stood and cheered. Sirius clambered onto the bench and glared at the Slytherins. Severus wasn't there. "Coward!" he yelled. "Where's the slimy little coward?"

He raged out of the door, James behind him, and teachers beginning to spill from the front table to head off the fight. There in the middle of the entrance hall stood Severus, wand in hand, calmly waiting. "Nice hair," he said.

Black stopped several feet from Severus, his own wand now in his hand. Behind him, Potter was trying to talk him out of his rage. Students were spilling out of the Great Hall, and they could hear Dumbledore, Hagrid, and the teachers telling people to step aside and let them through. The two antagonists were glaring into each other's eyes now, but only Dumbledore would have been able to warn Black of what that portended, and he was still battling his way through the crowd.

"You did this!"

"I presume you're talking about the hair. When am I supposed to have done it? I only just left Slytherin house and I haven't been in{\el}"

"Petrificus!"

"Stupefacio!"

"Accio wands!"

The air between the two combatants vibrated and expanded with the impact of their spells on Dumbledore's shield, and then both wands flew across the entrance hall into his hand. The Headmaster was furious. "You will both of you remain standing where you are. You will not move, and you will say nothing. The rest of you will either return to breakfast in the Great Hall, or you will go immediately to your dormitories to prepare for classes. Any student left in this hall after one minute, except for these two{\el} ah three, will be serving detention this evening."

The hall cleared. Dumbledore turned to the teachers, who were herding the students as quickly as possible up the stairs and out of the way. "Minerva, Horace, I am afraid I shall have to ask you to accompany me upstairs for this conference. And do you think you might find the prefects of your houses and bring them along, too."

"So, I am to understand that Gryffindor house and Slytherin house have been hexing each other all week, and no prefect has seen fit to inform the heads of their houses or to take any steps to stop the fighting."

The prefects hung their heads in shame, and both McGonagall and Slughorn vowed to watch their charges like hawks watch rabbits, and then the only ones left in Dumbledore's office were Dumbledore, Hagrid, James, Sirius, and Severus. Sirius was speaking first.

"Look at our hair. Look at what he did to us. He's making fun of us in front of the whole school. Will it even come out?"

Dumbledore looked to Severus for an answer, and met the quiet black eyes. The boy was totally shut down, tight as a Gringotts vault. \emph{O Eileen, is there no child in there at all?} "Have you a response to this accusation?"

"I don't know when their hair turned green. I wasn't in the Great Hall. I didn't see it. Why would I want to turn their hair green anyway?" Severus turned his inscrutable gaze on Sirius.

James gripped Sirius's arm, seeing the pit opening in front of them. "He's right. There's no reason to think it's him instead of some other Slytherin."

"But he gave us something that made this happen!"

"You're mistaken," said Severus. "I've never given you anything in my life."

Sirius saw the trap then and shut his mouth. All three boys were silent. Dumbledore sighed. The trio was dismissed, but both Sirius and Severus were given detention for having raised their wands against each other.

Outside the office the three boys were forced to go as far as the staircases together. Potter placed himself between Black and Severus in an attempt to avoid physical violence so close to Dumbledore's office. "We know it was you," Black growled.

"And I'd love to be a fly on the wall while you explain to Professor Dumbledore why you think so."

"It isn't over."

"I didn't think it was." As the two Gryffindors started up the staircase, Severus added. "You might try shaving your heads."

Only the realization that Hagrid was watching from the end of the hall prevented bloodshed there and then.

"Did you?"

"Will you hate me if I say yes?"

"You did! Why"

Severus buried his face in the arms he'd wrapped around his knees. He really didn't want Lily to know about his own humiliation, but if he didn't tell her she'd think he'd instigated his attack for no reason. "They jumped me," he said.

"Go on."

The story came out slowly, about being dragged into the waiting chamber and losing his wand, being forced to drink the liquid, then lying paralyzed for twenty minutes vomiting up slugs{\el}

"Ugh! That is so disgusting! What horrible, vicious bullies! And all you did was turn their hair green? They got off lucky." Then she began to feed him information.

"The tall one, Sirius Black, he's Bella Black's cousin, but I think you know that. They're arrogant purebloods, but he pretends not to be. The one with glasses is James Potter. He's our new Quidditch Chaser. Quidditch? Oh, you. You know it's a game. I think his family's really rich or something. The pale one with the brown hair is Remus Lupin. He's kind of nice, but shy. He gets sick a lot. And the fat one with the little eyes is Peter Pettigrew. They've been hanging around together since first year, at least Sirius and James have."

He came away from their talk knowing more about the Four Horsemen than he did about what Lily was doing in her life. She didn't really want to talk about herself. Severus didn't push it, though, since he knew what it was like having people prying into your business when you didn't want them to.

Then Hagrid started seeing him again.

"Open wide, now. I think that one's a baby tooth doesn't want t' come out. Ya let me pull it and there'll be more room for the others. What'd them two do that made ya so angry anyway?"

"Nobody made me angry. I don't get angry. Go ahead and pull it if you think it'll help." It was a baby tooth with hardly any root. The extraction was almost painless.

"Ya got to do exercises for the muscles in the legs. Rickets always affects the muscles. Y're not going t' have much strength if ya don't exercise. Must've been something bad if not one of the three of ye was going to tell Dumbledore."

"Maybe there was nothing to tell. And I've been drinking the milk and eating what you told me. And there's no place to exercise."

"Yer mum should've given ya more proper food when ya was growing up. Then ya wouldn't{\el}"

"You leave my mother out of this!"

"So I'm talking 'bout that little upset with Black and Potter, and I got nothing. Not a rise out o' him. But when I start mentioning his mum{\el} Well, let's just say he was a mite `irritated.'"

"His mother, do you say? Hagrid, that is very enlightening information. We need a breakthrough with that boy. If it is his mother that brings up the powerful emotions, so be it. I would have wished for something less{\el} fundamental, but one cannot have everything."

"So. Do I start working on him?"

"Hagrid, you already have."

The war went underground. First, Professor Mullein spent a fruitless two days trying to discover why the Venus Flytraps in his Herbology class had developed a sudden fondness for Severus's nose, then Black went around with his left hand hidden up his sleeve for nearly a week until he could figure out how to get rid of a wart that bore an uncanny resemblance to Professor McGonagall's hat. After picking up a quill in Charms class, Severus found he was leaving sticky fingerprints on everything, ruining all his homework and gluing the pages of his books together. But all agreed that the piece de resistance was the hex on Black's voice one evening that gave him an extra ultrasonic squeak perfectly pitched for summoning bats.

Rabastan was beside himself with frustration. Severus was simply no longer interested in developing grander curses. He considered it entirely Rabastan's fault that Sirius and James had attacked him, and he flatly refused to work on hexes that would raise the combat level to the point of appearing on the teachers' radar screen. The Lestranges and their group backed down again and bided their time. At least the conflict with Gryffindor might push Severus a little further in the `right' direction.

Sirius had checked a book of advanced spells out of the library. It was open on his bed to the page with the Incendio charm. James glanced at the page, looked again, then gazed thoughtfully at Sirius.

"You can't use that one. It might hurt him."

"I want to hurt him."

"No, I mean really hurt him." James closed the book and carried it over to his own bed. "Fun's fun, but you've lost track of why we're doing this." He waited until he knew Sirius was listening. "We want to scare him away from the Black-Lestrange gang, not push him into it. At least that was what we tried last year."

"And it's gotten bigger since then. Now he's one of their lieutenants. No holds barred, I say."

"I think you're wrong. Rabastan doesn't go around looking like he's sucking lemons when he's getting his way. And the curses are still kid stuff. We know he can do more, we know Rabastan wants more, but he isn't doing it. There seems to be discord in Slytherin house."

"You want me to just let him get away with the bat thing?"

"You take things too personally. There's a third year kid in Slytherin who's known more hexes than anyone in school since day one, and every son and daughter of every What's-his-name follower in Britain is being nice to him. They're pulling him in to the dark side. We want to make them fail. Your personal grudge is getting in the way."

"Right. Like warts and bats are going to conquer the world."

"Warts and bats in third year. If you keep pushing him, what's he going to hit you with in seventh year? We have to start looking ahead. I'll wager Rabastan is. Lay off."

And Sirius laid off.

"I can't check for damage t' the hip an' leg joints if I don't look at yer spine."

"There is Nothing. Wrong. With my. Spine."

"Like there's nothing wrong with yer teeth or yer bones or yer muscles. Yer parents ain't been doing right by your feeding{\el}"

"My parents care for me the best they can."

"Best ain't so good then, judging by the result."

"This is over. I am going to class." A goal rendered difficult by Hagrid's bulk blocking the door.

Hagrid's pause reflected his puzzlement. It had been going well, the boy's ire had been rising, and suddenly he was cold as ice. Hagrid was no Legilimens, but even he could sense the mind shutting down and closing off. He stepped aside and let Severus go to class.

"And it was over. Like talking t' a wall."

"You switched the topic, Hagrid. You were on his parents, then you switched to him. It seems that when you criticize him, he can close you out. You have to press his vulnerabilities. Next time you examine him, let me know. I shall join you part way through. We have got to crack that shell."

\subsection{Thursday, October 25, 1973 (the new moon)}

The chosen ambassador was Remus Lupin. He spoke to Severus briefly in Potions, and they arranged to meet in the fountain courtyard. Severus was fifteen minutes late. "I had to check for traps," he explained.

"You don't trust me."

"Should I? I seem to recall that you jumped me."

Remus shrugged. "I'm not proud of that. The point is that it's history. They don't{\el} We don't want it to get any bigger."

"I think the term is escalate," interjected Severus, but Remus didn't appear to understand the reference.

"They're willing to forget the whole thing if you will. They'll stop it right now, and let you have the last jinx, just to show good faith." Severus radiated skepticism, and Remus bristled. "It's fair. We're not backing down from you, we don't have to. There's four of us. You've seen what we can do. Now we're trying to be nice because we think it's going too far."

"Four?" responded Severus. "I'd have said three and a half. Or even two and two halves. But how can you be equal partners when you miss one week in four?"

Remus's face flushed. "You think you're smarter than everyone, but you're not. You want this to go on? Then you should get ready to be beaten. You want to stop it now, accept our offer."

"I'll think about it."

"Don't think too long."

"Thanks for the warning."

Depressed by his lack of success, Remus left the courtyard and wended his way down the hill. Partway down he became aware of the smell of a small fire. The fire was properly banked and made with dry wood, so it's likely no one else would have noticed it, but Remus's olfactory senses were rather acute.

He crept nearer to discover that the builder of the fire was a girl he knew, a fellow Gryffindor named Evans. "Oh," he said. "Sorry to bother you."

"You're not a bother{\el} Remus, isn't it? It's just that I can't get this potion to come out right."

"I can't help you there. The best person I know in potions is{\el}"

"Yeah. I know. In Slytherin. And if I can't get this to work, I'm going to ask him."

"Do you know him?"

"Not really. Hey, do you feel all right? I know it isn't the full moon, but you look pale."

Remus could feel his face getting paler. "What do you mean, full moon?"

"Nothing, except{\el} This friend of mine is really interested in the moon, and I started noticing the phases, and then I noticed you tend to get sick when the moon is full. Are you okay?"

"Yeah, I'm fine. It's just{\el} It's Thursday and we have Potions, and I think I should get back to the castle. It was nice talking to you."

"You, too." Lily watched him leave. He seemed so lonely sometimes that she wanted to hug him and tell him that people cared. There was something about the hapless loners that brought out the caregiver in her. She knew Remus had James and Sirius, but she also knew he needed more. \emph{Why do I always go for the runt puppies in the litter?} She went back to her potion, wondering if Severus would help her if she asked.

\subsection{Halloween, Wednesday, October 31, 1973 (3 days before the first quarter)}

Nelson was not a particularly big owl, and on Halloween morning he came flapping in slow and heavy, winded by the load he carried. Severus watched the tawny owl with some trepidation, for owl mishaps were always a source of general mirth. Nonetheless, Nelson made it to him without falling into any of the food.

Severus held the owl for a return message, then opened the larger package. It was an algebra book. It was second hand, but it had the answers to the problems in an appendix in the back, and one of the previous owners had worked problems in the margins. It was, thus, a treasure. A smaller package held a book of logic problems and an envelope contained news clippings. Severus hoped that Gra and Nana were getting on well together because he did not want this bounty to stop. He scribbled a hurried `Thank you' to both grandmothers on scraps of paper and sent them off with Nelson.

Back in his dormitory he poured over the clippings. Someone in Czechoslovakia had discovered a comet that was heading toward earth even as he read. It was the "comet of the century." Skylab III was going up in November to photograph it. Suddenly space was his passion again, and he longed to see the lump of dirt and ice that was going to blaze its way across the heavens and flirt with the sun. He had to tell Lily, but he wouldn't see her again until the Halloween feast that night.

Severus pulled out the old\slash new algebra book, the book that contained information beyond the ken of Hogwarts, opened to the first page, and began reading.

"Well she clear never kept the right amount of milk at home. Look at the curve of that leg bone. It won't never be straight, and Eileen had somewhat t' do with that."

"I don't see why you keep bringing my mother into this."

"She had the care and feeding of ya, didn't she? If y're gonna take care of a child, ya got to learn what they need an' don't need. And I ain't talking about pencils in their school boxes."

"You are supposed to give me medical attention, not criticize my mother at every opportunity."

"And that medical attention is needed because of what Eileen wasn't able to{\el}"

"STOP talking about my mother!"

Dumbledore entered the hut without knocking, catching the flash of Severus's temper as he did. Close. \emph{Very close. Very near to the surface.}

"Are you discussing Eileen Prince's parenting skills, Hagrid? Surely that is not necessary. Eileen, of course, had no real preparation to be a mother, but I am sure she{\el}"

"You're doing the same thing! My mother did all she could for me, and she's worth ten of the two of you put together."

"Severus, your mother is teaching you dueling skills to compensate for her own lack of those skills while she was here at Hogwarts."

This was a new angle, and Severus wasn't sure how to deal with it. His fury was barely under control as it was. "You're wrong. She wants me to take care of myself. We learn from mistakes."

Dumbledore frowned. \emph{Too clinical. We need raw anger here.} "She has left you vulnerable to the very problems she says she is shielding you from. She will sacrifice your protection on the altar of her own ego."

"My mother's{\el} not{\el} like that. She won't{\el} ever{\el} hurt me. She wants me{\el} to be strong."

"There is the possibility she wants to live her life through you like some kind of maternal vampire."

Severus exploded in a blinding crimson rage and sprayed Hagrid with wasp stings. "You don't know!" he screamed. "You don't know her! She loves me!" Cinders burst from the logs in the fireplace, and clay cups leapt from the shelves to shatter on the floor. He spun on the window shutters, and they crashed open, splinters of wood spraying onto the garden outside.

Hagrid was moving, trying to block the spells that lashed at Dumbledore now, boils and blisters, carbuncles, warts, and pustules{\el} and screaming, all the while screaming, "You don't know! You have no right! You don't know her!"

Hagrid finally succeeded in pinning Severus's arms. He held the kicking, twisting boy above the ground while Dumbledore extracted his wand.

"Well," said Dumbledore calmly. "I think that was a success."

Dumbledore seated himself in one of the chairs, carefully laying Severus's wand on the table. Hagrid held the boy until his struggling weakened, then lowered his own bulk to the floor in front of the hearth. Severus was trembling uncontrollably now, his breath coming in gasps. Then, quite suddenly, he began to cry, huge sobs wracking his body. Instinctively, Hagrid began to rock gently back and forth, murmuring soothing nonsense, his hold slowly loosening until Severus lay limp in his arms, crying more softly now.

Dumbledore knelt beside them. "I fear there is one more thing to do, but it is better to do it now than try to force it later." Gently he unbuttoned the top of Severus's gown and drew both gown and robe away from the thin shoulders to examine the lash marks. They were several years old, but the faint color around the edges could still be seen. No muggle belt or whip had caused those marks. Eileen had beaten her son.

Dumbledore replaced gown and robe, and rebuttoned the gown. "I am sorry Severus," he said, "I shall not do that again." He put a hand on the boy's shoulder, but Severus turned from him and buried his face in Hagrid's coat. "I am leaving now, Hagrid. I think things will go more easily without my presence." Dumbledore rose carefully, brushed the dust from his robes, and went to the door. He paused to look at Hagrid, cradling Severus like a mother with a child. Magical creatures, both of them. Dumbledore closed the door quietly behind him.

"I know you think she's awful, but really, it only happened once. And it was my fault."

"Once? All that happened one time? Here, give this t' Herbert." Herbert was the youngest of the Thestrals and Hagrid's favorite. Giving him his feedbag was a little difficult since Severus couldn't see him. Luckily Herbert did most of the work, nudging the boy to show him where to fasten the straps.

"I used magic on m' dad. He fell down the stairs, and Mum had t' use healing spells t' save him. The Ministry was furious because they knew it was two wands and only one adult wizard. They threatened t' keep me out of Hogwarts. Mum was{\el} angry."

"I'll say she was. You got a bit of her temper, too. More `n a bit seems like. She never beat you again?"

"She stopped using magic. She put up her wand and only takes it out when we go to the moor to practice dueling. She says she can't trust herself."

"How old were you?"

"Nine."

The sessions with Dumbledore were becoming interesting.

Dumbledore at first tried to convince Severus that he didn't need to use Occlumency at all, but soon gave that up as hopeless. There seemed to be more to it than just Eileen's teaching, almost as if the shutting of his mind was an instinct. There were ways around it, though.

"You do not have to shut yourself off to keep people out. In fact, it is safer if you do not. I can tell if you shut me out. It gives you away. Try controlling the thoughts so that the ones you do not want people to see stay down, and the ones you want them to see come up."

It took practice, a lot of hard practice, but Severus was a good pupil, and with Dumbledore's help it gradually became easier to do.

\subsection{Thursday, November 15, 1973 (2 days before the last quarter)}

As he was leaving Potions class, Severus saw Lily ahead of him. He didn't call to her, but watched to see if she was going down toward the lake. She was, and he headed in the other direction to meet her there by a roundabout way. He hadn't had a chance to talk with her for a while, and it was lucky that she was going where they could be alone.

She was there ahead of him, but as he approached quietly he heard another voice, a boy's voice. He stopped. \emph{Who else knows about our meetings?}

Lily was sitting on her rock listening. Pacing back and forth on the beach in front of her was the thin, brown-haired boy who'd helped corner him in September. Remus Lupin. Lily had told him Remus's name, but she'd never mentioned she knew him as other than a fellow Gryffindor. Severus sensed an uncomfortable, tight feeling in the center of his chest that made it hard for him to breathe. He backed away, careful to make no noise, and returned to the castle.

\emph{Why him? What does she see in him? Can he tell her about things like comets and space launchings? He's just some pale washed-out nobody who's sick all the time.} Severus stopped pacing. Remus had been sick for three days about a week before{\el}

Severus hadn't been paying much attention to the phases of the moon, as the position of the moon wasn't important to a Skylab launch, but hadn't it been full just a week earlier? \emph{Is Remus always sick when the moon is full?} It was something to check.

"Ya seem preoccupied, lad. Somewhat bothering ya?" It was Severus's weekly checkup with Hagrid, and it usually lasted about ten minutes now, most of the major things having been covered.

"Why do you feel bad when your friend has another friend?"

Hagrid paused in the middle of checking the reflex in Severus's left elbow. The question was a milestone in his treatment, dealing as it did with actual emotion. And after only two weeks. "Uh, I would say that it was jealousy." He tapped the joint again. "Ya got someone t' be jealous of?"

"I don't know. I have a friend, but{\el} my friend is talking to someone else, and now I don't have anyone to talk to."

"If ya was friends with the other person, then there'd be three of ye."

"I don't think that would work."

"Ya got a problem with this other person?"

"Sort of."

He left a message the next morning at her desk in her Ancient Runes class. All it said was `Kohoutek. Today. Rock,' but she knew who it came from.

"Who's Kohoutek?"

"He's from Czechoslovakia. He discovered a comet. It's heading for the sun right now, and we should be able to see it pretty soon."

"I've never seen a comet."

"It's supposed to be pretty spectacular. It's supposed to be the comet of the century. They're sending up the Skylab III team today to take pictures. You want to try to see it with me?"

"Okay. Do we need a telescope?"

"I don't know. It'll be brighter after perihelion."

"And that is{\el} ?"

"After it goes around the sun. It'll be around for a while, so we just look for clear nights."

There were no clear nights for more than a week, but during the same time Lily found three occasions to talk by the lake with Remus Lupin.

Probably the most unnerving thing was the sudden tendency Lily had developed to giggle and worry about her hair. She was three weeks younger than Severus, almost fourteen, and Severus found himself paying more attention to other girls of their age to see if they behaved in the same silly way. To his great disgust, they did.

As November faded into December and the hills around Hogwarts turned white again, another female fulfilled her promise to become important in Severus's life.

"Snape, wait a bit, I need to talk to you." Bella Black was waving from the corner by the fire in the common room. Severus crossed the room and stood quietly in front of her, waiting. "Remember about my Potions OWL? You were going to tutor me for the exams."

"You were serious about that?"

"Of course I was! I don't joke about exams. We really need to get together so you can find out how much work I need. What about this evening after dinner here in the common room?"

Severus thought quickly. Slytherin house had no windows, but he knew the sky was gray and overcast. No Kohoutek tonight. "All right," he replied. "This evening after dinner."

It turned out that Bella, while a highly proficient spell caster, was a remedial potions maker in almost every way. Severus asked her about ingredients, measurements, heating, stirring, cooling, about moon phases and sidereal time, and Bella did not have a clue. And this was third year stuff. He insisted that she loan him her Fifth Year Potions book so that he could study it overnight. She obeyed without demur.

This was the biggest challenge that Severus had yet faced at Hogwarts, and for the first time his ego was on the line. He was the best Potions student in his year, in the years behind him, and for two years ahead of him. He might be the best Potions student in the whole school, but that was information beyond his ken for Slughorn noticed only three things: 1) Was your family old and famous? 2) Was your family rich and influential? and 3) Was your face pretty? Having none of these things, Severus was unnoticed by Slughorn, without Dumbledore's prodding.

But in the student world, the notice of teachers was of little import. It was the notice of other students that mattered. Who cared what Slughorn thought, or McGonagall, or even Dumbledore, if the other students acknowledged your position? Bringing Bella up to getting her OWL in Potions would mean status. It would mean reputation. It would mean respect.

The next night started Bella's tutoring, and Severus took her to the Potions classroom for the lesson. A whispered `Alohomora' and they were in. The expression on Bella's face was priceless, for it had apparently never occurred to her that he would commit trespass, and he could see that she was reevaluating his worth then and there.

They began with the basics, first year stuff, but basics that really were fundamental to the rest of the curriculum. And he made her tell him what was important about what she was doing. From time to time he got frustrated because it was so clear to him and she was so obtuse, but they avoided blows.

Then, after a week of lessons, Severus told Bella he could not tutor her that evening. He never said so, but the sky was crystal clear and now, two weeks before perihelion, the sky just after sunset was perfect for viewing the comet. He had already left a note for Lily, and they were going to the Astronomy Tower during dinner to try to see it.

Bella didn't have to be told anything. She sensed a rival, and she moved instinctively. First and foremost, you cannot act without information. Bella cornered Avery, and the two recruited a first year named Regulus, some kind of cousin of Bella's. Their orders were simple and clear.

Find out where Snape is going, and who he's with.

\subsection{Wednesday, December 12, 1973 (2 days after the full moon)}

Severus went up to the Astronomy Tower first. There was a light dusting of snow, but since no one else would be out on such a frosty evening, he was not worried about footprints. A few minutes later, Lily joined him. Together they watched as the sun sank below the line of hills.

"As soon as twilight deepens, we should be able to see something, as soon as the sunlight isn't overwhelming everything else," Severus explained.

The sun's disk disappeared, and the orange glow of sunset slowly faded. Their eyes became accustomed to the dark and—there it was. Far fainter than Severus had hoped it would be, Comet Kohoutek was still the brightest star in the sky. What's more, it had a tail. Not a long spectacular tail streaming across the heavens, but a short modest one. A tail, nonetheless.

The two watched the comet until the light of the rising moon dimmed the stars. It was time to go down to supper. Both knew this was probably the last time they'd talk in 1973 because Lily was going home for the Christmas break in less than a week. They would meet again in January.

"It'll be better then," Severus promised. "It'll be closer to earth, and the sun will be pulling the tall out across the sky. Lots of comets are so bright they can be seen in the daytime."

Lily went down first, and Severus followed a few minutes later. He was cold, but happy, and he planned to go down to the lake to watch the moon. He really didn't feel like meeting Bella for Potions after having shared Kohoutek with Lily.

Avery flopped onto one of the sofas, near enough to Bella so that they could talk without being overheard. Bella raised her eyebrow and waited. Avery had the air of a man with news.

"The half-breed has a mudblood girlfriend." The shock on Bella's face gave Avery so much pleasure that he wished he'd planned an even more dramatic announcement.

"That's impossible," she stated flatly. "I'd have known."

"Clearly you don't know everything. He went up to the Astronomy Tower by himself, so Regulus and I waited."

Bella's expression changed to one of greater interest. "That's a cold place for lovers to meet."

"A few minutes later that mudblood Gryffindor comes along and goes up onto the Tower, too, so I left Regulus as a lookout and climbed up myself. Had to go slowly because I thought they might have stopped on the stairs, but they were right out on the Tower watching the sun set."

"Cute. Where did they go after the sun went down?"

"They didn't. They stayed there watching the stars. It looked like they were looking at one in particular. Then I had to move fast because she came down by herself and went to dinner. Then he came down and went to dinner."

"Where are they now?"

"She's in Gryffindor house, and he's down by the lake watching the moon."

Bella dismissed Avery and sat gazing into the fire, pondering the unexpected strangeness of this information. She'd been unaware that Severus had continued his friendship with the Gryffindor girl after being warned in first year. Her initial reaction was to eliminate this mudblood as a factor, but she already had warning of how Severus reacted to force. Which was why Bella was handling this case and not Rabastan. No, a lighter touch was needed. A gentle, friendly touch.

Standing and moving to a desk, Bella pulled out quill and parchment. It took her a while to compose her letter, since it had to be just the right tone, but at last she was satisfied. She looked around. It was late, and everyone had gone to bed. Bella folded the letter carefully, sealed it, and went to her own dormitory. The next day she sent an owl.

By Thursday, there was an answer, the right answer. Bella gave the owl a tidbit from her breakfast plate and looked around for Severus. Alone in a corner, as usual. Bella went over and slid onto the bench beside him.

"You don't go home for the holidays, do you Snape? Rodolphus says you always spend Christmas here."

Severus nodded. "It's okay. It's quieter without all the students."

"But not a lot of fun. Look, I really need to work for this OWL Why waste a fortnight? Why don't you come spend the break with my family? It'd be mostly to tutor me, but we'd have a lot of fun, too. You could meet some people who could help you later after you leave Hogwarts."

Severus wasn't sure, but Bella painted a lovely picture of light and laughter, and being part of a family. The next morning in the common room he told her that he'd decided to accept her invitation and spend Christmas with the Blacks.


