% A Difference in the Family: The Snape Chronicles (Rannaro)
% Where Your Loyalties Lie

\chapter{A Hidden Menace}

\subsection{Thursday, September 12, 1991}

Quirrell was going on about werewolves at breakfast, and Snape was trying to tune him out. \emph{What if I told you I was almost killed by one. Would that shut you up? And didn't you say you were buying a book on werewolves that day you went down to London. Didn't read it, did you? Call yourself a Dark Arts teacher! You even used to be good. What happened?}

Then Severus rose from his seat as Professor McGonagall left the dais in a beeline to the Gryffindor table. Draco was there, along with the Crabbe and Goyle boys, and McGonagall seemed to be breaking up an altercation. \emph{She is so good at noticing things like that. Why don't I notice things like that?} With a perfunctory "Excuse me" to Quirrell, Snape went to meet McGonagall as she returned to her seat.

"Is my house causing you trouble? Did those boys go over there to start something?"

"It's nothing, Severus. The Longbottom boy got a Remembrall from his grandmother. Draco was teasing. It's over."

But it was not over, as McGonagall was gleefully prepared to inform him at supper that evening.

"Move over, Quirrell. I need to discuss a matter with Professor Snape." Quirrell moved, not wishing to cross McGonagall.

"I am ready to place that bet with you now, Severus. Five galleons on Gryffindor to win the Quidditch Cup this year."

"Five galleons? What did you do? Draft someone from Pride of Portree?"

"We have a Seeker. And it's not Wood. It's a new Seeker, a natural."

"I'm impressed. How did you find this prodigy?"

"Do you remember that bit of a tiff this morning over Longbottom's Remembrall? Well, it didn't stop there{\el}"

Draco was called into Snape's office immediately after supper.

"You teased a member of another house this morning over a gift from a relative."

"It was just that Longbottom kid. He's as stupid as they come."

"Which makes the teasing less sporting. You do understand `sporting' do you not, Malfoy? To make matters worse, you continued the teasing later on during Madam Hooch's Flying class."

"But he wasn't even there. She took him off to hospital."

"Nonetheless, you continued to tease, and threatened to leave his property up a tree. I am deducting ten points from Slytherin for your actions."

"You can't{\el} I didn't do anything wrong. I didn't hurt the dimwit. You're punishing me for nothing."

"You really don't understand. Let me put it in terms you can understand. You picked on someone weaker than yourself, which is not sporting. You brought the negative attention of another Professor on this house, which reflects badly on your housemates. Your continued teasing led to the discovery of a talented Seeker and may result in Gryffindor's winning the Quidditch cup for the first time in seven years. Does all of this seem like nothing to you."

"No, sir."

"I am pleased you are showing some sense. Ten points from Slytherin. And do not do it again."

"No, sir. Yes, sir. I mean{\el}"

"I know what you mean. Now get out of my office."

The next morning at breakfast, six screech owls brought the Potter boy a long, narrow package that could only be a broomstick. Snape leaned forward and looked down the table at McGonagall. The expression on her face was positively gloating. She seemed to sense that he was watching her, for she turned and gave him a `thumbs up' sign, then rubbed her hands together, chuckling.

It was Friday again, and first year Potions with Slytherin and Gryffindor that morning. Snape left breakfast early to go back to his office and try to center himself for the ordeal. After the problems of the first week, he had no idea what was going to happen.

What happened was a perfectly normal, well-behaved class. Potter's brain was clearly somewhere else, as was his partner's, the Weasley boy. \emph{Probably on the Quidditch field already.} The Granger girl seemed to be snubbing them both, and the Longbottom boy started at every sound, but otherwise caused no damage. Draco was glowering and resentful, but that could be due to Potter's new broom. Everyone else was subdued and attentive. \emph{What happened?}

The class now started the basic curriculum. "{\el} important that you understand the difference between an infusion and a decoction. Infusions are steeped; decoctions are boiled. Each operation gives a different part of the herb, so you must know what you are looking for. Infusion provides the volatile principles and essences, decoction the extractive and resinous principles. We shall learn later what these are for. Today we practice the techniques."

Homework was to write out the distinctions of tinctures, essences, syrups, fomentations, ointments, and poultices. Despite romantic misconceptions, the main function of Potions was healing. Snape's predecessor, Professor Slughorn, had not been particularly interested in medicines, but Snape made them the cornerstone of his class, a legacy from his witch grandmother.

McGonagall rescued Snape from Quirrell at about a quarter to seven. "Finished eating?" she said brightly. "Good. Quirinus, I'm going to steal Severus from you now. House business. Hope you don't mind." Together they left the hall, and McGonagall steered Snape outside.

"Don't thank me yet, I have ulterior motives," she confessed as they went down the stairs onto the lawn. In front of them, already walking down the hill toward the Quidditch pitch, was Harry Potter. He was carrying his new broomstick.

"I did so want to watch his first practice, but Wood says it will make him nervous. So I'm going to spy on them from up here." McGonagall pulled a small pair of binoculars from her robe. "I'm giving you the chance to assess the opposition."

Snape accepted the binoculars and focused them on the broom shed. Wood was coming out with a case of Quidditch balls and a couple of bats. Potter joined him and they went out of sight on the other side of the stands. A moment later a bludger sailed up from the pitch, then turned to attack.

"How long has Potter been playing Quidditch?"

"Wood says he knows nothing of the game. A novice, but a natural Seeker. There they go."

The two boys were in the air now, and Wood was tossing golf balls for Potter to catch. Snape had to admit the boy was good. Too good. Just like his father.

"So, Professor Snape, I propose a wager of five galleons that says Gryffindor wins the Quidditch Cup this year. Will you take the bet?"

"Minerva, you're going to lose five galleons."

September faded into October. The first Hogsmeade excursion was on Saturday, October 26, and nearly all the teachers were required to supervise. Aside from wanting to ensure that a substantial percentage of the Hogwarts student body didn't run amok during this day of unaccustomed freedom, it was the first Hogsmeade outing for the new third years, among whom were Fred and George Weasley. Just those two warranted the presence of three extra teachers.

It was a pleasant day, even a little warm, and Snape took his post on a bench outside The Three Broomsticks with a hot mug of mulled mead. Here he had an almost straight view down the main street and would see and be able to assist in any incident that arose. Professor Kettleburn came to sit with him and gossip for a while.

"Don't see how you manage to sit next to Quirrell every day and still stomach your food, Severus. I got a whiff of that turban yesterday, and it near knocked me out. Vampires my eye! There's something else in there, and he's using the garlic to mask the smell. Why'd he start wearing that thing?"

"Says it's a gift from an African Prince, and one gets used to what one must." Snape never let down his guard in Hogsmeade, and a movement to his right caught his eye. "You set off that dung bomb, Fred Weasley," he said without turning around, "and I'll have you hanging by your thumbs in Filch's office for the next three days."

"Yes, sir. How'd you know it was me?"

"Lucky guess."

\subsection{Halloween, Thursday, October 31, 1991}

Samhain. Halfway between the autumn equinox and the winter solstice. The ancient New Year. It was always a time of great feasting at Hogwarts, and today was no exception. That evening, the Great Hall was decorated with dozens of pumpkin Jacks o' Lantern, while Dumbledore thought to enliven the festivities with a thousand live bats. Professors Sinistra and Trelawney had places of honor in keeping with the holiday's traditions of astrology and divination. Mounds of food were served on golden platters.

Eating had already begun, but Quirrell was not yet in his seat. \emph{Odd for him to be late to dinner. Maybe he thinks the bats will attack his turban. Now that would be a Halloween to remember!} Snape chose his food carefully, not being overly fond of sweets. His attention was suddenly attracted by the doors opening in the back of the Hall.

It was Quirrell, and he was running. Right into the center of the Hall. His turban was at an angle, and he looked terrified. He made it to Dumbledore's table, gasped, "Troll—in the dungeons—thought you ought to know," and collapsed in a dead faint.

Pandemonium broke loose as students jumped from the benches yelling in panic. Dumbledore set off a couple of explosions from his wand that quieted the crowd. "Prefects, lead your houses back to the dormitories immediately!"

Snape jumped from the dais and managed to corner Higgs. "If the troll is in the dungeon area, you can't take them back to our house. The first floor is better, near the hospital wing. A troll won't be able to climb the staircases." Higgs nodded and began to herd Slytherin house toward the stairs.

Turning back to the high table, Snape watched as Pomfrey and Sprout revived Quirrell. \emph{That makes no sense at all. Quirrell's a troll expert. It's one of the few exceptional talents he has. Why would he faint at the thought of a troll?} He joined the crowd of teachers and students, making sure that all were heading toward safety.

Then the pieces fell into place. Quirrell in London the day before Hagrid was supposed to be there. A robbery already planned, but too late. Students all in their dormitories, and every staff member in the school heading for the dungeons to fight a troll. Quirrell was after the Stone.

As quickly as he could without attracting too much attention, Snape followed Hufflepuff house toward their dormitories, then turned into a side corridor. There was a staircase there that led up to the third floor and the room where Fluffy guarded the trap door leading down. He should get there well before Quirrell. Snape took the steps two at a time.

The corridor was empty, and the door locked. Snape slipped into a statue niche to wait. If Quirrell didn't come, well and good. If he did{\el}

Quirrell came a few minutes later. A muttered spell, the door opened, and Quirrell slipped inside. Snape left his niche and followed.

Fluffy was asleep. \emph{Not surprising. It has to be Hogwarts's most boring job.} Quirrell stood in front of the great three-headed dog, clearly pondering what to do next.

"What are you doing here?" Snape asked softly.

Quirrell jumped and shrieked. "I{\el} was{\el} worried about the{\el} Stone. Thought{\el} someone might be{\el} after it."

"I do believe you were right. Interesting coincidence, that."

Quirrell shrieked again, but this time it was because Fluffy was awake and moving. Pushing Snape aside, Quirrell jumped for the door. Snape staggered back, then dove down as Fluffy attacked. Wand out, Snape hit the center snout with a bolt of electricity, then rolled under the first head, nearer to the door. He almost made it. The third head grabbed for his left leg, and the teeth scraped skin and flesh as Snape escaped the room and slammed and locked the door.

Quirrell was in the corridor, watching. Snape opened his mouth to yell at the twitching idiot, when both heard horrible noises coming up the stairs from the first floor. They sped down the stairs and along the corridor, meeting McGonagall just as she came up from the dungeon level.

The last horrible crash had come from the girls' bathroom. McGonagall reached it first, with Snape right behind her and Quirrell in the rear. There, unconscious on the floor, was the troll. Standing over it were Potter and Weasley. Quirrell sat down on one of the toilets and put his hands over his heart.

The troll lay stretched out on the bathroom floor. Snape bent over it to see if it bore any signs of restraint, like the marks of a collar, but there were none. McGonagall was furious and letting the two boys know it. "{\el} Why aren't you in your dormitory?"

Snape glanced quickly at Potter and Weasley. \emph{Yes, why are you here? This is the way I took to go to the third floor. Were you following me? Or were you following Quirrell? Why would you follow either of us?}

Then a girl's voice came from the shadows. "Please, Professor McGonagall—they were looking for me." It was Granger.

The girl told a rather far-fetched story of trying to take on the troll herself, but at least her presence helped explain the boys'. McGonagall sent them off to Gryffindor Tower, then she and Quirrell went to find the other teachers to let them know that the troll was captured. Snape headed for the hospital wing to tell Higgs to bring the Slytherin students down so they could finish the Halloween feast in their dormitories.

By now his leg was stiffening to the point where walking was difficult, so Snape's last stop was his own office. He raised robe and gown to examine Fluffy's tooth marks. Skin and flesh were torn, but for some reason it hadn't bled much. \emph{Good thing, or the others would've noticed.}

After washing and disinfecting the wound, Snape looked through his salves and ointments for something that would heal bites. Nothing seemed to work. \emph{That's what you get for tangling with a magical dog, you blasted twit! I could go to Madam Pomfrey, but she doesn't know about Fluffy. Dumbledore may not want her to know.}

Dumbledore. He had to tell Dumbledore. He had to walk up all those flights of stairs to tell Dumbledore about Quirrell and the troll. Snape stood, and the pain in his leg was like fire. He tried to walk, and all he could do was hobble. \emph{Tomorrow. I'll tell him tomorrow}.

Snape never did have any more dinner that night and frankly, he didn't care.

Early the next morning, Snape went up to see Dumbledore. His leg was better, but still painful. Dumbledore did not appear surprised to see him.

"Quirrell came last night. He seemed to be worried that you were trying to get to the Stone during all the confusion. He thinks I should keep an eye on you."

"I think you should keep an eye on him." Snape explained all his suspicions about London, the robbery, the fact that Quirrell was an expert with trolls, and what had happened in Fluffy's chamber.

Dumbledore was sympathetic about the leg. "I appreciate your discretion regarding Madam Pomfrey. I would rather she did not know. Filch has some medical supplies, splints and bandages and such, if you need them. And he already knows about the dog."

Snape arranged his morning class so that the students would be working on simple preserving of herbs, drying and powdering. Then they had time to work on the reports of their lab work. That way he didn't have to stand or walk around the room. Any student with a question could come to his desk.

As the day progressed, the leg worsened. During the break after lunch, which like breakfast was served in the dormitories because of yesterday's excitement, Snape went looking for Filch. He needed supplies and someone to look at the wounds. He'd have preferred Hagrid, but Hagrid wasn't in the Castle, and Snape couldn't walk all the way down the hill to his hut.

Passing through a courtyard, Snape spotted Potter and his Gryffindor friends acting in a suspicious manner, as if trying to conceal something. "What's that you've got there, Potter?"

It was a library book, out in the cold and damp of the courtyard. Snape confiscated it and, angry that he was forced to handle little problems like this when he was in pain, deducted five points from Gryffindor.

Filch said he could come by in the evening. By then it was all Snape could do to limp to the staff room. He hadn't eaten since lunch the day before, and his mood was foul. He sat in a straight chair and raised his robes so that Filch could examine the bites.

"That's nasty, that is, Professor. You got it nice and clean, though. I seen a bite like that fester and have to cut the leg off, it ain't took care of. I brought you some bandages. That Hagrid, he plays with some dangerous beasts. You're lucky you got out in one piece."

"Blasted thing," Snape said. "How are you supposed to keep your eyes on all three heads at once?"

There was a small noise, and Snape looked toward the door. A student stood there. "POTTER!"

"I just wondered if I could have my book back."

Snape rose, and pain stabbed from his foot up into his back. "Get out!" he screamed at the boy, "Out!" \emph{How dare you enter here without permission! How dare you spy on me and spread stories of my private life through the whole school!}

"Here, Professor," said Filch. "Try this salve. It always worked wonders for me."

\subsection{Saturday, November 2, 1991}

% FIX?
% \emph{[JKRowling's story implies that a longer time passed between Halloween and the first Quidditch match, but if that were true, then Harry and his friends would have noticed Snape's limp sooner than the day before the game.]}

Filch's salve actually did work wonders, and the next day the leg was decidedly better. Snape still limped, but sixty percent of the pain was gone. It was Saturday, and the day of the first Quidditch match between Slytherin and Gryffindor. Time to see if McGonagall's confidence was well placed.

Breakfast was once again in the Great Hall, and the moment Snape entered, he was accosted by Hagrid. "Elves say you ain't eating again. I'm sitting next t' ya this morning, and if ya don't eat a fit amount, I'll spoon-feed ya in front of the whole student body."

Snape agreed to the arrangement, since he was famished. Hagrid would have no excuse to spoon-feed anyone. It also forced Quirrell to move down, which could only help Snape's appetite. Already the smell of fried sausages was making his mouth water.

Both teams looked focused and subdued. The Potter boy wasn't eating. \emph{Nervous before his first game. I should send Hagrid to spoon-feed him}. Snape glanced over at McGonagall. She seemed nervous, too.

For some reason passing understanding, Quirrell decided he wanted to watch the game. He followed Snape out and joined him in the Slytherin stands. \emph{Why doesn't he sit with Ravenclaw? I'm sure they'd love to have him.}

The game started normally, the most irritating thing being the announcer, Lee Jordan, who was so blatantly pro-Gryffindor that it was insulting. Snape made a mental note to mention it to McGonagall later. Gryffindor scored first, a foul was called against Flint for stopping Potter from catching the Snitch, then Slytherin scored. Snape had never really liked Quidditch, except for the bludgers and the house competition. Only two things made today interesting—seeing if Potter really was any good, and watching McGonagall try to contain her excitement.

Suddenly something was wrong with Potter's broom. It was lurching and twisting in an unnatural way and gradually moving higher and higher. It looked as if it were trying to buck the boy off, which at the height it'd reached would be dangerous. Snape realized then that his own instincts had taken over, for without thinking, he'd already started murmuring a countercurse.

Whoever was cursing the broom was powerful. Powerful enough to not only jinx a Nimbus 2000, but to withstand his countercurse as well. The broom threw Potter off, but he managed to hold on to the stick. The Gryffindor Beaters were trying to get close enough to help as the broom continued to ascend. Snape struggled against his unknown foe to bring the broom lower and stop its bucking. A fall from that height could be fatal.

Suddenly people were pulling at his arms and pointing beside him. At the same moment Snape felt flames burning the hem of his robe and cried out in pain. His concentration was broken, but when he turned back to the game, Potter's broom was flying normally again. Whoever had been cursing it had stopped.

Potter clambered back onto the broom and went into a nosedive that ended with him on the ground and the snitch in his hands. Gryffindor erupted in cheers, Slytherin stood in silent shock, and Snape shook his head in bewilderment. \emph{What just happened?}

Hagrid and Snape were both in Dumbledore's office after the game.

"It was a curse. Someone was cursing the broom. Someone powerful. I couldn't stop it; it took every bit of concentration to restrain it. Until I caught on fire."

"How did you catch on fire? A fire that stops as soon as you break eye contact? And yet it seems that it broke contact for the other spell caster as well. Another mystery."

"Begging yer pardon, Professor, but they think you did it."

"Who thinks I did what?"

"The students. Potter an' his friends. They saw ya saying the countercurse, and they thought ya was the one cursing. And they know about Fluffy."

"Potter saw my leg yesterday. He probably suspects Fluffy did that."

There were no answers, only more questions. Dumbledore dismissed the two with instructions to keep an eye on Potter and his friends. As Snape and Hagrid left the Headmaster's office, Hagrid turned to Snape.

"What did Fluffy do t' yer leg? And ya didn't come t' me? We're going right t' yer office now, lad, or I'll be on yer tail for the rest of the year."

The two went to Snape's office, where Hagrid looked at the leg. "That's got t' of hurt. What'cha put on it?"

"Some stuff Filch gave me. It's on the shelf there. It worked."

Hagrid sniffed the small dish. "I don't doubt it. That'd soothe dragon burns—probably what it's meant for. Who d' ya think did it?"

"Attacked Potter? I'd suspect Quirrell, except he's not strong enough."

"Why him?"

"I think he's after the Stone. He heard about it on the thirtieth. He tried to be sure you wouldn't be in London 'til the first, then he went down on the thirty-first and there was a break-in at Gringotts. I think that was Quirrell after the Stone. Then on Halloween he pulled the troll stunt. When have you known Quirrell to be terrified of trolls? I suspected him then and went to the third floor. Quirrell did go in and was trying to decide how to deal with Fluffy. That's how I got this."

"Then ya say he's not strong enough."

"That was at the Quidditch match. Whoever was trying to hurt Potter was a lot more powerful than Quirrell. Though it would explain more. Did the students tell you how they knew about Fluffy?"

"Nope. Didn't{\el} well, yes I did ask, but they distracted me."

"On Halloween, both Quirrell and I used the stairs in the back corridor to get to Fluffy's chamber. The same corridor where Potter and friends found the troll. But what were they doing in that corridor? The girl's story about wanting to take on the troll is obviously a lie. So, were they following me, or were they following Quirrell? And that's probably when they saw Fluffy. It would all fit if Quirrell reached the same conclusion and tried to kill Potter to keep his own secret. But I would never have suspected Quirrell of being that strong."

It also occurred to Snape, though he didn't mention it to Hagrid, that if Quirrell felt he had cause to kill Potter, then he also would have cause to kill Snape.

\subsection{Wednesday, November 20, 1991 (the full moon)}

The next month and a half was like waiting for a storm to break. Every day Snape sat next to Quirrell at meals as if he suspected nothing, and Quirrell did nothing to justify his suspicions. Every Friday morning he taught Potions to Gryffindor first years, trying to avoid the green eyes, yet Potter was turning out to be almost as much of a dunderhead as Longbottom, and Snape could not simply ignore him. And Longbottom{\el} Was there ever anyone as complete and total a failure at everything as Longbottom?

At the end of supper on November 20, Snape glanced back, out the windows of the Great Hall, and saw the full moon rising in the night sky. For the first time in a long time, he felt like going down to the lake to sit on Lily's rock and watch the moon. He wished she were there, so he could tell her how he felt.

\emph{I don't like your son, Lily. I'm sorry. He's moody, rude, arrogant, a popularity hound like that husband of yours. You should have seen the gaudy `Potter for President' sign at the Quidditch game. He even thinks I want to kill him. Why couldn't he inherit Potter's eyes and your personality?}

\emph{And then there's the Longbottom boy. Do you have any idea how long I've hoped the prophecy was about him? But it wasn't about him. He couldn't hurt anyone but himself. There was no mistake. The prophecy was about your son. I am so sorry. I did that. It's my fault. Entirely my fault.}

Then it was midnight, and Snape remembered that he had a six o'clock wake-up, breakfast at seven to supervise the students, and a nine o'clock class. He rose and bid the moon, the moon that blazed bright above him, goodnight. As he walked back toward the Castle, he noticed two things. First, a fleeting glimpse of Albus Dumbledore at an upper window, suddenly turning away, and second a dog whining in the woods behind him. \emph{Fang, I swear that's Fang. Hagrid will not hear the end of this.}

And yet he was tired, and so Snape returned to his own quarters and went to bed.

December came, and it began to snow. When the storm was over, all of Hogwarts was covered in a blanket of white. The upper classes were given one more Saturday at Hogsmeade before the Christmas break, and Snape stood at a first floor window watching as Quirrell descended the steps and walked across the top of the hill in the wake of the students he was supervising.

"What do you find so interesting?" McGonagall came over to watch, too.

"Look at Quirrell. Now wait."

About five snowballs appeared from their right, flying in a V formation. One by one they dive-bombed Quirrell, bouncing off his turban and swooping back up into the air for another attack. McGonagall was making wheezing sounds as she tried to control her laughter.

"You didn't do that?"

"No. My hexing days are long over, though I could show them a trick or two."

"Do you know who it is?"

"I do not, Minerva, and good for you that I don't because if I did I'd have to deduct points from your house."

"The terrible twins?"

"I'm not saying."

\subsection{Friday, December 20, 1991}

The dungeons were cool even on the hottest days of summer. It was the perfect place to store all the potions ingredients. Now, in the winter, it was nearly as cold in Snape's living and working area as it was outside.

The last Potions class of the year ended on the last day before the Christmas break. The students were leaving on Sunday, those that were going home. A skeleton staff and a few dozen students would stay. For their sake, the Great Hall was being decorated for the holidays.

Snape closed and locked the Potions classroom after the students were gone and started up the stairs to the warmth of the Great Hall and something hot for lunch. A little group was standing around Hagrid and one of the fir trees. Just as Snape reached the top of the steps, one of the boys jumped at another and grabbed his robes, clearly intending to start a fight.

"Weasley!" Snape shouted, and the boy let go. Snape realized then that the student he'd attacked was Draco.

"He was provoked, Professor Snape," said Hagrid. "Malfoy was insulting his family."

\emph{Don't get me into a `he said, he said' situation. Words are one thing; physical violence is another.} "Be that as it may, fighting is against Hogwarts rules, Hagrid. Five points from Gryffindor, Weasley, and be grateful it isn't more. Move along, all of you." Snape herded the Slytherin boys into the Great Hall.

Hagrid and the Gryffindor students came in after them and busied themselves setting up the last tree. Then the students left. Hagrid looked upset about something.

Later, Snape brought the subject up again. "Why've you started playing favorites with Gryffindor students? You were pretty quick to jump to that Weasley boy's defense." Snape was sitting next to Hagrid for dinner at the high table because Quirrell was in his quarters nursing a cold.

"Malfoy was just being nasty. He was egging the boy on an' insulting me t' boot. Don't look at me like that, it were just a comment on m' living arrangements, that they're not palatial."

"Malfoy's been taking some flak in Slytherin for helping put Potter on the Gryffindor team. He seems to be having trouble dealing with it. Should I talk to him tomorrow about it, before he goes home, or wait 'til next term?"

"Don't talk t' him at all on my account. I can take it. By January it may've all blown over."

Saturday was hectic, with students packing, students exchanging Christmas presents, students promising to send owls during the break, students mailing cards{\el}

Sunday they left, and Hogwarts was suddenly very quiet.

\subsection{Christmas, Wednesday, December 25, 1991}

The few days before Christmas were calm and rather enjoyable. With no classes to worry about, all of Snape's supervisory duties involved patrolling empty halls or observing students from a distance. When he wasn't on duty, he caught up on some reading. It was a welcome time to recharge energy. Being around masses of students always left Snape feeling drained.

Christmas morning was icy cold, with the feeble sun glittering on the snow from a cloudless sky. Most of the little group of students and staff stayed in bed until after sunrise, which that far north was not until nearly nine in the morning. The sun would set again around three-thirty in the afternoon. The shortest days in the year. Christmas dinner would be served at noon.

Snape woke several hours before dawn and immediately started fires to take the chill off his bedroom and office. His was one of the few areas where, because of all the poisons, the house elves were forbidden to come. Snape preferred the added privacy.

There were no presents. Snape didn't exchange Christmas presents with anyone, which spared them and him the torment of trying to find out what someone else wanted. Instead he passed the time reading, and then went to the Great Hall an hour early to supervise the arriving students, that being his duty station for the day.

Quirrell wasn't at dinner. He hadn't been all week. \emph{Still sick, I suppose.} Dumbledore was insisting that everyone break open the wizard crackers in front of them and put on their hats. He already sported a gaudy flowered bonnet. Snape sat on one side of McGonagall and Hagrid on the other. She and Hagrid pulled a wizard cracker, and McGonagall got a jaunty top hat, which she immediately set on her head at a rakish angle. Hagrid got a Dutch ladies cap with starched white wings.

"Now you, Severus," said McGonagall. "You have to have a hat, too."

Snape shook his head. "With my luck it'd be a feathered war bonnet like the Indians in America wear. I'd rather not live with that image."

McGonagall and Hagrid insisted, however, and Snape reluctantly pulled the cracker Hagrid held out to him. To his enormous relief, it was a relatively dignified Turkish fez in green and black.

The feast began. The few occupied tables were loaded with food to feed two armies. Hagrid helped himself to more wine than was good for him and kissed McGonagall on the cheek. Then the little warning bells began ringing in Snape's brain.

\emph{Quirrell isn't here. Everyone else in the entire Castle is here but Quirrell. This is exactly like Halloween.}

Snape quickly excused himself from the table and left the Hall. Running along the corridor to the back staircase, he again took the steps two at a time and, arriving outside Fluffy's room, found himself face to face with Quirrell.

"Quirinus! What a pleasant surprise. So good to see you up and about. I trust you're feeling better."

"S-Severus. What{\el} brings you here?"

"The pricking of my thumbs. But you should really join us downstairs for the feast. It will do you a world of good and speed your healing." Snape took Quirrell by the elbow, turned him around, and steered him back downstairs into the Hall.

Dumbledore looked up as the two entered the Hall but said nothing. Hagrid and McGonagall did not seem pleased at the addition to their company. Snape resumed his seat and proceeded to enjoy the rest of the Christmas dinner. Quirrell sat sullenly at the end of the table and didn't eat a thing.

The afternoon was most enjoyable. The majority of the students were outside, playing in the snow. Quirrell was at his station keeping an eye on them, and so could not be somewhere else. Snape sought out Filch, who'd slept through the Christmas dinner since he had the night watch and didn't get to bed until nearly sunrise.

"Filch, I'm entirely on day duty during the holidays. Do any of the teachers have a night patrol?"

"No, Professor. There's so few students here they thought it wasn't necessary. Decided to let the teaching staff have a holiday, too. No, it's just Filch in the corridors at night. Me and Mrs.~Norris."

"It's a burden for one person. If you ever see anyone—anyone—out in the school at night, let me know. I'll help you get them back where they belong."

"Anyone at all, eh?"

"Well, except Dumbledore, of course. Other than that, anyone at all."

Supper was almost as festive as the earlier feast had been, certainly in the amount and type of food available. Then most of the students went to their various dormitories while the teachers gathered around one of the tables for a more convivial evening of brandy, coffee, whist, chess and, for Snape and Flitwick, cribbage. Quirrell was with them, trying to play chess with Professor Vector and losing ignominiously.

"I understand your quarters are, well, cold, Severus," commented Flitwick between games. "Aren't your students freezing as well?"

"The water in the lake helps maintain a constant temperature."

"But the lake freezes."

"Only on the surface. The water underneath doesn't get as cold."

"Someday you'll have to explain that to me."

Gradually the teachers drifted off to bed, but for a few the evening of cards and chess continued until nearly midnight, when the last wished each other a good night and started off for their various rooms. Flitwick was still concerned about the cold.

"Have you ever tried a warming pan?"

Snape raised his eyebrows. "I can't say that I have. Now you'll have to explain that to me."

"You heat bricks at a fire and place them in a flat metal pan to warm up a bed on a cold night."

"And the bricks radiate heat for a long time. Ingenious idea."

"I have some heating on my hearth right now. Come on up and take a couple with you. No need to be cold on Christmas night."

Professor Flitwick's rooms were on the third floor, and the two were almost at the door of the Charms classroom when Filch came hurrying down the stairs. Seeing Snape, he stopped suddenly.

"Someone's prowling upstairs," he snapped.

Snape excused himself to Flitwick and quickly followed Filch up to the fourth floor.

"You asked me to come directly to you, Professor, if anyone was wandering around at night, and somebody's been in the library—Restricted Section," Filch explained.

"The Restricted Section? Well, they can't be far, we'll catch them."

They caught no one, however. Filch led Snape back to the area of the Restricted Section where the prowler had been and showed him the extinguished lamp, still warm, and the book that had alerted him by its screaming.

\emph{A screaming book? `Spells and Enchantments for Guarding and Protection.' Quirrell must still be looking for a way past Fluffy. But if Quirrell were here, why is there no lingering smell of garlic?}

"Whoever it was, Filch, we seem to have chased them away. Thank you for fetching me. If anything else suspicious happens, let me know. Good night."

"Good night, Professor."

It was too late to get warm bricks from Flitwick. Snape made his way back to the dungeon area and his own rooms, considering the events of the night. Someone had been in the Restricted Section looking at dark spells for guarding things. Someone who was not Quirrell. So now there were two unknowns, the prowler in the library and the strong spell caster who'd tried to kill Potter at the Quidditch match. Unless, of course, they were the same person.

\emph{Who besides Quirrell would be trying to steal the Philosopher's Stone?}

The meeting with Dumbledore was not satisfactory.

"I assure you, Headmaster, that we're dealing with more than one person here. Quirrell wants the Stone. I caught him once actually entering the chamber, and a second time approaching it. He had to have had something to do with the troll at Halloween. Quirrell wouldn't have simply run from a troll, then fainted. But he isn't strong enough to have continued jinxing Potter's broom over my countercurse, and he wasn't the one in the library or we'd have smelled the garlic. Besides, Quirrell can't just disappear like that. There are at least two people, Quirrell and someone else."

"Do you believe that they are working together?" Dumbledore asked patiently.

"I don't know. If Quirrell thought Potter'd seen him, he might have a reason to kill Potter, but then he'd have a bigger reason to get rid of me. And why would Quirrell hide it for three years if he really was stronger than me? He didn't know the Stone would suddenly appear."

"What other person at Hogwarts would you suspect? Who is stronger than you at this type of magic?"

"You are. That's it, just you. At least at this kind of dark magic. It might be one of the students, though. Some of them come from powerful dark families. I haven't seen any that I could suspect of hiding their strength, but that doesn't mean there aren't any."

Dumbledore leaned back in his chair. "I believe you are more worried about this than you need to be. Some of these incidents may be wholly unconnected to the central problem."

"Is there something you know that you don't want to tell me, sir?"

"I couldn't say."

"I'd like your permission to referee Gryffindor's next Quidditch match. They play Hufflepuff in February."

"Severus, Severus, you do want to be unpopular, do you not?"

"I don't understand, sir."

"Slytherin has been the top house in both Quidditch and the House Cup competition for what, seven years? Now Gryffindor has a chance to catch up and knock you out of first place. Do you honestly think that Ravenclaw and Hufflepuff are not in Gryffindor's corner? Anything to deflate Slytherin. And now you want to referee a Gryffindor game? You know what they will think. Besides, I do not recall that you were ever very, shall we say `comfortable,' on a broomstick."

"I bought a broom after I finished school. I use it to get around in Lancashire. I'm not great, but I'm adequate. If I was up in the air and mobile, and anyone started tampering with Potter's broom, I would be able to see who it was."

"Let me think about it."

"Thank you, sir."

Later that day Snape was down by the frozen lake, where he picked up a handful of pebbles and started targeting pinecones. There was a certain violent precision to his attack that would have terrified two-thirds of his Potions classes into imagining how good he might be with pieces of chalk and student heads. Only this time it wasn't student heads he was thinking of.

"Somewhat upset ya, Professor?"

"Are you spying on me again, Hagrid?"

"Spying, sir? Me?"

"Like you and Dumbledore did last month when I came out here to sit for a while. You think I don't notice?"

"Well, ya do get a bit high-strung from time to time, an' we want t' be ready t' head ya off. What's happened today?"

"Dumbledore."

"So ya take it out on the pine trees."

"I could go for birds or rabbits. It'd be more of a challenge."

"Pinecones is fine. What did Dumbledore do?"

"Hoard information. I went to him about this{\el} problem, and he tells me I don't have to worry about part of it, but he won't tell me which part, and he won't tell me why, so what good does it do?"

"Ya might take comfort from that."

"How so?"

"Well, if he's tightlipped about someone else's private affairs, he's likely tightlipped about yours as well."

"You're probably right, Hagrid."

Throwing stones at trees would not solve the underlying problem. Somewhere on the grounds of Hogwarts, in the Castle itself, unknown, unrecognized, was a spell caster stronger in dark magic than he was. A spell caster whose curses required all of his concentration and energy just to mitigate. In all Snape's life, he'd known only two whom he could not best easily, or at least face one on one as an equal. One was Dumbledore. The other was dead.

\emph{It was bad enough at the Quidditch game, feeling that strength. Now he appears to be wandering Hogwarts at will, as if he were invisible. Dumbledore knows something, but won't tell, which is even more disquieting.}

Snape knew two things for certain about this unknown. He was interested in spells of guarding and protection—but to create them, or to bypass them? And he'd tried to kill Potter. \emph{If he's still trying to kill Potter, he may be watching him constantly. If I can spot someone who's always keeping an eye on Potter, I may learn who this mystery spell caster is.}

Drawing up a list of all the staff and students who'd remained at Hogwarts over the Christmas break helped somewhat, though Snape couldn't see a single name that he'd suspect of being the one. Maybe he was hiding on the grounds, only pretending to leave. \emph{Maybe he's hiding on the grounds anyway, not a student at all.}

The beginning of the new term found Snape nervous and edgy. He reevaluated everyone, trusted no one. He began checking the places Harry Potter frequented to see if anyone else was following the boy. Growing in the back of his mind was a doubt, a worry, the rebirth of a long-dormant fear.

January was a hellish month. In addition to Snape's other troubles, the first years advanced from the simple stages of gathering, preserving, and storing herbs, and the brewing of infusions and decoctions, into full-fledged potions making. All the stunning ineptitude of that first Friday back in September reemerged.

It took two sessions before even half the class managed to grasp the difference between stirring, beating, and folding in. Snape's muggle half was throwing hissy fits. \emph{Didn't anyone ever show them how to bake cookies? Scramble eggs? Make a pudding? Idiot wizard brats!}

Friday mornings were a running commentary on potential disaster. "Bulstrode! Newts' eyes, not bats' eyes. Newt! It begins with an N. You know, the letter with all straight lines{\el} Weasley! Remove that cauldron from the fire before you add the venom—unless you want to redecorate the classroom{\el} Longbottom! Are you missing an entire page! There are six ingredients that come before the nettles{\el} No!" For Longbottom threw the nettles in anyway.

Snape sprang between the cauldron and Finnigan, seizing Longbottom by the wrist and flinging him towards Weasley and Potter, as he whipped out his wand with a quick incantation just as the brew exploded. There was a pop, and a gurgle, and the surface of the concoction belched a little, but catastrophe was averted, except for Snape's wand and right hand, which were splashed with the liquid. Welts and boils rose immediately, and it burned like fire.

Trying to suppress images of what might have happened if he hadn't been standing near the cauldron, Snape wheeled on Longbottom. "Are you deaf as well as illiterate?" he yelled at the boy. "Or do you enjoy sending half your classmates to hospital?"

The thoroughly frightened Longbottom rejoined Finnigan, and they began making the potion again. Snape went to his cabinet to look for a salve for his inflamed hand. It would be better to get something from Madam Pomfrey, but there was an hour left to go for the class, and leaving the students alone for even a moment was unthinkable. Still in pain, he forced his eyes to sweep the room again. Snape himself had been a relatively powerful eleven-year-old. What if the one he was looking for was here?

"Potter, you dunderhead! Can't you read either? Stir that with a clean spoon or we'll have an accident worse than Longbottom's! Don't you pay attention to anything at all?"

\emph{Azkaban has to be better than this.}

February's Quidditch match drew closer, and more of the staff discovered that Snape was going to referee. Sprout was telling everyone that she had nothing to do with it, preferring to have Hufflepuff win or lose on its own merits. McGonagall and Flitwick started eating together, pointedly avoiding Snape's company. He cornered McGonagall on the stairs after breakfast one morning three days before the game.

"How can you believe that of me, Minerva? We've been colleagues for ten years. Why would you think I would miscall a game for the sake of the Cup?"

"Are you or are you not the same rascal that talked the best Seeker I ever had into following dragons? I've never known you to want to referee before. It occurred to me that someone who fought like the devil to get to the top might fight just as hard to stay at the top. Set my heart at ease, Severus. Withdraw from refereeing. Otherwise I'll judge on the outcome of the game."

But Snape couldn't withdraw, not if he was going to have even the ghost of a chance of finding out who the spell caster was.

The Saturday of the Gryffindor-Hufflepuff Quidditch game was cold and overcast. The first thing Snape noticed was that he was being ignored at the breakfast table by every other teacher except Trelawney, who normally never spoke to him. She glided up as he was helping himself to a kipper and some toast and muttered. "All your hopes will be dashed today."

"Good morning to you, too, Sibyll," he replied, then stayed longer at the table than usual, trying to eat in a leisurely fashion to show how little the ostracism affected him.

Earlier in the week, Snape had tried out the school brooms and found one that was easy to manage and docile. After breakfast he went down to the Quidditch pitch to practice a bit well before anyone else arrived. It was fairly easy and, as he'd reasoned, from the air he could see every spot in the stands. If any spectator started to jinx Potter's broom, Snape would be able to see who it was.

Lunch was a repeat of breakfast. It'd never struck Snape so forcefully before how much the other teachers resented the fact that Slytherin had been in first place for so long. He could understand McGonagall, Flitwick, and Sprout. They naturally wanted their houses to win. But the rest? He reviewed the staff in his mind and experienced a small revelation. None of the others had been in Slytherin as students. \emph{I'm still the only Slytherin on the staff. I haven't thought about that since I started teaching. No wonder they resent our success.}

After lunch, the entire school began to make its way to the Quidditch stands. Everyone wanted to see if Gryffindor would win. Snape had the feeling that even Hufflepuff would cheer a Gryffindor victory.

The teams were still in their locker rooms when the next thunderbolt struck. Just as the game preliminaries were set to start, a flurry of excitement at the center stand attracted Snape's attention. From his aerial position he could see a tall, white-bearded figure take a seat.

\emph{What is Dumbledore doing here? He never comes to Quidditch games, why this one?{\el} Because he knows that no spell caster would try to jinx Potter with him here. He's here because he doesn't want me to find out who the spell caster is.}

As the teams filed out of their locker rooms onto the field, Snape felt himself consumed with a sudden anger, and it was directed against Dumbledore.

\emph{Why couldn't he just tell me he wouldn't let me referee? Why let me go to this effort, be hated by all and sundry, and then at the last minute make all the trouble worthless by ensuring the one thing I want can never happen?} Snape knew his anger showed on his face, and he didn't care.

Madam Hooch sent the teams into the air, and almost immediately George Weasley sent a bludger straight at Snape's head. "Penalty for Hufflepuff!" Snape called, and he and Weasley exchanged glares across the pitch. Just a moment later, Snape caught Fred Weasley trying to hex the quaffle. "Penalty for Hufflepuff," he called again, and this time there were boos from the Gryffindor stands.

Then suddenly the entire crowd was on its feet. Snape turned as Potter flashed past him in a dive for the ground. Though Potter did not actually hit him, the backwash of his speed nearly knocked Snape off his broom, while his robe lashed Snape's face, and bits of broom straw entered his mouth and nose.

Within five minutes of the game starting, Potter caught the snitch and the stands erupted in cheers. It was over, irrevocably over, and nothing of importance happened.

Snape landed his broom, furious with Dumbledore and with Harry, and spitting bits of straw out of his mouth. He stood respectfully in line to accept the congratulations of the Headmaster, since he was one of the game staff. When it was his turn to shake hands with Dumbledore, however, Snape looked him straight in the eyes and said softly, "Are you ever going to tell him it was rigged?"

Dumbledore froze, then his eyebrows shot up, but he said nothing. 


