% A Difference in the Family: The Snape Chronicles (Rannaro)
% What Of My Soul, Dumbledore?

\chapter{Burning Bridges}

Dumbledore's tone made Snape suddenly angry. "Did you by any chance give him any information that would let him reach that conclusion? Because if not, the fact that he makes a mistake here lies solely on you."

"I beg your pardon, Severus. I have done what I could to prepare Harry for his task."

"What if it wasn't enough? What if you played your cards too close to your chest, and he hasn't got clue one what you expect him to do? What if you treated him like you treat me? He's got the sword, and he thinks he knows what to do with it, but oops! we left out that small but vital piece of information, and the whole plan goes down like a house of cards? I'm not wild about freezing my rear end off for nothing."

"I assure you, you did not freeze your rear end off for nothing. Harry has what he needs, if he remembers it, to use the sword."

"Right. I know the lesson well. It's number two hundred sixty-six. `Oh, by the way Harry, if Ron should happen to retrieve a sword from a pool in the middle of the night because you were choking on something, please let him use it first.' A truly well developed lesson plan. I use the basic format all the time."

Dumbledore peered over his glasses. "You are becoming tiresome, Severus. You are assuming too much - or rather, too little. Harry knows what is expected of him."

Snape turned and swept out of the office. Behind him, as the door closed, he could just barely hear Nigellus say, "You know, Albus, the Potter boy isn't the only one with green eyes."

It wasn't until he'd stormed all the way down to the fourth floor that Snape realized he was heading for the dungeons and his old rooms. The headmaster's office, which had seemed a refuge in September, was a refuge no longer, and it was becoming clearer and clearer that contact with the portraits wasn't the same as human contact. Snape wanted to talk to someone, a person, even if it was just the meaningless banter of the staff room after a tiring day, but there was no one to talk to. McGonagall wouldn't talk to him; Sprout wouldn't talk to him; he doubted Hagrid would talk to him. No human contact at all. The headmaster's chair was an isolation booth. For the first time it struck Snape that when he died, he would probably be alone.

\emph{I like being alone. I want to be alone.} Yet `alone' was a relative term. It was one thing to seek solitude after a hundred student contacts in a day and the noise of the Great Hall. Being alone in his room with a book or a new potion at such times was a welcome relief. Now it was a constant state of being, and Snape missed betting on Quidditch games with McGonagall, or playing cribbage with Flitwick, or helping Sprout set out seedlings, or even having Hagrid fuss over his eating habits.

\emph{All I have now is Dumbledore - and Nigellus, and the hunt for Potter. And until we bring down the Dark Lord, that's all I'll ever have. Even Amycus and Alecto won't talk to me because they work for Bella, and Bella thinks I'm her rival. And to think there were times in my life when I thought I could actually live like a human being in a normal world.}

Truth be told, those times had been few and far between, and suddenly Snape wanted to get out of Hogwarts and go somewhere, anywhere, where he could be normal, do something normal, act human again. He trudged back upstairs into his office, and from there into his bedroom, and returned settling a warm cloak around his shoulders.

"Where are you going, Severus?" the portrait of Dumbledore asked.

"London," Snape replied.

"Whatever for?"

"I'm going to a movie, and then to a restaurant, and maybe I'll even buy a book or two."

"But Potter{\el} They have the sword now. We may learn{\el}"

"I already know the report, sir. They're camping. It's someplace quiet, rural, where there aren't any other people. Granger's doing the cooking. End of report."

"Severus, it is ten o'clock at night on Boxing Day. Nothing is open{\el}"

Dumbledore was right, of course, but Snape didn't care. He stalked down the hill to the gates and disapparated.

He ended up in the pub in his home village. Men who'd known his father, and who'd tried to teach Snape to play darts, came over to wish him a happy Christmas. He had a pint, then someone bought him another, and he found himself pondering the mysteries of table skittles, in this case devil among the tailors, and the use of geometry in determining the arc of the ball. It was a good sight easier than darts. All too soon, the pub keeper shouted "Last call, lads," and then it was closing time, and a much mellower Snape found his way to his own home, from which he apparated to Hogsmeade. As he made his way back up the hill, Snape decided that it was good to have a home village. Something to remember in times when he was more alone than usual.

And naturally, it would be precisely that evening, when he'd run off and played truant, that the report would be different. "I told you, Severus," Dumbledore's portrait said the instant he set foot in the office. "Ron Weasley has used the sword. The locket is destroyed."

That night, lying sleepless in bed, Snape tried to work things through.

\emph{Nigellus thinks I'm jealous of Potter. Is that true? Am I jealous?} Much as Snape hated to admit it, when set the question, he had to acknowledge that since Lily's death the most important person in his life had been Dumbledore. Dumbledore had kept him out of Azkaban, provided a place and a purpose, and to some extent had given him trust and that indefinable sense that he belonged to a family.

Now, inexorably, it was all being whittled away. Dumbledore was dead, the shadow of his portrait presence the only consolation. Hogwarts was no longer a home but once more a prison where he barricaded himself in the middle, against both sides. And trust? In the last year Snape had come to realize that Dumbledore trusted him about as much as he trusted anyone - to perform certain specific tasks, but no further. \emph{Am I exactly like Potter? Another pig being raised for slaughter?}

It was darkest, blackest night, the moon almost new, and Snape could not see the ceiling that he stared at. \emph{What if I had done differently? What if I had not set things in motion? If I had been strong and withheld the prophecy from the Dark Lord?} But that, of course, was silly. That night when he knelt before the Dark Lord to confess his failure and receive his punishment, the prophecy held no meaning, the child it referred to, if indeed it referred to a child, as yet unborn, as yet unconceived, but the pain of punishment was very real. \emph{And I was no seasoned spy for Dumbledore. I was nineteen, and the Dark Lord's faithful servant. There was no cause to withhold the prophecy.}

Still, if he had not chosen to climb those stairs and listen at that door, he would have heard no prophecy. \emph{I would have had nothing to give him to turn his wrath from my failure. I would have died that night, but Lily would still be alive.} And yet, was even that true? The night Snape had heard the prophecy, the Dark Lord was at the zenith of his power. Opponents fell before him like flies, and Dumbledore and the Order of the Phoenix battled in hopeless retreat, already betrayed, as Snape now knew, by Peter Pettigrew. It was only a matter of time before both James and Lily, and in all probability their son as well, would have died. As Fabian and Gideon Prewett had died. As Marlene McKinnon had died. As one by one all Dumbledore's followers had been dying. Until a new and hitherto unused spy had provided the information to turn all that around. The spy who spied because of the Dark Lord's interpretation of a prophecy.

\emph{No, Lily would still be dead, and the Dark Lord would have come into the fullness of his power sixteen years ago. The prophecy caused his downfall and gave Dumbledore time - time to learn more of the Dark Lord's plans so that now, even now, hope glimmers that the last item will be found, Potter will know of his role, and the Dark Lord will be vanquished forever. Maybe I don't stumble blindly in the darkness. Maybe instead of a blundering fool, I'm an instrument of fate, and my role in this is as important as anyone's.}

The problem was, there was no way to know. Not until the last choice had been made and the last act played out. And maybe not even then. \emph{The odds are that I'll die without learning if any of it was worthwhile.} But still, the idea of being an instrument of fate rather than of Dumbledore was somehow comforting, and at long last Snape was able to sleep.

He told Dumbledore so the next morning. "I've decided. You're not in control of the situation."

"No?" the portrait raised its eyebrows. "And who, Severus, is in control? Not you?"

"God," Snape said, and ordered breakfast from the kitchen rather than go down to the Hall to eat with the skeleton staff.

"You amaze me. Have you found religion at last?"

"Let's say I've decided that we're not leaves blown helplessly along by the winds of chance. Someone is guiding us. Call it fate if you like."

"This is truly astounding, Severus! You have taken a great step forward in the{\el}"

"Don't patronize me."

"I beg your pardon?"

"You're acting like an instructor whose job is to inculcate an understanding of the seven levels of wisdom. As if you already know what the seven levels are, and your job is to help me find them. As if you're partly responsible for my groping my way up to level three. Like a dog trainer. Well that's male bovine fecal matter. I'm not following you in order to expiate my sins. I made the right choices. You just happen to be going in the same direction I am. I'm not sure I want to trust your compass quite so uncritically."

Dumbledore peered over his glasses. "You might want to work that out better, Severus. It was a bit hard to follow."

"There you go being patronizing again. I decided last night that fate does play a role in this, but that fate and the will of Albus Dumbledore are not always the same thing. I decided I need more information." Snape took a small handful of Floo powder and knelt in front of his fireplace.

"What are you doing?" Dumbledore asked.

"Flourish and Blotts," said Snape, throwing the powder into the embers. When a clerk responded on the other side, Snape said. "This is the Headmaster of Hogwarts school. I'd like to order a copy of \emph{The Life and Lies of Albus Dumbledore} by Rita Skeeter. Put it on my personal account."

Snape tried to ignore the portraits most of the morning, even though Dumbledore did his best to engage conversation. Of the two, Dumbledore was the more successful.

"You know, Nigellus says that you really gave those three a morale boost yesterday evening. They know now that someone is helping them. They do not feel alone anymore," he said around ten o'clock, after several failed starts.

"They're exactly as alone as they were before." Snape answered. "Only their perception of the situation has changed."

"But that is because of you and your actions. The patronus was a brilliant inspiration."

"And if they knew where it came from, they'd be equally horrified and unsure of themselves."

"It does not detract at all{\el}"

"Yes, it does. I've been trying to protect that boy since his first year, and he hates me. If I told him London was the capital of England, he'd immediately insist it was Lincoln."

"You haven't exactly been the most loving of protectors."

"He hasn't exactly been the most endearing of students."

"You were comparing him to his father."

"I wanted to compare him to his mother."

"And how did you endeavor to do that?"

"When did Hagrid first take Potter to Diagon Alley?"

"On his birthday, wasn't it?"

"Right. July thirty-first. Then he took his books home and kept them for a month. A month. You would think he'd at least open them. The first day of classes, I asked him three questions. The answers were in the first chapter. He couldn't answer one of them."

"Which led you to the conclusion{\el}?"

"Lily would have known the answers."

"And James would not have. I see. I had understood from Professor Slughorn that under a different teacher{\el}"

"Now it's my fault? I'll remind you, sir, that the OWL scores in Potions have risen{\el}"

"That was not my meaning{\el}"

"And he was cheating!"

"You really do have to explain that to me, Severus."

"Slughorn let him use an older text until he got the new one. The book Potter got was my own, with all my notes and annotations. Potter was using my research, my experiments, to get good grades."

"Slughorn said he was like his mother."

Snape was silent.

"I see," said Dumbledore after a moment. "He was indeed like his mother, right down to the source of his inspiration and success."

"Lily was good at Potions!"

"But not extraordinary. No, Severus, that apparently took assistance. The assistance you gave to the mother, you also gave to the son. I see no cause to be bitter about it."

"When I gave him detention after Easter{\el} The spell he attacked Draco with was mine."

"I see," Dumbledore repeated. "It was rather a{\el} drastic spell."

"Sir, do you have any idea how long I worked with that spell, so that it could be wielded like a surgeon wields a scalpel, not like a lunatic with a meat cleaver?"

"I see the sins of Harry Potter are legion. He has taken after his father, has been insufficiently like his mother, and has benefited from your assistance, both intentional and unintentional, without showing the proper gratitude."

"You left out being an arrogant showoff."

"I thought that was covered in the `take after his father' part," said Dumbledore with a sad smile.

Snape went to the Great Hall for lunch, and it was there that the owl arrived from Flourish and Blotts with the biography of Dumbledore. The staff was not together at one table, so Snape unwrapped the book then and there and began to read, quickly aware that the others had noticed and were{\el} not happy.

After a few minutes, McGonagall joined Snape at his table. "You've actually given that woman money for writing trash?" she said.

Not looking up from the page, Snape remarked, "I thought you weren't talking to me."

"Don't flatter yourself, 'tis no conversation. I'm scolding you."

"Oh, well, that's all right, then."

They were both silent, then McGonagall took a deep breath. "Severus, I'd like a word with you, if you don't mind, in my office."

"It sounds like you're putting me on detention."

"This is no joke. There's something I want to say, and it wouldna do to say it here."

Snape rose, and McGonagall copied him. "I suppose," he said, "that I've no choice but to face the music."

She led the way out of the Hall, and all eyes followed them. It rather reminded Snape of an execution.

Neither spoke until they reached McGonagall's office, with its shelves of books and prim, academic decor. She ushered him in with a formal gesture, then closed the door and stood in front of it, barring his exit.

"Am I a prisoner?" Snape asked wryly.

"I don't know," McGonagall replied. "Are ye?"

It was a moment of clarity, clarity and sorrow for what had once been and could never be again. "You know why I'm here," Snape said.

"I know what was spoken of upstairs between ye, and Moody, and Dumbledore. But Dumbledore was already dead, and now Moody's dead, too, so there's just ye and me left to remember it, and I'm asking - Are ye a prisoner?"

Snape regarded her for a moment, his head cocked to one side. Fierce though she could be, confrontation was not McGonagall's strong suit, and he knew she was at least as uncomfortable about this as he was. "I come and go at my pleasure," he said at last, "but am always constrained to return, and the one who determines my actions is not always me. So you tell me. Am I a prisoner?"

McGonagall didn't blink. Instead she held out her hand, palm up. "I would take it as a very great favor, Severus, if you would be so kind as to allow me to look at your wand."

Knowing now what McGonagall wanted to do, and worse, knowing what she would find when she did it, Snape felt the blood drain from his face - and knew she would note that as well. He allowed himself to count silently to ten, then said softly, "I'm sorry Minerva, but I can't let you do that."

"Is it truly so bad as that?" McGonagall said, equally softly. She put her hand down. "Then there is nothing more we have to say to each other, is there?"

"Would you allow me to explain?"

"D'ye honestly think it would help?"

Snape turned away from her and went to the window, to look down onto the lawn in front of the castle, now covered with snow, and to the Whomping Willow and Hagrid's hut, from whose chimney a thin curl of smoke rose. The loneliness that had driven him from Hogwarts the night before filled him again. No matter what he did now, he'd lost McGonagall. Refuse or grant her request - either was equally damning. Yet in him was a desire, a longing, to have at least one person know his side of it, know what he'd gone through, to be able to say after it was all over - this is what Snape told me.

He turned to face McGonagall again and slowly drew his wand from his sleeve. "Promise me," he said, "that you'll let me explain. Promise that you'll listen."

She stepped forward and touched his hand. "How can I promise, laddie, when even you are so certain that I will not want to?"

McGonagall eased the wand from Snape's unresisting hand and took it to her desk. Clearing the desk of every item - for this was a powerful spell she needed to cast - she carefully laid the wand in the center as Snape watched, unmoving and impassive, from the window. Then, with a commanding upsweep and downward flick of her own wand, McGonagall ordered:

"\emph{Prioris omnis incantationis!"}

In its place at the center of the table, the wand vibrated. There was a small, percussive pop, followed shortly by another. "Apparation," murmured McGonagall. "Ye went somewhere. Last night, maybe," but another pop interrupted her, and then the unmistakable wisps of ghostly silver that were the shapeless traces of a patronus spell.

McGonagall glanced up in surprise at Snape. "Who were ye contacting with a patronus?" she started, then had to devote her attention to the backward scan of the daily life of a school - Lumos spells, graffiti-cleaning spells, Evanesco spells, a spell that carried an injured student to Madam Pomfrey{\el} all this interspersed with apparating - Snape remembered his trips to the Malfoy mansion, headquarters, Gringotts, and the Ministry, though the wand itself did not say where.

And then - "What were ye doing to Gryffindor's sword? Were ye daft, lad?" - followed by more routine until the unmistakable voice of Rufus Scrimgeour, Rufus Scrimgeour crying out in pain, emerged, and from that moment McGonagall could only stare speechless at the wand, stare and watch as, like bursts of color among the monotone of more mundane spells, she saw the Killing Curse that ended Alastor Moody's life, the slash of Sectumsempra that severed George Weasley's ear, the whiplash that struck Harry Potter's face and, finally, the twin curses that killed Albus Dumbledore and threw his body from the Astronomy tower.

At that point McGonagall stopped the Incantationis spell. There was nothing further she needed to see, and she sat down heavily in the chair behind her desk, her face a mask of shock and horror.

After a moment, Snape said tentatively, "Minerva?"

"Don't speak to me."

"You said you would listen."

"I made no such promise, and if I had, I would break it. There is nothing I want to hear you say."

"Minerva, please."

"That's what Albus said, isn't it? Harry heard it. Severus, please{\el}"

"He was asking me to do it."

"I don't believe you!" McGonagall was on her feet again, an avenging fury. "What about Alastor? And Scrimgeour?"

"Minerva, I swear{\el}"

"D'ye think I dinna remember what you hold against them? What you've held against them all these years? I watched them take ye off for a Death Eater, and I thought because ye were young, and a glib tongue in yer head, and a shy way about ye that maybe Albus was right and they were wrong, and no harm givin' ye shelter. And all these years ye've cozened me, and flattered me, and fooled me! Get out of my office ye snake! Get out! The sight of ye sickens me!"

Snape took his wand and left, and stumbled his way back upstairs to the seventh floor and the gargoyle. How could he possibly have miscalculated so badly? He'd considered McGonagall a friend, had assumed that even when faced with the worst she would at least think of him as a human being and hear his defense. How wrong he had been{\el}. how wrong. And where he'd hoped to make things at least endurable, he'd only succeeded in making everything{\el} everything{\el} infinitely worse.

Snape walked straight past the portraits, ignoring portrait Dumbledore's calls of "Severus{\el} Severus?" and up the short, spiral stairs to his bedroom, where he lay down on the bed and again stared at the ceiling. Below he could hear the portraits.

"Severus! Severus, what has happened?"

"I told you, Albus, we have been doing this{\el}"

"We're supposed to help the Headmaster, Albus, not drive him{\el}"

"Albus, this is too much of a burden{\el}"

"Quiet, the lot of you," said Dumbledore's portrait, muffled through the staircase, but still audible. "He will be fine. He is one of the most resilient people I have ever met. He bounces back from adversities that would crush a normal person. And he knows that what we do is for the greater good of the wizarding world. He will not fail us."

For the greater good of the wizarding world. Snape lay on the bed and listened to the portraits discussing him. \emph{If only I could believe that, believe that the pain and the suffering did serve some higher, better cause. If I believed that, I could keep going. If I believed that, I could accept even{\el}}

But why not believe it? The fact of the Dark Lord was inescapable. Voldemort existed. Voldemort was driving everything before him, taking control, destroying opposition{\el} Snape had been set a task, a duty, and that duty was to assist in the destruction of Voldemort. If that task was accomplished, then Snape existed for the greater good of the wizarding world. All pain, all heartbreak, all sacrifice, was worth it for the greater good. Snape rose and went back down the staircase to face the portraits.

\sbreak

Snape did not go down to the Great Hall for supper; he could not face it. Nor did he order food sent up from the kitchens since he wasn't hungry, his stomach rebelling, as it usually did when he was upset, against food. There was no news of Potter and his friends, and the portraits slumbered quietly. Snape stood by the window and watched snow flurries reflect the light from the candles in his office.

The slam of the door being kicked open made Snape jump and spin around, his wand instantly in his hand, expecting attack. And after a fashion it was an attack, though not one threatening bodily harm. Hagrid stood in the doorway of the office, holding a tray loaded with food. "Sorry to startle ya," he said gruffly. "M' hands was full."

"I'm not hungry," Snape said, putting the wand back up his sleeve and turning again to the snow.

"Yeah," said Hagrid, crossing the room to put the tray on the desk. "I heard. Seems you got a knack for doin' stuff that gets other people's backs up. Figured y'd be off your feed. There's plenty here 'cause I figured I'd join ya." He pulled a huge chair over to the desk. "So whyn't ya just settle yerself and do as y're told 'cause I don't relish sittin' on ya and forcin' it down your gullet, but I will if I have ta." He set out two plates and glasses for wine, and began loading food onto his.

Snape turned, leaning back against the stone wall, his arms crossed on his chest, to watch Hagrid. "Am I to assume you're not as particular about the company you keep as McGonagall is?"

"Professor McGonagall," said Hagrid through a mouthful of potato, "is a woman o' high moral character. She sees as there's things ya just don't do, not for any reason. It were bad enough suspecting y'd killed Professor Dumbledore, but now she knows there's three murders, and y've gone along with the Ministry, and y've allowed corporal punishment dealt out t' the children, and she's got t' figure y've sold yer soul."

"Maybe I have."

"Don't think so. I ain't too bright, but I can still add two and two."

"Meaning?"

"Alastor Moody. I was there that night, remember. I knew it was you. Y'never were comfortable on a broom. I figured you'd figure I were the one with Harry, so it weren't no surprise ya didn't go after me. Ya went after Lupin and cut off George Weasley's ear. Lupin recognized ya."

"That was an accident. I was aiming at the Death Eater who was going to kill Lupin. I{\el}. missed."

"I'm glad t' hear that. Didn't think ya had anything 'gainst George. Course, ya wouldn't've known it was George, would ya? Point is, ya didn't go after Moody. You-Know-Who went after Moody. Bill Weasley saw it. You-Know-Who hit Moody in the face with a curse, and he musta fallen fifty, sixty feet. So if you got a killin' curse in your wand for him, there's gotta be another story to it."

"Moody was still alive. He was dying - the fall - but it would have taken a couple of hours, and they were coming back. The Dark Lord's anger is both cold and cruel."

"Which o' you made the decision?"

"Moody."

"Tha's all right, then. And then there's old Scrimgeour. Ye were there?"

"Yes."

"How long did it take?"

"Twelve hours."

"There now! All that time and only the one curse outta your wand! They must notta been paying you much attention, ya get away with a halfhearted effort like that! Now you get over here and eat!"

"You haven't asked about Dumbledore."

"Don't have to. He told ya t' do it. I knew that the minute Harry said 't was you."

"How{\el}?"

Hagrid put his knife and fork down and leaned forward, his fists on his thighs. "Now ain't I taken care o' you since you was twelve? Wasn't it me ya first came to when ya turned yer back on You-Know-Who? Not Dumbledore, me! And wasn't it me as grabbed yer coattails that night ya thought y'd go flying off the tower? How'd I know? I know you. Now you start eating before I have t' sit on ya."

Snape left the window and joined Hagrid, helping himself to the food rather eagerly, for he was suddenly hungry. The first bite was halfway to his mouth when another question occurred to him. "Hagrid, how did you get into my office?"

Hagrid grinned at the question. "There's a conspiracy below stairs, has been for decades."

"Below stairs? Servants? You mean the house-elves?"

"Got it in one! You always was bright. House-elves can go anywhere. Ya don't make yer own bed, do ya? Lay yer own fire? Nobody ever asks how the house-elves get by the passwords." He held up his pink umbrella. "Didn't ya ever wonder about this?"

"I know it's a wand you're not supposed to have{\el}"

"Tha's right. I got kicked outta Hogwarts when I was thirteen over that Chamber business, and they broke my wand. Ever hear of a broken wand that still works? Ever hear of a broken wand that can be fixed proper?"

"Now that you mention it, no. I do remember the damage caused by Weasley's wand, and it hadn't actually separated."

"Mine wouldn't work either, but then Headmaster Dippet gave me the job. Well, that put me on staff, too, not like a teacher, but like them elves. Servants. They fixed my wand and put it in the umbrella. It still ain't real powerful, but it can do elf-type things, like get through doors."

Snape nodded. It was amazing the things that happened every day in the school that he never noticed or knew about before. He and Hagrid continued eating in comradely silence, but just as Hagrid was leaving, Snape had another thought.

"It's probably best if you don't try to defend me to anyone. There's a long road still ahead of us, and if the Carrows ever get the idea I'm not on their side, I may not make it to the end."

"Gotcha," said Hagrid. "Y're a deep-dyed villain."

"Thank you, Hagrid," said Snape. "And thank you for supper."

The next day was Sunday, the twenty-eighth. Snape went down to breakfast and endured the ostracism of his erstwhile colleagues. The Carrows weren't down yet, and Hagrid was obeying orders, so Snape ate alone, reading the biography of Dumbledore that he hadn't had the heart to pick up again the day before, after his encounter with McGonagall.

The book gave him a lot to think about. That the young Dumbledore had been friends with Gellert Grindelwald was a surprise, but that he'd dabbled in questionable, elitist philosophies didn't bother Snape at all. It was part of youth to stretch out and try things that appealed to the heart as well as the head, and to think that you had the secret for saving the world. Snape had dabbled in questionable, elitist philosophies, too, and had the mark on his arm to show for it. \emph{The key is whether or not you grow and learn and change. Anyone who has exactly the same principles at forty that they had at twenty just isn't doing any thinking.}

After breakfast, Snape continued to read in his office, taking notes from time to time of things he wanted to ask portrait Dumbledore about, though he wanted a clearer picture in his own head before he actually broached the topic. He was so deeply engrossed in the subject that when the mark on his arm started to tingle, he absent-mindedly scratched it. The tingle grew stronger and became an itch, and then he was staring at his arm as if it was a monster rearing up to strike him. He ran for his bedroom, grabbed a cloak, and raced out again, crying to the portraits, "He's calling me!" as he bolted out the door and down the stairs.

The Carrows had been called, too. Snape wasn't happy at the idea that the whole staff would guess that the three of them were dancing attendance on the Dark Lord together, but there was nothing else he could do. They could not disapparate from Hogwarts. They had to go down the hill and out the gate, and leave for the Malfoy mansion from Hogsmeade.

The call was not from the Dark Lord. The call was from Bella. This in and of itself was a shock, since Bella had never dared usurp the Dark Lord's prerogatives before. The cause, when she told them however, was sufficiently important that Snape understood, and felt the Dark Lord would likely not be angry.

"Potter's been seen," Bella announced as soon as most of the inner echelon had arrived and were seated around the meeting table. Bella sat between her husband and brother-in-law, leaving the Dark Lord's seat empty. "Travers and Selwyn saw him escaping from Lovegood's house this afternoon. The mudblood girl was with him."

"Did they apparate?" Rookwood asked.

"Selwyn tried tracing them, but it looks like they put up protective spells at once. He couldn't get a fix, so he contacted me immediately."

"What did they want from that nut case Lovegood?" Avery asked. "He has trouble getting the time of day right."

"We don't know," Bella replied. "They Obliviated him just as they were leaving. Luckily they trusted him at first, otherwise they'd never have given him the chance to contact Travers and Selwyn."

Rabastan smiled. "I told you he'd be more reasonable once we had his daughter in our power." At Snape's look of surprise, he elaborated. "We took her off the train at the beginning of the Christmas break. She's a prisoner in the cellar of this house right now."

\emph{Say something, Severus,} Snape thought. \emph{Something that a person in your position should say, would say{\el}} He gazed blandly back at Rabastan. "How long were you planning on keeping her? She is, after all, a student under my jurisdiction."

"I think your jurisdiction can take second place to stopping the articles her father was printing. She'll probably be a guest here for a while." Rabastan exchanged a smirk with Bella and Rodolphus while the others around the table waited in silence. Macnair was practically salivating.

"In that case," Snape said calmly, "I'll have to insist on evidence that the girl is unharmed."

Bella gasped. "You have to insist? Keep your nose out of Operations, Headmaster. You haven't got any authority here."

"Oh, but I have," Snape replied. "The girl is enrolled at Hogwarts for the entire academic school year which will not end until June twenty-eighth. I am legally responsible for her since she has yet to return to the protection of her family. Now if you had waited until she had gotten back home{\el}"

"Don't prat to me about legalities, Snape!" Rabastan spat at him. "The reality is{\el}"

"The reality is that you're blundering ahead without the authorization of the Dark Lord, and may be rudely awakened when he finds out you've angered his old Head of house and his Charms professor. But if you want to take that chance{\el}"

"What are you talking about?" Bella snapped, her eyes narrowed and dangerous.

Snape calculated the odds and rolled the dice. "How much has the Dark Lord told you of his time at Hogwarts, Bella?"

Her eyes widened. Snape's gamble had paid off. "He has{\el} hasn't{\el} I{\el}" she faltered.

"Nothing, I take it," Snape said. "You are completely unaware that the Dark Lord remembers his old school with a fondness he reserves for few other things." In this, of course, Snape was relying on information passed to him by Dumbledore, but it was better than anything anyone around him had. "I have already mentioned this," he nodded to the Carrows, "but it is worth repeating. We are supposed to be winning hearts and minds to the Dark Lord's cause. If he held ill feelings towards his former professors, people like Slughorn and Flitwick, or against former classmates, people like McGonagall, would he not have sought the Board of Governors to have them removed and replaced with others? That he did not should be a warning to you to treat them with care. Now you tell me that you are holding a girl of impeccable blood purity who is in the house of the Dark Lord's former Charms professor and in the Potions classes of his former Head of house. A girl who is respected and well-liked -" This was an exaggeration, but they would not know it. "- a girl after whom they will inquire. All I wish to be able to say is that she is safe and well treated. I do not consider that an unreasonable request."

Bella eyed Snape shrewdly, then called, "Wormtail!" When Pettigrew responded, she ordered, "Take the Headmaster to see our prisoner and show him she's safe. Don't let her see him."

Snape would have preferred staying at the table until the meeting was over, but took what he could get. Rising, he followed Pettigrew out of the room, down a corridor toward the kitchen of the manor house, and then down a spiral staircase to the cellar. It was a large area, with several storerooms. Pettigrew walked over to one whose door was both padlocked and sealed with charms and tapped on the wood.

"Who's there?" said a soft, gentle voice that Snape recognized as Lovegood's.

That's none of your business," Pettigrew said. "There's someone here who wants to hear you."

"Oh, how lovely!" replied Lovegood behind the door. "So many people just want to see you. But if someone wants to hear you, then you have to talk, and that's a certain amount of interaction."

"Tell him that you're okay, that you haven't been harmed."

"Him?" Lovegood asked. "Father, is that you? I am sorry I didn't have a chance to give you my Christmas present{\el}" She paused. "Not my father? An admirer, then? Someone who read my article on the Crumple-Horned Snorkack and wants an autograph? I knew I would be famous for that."

"Tell him everything is fine. You haven't been hurt."

"Oh, but I have! I have been hurt. Let's see. They twisted my wrist, and they pulled me by the hair. And then they used ropes to tie me up. And I was blindfolded when I so wanted to see the snow crystals on the trees. And I missed Christmas. And I haven't had treacle tart even one time. And they won't let me take proper care of Mr.~Olliv{\el}"

"Shut up!" Pettigrew yelled at her. Then he turned to Snape. "Satisfied?" he asked, rubbing his hands together, the flesh one and the silver one.

Snape nodded. He would have liked to have assured the girl that her captivity was under surveillance, but he didn't dare as that would have made the situation worse and jeopardized his own position. Still, she seemed perfectly normal - for Lovegood at least - and she'd thrown out a piece of information. Ollivander was also in the cell. Perhaps he was even the prisoner who'd been in the cellar during the meeting in July, when the Dark Lord had asked for Malfoy's wand.

"Well?" Bella asked when Snape returned to the meeting room.

"She seems well enough," Snape replied. "Make sure she stays that way. At least until you have orders to the contrary."

"Now," said Bella, "we need to talk about the rest of the school."

"I beg your pardon?" said Snape.

"We've been having a discussion. It seems you've been hampering your new professors."

Snape spared no glance for the Carrows. "The new curriculum for Muggle Studies has been implemented as fully as can be expected considering that there is no approved text. Professor Carrow is aware of the need for her to provide supplemental material. I have denied none of her requests{\el}"

"I was thinking more about Dark Arts."

"The curriculum for Defense against the Dark{\el}"

"No, Snape! You're not listening. I'm not talking about defense. I'm talking about Dark Arts."

"The Board of Governors hasn't{\el}"

"But you don't really work for the Board of Governors, do you?" Bella looked around the table, and Snape followed her gaze. Sharks was the word that again came to mind. Blood in the water. Jackals. Hyenas.

"Technically, I do," Snape said.

"But in reality, you don't. I think I'm going to have to remind you, puppy dog, that the Dark Arts class is part of Operations. We're training people, new operatives. They need to know the material. Unforgivables is part of the material. Amycus needs to teach it."

"Neither the Board of Governors nor the Ministry has{\el}"

"But the Dark Lord has. Who do you work for, Snape? We're all friends here." Her gesture was meant to take in the whole table, but seemed to point to Macnair more than anyone. "You're not talking to the Board or to the \emph{Prophet}. You're talking to the Dark Lord's servants. Don't you want to implement his will? Don't you want to train operatives for him?"

"Of course I do," Snape answered, there being no other acceptable answer.

"Then you should be finding ways to help, not looking for excuses to defend inaction."

"I'm still answerable to the Board. If they don't like what I do, they'll fire me. My replacement might not be as acceptable to the Dark Lord."

"You're a bright boy," said Bella. "You'll figure out something."

Snape looked over at Amycus, who was grinning. "I'm sure we'll be able to work out an acceptable solution," he said.

The return to Hogwarts took place in total silence. As they were walking back up the hill, Amycus finally spoke. "Cruciatus curses," he said. "That's what they really need to work on. Cruciatus curses. Only experienced people can handle Imperiuses, and killing is on special orders, but even the kids can help with interrogation."

"I'll keep your views in mind," said Snape, and left them in the entrance hall.

The portraits debated long into the night.

"Teaching students Unforgivable Curses," lamented Headmaster Dippet, shaking his head sadly. "What has Hogwarts come to?"

"I myself gave similar orders three years ago," said Headmaster Dumbledore, "though I admit the professor I gave those orders to was not who I thought he was."

"But that case was not at all similar," insisted Headmistress Derwent. "That was information. These students are being asked to practice the spells."

"And if they do not," interjected Headmaster Fortescue, "we will lose Headmaster Snape and acquire someone new who will not have Hogwarts's best interests at heart."

"And what do you have to say about this?" Dumbledore asked the hitherto silent Snape.

Snape was staring into the fire. "Potter has not yet," he said, "been given the information he needs to ensure the defeat of the Dark Lord. I understand that only I can give him that information. Is my remaining in a position where that might happen of sufficient importance to warrant causing students to suffer temporary pain? I don't have the answer to that question."

"Then let me ask you another, Severus," said Dumbledore. "If you were one of those students, would you be willing to suffer the pain in order to destroy Voldemort?"

Snape looked up at him, all that he had lived through glowing bright in the anger in his black eyes. "That, sir," he said, "is a question you already know the answer to."

The first one Snape had to talk to was Flitwick.

"Not coming back?" said the Charms instructor. "Detained? I don't understand."

Snape tried to chose his words with care. "Miss Lovegood's relations have been publicly attempting to undermine observance of laws. Her presence was required to assist in showing these relations the lack of wisdom inherent in these actions."

Flitwick refused to discuss the matter in a calm or rational manner. "She's been kidnapped to force her father to stop publishing! That's what you're trying to say, isn't it? They're using the children to coerce the parents! How can you go along with this, Severus? I thought you were a decent human being! How can you go along with this?"

\emph{Because of the consequences I cannot live with}, Snape thought, but did not voice this thought to Flitwick. Instead, he concentrated on the practical. "I saw where she's kept," he said. "She spoke to me. She's well - unharmed. Just detained. I'll do what I can to get her back, but you have to understand that I don't have a lot of authority in this."

"Well you'd better find some!" Flitwick bellowed in a voice much too large for his tiny frame, and stalked out of the office.

The meeting with McGonagall was equally tense.

"I'm denying them permission to go to Hogsmeade," Snape said for about the dozenth time. "I have good cause, and nothing you say will change my mind."

"Then why won't you tell me the cause?"

"I can't. Minerva, please{\el}"

"It's petty vengeance, it is, Severus Snape! These children - Weasley, Longbottom, Finnigan - they won't bow to your rule like sheep, so ye take away one of the few pleasures they have. It's mean, it's cruel{\el} It's action I'd have said was beneath ye a year ago."

\emph{It's protecting them from kidnapping, Minerva,} Snape thought, \emph{but I can't tell you that. It's as much as my position's worth to tell you that, and I have to keep my position at all costs, at least until Potter's informed and the last scene is being acted.}

McGonagall, like Flitwick, stomped down the stairs in rage.

The last straw, naturally, was the implementation of Amycus Carrow's plan to have detention served by being the subjects of the upper years' Dark Arts exercises. Snape actually found out about this in a backhand way since it was not school policy, just Amycus's idea of detention.

"Do not be hasty," cautioned the portrait of Dumbledore in the second week of January with the school humming again with students. "We are not talking about a large number of students. What is it now, three? And the students casting the curses{\el} they are not hardened Death Eaters. Have you known one of these curses to cause even as much pain as{\el} as dropping a copy of \emph{A History of Magic} on your toes?"

"That can be pretty painful," Snape answered.

"Yes, that is true{\el} Did you really once drop \emph{A History of Magic}{\el}?"

"No," said Snape. "Never. And McGonagall doesn't agree with you about the mildness of the spells. The fact that students are encouraged to curse other students is more than enough for her."

"I recall she got considerable amusement from James Potter and Sirius Black cursing you."

"Did she! The old witch! Not as pure as she makes out! I'm going to use that, sir. I mean it. I'm going to use that."

"Just," said Dumbledore, "don't tell her you got the idea from me."

And in the midst of the turmoil there was Hagrid. Three or four times a week, Snape crept out of the castle after curfew to sneak down to Hagrid's hut for a cup of tea and a chat. He usually did most of the talking. Mostly against McGonagall.

"Doesn't she understand it's for their own protection? Does she want them held hostage for their families' behavior? Does she want Arthur Weasley knuckling under to the Ministry because his Ginny's locked up under the floor of the Malfoys' dining room? Does she?"

"Probably not," said Hagrid, pouring more tea. "Have ya put it to her like that?"

"I can't. If I say anything and it comes back to me{\el}"

Hagrid shrugged. "This thing Dumbledore wants ya t' do, is it really that important? Is it important enough t' wager yer soul on? 'Cause it seems t' me that's what y're doin'.

Snape thought about this for a moment, "Yes," he said finally. "It's that important."

And then there was the long wait.

One of the great mysteries in all of this was the continued absence of the Dark Lord. Clearly he was off somewhere doing something that was vital to his closely held plans for success, but informed no one of his whereabouts or intentions. Even Bella had no idea where he was.

Equally mysterious was the continued lack of information about Potter, though here Snape was a little bit less in the dark than other people because of the continued reports of Phineas Nigellus. At least Snape knew of a certainty that Potter was with his friends, camping in a new spot every night, and lying low.

With the new year, however, others were not lying low. An underground resistance had sprung up all over wizarding Britain. It started with part-bloods, half-bloods, and purebloods giving shelter to fugitive muggle-borns. A clandestine radio station began giving reports of Ministry clampdowns and Death Eater attacks, and encouraging discontent. The hundreds of students going home for the holidays in the middle of December, revealing what was happening at Hogwarts - the new classes, the corporal punishment, the outbursts of rebellion against the regime of Snape and the Ministry - had added fuel to the fire.

Now, as the new year advanced, Bella took more and more control, sending operatives out on missions to crush opposition, round up rebels, and shut down the broadcasts. There were weekly reports of attacks and deaths, and no one was willing or able to curb Bella and her department.

At the beginning of February, Snape was called into his laboratory at headquarters to make more potions for the infirmary and Operations. It took the better part of two weeks, and Snape was constantly apparating between Hogwarts and the lab.

"I thought you'd been promoted while we were away. Guess I was wrong."

Snape didn't turn at the sound of Macnair's voice in the doorway, but continued decanting a wound-knitting brew. "Only to fill the vacuum until you got back," he said quietly. "You know I could never replace you."

"No stomach for it, eh?" Macnair laughed. "Or maybe you just prefer to be in the other role."

"Right," Snape said sarcastically. "The light touch of your wand at the base of my skull was one of the high points of my existence."

Macnair crossed the room easily and stood, a head taller than Snape, watching over the potion master's shoulder as he stirred the now clear medicine and poured it into a large flask. "Admit it, Severus, it's moments like that that let you know you're really alive."

Snape wanted to step away; Macnair's presence made his skin crawl. And yet, the ghost of an idea had formed. Macnair had information. "Walden," he said, and felt rather than saw Macnair's smile at the use of his first name. "Why was the Dark Lord so angry that night? He knew I couldn't come right away. What happened before I got there?"

"The Potter brat got away. You know that."

"No, I mean the details. What happened?"

"He was already angry when he called us. He was furious that the only ones who could answer were the ones who turned their coats, renounced him, wiggled out of Azkaban. He Cruciated Avery. I thought he was going to do the same for me since I was even working for the Ministry. But what he really wanted to do was duel Potter."

"Duel, not kill?" Snape was certain now that Potter had given all of this to Dumbledore, but that Dumbledore had kept it to himself. He also knew instinctively that a duel with wands must be connected to Lucius Malfoy's wand that the Dark Lord still carried, and with the old wand maker in the Malfoy cellar.

"Yeah. It was fun to watch at first, how he toyed with Potter. Forced him to bow. He was going to win, too, just playing with Potter before the kill, except something happened between the wands. The spells met in midair, and the wands couldn't separate, couldn't break away, and the Dark Lord's wand started giving up its spells."

\emph{Like McGonagall did with mine. Only this wasn't because of a spell. It has something to do with the wands.} "So there was a duel and Potter won. He didn't just escape, he won."

Macnair stepped quickly back, distancing himself from Snape. "Don't say that, Severus. The whining little rat didn't win, he just ran. Running isn't winning."

"Of course not. I was being foolish for a moment. The boy ran. He didn't win." But it was not Potter's wand that had been forced to give up its secrets. Was that the reason the Dark Lord took no part in the fight in the Department of Mysteries until forced to in order to salvage Bella from the debacle? Why he didn't come through the vanishing cabinets himself to preside over the taking of Hogwarts? Why he took Malfoy's wand that night{\el}? That night{\el}

"Walden," Snape turned to face Macnair. "Did you follow the Dark Lord in July, that night we tried to take Potter?"

Macnair frowned, puzzled. "Not me. I followed the thestral. Selwyn was with him, though. Why?"

Snape shrugged. "All these potions for all these operations got me thinking, remembering. That was the only operation I've ever been on and I found it all very confusing. I'm still not sure what happened that night."

"That's what you get for not socializing. You should hang around with me more - you'd pick up all the news. The Dark Lord got Moody, then he went after Shacklebolt. That's who I was after. Selwyn says they were following Hagrid when the Potter kid used a signature spell - he's too nice for his own good, that one, and they called the Dark Lord in for the kill. But something was wrong with Malfoy's wand, so the Dark Lord took Selwyn's and then they ran into a protective charm and Potter got away."

"Something wrong with Malfoy's wand? Isn't the Dark Lord still using it?"

"Who knows?" said Macnair. "Selwyn just said the Dark Lord was using Malfoy's wand until Potter got off a crack backhand shot, and then the Dark Lord ask for his, Selwyn's, to keep fighting with. Selwyn's got his wand back, but Malfoy hasn't."

"It still sounds confusing," said Snape, turning back to the counter and his potions work. "I think I'm not cut out for operations. I'll stick to what I'm good at."

Back at Hogwarts, Snape confronted Dumbledore's portrait. "What else are you keeping me in the dark about?" he demanded, furious and letting it show.

"In the dark? Severus, what ever are you talking about?"

"You've known for two and a half years that the Dark Lord is concerned about the wand he uses to fight Potter with, and you haven't mentioned it to me once!"

"Has this come up for some particular reason?" Dumbledore was peering over his glasses again, a mannerism Snape was beginning to find immensely irritating.

"Nobody knows where he is. He's looking for something. Did you know he borrowed Lucius Malfoy's wand the night Potter left his old home? At the time I thought he was just being mean to Malfoy, who still doesn't have it back{\el}"

"How would I know this, Severus, unless you told me? Who is keeping whom in the dark now?"

Snape stared at the portrait. "Oh, right," he said after a moment. "Macnair tried to{\el} well Macnair referred back to the night of the Dark Lord's return and told me what happened when his wand met Potter's. Nobody told me that before. Then I thought about his keeping out of Potter's way when there was fighting, and kidnapping Ollivander - I'm sure now it was Ollivander we heard in the cellar the night we went after Potter, and he didn't want to use his own wand to fight Potter, so he borrowed Malfoy's except he didn't say that was the reason, but he was perfectly willing to use his own on Scrimgeour. I thought he still had both wands, but Macnair says Potter was able to get off a backhand shot that made the Dark Lord take Selwyn's wand and{\el}"

Snape was perfectly aware that he sounded barely coherent, but the thoughts and images were connecting so rapidly in his brain, streaming in from all sides to form one suddenly clear picture, that for once he could not control the words that tumbled from his mouth. The portrait of Dumbledore remained silent, listening.

"Sir," Snape exclaimed, "could that be what the Dark Lord is doing? Looking for the right wand to fight Potter with?"

"It is very possible," Dumbledore replied. "And I wish to point out to you that it was wise not to entirely rebuff Macnair's advances. He has proven an excellent source of information."

"But why does the Dark Lord have to look for a wand? He has Ollivander. Can't Ollivander just make him a new one?"

"An excellent question," said Dumbledore, though he made no attempt to answer it.

Both were silent for a while, and then Dumbledore asked, "Do you remember the fairy tales, Severus?"

The question was so far off the topic that Snape opened his mouth, had nothing to say, and closed his mouth again. After a moment, he said, "You mean like `Sleeping Beauty?' `Snow White and the Seven Dwarfs?' You know neither of my parents ever told me stories. I used to get sent to a neighbor's house when my father wasn't{\el} feeling well. Mrs.~Hanson told me a couple of stories. I always liked `The Steadfast Tin Soldier.' I could see myself in that little paper boat, heading for the ocean."

"Yes," said Dumbledore, "it does seem to fit you. Rather a sad tale for a little boy, though."

"Really? I thought he was noble." Snape realized then what he'd said, and reddened. Both he and Dumbledore allowed the subject of fairy tales to drop for the time being, though later Snape wondered if Dumbledore might have been referring to Beedle the Bard.
