% A Difference in the Family: The Snape Chronicles (Rannaro)
% Where Your Loyalties Lie

\chapter{The Menace Revealed}

"I tell you, Minerva, Fred was jinxing the quaffle. I've cast enough jinxes in my life; I know what one looks like."

"Well, I didn't see it, or anything like it. I saw you give two penalties against Gryffindor in the first three minutes, and I didn't see cause for it."

Trelawney cackled as she swept past. "Hopes dashed! What did I tell you? All hopes dashed!"

\emph{You don't know the half of it, you old witch. Something happened out there that Dumbledore was controlling, and now I'm still no closer to solving my problem.}

Then Snape saw Quirrell heading toward his first floor rooms. \emph{No. I still have cards to play. If I can't go after the spell caster, I'll go after Quirrell. That'll be something Dumbledore can't interfere with.}

"Quirinus!"

Quirrell looked around. "Did you{\el} want to talk to{\el} me, Severus?"

"Did you enjoy the game? You've become quite a Gryffindor fan. I saw you at the November game as well. Don't remember your being so keen on Quidditch last year."

"I{\el} thought the air, you{\el} know, the excitement{\el}"

"Would do you a world of good, yes I know. Or maybe you're just curious about Gryffindor's new seeker."

"Severus, I don't think{\el}"

"Time you did. You and I are going to talk. Now. But not here. Meet me in the forest, just behind the willow, in about fifteen minutes."

\emph{In a spot where no listening spells will work properly. Not even the ones I invented myself.}

Snape went first to his rooms to slip on a heavy hooded cloak, partly because it 'd gotten quite cold, and partly to minimize notice. Enough people walked around in the warmer cloaks during the winter that few would pause to question another one. Then he left the Castle and hurried down the hill as if heading for Hagrid's hut. A little past the willow, he turned suddenly and darted into the trees, hoping that in those few seconds no one had been watching from the Castle windows.

Quirrell was already there, standing with his back to Snape, facing into the forest. As Snape reached him, he turned around. Snape lowered his hood.

"I came," Quirrell said.

"Very wise. I thought, before this went any further, that I'd give you the opportunity to show that trust in you was not misplaced. You and I have been running into each other at the most awkward moments, and I can't shake the feeling that your motives aren't entirely blameless. I have an interest in seeing that my labor isn't in vain, so you understand why I take this personally."

"We could{\el} talk about this inside. I{\el} don't know why you wanted{\el} to meet here of all{\el} places, Severus{\el}"

"Oh, I thought we'd keep this private. Students aren't supposed to know about the Philosopher's Stone, after all."

"You know that I'm{\el} just as dedicated to{\el} protecting it as{\el} you are."

"Have you found out how to get past that beast of Hagrid's yet?"

"{\el}But Severus, I—"

"You don't want me as your enemy, Quirrell." Snape took a step towards Quirrell and was satisfied to see that Quirrell retreated.

"{\el}I don't know what you -"

"You know perfectly well what I mean. Not everyone was fooled by your little bit of hocus-pocus. I'm waiting."

"{\el}But I{\el} don't -"

"Very well. We'll have another little chat soon, when you've had time to think things over and decided where your loyalties lie."

Snape drew the hood back over his head and left, not bothering to look back and see if Quirrell followed him or not.

\emph{Done. All cards on the table. No more guessing. He'll either be scared enough not to try anything else, or he'll come after me and prove I'm right. Either way, something will happen. And if it was Quirrell targeting the Potter boy, that should stop because now he knows I'm the greater danger. If it happens again, I'll know there's someone else behind it.}

The most infuriating thing was that after their conversation, Quirrell did nothing at all. At least nothing that could be specifically tied to Snape's threat. What he did appeared to be tied to the Quidditch game.

Walking into the Great Hall that evening for supper, Snape found that he was being ignored by every teacher there. It seemed that McGonagall's opinion about the penalties was universally shared, and the general consensus was that if not for Potter's lucky catch of the snitch within the first five minutes, Gryffindor would have been cheated of a victory.

Snape sat at the end of the high table anyway, so he didn't usually talk to most of the teachers except Quirrell, who sat beside him. Now Quirrell moved his chair to the left and spent the entire supper with his back to Snape, discussing the transits of the planets with Professor Sinistra. \emph{Not really a bad tradeoff. I'd rather look at that stupid turban all evening than his face.}

At least he could use the time to think. One of the biggest question marks was Dumbledore's role in the whole business. The Headmaster's presence at the Quidditch match made it twice that Snape was discouraged or prevented from looking for the spell caster. But what game could Dumbledore possibly be playing?

Suddenly, without warning, Snape began to shut down. Doors closed and locked, thoughts sank into hiding below the level of consciousness while other decoy thoughts swam to the surface, and Snape found himself remembering the first time he'd been jumped by James Potter and Sirius Black. He looked quickly around the Hall, and glanced down the teachers' table. No one was watching him, no one attempting to establish eye contact, and yet{\el} \emph{Some one is trying to read me. Someone here in the Hall.}

Snape let the decoy thoughts float freely in his brain, trusting to instinct to keep him safe, while he began slowly reviewing the face of every student in the Hall. No one was looking at him. No one gave the least sign that he or she was practicing legilimency. Again Snape glanced past Quirrell's back and along the teachers' table. No one there was acting suspicious either. \emph{An animagus? A mouse in the corner? A bat or bird in the rafters?}

His appetite now completely gone, Snape rose and quietly left the Hall. No one appeared to notice, probably assuming that it had to do with the afternoon's Quidditch game.

Back in his office, Snape sat alone in the dark room for several hours. He now had more evidence that a powerful wizard was in Hogwarts, but this evidence was even harder to prove. The first time, everyone at the game had seen that Potter's broom was being jinxed. The second time, Filch was a witness to the night prowler in the library. This time there was no evidence outside Snape's own head. \emph{Can I go to Dumbledore with this? Will he believe me? Will he tell me if he does?} He realized with a start that he was absentmindedly rubbing his left forearm.

Turning the lights on in the room, Snape stared for a moment at the arm, then rolled up the left sleeves of his robe and the gown underneath. The mark of the skull with the serpent issuing from its mouth was faint, but clear. \emph{Is it my imagination, or is it itching? And maybe just a touch darker and clearer? It isn't definite enough for proof. Besides, he's dead. He is dead, isn't he?} Was there something Dumbledore knew?

Then Snape thought again of Dumbledore's sudden secretiveness, and a knot tightened in the pit of his stomach, and an icy foreboding gripped his heart.

\sbreak

The next two months passed quickly as the students and teachers realized that the time until final exams could now be counted in weeks. In the hourglasses in the entrance hall, Gryffindor's rubies still topped Slytherin's emeralds, and McGonagall was speaking to Snape again.

"You've been jumpy as a cat on coals lately, Severus. Whatever is the matter with you?"

"It must be the students. It must be collectively the most incompetent new class I've ever taught. Don't you have the same experience?"

"Now that you mention it, there has been a higher percentage of mistakes and unfortunate incidents than usual, and Flitwick is rather on edge about some of the problems he's had. But you're worried about something more than just classes."

"I don't know why you think so, Minerva."

"The way you've been prowling the halls and watching the students{\el} There! You're doing it again. You keep looking around like you thought something was going to jump out at you."

"Maybe I just need a holiday."

"Speaking of which, what are you doing for the Easter break?"

"Nothing special. Just try to relax."

"I was thinking of getting down to London for a day, pick up a few things{\el}"

Over McGonagall's shoulder, Snape's restless eyes continued to search the faces of the passing students, finding nothing there to ease his apprehension.

\sbreak

Because Easter fell after the middle of April that year, the Spring Term had been long, while the Summer Term would be very short. As a result, a much larger percentage of the student body stayed at Hogwarts for the Easter break than had for the Christmas break in order to study for exams. There were no classes, but supervisory duties did not diminish.

McGonagall managed to fit in her London trip on the Tuesday after Easter. She'd been planning to go on the Monday until Snape reminded her it was a Bank Holiday, and while Diagon Alley would still be doing business, some other things might be closed.

"Stupid to give a holiday to a bank," fumed McGonagall. "These muggles and their idiot ideas, interfering with a person's plans."

So it was that Snape felt partly responsible for McGonagall's frustration, and made a point to speak to her on her return.

"How was London?" he asked at supper, snagging Flitwick's seat and forcing the Charms teacher to sit next to Quirrell for one evening.

"It was lovely, lovely. And I even managed to get into the Public Record Office for an hour, which I couldn't have done had I gone yesterday, so I owe you one."

"What were you looking for in the Public Record Office?"

"Oh, I'm doing this thing on seventeenth century witchcraft trials. A little here, a little there. Did you manage to find some free time today?"

"I'd thought to get down into Hogsmeade, but it wasn't going to happen today. The terrible twins managed to release whooping gas into the study hall on the second floor, and there was pandemonium."

"Well, that didn't stop Quirrell from getting out."

"Quirrell was in London?"

"No, silly. He was in Hogsmeade. I saw him when I apparated back in, late this afternoon. He looked like he'd just come out of the Hog's Head, and he was taking off this enormous hooded cape and stuffing it into a bag. I thought it odd because it's been so warm all day. I certainly wouldn't want to wear something like that in weather like this."

"I've given up trying to figure out why Quirrell does what Quirrell does. Maybe he was raised in a greenhouse."

But Snape began to look around the half-empty Hall again, and noticed for the first time that Hagrid had not come to supper.

\sbreak

More than a month passed, a very hectic month. The only bright spot in first year Potions was the Granger girl, and she managed to spoil it all by being an insufferable know-it-all, even when she was wrong. A major disappointment was Draco Malfoy.

"Your marks in both the autumn and spring terms were mediocre, Malfoy. I can't give you extra material to study when you can't excel in the classes you're required to study."

"I can handle the extra work. I'll work harder at everything, and bring my other marks up, too. Father says I have to learn this from you."

"Lucius can be{\el} very insistent. Very well. I am going to give you a description of the formation and dispersing of sound waves, and of various important frequencies. I want you to learn them, and be able to explain them to me in words other than the ones I've given you."

"What do I need to learn this for? It's just a bunch of numbers."

"That bunch of numbers can help you invent spells that will prevent anyone from overhearing what you're saying, let you listen into a conversation on the other side of a Quidditch pitch, or allow you to walk silently over autumn leaves. But if you don't know the numbers, you haven't got a prayer of inventing the spells. Physics first, magic second."

Malfoy looked at the list as if it were the mythical crock of gold. "I can do all that? I'll learn this so fast. You won't be disappointed in me, sir."

\emph{And there'll be snow fights in Hell when you come back to me knowing everything on that list. Oh, Draco. You haven't stuck to anything for longer than two days since you got here. Where do you get it from? Neither of your parents was like that.}

At the end of May, Draco Malfoy was brought to Snape for reasons much less admirable than studying the physics of sound waves.

It was a Saturday night, and Snape was up reading well past eleven, since he didn't have night patrol and didn't have to get up early the next day to prepare for classes. It was a murder mystery that he'd never read before, and he was deeply involved in the identity of the corpse plowed up in a field, and whether it was the missing wife of the potter turned monk, when there was an emphatic knock on his office door.

Crossing through the office, Snape opened the door on an infuriated Professor McGonagall and an embarrassed but defiant Draco Malfoy. McGonagall was clearly already dressed for bed.

"Professor, I{\el} do come in." Snape gestured to a chair next to his desk. "Sit down, please. Has Malfoy been causing you trouble?"

"This young man has been wandering the corridors, in the middle of the night, up on the top floor near the Astronomy Tower. And he has tried to fob me off with a story about Gryffindor students and a dragon."

"But it's true, Professor. They're getting rid of it{\el}"

"That will do, Malfoy. We haven't gotten to you yet. Now, Professor McGonagall, you apprehended Malfoy on the seventh floor near the Tower?"

"Not ten minutes ago. I've deducted twenty points from Slytherin for his offense and cheek."

Snape was taken aback by the severity of the penalty, but could not argue about another teacher's authority in front of a student. "Now what have you to say for yourself, Malfoy?"

"They've got a dragon. Hagrid got it over Easter break and it hatched, but it keeps getting bigger so they have to send it away before it burns his hut down and someone's coming tonight to take it from the Astronomy Tower. You've got to catch them."

"You see, Professor Snape. It's a concoction of lies. Where would Hagrid get a dragon? He didn't leave Hogwarts the entire break. And how could no one notice a dragon down there since Easter? And you cannot just fly in and out of Hogwarts. We have shields, defenses, that would have to be turned off{\el}"

"But I saw it! I saw it with my own eyes! In Hagrid's hut!"

Snape shook his head. "First, Malfoy, nothing gives you the right to be out in the corridors after curfew. If you thought something untoward was happening, you should have come to me or another teacher. Second, you may not talk to a teacher in a disrespectful way, and you must apologize to Professor McGonagall. And then you must go directly to the dormitories and go to bed. Your housemates won't be happy to learn tomorrow that you've lost them twenty badly needed points."

A resentful Malfoy apologized and left. Then Snape turned to McGonagall. "Twenty points, Minerva? Isn't that a bit steep? We dole them out in ones and fives and tens. To lose twenty at a shot{\el}"

"I'm sorry, Severus, but I've said what I've said. To be out and about, and then that ridiculous story, and his defiance{\el} twenty points."

Snape escorted McGonagall back to the entrance hall, where Slytherin's emeralds had already been removed from the hourglass. "I certainly hope the rest of your night is peaceful, Minerva. I'm just glad I'm not on duty tonight."

But McGonagall was to have no rest. At that moment, Filch appeared on one of the staircases. "Professors," he called, "there's students out of bed."

"We know, Filch," Snape called back. "One of mine. We've already got him."

"Not him, Professor Snape. Them. And they ain't yours. They're Professor McGonagall's. I've got 'em in your office right now, ma'am."

McGonagall turned scarlet, but whether with rage or shame was hard to tell. A brisk "Good night, Professor," and she was hurrying up the stairs after Filch.

\emph{I wouldn't want to be those students for all the tea in China. Not tonight. Not after what just happened with Malfoy.}

The next morning on his way to breakfast, Snape saw a crowd of students looking at the hourglasses. \emph{Rejoicing at Slytherin's loss, probably}. He started to move past them, then saw the points and stopped dead. Slytherin was once more in first place. Gryffindor was last. Gryffindor had, overnight, lost one hundred fifty points.

Snape went quickly into the Hall where a stony McGonagall was already eating breakfast. He slipped behind her and crouched down so his presence wasn't obvious. "Minerva, a hundred and fifty?"

"There were three of them. Fifty each." McGonagall turned to face him. "Severus, how could I punish your house yesterday, then not punish my own for a worse offense? They were actually up in the Tower. Malfoy was only in the corridor."

"Who was it?"

"Potter, Granger, and Longbottom. And Longbottom had the same silly story about a dragon."

Just then a great bulk moved in behind Snape. "Ya ought not t' be down there, Professor. I mighta stepped on ya."

Snape rose and started towards his own seat, but Hagrid touched his elbow and pulled up an extra chair. "T' tell the truth, I'd not mind having a chat with ya. Somewhat's come up."

"Love to be of help, but why me?"

"It's a dark sorta thing, needing a darkish sorta viewpoint, no offense meant."

"None taken, Hagrid, but Quirrell is the Defense against{\el}"

"Pshaw! Quirrell don't know his behind{\el} Begging yer pardon, ma'am{\el} But Quirrell don't know half what you knew at thirteen."

Realizing this might take time, Snape started putting eggs and sausages on a plate. "I'm all ears, Hagrid. I only hope I can help. With whatever it is."

"There's a unicorn died in the forest this last Wednesday." As both Professors turned horrified faces to him, Hagrid continued. "I don't know how it happened, but it'd been bleeding from the neck."

"Have you spoken to Kettleburn?" Snape asked.

"This ain't a matter of care, Professor. It's a matter of killing. I think something was drinking the blood."

"Adult or juvenile?"

"Adult male."

"There's nothing that preys on adult unicorns. It has to be human."

"I knew ya'd have the answer right at y'r fingertips. But who'd it be?"

"I don't know. But I've been worried about there being someone{\el} unusual{\el} on the grounds for some months. Nothing solid, just strange coincidences. What will you do now?"

"Wait. See if it happens again. Go looking for who did it."

"Professor McGonagall has a foursome looking at detention if you need eyes and ears."

Hagrid brightened as McGonagall added, "And a fairly intelligent group they are, too. They might actually be useful."

Two days later Hagrid reported another wounded unicorn, and Malfoy, together with the three Gryffindors, was sent out to help him find the beast and help it if possible. The following morning at breakfast, Snape noticed that Potter, Granger, and Longbottom were acting as if he'd transformed into a devil with hooves, horns, and a pointed tail.

"Hagrid, what happened last night? Did you find the injured unicorn?"

"We did, sir, but it were already dead. Something were slithering around it, no offense intended, an' it even drew the centaurs out. One of them was talking t' Potter, but I don't have particulars."

"Well if it's just centaur talk, there's nothing to it. Still, it would be nice if they stopped looking at me like I was going to roast them over coals." But what could have been `slithering' around the unicorn? Snape was suddenly reminded of Quirrell's snake of the year before.

\sbreak

It was testing week, and no one had anything to think about but exams. Preparing them, taking them, proctoring them. And for the Professors, another week of grading them. At the very end of the last exam, Snape watched the students stream out of his room, locked the exam papers in his office, and headed out toward the entrance. After so many hours cooped up, he wanted a bit of sunshine and a little stroll.

As he crossed the entrance hall, Snape heard, among the babble of voices, a student say his name. Not sure if someone wished to speak to him, he paused, and then realized the sound came from the three Gryffindors in front of him: Potter, Granger, and Weasley. He moved toward them and caught something about the Ministry of Magic, and Dumbledore turning up. Then the Granger girl saw him and gasped. \emph{What are they plotting that my presence startles her like that?}

"Good afternoon," Snape said. \emph{There's that look again, as if I was going to turn them into{\el} something unnatural.} "You shouldn't be inside on a day like this."

"We were{\el}" the Potter boy began, but hesitated. \emph{What does he feel guilty about?}

"Hanging around like this, people will think you're up to something. And Gryffindor really can't afford to lose any more points, can it?" The boy flushed, but his face was still defiant, James's face. Then suddenly Snape thought about McGonagall, and the distress this obstinate child had caused her. "Be warned, Potter -" he said quietly, "any more nighttime wanderings and I will personally make sure you are expelled. Good day to you."

Without another word, Snape turned and left, no longer going outside, but heading to the staff room to find McGonagall.

They were all in the staff room when Snape entered, McGonagall, Sprout, Flitwick, and Quirrell.

"Thank goodness you're here, Severus," McGonagall said as he entered. "Something's happened. They know about the Stone."

"Who knows about the Stone?" Snape tried to act surprised in front of Quirrell, not wanting Quirrell to suspect he'd already talked to Dumbledore.

"The Three Musketeers. Potter, Granger, and Weasley. They were looking for Professor Dumbledore to tell him that they think someone will try to steal the Stone tonight. But Dumbledore's been called to London."

\emph{The Ministry of Magic. The students knew that, too}. He glanced at Quirrell, who didn't meet his eyes. \emph{Maybe they're right about stealing the Stone. Maybe it is tonight}. "They volunteered this information?"

"They practically screamed it at me in the entrance hall."

"How many other people heard them, then?"

"It was just before the last classes let out. No one else was there."

"Is it possible someone will try to get the Stone?" Sprout asked.

McGonagall thought for a moment. "It is a strange coincidence that they would think someone would on precisely the day Dumbledore leaves for London. He won't be back until tomorrow."

"The students aren't going after it, else they wouldn't have run looking for teachers," Snape said. "If anyone is going to try, it would probably be tonight when the corridors are empty."

Flitwick spoke up. "My office is on the third floor, too. I shall watch the door for the rest of the afternoon and early evening."

"You need more time for your own work," said McGonagall. "I'll watch until after you have supper, then you watch this evening until curfew. Professor Sprout, if you would take the middle watch, then Professor Snape, you can watch from two to morning."

"What about me?" asked Quirrell.

"You have patrol duty tonight. If we change the routine, whoever it is might get suspicious. You just keep to your rounds."

Snape made no effort to hide his satisfaction at McGonagall's plans. He smiled sweetly at Quirrell as McGonagall left the staff room, then turned and walked out himself.

The Granger girl was standing there, looking nervous. "Is there something you need, Miss Granger?" Snape asked.

"I was waiting to see Professor Flitwick," she stammered. "I wanted to ask him about my exam."

"Professor Flitwick is right here. Let me get him for you." Snape went back into the staff room to tell Flitwick a student was outside, then left for his own rooms. He had the distinct impression, however, that Granger would rather have followed him than talk to her Charms teacher.

\sbreak

Snape couldn't sleep. He had the ominous feeling that the children were right, that tonight Quirrell would try to take the Stone. As midnight crept nearer, he decided not to wait for the beginning of his own shift, but to go up and keep Sprout company.

When he got there, the door to the dog's chamber was open and Sprout was nowhere in sight. The moon was just two days from full, and its light flooded most of the corridor. A quick search, and Snape found Sprout on the landing of the stairs leading down to the first floor. She was sound asleep.

"Pomona? Pomona, are you all right?" It was clearly an enchantment, and Snape spoke a quick waking spell. As Sprout blinked and sneezed, he asked, "Who attacked you?"

"I don't know," she replied. "What am I doing here?"

"Someone's after the Stone and knocked you out." He helped her to her feet and made sure she was steady. "You get Flitwick. I'm going downstairs after McGonagall. Don't go in until we join you. It could be dangerous."

Leaving Sprout to wake Flitwick, Snape ran down to the first floor and banged on McGonagall's door. "It's happening," he said when she opened the door, and together they hurried back upstairs.

Flitwick and Sprout were waiting. The four teachers edged near the door of Fluffy's chamber, and Snape felt a momentary twinge in his leg. \emph{How do we get past the dog? Why didn't we bring Hagrid into this?}

Fluffy was growling at them, and the trapdoor under him was open, but there were three things in the chamber that weren't supposed to be there. A small harp, a rudely carved wooden flute, and an invisibility cloak.

The rush of anger that swept through Snape on seeing the cloak was almost uncontrollable, and he fought it down with an effort. James Potter's cloak. The cloak that helped change Snape's life irrevocably nearly twenty years before. Snape turned to McGonagall. "Your Three Musketeers are already here," he said, pointing to the cloak, and knew there was a note of bitterness in his own voice.

"Music must calm the beast," said Flitwick. He picked up the flute and muttered a charm. The little instrument began playing a soft, haunting tune, and Fluffy yawned and dropped his heads onto his paws.

"Now," Sprout said, "we can jump down. There's a Devil's Snare there. It'll cushion our fall, then I'll immobilize it. I'd best go first." She stepped to the trap door and jumped. The other three teachers followed her.

Each chamber was under the control of the teacher who'd created it. Sprout got them past the Devil's Snare with no problem. Flitwick didn't need the key to open the door on the other side of his charmed room. The four teachers advanced into the shadowy chess room. There in front of them was the Granger girl, kneeling on the chessboard, trying to revive the Weasley boy, who appeared to be unconscious.

"Hermione! Ronald!" cried McGonagall, "What happened here?"

"Oh, Professor McGonagall, thank goodness you're here. Ron sacrificed himself to win the game so Harry and I could go through and stop{\el}" That was when Granger looked beyond McGonagall at the three other teachers and saw Snape. "You're not{\el} you're supposed to be{\el}"

"Pomona, stay here and see what you can do for Weasley," ordered McGonagall. "The rest of us need to find Potter."

Leaving Professor Sprout with the children, McGonagall, Snape, and Flitwick hurried into the next chamber. An unconscious troll lay sprawled on the floor, and the door to the other side was easy to open. The next to last chamber was Snape's. \emph{I wonder which child solved the puzzle. Probably Granger. Must be the muggle blood in her. No wizard brat could do it.} Snape opened the door, and they ran through, McGonagall in the lead.

There, kneeling beside the unconscious Potter, was Professor Dumbledore. "Ah," he said as the three teachers burst in, "there you are. And just in time, too. Even if I had not gotten here, you would have been able to stop him. He has just left."

"Who{\el}" McGonagall started to say, then looked with the others past Dumbledore. Quirrell was lying on the floor in front of a tall mirror, his face and hands covered with third-degree burns, and blood seeping from the back of his head onto the stones beneath him. The cloth of the turban lay tossed to one side.

"Lord Voldemort," answered Dumbledore, and Snape winced as pain shot from the mark on his arm up into his shoulder. "It seems that Voldemort was inhabiting Quirrell's head all year, and has been trying to get his hands on the Stone since last August. He discovered how to get past Fluffy around Easter, and has been awaiting an opportune moment ever since. Can you help me get this young man to hospital?"

The others attended to Potter, but Snape walked over to Quirrell, who was still moaning softly and obviously dying. Snape knew what it was like to have the Dark Lord probe his mind—it was one of the worst experiences of his life—yet the horror of what Quirrell had lived through was something Snape could only guess at. To have the Dark Lord share every moment of every day, know every thought, control every action{\el}

Snape knelt and lifted Quirrell to a sitting position cradled against his left arm, and began a low chanted healing spell to ease the pain of the burns. Quirrell opened his eyes.

"Severus, is that you? I need to{\el} I don't{\el}"

"Shh, Quirinus, it's all right. He's gone. You're free."

Quirrell shuddered and sighed, turning his face into the fabric of Snape's robe. "He suspects," he whispered. "You must be careful." There was a catch in his voice, and he seemed to gag.

"I will," Snape assured him and resumed his chant.

Gradually Quirrell relaxed, the pain fading from his eyes. A moment later, at the end, he sighed again and died in Snape's arms.

Dumbledore came and knelt with them, laying a hand on Snape's shoulder. The fear that had slept for over ten years was awake and growing once more. Snape looked into Dumbledore's eyes. "What do we do now?" he asked.

\sbreak

"So, the spell caster was Quirrell all along. Or rather, him—the Dark Lord—through Quirrell. No wonder he was so strong. And the mysterious prowler in the library was{\el}?" Snape watched Dumbledore across the desk in the Headmaster's office.

"Young Potter in his father's cloak. Somehow I did not think it would do you any good to know that he had it. I caught him out after hours, and he stopped using it. Until it was truly needed."

"And the Dark Lord, through Quirrell, killed the unicorns. When did you know it was him?"

"I suspected that first day, when you told me that Potter's scar was hurting. You have no idea how disturbed I was to find that you might have been dueling your former master over the curse on Potter's broom. I do not want to lose you, Severus, and the thought of what Volde-{\el} I am sorry. I must remember to be careful around you{\el}—he could do if you got directly in his way was not something I wanted to take a chance on."

"So you came to the Quidditch match. You might have told me. He tried to read my mind once. You might have warned me."

"Why? He clearly did not want you to know he was there. Otherwise he would have contacted you. I trust your instincts. I cannot read you. He could not read you even when you wanted him to. I was not too worried about that."

"You weren't worried? For a year he shared all Quirrell's experiences, had access to all Quirrell's memories. Every time Quirrell turned his back on me, he was watching me. Do you know that I've been trying to remember every conversation I ever had with Quirrell, trying to figure out what he knows about me? He's not gone. He's coming back."

"And you are here with me."

Snape rubbed his left arm. "He can summon me. He can punish me. Nowhere is safe."

"We shall deal with it when we come to it. By the way, Quirrell told Potter that you had been trying to help him. Potter could not understand why, so I told him that James had saved your life."

"You{\el}! That's none of his business! That's my private life. You promised!"

"I tend to think it is his business. It was his father. Besides, it seemed the least personal of all the reasons I might have given him. I shall try to keep you out of it as much as I can, but you are part of his family history."

There was little that Snape could say to this. A few minutes later he left Dumbledore's office.

McGonagall caught Snape on the stairs. "I thought maybe I would congratulate you now, since we won't be sitting together at the feast tonight. The Quidditch Cup and the House Cup seven years in a row. I think that's some kind of record."

"It was a record last year, Minerva, and you know it. Still, if you'd punished your students the same as Malfoy, instead of going overboard like that, you'd be in third place now instead of fourth."

"And if I hadn't punished them at all, we'd be in second place. You have a well-oiled machine there, Professor."

There was also one last interview with Malfoy.

"You've done well with the lesson I gave you. It seems you do understand something about the propagation of sound. Now I have a summer assignment for you."

"Homework? You're giving me summer homework?"

"Your enthusiasm seems to have waned. If you don't want to do it{\el}"

"No, I'll do it. What do I have to do?"

"Design a spell that will permit you to talk unheard in a crowded room. Use the information about sound, and see what you can come up with."

"That sounds really useful. Is it one you've already done?"

"It is. And your father knows it too, because I invented it for him and your mother. I shall find out if you learn about it from him."

"I'll get it done for you. I'll work on it all summer. You won't be disappointed."

\emph{We'll see about that, Draco. We'll see if the passion is really yours, or if it's just Lucius living through you.}

The Great Hall was resplendent that evening with green and silver, and a banner with the Slytherin serpent was displayed behind the high table. The Hall was already crowded when Snape entered and made his way to his seat. He tried to conjure up the same feeling of pride in his house that he'd felt in previous years, but somehow this year was not joyful.

First and foremost was the dread that lodged permanently in his heart knowing that the Dark Lord was back and had intimate knowledge of Snape's place at Hogwarts. He'd never released a former servant and never let a fault go unpunished. As long as his disembodied presence existed, there would be the danger of his return. When the Dark Lord returned, Snape knew that his own name would be at the top of the list for destruction.

The second reason was less in magnitude, but perhaps greater emotionally. For the first time, Snape truly saw the depth of resentment felt against him and against Slytherin for their long years of winning, and realized that the students of other houses, even some of the staff, suspected him of favoring his own house to keep it on top. Snape had no way to defend himself against the rumor, and he understood that every victory in the future would be a hollow one.

It was odd sitting at the end of the table without Quirrell beside him. No one moved to take Quirrell's place, though whether out of respect for the dead or to isolate Snape was anybody's guess.

Everyone, absolutely everyone, was in the Hall when the Potter boy appeared at the door. \emph{Did he do that on purpose? It would be so like his father to stage his entrance for maximum effect.} Students in the Hall were climbing onto benches to see him better as he made his way to the Gryffindor table to sit with Granger and Weasley.

Then Dumbledore arrived, and the Hall settled down to listen to his end-of-year speech. It was the usual stuff. When he reached the announcement of points for the House Cup, the Slytherin table erupted in cheers, but Snape was more sensitive than ever before to the silence of the rest of the Hall.

"Yes, yes, well done, Slytherin. However, recent events must be taken into account."

Snape froze. The room became eerily quiet. \emph{What is he doing? He's never changed points at the feast before.}

As Snape listened in disbelief, Dumbledore began to hand out points. Fifty to the Weasley boy for beating McGonagall's chess game. Fifty to the Granger girl for getting past his own logic puzzle. And sixty to Harry Potter for his courage. Not one negative point for the rules they'd broken. Gryffindor and Slytherin were tied. The suspense in the Hall was palpable.

\emph{As long as you decided to take the Cup away from us anyway, you might have the kindness to do it quickly instead of dragging it out like this. I never suspected you of being sadistic before, but now{\el}}

Dumbledore was still talking. "There are all kinds of courage. It takes a great deal of bravery to stand up to our enemies, but just as much to stand up to our friends. I therefore award ten points to Mr.~Neville Longbottom."

The Hall exploded as everyone but Slytherin began to cheer. Snape clapped his hands mechanically for Gryffindor's victory, but he really wanted to sink right down through the floor in shame at the way Dumbledore had so publicly humiliated him and his house. \emph{You couldn't have done this before, so at least we wouldn't have come to the feast thinking we'd won.}

"Which means we need a little change of decoration."

Green and silver became scarlet and gold. The serpent vanished to be replaced by a lion. McGonagall was beaming. The Hall was wild with cheers. Snape rose and went to McGonagall to congratulate her on her victory, trying to smile as if he meant it. He glanced over at Potter. Never before had the boy looked so much like his father, cocky and self-centered as he celebrated the defeat of a rival.

Then, as Snape started back to his own seat, he too became a small center of attention. Kettleburn was first, coming to shake his hand. "Second place isn't so bad, Severus, but that's got to hurt, the way it was done."

Flitwick and Sprout hurried over, too. "Hard luck, Severus. Never thought Dumbledore would do something like that." And Sprout added, "You come sit with us, dear. To think of treating you that way in front of the whole school."

It was an invitation not to be refused. "Save me a place," Snape responded, then went down to talk to his house and cheer up the Slytherin students a bit before returning to the teachers.

And so, as McGonagall basked in the glow of Gryffindor's triumph, Snape found that the ill feelings against Slytherin had vanished into sympathy and good will. While still less than perfect, it was at least a partly satisfactory end to a most unusual year, and Snape settled back to enjoy the feast with his colleagues, putting aside for tomorrow the troubles that tomorrow would bring.

\sbreak

17


