% A Difference in the Family: The Snape Chronicles (Rannaro)
% After Hogwarts

\chapter{The Death Eater}

\subsection{Wednesday, July 19, 1978 (the day before the full moon)}

Severus apparated directly into the Black residence, per Bella's instructions. She met him in the grand entry and escorted him to his room. It was not only not a servant's room, it was more sumptuous than the last one he'd been in. "The guest of honor gets the best room," Bella said, smiling.

That evening there was an `informal' dinner with only twenty guests. Rabastan and Roldophus were there, along with Avery, Mulciber, Rosier, Wilkes, and Lucius sitting happily next to Narcissa. All but Lucius were joining Bella in sponsoring Severus, and Severus expressed his surprise that Rosier and Wilkes had already become Death Eaters while still students at Hogwarts.

"Like you can't get away with murder in that school," was Wilkes's comment on the observation, which won him a laugh and a general cheer.

They coached Severus on what would happen, how he would apparate with Bella, blindfolded, into the dark room at headquarters, kneel and be interviewed, and then receive the first, novice Dark Mark. "Did it hurt?" he asked as he studied Rosier's tattoo, a small green skull with a snake issuing from its mouth.

"I asked the same question," said Wilkes, "everybody does. Yeah, it hurt. It burned. But then it goes away."

"You have to remember to let the Dark Lord see your whole mind," added Bella. "That part feels funny. It doesn't hurt, it just feels funny."

Severus went to bed just a little tipsy because Mrs.~Black kept giving him more sherry.

\subsection{Thursday, July 20, 1978 (the full moon)}

They assembled in the grand entry at noon the next day, dressed in formal robes, Severus looking very young and slender in his straight, modestly cut green and black, and his tall, peaked wizard's hat. Bella stood in front of him, a delicate gold cord in her hands.

"Cross your wrists in front of you." Severus obeyed, and Bella used the cord to bind his hands loosely together. "It's very easy to get out of, but try not to even if you're scared. It tests how calm you are, how much you trust the Dark Lord, and how willing you are to obey him. Understand?"

Severus nodded, and Bella took the wizard's hat off his head. She showed him the black hood he would wear. "You can't know where we're going, and you're not allowed to see anything until you look the Dark Lord in the eyes. We'll guide you and tell you what you have to do and when to do it. You just trust us. Now from this point on, you don't talk. You don't question. You just do what we say, and you don't say anything. Okay?"

Severus nodded again, and Bella slipped the hood over his head, then replaced his hat. Then she stood next to him and slipped her arm through his. "Everybody ready?" There was the sudden, tight pressure of apparation, and they were standing in a different room, one that was cold and muted, as if the walls absorbed all sound.

"Just walk with me," Bella whispered, steering Severus down an inclined floor. His shoulder brushed something, a doorway, then they were in a room that sounded larger. "Kneel," came Bella's quiet command. Severus knelt, and the hood was removed from his head.

The room was dark and shadowed. One thin, weak beam of light illuminated the spot between Severus and a standing figure robed in black. In a moment bordering on panic, Severus searched his own mind, checking if everything was open, unlocked, on display—this man would know. Then the figure in front of him lowered its own hood, and Severus was staring into the eyes of the Dark Lord. Severus heard and felt nothing, but he knew that questions were being asked.

His own answers were memories rushing to the surface of his mind: Toby drunk—Toby hitting Eileen—Toby lying on the stairs and his own wand in his hand—nights in a vacant church—Nana—the burned cottage—the doctor, police, pastor who wouldn't help—Dumbledore restraining his anger and his vengeance{\el}

Dumbledore saying `maternal vampire'—Hagrid holding him off the ground as he attacked the headmaster—Slughorn's scorn—the camaraderie of the Slytherin common room—Bella—Rabastan—Mulciber—tutoring—Regulus—Christmas with the Blacks{\el}

Sirius—slugs—James saying Scourgify—a fist hitting the pit of his stomach—Regulus yelling, \emph{Give me a reason}—Bella yelling, \emph{Touch him again, Potter}{\el}

Severus had no idea how long the session lasted, only that the rush of images and feelings was swamping him, drowning him, like water released from a floodgate.

\emph{What do you bring me?} a voice asked in his head as the memories rushed to a close. \emph{All I have and all I am are yours.} Severus's own mind responded.

And then it was over.

Above him a voice was speaking, a voice unlike any he'd ever heard, full of spectral power, resonating with authority. "This one has come to us like an innocent child to his father, open and trusting and obedient. Freely has he shown us the deepest recesses of his soul, and he has held nothing back. Greet him now as one of our family. Come forward, Death Eaters, and embrace your new brother, Severus Snape."

The group of Death Eaters helped Severus rise and untied his wrists. Bella threw her arms around him and hugged him. The others were shaking his hand and patting him on the back. The Dark Lord himself was aloof from this display of welcome, his hood once again shielding his face in shadow. Severus realized that he had no clear picture in his mind of what the Dark Lord looked like, and immediately accepted that maybe he was not supposed to know.

The final step was the tattoo, the brand. The Dark Lord stood now next to a brazier that flamed a ghastly green light. Metal rods tipped with tiny stars lay in the fire. Once again Severus knelt before his new Lord, and this time Rabastan and Mulciber knelt with him to support him. They strapped his left arm to a small table to keep it steady as one by one the Dark Lord seared the tiny stars into his skin to form the small, unbroken outline of skull and serpent. The pain was intense, but bearable. The Dark Lord then traced the lines of the mark with a long fingernail, and it seemed to glow.

"It is done," the spectral voice intoned. "united into one body until death. Take him now and celebrate his coming into our family. Teach him what he must know. And when the time comes for his work to begin, I will send for him." And the Dark Lord was gone.

"When you stand up," Bella said as they unstrapped Severus's arm, "lean on me. You'll be dizzy and feel a little sick. It's normal."

The group, now relaxed and beginning to chat, went out the door and up to the first chamber. Holding the wobbly Severus steady, they apparated back to the Black residence.

It was mid afternoon, but the house was full of people. Many of them were people Severus had met either at the Black's house, at the ballet, or seen arriving in their limousines years ago. As the group apparated in, the guests began to applaud, and a band struck up `For he's a jolly good fellow.' Cygnus Black was the first to shake Severus's hand, and then he was surrounded by well-wishers.

"Party time!" called Rodolphus. "Somebody get me a drink!" and the celebration was under way.

"Does everyone get welcomed like this?" Severus asked Bella as soon as he could escape the press.

"I don't know. We don't know everyone. The Dark Lord has several groups of Death Eaters, and we're kept separate so that we can't be forced to betray each other by spells or Veritaserum. We all know each other here because we've sponsored each other. Some of these people aren't Death Eaters, just people who support us and the work we're doing."

The party lasted all night. There was music and conversation, and a twelve-course dinner followed by dancing in the ballroom, and cards and billiards in the other rooms. The former Hogwarts students (with Regulus, of course, who was also there) ended up in one of the smaller drawing rooms, one with its own bar, where Avery showed them how to mix exotic drinks like Black Russians and Harvey Wallbangers. That was when Severus found out that Avery could almost juggle six table knives at once, and Rodolphus knew how to dance the can-can.

As dawn began to tinge the sky, the party broke up. The guests departed, the family retired to their rooms, and Severus, feeling very contented, went to his own room and slipped, deliciously tired, into bed.

That was when it hit him, and Severus sat bolt upright in bed, wide awake.

He hadn't shown Lily to the Dark Lord. In all that stream of memories, all that river of feelings, emotions, and recollections, there hadn't been one image of Lily. \emph{Impossible. I must be mistaken. Maybe I just didn't notice everything.}

Yet every image that had been pulled from his mind was as sharp and clear as if he'd lived it yesterday. Hundreds of images, large events and small. Severus began to review them, looking not for what was there, but for what wasn't there.

Nothing about Lily. Nothing about Gra or Wensley Snape. Nothing about Apollo, or Skylab, or Voyager. Nothing about Hagrid's examinations or Dumbledore's advice on Occlumency. Nothing about an encounter with a werewolf. Nothing about Narcissa.

Severus was frightened. He'd gone to the initiation honest and open, as honest and open as he could, and his own mind had filtered his thoughts without any action from his will. \emph{I'll go to him. I'll confess to him and show him everything. Maybe he won't be angry with me.}

But there was a saner part of him that rose in self-defense. \emph{What will he do to me if I tell him that I can hide things from him? That when he looks at me he can never be sure of seeing my thoughts? Can he even afford to have that known? He'll punish me.}

And the quietest, gentlest part replied. \emph{That's right. Besides, I don't think I want him to know about Lily.}

Nobody in the Black household woke up the next day until well after noon. A quick, simple luncheon, a renewal of congratulations, and by mid afternoon Severus apparated back to Lancashire. The entire London trip would've seemed like a dream were it not for the sting of the novice grade Dark Mark on his left arm.

Severus finished the interior work on the house. The shrunken sitting room lined with bookcases was like a little cave, a real den, his own personal reading room. The stairs going up were behind a set of shelves. He kept the little bedroom as his own, needing no more space, and the back storage area was now a potions workshop. It did have a white lab coat, but Severus never put it on.

Bella's owl came in the middle of August, and Severus apparated immediately to London. They left the Black house for a short walk.

"I'm going to show you a piece of paper. It has an address on it. Once you see the address, you'll know it, but you won't ever be able to write or say it because of a secrecy spell. It's the entrance to our headquarters here in London. Understand?"

Severus nodded, and she handed him the paper. Almost as soon as he glanced at it, it shriveled up and disappeared. "Why did you have to do that? Why not just take me there?"

"Silly, I can't take you there until you know the address. That's the same as saying or writing. The only one who can tell a new person where it is, is the one who wrote that note. Now, when we go there you'll get your first assignments. You won't see the Dark Lord. Only the higher-ups see him. But you might hear him. Or you might not."

"Are you one of the higher-ups?"

Bella looked smug. "He appreciates my enthusiasm for the work."

The outside of the house looked perfectly normal, but inside was the entrance to a labyrinth of underground passages. Bella knew her way. Severus quickly became lost. They reached a small room with a little pedestal in the center. On the pedestal was a parchment.

"Pick it up," said Bella. "You're the only one who can. That's your job."

It was actually several jobs, mostly in London. Severus was supposed to stay in Diagon Alley all of the last half of August, meeting Hogwarts students he knew from tutoring and talking to likely prospects about joining the Death Eaters. He was also to shop for books and artifacts in Diagon and Knockturn Alleys, and anywhere else in Britain for that matter, looking especially for long-forgotten ways to hide things, keep them secret, and protect them from discovery or theft.

Along with the parchment were two small bags, both holding a considerable amount of money, both wizard and muggle.

"Be sure you keep a record of all your expenses," advised Bella. "If you meet other students, and you buy the refreshments, that's okay, that's a legitimate expense. Don't use it just for yourself. though. He's touchy about that."

The assignment turned out to be quite pleasant. Severus got to meet and talk to students now in sixth and seventh year that he'd tutored the year before. He met new students as well, and was introduced to them as a fountain of knowledge about spells and charms. He even made appointments to get together with some students over the Christmas break for tutoring, accepting only those who'd be working to pass their NEWTs.

Browsing through the shops was enjoyable, too. For the first time he didn't have to worry about how much something cost, though he was careful not to buy anything unless he was sure it would be useful.

After September 1, Severus began to go outside London, searching not only through wizard shops, but also in muggle stores, antique shops, estate sales, and the like. Here his muggle background proved very useful since he was able to pass as a muggle anywhere he went, where a pureblood would have been spotted immediately.

By Christmas, the Dark Lord's catalog of spell books had grown immensely, as had the number of dark objects available to his workers. Severus had also managed to add to his own collection, though he was careful how he did so. He always paid for his own things with his own money, and he never took for himself anything that would be useful to the Dark Lord unless it was a duplicate of one the Dark Lord already had.

In all this time, Severus came into contact with none of the other Death Eaters except Bella, although he did hear of more and more attacks against witches and wizards all over Britain. The sense of being on the sidelines while others fought the real battles was galling to him. He had to keep telling himself that what he was doing was necessary, and helped the war effort as much as the true fighters did.

During Christmas he tutored Hogwarts students and found that he could get information from them that he passed on to Bella.

In January, as he turned nineteen, Severus got the message that his job was changing, and he went to headquarters in London for his new instructions.

An older wizard met Severus at the entrance to headquarters and escorted him to the assignments room. A new parchment lay on the pedestal.

% FIX THIS \emph
`You will work at headquarters and devise spells for our people,' it said. `There are three to start with.

1) A spell that will enable us to overhear conversations at a distance.

2) A spell that will enable us to walk unheard through dry leaves.

3) A spell that will keep dogs from noticing us.

If you encounter any difficulties with these spells, you will notify us immediately. The attendant will show you to a work area.'

The older wizard took him to an upper room with a window that looked out over roofs. There was a table and a chair, parchment, quills, and ink. "Tell me if you need anything," the old wizard said.

"Tea?" asked Severus, and it was brought immediately.

The first spell was no difficulty at all. Severus already had the Autiarachnon. It was mildly interesting to note that Lucius hadn't told anyone about it. The other two would be harder.

He could think of three ways to move through leaves, one of which was a levitation spell. That, of course, already existed, but was generally not used because it required so much power to sustain for any length of time. The next was to change the consistency of the leaves as you walked to make them soggy. Workable, but it would leave a trail. The third was to muffle the crackling of the leaves with a silencing spell. One that silenced only the leaves.

Severus went to the door and opened it. "I need to go out," he said.

"Why?" asked the wizard.

"Research on a new spell."

"I'll check."

Severus supposed they did have to be cautious around headquarters, but it felt odd not being able to come and go freely. He waited patiently inside the room.

"It's okay. You can go out. Report back before you go home this evening."

There was no snow in London, so Severus went to Hyde Park looking for dry leaves. \emph{How do you find the sound frequency of rustling leaves? There should be something like a sound meter that registers frequencies. Or maybe I could just use trial and error.}

The afternoon passed quickly. Severus made some progress with the leaf spell, but it would take a few days of refining. He went back to headquarters and was admitted by the same wizard.

"You have an interview. Follow me."

Severus was nervous, not knowing what the Dark Lord wanted to talk to him about. He followed the wizard to the same room as his initiation. The room was dark, lit only by the narrow beam of light. Severus stood in the center for a moment, then knelt as he'd done before.

"Do you have our spells?"

Warning bells were ringing in Severus's head. He was suddenly frightened This was not the time to try to hide anything.

"I have a listening spell. I made it months ago. I can give you that right away. The leaf spell will take a few days because I have to experiment with the sound waves. I don't think the dog spell will be possible."

"Not possible? Explain."

"Animals have certain instincts that make them immune to magic that disguises. If the dog is right in front of you, it'll know you're there. I think I can make something to alter scent and movement so that a dog at a distance won't notice you, but it won't work if it gets close."

"You have spoken truthfully. Write the listening spell before you leave. Bring the others as they are completed. Do not take too long."

"Yes, my Lord."

The Dark Lord was gone, but parchment and quill lay on a small table by the door. Severus quickly wrote down the Autiarachnon spell and left.

He had the leaf spell two days later, and the dog spell within the week.

The whole spring was spent working on spells and potions. Much of it involved the books and artifacts Severus had bought himself, and his labor seemed to be concentrated on hiding and disguising things.

Hiding and disguising was something of an obsession at headquarters. Severus almost never saw other wizards. Everyone who came or worked in the building was kept in his or her own cubicle except for the teams that went out on raids. Sometimes Severus saw people he knew, and they would exchange greetings, but they never talked for long.

At the beginning of April, Severus was asked to provide a potion that would protect someone from contracting dragon pox. He thought this a strange request, but had a vague recollection of the development of smallpox vaccine, and started researching reptilian viruses. It turned out that no one exposed to moke pox had ever contracted dragon pox. With the proper caveats, Severus suggested innoculation against moke pox.

Severus by now had become very familiar with the area around his own workroom, coming and going without an escort. He normally didn't pay any attention to what was happening in the other rooms, that being none of his business, but there is something special about hearing your own name. In a crowded room amid numerous conversations, you'll notice if someone speaks your name. In an empty corridor one afternoon in late April, Severus heard the word "Snape" and stopped to look around.

"We can't use him." Severus wasn't sure, but the voice behind the door sounded like Rosier.

"All he does is hang around headquarters all day. He never goes out on a raid. We need people."

"His work here is useful. Where would you be if we didn't have that dog spell yesterday? Don't say he doesn't do anything."

"But we need more people this time."

"Look. I'm only saying this once. He never, never comes on this kind of mission. You even tell him about it and I report you to the Dark Lord."

Severus left quickly. He wasn't sure what they were talking about, but if knowing it would anger the Dark Lord, he didn't want to know.

A few days later, the wizarding world was rocked with the news that Abraxas Malfoy had contracted, and quickly died of dragon pox.

Dangerous times make people more aware of the transience of our short lives. That spring and summer saw many young couples, who would normally have waited, rush into unions while there was still a chance for some happiness. It seemed as if there were two or three weddings every week. After an interval of only a month to mourn his father, Lucius Malfoy finally married Narcissa Black. Severus attended the ceremony, and was happy for their happiness.

In June, two weeks after the fact, Severus also heard that James Potter and Lily Evans had wed.

As the spring ended and summer progressed, it became clear that a new force had entered the battle to control the wizarding world. More and more, the Dark Lord's teams were running into opposition from an organized group of wizards and witches who seemed to be particularly well informed and well prepared to thwart their operations. More and more the signs pointed to the source and inspiration for this organization. It radiated out of Hogwarts and bore the stamp of Albus Dumbledore.

By August, the Dark Lord was in a continual foul temper about Dumbledore's new Order. That was when Regulus Black, not yet eighteen, was initiated into the Death Eaters. It was highly unusual for one so young, and rumors abounded of the Dark Lord's expectation of information through Regulus and his brother Sirius of Dumbledore and his plans. Severus, by now a full-fledged Death Eater, was one of many who sponsored Regulus, but he avoided the rumor mill. He'd already learned that it was best if one kept one's own council.

The new school year started, as it always did, on the first of September. In late October, Severus received a message to report to the assignments room for new orders. This time there was no parchment. Instead he was ordered to report to the Dark Lord himself for an interview. Severus went immediately, nervous but excited.

"You have taught your fellow students."

"Yes, my Lord. I began tutoring in Slytherin house in my second year."

"And every year from that time."

"Yes, my Lord."

"You organized them into classes."

"When there were too many to teach one on one, yes, I did."

"I wish you to become a teacher."

Severus opened his mouth to protest, then closed it in silence. He didn't want to teach, but it was not for him to say. "Who must I teach, Lord?"

"You will travel to Hogsmeade for an interview with Albus Dumbledore. You will convince Dumbledore to take you on as a member of the staff. Once you have established yourself in Dumbledore's confidence, you will transmit to me any information you can garner about the movements and whereabouts of Dumbledore and of this organization of his."

"The school year has already started. What if Dumbledore will not hire me?"

"You will have failed me."

"Yes, Lord."

That night Severus apparated home to Lancashire, and the following morning he went to Hogsmeade.

\subsection{Wednesday, October 31, 1979 (4 days before the full moon)}

Severus went first to the Three Broomsticks, there to sit at a table near a small leaded window and watch the passersby. He'd almost never visited Hogsmeade as a student, so none of the inhabitants recognized him, and as it was not a Hogsmeade weekend, there were no students who might recall their tutor. Severus was trying to decide how to proceed with the Dark Lord's instructions.

It would be so much easier if he'd even once expressed an interest in teaching during his years at Hogwarts. Then he could go to Dumbledore and say, `Do you remember{\el}' and they could at least have a normal conversation about it. Now he had to invent some excuse, some reason, for suddenly seeking a job.

\emph{Maybe I can tell him how bad things are in Lancashire, and how I desperately need the money because I haven't been able to find anything{\el} Dumbledore knows about my tutoring, doesn't he? I could point out that I have some experience{\el} I don't even know if they have an opening{\el} I'm going to look like such a fool{\el} It's too late in the year; he won't hire me and I'll fail on my first really big assignment.}

Around noon a frumpy looking woman entered the common room to inquire about lodgings, a strange lady with thick glasses and an absent manner. She seemed put off at the price, insisting that she had to have a place because she was expected. She had an appointment. She would have a position. The proprietress suggested the Hog's Head as a cheaper establishment, and the frumpy lady left.

\emph{So maybe Hogwarts is hiring. That's a good sign. And if she has an appointment, it might mean that Dumbledore will be here today. Better and better.}

In the middle of the afternoon it began to rain, and the weather became autumnly cold. Severus ordered supper and was beginning to eat when he spied Dumbledore walking down the street, turning, and then heading in the direction of the Hog's Head.

Severus quickly paid his tab and left the Three Broomsticks. At the head of the lane he was just in time to see Dumbledore enter the Hog's Head Inn. Severus didn't dare run, not wanting to attract attention, but he did walk very fast to the inn. There, through a dirty windowpane, he saw Dumbledore talking with the barman. Then the Headmaster left the bar and went up the stairs toward the rooms.

Severus slipped in. \emph{Should I wait for him in the bar? I could at least ask him for an appointment when he comes down.} Then he wondered what job the frumpy lady was applying for, and thought how much easier it would make his own task to know. The bartender was paying no attention, and Severus slipped soundlessly up the stairs after Dumbledore.

It wasn't hard to find them, for voices were coming from only one room. Severus crept closer, the narrow gap between door and jamb making listening all the easier.

"{\el}I am certain that my pedigree could not but impress you, for I am the great-great-{\el}"

"Yes, Madam Trelawney, but you must understand that we have not actually decided to continue the teaching of Divination{\el}"

"Oh, but you must teach Divination! The foreseeing of the future is so important a part of the education of every accomplished witch. And wizard, too, of course. I don't see{\el} don't see{\el} don't{\el}" Her voice became low and harsh, an unearthly voice that could never have issued from a mortal mouth:

\prophecy{The one with the power to vanquish the Dark Lord approaches{\el}}

\prophecy{Born to those who have thrice defied him, born as the seventh month dies{\el}}"

"Here! What are you doing here? Listening at keyholes?"

Severus turned to see the bartender standing behind him. "No," he said quickly, not fully able to disguise his surprise and embarrassment. "I was looking for someone who came up here. I have an appointment. I mean I want an appointment{\el}"

"You don't get an appointment by following people into private rooms. You wait downstairs 'til he comes down himself, 'stead of snooping."

"I wasn't snooping. I was{\el}"

"You were eavesdropping. I don't hold with people spying on the guests."

"No, not spying. I just wanted to see him."

"See me?" The door opened, and Dumbledore stood before them, his head cocked quizzically to one side. "Did you wish to see me, Mr.~Snape?"

"You know this bird, Albus?"

"Oh, yes. Former student. What did you wish to see me about, Mr.~Snape."

Severus shifted nervously. "I wanted to talk to about the possibility of a job. Things aren't going too well, and I could use{\el}"

"Oh, but I have no jobs, Mr.~Snape. There was one, but I have just hired the person to fill it."

And there was nothing for it but for Severus to return to London and admit to the Dark Lord that he had failed.

"How much do you think he heard?" Dumbledore asked the bartender, who happened to be his brother Aberforth.

"Ha! Now why didn't you ask him that yourself, you great legilimens, you? What's the use of having all that natural ability you always bragged about if you can't use it when you need it?"

"I never bragged! And besides, I can't read this one. He's a natural. A born occlumens."

"I thought you said they didn't exist."

"This one does. I can't explain him otherwise. The Sorting Hat put him into Slytherin. Can you guess why? Because it couldn't read him either. It decided anyone that secretive had to go to Slytherin. I wonder though if things mightn't have been different if he'd been in Ravenclaw. I always saw him as a Ravenclaw. Now, how much did he hear?"

"Not a lot. He wasn't there very long. And I stopped him about a minute and a half, near two minutes before you came out."

"That's good. So even if he heard something, he couldn't have heard everything."

"I still think you should've hauled him up to the castle and put thumbscrews to him."

"I like to take the long view, Aberforth. We may yet need him, and it's easier if he still has reason to trust us."

The interview with the Dark Lord did not start well.

"You have returned early. You do not come with favorable news."

"No, Lord. I've failed."

"You do not come with excuses. Your punishment will be abated because of this."

Pain hit Severus with the force of a sledgehammer, and he fell to the floor writhing and screaming in agony. Pain struck at head, gut, and back, and then it was gone. He lay on the floor of the interview chamber gasping for breath.

"Now you will tell us what mistakes you made."

"I followed him too closely. I eavesdropped on a conversation with another applicant. A seer. She went into a trance{\el}"

"You heard a prophecy. Who was this seer?"

Severus shifted his body so that he was on his knees again. "She claimed to be the great-great-granddaughter of Cassandra Trelawney. It seemed that Dumbledore wasn't interested in her until she went into a trance and started prophesying."

"This was not a hoax."

"I don't think so. Her voice changed, harsh and low. I don't think she could have faked it."

"What did she say?"

"The one with the power to vanquish the Dark Lord approaches{\el} Born to those who have thrice defied him, born as the seventh month dies{\el} Then I was interrupted and I didn't hear the end."

"Did Dumbledore question you?"

"A little. The bartender confirmed that he interrupted what I could have heard. I don't think he realizes I heard any of the prophecy."

"This is interesting. By great fortune you have redeemed your error and brought us a gift of some use. For this reason we will not punish you further. You will return to your duties."

"Yes, Lord. Thank you, Lord."

Severus went back to his workroom deeply grateful to the Dark Lord for his understanding and mercy. \emph{I failed him. I deserve so much worse, but he saw my intentions; he accepted what I was able to give. He is so much better to me than I deserve.}

Severus continued his work with a renewed sense of dedication and purpose.

Autumn advanced, and Severus continued his work with spells and potions. The Dark Lord forbade him to mention the prophecy to anyone else, though that was scarcely a problem since Severus saw and spoke to so few people in the course of a day, and then only briefly. Life was so different from Hogwarts, when it seemed he never had enough time. Now the focus of his whole life was the assignments he received from the Dark Lord.

Midway through November a well-known witch, Marlene McKinnon and all her family were killed. Initial shock quickly transformed into enthusiasm as word filtered through the ranks that McKinnon was a member of the shadow organization that surrounded Dumbledore, and the enemy were no longer immune. The Death Eaters had a new source of information, and things were going to turn around. Optimism spread through headquarters. People spoke of the future with confidence.

Severus was called before the Dark Lord at the beginning of December. "Bring your wand," was the only instruction the messenger gave.

Instead of the usual interview room, Severus was conducted to a larger hall. Rabastan Lestrange stood at the entrance, more worried than Severus had ever seen him. "I'm sorry," he said as he shook Severus's hand. "I didn't foresee this. Just remember, you whipped two of us when you were twelve."

It was not a comforting thing to hear, but Severus had no time to ponder it as he was ushered into what was clearly a small arena a little like a bull ring, with stands around it for a small group of observers. Unbidden, his brain began to lock down, to close off, and his senses sharpened in the presence of danger. Across the arena was a large, lumpy, brutal-looking wizard that Severus knew as Amycus Carrow.

The voice of the Dark Lord spoke softly in the silence. "You are being tested. The winner will be high in my favor. The loser, if he survives, will not. There are no rules."

Shock and surprise paralyzed Severus for a second, but Carrow grasped the meaning of the last sentence immediately, hurling an Stupify at Severus, who dove to one side in a defensive roll as he managed to conjure up a nonverbal Protego. Carrow's defensive strategy was to attack, and he unleashed a steady stream of striking and cutting spells, shouting wildly as Severus retreated backwards in silence around the circumference of the arena, barely managing to parry each blow as it came, with no time to consider how to counterattack, struggling to remain focused. Reading Carrow turned out to be nearly useless, since the spells varied little and never paused. It was his first duel against an adult wizard with battle experience, one who was trying to kill him. He remembered his father and Nel Tarleton.

The trick was not to waste time on spells for defense, but rather to use his physical ability to avoid the spells and his wand to attack. It didn't matter if Carrow got off three spells to each of his as long as the three spells missed and his struck home. His biggest handicap was that he had no intention of seriously hurting Carrow, much less killing him.

He spun counterclockwise to avoid another cutting spell and Carrow, not expecting the move, faltered. Severus hit him with a finely tuned Sectumsempra that nicked Carrow's right ear and drew blood. Carrow, bellowing in rage, responded with a blasting spell that Severus escaped by once again diving and rolling. From the ground, he hit Carrow with an Expelliarmus that sent the older wizard's wand against the stands. As Carrow grabbed for his wand, Severus sprang to his feet and scurried behind Carrow's back to the left, using the extra second of time to transmit a Doppelganger to Carrow's right. Carrow lashed out at the ghostly image, then wheeled around, his wand spitting fire as Severus again dove in the opposite direction, sending a leg-binding curse under the other wizard's spell. Carrow lost his balance, fell over like a log, and the fight was finished.

Brushing dust off his clothes as he rose from the floor, Severus glanced around at the spectators. During the whole duel, the only voice had been Carrow's. No one else had said a word, and all Severus's spells had been nonverbal.

"It is as I have been told," he heard the Dark Lord say, and he turned to face his master, breathing quickly and trying to control his trembling. "Your dueling skills are not balanced. You excel at defense; you are weak in attack. Yet you have bound your opponent and would therefore have a prisoner to bring to me. You have a new assignment. You will teach your brothers and sisters to protect themselves in battle, to use these defensive skills of yours to make them better fighters. You will start at once."

The observing wizards came into the arena to congratulate Severus on his success, none more relieved than Rabastan, who couldn't stop grinning as he said over and over again, "I knew you could do it."

The good part was that after months of seclusion amounting almost to isolation, Severus was once again among people, people he could talk to as well as teach. The bad part was that such a large percentage of the Death Eaters were so abysmal at casting nonverbal spells that he had trouble understanding how they ever made it through Hogwarts. Another problem was the almost total lack of understanding about defense.

"Why can't I just go for his head?"

"Because I'm sure even someone with a pea brain like yours has noticed you can't win a fight if you're immobilized on the ground."

"I can just do it faster."

"Not 'til you can do it silently. The first syllable you utter, he knows which spell you're using."

Rabastan came for lessons, and was one of Severus's best pupils. Bella came, as well, though with less sense of its value. Many of Severus's pupils were much older than he was, and the incongruity of a nineteen-year-old teacher with a forty-year-old pupil was a source of mild amusement.

Lucius Malfoy came, too. Freed from parental restraint and in possession of his inheritance, Lucius had quickly become a Death Eater. He and Severus talked a little of old times, and Lucius confided with some pride that Narcissa was with child. Severus was more patient with Lucius than with many of the others, and more careful to teach him the finer points of self-defense, for Narcissa's sake.

As Christmas approached, a raiding party of Death Eaters ambushed and killed Benjy Fenwick, leaving nothing behind but small pieces, a fact which did not please the Dark Lord, who had hoped to `talk' with Benjy.

Winter deepened and the Dark Lord led his forces to unerring victory. The new source of information was the best they'd ever had, and raiding parties came back to headquarters both successful and without casualties. With the New Year, one group cornered Edgar Bones and his family, leaving almost no one alive. It was a mark of the Dark Lord's power that such an accomplished wizard could be attacked and defeated with impunity.

The only bad news, in fact, was the sudden, unexplained disappearance of Regulus Black. He'd taken a bit of a holiday to spend Christmas with his recently widowed mother and had not returned. Rumor abounded that he'd been kidnapped and possibly killed by Dumbledore's organization, but despite the Dark Lord's sources of information, no answer to the mystery was found.

Feeling that it was now fighting a losing battle, the Ministry of Magic took the extraordinary step of authorizing its Aurors to use Unforgivable Curses against the Death Eaters. This was a great moral victory, since the Ministry could no longer claim to be representing the side of decency.

In May, the Death Eaters scored another triumph with the ambush and disappearance of Caradoc Dearborn, whose body was never found. The brethren who'd gone on that raid never told exactly what happened, though they seemed to think it exceptionally funny whenever anyone asked.

On the fifth of June, 1980, Narcissa Malfoy gave birth to a boy child, a son for Lucius. Severus was invited to the naming ceremony, and was delighted at Narcissa's radiance. Lucius, his patrician reserve for once set aside, was practically bursting with pride.

Narcissa allowed Severus to hold baby Draco during a quiet moment away from the crowd of relatives and well-wishers. It was a precarious moment, for Severus had never held a baby before, but Narcissa assured him, laughing, that he was doing a great job. Severus was entranced by the scrunched up baby nose and the pouting little mouth, and utterly amazed at the tiny perfection of infant fingernails. Most of all, it was good to see Narcissa so happy.

Holding Draco made Severus remember the prophecy. `A child approaches{\el}' But not this child, and for that Severus was glad. He'd heard that Lily was also pregnant, and he'd checked carefully with all his sources of information. The most reliable rumor said she would have her child before the middle of August, so that was good, too.

June brought a return of students from Hogwarts. One of them was Barty Crouch, who was initiated into the Dark Lord's forces. Crouch was a great coup for his sponsors, as his father was an official in the Ministry of Magic, and Crouch Junior was another good source of information.

The beginning of July almost brought a setback, for a raiding team intending to attack a single family was instead engaged by a party of Dumbledore's followers. There was a fight this time, from which both Avery and Lucius returned wounded. The Dark Lord was satisfied, however, since the team gave better than it got, and both his enemies Gideon and Fabian Prewett were dead.

Starting in the middle of July, the Dark Lord set up a team of researchers to go through \emph{The Daily Prophet} and all other wizarding news media looking for, of all things, birth announcements. Severus knew why, and the Dark Lord, of course, knew why, even though the team itself was not told the purpose of this information. For a while it seemed as if there would be a total dearth of babies in July, then on the last day of the month they found the article they'd been looking for. The day before, July 30, 1980, Alice Longbottom gave birth to a baby boy. She and her husband Frank would name him Neville.

The news gave Severus an odd feeling. The abstract danger to the Dark Lord that he'd known about for so many months now had a name: Neville Longbottom. For a brief moment he wondered if this child, too, had perfect fingernails, then forced the thought from his mind. Frank and Alice were both Aurors, enemies, and in a very important way it was fitting that their child should be the one that the Dark Lord would seek. It was fate.

So it came as a complete surprise to walk into headquarters on August first and find that the research team was agog with news. The announcements page of \emph{The Daily Prophet} had a small picture of a beaming James Potter, and the news that his wife Lily had given birth to a boy, Harry James Potter, the previous day—July 31st.

\emph{August. She was supposed to have the baby in August. He won't attack them anyway; the baby isn't a pureblood. Not as dangerous as the Longbottom child. They're Aurors. It makes more sense.} Severus smiled at the Death Eater who told him of the birth. "Is that what you were looking for, then?"

"Don't know. Any child born the second half of July. We're to keep on looking for another week or so in case there's a belated announcement. But we have two good ones. He'll be pleased."

The week passed in suspended animation, but there were no further births. The research team was disbanded and its members reassigned. Severus began to get more chatty with the Death Eaters he was training in defensive spells.

"{\el}You must be getting some difficult assignments. This is your third lesson on repelling Cruciatus curses. Which Aurors are they sending you up against, anyway?"

"Usual Ministry thugs. I'm just not good at it{\el}"

"{\el}I'm getting a lot of repeat work from people going to the northern counties. I hope you're not always being sent against that Dumble crowd."

"It was more a `muggle control' thing, if you take my meaning{\el}"

"{\el}Sometimes I envy you. Here I have to stay at headquarters all the time and never get to strike a blow for the cause. You must go up against some powerful adversaries."

"Not always. They've got a lot of us chasing the Potters for some reason. I understand it's a personal vendetta. Not that I'm complaining. I don't want you to think I'm complaining{\el}"

So there it was. Several of the teams were specially delegated to hunt down the Potters. Not the Longbottoms, the Potters. Severus felt sick.

As week followed week, waiting for the news that one of the teams had succeeded, Severus racked his brain for the glimmer of an idea of something he could do to avert catastrophe. There was nothing he could do about the baby or about James—the attempt alone could mean his own death—but he might be able to help Lily. He requested an interview with the Dark Lord.

"So, Potions Master, you petition us for this woman? This mudblood?" The shadow of the Dark Lord's form loomed outside the circle of light where Severus knelt.

"Please, Lord. I saw her{\el} her picture, and now I can't get her out of my mind. We were in the same year{\el} I recall her from my Potions class. She's talented. She could be turned to your service{\el} in brewing potions{\el} I've served you loyally, Lord, and now I{\el} I need her{\el} I{\el}"

The Dark Lord's laughter cut across Severus's words. "The body burns when one is twenty, but it can burn for more than one woman. Take heart, Potions Master, we shall consider your need, but it will not be this woman. This woman is our enemy. Find another to suit your `needs' and we shall listen to your request. But not this one."

Severus left the Dark Lord's presence defeated and despairing.

Faustino Pembertine was one of the Death Eaters that Severus tutored from time to time. At the end of August, all those who'd worked with the unfortunate Pembertine were called into the interview chamber, for he'd been apprehended trying to defect to the Ministry of Magic.

"Did you think we would not know?" the spectral voice asked.

"Lord, I didn't betray you! I would never betray you! But my family, the Ministry, I had to look out for my family."

"We do not see the distinction. Betrayal is betrayal."

Pembertine gasped and began to claw at his left arm. "No, Lord!" he screamed. "I won't leave you! I'll serve you!" He ripped the sleeve from his arm and tore with his fingernails at the flesh beneath. The mark there was glowing a ghastly, putrid green. As Pembertine struggled, boils began to erupt on his skin, burst and spew green slime. He twisted and contorted on the floor of the chamber, clutching his stomach in wild torment, vomiting blood and maggots. And then he was dead.

"We have been merciful," intoned the spectral voice. "His punishment was quick. Those whose betrayal is on a greater level shall have greater punishment. Their torment will last for days. Take care that none of you join him."

Severus returned home that evening in a state bordering on panic and spent hours staring at the tattoo, the mark on his left arm.

Then a team of Death Eaters captured Dorcas Meadows, who was brought alive before the Dark Lord. Everyone at headquarters was summoned for the interrogation. It did, indeed, last for days. In the end it was a shell of a woman who stood before the Dark Lord, but she did not break. And she died there in the interview room, a lesson and a warning to all.

Severus couldn't sleep or eat or even think straight.

\emph{What can I do? I'm not strong enough. I can't fight the Dark Lord. I can't face the pain. It wouldn't help anyway. Who? Who? Who can I go to? There's no one. I have no one{\el}}

\emph{I have Hagrid. Hagrid can get me to Dumbledore. But I can't get to Hagrid. If I go near Hogwarts I'm dead. If I enter Hogwarts he'll know and I'm dead. There's no way. No way{\el}}

\emph{There is a way. The Shrieking Shack. It's a way into Hogwarts. He'll still kill me. But I can speak to Hagrid first.} 


