% A Difference in the Family: The Snape Chronicles (Rannaro)
% Yes, That Is My Job

\chapter{Occlumency}

Monday should have been a thoroughly normal day, and to outward appearances maybe it was, but inwardly Snape was dreading the evening. At the end of his last class, he went up to Dumbledore's office, using side staircases to avoid Umbridge, now back at Hogwarts, and took the pensieve down to his own rooms. There, in the dark, he set it on his desk with a candle on either side to help him focus.

Seating himself in a chair in the corner, Snape contemplated the pensieve, then began to review and lock away all his thoughts about Lily. It was painful to remember what had been lost, but beneficial, too, for this was Lily's son he was trying to help. Lily's son. He hadn't felt that so strongly since two years earlier, when Sirius Black escaped from Azkaban. How much had changed since then.

In the dim silence, Snape rose and placed three memories into the pensieve, the one long and two short of Lily that he'd chosen. Every other trace of her was locked away. Then he sat again to review the long relationship with the Dark Lord, that had started in trust and turned so foul, shutting away all of it, hoping it would not burst open and spill out when he confronted the green eyes.

A knock startled Snape from his reverie, and he watched as the office door opened and Lily's son stepped into the room, confused by the dark and the candlelight. "Shut the door behind you, Potter," Snape said quietly, and the boy did as he was told. Snape moved forward and motioned to a chair on the other side of the room from the desk. He himself sat in front of the pensieve, watching Potter's shadowed face across the room, shadows that hid Lily's eyes.

"Well, Potter, you know why you are here. The headmaster has asked me to teach you Occlumency. I can only hope that you prove more adept at it than Potions." \emph{If not, I am dead, and you are dead, and all is lost.}

"Right," Potter replied, his voice not masking the scorn.

"This may not be an ordinary class, Potter, but I am still your teacher and you will therefore call me `sir' or `Professor' at all times."

"Yes{\el} sir."

\emph{This is going to be harder than I thought. We've added a new layer. Now I have Lily's eyes, James's face, and Sirius Black's mannerisms.} "Now, Occlumency. As I told you back in your dear godfather's kitchen, this branch of magic seals the mind against magical intrusion and influence."

"And why does Professor Dumbledore think I need it, sir?"

\emph{Because you did a mind-meld with the Dark Lord and attacked Arthur Weasley while inhabiting the body of a snake.} "Surely even you could have worked that out by now, Potter? The Dark Lord is highly skilled at Legilimency{\el}"

"What's that? Sir?"

"It is the ability to extract feelings and memories from another person's mind{\el}"

"He can read minds?"

\emph{How do I explain this? I speak to Dumbledore of reading, and call myself an open book, but that's because we both understand that to be a quick way to refer to something far more complex. But if Potter thinks only of the simplistic action of reading, he will not learn to hide his thoughts and feelings.}

Snape tried to make Potter understand the subtle control of memory and emotion that allowed an occlumens to reveal those thoughts that would confirm what he was saying while concealing those that would contradict him. It was almost as if the boy was not paying attention.

"So he could know what we're thinking right now? Sir?"

"Time and space matter in magic, Potter. Eye contact is often essential to Legilimency."

"Well then, why do I have to learn Occlumency?"

\emph{I don't know. Maybe you vicariously enjoyed attacking Weasley. Maybe you have secret ambitions of becoming a Dark Lord yourself and want to pick up hints on how to go about it. Maybe you're just lazy and stupid.}

With a deep sigh, and a prayer for patience, Snape went back to the beginning and once again tried to explain.

\emph{Make it simple, Severus. He has to understand this.} "The usual rules do not seem to apply with you, Potter. The curse that failed to kill you seems to have forged some kind of connection between you and the Dark Lord. The evidence suggests that at times, when your mind is most relaxed and vulnerable—when you are asleep for instance—you are sharing the Dark Lord's thoughts and emotions. The headmaster thinks it inadvisable for this to continue. He wishes me to teach you how to close your mind to the Dark Lord." \emph{Any simpler, and I'll be using words of one syllable only.}

"But why does Professor Dumbledore want to stop it? I don't like it much, but it's been useful, hasn't it? I mean{\el} I saw that snake attack Mr.~Weasley and if I hadn't, Professor Dumbledore wouldn't have been able to save him, would he? Sir?"

\emph{This is like beating my head against a brick wall! He really does need words of one syllable. I can't tell him how I know—he's dumb enough to blab it to everyone, including the Dark Lord. Was James like this?} "It appears that the Dark Lord has been unaware of the connection between you and himself until very recently. Up till now it seems that you have been experiencing his emotions and sharing his thoughts without his being any the wiser. However, the vision you had shortly before Christmas{\el}"

"The one with the snake and Mr.~Weasley?"

"Do not interrupt me, Potter. As I was saying{\el} the vision you had shortly before Christmas represented such a powerful incursion upon the Dark Lord's thoughts{\el}"

"I saw inside the snake's head, not his!"

"I thought I just told you not to interrupt me, Potter?" \emph{Does two plus two always give you three, Potter? Can you not infer the simplest thing? Is there no intuition in you at all?}

"How come I saw through the snake's eyes if it's Voldemort's thoughts I'm sharing."

Pain lanced through Snape's left arm, and his breath hissed inward with the shock of it. "Do not say the Dark Lord's name!" he gasped. The two of them glared at each other.

"Professor Dumbledore says his name."

"Dumbledore is an extremely powerful wizard." \emph{And I will not give you the truth as a weapon to use against me.} "While he may feel secure enough to use the name{\el} the rest of us{\el}"

"I just wanted to know why{\el}"

"You seem to have visited the snake's mind because that was where the Dark Lord was at that particular moment. He was possessing the snake at the time and so you dreamed you were inside it too{\el}"

"And Vol{\el} he{\el} realized I was there?"

\emph{Thank goodness! We've arrived at last!} "It seems so."

"How do you know? Is this just Professor Dumbledore guessing, or{\el}"

Snape froze. That information in Potter's brain was dangerous. He shifted the subject. "I told you to call me `sir.'"

"Yes, sir, but how do you know{\el}\,?"

"It is enough that we know. The important point is that the Dark Lord is now aware that you are gaining access to his thoughts and feelings. He has also deduced that the process is likely to work in reverse; that is to say, he has realized that he might be able to access your thoughts and feelings in return{\el}"

"And he might try and make me do things? Sir?"

"He might." \emph{And if that were all, I would feel much calmer about this.} "Which brings us back to Occlumency."

It was time, but Snape still had three more memories to put in the pensieve. Placing the tip of his wand against his temple, he thought the nonverbal spell Dumbledore had taught him and withdrew the memories of Nana, his return to Dumbledore, and that terrible Halloween night. Then Snape carefully removed the pensieve to a safe counter and turned to face Lily's son, his own wand ready in his hand.

"Stand up and take out your wand, Potter." The boy obeyed, seeming relieved that the desk was between them. There was still the prohibition against a student attacking a teacher, but Snape quickly dismissed it. "You may use your wand to attempt to disarm me, or defend yourself in any other way you can think of."

"And what are you going to do?" Potter asked, his nervousness evident in his voice.

Explanation was necessary. Legilimency practiced against an unsuspecting target, except in battle, was unethical. "I am about to attempt to break into your mind. We are going to see how well you resist. I have been told that you have already shown aptitude at resisting the Imperius curse{\el} You will find that similar powers are needed for this{\el} Brace yourself now{\el}" As Snape spoke, he also checked his own mind to be sure his thoughts were still locked away. Then, gazing into the well-loved eyes, he cried, \emph{"Legilimens!"}

It was a bizarre feeling, for up until this moment Snape's only experience with legilimency was reading the surface thoughts of someone about to fight him, or the projected thoughts of Dumbledore. Now it was as if a window opened in the front of his mind, and through that window he could see and feel the thoughts flitting through Potter's brain. He projected an undefined negative feeling, and the memories responded as if trained.

A fat little boy—his cousin?—rode a red tricycle, and Snape himself felt the resentment at not receiving such toys{\el} A dog chased a small Potter up a tree while others laughed{\el} The Sorting Hat's voice told Potter he would do well in Slytherin—\emph{He was almost sorted into Slytherin? Does Dumbledore know?}{\el} Granger lay in the hospital after the disastrous experiment with Polyjuice Potion—\emph{poor girl, muggle-born like Lily}, and Snape realized that the doors in his mind were being forced open{\el} Dementors clustered around, and Snape cringed in remembered fear as he fought to keep his own vision of them away{\el} A girl drew near, and Snape realized there was a sprig of mistletoe{\el} Then Potter was yelling, "You're not watching it! It's private!"

Sudden burning pain hit Snape's right hand, and he broke the connection as he jerked hand and wand away from Potter's attack. Glancing down, he saw an angry red welt, like the mark of a whip, across his right wrist. \emph{Interesting. The boy fought back because of the girl.}

"Did you mean to produce a Stinging hex?" he asked.

Potter had moved closer to the desk and fallen as he attacked. Now he clambered to his feet. "No," he answered, his voice hard and wary.

"I thought not. You let me get in too far. You lost control." Snape was watching for any sign that Potter had seen his thoughts as well.

"Did you see everything I saw?"

"Flashes of it. To whom did the dog belong?"

"My Aunt Marge."

Snape rotated the injured wrist, trying to relieve the sting. "Well, for a first attempt that was not as poor as it might have been. You managed to stop me eventually, though you wasted time and energy shouting. You must remain focused. Repel me with your brain and you will not need to resort to your wand."

"I'm trying, but you're not telling me how!"

"Manners, Potter," Snape replied, though he realized the boy had made a point. \emph{I can't tell you how to do it because I don't always know how I do it. It just happens. You can't teach instinct. I can't teach anything with Lily staring at me out of James's face. Try something different, Severus.}

"Now, I want you to close your eyes."

Potter glared at Snape, clearly angry at being forced to reveal his thoughts.

\emph{If you don't want to show me what you're thinking, learn to block me. Your anger is hindering your concentration.} "Clear your mind, Potter. Let go of all emotion{\el}" Yet the boy was not letting go of his emotions. He didn't seem to be trying, his anger bubbling up so strongly that Snape could feel it even without eye contact. A familiar anger, boiling near the surface. "You're not doing it, Potter{\el} You will need more discipline than this{\el} Focus, now{\el}"

Then the passion began to diminish, the turmoil to lessen. It was a hopeful sign. Snape raised his wand. "Let's go again{\el} on the count of three{\el} one—two—three—\emph{Legilimens!}"

A great dragon reared up in attack, black scales glistening through the haze of fire and smoke, and then{\el} Snape was startled to see Lily in front of him—Lily and James waving and smiling—\emph{Is this my thought, given to Potter even with the green eyes closed?} Snape struggled to control his own feelings, and noticed only at that moment that the image was framed in a mirror, a mirror he recognized{\el} which dissolved into the staring dead eyes of Cedric Diggory{\el}

Potter was on the floor, howling NOOOoooo! as Snape broke contact and released him, nearly as shaken and distraught as the boy. But Snape recovered faster, now burning with anger himself. \emph{I know where this comes from, this self-indulgent, lethal sentiment that's going to get us all killed. He's been wallowing in it at Grimmauld Place. There's another one who never could control his emotions or his actions!}

"Get up!" he snapped at Potter. "Get up! You are not trying, you are making no effort, you are allowing me access to memories you fear, handing me weapons!" \emph{Handing the Dark Lord weapons!}

Potter stood, and Black's uncontrolled, murderous anger blazed from Lily's eyes. "I. Am. Making. An. Effort." he forced out.

"I told you to empty yourself of emotion!"

"Yeah?" Potter snarled, and his mouth curled in a way James's never had. "Well, I'm finding that hard at the moment."

"Then you will find yourself easy prey for the Dark Lord! Fools who wear their hearts proudly on their sleeves, who cannot control their emotions, who wallow in sad memories and allow themselves to be provoked this easily—weak people, in other words—they stand no chance against his powers! He will penetrate your mind with absurd ease, Potter!"

They confronted each other across the desk, fire and ice, and Snape could see the violence brewing behind the green eyes as his own mind began automatically to lock down in the face of an imminent attack. "I am not weak," Potter hissed in a threatening whisper.

"Then prove it! Master yourself! Control your anger, discipline your mind! We shall try again! Get ready, now! \emph{Legilimens!}"

A large man nailed a board over a slot{\el} Dementors glided next to the lake at Hogwarts{\el} Potter was running with a man, with Arthur Weasley, down a corridor toward a black door, but swerved aside down a flight of stairs{\el}

"I KNOW!" Potter screamed. "I KNOW!"

Snape broke away again and stared down at Potter, once again on the floor. "What happened then, Potter?"

"I saw—I remembered. I've just realized{\el}"

"Realized what?" A terrible feeling of apprehension was growing in Snape.

Potter looked up suddenly, "What's in the Department of Mysteries?"

Now fear began to overtake anger, and Snape could feel the blood drain from his face. "What did you say?"

"I said, what's in the Department of Mysteries, sir?"

"And why{\el} would you ask such a thing?"

Potter's face took on a speculative look as he seemed to search Snape's features. "Because that corridor I've just seen—I've been dreaming about it for months—I've just recognized it—it leads to the Department of Mysteries{\el} and I think Voldemort wants something from{\el}"

Pain seared again. "I have told you not to say the Dark Lord's name!" But over and above the pain there was now well-defined and focused fear. \emph{The Dark Lord has been trying to break into the Department of Mysteries for months, and Potter has been dreaming of the Department of Mysteries for months. They've been linked for months, this idiot boy and the Dark Lord, and we're only now finding out about it.} With an effort, Snape forced his own emotions into the background.

"There are many things in the Department of Mysteries, Potter, few of which you would understand and none of which concern you, do I make myself plain?" \emph{And I thank Providence that I, too, am ignorant, for you now can never learn that information through me.}

"Yes," replied Potter, rubbing the scar on his forehead.

\emph{Once a week may not be enough.} "I want you back here same time on Wednesday, and we will continue work then."

"Fine."

"You are to rid your mind of all emotion every night before sleep—empty it, make it blank and calm, you understand?"

"Yes."

"And be warned, Potter{\el} I shall know if you have not practiced{\el}"

"Right." And Potter picked up his book bag and left the room.

Snape didn't watch him go. Shaken to the core of his being, he moved mechanically to the pensieve to retrieve his thoughts. Only then did he realize how the relationship between himself and Potter had subtly changed. The stilted formality of `Professor' and `Sir' had disappeared, and they had spoken and interacted as equals. Equals caught in a strange mesh of mental connections that included Lily and Black and, most frightening, the Dark Lord, who had now touched both their minds. It was a net that Dumbledore had to be protected from at all costs.

Picking up the pensieve, Snape started for Dumbledore's office, when another thought came to him. \emph{Chased up a tree while everyone laughed. His childhood must have been miserable. Not what I imagined at all.}

Filling Dumbledore in on the extent of Potter's contact with the Dark Lord and its implications was a matter of fifteen minutes. Dumbledore was concerned, and agreed that contact with Potter at this time could put them all into jeopardy. Then Snape went back to his rooms and tried sorting and reviewing everything he'd seen and felt that evening.

The summons came shortly before eleven, not a blinding, numbing insistence, but one strong enough that Snape knew he had to leave at once. Sneaking from the castle, he sent his patronus to Dumbledore with a request to be allowed out, and was soon disapparating from Hogsmeade.

Midnight Croydon was calm and peaceful as Snape made his quiet way to the headquarters building. Around him other Death Eaters were apparating in, all of them apparently as mystified as he. They filtered into the building in small groups, and were ushered into a now crowded interview chamber.

Lucius Malfoy was standing at the door, and pulled Snape aside as soon as he saw him. "They'll all know quick enough," he whispered, "but you're going to get a preview. Somebody wants to see you."

After the evening's session with Potter, that didn't sound like good news. Snape trailed reluctantly behind Malfoy down one of the basement corridors into a dim room where a group of people were gathered.

"Look who's here," chuckled a female voice, a sultry contralto that even after fourteen years Snape recognized instantly. "My little puppy dog's come running to greet me at the door."

Snape turned to the voice, registering as he did so the faces of Rabastan and Rodolphus Lestrange, of Aloysius Mulciber, Antonin Dolohov, and Augustus Rookwood, all suddenly and inexplicably free of Azkaban prison. She stood behind them, raven hair brushed back away from her face, heavy-lidded eyes and pouting lips crinkled in what might pass for a smile. Snape felt his heart sink down to his feet, even as he prayed that his voice sounded warm and pleasant.

"Hello, Bella," he said. "Welcome home."

"My, my. You've grown up," Bella commented as she moved to Snape's side. "The last time I saw you, you were scarcely more than a teenager. How did you survive the interregnum? I'll bet you have a wife and children by now."

Snape realized to his embarrassment that he was blushing, and Malfoy crowed with laughter. "You're talking to a monk, Bella. Dumbledumb keeps him locked in a cell most of the year, and the month he gets free, he spends with books."

"Dumbledore? You're still teaching at Hogwarts?"

"Fourteen and a half years now," Snape replied. "It was that or join you in dementor heaven."

"Sounds like Dumbledore knows how to tighten the screws. How did you manage to slip the chain and get here tonight for the party?"

Once again Malfoy answered for Snape. "Madam Lestrange, you are looking at a double agent. Dumbledore thinks Severus spies for him when Severus really spies for us."

"Really?" Bella hooked a finger in the fastening of Snape's cloak and pulled him closer to her. "I bet you make a great spy."

"I do my best," Snape said, feeling like a schoolboy again.

Rodolphus edged over to the little group. "Unhand this boy, wife, or I shall have to do battle for your honor." He winked at Snape and Malfoy as he grasped both Bella's wrists and pulled her into a kiss. "Gad, I've missed you."

The two locked lips just as an underling stuck his head into the room. "The Dark Lord is ready for you now. Just go through that door, please."

The escapees from Azkaban were introduced to the throng of Death Eaters, many of whom had apparated in from the branch offices, and there was cheering and back slapping, especially at the news that the dementors now worked for the Dark Lord.

"The best part," Macnair shouted to the crowd, "is that the Ministry still doesn't believe in our existence. (\emph{Cheers from the crowd}.) They're blaming the escape on Sirius Black. (\emph{Boos and jeers}.) And we are free to operate unchecked. (\emph{Wild, tumultuous cheering}.)"

Of course, the whole evening degenerated into a mad party. At one o'clock in the morning, Snape found himself sitting next to Bella as she tried to twist his hair into ringlets. "You know," she teased, "we really have to find you someone. It isn't right for a man as young as you to be forced to live like a priest."

Snape 'd had just enough to drink to consider this highly amusing, thoughts of his father's demon being suspended in the general happy glow. "Just make sure she's dark," he said, "with deep, mysterious eyes."

"Ah, you like them hard to control."

"Why should I control them? Some of the most fascinating women in the world were born to be controllers themselves." Rodolphus, isolated in a corner, was beginning to get pugnacious, but Snape was not focused enough to care about him.

"I remember when I controlled you." Bella shifted her attention from Snape's hair to the buttons on his jacket.

"Happiest time of my life."

"'T isn't fair. A young man like you shouldn't be wasting away in a cloister. I'm going to find you a woman. A good woman. One who'll beat you when you want beating."

"I don't think I said anything about beating. Why not just someone who'll boss me around?"

"You got it, puppy dog. Now just point me in the direction of my husband, before he gets too antsy and tears your face off."

A couple of hours later, it was Dumbledore's job to get Snape to stop giggling and generally sober up enough to teach classes.

\sbreak

By breakfast time, Snape was in acceptable condition, and Dumbledore left him to join the staff table. About twenty minutes later, Snape followed him down. For the most part, the Great Hall looked normal. Potter, Weasley, and Granger were deep in \emph{The Daily Prophet}, so Snape assumed the news of the breakout was already public. Dumbledore and McGonagall were engaged in a private conversation, the seats on either side of them filled with teachers who were studiously not paying attention, while Dolores Umbridge scowled down the table at them, knowing there was no place she could insert herself to listen. Snape sat at the far end from her, not trusting himself to eat anything but toast and coffee.

Flitwick joined him.

"You're looking a trifle peaked this morning, Severus. You're not ill, are you?"

"Nothing time won't cure," Snape replied.

"Have you heard the news? \emph{The Daily Prophet} says ten prisoners escaped from Azkaban yesterday evening. The Ministry is claiming that Sirius{\el}"

"Black is involved. Yes, I heard."

Flitwick peered at him. "It's in this morning's paper, which comes directly to the Hall, and which you have not yet picked up. Nor did you speak to anyone before speaking to me. So, did you have a pleasant evening? And did you get any sleep?"

Snape winced. "Yes and no, Sherlock," was all he said. \emph{How many people know about my double life? How many other teachers are being admitted to the Order? I hope that's how Flitwick knows.}

More information was filtering through the grapevine as teachers leaving the table for their classrooms ostensibly greeted teachers newly arrived for breakfast. "Good morning, Filius—Severus," bubbled Sprout in passing, managing to whisper "Trelawney—Hagrid—probation" as she passed.

Throughout the day it was the same. Tiny groups of teachers would form for thirty seconds, break, and reform in different groups in different places. There wasn't a lot to pass from person to person, but it was good to know the network was functioning.

Wednesday morning brought a surprise. Pinned to the house notice boards and to the staff room door was Educational Decree Number Twenty-Six: `Teachers are hereby banned from giving students any information that is not strictly related to the subjects they are paid to teach.'

Snape and Sprout, both of whose houses were on the dungeon level, met in front of the staff room and read the notice together.

"That power-hungry, interfering old{\el}" Sprout began, but then saw the look on Snape's face. "You have an idea. You're going to pull a Lockhart on her, aren't you? Spill, Severus."

"I can't do it myself because I'm under orders to stay on her good side, but you can. Especially since you are so good at acting innocent." He bent and whispered in Sprout's ear, and she grinned.

At the end of breakfast, a group of brave Hufflepuffs remained at their table after the bell rang for first classes. Sprout, seeming casual and unaware, contrived to pass by Umbridge as she left the staff table and was stopped.

"Isn't that your house," Umbridge snapped, pointing at the loiterers. "Tell them the bell's rung and their classes will begin soon."

Sprout smiled a timid and diffident smile. "I'm sorry, Professor," she replied. "That information is not strictly related to the subject I'm paid to teach," and she marched past and out of the hall without another word, managing to give her students a sly, conspiratorial wink as she did so.

All day, Umbridge found herself facing situations that had nothing to do with academic subjects and teachers who refused to disobey Educational Decree Number Twenty-Six, at least not in Umbridge's presence. By supper time, Professor Umbridge was very short-tempered indeed.

Wednesday ended unpleasantly with Potter's second occlumency lesson. Even before the boy arrived, Snape was regretting his decision to have two lessons in one week. Dumbledore'd said one, and though Snape felt Potter needed more frequent work if he was to have even a small chance of success, the experience was so distasteful to Snape that he wondered if it would be counterproductive.

"Did you feel anything Monday night?" Snape asked after Potter sat down in the chair opposite.

"I thought I wasn't supposed to. Sir."

"If you think I am going to let you get away with not answering the question, you are very much mistaken."

"No. I didn't feel anything. I emptied my mind like you told me to."

"We shall see."

They stood facing each other and Snape began, already knowing what he was looking for. He projected an image of the Dark Lord, and was rewarded with the memory of wild, almost insane laughter. He broke off contact immediately.

"You lied to me."

Potter glared back defiantly. "You don't know when that happened."

"Yes, I do. It happened Monday night, the moment the Dark Lord received word that the Azkaban breakout was successful. I am a mediocre legilimens, Potter, but even I could pull that out of you with absurd ease."

"But I wasn't asleep when it happened. You told me to empty my mind before I went to sleep."

"I didn't ask you if you dreamt anything. I asked you if you felt anything. You lied to me. Now, we shall continue."

It started with another string of bad childhood memories, but Snape wasn't looking for these. Although unpleasant, they didn't make Potter defensive enough. Snape was looking for the girl. "Tell me about Miss Chang," Snape said quietly.

The girl's image surfaced at once, and Potter did nothing to stop it, although Snape could now feel anger rising in him like a tide. "Mistletoe," Snape prompted, and got the image that Potter had reacted to on Monday.

"Stay away from that!" Potter yelled, the Stinging hex flying from his wand to be deflected by Snape, who was expecting it this time.

Snape broke contact. "Physical reaction. Typical Gryffindor move. No matter how you're attacked—verbally, mentally—you always react physically. But physical reaction won't keep me out. It won't keep me from seeing the image. And you won't be facing the Dark Lord with a wand in your hand either. You have to learn to block this mentally."

"So teach me how."

"Try thinking of your mind as two compartments. One is there to be seen, and the other is for hiding things. Put the image of Miss Chang in the second compartment and close it off so that even you can't see it. Then, no matter what I do, don't open that compartment."

"I don't have any compartments."

"Anger, any strong emotion, gets in the way. You can only keep me out if you can learn to regard me clinically, coldly, and leave your emotions out of it. Let's try again."

But it was useless. Either Potter would not, or he could not, let go of his anger. Snape deflected hex after hex, and saw image after image. Finally, drained, he stopped.

"You know, Potter, if I got you angry enough, I could watch your whole life like watching a movie. You are that open. Your next session is on Monday. Please try working on emotional control during the next few days. Try putting feelings aside and viewing everything dispassionately."

After Potter left, Snape sat for a while in front of his cold fireplace, his head in his hands. \emph{James was like that. He never could hide his feelings. When the Dark Lord came that night, did James try to protect Lily? And did the Dark Lord read where she was just as easily as I saw Miss Chang in Harry's mind? James would have faced him with a wand, fighting. And he would have given Lily to the Dark Lord right there, even as he died trying to save her.}

Snape informed Dumbledore of the signal lack of any progress at all in the occlumency sessions, and of Potter's lying. Dumbledore asked to be informed only of any change in Potter or, if there was no change, a monthly report. They decided that a lesson once a week was sufficient, especially since it appeared that too many sessions might cause Potter to rebel.

And then there was Croydon.

The next summons came the very next day, Thursday. Snape left after supper and was asked to wait at the entrance by a junior level Death Eater. A few minutes later, he was joined by Lucius Malfoy and Bella Lestrange, who smiled and said, "Good. Now you can show me around your laboratory."

A protest formed immediately in Snape's mind, but he never voiced it for Malfoy was making faces at him over Bella's shoulder. Instead he replied, "Certainly," and led them upstairs where he released the magical locks and ushered both into his fiefdom.

Bella wrinkled her nose as she sniffed the air. "I'm not convinced this is a useful setup," she stated. "You only come in once a week. What happens if we need supplies in the meantime?"

"Why does this concern you?"

"I'm in charge of Operations now." Behind Bella's back, Malfoy was nodding confirmation.

"Both Operations and the clinic are more than amply stocked. And you can always send for me to make a special trip down. As you've done tonight. The inconvenience is minor, whereas the damage that could be done by giving unqualified personnel access to brewing potions is enormous."

"The Dark Lord thinks you're being too secretive."

"No, he doesn't. You're the one who likes to poke around in everything." Malfoy was making hissing noises and emergency stop gestures, but Snape ignored him. Instead he continued, "Why don't we ask for an immediate interview with the Dark Lord and both explain our positions to him."

There was a pause, and Snape could practically see the gears turning in Bella's brain. "No," she said at last. "It's too minor an issue to waste his time with."

"I doubt he would consider the total collapse of his potions supply a minor issue." Snape stepped to the row of cords that attached to bells in the support staff area. A moment later a messenger appeared at the laboratory door. "Please request that the Dark Lord grant an interview this evening to me, Mrs.~Lestrange, and Mr.~Malfoy." The messenger was gone at once.

"This really isn't necessary," said Bella.

"I think it is," replied Snape.

To the surprise of all three, the interview was granted at once. With all three standing before him, the Dark Lord addressed Snape first. "We know, Potions Master, that you are not pleased with our desire to give our personnel in Operations access to your laboratory. You will explain your position."

Snape explained. He explained in excruciating detail. It was hard to tell if his words were making an impression. "Lord," he said finally, "if they are allowed into the laboratory, I can no longer be responsible for the quality of your potions. What if one of them decides it is too cool, turns up the heat, turns it back down, and doesn't tell me. I'd be giving your people doses of wound healing medicine that made them bleed more instead of less. No offense to your new head of Operations, but she doesn't know the basics of advanced potion brewing. I know. I used to tutor her. She couldn't even tell you what H2SO4 was."

The Dark Lord fixed his gaze on Bella, who turned crimson and looked at the floor.

Seizing his advantage, Snape pressed it home. "Please, Lord, keep them out of my laboratory. Or let me leave Hogwarts and tend it twenty-four hours a day. Or get another Potions Master. I would rather serve you as a soldier on the front lines of battle than supply you with potions whose quality I could not guarantee."

Bella lost. The Dark Lord pronounced that the laboratory would remain under the exclusive control of Snape, and that any person found entering it without express authorization would be punished.

Lucius Malfoy was pleased. Bella Lestrange was not. \emph{I've made an enemy, perhaps, but winning this battle was worth it.}

By the time of Snape's regular Saturday trip to Croydon, things were truly being shaken up at headquarters. Bella Lestrange had clearly finessed a power play and was now, with her husband Rodolphus, the Dark Lord's lieutenant for all of Great Britain. Her only disappointment was the continued influence of Lucius Malfoy. Battle lines between Malfoy and the Lestranges were being drawn, and Bella was out for blood.

Luckily for Malfoy, the Dark Lord was not entirely blind to Bella's shortcomings. She'd worked hard to persuade him to send Malfoy out to one of the branch offices, but Malfoy's value as a contact with the Ministry of Magic was too great, and he remained in charge of the London\slash Croydon headquarters.

It was in the context of this duel for power that Snape found he had unwittingly placed himself in Malfoy's camp. The confrontation between him and Bella over access to the laboratory highlighted certain areas of weakness in her leadership abilities, and while her energy, creativity, and devotion kept her in charge of coordinating all Operations in the country, her authority to intervene in the internal structure of the various branches was reduced. As a result, Malfoy valued Snape even more highly, while Bella{\el}

"She's already got Macnair, and she's after you now, you know," was Malfoy's way of putting it as the two met for tea in the staff lounge. "At least that's what some of my contacts tell me."

"That could be interpreted in a variety of ways."

"She means it in a variety of ways. She'd like to seduce you over to her side. That would strengthen her and weaken me. If she isn't successfully in wooing you, she'll try to discredit you or eliminate you. No more power to her, but less for me. A dangerous enemy, that one."

"She was like that even in school. I've been wooed before. It's a carrot and stick operation. Rabastan and Rodolphus were the stick. Protection from them was the carrot. It worked quite well."

"I'm sorry you've gotten caught between Scylla and Charybdis. Things were nicer before. Part of me is beginning to regret the recent depopulation of Azkaban."

It was a dangerous thing for Malfoy to say, and Snape was keenly aware of being made part of a small conspiracy. "How would you like me to handle attempts at seduction?"

"It's a hard thing I'm going to ask you to do, but do you think you could string her along? Make her think that you might be for sale if the price is right? It could buy me some time, and in that time she'll have more opportunities for making mistakes. Ultimately, I think, she'll bring herself down."

The branch offices were experiencing changes, too. At the end of January, Yaxley was unceremoniously booted out of the position at Cardiff, which had seen almost no growth and very little in the way of action. Nott was ordered down from Glasgow to replace Yaxley in the hope that new management would spur the office to greater things, and Yaxley returned to Croydon.

Avery was fortunate enough to retain his control of the Lincoln office, while Rabastan Lestrange took over Nott's job in Glasgow. The attempt to establish an office in York was abandoned in favor of Manchester, where Rookwood was dispatched to set things up. Finally, the Norwich office opened under Dolohov, using some of the people from Lincoln as a core group.

In three weeks, the newly released lieutenants from Azkaban had managed to consolidate their power in the most important positions in the organization, with the sole major exception of Croydon itself. There was a sense that it was only a matter of time before both Avery and Nott would be replaced, and then Malfoy would be isolated in London.

Seduction started the first weekend in February. Snape had hardly been in his laboratory for ten minutes before Bella herself pushed open the door and walked in. Behind her was a younger female Death Eater with long dark hair and sultry brown eyes.

"I would prefer that you knock," said Snape. "Letting drafts in like that could spoil some of the Dark Lord's favorite potions, and then I would have to complain."

Bella ignored the comment. "I have a job for you. Top priority. This is Delphina Vaughn, a distant cousin of mine. She's being groomed in Operations for field work and needs self-defense training. You start today, come in three times during the week whenever you can make it, and finish next Saturday. The Dark Lord has particular interest in this one, and will be watching you." Then, abruptly, Bella spun around and left the room.

Snape regarded the young woman for a moment. He guessed her to be under twenty-five years old. "Just sit in that chair," he told her, "and don't touch anything. It will take me about fifteen minutes to finish up here, and then we can go to the training room." As he worked, Snape could sense that she was watching him, sizing him up. \emph{I wonder what, exactly, Bella has assigned her to do.}

The answer came sooner than he expected. In the training room, Snape started with the first routine lessons on falling, rolling, and recovering. Vaughn's first falls were clumsy, but she soon got the hang of it and was hitting the mat like a gymnast. On her tenth fall, however, she seemed to twist her ankle, and sat there for a moment, not even trying to stand.

"Are you all right?" Snape asked.

She nodded, and he walked over to her, holding out his hand to help her rise. She grasped his wrist and rose smoothly to her feet, clearly uninjured but now close enough to him to clasp her hands behind his neck, leaning against him as if for support. "That was fun," she whispered. "I know some good falls, too. Would you like to try them?"

Snape remained very still, acutely aware that he was as taut as a strung bow. "I think we had best stick to the lesson plan," he said coldly, his voice sounding hoarse in his own ears.

"Whatever you say, Professor," she teased, and instruction continued by the book, but now every move, every command and response was charged with flirtatious tension, a commodity Miss Vaughn manipulated to perfection. It was insulting that Bella would think he could be ensnared in such a blatant fashion, and yet Snape was unable to ignore the effect that the sight, the touch, the very scent of this woman had on him.

When the lesson was over she glanced at him sideways, veiling her eyes with long lashes. "When is our next lesson? Tomorrow?"

"I don't know," was Snape's curt reply. "It depends on what's happening at Hogwarts."

"I hope it's tomorrow. I'd like to see you again soon." She stepped forward as if to kiss him on the check, but Snape pulled back an arm's length, then watched as she pouted her way to the door. "Next time," she said, "maybe we'll have more fun." And then she was gone.

Retreating quickly to the sanctuary of his laboratory, Snape sat for a while, rubbing his forehead with one hand. \emph{Well, Bella said she was going to get me someone, but I honestly didn't think it would be like this. Does she think I'm going through a mid-life crisis, or something? I'm too young for a mid-life crisis.—Too young to live like a priest—that's what Bella said. I must have looked like a fool tonight, trying not to stare at a girl young enough to be{\el} well, my younger sister.} Snape stopped, amused by the situation. \emph{Why am I thinking of myself as ancient and of her as a child? I'm definitely not ancient, and someone in her twenties is certainly no child.}

Apparating back to Hogsmeade, Snape sent his patronus up to Dumbledore and was admitted. The trudge up the hill in the snow gave him time to cool down, and Snape was feeling relatively calm as he entered his office, there to come face to face with Dumbledore.

"Here you are, Severus. I thought we might talk. To come straight to the point, that was by far the most vibrant patronus you have ever sent me, yet it also gave me the sense that all was not well. Did you have a{\el} pleasant evening?"

"Doesn't this rank as a violation of privacy?"

"Well, I suppose it does. And normally I would have nothing to say about your personal life. But this was your normal visit to{\el} London, and it was hard to imagine anything{\el} well, normal{\el} I mean usual{\el} that would have produced such a{\el} glow."

Dumbledore looked so confused, embarrassed, and expectant, all at the same time, that Snape could only sit down at his desk and burst out laughing. Several moments later, after he managed to control himself, he said, "Headmaster, I have a beautiful young woman who is trying to seduce me."

"You are joking."

"Thank you, sir. You have just done wonders for my morale."

"I did not mean{\el}"

"Naturally not. It just slipped out, Freudian-like."

"Now Severus, you have caught me unawares and unprepared, and it is hardly fair{\el}"

"I've always suspected that you think of me as a tool rather than a human being, and now I have proof."

"That is not{\el}"

"Why can't I enjoy life a little? After all, it's not like I was a hundred and{\el}" Snape looked shrewdly at Dumbledore, "fifty? {\el} one? {\el} two? I'm not out of the game yet, you know."

"The last time you giggled like this, you had been drinking."

"And enjoyed every moment!" Snape stopped, suddenly calm and wary again. "Professor," he said, "Bella Lestrange has brought in a temptress she claims is her cousin to entice me into her camp and leave Lucius Malfoy isolated in a headquarters power struggle."

"Ah," said Dumbledore, nodding, "now I understand. This is not a suddenly blossoming relationship. It is a trap. And a rather heavy-handed trap by the sound of it."

"I'm supposed to go back three times in the middle of the week for her defensive training, one on one, and finish next Saturday. I find the whole thing offensive, that Bella thinks I'm so starved for affection that I'll walk right into this one in such a short time. The young woman also seems to feel she can twist me around her little finger. Although she is very attractive. Very."

"Was she using any spells?"

"No. I detected none. Not that she won't in the future. This is going to be a very tense week."

"Is there any way you could take advantage of the situation?"

"I hope you don't mean play along with her? There are certain parts of my life I'd like to keep private, and the idea that Bella Lestrange would get a detailed account{\el} You have the right to ask a lot of me, Headmaster, but there I draw the line."

"Well, it was a thought. You have been rather tense lately."

"Now you're joking at my expense."

"Why not? You joked at mine."

"Touché."

"Seriously, though," continued Dumbledore, staring into the empty fireplace, "there are many different layers of intimacy, some of them quite superficial. This young lady might be a source of information. It might also be valuable to have you neither in Malfoy's camp nor in Bella's. That way both would be trying to lure you to them, maybe with offers of higher status, and Riddle would see you as independent of faction and therefore more devoted to him. It could work very much to our advantage."

"It could backfire. They might both see me as another rival and conspire to get rid of me first."

"I leave it up to you, Severus. You have a much better feel for the situation on the ground than I do. But do consider it."

"Just out of curiosity, if I did follow your plan, would I have to report on it to the Order? Sirius Black is another person I'd rather not have know anything about my private life."

"It would be entirely between you and me. Think about it."

"Yes, sir."

Snape spent most of Sunday thinking about it, then decided to return to Croydon that evening. He knew Bella would see this as an indication that he was falling into her trap, but it also left him with more flexibility later in the week. He still hadn't determined how he would handle the whole situation, but there was something to be said for playing it by ear.

The best part was that Snape didn't have to worry about Umbridge spying on him. That Lady had put both Hagrid and Trelawney on probation and was now observing all of their classes and maintaining a running evaluation that had the two teachers on the edge of nervous breakdowns.

The good part was that it had Umbridge on the edge of a physical breakdown. In order to accommodate this killing schedule, she'd had to change the times of all her own classes, teaching Dark Arts in the early morning and evening, and also rearrange the times of Hagrid's and Trelawney's classes where they conflicted. It was only a matter of time before the woman suffered a total collapse (some of the teachers had a pool going), and in the meantime Umbridge had lost interest in Snape's actions.

So, after a fairly leisurely and meditative Sunday, Snape ate supper in the Great Hall and then left the grounds and apparated to Croydon.

Miss Vaughn stuck her head into the laboratory less than five minutes after Snape arrived. "Oh good! You're here. I was hoping we could continue the lessons today. Frankly, I think five lessons isn't enough. I'm hoping you can be here every day this week."

"That, I fear, is not possible. Let's just take this lesson business one day at a time and see how you progress. Who are you going up against, anyway?"

The question seemed to confuse her. "I really don't know yet," she finally said. "They'll tell me after I complete my training."

\emph{Which means you probably aren't going out into the field at all. You probably have a nice, safe desk job, and the field assignment is a ploy to convince me that lessons are necessary.} "Wait there a few minutes and I'll be with you."

The session started with a review of the previous day's moves, then progressed to holds that used the opponent's own weight and movement against him. One week was definitely not enough time to teach the more advanced moves, but the simpler ones could be covered. Especially since it appeared that Miss Vaughn had excellent muscle control and coordination.

The instruction of necessity involved considerable physical contact. Snape had first to disarm or throw Vaughn, then he had to show her the holds to use on him and have her practice the throwing. She inevitably turned each move into one with more contact than was needed, and clearly derived pleasure from teasing and flirting with him.

They came to one move where he feigned an attack, and she was to use his forward momentum to pull him past her and trip him. Instead, she pulled him forward and then blocked him with her own body. They stood for that instant, face to face, touching, and then she kissed him.

Snape stood very still, his heartbeat throbbing in his ears, and after a moment she stepped back. "What's wrong?" she demanded. "Don't you like me?"

"I hardly know you."

"Why should that get in the way? Or maybe you just don't like girls."

Refusing to be baited, Snape crossed his arms over his chest and regarded her thoughtfully. "Maybe I don't like pushy, aggressive girls."

"I can be sweet and soft."

"Quite the chameleon, aren't you?"

"Come on, why do we have to be so serious?" She reached forward and pulled his arms away from his chest, placing them behind her at the small of her back. Suddenly, Snape wanted her to kiss him again, and he ceased thinking or caring about Bella. She leaned forward, and their lips touched.

Intensely aware of his own tension, Snape gingerly tried returning some of the pressure against his mouth. Her eyes widened in surprise, and she stepped back to stare at him in wonder.

"You've never done this before! Cousin Bella said you lived like a monk, but I didn't{\el} Oh, I'm sorry. I didn't mean to embarrass you."

Snape turned away, staring down at his hands. "Bella put you up to this, didn't she, Miss Vaughn?"

"No. Of course not. I mean{\el} Well, yes she did. She said you needed to relax, a little recreation. She says the way you live isn't healthy for a young man. And I agree with her. I do. I mean at first I thought it would be more like a job, but most of the men I meet, well they just turn into octopuses around me, all hands, you know. But you—it was fun being the aggressive one, you seemed kind of nice, in a straight-laced, reserved kind of way. Look, I'm sorry. But you know, maybe I could give you some lessons."

"What would you teach me?"

"How to kiss. You don't want the next woman to know you're an amateur, do you?" She scooted around to the other side of him so that they faced each other again. "It's easy, really. Just put your arms around my back, and lean forward a bit. Relax the muscles in your face and open your mouth just a little. And when I press my mouth against yours, you just push back at exactly the same pressure."

It was like following instructions in a training course, but this time the kiss was far more satisfactory and lasted longer. "There," she said as they separated, "that was much better."

"You know, Miss Vaughn, I could get used to this very easily."

She had silver laughter. "Silly, you just kissed me. You can stop being formal. Call me Phina. It's what my friends call me."

The lessons, both kinds, continued for another hour. At the end, Phina was far more proficient at her studies than Snape was at his. "That's all right," Phina assured him. "You just need more practice."

Back at Hogwarts, Snape tried to figure out where all of this was going. \emph{I'm using her for my own ends. But then she's using me for her own ends. As long as we're honest about that, is it so bad?}

Monday was Potter's occlumency lesson, but on Tuesday he could go back to Croydon. Snape found himself looking forward to the next lesson with some pleasure.

It was a trick of fate that Snape's lessons with Phina were the only bright spot in his life that week. Potter continued to be dismally inept in his occlumency, Hagrid continued to be bruised and insist nothing was wrong, Dumbledore remained aloof from everything to keep Umbridge from exploding, while Umbridge continued her harassment of both Hagrid and Trelawney. Trelawney had started visiting the staff room at odd moments, a place she'd never frequented before, clearly a little worse for having monitored the quality of the sherry in the kitchens. Hogwarts was running out of pleasant places to congregate with one's colleagues.

But in Croydon all was light and sunshine. Phina was bright, cheerful, amusing, gentle and, it turned out, a great listener. She was an apt and attentive pupil who always practiced her homework assignments (so different from Potter), but she never pushed or made demands on Snape. He was actually beginning to enjoy her company, despite the fact that academics were not her strong point.

"Have you ever gone to a play," Snape asked on Thursday, their fourth session.

"Is that like Quidditch?" was Phina's immediate response.

"No, it's something muggles do. A group of them performs a story in front of an audience. Plays can be quite entertaining. No magic allowed, though."

"Odd thought. Do you mean we'd pretend to be muggles? What would I wear?" She was dressed in midnight blue robes, rather plainly cut, almost like an evening coat.

"Without the hat, you'd be fine as you are. A little overdressed maybe, but no one would really notice."

"All right. Sounds like fun."

It took but a moment to leave headquarters, then apparate to Hammersmith, where \emph{`Macbeth'} was playing at the Lyric Theatre. Phina was giggling.

"What's so funny?"

"Cousin Bella was watching. She's going to be so pleased that I got you to go off alone with me. I don't think I'll tell her we were watching a play."

"What will you tell her?"

"I'll make up something. I always do."

"About me?"

"Not yet. I haven't known you long enough. You're not the first one she's set me after, you know."

Snape thought about this for a moment. "She's only been out of Azkaban for a month, and you would have been what? eleven? when she was sent there. Either you started young, or she works very fast."

"All right, I lied. But I'll still make something up."

The production was somewhat \emph{avant garde}, but lost none of its dramatic impact. Phina giggled over the witch scenes, but followed Lady Macbeth with fascination. "They're like Cousin Bella and Rodolphus," she whispered. Then, as Macbeth waded deeper into murder, and Lady Macbeth sank into madness, she gripped Snape's arm, practically holding her breath until it was all over.

"They never lie," Phina announced as the two exited the theatre into a chilly London night.

"I beg your pardon?"

"Muggle witches. They never lie. Macbeth was told the truth. He was fooled by the truth. He assumed he understood the prophecies, but he didn't. That's what destroyed him."

The shock of what she said ran through Snape like a jolt of electricity. Six months earlier, he himself had been thinking the same thing about Dumbledore and a prophetic truth that had lured the Dark Lord to his doom. Was Dumbledore like Shakespeare's witches?

First escorting Phina back to Croydon, Snape then apparated to Hogsmeade, where the gate opened for him without bringing Dumbledore down. Which was just as well, since Snape needed time to think. \emph{Banquo said it: But 'tis strange: and oftentimes, to win us to our harm, the instruments of darkness tell us truths, win us with honest trifles, to betray us. Did Dumbledore trick me into betraying the Dark Lord?}

Even though it was late, Snape did not go to sleep. Instead he started making notes to help him order his thoughts.

% FIX

\emph{\textbf{Question 1:} Did Dumbledore know that Trelawney was going to make a prophecy?}

\emph{Probably not. Prophetic utterances are neither forecast nor predictable. Trelawney herself would not know. At least, not if it was a true prophecy. The possibility exists that the scene was staged for my benefit, though I would not normally credit Trelawney with acting ability.}

\emph{\textbf{Task:} Find a way to demonstrate that Trelawney's prediction was the real thing.}

\emph{\textbf{Question 2:} Did Dumbledore arrange for me to come to Hogsmeade that day to overhear the prophecy?}

\emph{The Dark Lord sent me to interview for a position. What prompted him to do that at exactly that time? Might Dumbledore have found a way to arrange it? And how would Dumbledore have known that I would overhear the prophecy? No one suggested that I follow him upstairs to listen outside a closed door.}

\emph{\textbf{Task:} Find out why the Dark Lord decided to send me to Hogsmeade that day.}

\emph{\textbf{Question 3:} Assuming that the prophecy was real and my overhearing it a coincidence, why then did Dumbledore let me leave and return to the Dark Lord with that information?}

\emph{If I had just received a prophecy about a child who would destroy the Dark Lord, I would want to do everything possible to protect that child until he was old enough to fight. Letting the Dark Lord know could result in the child's death. So why didn't Dumbledore use a memory spell on me? Didn't he suspect that I was a Death Eater?}

\emph{\textbf{Task:} Find out what, if anything, Trelawney knows about the aftermath of the prophecy incident. (Does she even know she prophesied?)}

Tired now, Snape went to bed. He spent the next couple of days trying to work out how he could gather the information he wanted.

\subsection{Saturday, February 10, 1996} % \emph{[JKR calls it Valentine's Day, but Valentine's Day that year was the following Wednesday.]}
% FIX

Saturday was calm and peaceful, primarily because three-quarters of the students were in Hogsmeade, and Snape did not have supervisory duties with them. It was only at supper time, with the students back on the grounds and his normal weekly trip to Croydon about to start, that Snape realized the questions about Dumbledore's actions had chased all thoughts of Phina Vaughn from his head.

\emph{I suppose that's evidence that I'm not really infatuated with her. I feel better about a casual{\el} friendship? than about a relationship.}

The one who met Snape at the door in Croydon, however, was Lucius Malfoy.

"What are you doing? Are you trying to stab me in the back?"

"Why Malfoy{\el} whatever are you talking about?"

"Word is Bella dangled a skirt in front of you and you're dancing to her tune now."

"Dancing. That might be fun. The word is wrong. Oh, yes, Bella is trying, and I'm not running away, but I haven't spoken to Bella in a week, and no one has talked to me about what `side' I'm on."

Malfoy glared, stepped back, and then began to relax a little. "So you didn't fall straight into Bella's arms?"

"Now there's an unpleasant image. No, you can rest easy. Bella doesn't own me. Of course, you don't own me either."

"Wouldn't dream of it. All I want is you, safe and sound in your laboratory and not working against me."

"It sounds like we agree on something."

Malfoy and Snape went back to their respective stations, where Snape checked the potions that were brewing. The Polyjuice Potion was almost ready, and he estimated a Wednesday return to bottle it and start testing it. He wasn't as concerned about the Veritaserum, since he already had what he wanted. He brewed it now only in case the Dark Lord inquired.

A little later Phina came for what was supposed to be her last lesson.

"You seem distant today," she complained after a warm-up and the first few throws. "Are you tired of me already."

"You've learned what you were supposed to. Technically we're almost done."

"That's it? One week and a couple of kisses, and we're through?"

"I hardly see a future for us. You're going out into the field."

She was silent for a moment. "What if I wasn't going into the field?"

"Are you authorized to tell me that?"

"It's just a `what if.' Can't you hypothesize?"

Snape registered that Phina's vocabulary seemed to have miraculously expanded. "All right, hypothetically speaking, if you weren't going out into the field, I might invite you to dinner. But I can't until you're authorized to tell me what you're really doing. Until then, we have no future, and it's useless trying to pretend we do."

Phina dropped the subject, but her face wore a strangely calculating expression throughout the rest of the self-defense lesson.

Before apparating back to Hogwarts, Snape rechecked his potions and realized the Polyjuice would be ready earlier than he had calculated. \emph{Looks like I'm coming back on Monday. I'll have to reschedule with Potter.}

That was the action of a moment the next day. Outside the Great Hall just before a leisurely Sunday breakfast, Snape pulled Potter aside and informed him that Remedial Potions lessons were being switched to Wednesdays. Potter seemed relieved at the postponement, but otherwise said nothing.

Croydon was back to normal on Monday, and Snape saw neither Phina nor Malfoy. He checked his potions, bottling small amounts to take back to Hogwarts and test, then got ready to leave. On the way out he saw Avery heading for the interview room.

"What brings you to London? I thought you were in Lincoln?" Snape said in greeting.

"Special assignment. Got to hurry now. He's waiting."

Snape delayed, hoping to hear something, but eventually returned to Hogwarts none the wiser as to what Avery was doing in London.

Wednesday's occlumency lesson with Potter was dismal as usual. Even young Dursley's pranks had become boring, since the muggle boy had no creativity whatsoever, his mind centering entirely on punching, stealing, predictable name calling, and toilets. Potter kept insisting that he was trying to clear his mind of emotions, but Snape knew he was lying. They were going nowhere.


