% A Difference in the Family: The Snape Chronicles (Rannaro)
% Yes, That Is My Job

\chapter{Flirting with Enemies}

They spoke in quiet voices, even though it was late and the castle slept, even though Snape's office was too far from any other room for them to be heard.

"{\el}and if he finds a way to sneak out, Bella's people may snatch him, despite the certainty of being seen. On the other hand, if he stays at Hogwarts they'll try Lucius's plan, and I don't know what that is, but it involves luring Potter off the grounds."

"So we keep him here. I shall alert everyone I can. Do not fret, Severus. We shall succeed in this."

"Can we trust Potter not to do something horribly stupid? He is the most unpredictable factor in all of this."

Dumbledore sighed. "The day will come, Severus, when you will understand that there is good in the boy. And a glimmer of intelligence. He knows that now is not the time to be breaking rules."

There was a pause heavy with portent, and then Dumbledore spoke again. "Now tell me about this girl."

"What girl?"

"Do you love her?"

"I presume you're asking if I'm going to bring her to Hogwarts and introduce her to you."

"No, I am asking if you love her."

"I'm not even sure what that means."

Dumbledore leaned back in his chair. "You are serious, it would seem."

"Yes, I am. People throw that word around like a weapon. They use it when they're talking about a whole range of emotions, some of them contradictory. Does it mean affection, tenderness, infatuation, the desire to protect, the desire to dominate, possessiveness, jealousy{\el}? People use it to cajole, coerce, and manipulate, but I've never seen anything I could separate out and point to and say `this is love.' I don't think it exists." Snape had risen and was standing by the fireplace, his back to Dumbledore.

"What about Lily?"

"What about Lily."

"She sacrificed herself for her child. Is not that love?"

"Maternal instinct. Rabbits have it. Wolves have it. Mother birds will risk their lives for their young and then not even recognize them the following season. How is `love' different?"

"You are bitter tonight. Something happened."

"I wanted something. I almost had it. It was taken away. There was no love involved. Satisfied?"

"No, but I shall have to be content with it." Dumbledore rose, too, and laid a hand on Snape's shoulder. "You have a right to some joy in life. I hope you find it."

After Dumbledore was gone, Snape stood for a while staring down at the cold stone of the fireplace. He was thinking of his father. Toby had needed Eileen. Needed her presence in his life, her care, her validation of his existence. Needed her so much that when she died, he died too.

\emph{Is that love? The desperate need that supersedes and overwhelms the need for life itself? Who would want that? I can understand sacrifice. I can understand being given a choice and choosing to die so that something else can live. But even that isn't love. Sometimes it's pride, or fear of consequences, or guilt, or most likely a strong sense of duty{\el}}

The question didn't go away as Snape mechanically readied himself for bed, though it did permute into a wide-ranging variety of different aspects. Restless, sleepless nights were becoming habitual.

The week passed quickly, with end of term and Easter break coming up, the need to both court and avoid Umbridge, the mind-throbbing frustration of Potter's occlumency lesson—and suddenly it was Saturday and the Hogsmeade excursion.

Potter stayed on the grounds, his friends keeping him company rather than go to Hogsmeade. From returning Slytherins, Snape learned that there'd been several strangers in the village, strangers that seemed to be waiting for something. Snape had a reasonable idea of what he would find when he apparated that evening to Croydon.

No one was waiting to usher him into the interview chamber. Snape breathed a sigh of relief, then went up to his laboratory where the next batches of Polyjuice Potion and Veritaserum were in their final stages of preparation. A half hour later, Malfoy came into the room looking immensely pleased with himself.

"Your information was perfect. She had eight people up there from three different offices. Not a hair of Potter did they see. Ha! Poor Bella. She's still with the Dark Lord, answering for her sins. He is not happy with her, oh no. He'll want to speak with you when he's finished with her."

"Why?"

"To find out how much damage was done. I wouldn't mind being a fly on the wall right now, I will admit."

It came sooner than Malfoy expected, for a Death Eater stuck his head in then and said simply, "He wants you. Both of you."

They hurried down to the chamber, where a groggy Bella was still on her knees before the Dark Lord. Snape did not feel the least sympathy for her.

"You will report to us now."

"Potter did not go to Hogsmeade. Returning students were commenting on the unusual presence of a number of strangers. Although they were curious, no one seems to have connected it to us."

"Then this careless servant has been more fortunate than she deserves. Presumptuous one, you will beg this servant's forgiveness for having impugned the quality of his information to us."

Bella twisted around, her eyes slightly glazed from her punishment. "You were right, Snape," she forced out in a rasping voice. "Forgive me for questioning you. You were right, and I was wrong."

Red eyes turned on Snape. "You will respond."

The assessment of possible future needs took only a second. "There's nothing for me to forgive. You serve our Lord loyally and advise him to the best of your ability. If you err in your advice, it is for him to forgive you, not me."

Malfoy did not look at all pleased, but the Dark Lord nodded. "You say well. Malfoy, you will remain and give me your counsel. Potions master, you will leave and take this erring one with you."

Snape bent and helped Bella to her feet, supporting her out of the chamber. Steering her into the same room they'd been in before with Macnair, he sat her at the table and went to find Rodolphus, who was waiting nervously in the staff lounge, forbidden to come nearer while his wife was being disciplined. Snape quickly prepared a cup of tea and followed Rodolphus down.

The tea was hot and soothing, and though Bella shuddered a little as she drank it, she seemed to feel better. Shakily she recounted her experience to Rodolphus, who looked up at Snape.

"It was good of you to say what you did. I owe you one."

"I was looking out for myself."

"It was still good of you."

A half hour later, Phina walked into the laboratory. "Cousin Bella sent me," she said, grinning provocatively. "She wants to make it up to you for all the things she said last week. I'm a peace offering."

"Have you ever come here on your own initiative?"

"Yes. Last week. That's why cousin Bella was so angry. I'm not supposed to like you, just get you all hot and bothered."

"Nice image."

"I thought so," said Phina, closing the laboratory door. "Are you all hot and bothered?"

"Hot and bothered? Not really. More cool and collected. I get like that when heads are rolling." Snape continued checking his potions, not wanting to face Phina at the moment.

Phina pouted a little. "Cousin Bella will be fine. The Dark Lord really does value her, you know."

"Did he tell you that, or is that Bella's version."

"You can tell just watching him. He gets all gooey-eyed{\el} All right, it's Cousin Bella's version."

"I'd be careful how you speak of the Dark Lord. That came very close to ridicule. If I thought you meant it, I'd have to report you."

"You're serious!"

"Always where my life and health are concerned. Has Bella mentioned why the Dark Lord holds her in such high regard?"

"Oh, yes. It's because out of all of you, she was the only one who refused to believe he was dead and gone. She got herself thrown into Azkaban not for what she did before, but for searching for him when everyone else believed he'd been destroyed. She never gave up hoping for his return. Never. He prizes that, and he prizes her."

"Surely that includes Rodolphus and Rabastan."

"No, because she had to work hard to convince them. The only other one was Barty Crouch. He never gave up hope either, not until he was finally captured anyway. They say he cracked then. Bella never cracked. And she's still here. Don't you want to get all hot and bothered?"

"Not really. The ease with which we were interrupted last time rather puts a damper on things. It might have been much more embarrassing."

"That's all right," Phina laughed. "We don't have to go that direction. There are other fun things." Behind him, Snape sensed a wand being drawn and items being conjured. He turned to find the cushions and pillows arranged on the floor again. Phina stepped near and began undoing buttons. "First we have to get this jacket thing off of you."

The frock coat off, Phina insisted Snape lie down on the cushions on his stomach, hands under his head. Caution warred with curiosity in his mind, but curiosity had caution beat by a good four to one, so he did as he was told. "Normally I prefer bare skin," she said, "but it can be just as good through the shirt."

Snape hardly had time to wonder what `it' was when she positioned her hands, fingers on his shoulders and thumbs at the base of his neck, and began to massage his back. Gently at first, then with increasing pressure, she worked her way to the small of his back, up the rib cage, to his neck, shoulders and upper arms, where the cycle began again, kneading and stroking the tension out of muscles that had been tight for years. It was wonderful. Snape had no idea how much his back ached until Phina began to make it feel better.

The rhythm and pressure were hypnotic. Snape found himself drifting, unthinking and uncaring, his eyes closed, aware only of the purely physical relaxation that spread through him, wanting it never to stop{\el}

His eyes opened lazily to candlelit darkness and the softness of pillows. Phina lay beside him on the cushions, staring at the ceiling. At his movement she turned to look at him. "I wish I could say that was the first time anyone ever fell asleep on me," she said, "but actually it happens a lot. How do you feel?"

"Fantastic. Where did you learn to do that?"

"I don't know. It seems to come naturally. Now, put your arms around me. We're just going to enjoy the moment." Which Snape did, losing himself in the warmth and peace, in the scent of her skin and hair, until reality impinged on his content.

"What time is it?" he asked suddenly.

"Nearly midnight."

An hour later than usual. Snape started to rise, but she pulled him down, and they kissed for the first and only time that night. Then he stood and slipped on his coat, helped her to her feet, and together they removed the evidence of the evening. After locking the laboratory, he bade her good night, and left to return to Hogwarts, wishing for the first time that he could stay at Croydon instead.

Even though there was only one chess board out in the Great Hall the next day, two games of chess were being played.

\emph{You were late in last night.}

\emph{Not inordinately so, I don't think.}

\emph{Any trouble?}

\emph{Not what I would call trouble. Not for me at any rate. Bella had some explaining to do.}

\emph{Until midnight?} "Check."

\emph{Oh no. Bella was out and about long before that.} "You forgot to cover that bishop. Serious mistake."

\emph{So you were being interrogated until midnight?}

\emph{No. I was in the laboratory by eight.}

\emph{What happened in the laboratory? An explosion?}

\emph{Define explosion.}

Dumbledore paused, his hand on an unmoved knight, peering at Snape over the rim of his glasses. \emph{Do not be cheeky. Your young lady was there, no?}

\emph{Well if you already knew that, why were you beating around the bush?}

\emph{And?}

\emph{And what? Why didn't I ever realize before what a voyeur you are?}

\emph{Here I am, shepherding my young son through his first dating{\el}}

\emph{I'm not that young!} "Check!"

\emph{Compared to me, you are an infant.} "Capture your rook and check to you."

"How dare you think that because of your age you have a right to{\el}" Snape paused, suddenly realizing he was speaking out loud. "{\el}show off how good you are at chess. I swear you deliberately made me think you were an amateur just so you could beat me now."

"We all have our little secrets, Severus. I am not as clever as you seem to think I am, but then again, neither are you."

The game ended five minutes later when Dumbledore mated Snape's king.

Monday started out normally. There were the usual problems in Potions class, and the usual end of term hysterics, but on the whole, normal was the operative word. In fact, Snape might not have known anything was amiss until the following morning had not he and Sprout lingered in the Great Hall after supper discussing the early summer plantings.

The evening was well advanced when Snape and Sprout left the Hall, both towards their respective rooms. At once, as if a floodgate opened, a flurry of Hufflepuff students came clattering down the staircase, ignoring the two professors entirely, and heading for their own dormitories as if bloodhounds were after them.

"Whoa!" yelled Sprout, but none of them heeded. A boy at the tail end of the stream was easier to catch. "Zacharias, what is the meaning of this!"

The boy paused only a moment. "Sorry, Professor. Umbridge{\el} caught us{\el} Potter{\el} hide from her{\el} Dumbledore{\el} gotta go{\el}" and he vanished into the kitchen passage with the others.

Sprout hurried after him and was gone for many minutes while Snape waited in the entrance hall. When she returned, she was almost running. "They've been organizing a combat group behind Umbridge's back," she gasped to Snape. "They called themselves Dumbledore's Army."

Both professors sprinted for the stairs, Snape ahead of Sprout only because he was younger and had longer legs. As they reached the floor with the gargoyle statue and the spiral staircase, they narrowly avoided running into a group of people. A group of impressive people headed by the Minister of Magic himself, Cornelius Fudge. Umbridge was with them, as was Kingsley Shacklebolt, who saw Snape and gave him a short, decisive shake of the head, then looked quickly away. Behind them McGonagall was descending the spiral stairs with Potter as Umbridge turned to the group from the Ministry.

"Shall we discuss this grave matter in my offices, gentlemen?" she said, and they nodded agreement and followed her.

McGonagall sent Potter up to Gryffindor house and was about to leave when the two professors hissed her over to them. "Oh, it's terrible!" she exclaimed in unconcealed anguish. "They caught the students organizing an army, and now Dumbledore's fled from Hogwarts!"

\sbreak

Malfoy and Snape left the interview chamber together.

"Very timely news. He was wondering what was going on. He thought old Dumbledore looked a bit combative."

Snape felt his heart nearly skip a beat. "The Dark Lord can see Dumbledore?" he asked, trying to keep his voice sounding casual.

"From time to time. It takes quite an effort, and the Potter boy's mind has to be in the right receptive condition. It only lasts a moment, so it's nowhere as useful as the dream connection, but he hopes to be able to improve the link with practice."

It was cold. The corridor was very cold. \emph{Maybe it's me. Maybe I'm cold.} "Can he hear what they're saying?"

"Not yet, but he's working on it. Can you stay? I'd like to go over a few things with you."

"No, not tonight. I have to get back before Umbridge notices I'm gone. I'm not sure how easy it'll be to get out anymore. The Dark Lord may wish to be reminded of that."

"All right. Good luck at Hogwarts."

Snape made it in good time. It was another hour before Umbridge was finished and the Minister left. Then he was summoned rather brusquely to her office. She did not invite him to sit.

"I think I commented to you before that you seem to spend quite a bit of time away from Hogwarts, Professor."

"No more than I'm entitled to. Less than many of the others."

"Yes, but you come back at very late hours."

"Eleven o'clock can hardly be considered late, certainly not if one goes to the theater."

"You must have the spells for opening and closing the gates, though, to be able to move around so freely."

"No, I don't. The Headmaster always lets me in. Occasionally the Deputy Headmistress." Snape knew exactly where this conversation was going. McGonagall must have refused to turn over the spells.

"I see. Well, until this whole matter of chain of command can be resolved once and for all, your excursions may be somewhat restricted." She waited, but Snape saw no reason to comment. "There is another matter I wish to discuss with you. All potions kept for the needs of the school in general are in your custody, no?"

"Except for medical stores. Madam Pomfrey has those."

"I understand you are required to stock a small supply of Veritaserum."

"Yes, Ma'am. Very small. One vial."

"Bring it to me."

"I can't do that, Ma'am. The regulations are very strict. I can only give it to the Headmaster or to the Deputy Headmistress."

"But I'm the High Inquisitor."

"There is no mention of the title `High Inquisitor' in the regulations. If I were to give the Veritaserum to you, I would be breaking the law."

Umbridge tapped her fingers on the desk, clearly debating whether to push the issue or not. At last she said, "That's all. You may go now."

Snape sped down to his office and unlocked the cabinet with the controlled stock in it. The little vial of Veritaserum with its Ministry registration label was near the front, full except for three drops that had been used on Barty Crouch the year before. Quickly Snape got another vial and emptied the Veritaserum into it, stoppered it, and hid it in the wardrobe in his bedroom. Then he rinsed out and dried the official vial.

The little flask of false Veritaserum that he'd made in Croydon was in another cabinet, unlabeled and anonymous. Carefully, Snape filled the official vial with the false serum, full except for three drops. The deception was undetectable. Snape replaced the vial in its cabinet and locked it securely.

The next morning, Educational Decree Number Twenty-eight was posted, announcing that Dolores Jane Umbridge, High Inquisitor, was now also Headmistress of Hogwarts School of Witchcraft and Wizardry. One of the new headmistress's first actions was to summon her potions master and demand the vial of Veritaserum that was kept locked in his office in case of need. Snape went down into the dungeons and returned at once with the vial.

It was interesting to Snape to note that Umbridge was still working out of the Dark Arts office. It seemed that the headmaster's office refused to recognize the authority of the Ministry of Magic. As far as the office was concerned, Dumbledore was still headmaster. \emph{How would one go about punishing a piece of architecture for insubordination?}

McGonagall was not in the mood to be kind at breakfast.

"I see you caved in very quickly. And here I had just convinced myself that you'd developed a spine."

"Now, now. You were nasty to me last year, too, and then you had to backtrack and apologize."

"You mean all is not what it seems in faeryland?"

"All is not what our beloved and fearless leader wishes it to be."

"So counsel me. What should I do if offered a cup of tea on the second floor?"

"Accept it graciously and drink it politely. It cannot harm you. Just don't give in to sudden impulses unless you actually desire to make enemies."

"Mendaciuserum?"

"More like Fraudiserum, but you have the right idea."

"You wicked, wicked boy. And to think there was a time when I was naive enough to consider you trustworthy."

"It depends on who's trusting and what it's worth."

"There. I have no illusions left."

Word passed quickly among the teachers that no one was going to be overwhelmed by a sudden passion to confess all, and they relaxed and tried to formulate plans.

As it turned out, the one called before Umbridge was Potter. Were it not for the fact that the whole school was in danger, Snape would have been quite content to have Potter forced to spill his soul to Umbridge. It served the evil little prima donna right for causing all the trouble in the first place.

\emph{He knew she was looking for any excuse to take over the school, so he hands her one on a silver platter. I still believe Dumbledore should have told him the Dark Lord wants to kidnap him, but I honestly don't think it would have made any difference. He's too conceited to imagine that an idea of his might have a flaw, so he'd have gone right on with his meetings, and the result would've been the same. I'd wager even now Potter doesn't realize he forced Dumbledore out. If he thinks of it at all, which he probably doesn't, he probably believes that Dumbledore took the blame out of affection, because precious Harry Potter is so unique and lovable that the whole world must want to sacrifice themselves for his benefit. Just like his father. Just like Black. Now it's Potter against Umbridge, and I don't know which I'd prefer to have lose, since they both so deeply deserve it.}

As it turned out, Potter told Umbridge nothing, though whether this was as a result of the false Veritaserum or not, Snape never learned. The day was full of surprises, most of which could be credited to Fred and George Weasley, and Umbridge was kept busy all day answering the desperate calls of teachers with firework dragons in their classrooms, none of whom seemed to be the slightest bit upset with either Fred or George.

A select group of Slytherin students had begun working for Umbridge, headed by Draco Malfoy and several other children of Death Eaters. Snape was reasonably sure that Lucius had approved the action, since it would help deflect attention from the work of their parents and keep Umbridge focused on Hogwarts as the center of her problems. The only headache for Snape in all of this was that one of his Chasers had vanished, and he had Slytherin students combing the castle for any trace of the boy.

Umbridge didn't seem to think the disappearance of a student was worth her notice, and refused to be of assistance.

By Wednesday, things seemed to have returned to a semblance of normality. Classes were conducted as usual, and it turned out that most of the fireworks had been used up in one day, so that there was no repeat of the previous day's chaos. The only thing that spoiled Snape's peace was the thought of occlumency lessons with Potter.

Snape hadn't seen Potter since Dumbledore's departure. Every time he thought of Potter, he became furious and ill at the same time. Part of it was the sheer arrogance of the boy, combined with a talent for committing stupid actions unparalleled in Snape's experience. \emph{How could he not have realized that Umbridge would be watching him more closely than anyone? Wasn't it Potter's account of the return of the Dark Lord that had brought Umbridge to Hogwarts in the first place? Wasn't it Potter's interview that had suddenly upped the stakes? How could he disregard his own role in the events of the entire year!}

That was the furious part. The ill part was waiting for the mark to itch or burn, wondering how he would be able to depart Hogwarts unseen on either a scheduled or unscheduled trip to Croydon. And how he might return undetected. Dumbledore had been sheltered up in his office, but McGonagall's rooms were near Umbridge's, and Umbridge's wrath was now directed against McGonagall for withholding precisely the information that allowed Snape to enter and leave the grounds. \emph{Which makes me feel like a paramecium on a glass slide under Umbridge's microscope.}

Too tense to even go to supper, Snape waited for Potter in his dungeon offices. The time for the lesson came, but no Potter. Snape began to place the dangerous memories into the pensieve anyway. \emph{Thank goodness Dumbledore allowed me to keep it down here instead of carrying it up to him every evening. If it had been in his office Monday, I'd have no way of hiding these.}

The door opened. Snape recognized Potter's step without turning around. "You're late, Potter," he said, trying to keep his anger out of his voice. Then he turned to face the boy. "So. Have you been practicing?"

"Yes," answered Potter, in a blatant lie. The boy's own dislike was palpable.

"Well, we'll soon find out, won't we? Wand out, Potter." Snape was now making a serious effort to control his own feelings, the very sight of Potter rendering that discipline more difficult than usual. \emph{Control yourself, Severus}. "On the count of three then. One{\el} two{\el}"

The office door was opened suddenly by an agitated Malfoy, whose shocked look told that the last thing he expected was to find Snape and Potter together, wands drawn. Snape lowered his own wand quickly and tucked it away. \emph{Death Eater child and Inquisitorial Squad. That's all I need. To have both Umbridge and his father know that there is some special arrangement between Potter and me.}

"Professor Snape, sir{\el} oh{\el} sorry," was all Malfoy managed to say.

"It's all right, Draco. Potter is here for a little Remedial Potions." It was the cover story already planned and used before, but Snape realized from Malfoy's gloating expression that Potter was going to be more than a little teased about it. He was unconcerned about Potter's feelings. Quite the contrary.

"I didn't know," was all Malfoy said.

"Well, Draco, what is it?"

"It's Professor Umbridge, sir{\el} she needs your help. They've found Montague, sir. He's turned up jammed inside a toilet on the fourth floor."

"How did he get in there?" \emph{And how did Umbridge get involved? I thought she didn't care about Montague.}

"I don't know, sir, he's a bit confused{\el}"

"Very well, very well{\el}" Getting a student out of a toilet might take some time, presuming that Umbridge did not want the plumbing damaged. "Potter, we shall resume this lesson tomorrow evening instead."

Malfoy trailing behind, Snape hurried out of his office and up the stairs to the fourth floor boy's lavatory. He assumed that Potter had left the office at the same time.

It took longer than expected to extract Montague from his predicament since, from what they could glean from the dazed Montague himself, he had apparated into the toilet and was therefore wedged in as tightly as was possible. A series of enlarging (for the pipe) and shrinking (for Montague) spells eventually effected his release, and Snape helped get him downstairs to Madam Pomfrey before returning to his office.

Potter was still there. Potter was not only still there, he was deeply immersed in a pensieve memory, oblivious to the fact that Snape had reentered the room. Snape felt a moment of stunned shock as his mind registered that Potter had no scruples about violating another person's privacy, and then anger and panic began to surge in him as the full import of what was happening struck. The memories he'd worked so hard to conceal from the Dark Lord were now freely available for discovery and review, floating around in Potter's undisciplined mind, accessible by dream connection, waking intrusion, or face-to-face legilimency.

Edging nearer, Snape was able to see which memory Potter had found. It was the Levicorpus incident, with Lily standing bravely in front of the whole school, challenging James Potter in his defense. One glimpse of that memory and a decade and a half of concealment from the Dark Lord would be shattered.

Furious, Snape gripped Potter's arm and dragged him from the pensieve. "So," he hissed between clenched teeth, "been enjoying yourself, Potter?"

Potter struggled to release his arm from Snape's grip. "N-no{\el}" he stammered, though whether from fear or shame was hard to tell.

\emph{Not that this boy will ever feel shame. He has no concept of what that is, not Mr.~Perfect Potter. Just like his father.} "Amusing man, your father, wasn't he?"

"I{\el} didn't{\el}"

Snape realized then that he was shaking Potter, and pushed the boy away from him. Potter staggered and fell to the floor. "You will not repeat what you saw to anybody!" Suddenly Snape saw a vision of students passing gossip through the different houses{\el} and someone telling Draco{\el} and Draco telling Lucius{\el} and Lucius telling{\el}

"No, no, of course I w{\el}" Potter was saying, but Snape wasn't listening.

"Get out!" he screamed at the retreating Potter. "Get out! I don't want to see you in this office ever again!"

There was a jar in his hand, and Snape hurled it at the door, narrowly missing the boy, who was out into the corridor and racing toward the stairs and Gryffindor house. It didn't end there for Snape, though. Two more jars followed, shattering on the threshold, at which point some instinct of survival kicked in and the next spun a hundred thirty-five degrees and smashed into the back of the fireplace.

Two dozen beakers, flasks, cruets, vials, bottles, crocks, and other vessels were flung savagely against the hearthstones, until Snape finally collapsed exhausted next to his desk. It did no good. Ultimately nothing could do any good, for the danger was not within Snape's control. The danger was within Potter's control, and that was no control at all. All Snape could do was wait until the moment when Potter revealed his secrets to the Dark Lord, and then all the plotting and scheming would be over.

There was only one thing that might have helped at that moment, and that was to talk to Dumbledore, but Dumbledore wasn't there. Dumbledore was gone, perhaps forever, because of Potter. Potter with his total disregard for the rights, the interests, the needs of anyone but himself.

At that moment of blank despair, Snape hated Harry Potter with every fiber of his being.

Then the Easter break began, and the school emptied. Only the fifth and seventh years stayed in any numbers, studying madly for their OWL and NEWT exams.

On Saturday morning, Snape slid into the chair next to McGonagall and said in a more or less conversational manner, "Going anywhere during the holidays?" then dropped his voice and added, "I need out tonight."

"I hadn't thought about it. There's so much that needs to be looked after here. Timing, of course, is key. Do you have a particular time when you like to go?"

"Generally at the beginning of the break," Snape said, then bit off a piece of sausage, murmuring `seven' at the same time. "But I usually come back early so I can spend the last week preparing for the third term." Another bite of sausage covered the word `eleven.'

"Well this break you may have to forgo a vacation." McGonagall's voice dipped as she added `done.' "We have a duty to ensure that our classes do not suffer from the turbulence of the events that surround them. This coming term in particular we must work hard to see that the standards of Hogwarts do not fall."—`Be punctual,' was the last whispered exchange.

Snape snuck out of the castle at six thirty, just to be sure that nothing delayed him too much on his way to the gate. By ten to seven he was crouched behind the bushes that lined the path up the hill, waiting for the percussive snap in the air that said the shields were lowered. When that came, he slipped through the gate then, out of curiosity, waited to see how much time McGonagall gave him. The thrum of the closing spell shivered through him a bare five minutes later.

\emph{That woman really believes in punctuality. I can't be late tonight, or she'll lock me out for the rest of the weekend.} It was not the most comforting thought as Snape apparated to Croydon.

Things had gotten to the point that Snape expected to be met at the entrance to headquarters and directed to the interview chamber. That the messenger was a lower-level operative was the good news. \emph{Unless the Dark Lord is becoming more subtle in his management techniques.}

Malfoy joined Snape in the basement corridor, and they went in together. The Dark Lord was direct and to the point. "Has Potter dreamed of entering farther into the Department of Mysteries?"

"I do not know, Lord. Potter does not discuss his dreams with me. The one he might have spoken with was Dumbledore, but now Dumbledore is gone from Hogwarts, that line of communication is closed."

There was silence, and then the Dark Lord spoke again. "The good news was not entirely to our benefit. Our plans would progress more swiftly if we were certain that the boy receives the images in their entirety when they are sent. When was it that the boy first knew he had entered and encountered the many doors?"

"The Wednesday before you reprimanded me for my slowness in reporting."

"You are sure."

"Yes, I am, Lord. I was near him when it happened and{\el} he commented on it."

"And yet that was many days after the initial projection."

"Lord," interjected Malfoy, "perhaps all you must do is project the same image multiple times. He'll think it's a recurring dream. Slow certain steps will lead us to our goal more safely than quick, uncertain ones."

"You see, Potions master, Malfoy counsels caution while Bella Lestrange counsels precipitate action. What do you counsel?"

It wasn't a question Snape wanted to answer. He was more than content to have Lucius and Bella be the Dark Lord's advisors. Let them take the blame when something didn't work. He took a deep breath. "Make wise use of the time we have, Lord. Right now we are undetected and may operate at leisure. This is the time to move carefully and be sure that every step is successful. Later we may not have the luxury of abundant time. Then, we'll have to move quickly and take our chances."

"You have a talent for taking both sides, Potions master. This amuses me. Take care that you always do it for my sake, and not for your own."

"Yes, Lord. That is always my intent, Lord."

Malfoy and Snape left together, each heading for his own work area after they left the basement area.

Phina didn't come to the laboratory that evening, and Snape found that he missed her presence. He even worried a little that something might have happened to her. The rest of the evening was quiet and restful, however, until Snape left headquarters to apparate back to Hogwarts. That was when he was accosted by a ghostly image in the form of a phoenix. "The Order needs you tonight," it said in Dumbledore's voice, and then vanished.

\emph{Wonderful. McGonagall will have the gates open in ten minutes and keep them open for five. What are the chances I can get back to Hogwarts before I'm locked out? And how do I explain that to Umbridge tomorrow morning? This had better be important.}

Snape apparated at once to Grimmauld Place, where Lupin opened the door. "Dumbledore's already here," he said, "but this isn't a full meeting. Basically he wants to talk to you."

Dumbledore was in the kitchen talking to Black when Lupin and Snape walked in. Snape immediately stepped to one side, away from the table, and waited quietly. Black leaned back in his chair and regarded Snape thoughtfully, a small, wry smile on his lips.

After a moment, Dumbledore spoke. "I hope you will excuse me, Sirius, but I have asked Severus here because I need to confer with him for a moment. This was, unfortunately, the only convenient place as it is the only location available that is protected by a Fidelius Charm."

"I understand completely. Don't worry, Professor, I know that if you think something is necessary, then it probably is. I have no objection to your using the premises when you need them." He continued watching Snape, but didn't move.

"Oh dear," sighed Dumbledore, "I fear we have an awkward situation. Is there perhaps somewhere where I might speak privately with Severus?"

"Don't worry about disturbing me; the conversation won't bother me at all."

"I was thinking perhaps somewhere out of the general common areas{\el}"

"So you're telling me to get lost in my own house."

"I would not have put it quite so harshly."

"There's no sense offering you refreshments, is there?"

"That won't be necessary."

Black rose and sauntered out of the kitchen, Lupin accompanying him. Dumbledore gestured toward the empty chair. "Please sit down, Severus. I need to ask you about Hogwarts, and especially about Harry."

Snape sat down where Dumbledore indicated. Three days earlier he'd wanted to discuss this with Dumbledore. Now he wasn't sure.

"Umbridge first," Dumbledore prompted.

"She's officially headmistress now. Decree Twenty-eight. She has two major opponents: McGonagall—who won't give her the security codes to the grounds, and your office—which won't let her in. Both students and teachers are giving her a hard time, the students playing practical jokes, and the teachers holding an Italian postal strike."

Dumbledore had started chuckling at the mention of McGonagall's name. Now he laughed out loud. "You are going to have to explain that one to me, Severus. None of our teachers is Italian."

"The government workers of many countries are forbidden by law to strike. When the employees of the Italian postal service failed to negotiate what they considered a decent contract, which included updating their job descriptions, they began actually enforcing every postal law and regulation still on the books. Postal service ground to a halt in a matter of days since no one had ever bothered to revoke hundred-year-old regulations. Needless to say, they won."

"So my staff is doing only what Umbridge says they can do, and making her do all the rest?"

"That's it in a nutshell."

"And how is McGonagall holding up? And Hagrid? And Trelawney?"

"McGonagall loves a fight. She'll circle the wagons and{\el}" Snape stopped at Dumbledore's quizzical look, then elaborated. "American slang. A reference to pioneer wagon trains when attacked by hostile Indians. You really do need to become familiar with other cultures, sir. Well, she'll dig trenches and settle in for the long war. Hagrid{\el} I don't know what's happening with Hagrid. It's like he's beating himself up. I can't think of anything else that could cause such extensive damage. But you knew that already. It hasn't changed. Trelawney hides in her tower. She's safe. Umbridge has forgotten she exists."

"And Harry."

"Has still not learned occlumency."

"There. Something has happened. Tell me about it."

Snape looked at his hands, then at the table, the walls, the ceiling{\el} everywhere but at Dumbledore. "There's been an incident. Do you recall you offered me the use of your pensieve?"

"Potter looked in it and saw one of your memories? That was an inappropriate action."

"No. It isn't just that. When it comes to that, I shouldn't have trusted in Potter's sense of decency. I should have made him step out of my office first and then locked the door on him. That was my own naïveté, my own stupidity. But the Dark Lord is actively trying to influence his dreams, is actively in contact with his brain every day. Not only that, I learned only after you `left' that the Dark Lord has been able to look through Potter's eyes while Potter is awake. He saw you that day and knew you were angry about something. I don't care what Macnair thinks, I don't want to be tortured. I don't want to die. I have to stay out of Potter's surface thoughts and below the Dark Lord's radar. I told Potter never to come to my office again."

"I am deeply disturbed to hear that, Severus. It is vitally important that the boy learns to block Riddle's access to his mind. You really must resume the lessons. It is imperative."

"Do you mean that Potter's ability to use occlumency is more important than my life{\el} than whatever the Dark Lord will do to me between now and the day I die? If you can look me in the eyes and tell me that is so, then I'll resume the lessons."

"You trust me that much?"

"I do."

"'If you can look into the seeds of time, and say which grain will grow and which will not, speak then unto me.' The problem is, I do not know which of my three boys will blossom in importance and become the chief player in this drama."

"Three boys?"

"Yes. Tom, Dick, and Harry." At the sight of Snape's raised eyebrows, Dumbledore smiled. "We do have your full name in our files, you know, though you might prefer `Tom, Russ, and Harry.' Still, there are three, and I do not yet know which is the most important of them."

"So are you saying I shouldn't resume the lessons?"

"I am saying that I do not wish to lock you into a position that you feel you cannot escape from should the need arise."

"That's just a fancy way of saying you don't want to be responsible for the consequences of a decision you make."

"I suppose, in a way, that is a fair comment."

The two sat quietly for some minutes as Snape debated whether this was an appropriate time to bring up another matter that he'd been considering for some months.

"Sir, may I ask you a question? It is related to the matter at hand."

"That has a portentous sound. Very well, yes, you may."

"Whose idea and whose decision was it to make Peter Pettigrew the Secret Keeper for the house in Godric's Hollow?"

Dumbledore's surprise at this question was revealed only by the length of time it took him to respond. "The decision was James's."

"Only James's?"

"I believe so. Yes."

"Not Lily's. And whose idea was it?"

"I don't believe I should answer that question."

"That answers it. The person is still alive. That means it was Sirius Black's idea. Black tried to weasel out of a dangerous position by giving it to someone even weaker. Sterling character, that one."

"It was true that Sirius would have been suspected at once. There was some merit to the idea of giving the position to someone no one would suspect."

"Really? I'd say any one of the three friends would have been suspect. Why not go back to the original idea of making you the Secret Keeper? Even better, why not make James or Lily the Secret Keeper? Then the Secret Keeper would always be in the place protected by the charm."

"I cannot answer your question. I did not become aware of the switch until two years ago. What does this have to do with Harry's occlumency lessons?"

"I think James's arrogance killed Lily. I think he was so convinced that his own plans were flawless that he never made provisions for unexpected contingencies. I think he honestly believed that his foolhardiness and emotional intensity were more than a match for simple mind games, but that his own undisciplined mind was pouring out to the Dark Lord the exact location of his wife and child even as he died trying to protect them. I think that Potter is just like his father, and he will betray every one of his friends and colleagues to their dooms, never abandoning, even at the moment of his own death, the belief that he must have chosen the right path because his motives were sincere. I don't want to be one of the sacrificial victims."

"So you blame James for Lily's death."

"Among others."

"Am I on your list of suspects?"

"I don't believe I should answer that question."

"Ah. Now I must bring the conversation back to its beginning. Do you think it possible for you to resume Potter's occlumency lessons?"

"No. Enough damage has been done. My person and my position have already been placed in jeopardy, and I don't wish to make the odds any worse. It might be different if you could guarantee to me that Potter is essential while I am expendable, but you can't or won't do that. So far as I can tell, we have a stalemate."


