% A Difference in the Family: The Snape Chronicles (Rannaro)
% The First Year

\chapter{Settling In}

"I think," Lily said with a contented sigh, "that broomsticks are the most wonderful thing in the world, don't you?"

Russ made a face, wrinkling his nose in distaste, but didn't respond.

Lily rolled onto her stomach on the soft autumn leaves. "It's just so wonderful to be able to go up into the air like a bird and look down on everything, and feel the breeze in your hair{\el} Pretty soon I'll be able to steer the broom better and maybe go faster. Don't you just adore it?"

This time Lily noticed Russ's silence. She reached out and smacked him on the nose with the seed head of the blade of dry grass she was holding. "Aren't you enjoying flying on a broom, Severus?"

"I suppose," Russ replied with some dignity, "that I might enjoy it if I ever got around to doing it. As it is, I have other things to occupy my time."

"You take flying lessons, too! It's just like riding a bicycle. Almost."

The great thing about talking to Lily was not having to pretend. "I never had a bicycle," Russ said, "I never rode one."

"Do you mean," Lily giggled, "that you never got your broom up in air?"

"Up?" said Russ. "Are you saying they're supposed to go up? If I'd known that{\el} Silly teachers never tell you anything."

Lily was laughing now, and tossed a handful of leaves in Russ's hair. "I bet I could get you to fly on a broomstick," she boasted.

It turned out that Lily, in fact, had a plan. They agreed to meet again after supper, and she went running back to the Castle. Russ waited a few minutes, then strolled to his usual place at the foot of the cliff. He'd only been there half an hour when it started to rain. With a sigh, Russ got up and went into the Castle. He spent the rest of the day studying in the library.

It continued raining all afternoon. Unable to take food from the table to eat outside, Russ stayed in the Great Hall, which also gave him the opportunity to see what Lily wanted him to do, since she couldn't go to their usual meeting place either. A few moments after she left the hall, he rose and left, too.

Lily was at the end of the classroom corridor opposite the Hall. As soon as Russ appeared, she slipped down another corridor to the right, one that led to the fountain courtyard. Russ followed her out. There were a few students there, but it was easy to stand off to one side of the large courtyard and talk, basically unobserved.

"Tomorrow morning," Lily said, "go down to the Quidditch stadium. They keep the school brooms stabled there. Nobody 'll be there that early, and we can practice with the brooms for a while. I'm going to get you airborne!"

Russ returned to Slytherin for the night feeling more light hearted than usual. He was accosted in the passage to the dormitory by Aloysius. "What were you doing talking to a Gryffindor?" Aloysius said.

"Potions{\el} homework," Russ replied.

"Why doesn't she ask her own house mates?"

"Gryffindors are{\el} stupid at potions."

"She's a mudblood, isn't she?"

Russ had never heard the word before, but it didn't sound complimentary. "I don't know," seemed the most neutral reply. "I didn't{\el} ask."

"Blood calls to blood, I guess. You might try to rise out of the ooze, you know. Part of you is supposed to be a wizard."

Russ didn't answer. Instead, he went inside the dorm and to his bed to get ready for the night. What Aloysius said didn't really bother him. On the day wizards walked on the moon, he'd start giving them credit for being almost equal to muggles. Not before.

The next morning after breakfast, Russ snuck down to the Quidditch stadium. Lily 'd already opened the broom lockers where the ordinary brooms were kept and selected a couple she knew to be docile and easy to manage. Neither of them responded to Russ's command of "Up!"

Lily stepped in and ordered a broom to rise. With the broom already in the air, Russ mounted and, on Lily's instructions, kicked into the air. For a moment, Russ had the heady feeling of hovering a few feet from the ground, the best he'd ever managed. Then the broom began to buck and tossed him onto the grass.

"That's an unusual dismounting technique," Lily said, laughing heartily. Russ smiled as she coaxed him back onto the broom. They were there for an hour, but with Lily's help Russ was finally able to get a broom up on command, and to mount and hover. He had a fine sense of accomplishment that day.

\subsection{Thursday, September 30, 1970 (four days before the full moon)}

On the morning of the last day of September, Russ received his first owl message. The tawny owl was already up in the rafters waiting when he walked in to get his breakfast, and it swooped down and deposited a blue envelope in front of him before he started picking up food. Then it returned immediately to the rafters to wait for a reply.

A glance down the table showed Russ that his dormitory mates had seen the exchange and were curious. There was even the vague sense that getting an owl had brought him up a notch in their estimation. It made him more a wizard and less a muggle.

By this time Russ had gotten used to pumpkin juice, so he took a glass, put a couple of slices of bacon between two pieces of toast, and went back to the dormitory to read his letter.

\begin{writtenNote}

\letterAddress{Dear Russ,}

How are you doing in school? We all miss you and think about you. Your mum wants to know which house you were sorted into, and whether you're doing what you're supposed to in classes. Your dad had a spate of trouble getting used to you not being around, but he's back to normal now. He says you better not come home a `college pudding' whatever that means.

This grandmother has finished drying her winter herbs and harvesting the last of the annuals. The pumpkins you planted at the start of the season are huge and could bring you a bit of pocket money, maybe even a sickle or two from the local `community.' I'll let you know. The other one says you have to keep the second half of April free for sixteen. Destination Descartes. Crew Young, Mattingly, and Duke. Muggle talk, I suppose.

Don't think you have to answer right away. Your mum says Nelson can wait in the owlery a day or two while you write. We're all looking forward to getting your letter. And Mrs.~Hanson is back and sends her love.

\letterClosing{Nana}

\end{writtenNote}

Russ returned to the Great Hall and called Nelson. Once again he noted that the others were watching. He told Nelson to join the rest in the owlery while he thought about his answer, then watched as the owl flew away.

All during the day, Russ used his spare time to compose an answer to Nana. There were things that weren't so good, but he didn't want anyone to worry, especially his mother.

\begin{writtenNote}

\letterAddress{Dear Nana,}

Thank you for your letter. I got it at breakfast this morning. The news about the pumpkins is great. My Herbology class is my best, and Professor Mullein says he knows you. Do you know him? Tell mum she was right about that Potions teacher. He don't know half. I've been doing everything she told me.

I got into Slytherin like she thought I would. It's down in the spooky old dungeons and there aren't any windows. I don't stay there much. Tell dad a couple of the boys tried to mess with me, but I gave them what-for, and they don't mess with me any more. I won't be no pudding.

Classes keep me busy, but I get outside, too. There's mountains here, and a forest, and a lake. The castle is really big. I was scared at first but just for a day or two. Now I started exploring and I've got my bearings. I'm going to know it better than anybody.

Tell Gra I copy. I got a telescope in Astronomy class and everything is `go' for April.

I miss you all, but don't worry. Things are fine here. Tell Mrs.~Hanson I miss her, too.

\letterClosing{Russ}

\end{writtenNote}

Later that afternoon, Russ climbed up to the owlery and found Nelson. He gave the owl a treat he'd saved from lunch, and sent it back home to Nana with his letter.

The next morning in Transfiguration, the Ravenclaw students had some interesting news. The headmaster himself had come into their first morning class, which was Astronomy lecture with Gryffindor, to see how they all were doing and make sure they were settling in well. He watched them make star charts for the polar region, and they showed him how they set up their telescopes. He even talked with a couple of students personally.

"It was scary at first," said Patience Ferguson. "He's so tall and it's like he sees everything. But he was nice, too. I thought he really wanted to be sure we were getting on all right. He says he's going to visit all the first year classes this month."

"Is he coming here?" Mitchell asked.

"I don't think so. Not today, anyway. I think he went to Dark Arts with Hufflepuff."

Russ thought about this information for a couple of minutes, but it didn't worry him. He turned his full attention to trying to transform a pin into a paper clip.

The first of Russ's classes to be visited by Dumbledore was Flying, that same Friday afternoon. Flying lessons only lasted for a month, after which it was assumed that first year students who wanted to continue on broomsticks could practice by themselves with the school brooms. Students who didn't want to continue didn't have to.

Professor Dumbledore arrived halfway through the lesson, but from some of the things he said to the students, Russ got the feeling he'd been watching from a window. He talked first to the Ravenclaws who were really good on their brooms, and to the Slytherins who were pretty good. He encouraged them to try out for Quidditch in their second year because the school could always use good players. He'd noticed some of their moves, and thought they were team quality.

Russ was now with the small group of students who could rise and descend on their brooms, but little else. There was one more lesson, but after that he was quitting brooms entirely. Even Lily's encouragement would never make him really like the experience. Mercifully, the headmaster paid no attention to the less than brilliant. It would have been mortifying to be singled out for notice because of ineptitude.

Dumbledore was enlightened so far by what he'd learned in the different classes. Young Black of Gryffindor, for example, was a definite mischief maker, and would need an eye kept on him. Three of his dorm mates—Lupin, Pettigrew, and Wintergreen—were overawed by him and perhaps a little frightened. The fourth, Potter, seemed to have already become a Black follower. There was a moment when Dumbledore worried that this boy, too, might be another Tom Riddle, but Black's skills were more physical than magical, and he was too open to be a plotter as Riddle had been.

Another good thing was that in Slytherin there had been no indication of teasing or bullying when the children went out with their brooms for the flying lesson. The more proficient students had gathered for their next instructions while the less adept had started a review, but there was no exchange of words or gestures, no offensive or defensive body language, to express any kind of ill feeling. An excellent sign.

It was beginning to look as if Hagrid was right, and whatever problem there was had been dealt with by the boys themselves.

The next observation was Monday morning Potions with Gryffindor and Slytherin together. Dumbledore intentionally delayed his arrival until twenty minutes into the class, then was able to stand in the doorway for another ten minutes unnoticed by anyone while he watched the activity.

Slughorn was on the Gryffindor side of the room showing a group of girls how to shred the suckers from octopus tentacles. Other students were scraping soot from lamp chimneys or squeezing juice from marshberries. It looked like a writing potion, Duplicating Ink, that could be written on one page of parchment then, when the page was divided, reproduce the exact text on each part in slightly reduced size.

From his great height, Dumbledore looked down across the room onto the surfaces of the cauldrons. Most of the students were still in the preparation stage, but one cauldron shimmered with iridescent purple, a perfect Duplicating Ink. The pale pointed face of its maker regarded the creation with some pride.

Then, as Dumbledore watched, Master Snape took a vial of octopus ink from his robes and added exactly six drops. A quick stir, and the mixture had changed to dull black. It was now a perfectly serviceable ink, but not the Duplicating Ink it was meant to be.

Slughorn looked up. "Headmaster! I didn't see you. Welcome to my class. Come in, look at what the students are doing."

"With pleasure, Professor Slughorn. I see the students are quite industrious. Some have already reached the brewing stage, and one has even finished."

"Ah, yes. Sometimes I wish he wouldn't go so fast. He gets careless. Now look at this. Not what he's supposed to be making at all."

"It looks like there's a bit too much octopus ink," Dumbledore said. He watched carefully, but the Snape boy had dropped his gaze modestly at their approach—or maybe it was because he knew he'd been caught.

"Octopus ink? I don't think so. Suckers, yes, but there's no ink in this one." Slughorn looked around the table. "No, no ink."

"A mistake then," said Dumbledore, smiling slightly. He glanced around at the Slytherin boys with the distinct feeling that they also knew more about the altered potion than Slughorn did, but didn't want to say anything. The feeling of foreboding returned.

"Perhaps, since he has plenty of time, Master Snape would like to try making his potion again. I remember having a bit of trouble with it myself when I was younger."

Under Dumbledore's gaze, Master Snape remade his potion, and Dumbledore was well aware that all of the Slytherin students were paying surreptitious attention. Once again the perfect, shining purple filled the cauldron, where no octopus ink tainted its purity.

"Wonderful!" cried Slughorn. "It's good to see you can make a potion. Now you have to try to do it when no one's watching."

Black eyes flickered up to Dumbledore's face and down again, though they did not meet the headmaster's own.

As soon as the lesson was over, Lily rushed out of the Potions class ahead of everyone, but then realized she'd left her quill and notebook behind and darted back in. In her haste, she bumped into Russ, murmured an apology, and was gone. Russ found himself holding a tiny piece of paper that said Trees. Dinner.

The afternoon seemed to drag, but finally it was dinner time. Russ grabbed some bread and fruit from the Slytherin table and went quickly to the meeting place. Lily was already there and wasted no time.

"He saw you!" she exclaimed even before he was safely under the shielding shade. "He knows what you did to the potion. How could you be so careless?"

"I{\el} didn't see him. If I'd{\el} seen him, I wouldn't have{\el} done it."

"Do you think he'll report you? Do you think he'll tell the Ministry and have you expelled?"

"I{\el} don't know."

"He can't do that," Lily insisted. "You're my best friend here. You're the one who prepared me for Hogwarts so that now I'm getting good marks in all my classes, so now I even understand what they're talking about and don't have to ask stupid questions. You made me fit in. They can't expel you! I'll go to Professor Dumbledore myself{\el}"

"No." Russ's flat negative stopped Lily cold. "We can't do that. My dad{\el} can't know you're my friend. Your dad can't know I'm your{\el} friend. Slytherin and Gryffindor can't know either. I'll do my{\el} best with Professor Dumbledore, but you have to stay out of it."

Lily agreed, and they returned to their separate dormitories. Russ's dorm mates eyed him speculatively as he prepared for the night, but said nothing.

There were in all sixteen classes to observe: two each for Astronomy, Charms, Flying, Herbology, Potions, and Transfiguration, and four for Defense against the Dark Arts. Dumbledore did not visit Binns's classes since there would have been little point. What he saw confirmed two major worries—both Sirius Black and Severus Snape were of concern, but for very different reasons.

Black was self-confident, arrogant, sure of the validity of his own opinions and willing to enforce them. He had the air of a bully, though he did not yet seem to have bullied anyone, and he lacked any sense of the immorality of practical jokes. He enjoyed laughing at, rather than with, others. On the plus side, he seemed to enjoy laughing at himself as well, as long as the experience was not too embarrassing. Black harvested followers the way other students gathered in grades and awards. The more students looked up to him, the better he felt.

Snape, on the other hand, was quiet and self-effacing. He seemed not to care for the opinion of others, scorned notice or approval, and avoided social contact. And yet this boy was possessed not only of an understanding of witchcraft that many adults would envy, he had that strange, indefinable quality of being remote, alien, that none of the others had.

So different, so opposite, so great a potential problem each in his own right, so separately unlike that other problem, Tom Riddle—Dumbledore did not want to create a greater problem by distressing either boy, and yet he wanted a better grasp of what he held in his hands. He arranged appointments with all the first years, sandwiching Black and Snape into the middle of the general crowd.

The interview with Black was all fire and passion. This was a rebel, not merely discarding the views of his pureblood family, but renouncing them with the fervor of a religious convert decrying his old faith as heresy. Dumbledore came away from it with a firm understanding of why the Hat had placed young Sirius in Gryffindor, and more at ease with the boy's place in the future of the wizarding world.

Now Snape stood in Dumbledore's office, mute, ill at ease, waiting for questions to respond to, volunteering nothing. There was something in his self-conscious stance, the awkward placement of his hands at his sides, the slightly hunched shoulders and the defensive downward tilt of his head as he watched a spot on the floor four feet ahead of him that suddenly reminded Dumbledore of Eileen. He was his mother's son.

"How are your classes, Master Snape? Are you having any problems."

"No, sir. They're{\el} fine, sir."

"And Slytherin house? Are you settling in well?"

"Yes, sir."

"I notice you do not eat much in the Great Hall. Is there a problem there?"

"No, sir." The silence stretched out, compelling the boy to continue. "Too{\el} many people," he added, then stopped.

"Do you mean that you feel uncomfortable because the Hall is too crowded?"

"Yes, sir."

It was, Dumbledore thought, like pulling teeth. This was not liking speaking to Tom Riddle. Tom would not have stood so shyly, or answered so shortly, or stuttered. \emph{I wonder now if the problem is that he has never had friends his own age. Or any friends at all, for that matter. If that is the case, then Hogwarts must be an intimidating place. And trying to force the issue might only make it worse.}

"Thank you, Master Snape. I hope your time at Hogwarts is pleasant and profitable. If you ever have anything you wish to talk with me about, do not hesitate."

"Yes, sir. Thank{\el} you, sir," and the boy was gone.

Russ scuttled quickly down the spiral staircase, relieved that the ordeal was over. He found Dumbledore terribly frightening—so tall, with his long beard and long hands, and the piercing blue eyes that could probably steal every thought in Russ's head if he wanted to. Russ wanted desperately not to be noticed by the headmaster, and was unnerved by the knowledge that Dumbledore was aware that he did not eat in the Great Hall.

The seventh floor was the natural abode of Gryffindor and Ravenclaw. A Slytherin student ought not to be there alone, and so Russ scurried for the nearest staircase. It took him to the fifth floor and a long corridor leading to the stairs downward. Here, blessedly, there was no one, and Russ continued on to the library where he hid at a table in a corner, behind a large book.

There he stayed until dinner time, when another momentous decision loomed. Should he avoid the Great Hall altogether and miss supper, or go and take food away with him, or go and eat in the Hall? It was a question of which action would cause the headmaster to notice him the least. With a sigh, Russ left the library and headed for the Great Hall.

He saw Mitchell in the entrance hall, and walked in behind him. For lack of a better plan, he stayed near Mitchell, picked up a small plate and start putting bits of food on it.

"Where do you go with that?" Mitchell said next to him.

Russ had started at the voice, but quickly recovered. "Out," he replied.

"Why don't we just sit here. I want to ask you something."

At the teachers' table, Dumbledore watched. It was a good time to have someone to talk to. "Right," Russ said.

They didn't sit at the very end, for that had been taken over by a rough group of fifth years, but space not too far up the table was usually relatively clear. The two boys sat next to each other on a bench, and Mitchell heaped his plate. The were a study in contrasts, the big sandy-haired athlete and his small, dark companion.

"Why don't you eat more? You'd grow some if you did." Mitchell bit into a forkful of Yorkshire pudding.

"No. I'm naturally{\el} small."

"Why? Are your mom and your dad small?"

Russ thought about this for a moment. Neither his mum nor his dad was small, but he'd grown up being told his size was natural. Now he wondered, too. "No, just me," he answered.

"Well I'm just naturally big. My uncle has me down for a beater or a keeper if Chudley'll take me. I'd rather be a chaser, but I don't have the build." He paused. "You don't know anything about Quidditch, do you?"

"It's a{\el} game." Russ shrugged.

"Do you have to always talk like that?"

"Like{\el} what?"

"Like th{\el} th{\el} this."

Russ stopped eating his dinner and was silent.

Mitchell pretended to ignore him for a moment, then relented. "Look, I'm sorry. It's just I was sure it was an act."

"Why?"

"'Cause you didn't talk like that when you were facing Aaron down. You talked really good then."

"That was{\el} different. Aaron is{\el} dangerous."

Mitchell chewed a bit more, then turned suddenly and made a hideous face at Russ. "There," he said, "now I'm dangerous, too, and you can talk straight."

"It doesn't{\el} work like that," Russ said, but he was almost smiling.

"So, you're Sev?" Mitchell asked later in the dormitory.

"Severus," Russ said firmly. He wanted no undue familiarity from people potentially set on him as spies, however nice they might seem.

"Doesn't matter," Mitchell said. "They say only the first years go by given names. Everybody else uses last names. So by next year we'll be Edison and Snape anyway. I kind of like it. Sounds more grown up."

That suited Russ fine. He didn't want anyone using his own name but his family. Outsiders could use Severus, but Snape was even better. Less personal. Less of an intrusion into his own world.

Aloysius Mulciber came in then. Mitchell went out into the common room, and Russ went to his bed where he pulled a library book from his footlocker.

"Studying your hexes?" Aloysius asked from his own bed where he was laying out robes for the next day.

"Don't need to{\el} study that," Russ replied after a moment's hesitation.

"Why? Your mum already teach you all of that?"

Russ thought of the spells his mother had taught him—Expelliarmus, Stupefy, Protego{\el}—and of the trouble they could get into if the Ministry discovered she'd taught adult spells to a child. "No," he said.

"Where'd you learn them?"

"Didn't."

"Somebody had to teach you those spells. Didn't Mullein say something about a grandmother?"

"No."

"I'm sure he did. But my dad says healers and potions brewers aren't usually good at curses. Who else do you know?"

"Nobody."

"Suit yourself." Aloysius devoted his attention to his robes and the way they were folded over the chair. Then, "You caught old Dumbledore's attention the other day, didn't you? That wasn't a good idea."

"Why?"

"Dumbledore's looking for reasons to slap Slytherin down. Ask any of the older students. You were cheating. He saw that. Now we're in trouble."

Getting others into trouble was definitely the wrong way to be noticed. "I{\el} didn't do{\el} anything wrong."

"I'll admit," said Aloysius, "most people would cheat to get higher marks. Cheating to get lower marks is strange. He was watching you at dinner. You'd better be careful."

"I{\el} will."

Aloysius left Russ alone then. No one bothered him for the rest of the evening, though Evan and Aaron kept glancing at him when they came in to go to bed. Russ lay awake that night wondering how things had conspired to make him so unpleasantly noticed when he'd tried so hard to do what his mum wanted.

After that, Russ began to notice things himself, mostly in the common room. The fifth year prefect, Rabastan, had a younger brother named Rodolphus. They seemed to be good friends with the third year student who'd threatened Russ in the lavatory. His name was Kenneth Avery. The three of them were always talking to Aloysius, Evan, and Aaron. They also got into long, earnest conversations with other students, but only when the other prefects weren't around. If Lucius Malfoy walked into the common room, they would leave whoever they were talking to and start doing something like homework.

That was when Russ also started to notice the phrase, `You know{\el}' It was used to refer to shared information that the Lestranges, Avery, Aloysius, Evan, and Aaron understood but didn't want to say. It was used in sentences like, `My dad has to go this weekend to{\el} you know,' or `We got instructions from{\el} you know.' They used it a lot, and with the exception of Malfoy, they didn't seem to care who heard them.

It was all very mysterious. Russ stayed out of the dorm room and the common room as much as possible. He didn't want to be noticed by anyone any more.

In the middle of October, the weather suddenly became quite cold, so that Lily and Russ couldn't meet out by the trees on the weekend of the sixteenth and seventeenth, nor on the following weekend. It was only a minor problem for Lily, who spent the time with the girls in her dorm or studying, but for Russ it was a depressing reminder of how important his weekly talks with Lily were. He hated the fact that the hills of Hogwarts were colder than the moors of Pendle.

Back in Lancashire, Russ had his parents to talk to. In fact, their company was more important than Lily's, and little routine things like cribbage with his dad or helping his mum in the kitchen were that crumb of daily human contact he needed. Meetings with Lily had been extra. Now meetings with Lily were all he had since he couldn't talk to his dorm mates. He started spending more time in the dorm, sitting on his bed studying, and once even squeezed into an isolated corner of the common room where he could at least listen to the voices of the others and not feel so alone.

It was in those two weeks that Russ learned that the Lestranges, Avery, Aloysius, and Evan were trying to get some of the others to join something. One of the people they were always talking to was Aaron, who seemed to be wavering. At first they were also interested in a dark-haired girl in third year, but stopped talking to her near the end of October. Rumor had it that her older sister 'd married a muggle, and she was no longer acceptable. Russ sympathized with her.

On the last Saturday in October, the day before Halloween, at midmorning, the school suddenly emptied. Russ was surprised at how quiet the Great Hall was at lunch that day. "What's{\el} happening?" he asked Mitchell, who had quickly become his source of information for the more social aspects of Hogwarts.

"They're going into Hogsmeade, the village outside the gate."

"What's in{\el} Hogsmeade?"

"Lots of things. Shops and places to eat. There's a candy store and a joke shop{\el} It's supposed to be great!"

"Oh," said Russ quietly. It all sounded like it cost money, which meant there was nothing for him to do there. "Are you{\el} going?"

"Can't," replied Mitchell, his mouth full of chicken sandwich. "Have to be third year or older. None of the firsts or seconds can go."

"Oh," said Russ again, but now he felt better. No one would question why he didn't join them because no one would think it strange that he didn't go. Lily caught his eye from the Gryffindor table and opened her hands as if she was reading a book. After lunch, Russ hurried up to the library to meet her.

"There's absolutely no one here!" Lily whispered fiercely after Russ found her in the corner dedicated to Herbology. "The Castle's practically deserted. Wouldn't this be a great time to find a new place to meet when it's cold or rainy?"

"But if we meet inside, we'll be caught."

"Silly, this castle is huge! They don't use even half the rooms. There must be rooms all over that no one ever goes into. Now's our time to find one. We can start on the seventh floor and work our way down."

"No," Russ said immediately. "No Slytherin should ever get caught alone on the seventh floor. It's dangerous. And with a Gryffindor girl, it'd be worse. Gryffindors are mean."

"No we're not! It's Gryffindors who have to be careful about being caught alone in the dungeons. That's what everyone says."

"I've never heard anyone in Slytherin talk about going after Gryffindors, but several of the older students 've been pushed around by Gryffindors. They say Gryffindors prefer fighting to magic."

"There is a lot of pushing and shoving and horseplay in the common room and dorms," Lily admitted, "but it's all in good fun." She studied him for a minute. "Maybe we should stay off the seventh floor. But we'll stay away from the dungeons, too."

They decided to start on the third floor, then left the library separately to meet again in an alcove near the Charms classroom. There were several empty classrooms nearby, but the Charms corridor would have a fair amount of students in it on Saturday and Sunday mornings, so they discarded that idea.

The next possibility was the trophy room but that, with all its glass cabinets, was too exposed. Russ and Lily also checked the armor gallery without finding a convenient place to meet unobserved. They explored more corridors and found a passageway behind a tapestry that led them to yet another corridor. Russ, with his `bearings' and sense of direction, reckoned it wasn't far from the Charms classroom where they'd started.

"Let's try this way," Lily suggested, and led the way to the end, where they found a door that didn't look like a classroom door. The door opened into another corridor, one clearly long disused.

"What's that?" Lily asked, pointing to the flagstone paved floor, her voice puzzled.

"A trapdoor," Russ replied, equally puzzled. \emph{What would a trapdoor be doing here?}

Being children, Russ and Lily naturally tried opening the trapdoor. What they found was a shaft that dropped out of sight into darkness. Russ looked around for a stone or a pebble that he could toss down the shaft, but castles that are not falling into ruins do not have stray stones or pebbles lying around on the floor. So Russ extracted his wand from his sleeve.

"What are you doing?" Lily cried as Russ held the wand out at arm's length.

"Experimenting," Russ replied, and dropped the wand. The two listened for the sound of the wand hitting the bottom, but heard nothing. Russ sighed. \emph{"Accio Wand!"} he commanded, and the wand returned to his hand.

Lily plumped her fists onto her hips. "How did you do that?" she demanded.

"Summoning charm," said Russ.

"That's a fourth year spell!"

"So?"

"So what are you doing, doing fourth year spells?"

"Now you know why my mum's worried about the Ministry."

There was no denying this irrefutable logic, so instead Lily insisted that Russ teach her the spell. They found an empty, abandoned classroom in the trapdoor corridor and spent the next couple of hours working on charms. Russ knew more of them, but Lily caught on faster. He taught her the Accio, the Reparo, and the Expelliarmus. The rest could wait for another day. They agreed that in inclement weather, they would meet in this little out-of-the-way room rather than outside under the trees.

About mid afternoon, Russ and Lily left their new meeting place to return to the library so it would look as if each had spent the day there doing homework. As they reached the Charms room and were about to start up the staircase, they saw Aaron on the landing above them. That was nothing strange except{\el}

Suddenly two masked students jumped out and grabbed Aaron from behind. Aaron started to cry out, but was stopped by a silencing spell. "Think he'll do?" one of the students asked the other.

"Better if he was rounder, but he'll do. Any Slytherin would do."

As Russ and Lily stood rooted, concealed by the angle of the passageway, the two pulled Aaron to the top of the staircase, said the spell \emph{Propulso scalae!}, and pushed him forward. Aaron hit the third step and bounced upwards, then came down again, bouncing each time as his body descended the flight of stairs. Russ, terrified, looked around and saw only a suit of armor. Pushing Lily back further out of sight and swinging his wand, he struck it, and the reverberating sound made the two attackers run from the stairs as fast as they could go.

The coast clear, Russ stepped forward, wand out, and cried, \emph{"Arresto momentum!"} Aaron's downward trajectory stopped, and Russ managed to get him seated on the step so that he wouldn't fall any more.

Lily joined him, her face pale with the horror of what she'd just seen. "That was{\el}" she started, but Russ stopped her.

"I know. Look, you have to get{\el} out of here. If anyone knows we were{\el} together{\el}"

"He'll know." Lily nodded at Aaron.

"I think he's{\el} dazed. Get out now. I'll take{\el} care of this."

Russ waited until he was sure Lily had enough time to get to the library. Then he raced to the hospital wing for help.

"Did you see who they were?" Dumbledore asked, but Aaron shook his head, still too dazed to think properly. They were in the hospital wing with Dumbledore and all the heads of houses later that afternoon. "And you?" Dumbledore said to Russ.

Russ shook his head.

"Are you sure you couldn't see who they were?" the headmaster prodded. "You watched the whole incident."

Russ thought for a moment. "Light{\el} behind them," he said, nervous and more tongue-tied than usual. "They{\el} had{\el} masks." He paused and thought. "Gryffindors," he finished.

"How do you know?" asked Professor McGonagall.

"Borders on{\el} robes. Red and{\el} gold. They wanted a{\el} Slytherin."

"At least we are fortunate," said Dumbledore, "that almost all of the Gryffindor boys were in Hogsmeade. There are only about ten to check and see where they were when this happened."

"I'll get on it right away," said McGonagall, and left the room.

"Are you all right?" Dumbledore asked Russ gently.

"They{\el} didn't get{\el} me."

"No, but you were on your way up there when it happened. If Master Wilkes had not been there, they might have gotten you. Had you thought about that?"

Russ nodded. He'd thought of little else since the attack occurred. The thought of what might have happened to himself was intensely frightening. The headmaster seemed to realize it. The thought of what might have happened to Lily was worse, but that had to be concealed.

"Professor Slughorn," Dumbledore said. "Would you see that this young man gets safely back to Slytherin house? He has had a rather unpleasant day."

Russ followed Slughorn back to the dormitories where he became the center of attention for those back from Hogsmeade. Everyone wanted details on what had happened to Aaron, and suddenly Russ felt himself part of the house, one of the group, for it was Gryffindor that was now the common enemy.

Aaron himself was back in the common room in time to go up to the Great Hall for supper.

Slytherin house went to supper en masse, to show their distrust in the honor of Gryffindor. Third and fourth years stood as bodyguards next to first and second years while the older students acted as perimeter guards. Russ's `protector' was Avery, the student who'd attacked him in the lavatory. It didn't make him feel safer.

Rabastan Lestrange came and stood beside him, whispering in Russ's ear, "Which ones attacked Wilkes?"

"I don't{\el} know. I didn't{\el} see them," Russ replied. "They w{\el} ore masks."

"You heard them, didn't you? If they were first years, you'd know the voices."

Russ couldn't explain to this older house mate that he knew who the Gryffindor attackers were, but couldn't say anything because he didn't want the possibility of involving a Gryffindor girl. He knew it was Black and Potter from the train, and Lily knew it was Black and Potter from the train, but if Russ identified them, then Black and Potter might start watching him, and he wouldn't be able to see Lily anymore.

"I was{\el} too far{\el} away. I couldn't{\el} hear," Russ told the prefect.

Lestrange went away, muttering `dumb half-breed' under his breath.

Because of the situation, Russ was forced to stay and eat supper with his house instead of going off by himself. This gave him the chance to watch as Lily pointedly refused to sit near either Black or Potter and turned away from both of them in distaste. Russ loved watching it, though he fervently hoped the two boys wouldn't deduce anything from Lily's behavior.

Back in the dormitory at the end of the supper, there was a semblance of patching things up with Aaron. "They told me you were the one that chased them off," Aaron said.

"I made{\el} noise, and they{\el} ran."

"How come you didn't fight them?"

"I can't{\el} fight."

"You fought us in the lavatory. A whole bunch of us. How come you didn't make their noses bleed?"

Russ looked at the ground and shrugged. Aaron shrugged too. "Well, thanks anyway. At least you got them to stop." Then Aaron went to his own bed and put out his light.

\subsection{Sunday, October 31, 1971—Halloween (two days before the full moon)}

Sunday was Halloween, and the Great Hall that morning was already festooned with black and orange, with pumpkins, and with silhouette figures of black cats, witches, crescent moons, and broomsticks.

Halloween was an alien holiday to Russ. They'd never celebrated it in his town, and it held no memories for him. For him the great autumn celebration was Bonfire Night when they paraded the Guy and roasted potatoes. This particular Halloween was like being in prison, for the combined students of Slytherin continued to express internal solidarity and external distrust by banding together, and he was not allowed to be alone all day, especially since he'd been the one who'd interrupted the foul deeds of Gryffindor and could therefore be presumed to be a target of retaliation.

The table that evening was loaded with sweets, which Russ didn't want to eat because he knew they'd upset his stomach. He was forced to accept them, however, since for the moment a hefty percentage of Slytherin students were still congratulating him on foiling a Gryffindor plot, and presented offerings of cake, candy, and caramel covered apples.

The being congratulated was nice. The eating sweets all evening had him in the lavatory later throwing up, but this time there was no teasing. Everyone was really quite sympathetic about it.

The next day Nelson came with the monthly message from Nana. Russ took the blue envelope outside to open and read it.

\begin{writtenNote}

\letterAddress{Russ}

I didn't send yesterday because your mum says Halloween is a big thing at your school. Did you enjoy it?

Your mum is concerned about what you said about Slytherin. She says if they give you grief about your dad, you just forget what she said about being nice. They don't deserve it. She hopes you didn't forget how to take care of yourself.

Your dad says he's `pleased as punch' that you gave them what-for. That's what he'd expect from his boy, and he's proud of you. He says you just remember that Nel Tarleton was a featherweight, too, and one lung to boot. He won two titles on pluck and skill, and your dad says you've got the pluck and the skill. You just keep giving them what-for.

This grandmother is the same as always, but misses her assistant brewer. The other one thought your brain might do with a little exercise and sends you a gift.

\letterClosing{Nana}

\end{writtenNote}

Russ took his letter to the lakeside at lunch time to think about it, and by supper he had a reply for Nelson to take back.

\begin{writtenNote}

\letterAddress{Dear Nana,}

Thank you for the letter. Halloween was not so good because some Gryffindors thought they could push us around, but we faced them down. Tell Mum I already remembered what she told me about taking care of myself, and I'm doing it. Things are getting better. And I remember what Dad told me about Nella, so I'm sticking all fifteen rounds.

I made a little mistake about Potions. The headmaster came into class and caught me hiding a good one. I think maybe he knows. But the professor's so thick, I don't think he'll ever catch on, so I'm probably all right.

Thank Gra for the puzzle book. I like the logic ones best. I miss you, too. I'd like to be somewhere I didn't have to botch potions.

\letterClosing{Russ}

\end{writtenNote}

\subsection{Saturday, November 6, 1971}

Slytherin house never did find out who the boys were that attacked Aaron. They were told that the two were identified and punished, but Dumbledore and the heads of houses wanted no retaliatory feud started over the incident and refused to give Aaron or his house mates the names. Since neither Aaron nor Russ could name the attackers, the matter was forced to stop there. Slytherin was not satisfied.

The Saturday after Halloween was the first Quidditch match of the season, and by tradition it was between Slytherin and Gryffindor. Under the circumstances, things were tense, and it was probably a good thing that at breakfast and lunch the two houses were separated by Hufflepuff and Ravenclaw.

Russ met Lily right after breakfast in their meeting room on the third floor, but all she could talk about was Quidditch. For the first time in all their years of friendship, Lily confessed to Russ that she was a devoted fan of the Red Devils of Manchester, and that one of the things she missed most at Hogwarts was football. One of the things that reconciled her to being sorted into Gryffindor, apparently, was that the red and gold of Gryffindor matched the red and yellow of the crest of Manchester United.

When the whole school marched down to the Quidditch pitch for the game, Lily firmly surrounded by other Gryffindor students and clearly enjoying herself, Russ did not go. Instead he slipped into the corridor where the unused classrooms were, snuck into one, and waited until the Castle was empty. Then he scurried out the front doors and down the narrow path on the face of the cliff to the lake side.

It was cold, but otherwise pleasant, the cliff itself shielding Russ from the cheering that rose in the house stands as the game started. Russ had no intention of being in the middle of a crowd of yelling, pushing students, and was quite content alone. He was trying to work out a new spell that would throw things at an attacker from another direction than his own, to make them think he had help. He thought it might come in handy if he was ever attacked as Aaron had been. The two Gryffindor students hadn't been as brave when they thought someone besides Aaron was approaching.

Russ decided to start with stones. He was pretty good at throwing stones, his father having taught him to bag birds and coneys out on the moors. He searched the narrow beach for a good one, the right shape and weight, then looked around for a target.

The beach didn't offer too many good targets, but nearby there was the forest. That might be a place to experiment. Picking up more stones as he went, Russ studied the trees on the forest's edge. Several were about the girth of a human being, and would give him an accurate size to work with.

The first thing he had to do was work out the mass involved. Hefting the stone, he concentrated and cast a levitation spell. Since he was close enough to the stone to focus easily, he didn't bother using his wand. Satisfied with the force he'd need to lift it, he tried the stone to examine the force required to toss it and the trajectory it would follow. With practiced ease, he shot the stone at one of the lower branches of a nearby tree.

"Here! What're ya doing there? Ya hadn't ought t' be throwing stones at birds, ya know!"

Russ wheeled, startled at the gruff voice that had come out of nowhere, and found himself face to face with the monster who'd lifted him into the boat on his first night. Except, of course, he knew the monster's name was Hagrid and that he was the keeper of the grounds.

"I{\el} wasn't," he stammered.

"Wasn't? Sure looked like ya was to me. Wha' cha chucking rocks for if not at birds?"

"Just{\el} throwing one. No{\el} bird."

"That's better. Why ain't ya watching the Quidditch game with yer mates?"

"Don't{\el} want to."

"That don't sound right. All boys want t' watch Quidditch. Didn't yer mum an' dad ever take ya t' a Quidditch game?"

Russ shook his head, this question at least not needing a vocal reply. He let the rest of his carefully gathered stones drop to the ground.

"Oho!" said Hagrid. "More 'n one. You was going huntin' in the forest, then? That's two things. Huntin' birds and goin' into the forest. You oughtn't t' be doing either."

"I{\el} wasn't{\el} hunting."

"Ya look kinda cold. Whyn't ya come with me an' I'll fix ya somewhat warm."

There was no choice. Russ reluctantly followed Hagrid to his hut for a cup of hot tea.

"I don't know where ya got yer ideas from, but that boy ain't nothing like Tom was, with all his smooth talk an' easy answers. Don't know if it's the stutterin' or somethin' else, but he won't hardly open his mouth at all, and he's nervous an' shy t' boot."

"What did you talk about?" Dumbledore asked.

"I talked about Hogwarts an' how was he doing in classes. He didn't hardly say a thing. Drank a little tea. Didn't eat nothing. It ain't natural f'r a boy his age not t' be hungry. No wonder he's knee-high t' a goblin. Was Eileen that solitary?"

"I do not recall what she was like at that age. It is very possible, as she never did have a large number of friends. Perhaps I should ask Professor Mullein about her. If we have more information about the mother, it may give us insight into the son. Thank you, Hagrid, for bringing this information."

"Just like t' be helpful."

The next day Lily could talk about nothing but Quidditch. All during their morning meeting it was snitch this, and quaffle that, and Chasers, and Seekers{\el} It didn't help that Gryffindor had won. Probably the worst thing was having Lily so enthusiastic about her house's victory. If Slytherin had won, Russ would never have exulted over Lily the way she did over him.

It wasn't until Lily was nearly talked out that Russ realized that Lily wasn't exulting over him. She was exulting Gryffindor over Slytherin, and for some reason she didn't connect Russ with Slytherin in this at all. For her, he was like some neutral outsider that she was recounting the exciting moments of the game to. Gryffindor had beaten Slytherin, but that had nothing to do with Lily's friend Russ.

Russ didn't know whether to be pleased or depressed by Lily's attitude. In a way, it was good because she could share with him her excitement over things like Quidditch without worrying about whether or not he agreed with her. Russ rather liked that because it made him more of a friend. On the other hand, it meant that Lily didn't think about the rest of his life, about what it was like to live in Slytherin house, at all. For her, he didn't exist except in their weekly meetings.

That made Russ think about himself and his attitude. Did he think about Lily at all except in terms of their weekly meetings? He realized that he knew almost nothing about her daily life. He started watching her dorm mates, wondering what it was like living with them, thinking about Lily as a whole person and not just his friend.

Russ's encounter with Hagrid didn't stop him from working on new spells. By the end of term in December, his Rixno spells were working well, and he could throw stones, sticks, dirt, water and, with the first fall of snow, snowballs. The only problem was that this was primarily an outdoor spell since he had trouble picking up anything heavy with it, though indoors books were a possibility.

End of term brought a profound change to Hogwarts, since everybody went home for the holidays. Everybody but Russ, that is. Even Lily left, going back to Lancashire to be with her parents and Petunia. They were going to meet her in London and stay there for a few days, then go back to Pendle for Christmas and the New Year.

Everybody but Russ{\el} Well, that was not exactly true. Two fifth year Slytherin girls stayed to study for their OWLs, and there were in all seven other students from Gryffindor, Ravenclaw, and Hufflepuff. Then there were Headmaster Dumbledore, Professors Slughorn, Flitwick, McGonagall, and Mullein, Madam Pince and Madam Deering, Hagrid, and Filch.

On the twenty-second, two days after everyone else had left, Slughorn summoned Russ to his office just before dinner time.

"What's the matter with you, boy?" the Professor asked after Russ shut the door and came to stand in front of his desk. "Are you sick or something?"

It was Russ's second time in the office, the first being for his very short beginning of term interview, and he was decidedly uncomfortable. "No{\el} sir," he replied.

Slughorn stared at him for a moment. "You just remember to be respectful, Master Snape. Now if you're not sick, why aren't you eating?"

"I{\el} am{\el} eating{\el} sir."

This brought another stare, though a more sympathetic one. "Do you always talk like that?"

"Yes{\el} sir."

"Humph. You should speak up more in class. Give it some exercise. That'd take care of it. Now, what and where are you eating, because you're not doing it in the Great Hall, and the headmaster has taken notice. It's rude to avoid us all, especially when we're such a small group."

"Yes{\el} sir."

Slughorn didn't notice that Russ hadn't answered the question. "It's time to go up for supper now, and you're coming with me. You'll sit at the table like a well-behaved young man, you'll eat what's put before you, and you'll speak when spoken to. I won't have the headmaster regard Slytherin house in an unfavorable light. Do you understand?"

"Yes{\el} sir."

Russ meekly followed Slughorn out of the dungeons into the Great Hall. Most of the others were already there, so they were all looking at him, and he blushed with embarrassment.

"He's fine, Albus," Slughorn announced, clapping Russ on the shoulder. "Just wanted to do a little extra studying. I told him all work and no play{\el} So he's happy to join us. Sit here next to me, Master Snape. Fill your plate."

Placed securely at Slughorn's left, Russ had no choice but to obey, and he tentatively took morsels from the less exotic dishes and put them on his plate. Slughorn grunted, then reached across and loaded the plate with more food. "A growing boy needs a good appetite," he said.

Suddenly, Russ understood that Slughorn was like his father. He, Russ, was doing something wrong and, as he always did with his father, he was making Slughorn angry. Now he had to try to do the right thing, or he would make Slughorn angrier and force Slughorn to punish him. He quickly picked up a fork and took a bite of sweet potato pudding.

It was thick with cream and butter, and cloyingly sweet. Russ knew it was going to make him sick, but he had to force himself to eat it to show Slughorn he was being good. He took another bite. Slughorn was in conversation with Mullein now, and had ceased watching, but he would notice if the plate remained full. Reluctantly, Russ took a third bite.

Someone was watching him. Glancing around out of the corners of his eyes, Russ realized that it was Dumbledore. When he looked back at his plate, the sweet potato pudding was gone. Instead there was a manageable amount of plainer food, something that Russ could deal with.

Russ stared at the plate, eyes round with surprise, then shot another sideways glance at Dumbledore. Was it his imagination, or did the headmaster wink at him? Russ didn't dare look again to be sure.

Another mysterious thing about the dinner was that Russ never had to talk. The three times a teacher asked him a question, somehow Dumbledore entered the conversation and turned it away. No one even seemed to notice that Russ had not responded. Beginning to relax, Russ found that he was able to finish his food to the point of satisfying Slughorn. At the earliest possible moment, he excused himself and escaped back to the Slytherin dormitories.

Night in Slytherin house was so far very pleasant with all the boys gone. In fact, Russ had taken advantage of the opportunity to search the house thoroughly on the very first day of the break. Thoroughly was, of course, a relative term. He hadn't touched the beds or belongings of his dorm mates, nor had he entered any of the other dormitories. That wouldn't have been right. That there may or may not have been protective spells was irrelevant. What he had checked were the corridors, the boys' lavatory, and the common room.

He found that he could not identify the springy, translucent material that allowed light to filter through the lake water to the house beneath. He found that there had once, many years earlier, been a fierce fight outside the girls' dormitory farthest from the common room. The jambs and lintel were scarred by burning spells that had come from inside the dorm. He found that the scrolling of the rock surface around the great fireplace was really the marks left by generations of students scratching their initials into the stone, which had been painted over and now appeared part of the decoration, but could still be read as initials up close.

Bathing in the empty lavatory was delicious and decadent, and Russ hoped that every Christmas and Easter break for all of his seven years would be as devoid of other students as this one was. There was no bathroom in his own home, and there was never enough hot water in the sink by the toilet—aside from the fact that hot water cost money—but here at Hogwarts during the break Russ could stretch out his legs and submerge himself, and let the warmth sink into his very bones, with no fear that anyone would ever see his back. The peace it brought him made him want to cry.

This night, for a contented hour, Russ forgot all about Slughorn, Dumbledore, sweet potato pudding, or his home, and luxuriated in the warm water. Then he toweled himself dry, put on his pajamas and bathrobe, and padded barefoot back to the dorm. There he read another of the books he was constantly checking out of the library—this one on vampires—and finally went to sleep.

The next morning Russ was up early, and was almost out the door of Slytherin house into the dungeons before he remembered that Slughorn would be watching him at breakfast. The thought put a brake on his movements, but there was no avoiding the fact that he had to eat breakfast in the Great Hall, so he continued reluctantly on his way.

Only a few of the teachers and two of the students were there ahead of him. Russ considered for a moment and decided he would get into the least trouble if he sat exactly where Slughorn had placed him the evening before. Professor Mullein took his usual seat and wished him `good morning.' The table was beginning to fill.

Then a form settled in the seat next to him, and Russ realized with a shock that it was Dumbledore. The headmaster immediately struck up an earnest conversation with Professor Flitwick concerning the effect prestidigitation had on performing spells, about which Russ understood nothing. Slughorn arrived, and Dumbledore beamed up at him beatifically.

"Horace, I seem to have appropriated your place. Do you mind switching seats for the meal? It has been a while since Filius and I could chat." Slughorn moved to the head chair. Food appeared on the table.

"Have you ever tried kippered herring?" a voice spoke near Russ's ear, and he realized it was Dumbledore's. He nodded in response, not sure what to do or say.

"The kipper over there looks quite nice," continued Dumbledore. "That is, if you feel like kipper this morning." Then he continued his conversation with Flitwick.

Kipper was what Russ had eaten in the railway restaurant, during his last breakfast with his mother before he boarded the Hogwarts express. He took some, together with bacon, toast, and eggs. It was a lot for him, but it reminded him suddenly of his mum and that morning at King's Cross.

A few minutes later, Dumbledore said, "How is it?"

"It's very{\el} good, sir," Russ managed.

"Excellent!" said Dumbledore, as if Russ had just recited a prize-winning speech. "Maybe I'll have some, too." He helped himself to kipper and turned once more to Flitwick.

During the rest of the meal, Dumbledore requested that Russ pass the butter, a feat accomplished without talking, asked two questions that could be responded to with a nod or a shake of the head and once, just once, said, "What do you find most pleasant about Christmas break, Master Snape?"

"Less people," Russ replied, and Dumbledore nodded in concurrence.

"I, too, prefer fewer people around. It offers a measure of peace and quiet," he said.

When breakfast was over, the Snape boy said, "Excuse me{\el} please," and scurried out of the Great Hall. Dumbledore watched him go with a mixture of concern and tenderness. \emph{Not Riddle. Most blessedly not Riddle at all.}

Then, later, from the windows of his office, Dumbledore watched as the tiny dark figure appeared from the direction of the main doors and approached the cliff face. Unerringly it found the steep, narrow, downward path and disappeared from view. Vowing to finish the rest of his business later, Dumbledore hurried down the staircases and onto the cliff edge in time to see the boy head right, along the lake shore to a stand of trees beyond the outermost bounds of the Quidditch pitch. Above him and slightly behind, Dumbledore followed.

As Dumbledore stalked his small quarry, he began to speculate, and the first point of speculation was as to Master Snape's direction, for he was definitely heading toward trees but toward a smaller stand of trees farther away than the forbidden forest. Was he overzealous in obeying school rules, or was he trying to avoid Hagrid? Dumbledore tended to think the second more likely than the first, but reserved judgment.

Another major question—why go as far as the trees at all during a time when the school was nearly empty—was soon answered. The trees were targets. The boy looked around, but Dumbledore made sure that he himself was not visible to the viewer below. Then Master Snape attacked a tree notable for its resemblance in size to a teenage boy.

The attack was with snow, which fortunately had no adverse affect on the tree whatsoever. The snow, in fact, was of minor concern to Dumbledore. What attracted his attention was that the attack was silent, and there was no evidence of a wand. Dumbledore watched, fascinated, as apparently random flurries of snow swirled against the target, gradually coalescing into more compact clouds. Young Snape then used his wand, still in silence, and the clouds of snow instantly formed into tight snowballs, striking the tree with unerring accuracy.

There followed demonstrations of rock throwing, where a much more closely targeted pattern could be observed, and of tossing up amounts of leaves and other small debris. This last supported Dumbledore in his suspicions that the exercise was one intended for defense rather than offense, since the dirt and leaf blind would be more useful in distracting an enemy while trying to escape than as a weapon of attack.

It was clearly a demonstration of variations on one basic spell, the astounding parts being the nonverbal casting of the spell and the novelty. The boy had invented it. No, to be more precise, the boy was in the process of inventing it. Dumbledore had just watched a session where a crude new spell was being refined. It was impressive. It was more than impressive. Most older wizards never attempted to create spells, yet this child was clearly no novice.

It was, however, nothing compared to what came next. Suddenly the wand was gone—Where does he keep it? Dumbledore thought—and the boy stood quite still. Nothing happened. Nothing until a small shower of pebbles skittered down the cliff face. Dumbledore was intrigued. Master Snape's wand appeared again, and again he concentrated. This time small, loose rocks near Dumbledore were dislodged as well and rolled a short distance. Along the adjacent cliff the rustle of pebbles and the soft thud of clumps of snow were clearly audible.

\emph{Did the cliff vibrate? Did that child just cause a small earthquake?} Dumbledore continued watching, but the boy was now finished. He turned and walked back along the lakeshore, Dumbledore once again following, until Master Snape got to the narrow path up the cliff face. Then Dumbledore waited until the boy was inside the Castle before he, too, entered and went up to his office. He had a lot to think about.

Russ was extremely pleased with his practice session. His throwing spells were improving measurably, and he considered them nearly complete. He was a bit disappointed that the focus needed for snowballs and rocks required a wand, but that was not uncommon with targeted spells. The Seismos spell at the end was just the icing on the cake.

Until the previous year, Russ had never even thought about earthquakes. Then, that Monday evening at the beginning of June 1970, his father 'd come home with a newspaper, and there it was on the front page—the earthquake that sent a landslide to bury a town in South America, killing forty thousand people. He got to read all about it for several days, too, for a disaster in a foreign land was one of the few reasons his dad was willing to spend money on newspapers at all, since he got most of his local and national news at the pub.

For weeks Russ immersed himself in fault lines, plate tectonics, and seismic research. He didn't begin to understand it all, but the concept was so alluring that he began trying his own miniature imitations, mostly by setting up vibrations radiating from a circle around his feet. It wasn't a real earthquake, but it had a similar feel for a very short distance. Today he'd gotten almost exactly the result he wanted. The only problem was that he absolutely needed a wand to focus that much energy. Russ didn't like having to depend on the wand for so many things. It was a point of vulnerability.

That evening Russ walked behind Slughorn into the Great Hall and sat next to him to obediently eat his dinner. Quiet and shy, he kept his eyes on his plate, answered briefly when spoken to, and pleased Slughorn by his polite and respectful demeanor.

"How are your studies coming, boy?" Slughorn asked him during a lull in the adult conversation.

"Fine{\el} sir," Russ replied.

"His work in Transfiguration is showing improvement," added Professor McGonagall kindly. "If he continues to apply himself, he may become quite a competent spell caster."

"More than competent, I'd say," chimed in Flitwick. "His wand work in my class is very good."

"Excellent!" cried Slughorn. "Excellent! And if you work a little harder at your potions, well{\el} We may make a wizard of you yet!"

"Thank{\el} you, sir," said Russ demurely.

Dumbledore followed the exchange in silence, wondering with some amusement how the others would react if they saw what he had seen that day.


