% A Difference in the Family: The Snape Chronicles (Rannaro)
% Where Your Loyalties Lie

\chapter{Enter Harry Potter}

\subsection{Tuesday, July 30, 1991}\emph{[JKR says that it is Monday. This is an error.]}

Severus Snape looked around the sitting room in his small house in Spinner's End, reviewing his mental checklist. Windows closed. Fire out in the grate. Everything breakable packed away in the workroom. Spells to protect the house and shield the cul-de-sac from notice by muggles all in place and strengthened. He'd probably not have a chance to return until the next June, and it wouldn't do to leave the gas on. Not that there'd been any gas since 1974, but the principle was the same.

Stepping out into the area yard behind the kitchen, Snape locked the last door. He carried a battered old Gladstone bag with just a few personal things, since everything he would need for the coming school year was already at Hogwarts. \emph{Rotten luck that Dumbledore's calling us back two days early, just as that new potion was coming together. No help for it.}

Snape concentrated on Hogsmeade. The incoming teachers usually picked spots on the outskirts of town to apparate to, it being considered bad form to materialize into one of the local citizens. Destined, determined, and deliberate, Snape disapparated and reemerged in Hogsmeade, so used to the action that he no longer noticed the discomfort.

Almost immediately, a large man with a misshapen face and a mane of long gray hair stepped out from a doorway to accost him. Accustomed to these encounters, Snape glanced away to avoid the other's constantly shifting eye.

"Good morning, Professor," the man said, with sinister good humor. "Still teaching, I see."

"Good morning, Moody," Snape replied. "Arrest anyone yet today?"

"Was kind of hoping it would be you. Disappointed again. You be sure to tell me if you ever decide to retire. The guest room's been ready for some time."

"You will excuse me. I have a meeting."

As Snape walked away, he heard behind him the `pop' of Alastor Moody returning to London. \emph{How did he know we were starting two days early?}

"Severus! Do wait a moment."

Snape turned and paused to allow the older witch to catch up to him. "Good morning, Minerva. I see the clans are gathering."

"Was that Mad-Eye Moody? What would he want here?"

"He takes off a half an hour from his busy schedule every August to wish me a pleasant school year."

"He's not still after you? After all these years?"

"The phrase `Statute of Limitations' does not exist in an auror's vocabulary. If I didn't know better, I'd think Professor Dumbledore put him up to it, just to avoid the trouble of hiring another Potions teacher."

Professor McGonagall suppressed a grin. "Did Professor Dumbledore tell you why he's summoned us? I've been working on registering all the new first years, and suddenly I find we have a meeting."

"I fear I'm not so deep in the Headmaster's confidence."

They stopped at the gate while the caretaker released the shielding spells to admit them, then wished him a polite but restrained, "Good morning, Filch," as they entered.

"Good morning, Professors. Getting an early start this year, eh? Others are already up there waiting on ye."

Snape and McGonagall climbed the hill to the castle and entered the enormous entrance hall. Professor Dumbledore was there to welcome them.

"Wonderful. Wonderful. We are all here, I see. I have taken the liberty of preparing a brunch for all of us in the Great Hall. Much more comfortable than my office, and just as private with no other staff or students here. Come, come."

They were seven, Professor Dumbledore, groundskeeper Hagrid, Professor Quirrell, the Dark Arts teacher, and the four heads of Houses, Professors McGonagall, Flitwick, Sprout, and himself. Snape acknowledged them all with his usual reserve, his coldest greeting being for Quirrell. \emph{The curse really must be broken if he's back in his old job. First Dark Arts teacher in two decades to last two consecutive years. Wish he hadn't gotten so twitchy, though. Makes my skin crawl.} Snape chose to overlook the fact that he himself was in part responsible for the twitchiness.

They sat around the center table on the dais. Dumbledore clapped his hands, and the table was loaded with food. On a whim, Snape helped himself to eggs Benedict and coffee. Then Dumbledore coughed and spoke in the resulting silence.

"We have an auspicious year ahead of us, ladies and gentlemen. First, it will be the first year of a young man we have been awaiting for some time, Master Harry Potter. Second, I have asked you here early because I have received a request from a very old and very dear friend of mine, Nicholas Flamel, and I need your assistance. Nicholas Flamel is an old friend in more than one sense of the word. He is now about 660 years old. I think most of you have heard of the secret of his longevity."

"The Philosopher's Stone," interjected McGonagall, and the others nodded.

"Yes, well. Those of you who have been on the staff longer," here Dumbledore nodded towards Flitwick, McGonagall, and Hagrid, "will know exactly what I am asking, but the newer and younger staff will need some background.

"Nicholas does not keep the Philosopher's Stone about his person. In fact, it is locked in a vault in Gringotts Bank and is only brought out when Nicholas needs to brew more of the Elixir of Life for himself and his wife Perenelle. Sometime during the coming year, they will have need of the Elixir, but Nicholas is not certain when. He has asked me to get the Stone out of the vault and safeguard it at Hogwarts.

"Now safeguarding the Stone is a serious business, and I am asking each of you to contribute something of your own talent to the task. Where one device might be foiled, seven would be almost invincible. Each of you should choose something at which you excel, but which might be difficult for someone else to circumvent."

"Professor," said Snape, trying to hide the exasperation in his voice, "why not simply leave the Stone in the vault until Flamel needs it, then bring it out for the Elixir, and immediately put it back?"

"Ah, I fear that Nicholas has become less than precise as he grows older. He has been known to doze off for up to twenty minutes in the middle of an otherwise scintillating conversation, and recently he has begun confusing me with his great-uncle Pierre who, I regret to say, died at the battle of Crecy. I told him that I could not require my staff to spend their valuable time concocting ways to guard the Stone while at the same time conducting classes and grading assignments. I said it must be done before the students arrive, or it will not be done. He concurred.

"Later today we shall go to the underground area where the Stone is to be housed, and you shall each see the section I shall ask you to defend. Are we agreed?"

They all nodded assent

"Good. Since we are all here, why not kill two birds with one stone (no pun intended, I assure you Minerva) and continue with our regular staff meeting? Minerva?"

Professor McGonagall shifted uneasily. "I have been registering all the students as the confirmations come in, and we seem to have a perfectly normal class of first years. Except{\el} well except that we have as yet no response from Harry Potter, and the deadline is tomorrow. I have sent hundreds of owls, with no luck. I am not certain what to do."

\emph{That does seem odd.} Snape thought. \emph{On the other hand, this is Lily's son, and maybe he would rather pursue another career. I for one would not blame him.}

Dumbledore seemed to have other ideas. "His muggle relatives are notoriously opposed to his training as a wizard. Hagrid, I should like you to visit them tomorrow and make sure that all is in order. Now, as to the class schedules{\el}"

They sorted out classes, evening patrols, Quidditch practices, use of the teachers' staff room, and the supervisory duties for Hogsmeade excursions. Professor Sprout requested that barrier tape be put around a new planting area that had just been set out with seedlings. Professor Flitwick wanted the temperature on the third floor adjusted, as he had recently begun feeling the chill more than usual.

Finally, Dumbledore turned to Snape. "And what is the forecast in the muggle world? Are we looking at any pending catastrophes?"

"On the contrary, things are looking good. The early spring war in the Middle East caused much less disruption than we feared. South Africa has repealed its apartheid laws, the Warsaw Pact dissolved earlier this month ('Where do they get these outlandish names?' McGonagall stage whispered), the Russians have their first freely elected president, and even as we speak the American President is in Moscow to sign a treaty tomorrow limiting long-range weapons. I would say it's quite optimistic." Snape was the only part-muggle at the meeting, and had a better grasp of these matters than the others.

"Excellent!" responded Dumbledore. "Shall we adjourn now and go look at the chamber where the Philosopher's Stone will be housed?"

The entrance to the chamber was on the third floor, not far from the Trophy Room, but its trap door led to a several story drop that had to be negotiated with serious levitation spells. In what was a truly gratifying display of his trust in Snape's abilities, Dumbledore gave the Potions master the task of guarding the last antechamber. "I want something that no wizard, even one able to get through all the other tasks, would be able to accomplish. Think long and hard, Severus. Yours could be the deciding barrier."

Back in his own office in the dungeons, near enough to the entrance to Slytherin house to be able to oversee its activities during the school year, Snape pondered his assignment. \emph{Something no wizard would be able to accomplish. That should be easy. Simple logic}. Rather than waste his talents on too much magic, Snape began to design a logic problem worthy of his muggle grandmother, Gra. He started with seven bottles: three with poison, two with nettle wine, one to go through purple fire, and one to go through black flame. Then he began to write the logic problem.

An hour into refining the problem, Snape decided he needed to rest his eyes. He walked out onto the lawn and stretched his back and shoulder muscles in the warm afternoon sun. Down the hill from the castle, Quirrell was leaving Hagrid's hut, and Snape wondered why the Dark Arts teacher was talking to the groundskeeper.

The sun glinted off the water of the lake where he and Lily had skipped stones, a memory softened by distance for many years now. \emph{How will I react when I see her son? Does he take after his mother? Or his father? Her talent for potions, or his for mayhem?}

Two other boys were arriving in a month. One was Narcissa's son. Snape had held baby Draco on his naming day. Little scrunched up nose and tiny fingernails. \emph{Don't be an idiot; he's eleven. He'd better still be a source of happiness to his mother.}

And then there was the auror's child, the one Snape would have sold to the Dark Lord without remorse, except that Lily and her son were chosen instead. \emph{What will it be like to actually see Neville Longbottom?} Not a pleasant thought at all.

The afternoon sun brought too many memories, few of them good. The only way out of a difficult emotional situation was to turn it off. Snape shut out and locked down the problem areas of his mind the way he would close a closet door. Time enough to deal with the three boys when they arrived. It would have been so much easier, though, if they weren't all coming to Hogwarts at the same time.

\emph{It's going to be a terrible year{\el}}

"What'cha thinking about, lad{\el} Sorry, Professor Snape."

Snape turned from his contemplation of the lake. "Old times. Old faces. How was your summer, Hagrid?"

"Short, truth be told. All this Flamel business, and this Potter business."

"What've you to do with the Potter boy?"

"I got t' go down an' find out why he ain't answered his letters. Professor McGonagall says they've taken off for the coast, and Quirrell says there's a storm coming in. I'm like t' take his advice an' hunker down 'til it's past, then go get him tomorrow afternoon an' take him t' London for his things on Thursday. Thursday'll be when I go t' Gringotts, too."

"Quirrell suggested that?"

"He did. 'T ain't good traipsing hither and yon in a storm."

It was a sound idea, but suddenly Snape resented the fact that Quirrell was offering unsolicited advice about anything. \emph{Twitchy little busybody}. "You could go down tonight."

"What good'd that do?"

"Well, if you were there tonight, then you could leave with the boy for London as soon as the storm let up. You wouldn't have to wait for Thursday. You might have it all done tomorrow. I agree about not taking the boy out in a storm, but when has a storm ever bothered you?"

"That's the truth of it, lad! I'll be off tonight an' greet him on the stroke of his birthday, I will! Maybe even take him a birthday cake, though it won't be much next t' what his family'll do t' celebrate. That's a good idea, that is."

"Do me a favor?"

"Sure."

"Don't mention it to Quirrell. It'd bend his nose out of shape if he thought I was going behind his back."

"I got ya, Professor. What he don't know{\el}" Hagrid went up to the castle to find a birthday cake for Harry Potter.

Snape watched him go. \emph{This year is going to be one of the low points of my life. Here I am feeling superior because I got Hagrid to not listen to Quirrell when Quirrell is probably right. How petty can one get?}

Snape went back to his logic problem. Setting up the classroom could wait, especially if Hagrid was coming back early with the Stone. Supper in the Great Hall was pleasant, since the teachers had all known each other for several years and knew what not to talk about.

"Prospects for Quidditch, Minerva? I didn't want to place a bet until I'd spoken to you."

"I fear this year may be another washout, Severus. Our last Seeker was a seventh year, so we don't even have a full team. You can't put just anyone in. I may bet on Slytherin this year. Seems the only certain money there is."

"Have you considered Wood for a Seeker? He's a superb Keeper, but he might make a passable Seeker. It'd be easier to find a new Keeper."

"'T is an idea. I shall suggest it to Wood in any case."

Around eight o'clock Dumbledore mentioned charades, and immediately everyone had something else to do. Hagrid rose and stretched. "I'll be off now, I'm thinking, Professors. Early start an' all. You all be ready for me when I get back." He lumbered out of the Hall, winking slyly at Snape on the way.

"Where's he{\el} going so soon?" muttered Quirrell, standing at Snape's elbow.

"Probably to bed. I believe he wants an early start tomorrow morning." \emph{And you won't even know he's gone until he's back, Mr.~Nosey Parker. Down, Severus. Down}.

"Severus, would you fancy a game of cards?"

Snape looked down at Professor Flitwick. "I should like that very much, Filius," and the two retired to Snape's dungeon office for a few games of cribbage.

The next morning the teachers met for brunch rather than breakfast. The month before school started was always more relaxed than any other time of the year, and this time the seven of them were in ahead of the other teachers as well. The rest of the Hogwarts staff would be arriving the next day, when things would settle into a more normal routine. At brunch, however, they were only five.

"Where's Quirrell?" asked Snape as he settled into his seat.

"Saw him heading into Hogsmeade earlier. Don't know why. Didn't ask." Sprout reached for another piece of toast.

"I was looking at your new plantings yesterday, Pomona. You didn't by chance put in some new orris or mugwort, did you? We're getting a bit low."

"Mugwort, yes. Good you mentioned the orris. I'll put some in this week."

Snape left the table as soon as he finished eating. Creating a logic problem took time. It had to be exactly the right amount of information in just the right form or it wouldn't work. He needed to concentrate on it for a couple of hours. \emph{If I finish today, I can start August like a normal school year, without rushing any of the preparations}.

Hagrid was back early that evening and spent the first hour closeted with Dumbledore. Snape didn't see him until they gathered for supper.

"An' he didn't even know he was a wizard! They told him his parents died in a car crash. A car crash! I'd like to thump that Dursley! He seems a nice lad, though. Quiet an' unassuming. Kinda shy, but that could be 'cause everything was so new. Got quite a reception at the Leaky Cauldron, he did. Well, you'd know about that, Professor Quirrell."

The others all looked at Quirrell, who seemed embarrassed. "We{\el} got started so early. I{\el} needed to{\el} pick up some things. A{\el} book on werewolves, and{\el} some wolfsbane for the{\el} third years."

"Thought the book was on vampires," muttered Hagrid into his soup.

Snape glanced from Hagrid to Quirrell. \emph{Now what was that about? Quirrell was in London? If it was just a book and some herbs, why didn't he ask Hagrid to pick it up for him? Right. Because I told Hagrid to leave early. Well, I hope Quirrell enjoyed London.}

They all went to bed early, and the next day the rest of the staff began apparating in.

The first to arrive were Madam Pince, Madam Pomfrey, and Professor Kettleburn, assuming one did not count Professor Binns. Of course, no one ever really counted Professor Binns, as he never left the History of Magic classroom anymore. Snape thought about him briefly as he passed the Professor's first floor room on his way to McGonagall's office. \emph{Pity he stopped coming to the Great Hall for meals during my fourth year. It used to be quite entertaining watching him try to eat. How can a ghost not know he's dead? Then again the general consensus always was that he died long before he died. Imagine me coming back to teach Potions as a ghost. Now that would scare the little demons.}

He stuck his head around McGonagall's door. "Library's open. I'm going up now. If you have your list, I can take it for you. I know you're busy. And Dumbledore wants us all on the third floor at ten-thirty. Are you ready?"

"Oh yes, I had it finished yesterday. I've done this before, remember? It's just you youngsters who have to make up something new. Here, I have that list somewhere. And thank you. These registrations will send me to Bedlam."

The precautions for defending the Philosopher's Stone were ingenious. As each of the team members installed his or hers, Snape evaluated his own chances of getting through the tasks. His task and Sprout's were easy for him, but he knew he would have trouble with Hagrid's, maybe even with Quirrell's. No one knew what Dumbledore put in, and McGonagall's and Flitwick's were impossible. \emph{For me at least. I can follow a chess game, but play one? A good one? And though I've reached the point where I can sit on a broom without looking like a fool, the key challenge is out of my league.}

"What'cha think of Fluffy, Professor?"

"Hagrid, you have a talent for the incongruous when it comes to names."

"Ya think so? I thought it sorta fit."

By the end of the day, the entire staff had arrived. Madam Hooch was the only one to fly in. Professors Sinistra, Vector, Futhark, and Burbage apparated into Hogsmeade during the afternoon.

Professor Trelawney came last and made a dramatic entrance at the beginning of supper, flinging herself through the doors of the Great Hall, the back of her right hand held to her forehead, shawls clutched around her shoulders, proclaiming, "The portents{\el} the portents{\el} We shall see dire things at Hogwarts before the end."

"So good of you to arrive in time for supper this year, Sibyll," said Dumbledore in a calm, matter-of-fact voice. "Do join us. The asparagus soup is quite good tonight."

Trelawney ignored a seat next to Snape and rather pointedly sat by Professor Futhark. "Mark my words, we are in for difficult times. I see death in the omens. Death."

Sprout leaned toward Snape. "We ever get a start-of-year dinner where she doesn't see death, I'll faint. Has she ever been right?"

Snape didn't like that question at all. "At least once, I believe," he whispered back. He didn't elaborate.

Dumbledore rose and proposed a toast. "To the coming school year," he said. "May it be pleasant and profitable."

"To the school year," chorused his staff, and all stood and raised their glasses to the coming year.

All Snape's work was done at the desk in his office, not in his own adjoining room. For the most part the bedroom was sparse and austere. Being in the dungeon and therefore without windows except for narrow slits near the ceiling, it was dark and cool all the time. It contained a bed, a night table, a narrow wardrobe, a comfortable chair for reading, a lamp, and two bookcases for private reading material. Here Snape kept his math and science books and a rotating selection of the mysteries that he'd inherited when Gra died. Right now he was rereading Edgar Allan Poe. Or would be if he did not have so much other work.

Every jar, every tin, every package in the Potions room had to be inspected. Some ingredients were old and had lost their potency. Two boxes of powdered amanita were water damaged and would have to be burned. An entire case of newt's eyes came in with faulty sealing and needed to be shipped back. Luckily they would not be used for two months. Shelves had to be dusted, desks and chairs checked for necessary repairs, and in general the entire classroom and office area put in order.

Other duties kept him busy as well. As head of Slytherin house, he had to inspect the common room and all the dormitories to be sure they were fit for the students before the beginning of school. This was particularly important for Slytherin since the house extended under the lake, and was notoriously susceptible to damp and leaks.

Snape also checked out the brooms and other equipment for the house Quidditch team. Although he'd never been interested in Quidditch as a student, as head of the house one of his tasks was to promote a spirit of belonging and friendly competition. Slytherin had done so well under his direction that for the last several years both the Quidditch Cup and the House Cup frequently remained in Slytherin possession. In fact, Slytherin was close to setting a record for consecutive winning of the House Cup. Snape considered it quite an achievement for someone who during all his own school years had been something of a misfit.

As the beginning of the term got closer, Snape found it harder to block out his forebodings about the incoming students. His greatest concern was Neville Longbottom. This boy, the pureblood son of an auror, was the subject of the prophecy that Snape had given to the Dark Lord. It was the Longbottom baby that was the real danger, the Longbottom baby the Dark Lord should have hunted down. If it had not been for a great error of judgment on the part of the Dark Lord in pursuing the wrong child, Lily would still be alive. Snape had high expectations about Neville Longbottom. A boy of great natural ability and potential who would prove that Lily's tragedy was the result of a mistake made by{\el} someone else.

\subsection{Sunday, September 1, 1991}

It was a relatively clear sunny day, and the last day of calm for ten months. The teachers ate lunch around a table for the last time until the Christmas break, since from the coming evening forward they would be on the dais where they could watch the students. They shared problems, swapped stories, and tried to relax. That was not easy to do with close to three hundred students only a few hours away.

At last, as the sun sank in the hills to the west, the teachers wished each other luck and went to change into their school robes, to be in the Great Hall when the horde arrived. They had assembled, and Dumbledore had just finished his usual pep talk, when the train whistle sounded at the Hogsmeade station.

"Places, everyone," said Dumbledore. "It is show time."

Within the hour, the thestral carriages were disgorging students, who entered the Great Hall in a mass of black robes trimmed with the colors of their different houses. Anticipation always ran high for the sorting, and many of the students had younger siblings that they hoped, or dreaded, to have sorted into their own houses. It was also widely known that Harry Potter had been on the train, and many of the students were already craning their necks for the first glimpse of the first years as they entered the Hall.

Then the doors swung open, and Deputy Headmistress McGonagall entered, the first years strung out in solemn parade behind her.

Snape searched the faces of the children. James Potter would have been at the front of the line, claiming the spot as if by right, yet none of the first eleven-year-olds bore any resemblance to either James or Lily. Then, behind a taller sandy-haired boy, there he most unmistakably was, beyond a doubt the son of James - same stature, same thin face, same hair. And yet not the same. A trick of memory made the nose seem shorter, the features a tiny bit softer - or was it Lily coming through? Snape shook his head. Difficult to tell.

Nor was Lucius Malfoy's son hard to detect. Same hair, same eyes, same posture. Here, too, Snape saw, or hoped he saw, a toning down of Lucius's hard lines, something of Narcissa in the boy's face. With Draco were two boys who were also immediately recognizable, two heavyset boys that hadn't before entered Snape's mind. But these were clearly the sons of Crabbe and Goyle. It was unsettling to think that they were still close enough after all the troubles that their sons should be friends.

Snape had no idea what the Longbottom boy looked like and was forced to wait for his name in the sorting.

The first years lined up below the dais, backs to the teachers, facing their future classmates. The Potter boy was looking at the ceiling until a girl next to him said something, then he focused on the ceremony. The stool and the Sorting Hat were brought out, and the Sorting Hat sang its song - basically the same drivel it sang each year - and then the sorting began. Slytherin's first student was a girl named Millicent Bulstrode. The Crabbe boy and the Goyle boy were also Snape's.

The ceremony seemed to crawl as McGonagall read through the list of forty names. Some of the students were sorted quickly; others took time. Snape recalled his own sorting, and how it belied the Hat's claim that there was nothing in a head it couldn't see. The horrid thing had actually asked if there was a student there. Understandable considering the occlumency, but embarrassing nonetheless.

"Longbottom, Neville," read McGonagall, and Snape was suddenly focused. A shortish, round-faced boy stepped forward, and immediately tripped and fell down. Giggles in the Hall were hushed, and the boy put on the Hat. Time crawled. Then the Hat cried, "Gryffindor!" and the boy ran off with it still on his head. \emph{THIS is the child of prophecy meant to destroy the Dark Lord? There must, must be another Neville Longbottom.}

There was no other Neville Longbottom. Draco Malfoy followed Crabbe and Goyle into Slytherin as expected. And then the Potter boy's name was called. Naturally it was Gryffindor, though the Gryffindor table acted as if the issue were in doubt. \emph{What else could it be, since both James and Lily were Gryffindors?}

The very last student, Blaise Zabini, was a Slytherin, and then the feast began. Food appeared on the tables, the ghosts came out to join the celebration, and all the students started to talk. The decibel level in the Hall rose to a painful point. Snape was sitting next to Quirrell and had to endure his twitching and stuttering with at least a semblance of good grace.

It happened very suddenly. The Potter boy looked up, and the movement attracted Snape's attention. He was suddenly surprised by emerald-green eyes, Lily's eyes, staring into his own, and then the boy flinched. He turned away and touched his forehead. Snape, too, turned away.

\emph{He touched the mark, as if in pain. That isn't logical. The mark was made by the Dark Lord. I bear a mark made by the Dark Lord. It only hurt if the Dark Lord called or someone said his name, but he's been dead for ten years. How could the mark hurt?} Quirrell babbled on, but Snape could do no more than pretend to hear.

The feast ended, and the new prefects escorted their charges to their respective houses. Snape sought out Dumbledore.

"He was in pain. As I am standing here, I swear to you, that mark on his forehead hurt him."

"I do not doubt you. But what does it mean? Has your Dark Lord returned? I do not think so. Not yet at least. What in the Hall might have caused this? Is it possible that his mark spoke to your mark, and that is all there is to it?"

Snape thought for a moment. "He looked at me, and I at him. In that moment he clutched his head as if it hurt. But I felt nothing. If mark speaks to mark, wouldn't I have been in pain, too?"

"I do not know. It is something we must bear in mind. Severus, this incident troubles me, and I am pleased beyond measure that you have brought it to my attention. Now we must wait, for we do not know what it means. I shall speak privately to his other teachers. If you or any of them notice a recurrence of this reaction of his, we will know that it is a serious matter. Do not fail to keep me informed."

"No, Headmaster, I shall not."

"Then we must both go to bed. I do not know about you, but I am very weary."

Professor Snape didn't sleep well that night. The few times he managed to doze off, he dreamed of the Sorting, of the Longbottom boy falling down and scurrying to Gryffindor with the Hat on his head. When he got out of bed early Monday morning, Snape already had a headache.

It was a couple of hours until breakfast. There was no point thinking about the problem with no new information to add to the equation, so Snape closed off the section of his mind that was fixating on Longbottom and reviewed the coming day. There were no classes yet, as the students needed to settle in and the heads of houses had to meet and interview their new charges. Tuesday was orientation, and formal instruction began Wednesday.

Today dealt mostly with Slytherin house, and of course he had to meet with the Quidditch team.

By seven o'clock, the Great Hall was filling with students and staff. The new first years stood out because they couldn't find their way, so Snape cornered his two Quidditch Beaters, Bole and Derrick, and set them in the corridor to be sure everyone in Slytherin made it to breakfast. The two were threatened with immediate dismissal from the team if any, even one, new student got lost. Luckily the passage from Slytherin to the Hall was simple to negotiate, as neither Bole nor Derrick was overwhelmingly bright.

Before sitting down in his place at the far end of the high table, Snape exchanged a word with McGonagall. "It wouldn't be a bother if I dropped by your office to check a couple of files this morning, would it?"

"No, no. Not at all. Right after breakfast is best as I have to greet the students, but that isn't until eight-thirty."

In McGonagall's office, Snape pulled out three thin files on three new students, two of them legitimately Slytherins to disguise the fact that he was checking on Longbottom, who was one of McGonagall's. "This will take just a moment, if you please, Minerva. I don't need to borrow them."

McGonagall stood by the door and waited, then locked up after Snape replaced the files. She went upstairs to Gryffindor Tower, while he went downstairs to his office in the dungeon. He didn't like what he'd found.

Neville Longbottom was two points off being a complete squib. His first even remotely magical act, maybe his only magical act, was bouncing after a fall from a window at the age of eight. He had not ever, not one minute, been a threat to the Dark Lord. And so there was no mistake. The prophecy had been about Harry Potter, and from the moment the Dark Lord heard that prophecy, Lily was doomed.

There was a tentative knock at the office door. "Come," Snape called automatically, and Terence Higgs, a seventh-year prefect, entered.

"Sir, it's almost a quarter to nine and you{\el} are you all right, sir?"

"Yes, thank you, Higgs. I'll be there in a moment." The boy left and Snape closed off the whole Longbottom question from his conscious mind and went to talk to Slytherin house.

It was a set speech. The seventh years knew it by heart. That was, in fact, the point, since no one could claim ignorance of the rules. Snape welcomed the students to Slytherin, spoke briefly of Salazar Slytherin, the founder of the house, and of famous former members.

"Slytherin house is currently the highest placed of the four houses of Hogwarts, and we expect you to keep it there. As of this year, there is not a student here who has any memory of the House cup going to any house but Slytherin. Since 1985 we have held the Quidditch Cup four times, and since 1986 the House Cup without rival, and I intend it to stay that way.

"Most of you have little control over the Quidditch Cup, but you must support our team members by being at the games and cheering them on. They are the showcase of our house spirit. Gentlemen, step forward. The team captain is Flint, and the other two Chasers are Pucey and Montague, our Beaters are Bole and Derrick, Keeper Bletchley, and Seeker Higgs. Thank you, gentlemen. For our new members, Montague last year was a first year like yourselves, and every one of you has the chance to try out for the team. Higgs is now in his seventh year, and next year we shall need a new Seeker, so there is a chance for greatness for at least one of you.

"The House Cup, on the other hand, is all of our concern. We make or lose points every day, and each of you is responsible both for yourselves and for your housemates. Good study habits and academic performance earn points. Laziness and misbehavior lose them. And do not be fooled - I shall be the first to subtract points from my own house if any of you break the rules. So there will be no hazing or teasing, no fights, no practical jokes, and this includes against the other houses as well as within our own{\el}"

As he talked, Snape was aware that the students, the first years especially, regarded him with some awe. Many of them came from families that had supported the Dark Lord in his days of power, and Snape knew that from the first night at Hogwarts every student learned that he had been a Death Eater. He didn't mind, since it was also understood that students from the other houses would never be told.

Besides, it scared the little monsters and helped keep them in line.

The new students were interviewed alphabetically, starting with Millicent Bulstrode. This day of interviews was something of an ordeal for Snape because it required actually looking at the students. Directly in the eyes. They seemed to expect it as a sign of interest and sincerity. That meant that Snape had to keep his mind locked down and closed the whole time, a conditioning of his childhood that he'd never been able to overcome. There had, in fact, been only two people in his life that he could talk to fully and frankly, with open, direct eyes and mind - his mother and Lily. Both were dead now.

It was after lunch before Snape got to Draco Malfoy.

"Come in, Master Malfoy. Sit down. I hope your parents are well." \emph{There is something of Narcissa around the mouth and nose. It softens Lucius's patrician features.}

"They're fine, sir. They send you their best wishes for the coming year."

"Very kind of them. Well, Draco, are you looking forward to life at Hogwarts?"

"Oh yes, sir. Especially since, well Father mentioned{\el} If I showed promise, that is{\el}" The boy seemed suddenly embarrassed, as if he'd trespassed where he wasn't supposed to go.

"What exactly are you trying to say?"

"Father said that if you approved of my studies, and if I showed talent, you could teach me extra things, special things."

"Indeed. He's not communicated that to me. What kinds of things?"

"Like how to invent my own spells, and how to take care of myself in a fight. Sir."

"The first takes a tremendous amount of extra study. The second requires long practice. Are you sure you could handle it?"

"Yes, sir. I could, sir. Father wishes you could have taught him. When he was younger, I mean."

"Very flattering, I'm sure. Well, Draco, let's see how you do with your regular studies before we go adding more work. Do well in first term, and after Christmas break we may discuss this again."

"Yes, sir. Thank you, sir."

After he finished with the first years, Snape met with the Quidditch team. Not that he had much to say in the way of play or practice. That was Flint's job. The crux of the matter was that Quidditch victories were a primary reason why Slytherin kept winning the House Cup. It was in everyone's interest that the Quidditch players were taken care of.

"So far as I know, Flint, Gryffindor have not yet found another Seeker. How would it affect us if they made Wood the Seeker?"

"We could handle that, Professor. He'd be competent, but not great. It might even help us to get him away from defending the goal. Another Keeper probably wouldn't be as good."

"I'm pleased to hear that, as I suggested it to Professor McGonagall in August."

Flint grinned. "Blimey, Professor, we may teach you Quidditch yet!"

Fortunately, Snape didn't have any particular duties regarding orientation. The first years were shown around the whole school and grounds. It was hoped that after the tour the number of lost and strayed could be reduced to about ten percent for the rest of the first week. After that, lateness and truancy were automatically considered to be intentional.

Wednesday and Thursday were fairly normal. Potions was a double class, taking a two-hour period each week rather than two one-hours. This was because of the laboratory work, which always needed more time for setup, brewing, and cleanup. The first years had their Potions later in the week, Ravenclaw and Hufflepuff on Thursday afternoon, Gryffindor and Slytherin on Friday morning.

The first Friday session was not one that Snape was looking forward to. All three boys would be there, Longbottom, Potter, and Malfoy. Snape hated personal or emotional situations. They were physically and mentally very draining. Combining that with the chore of keeping twenty as yet unknown eleven-year-olds under control and on task was Snape's newest image of a private and individual hell.

\subsection{Friday, September 6, 1991}

Breakfast was stressful. Snape didn't like sitting next to Quirrell under the best of circumstances, but today in particular he was trying to focus and control his thoughts. Quirrell was not helping. For some reason he wanted to talk about Romanian vampires. It was driving Snape crazy, not least because Quirrell seemed not to know anything about a subject he'd always been quite competent in.

"Fourteen-seventy-six. He was killed in battle in 1476. His head was cut off and sent to the Sultan. Headless corpses do not become vampires. That whole story is tripe." \emph{If I dump on him enough, will he leave me alone?}

"{\el}But he was the{\el} most famous of them{\el}all. I've{\el} seen his{\el} grave." And amazingly Quirrell twitched four times during this short speech.

"And it's not in a castle in Transylvania, is it? It's at Snagov monastery near Bucharest."

All the while, Snape was watching the Gryffindor table without watching the Gryffindor table. \emph{Focus, Severus, focus. You have to face this lot in an hour.}

Then, suddenly, the idea came to him. \emph{I can test the boy. I can find out if he's James's son or Lily's. James would just fool around. Lily would come prepared.}

Snape strode into his first year Potions class determined to treat it, with minor exceptions, like any other first year Potions class. He started out by taking roll. When he came to the name Potter, Snape focused and took a deep breath. "Ah, yes. Our new celebrity." He began to shut down at that point, to close off and lock out the parts of himself he didn't want seen. At the end of the roll, Snape looked up at the class. It was another set speech.

"You are here to learn the subtle science and exact art of potion-making{\el}" They were listening. Listening with total silence and apparent respect. It was time to test Lily's boy. "{\el}if you are not as big a bunch of dunderheads as I usually have to teach. Potter! What would I get if I added powdered root of asphodel to an infusion of wormwood?"

It was not a hard question. Hagrid had gotten Potter his books on July thirty-first, and he'd had a month to study them. The answer to the question was in the first chapter, yet the boy could not respond.

"I don't know, sir," said Potter.

Snape recoiled, unwilling to accept the answer. "Tut, tut - fame clearly isn't everything." Not for Lily, at least. "Let's try again. Potter, where would you look if I told you to find me a bezoar?"

"I don't know, sir." An answer Lily would never give, but the boy'd said it twice.

"Thought you wouldn't open a book before coming, eh, Potter?"

Suddenly he was looking the Potter boy directly in the eyes. Emerald green eyes. Her eyes. And suddenly Snape wanted to respond, to open, to unlock all the locked doors because that was what he always did for the emerald green eyes.

But it wasn't her; it was James. James looking at him through her eyes.

Mechanically, Snape continued, "What is the difference, Potter, between monkshood and wolfsbane?"

The boy sneered, and said, "I don't know. I think Hermione does, though. Why don't you try her?"

Someone snickered, and Snape noticed the girl, standing with her hand raised as if she wanted to touch the ceiling. "Sit down," he snapped. "For your information, Potter, asphodel and wormwood{\el}" and he proceeded to give the answers to all his questions. The first years just sat there, like lumps on logs. "Well? Why aren't you all copying that down?"

The flurry of sudden activity meant he was in charge of the class again. Snape turned back to the smug, insolent student. "And a point will be taken from Gryffindor House for your cheek, Potter."

The class had still over an hour and a half to go, and it did not improve.

The first Potions assignment was a kind of evaluation to find out who was already competent and who had no experience at all. It was a potion to cure boils, more complex than some of the simple infusions they would be doing later, but that was to give the students with more background something a bit challenging. Since it used mostly natural ingredients such as dried nettles, crushed snake fangs, and porcupine quills, it was not really dangerous, yet required the students to learn and practice certain elementary laboratory safety rules.

"Not those gloves, Bulstrode. They aren't heavy enough to handle quills with. We'll be pulling them out of your hands with tweezers{\el} Goggles, Granger, goggles. Never crush snake fangs without goggles unless you want to be blind{\el} Well of course you're not getting the proper amount, Goyle. The balance beam on your scale isn't centered{\el}"

It was, perhaps, the worst first year class he'd ever taught. No one, no one had any prior experience with potions at all. And only two showed any aptitude, one of them being the Granger girl, if she would just stop bouncing up and down with her hand in the air. \emph{Gad, she's worse than Quirrell's twitching.} The other, thank goodness, was Draco. Narcissa's son was the one bright spot in the whole day.

"Class, if you want to see the proper consistency of the stewed slugs, you can come and look at Malfoy's. His are perfect."

Suddenly the telltale hiss of a dissolving cauldron had Snape yelling at the class, "Off the floor! Up onto the stools and tables, quick!" Acid green smoke boiled through the back of the room before Snape managed to say the spell that cleared up the mess. One of the cauldrons was a twisted mass of metal. The boy who owned the cauldron, Seamus Finnigan, was in shock. His partner was on the floor, moaning in pain. It was Longbottom. \emph{So you don't have great natural ability and potential, but did you have to be a bumbling fool?}

"Idiot boy!" Snape muttered as he diluted the potion on Longbottom's arms and legs with water. "I suppose you added the porcupine quills before taking the cauldron off the fire? Here, you, Finnigan{\el} Take him up to the hospital wing. It's on the first floor." Then he wheeled on Lily, who should have kept an eye on the first years.

"You{\el}" \emph{Evans. But it isn't Evans, it's{\el}} "- Potter - why didn't you tell him not to add the quills?" The sullen boy just stared at him. \emph{Just like his father. He's not supposed to be like his father. He's supposed to be like his mother.}

At once the demon, Toby's demon, was back with a power that Snape hadn't felt in more than a decade, and he wanted to strike the boy. With an effort he wrestled the demon down, releasing its pressure in words, "Thought he'd make you look good if he got it wrong, did you? That's another point you've lost for Gryffindor."

They finished the potions and cleaned up, the incident making the rest of the students more cautious. When class was over, Snape went up to the hospital to check with Madam Pomfrey that Longbottom was all right. She'd already released him.

"It was just a few boils, Professor. He was more frightened than hurt. You do have some excitement in that class from time to time, I will say."

Instead of going to lunch in the Hall, Snape went back to his office to rest his head on his arms at the desk. \emph{Is it going to be like this all year? Maybe I should ask Moody about that `guest room.' It can't be this bad.}

The office door opened without an announcing knock. "Thought I'd find ya here, Professor. Missed ya at lunch. Ya ought not t' be skipping yer meals. I take it the morning weren't one of yer best."

Snape sat up. "Understatement of the year, Hagrid. It was a disaster. The first years have no background at all, the Longbottom boy is a catastrophe waiting to happen, and I have to teach James Potter for the next seven years or go to Azkaban. Azkaban is beginning to look like a pleasure resort."

"Can't be that bad. You'll whip 'em into shape soon enough."

"There isn't a lot to work with. And the Potter boy is going to be trouble."

"I thought he seemed right nice. He's coming by this afternoon for a spot of tea. Would it help if he knew about you an' his mum?"

"Don't. You. Dare!" Snape half rose from his chair as all the bad feelings of the morning surfaced again. "I do not need my personal life to become fodder for school gossip! You tell him NOTHING!"

"Suit yerself. That's not why I came by anyway. I wanted t' thank you for saving my hide an' Dumbledore's hide."

"How did I do that?"

Hagrid showed him a clipping from \emph{The Daily Prophet}. It was about a robbery at Gringotts. "Found this in a paper stuffed behind a chair in the staff room. See that vault number 713? That's where the Stone was. The robbery was July 31. If ya hadn't sent me off early, I'da got there the next day, an' the Stone'd be gone. Thought ya might like t' know."

Hagrid left. Snape pondered the mystery of the Stone and Quirrell's sudden trip to London for a while, then left as well, for he had an afternoon class.

Snape was locking up the Potions classroom when Dumbledore appeared at his elbow. "Ah, Severus, I am glad I caught you. I was wondering if you would sit with me at supper this evening. I rather want to gather your insights on this new business in Russia. The Ministry has a war watch started, but I am not convinced that it is necessary. I hope you do not mind entertaining an old man tonight."

"Not at all, Professor. I'm happy to oblige." \emph{Hagrid must have talked to him. He'll be prepared to discuss aborted military coups and Lithuania, but he really wants to monitor my food intake. Still, it is rather nice that the Headmaster came all the way down to the dungeon because I wasn't at lunch.}

The conversation about Eastern Europe was interesting, and Snape was able to relax a bit about the Potter\slash Longbottom problem. In fact, the weekend and most of the following week were quite pleasant, allowing for the fact that the term was just settling in. 


