% A Difference in the Family: The Snape Chronicles (Rannaro)
% The Middle Years

\chapter{Fortress Slytherin}

\subsection{Monday, January 25, 1982}

Unpleasantness hit the fan on the twenty-fifth of January, and it took everyone by surprise. Morning was normal, breakfast was normal, and then as first hour classes were about to begin, it was announced that the Dark Arts students should stay in the Great Hall for a study period.

That, at first, was all anyone knew - that Scrimgeour would not be arriving at Hogwarts on time to teach his morning classes. Fifteen minutes into the second session, however, the Potions class was interrupted by Dumbledore coming in himself.

"Excuse me, Severus, but I really must see you in my office at once. Students, if you will quickly clean up your potions work and go either to the library or to the Great Hall to study... You may check with Professor Snape tomorrow about assignments that will be due next week. Very good... that is right... quickly now... Lock the door, Severus. It would be wise to hurry."

They did hurry, through the dungeon corridor, into the entrance hall, and up the marble staircase, but they didn't hurry quite fast enough. Scrimgeour burst through the great oaken doors, Hagrid at his heels.

"You can't hide him this time, Albus! This time he goes down!"

Dumbledore came down three steps so that he stood between Snape and Scrimgeour. "Rufus, we have been expecting you. I trust you bring news, though mine is fairly recent. Let me suggest, however, that we discuss it in my office, for while you and I know what this is about, Professor Snape and Hagrid are ignorant, and there is no need to gossip before the entire school. If you would follow Hagrid up..."

Dumbledore turned, pushing Snape upwards so that he remained between. Scrimgeour sprang for the stairs and was stopped by Hagrid. "The professor asked you to follow me," Hagrid said, "That means me first, and you second." Hagrid then made his way leisurely up the stairs, ensuring that Snape and Dumbledore were well ahead, and Scrimgeour well behind.

As soon as they were in the office, Snape crossed to the far side, wanting as much substantial furniture as possible between himself and Scrimgeour. He still had no idea what the problem was, but considered that of secondary importance. Scrimgeour stormed in behind Hagrid, though the groundskeeper prevented him from going far into the room.

"This has gone too far, Albus!" Scrimgeour shouted. "You can't protect him anymore. I'm taking him back to London."

"Do you happen to have a warrant, Rufus? I fear without a warrant I would be in violation of the law if I were to force Severus to accompany you. No? Then let us take this a step at a time. Would you care to sit down?"

"I'll stand!"

"Suit yourself. Severus, you need to know that last night Alastor Moody was involved in a fight with several Death Eaters and is currently in St. Mungo's hospital. My latest information, Rufus, is that he has regained consciousness, and that his prognosis for recovery is excellent."

"Right. Except that the blasting spell hit him in the face and he'll never see again."

Snape had long since closed himself down, but now a knot tightened in his stomach. Another victim who'd be laid to his blame, even though he'd known nothing of the attack. Part of him felt he should say something, but he couldn't think of anything to say. It struck him that Scrimgeour, with his irrational accusations, and the violence of his actions and emotions, was remarkably similar to Sirius Black.

Dumbledore continued. "Do they have in custody the people he was fighting?"

"Yeah. Yeah, they do. A couple from Lincoln and her cousin. You know anyone named Folkenstone, Death Eater?"

"No," replied Snape quietly. "I don't."

"Liar."

"Rufus!"

"Albus, you know what he can do! Alastor's good, and Alastor said he couldn't read this one. Can you stand here, look me in the face, and tell me honestly that he's never lied to you?"

"That is not the point under discussion."

"It's exactly the point under discussion. He could lie, and lie, and lie, and none of us would even know it."

"He has not lied to me about this."

"Albus, you have no way of knowing."

They stood, staring at each other across the room. "Do you have a suggestion?" Dumbledore asked. "Because if you do not, I shall be forced to ask you to leave. I believe that although I cannot fire you while under contract, I can suspend you from your teaching duties for the rest of the year. We would continue to pay you, of course."

"I don't want your pay!" Scrimgeour's face was red now. "For God's sake, Albus, why won't you listen? We don't want vengeance, we want justice. Frank and Alice are lost. Alastor's lost, too. You don't care what happens to us. When did we become expendable? Why are you wasting this time on a proven Death Eater who won't even repent?"

"This is a very good question, Rufus. Perhaps we should ask Severus." Dumbledore turned to Snape. "Rufus accuses you of being unrepentant. What have you to say?"

Snape flipped through all the responses he'd been preparing, and the answer to `Why are you still shielding Death Eaters?' seemed to fit best. "I didn't know what they did. All I know is that they came to me for potions, and for spells, and for lessons on how to protect themselves. I was tricked into becoming a Death Eater. I don't know how many of them were tricked as well. Why should I let you punish them for having been tricked into a lie?"

"So you think they're just going to innocently crawl under rocks and hide? Your record hasn't been good so far."

"As a total percentage? It's been very good. I can't help that there are a few."

It was the wrong thing to say. Scrimgeour jumped on it immediately. "Total percentage? You mean that the number of attacks are small compared to the number of names you know? Who else is going to ambush us, Death Eater? Who else?"

"No one that I know of."

"Yeah, but that's what you said before Alastor was attacked. And the Longbottoms."

"I can't give you names of people I think are innocent."

"You think the Lestranges and Crouch are innocent? You think the Folkenstones are innocent?"

"I didn't know the Folkenstones."

Turning to Dumbledore, Scrimgeour demanded, "Let me talk to him, Albus!"

"You are talking to him, Rufus."

Scrimgeour stiffened and became suddenly quite cold. "Then we have nothing more to discuss, have we? Perhaps you'd better suspend me, Albus. I see no more reason for me to come to Hogwarts."

"I shall be sorry to lose you, Rufus. You were a good teacher. But this is probably for the best."

With that, Scrimgeour strode from Dumbledore's office. He neither looked at nor spoke to any of them on the way, but hastened from the castle and apparated back to London.

Dumbledore went to a cabinet and took a cloak. "You will excuse me, now, gentlemen," he said to Hagrid and Snape, "but I, too, must be going to London. I shall be at St. Mungo's visiting Alastor. If you would remain in the castle this afternoon, Hagrid, near the dungeon area, I should appreciate it. I expect to be back before supper time." Dumbledore left the office and followed Scrimgeour's route out of the castle and down the hill.

"It'll be lunch time, now," said Hagrid. "We'd best go down and have a bite t' eat."

"I'm not hungry," Snape replied.

Hagrid took him by the arm. "Well, I am. And if I'm to look out for ya this afternoon, y're just going t' have t' come t' the Hall with me and watch me eat, then. Now, we can walk down side by side, or I can put ya over my shoulder like a stack of wood."

"Hagrid, are you angry with me?"

Hagrid took Snape by the shoulders and turned him so they faced each other. "I don't have much fondness for Rufus Scrimgeour, lad, and Professor Dumbledore, he wants ya safe up here. But Frank and Alice, and Alastor, too, they're friends of mine. I ain't sure yet what's t' become of Alastor, but it's beginning t' look like Frank and Alice are as good as dead. Don't get me wrong. I got a fondness for ya, and I'll do what it takes t' protect ya, but I got other friends, and there's still a lot of Death Eaters out there. So you'll excuse me if I'm having a bit of trouble understanding this blamed stubbornness of yers. Now, let's go t' lunch."

Dumbledore was back at Hogwarts before the end of the afternoon classes. Hagrid stood outside Snape's classroom as the last lesson of the day ended, with a message to come to Dumbledore's office whenever convenient. Snape and Hagrid went up together.

It was something of a shock that Dumbledore looked so tired. He motioned them to sit, then poured mead, hesitating a moment with Snape's goblet still in his hand. "That's all right," Snape said, "I'll take it."

After a moment, Dumbledore began. "It is hard, very hard, to witness. Frank and Alice have no awareness of anything around them. Their eyes follow the light, they flinch slightly at loud noises, but that is all. The healers believe it to be a combination of physical damage and psychological trauma, so the long-term prognosis is not good. They may be institutionalized for the rest of their lives. Alastor is a little better than we originally feared. He has, indeed, lost one eye, but they may be able to save the other. They have apprehended Berengaria Folkenstone, and she has implicated two additional Death Eaters, Rudy Carstairs and Horatio Gamp. Severus?"

Snape's grip had tightened on his glass, sloshing some of the mead onto his hand. He set the goblet down and rose, walking over to the windows where he stood looking down at the lake.

"I take it," said Dumbledore quietly, "that these names are not unknown to you?"

"They took lessons from me."

"So we are two for two. Two attacks, both involving people you know."

"Headmaster, I don't know what to do."

Dumbledore didn't try to hide his concern. "Is there some criterion you could use to distinguish the potentially dangerous ones? The lessons, perhaps?"

"Those who took lessons were generally those who went out on raids, but the Lestranges and Crouch never took lessons. Neither did the Folkenstones. And most of those who did haven't been involved in any dangerous activity."

"So there is no benchmark you could use."

"None."

"Then we must defend ourselves as best we may. Crouch has ordered that any group involved in a roundup of former Death Eaters be prepared to use deadly force at the slightest hint of resistance."

"They can't do that. There are healers, and cooks, and supply personnel, and clerks."

"Give us the names of the inoffensive, then."

"The ones who never hurt anyone, who might otherwise escape them entirely? No."

"We are at an impasse, and each must look out for his own as he can."

Snape turned back to the window and the lake, while Dumbledore and Hagrid were silent. Minutes ticked by, but by this time the outcome was inevitable, and Dumbledore was willing to wait as long as it took. Finally Snape returned his attention to the room. "Let them know I'll give them some of the names. But only the ones I think may still be dangerous. Only not in London. If I'm seen going into the Ministry again, and then roundups resume..."

"It shall be somewhere else. Not Hogwarts either. That would be traced back to you. Somewhere else." Dumbledore left the office to contact the Ministry.

The inquisitor was Gawain Robards, all business and practicality. The venue was a house in Newcastle, not normally a place for any kind of Ministerial or Death Eater activity. Snape apparated in with Dumbledore, and Robards with a clerk.

They sat at a table in a large kitchen, where Dumbledore brewed coffee for everyone. Snape and Robards sat opposite each other with the clerk at a nearby desk and Dumbledore standing behind Snape. The first thing was a piece of parchment with a statement for Snape to sign.

"What's this?" Snape asked.

"A standard statement that you are doing this of your own free will," Robards replied. "Just sign there."

"I'd like to read it first." Snape read for a moment, then looked up at Robards. "This says that since I agreed to give you information, once I start talking if I withhold anything, I'm liable for criminal penalties."

"I believe that's just standard language."

"Gawain..." Dumbledore warned.

Robards sighed. "I can reword it, but they want a statement. What about `withhold information about a person I know to be dangerous'?"

"And add, `who thereafter initiates violent action,'" suggested Dumbledore.

Between them, Robards and Dumbledore worked out language that would satisfy the aurors and yet be specific enough that Snape would be protected from arbitrary action, after which, having little other choice, Snape signed the paper.

"Now," said Robards, "in December, you gave us a list of names which I have here." He handed another piece of parchment to Snape. "All of the names on that list were of Death Eaters who were dead, had already been captured, or who have since been captured, the most important being the Lestranges and Crouch. They were also fairly high-ranking, what we would consider the inner circle. We're now looking for lower level operatives who engaged in violent actions against the wizarding world or the muggle world. First, is there any name you feel that you left off the first list?"

Snape looked over the names. "No," he answered.

"Are you sure?" The hostile note was clear in Robard's voice. "What of Lucius Malfoy?"

Narcissa's husband. Snape glanced away, toward the window. "He became a Death Eater late, not until after his father died of dragon pox. I never had anything but social contact with him. I never heard of him going on raids. I think they recruited him for his money."

"Wasn't he involved in high level planning?"

"I wouldn't know. I didn't have that kind of access." Snape paused. "If you already know about him, why do you need me?"

"Just curious how you would respond." Robards then began the slow, careful search for names and data, trying to obtain as much detail as possible while Snape took his time with each person, trying to decide whether or not that one might be a threat. From time to time he had trouble remembering names, but adamantly refused to put his memories into a pensieve for fear that the `innocent' might be revealed along with the `guilty.' All four of them were exhausted and irritable when, several hours later, Robards packed up his papers and returned to London. He had a list of twenty-seven new names.

They had results by Friday. Dumbledore called Snape into his office and had him sit down. "Lemuel Lufkin and Dickon Varney are dead," he said quietly, pouring Snape a small glass of firewhisky.

Snape's eyes grew wide with shock. "What happened?" he whispered.

"There was a raid. They fought back. I hope it is a consolation to you to learn that inside the house were detailed plans for attacks on Mr. Crouch, the head of Law Enforcement, and on Judge Bones. The information you provided has foiled those plans, and both are being given extra protection. The aurors also found the names of seven more Death Eaters from the west of England that they are checking out." Dumbledore handed Snape the firewhisky. "You do not look pleased."

"I feel like a traitor." Snape looked at the drink, then quickly consumed half of it.

"How would you feel if the news I was giving you today was of the assassination of Judge Bones by people you knew?"

Snape thought about this for a moment. "I'd feel worse," he said at last.

"Then we may derive a measure of contentment knowing that we have been given the better of two evil situations."

"I suppose so."

"Stay here for a while, Severus. Think about all the things that might have happened. There is some good to be found in the thought that of all the bad choices we have, we made the one that was least bad."

It was a comfort, as Dumbledore said, for while Snape knew little about Mr. Crouch beyond his being Barty's father, Judge Bones had been kind. And Snape acknowledged that he would have been devastated to learn of her death knowing that he'd held the information that might have saved her. That was guilt that he'd been spared.

Much later, returning to the dungeons, Snape ran into Algie Colfax.

"Professor Snape," Algie called from beside the Slytherin wall. "I was wondering if I might have a word with you."

"What's on your mind, Algie."

"Next week's the Gryffindor-Hufflepuff game, and then in March we play Ravenclaw. Wanted to talk about it with you if you don't mind."

Snape invited the Quidditch team into his office rather than meeting in the common room. They all seemed a bit apologetic, as if they knew that Snape had other problems, bigger problems, to deal with.

Algie plunged right into Quidditch talk. "The thing is, the Gryffindor-Ravenclaw game was high-scoring. Can we score high against Ravenclaw, too?"

"You're going to have to explain this to me," Snape said. "I don't usually bother with Quidditch, and I haven't been thinking about it at all for a while."

"There are three rounds of play in which each team plays a game against one of the other teams. The team that wins the most games, wins the Quidditch Cup. If two teams win the same number of games, the team that accumulated the highest number of points wins the Cup. Right now, Slytherin and Gryffindor have won, Ravenclaw and Hufflepuff have lost. But Gryffindor made one hundred twenty more points than Slytherin did, so in a way, they're ahead."

"Do we have a chance of beating Gryffindor?"

"Not really. They've had the best teams for years, and we've been at the bottom. We'd love to win, but a respectable year would be good, too. That game against Hufflepuff was our first win in more than two years. Even if we don't get anything else, we have that. We won a game, and it was a good game, too. Not a Seeker fluke."

Snape thought for a moment. "I know everyone hates Gryffindor for being so overbearing and cocky about Quidditch, and we're the underdog. So now it's to our advantage to have exciting games, whether we win or lose."

"Come again, Professor?"

"Look, it wasn't planned, but I was `sick' and our first game was canceled. So this year we play Gryffindor last, the final game of the season. Let's take a worst-case scenario. Let's say Gryffindor beats Hufflepuff and Ravenclaw beats us. We get down to that last game, we want the whole school to be cheering for us, not for Gryffindor. Doesn't it help you play if everyone is cheering for you?"

"Sure it does, but why would they want to?"

"Let's say Ravenclaw beats Hufflepuff. Hufflepuff would have no chance of winning, but they'd cheer the underdog, especially since our game against them was a good one with no hard feelings between the houses. Ravenclaw would cheer for us, especially if they scored high against us and Hufflepuff, because if we won, they'd be in contention for the Cup in a three-way draw."

"What if we beat Ravenclaw, Professor?"

"Then it would be straightforward us against Gryffindor for the winner, but we could still get the underdog support if we've played good, exciting games. Wouldn't you like to play well against Gryffindor, even if we don't win the Cup?" They nodded emphatically, and Snape continued. "In addition, the longer the game lasts, the more practice our team gets for next year. That won't affect Algie and Chris because they won't be here, but the rest of you are next year's team, too, if you all continue playing well."

The rest of the meeting was tactical on drawing the game out by scoring without catching the Snitch too soon. Ravenclaw had good Chasers and a weak Keeper, the opposite of Hufflepuff. Slytherin's Keeper was good. Now it was the Chasers who needed more work. The team went out to practice with a clearer idea of what they were working towards.

The question came up of what to do with Scrimgeour's classes, since Dark Arts could not be canceled for the rest of the year, especially for the fifth and seventh years who were preparing for OWLs and NEWTs. The only way it could be handled was to redo the master schedule.

First, the number of Dark Arts classes was cut in half by lumping two houses in the same hour, Slytherin with Ravenclaw, Gryffindor with Hufflepuff, and sixth together with seventh year. Then the classes were dealt out to the teachers, with the least experienced instructors getting the lowest level classes, and the more experienced the higher levels. Dumbledore himself took the sixth and seventh years. Some of the other lessons in other courses were also merged to give the professors the time to take the new class.

Snape was not given a Dark Arts class because all his Potions classes already contained two houses, and they were all two-hour sessions. His classes were, in fact, the ones that the schedule had to accommodate since they were impossible to shift. Dumbledore did admit privately that the schedule alone was not the whole reason for Snape's being kept out of Dark Arts.

"What would the Ministry think, or worse - do, if I put you into Dark Arts when your relationship to the dark powers has been a bone of contention between us since the school year began? No, no, Severus. We give them no excuses to interfere."

With all his other problems and irritations, Snape actually found himself looking forward to the Gryffindor-Hufflepuff Quidditch match.

\subsection{Saturday, February 6, 1982}

Most of the week was clear and cold, but Saturday was overcast and therefore warmer. It was good Quidditch weather, since the players wouldn't have to worry about the glare from the sun as they flew. As it turned out, there would be other things to worry about. Snape had hardly walked into the Great Hall and sat down to breakfast when it hit him.

"Have you seen this?" McGonagall asked, laying a copy of \emph{The Daily Prophet} on Snape's as yet empty plate. "Page three."

Snape opened the paper to page three and felt as if someone had punched him in the chest. There was an article on the efforts of the Ministry to round up the last of the Death Eaters, and his list of twenty-seven names was prominently displayed together with the names of all of those arrested since Halloween. Snape's own name was never mentioned, but several of the students in Slytherin house, a couple in Ravenclaw, and one girl in Hufflepuff had family members listed.

A glance around the hall showed that students at every table were reading a larger than usual number of \emph{Prophets}.

"Does Professor Dumbledore know about this?" Snape asked McGonagall.

"He does. There isn't much we can do, however."

"We can protect our students."

"You'll have the biggest job," she responded. "You have more of them in your house than the others do."

Something in McGonagall's tone made Snape turn to look her in the face. "I hope we have the same understanding of who the likely victims are," he said.

Shouting from the entrance hall had every professor at the breakfast table up and heading out of the Great Hall. At this early hour on a Saturday morning, that meant Snape, McGonagall, Sprout, and Flitwick, since most of the other teachers stayed home on weekends, and the few left in the school were late risers.

A crowd of students was beginning to form in the entrance hall around a little group of boys. Three of them were Slytherins - Algie Colfax, Chris Tobin, and a third year named Richie Gamp. The other boys, five of them, were Gryffindors. All of them but Gamp had their wands out.

"What is the meaning of this!" McGonagall cried out in her most authoritarian voice. Algie and Chris put their wands away at once. "Peterson! Maddock! Explain yourselves!"

Peterson pointed at Gamp. "He's a Death Eater. It's in \emph{The Prophet}. My cousin Oscar and his family had their house destroyed by Death Eaters and lost everything. He shouldn't be here at Hogwarts."

Snape had moved to the same side of the hall as his three students, watching warily now for what McGonagall, as deputy headmistress, would do.

"That is ridiculous, Peterson. \emph{The Prophet} has not named Master Gamp. It may have listed someone with the same last name, but that is irrelevant. You are both students here, and you will obey the rules. There will be no fighting, no teasing, no harassment. Put your wand away."

Peterson didn't obey. Instead he pointed at Snape. "What about him. Tiberius's father says he's the biggest Death Eater still at large. How come he's teaching here?"

"Peterson!" snapped McGonagall. "You will close your mouth, put your wand away, and go to my office at once!"

"But it's true!" exclaimed Tiberius Diggle. "My uncle works in the Improper Use of Magic Office, and he says Professor Snape should be in Azkaban, but Professor Dumbledore is shielding him!"

Everything happened at once. McGonagall cried, "Silence!" as Peterson raised his wand at Snape and screamed, \emph{"Stupefy!"} Unable to use a shield because of the crowd of students, Snape dove to his right, dodging the bolt of red light and rolling smoothly to a standing position, wand in hand, sending Peterson's wand into the air with a finely aimed, nonverbal Expelliarmus.

"Enough!" bellowed Dumbledore from the stairs, and the students in front of him parted to let him through. "Miss Thackery, you will kindly bring me Master Peterson's wand. Master Peterson, you have attacked a Hogwarts teacher and are suspended from all classes and activities. Go to my office at once. We shall have to contact your parents about expelling you. Professor Snape, I hope you are not injured."

"No, sir. I'm fine."

"Good. The rest of you get in to breakfast. Heads, please sit with your houses. Attacks, wild accusations, teasing, none of this behavior will be tolerated. A Quidditch game is scheduled for this afternoon, but if the school is disrupted it may have to be canceled. Professor McGonagall, I shall be in conference with Master Peterson."

Hagrid arrived as the professors were shepherding the students into the Great Hall, trying to maintain a strict silence as witches and wizards from different houses brushed shoulders going through the great doors. Sprout filled Hagrid in on what had happened, and the groundskeeper found himself nearly alone at the high table because the heads were with their houses. Hagrid didn't want to join any particular house for fear of appearing to take sides.

One thing that Snape noticed immediately was that his own students were watching him closely. At first he wondered if they were afraid of him, then slowly realized that their faces reflected a mixture of awe and pride. Algie looked positively proprietorial, as if he'd been trying for ages to convince the others that their head of house was more than just a bookish potions brewer. \emph{O Lord, now they think I can fight. They'd better not ask for lessons.}

Dumbledore returned in about forty minutes, followed by an obviously contrite Peterson, who went to join his friends at the Gryffindor table. Beckoning to the heads of houses, Dumbledore informed them quietly that Master Peterson was suspended from classes for a week and on detention until after the Easter break. "I hope this is sufficient, Professor Snape. I am certain that Professor McGonagall will find appropriate work for the young man."

"I certainly will! Behaving like that, and in front of the whole school!"

A spark of mischief rose in Snape, a reaction to the tension of the morning perhaps. "Foolish child. If he'd attacked me in private, it would have been acceptable. When will they learn?"

McGonagall spun on him. "Now listen to me, youngster!" she began, then caught the tilt of his head and the glint in his eyes and began to laugh. "You got me there, Professor. Dear, dear, you did." The rest of the school saw them at ease with each other and relaxed as well.

Dumbledore stepped onto the dais and addressed the assembled school. "All students will, after breakfast, return to their common rooms to discuss the proper way to deal with the difficulties we face as a school over the next few weeks and months. I know that all of you realize that we as a community must work together to keep Hogwarts a place of safety and of dedication to the future that we all will share. Your maturity, your wisdom, will carry us through rough places. I am sure that enough progress will have been made before the lunch hour that we shall be able to devote the afternoon to the friendly competition of a well-played Quidditch game. I hope to see you all there."

The meeting in the Slytherin common room didn't start well. The majority of the students carefully avoided the group of Death Eater children. When Snape entered the common room, their attitude was more ambivalent, as if they wanted to be able to trust him, but weren't sure if they could.

\emph{There are things I can tell them, and things I can't. Help me distinguish which is which and say the right things. But I can't hide things - they all know what's been going on.}

Marlene Kingsford stepped forward. "The first thing we want to know, sir, is - is it true? Are you a Death Eater?"

It was a question that had to be answered. "I was." It was an answer that raised more questions.

"Why?"

"Marlie, do you remember when you were in third year that I had to leave school for a while? It was in the autumn term. Do you remember why?"

"Yes," Marlie said, and Chris added, "Your grandmother was killed. They burned her house down with her in it. Muggles. We were all talking about it." The majority of the students looked shocked, but the fifth, sixth, and seventh years nodded. They all had some memory of the occasion.

"I was afraid. I believed muggles were instituting witch hunts again, and I believed that... You-Know-Who was the only one who could help. So I became a Death Eater. It was three years before I found out that You-Know-Who had ordered the attack, putting muggles under Imperius curses, to trick me, to recruit me. By then it was too late."

"Why did they want you?" asked a fourth year girl.

Algie spoke up. "Do you know what we used to call him? Cursemaster. Any curse, any hex, any jinx, any potion you wanted, he could do it."

"Did you ever kill anyone?"

Snape didn't look for the questioner. "No. I worked in a potions room. I watched people die, though. I watched him kill people. By the time it ended, most of us were more afraid of him than anything. Now he's gone, we just want to stay away from trouble."

"Why aren't you in prison if they know this?"

"I work for Dumbledore. I told you, he takes care of his own. You're his, too. He'll take care of you if you give him a chance."

After that, others whose family members had been Death Eaters, but whose names had not been in \emph{The Prophet}, also came forward. Some of them were from families Snape had not known were servants of the Dark Lord. Fortunately, not a single one came from an important Death Eater family, and most of their families had long since been disillusioned. At one point a debate started as to the relative worth of blood status, but then Snape mentioned that he himself was a half-blood, and the discussion was halted. The general consensus of Slytherin house boiled down to five points:

First, the Dark Lord was gone, and whether your family had followed, opposed, or been neutral, the question was now moot and, in any case, a problem for the older generation.

Second, there were more Death Eater families represented in Slytherin house than in the others, and there was therefore some actual logic to their house being targeted for reprisal more than the others. The students resolved to check with Ravenclaw and Hufflepuff to be sure the other students named in \emph{The Prophet} were not being harassed, but otherwise to treat each incident as separate and unique, to be dealt with on a case by case basis.

Third, any future harassment was to be responded to in defensive mode only, and to be reported as quickly as possible to a staff member. Offensive or retaliatory strikes were counterproductive. In order to reduce the number of incidents, each Death Eater student was to have a constant bodyguard of non-Death Eater housemates so that the targeted students would never have to face harassment alone.

Fourth, any statement made in the common room as a committee of the whole was to be regarded as confidential, and never to be revealed to anyone outside the common room, as long as it did not involve criminal activity.

Fifth, Dumbledore was to be given the opportunity to show that he protected his own, and Slytherin students were at all times to show the utmost respect for the Headmaster and his directives so as not to jeopardize the relationship.

Leadership had been taken by the non-Death Eater upper classes of Slytherin house, the sixth and seventh years, and Severus was immensely impressed at the seriousness with which the whole house debated the issues and reached resolutions. It occurred to him that these students had been living together for years knowing who was `dark' and who was not, and that what they were doing now was bringing into the open a system of mutual coexistence that they'd been practicing ever since they entered Hogwarts.

It was with great pride that Snape made his report to Dumbledore and the other heads on the discussions in the Slytherin common room.

Flitwick and Sprout also reported relatively serious debate in their houses. A most encouraging sign was that the two houses had decided that their reported Death Eaters were their Death Eaters, and that no other house was to be allowed to touch them. Ravenclaw's business was Ravenclaw's business, and Gryffindor had better keep its nose out.

McGonagall's report was of a far more emotional meeting. Plea after plea for logical, rational debate was met with anecdotal challenges of relatives who'd suffered, and calls for justice on a higher plane that had nothing to do with practicality or the general well-being. Every time a general resolution was passed, someone would announce with an almost religious fervor that it might be well and good for the house as a whole, "but if you think I'm going to sit quietly by and not get the people who hurt my aunt Susan, you are sorely mistaken." The degree of insistence on the absolute moral right of individual action was discouraging.

Snape, Sprout, and Flitwick mutually agreed that they were very lucky that all the crazy students got funneled to McGonagall.

It was determined that due to the maturity shown by the student body of Hogwarts as a whole, the Quidditch game between Gryffindor and Hufflepuff would take place as scheduled. The school was informed at lunch to tumultuous cheers, and by one o'clock long lines of students were wending their way down the hill to the Quidditch pitch and their house stands.

Members of the staff who usually weekended away from the school were apparating into Hogsmeade for the game as well, and Severus was heartily greeted by Kettleburn, and exchanged greetings with Futhark and Vector as well. The centers of attention, of course, were McGonagall and Sprout, and though the staff had agreed to show solidarity by sitting all together in the same booth, Flitwick and Snape were careful to sit between McGonagall and Sprout, just in case tempers might flare.

Dumbledore accompanied Madam Hooch to the pitch, then waved cheerfully at the assembled students and took his place. Madam Hooch gave what was becoming her classic "I want a good, clean game" speech, and the two teams were off the ground and fighting.

It was disappointingly quick. Gryffindor pushed past Hufflepuff's sterling defense only once to score ten points. Then there was a defensive battle for all of fifteen minutes before the Hufflepuff Seeker spied the Snitch and went into a nosedive. And then it was over. Hufflepuff emerged victorious over Gryffindor, 150 to 10.

Happier by far than the Gryffindor players were the Slytherin and Ravenclaw teams, for not only had Gryffindor lost, their massive point lead had been slashed to modest proportions by their modest score. It was anyone's Cup.

As students poured onto the field to congratulate or commiserate with the players, Dumbledore approached the heads of houses. "No urgency," he said, "but when you are back in the castle, could you all come up to my office?"

That, naturally, injected precisely a note of urgency into the whole proceeding, and the four heads tried to urge the students up the hill as quickly as possible, leaving in Hagrid's hands the question of order in the entrance hall as the four of them made their way upstairs.

"So pleasant we could all get together," Dumbledore said as he passed around mead, wine, and firewhisky. The words "Sit, Severus, I have a new brandy I'd like you to try..." were a clue that whatever it was had to do with Professor Snape, and the other three relaxed a bit. Still, an afternoon summons and glasses of spirits boded no good for any of them.

"I wanted to let you know," said Dumbledore as they settled into chairs with goblets in their hands, "that your classes will be a bit smaller on Monday."

"Smaller?" McGonagall exclaimed. "Whatever for?"

"We have," continued Dumbledore calmly, "a few families who have expressed a desire to have their children educated elsewhere. The students in question will be departing this evening or tomorrow, and will therefore not be in your Monday classes or any classes thereafter."

McGonagall was once again the spokesperson for all of them. "Pulling out in February? Why would they pull the children out in February?" They all knew the answer, but somehow it seemed right to make Dumbledore say it.

Dumbledore hesitated. "It seems... Well, to put it in a nutshell, they do not want their children taught by a former Death Eater, and Potions is a required course."

"How many?" asked Flitwick.

"Eleven from Gryffindor, five from Ravenclaw, and two from Hufflepuff. None from Slytherin so far."

Snape, having begun to shut down from the moment Dumbledore offered him a brandy, was now completely closed, his eyes distant and cold. "Would you like me to resign, sir?" he said.

"You forget. That is not an option." Dumbledore looked over at the three other professors. "It is a type of probation imposed by the Ministry. Severus must remain here under my authority."

"How small do you think the school will get?" McGonagall asked.

"Word has gotten out very quickly since this morning. Two of the students in question have already approached me and asked if I might intercede with their parents to allow them to stay at Hogwarts, so I do not think they were motivated by a desire to get out of school."

"They want me fired," said Snape dully.

"I shall admit, that was the initial request made by all the parents. I was instructed to get you out of the school. I informed them that I had the utmost confidence in you, and that under no circumstances would I ask you to leave. That was when they told me they were withdrawing their children."

"Well, there it is," Sprout said. "This is all very recent news, and people are overreacting. When they all find out that Hogwarts can't be swayed by their prejudices, they'll back down and send the children here again. We just have to give them time for all this to sink in and be digested."

"Pomona's right," chimed in Flitwick. "Something unexpected comes up and they respond without thinking. It will sort itself out given a little time. Like the Slytherin parents."

"What do you mean?" Snape was suspicious and defensive.

"Correct me if I'm wrong," Flitwick answered, "but haven't the Slytherin students known from the beginning of last term that there was a Death Eater on staff? Even before You-Know-Who fell, and you might really have been dangerous? I mean, we were all wondering about you and what you'd been doing for three years, but some of them knew for certain."

"I am curious," said Dumbledore. "What made you wonder?"

McGonagall raised her chin and glared at the headmaster in defiance. "You can't honestly think we're such dunderheads as that, Albus. You bring in a child to teach, a boy who tells us he's had no regular employment since he graduated, and yet he's clearly had the experience of setting up a large potions workshop and has been `tutoring' people older than himself, and who comes close to panicking at the thought of an auror on staff... What were we to think? And then the other things."

"Such as?"

"He saw the thestrals and it surprised him, so he's watched people die since he graduated. He collapsed at the news that You-Know-Who was destroyed. You think you're so devious, Albus, but really it was as clear as the nose on your face that Severus was a Death Eater, even before they arrested him in December."

McGonagall's words flowed around Snape like water around the pilings of a bridge, hardly affecting him at all for, locked down as tightly as he was, they couldn't reach the inner core of feeling. Nothing could. He watched her as calmly as if he were watching a performance, then turned to Dumbledore, whose duty it was to respond.

"I am properly contrite, Minerva," said Dumbledore. "I am not as clever as I thought I was. We may then accept as probable that there will be no defections from Slytherin house because this is not news to them. A few of those leaving may change their minds and return. Others may ask to leave as word leaks out. It is a mutable situation. Well! Now that you know the worst, what do you all say to supper? The elves should be laying out the meal shortly, and I for one am famished. Severus, would you walk with me, please? I wanted to ask you about the situation in Poland, and I have only recently discovered that people are playing with these strange little cubes, nine faces to a side..."

The majority of the student body, released earlier than expected by the quick end to the Quidditch game, was already in the Great Hall when Dumbledore and the professors arrived. At once, the glances and whispers began. Dumbledore laid his right hand on Snape's right shoulder, seeming engrossed in their conversation, his encircling arm guaranteeing protection, both psychological and physical as the staff made their way to the high table.

Snape could tell immediately which were the students who were leaving. All of them seemed either downcast or angry, and were surrounded by commiserating housemates. It suddenly occurred to him that among the nearly three hundred students, there must be a few who were naturally skilled in legilimency. \emph{I can't let them see how much this situation affects me, how much it hurts. They can't see.} And he left his defenses up, as strong as he could make them.

The professors chatted amicably during dinner, and as the meal was ending, Flitwick suggested a game of cribbage in the Hall. Snape didn't want to stay there, under the eyes of the whole school like a fish in a tank, but he realized what Flitwick was trying to do and stayed long enough for two games, by which time most of the students had filtered out of the Hall for the library or their dormitories, it still being far too cold to go strolling outside at night.

McGonagall suggested the staffroom for the teachers, but Snape offered his excuses, saying he was tired and preferred to rest a bit before he had to make his rounds. They wished him a pleasant night.

"I see what you meant about him," said Sprout as she accepted another butterbeer from the staffroom stores. "It gave me the shivers just looking at him. I had no idea his eyes were so dark, like pieces of jet. And nothing behind them, nothing at all."

McGonagall had an `I-told-you-so' smirk on her face. "Now, my dear, you just imagine standing out there with the first years preparing for sorting and seeing those identical eyes on an eleven-year-old only about this tall. Shifty little boy who never would look anybody in the face. I wouldn't be surprised if all this butter-wouldn't-melt-in-my-mouth politeness wasn't just an act, and the real Severus Snape was reappearing. Tonight was more the way I remember him from school.

"I don't know, Minerva," Flitwick mused, "he's been through a lot in the last few months. It would put a strain on anyone."

"On probation, Albus said. The Ministry wouldn't do that unless there was something he was guilty of. Now that we know he was one of them, I won't feel comfortable until I have some answers. Like what was he teaching to people older than himself? Not potions. Curses, probably, or dark magic. And who did he watch die? How many? Under what circumstances? And why did he come to Hogwarts looking for a teaching position before You-Know-Who died? Answer me that one! His presence here was for some dark purpose."

Sprout was thoughtful. "He did react rather strongly to news of You-Know-Who's death. You don't usually have a nervous breakdown over the death of someone you hate and fear."

"Nervous breakdown! Rumor says he tried to kill himself."

"Maybe that's nothing more than a rumor," said Flitwick. "Maybe he was distraught over the death of the Potters."

"Come now, Filius! He hated James Potter. I wouldn't be surprised to learn he was pleased at Potter's death. I'll bet he collapsed because he knew the jig was up, he knew he'd be called to account. He was sent to Hogwarts for no good, and he was about to be arrested and tried, and he couldn't face it."

"Be logical, Minerva. If he's really that bad, why is Albus going to such lengths to take care of him?" Flitwick sat back in his chair with the air of a man who'd just scotched an opponent.

McGonagall glared at Flitwick as she paused to think. "I don't know," she said finally. "He never showed any fondness for Master Snape while he was a student. The boy never visited Hogwarts after he graduated. If Trelawney's telling the truth, he showed up over two years ago looking for a job and was tossed on his ear for eavesdropping. That was probably on You-Know-Who's orders, too. Then last year he's sent back to try again, and Albus gives him everything he wants. It's a mystery."

"It's ten o'clock," said Sprout. "Time to see the children are all in bed." The three professors wished each other good night and left for their rounds and a good night's sleep.

Snape rested that evening by sitting in front of a small fire staring at the flames until it was time to make his rounds. As much as possible, he emptied his mind by forcing unwanted thoughts down into the sealed areas of his brain. Red, yellow, orange, and blue danced before his eyes, and he let it mesmerize him, the semiconscious state being at the moment preferable to most others.

At ten o'clock, Snape rose and left the dungeon for his outside rounds. It was still bitterly cold at night, one of the coldest winters on record. He paused at the cliff edge to look down at the lake, but had no intention of going down. It did remind him of his dream the month before, and the admonition not to stop fighting.

\emph{It would be so much easier if I knew where it would end, but it seems it's never going to end. Just when I've gotten through one trial, a new one rises up and the battle goes on. I don't know if I have enough strength to keep fighting. I'm just so tired and it's all so discouraging.}

Sunday brought empty seats at the Gryffindor table, Peterson among the missing. "Too bad none of their Quidditch players are going," said Algie when Snape paused by the Slytherin table on his way out of the Hall.

"What are you planning?"

"Well, Professor, whoever wins the next one is at least neck and neck with Gryffindor, and maybe even way ahead depending on the score. If we win, then Ravenclaw's out of the running, and Hufflepuff's only hope is a tremendously high scoring win against Ravenclaw plus a Gryffindor win against us. But if we win the last game, it's us all alone in first place with the Cup. If we lose, it could be a three-way point decision for the Cup. On the other hand, if Ravenclaw wins, it'll be a point decision between whoever wins the Ravenclaw-Hufflepuff game and whoever wins our game against Gryffindor. So we have to work on scoring and scoring high. A quick, low-scoring Seeker win could scuttle our Cup chances."

"So it's a Chasers' game?"

"If we can do it. Problem is, they're good on offense, and we're good on defense. It's going to be hard for us to rack up the points."

"Won't they be trying for a high-scoring game as well?"

"That's right, sir," Algie grinned. "At least we shouldn't have to worry about a fluke Seeker win fifteen minutes into the game. Ravenclaw needs the points, too."

Snape spent most of the day alone in his rooms. There really wasn't anything to do there, but he wanted primarily to avoid people's eyes. He hadn't been able to leave Hogwarts since Halloween except for the trips to the Ministry for interrogation, arraignment, and trial, and he was beginning to hate the castle intensely. It might not have been so bad if he could spend more time outside, but it was too cold. He looked through his books and noticed the cookbooks he'd bought when the world still seemed good - they held no interest for him now. Finally, Snape lay down on the bed facing the wall, locked inside himself, trying to think of absolutely nothing. After a while, he slept.

Dumbledore left early in the afternoon to visit Moody and the Longbottoms in the hospital. He returned around supper time and went to his office to meditate.

McGonagall cornered Hagrid at supper. "How well did you know Professor Snape when he was a student here?"

"'Bout as well as most, which is t' say not well at all. Has he been in the Hall today, had somewhat t' eat?"

"I saw him earlier, he was fine."

"Was he eating?"

"I believe so. Now, tell me what you know."

"Ain't much to tell. Quiet boy, but deep. Calm on the surface, but a lot going on underneath. Never liked to give hisself away, that one."

"I don't recall his having many friends."

"He weren't the type. Didn't have the knack. I never knew of any but the one... Well, that's not my business. His feeding now, that were my business 'cause he weren't never in the best of health - nervous and all. Are you sure he was eating?"

McGonagall assured Hagrid that she'd seen Professor Snape consume food earlier that day, and then Hagrid returned to his hut for the evening, leaving McGonagall dissatisfied with the paucity of information she'd received and wondering who `the one' was that Hagrid had mentioned.

\subsection{Monday, February 8, 1982}

Snape dragged himself out of bed shortly before seven o'clock on Monday morning, not wanting to face the day but seeing no way out of it. Throwing on his robes and not bothering even to run a comb through his hair, he slouched to the Great Hall. There he found the one thing powerful enough to lure him so far from his own rooms that day - coffee. He poured a cup and returned to the dungeons, just managing to avoid Hagrid, who came into the castle a moment later.

"Professor Snape been to breakfast yet?" Hagrid asked Flitwick.

"He was just here. Came in and left right away, I imagine."

"Did he eat?"

"I think he took a plate back with him. He may be working on something."

Hagrid grunted and sat down to his own breakfast, reasonably content that his charge was obeying the rules.

The first morning class was hell. Three Gryffindor students had departed over the weekend, and the cauldron groups had to be rearranged, with one student lacking a partner. The Gryffindors as a whole glared and muttered at Snape, too low for him to chastise them as they mixed their potions, but too loud to completely ignore. He was certain that everything they did wrong was done on purpose to stretch his patience to the breaking point. \emph{They're hoping I'll strike one of them so they can get me fired.}

"Don't tell me you didn't burn something in this cauldron. I smell smoke. I see soot. You may think I'm an idiot, but this idiot determines your grade."

"What possible resemblance could you see between Iceland moss and centipede scales? Perhaps that \emph{Centraria Islandica} begins with the same three letters? Because I assure you, the resemblance stops there."

"Put that damned wand down and read the instructions! You do know how to read?"

Then, in the second class, a fourth year Ravenclaw student poured octopus ink into yak bile, a combination they were taught to avoid in second year. No one reacted as putrid green smoke billowed through the classroom, until Snape slammed a Potions text against a desk with a resounding thud that caused students on the far side of the room to cover their ears and yelled, "Everyone with at least half a brain into the corridor! The rest of you can stay and raise the average intelligence of the class!"

They poured out of the room then, while Snape battled the fumes, ending up with a clean classroom and a hacking cough that continued for three weeks. "And what did you do to get into Ravenclaw," he asked the offender, "bribe the Hat?"

Hagrid came by as the class was ending, sniffing the air with a sensitive nose. "Go away!" Snape snapped. "This is none of your business!"

"I weren't going t' say nothing about the class. I'm here on official business seeing as I can't find no one's seen ya eat nothing since breakfast yesterday."

"Leave me alone!"

"I hear the grub in Azkaban is right tasty. Maybe ya should be eating it."

"Maybe I should! It would be an improvement!"

Hagrid grew suddenly timid. "Ya ought not t' let the house-elves hear ya say that. They can be a mite sensitive..."

"Bugger the house-elves!" And Snape stomped off down the corridor to his office, slamming the door behind him.

There was blessed silence for all of fifteen minutes, and then Hagrid lifted the door off its hinges. He'd brought a plate of food from the Great Hall which he placed on Snape's desk before he turned to fix the door. "You eat at least half of that, now," he said.

"Why? What's the point? What good will it do?"

"It might keep ya from giving up out of sheer weakness."

"And how is that a good thing! Did it ever occur to you how much happier I'd be now if I'd given up two months ago?"

"I ain't having the selfsame argument with ya every few weeks! Ya got any idea how boring that is?"

"Then why do you do it, you big oaf?"

"'Cause strange as it seems I might happen t' like you!"

"Well that just goes to show how much of an idiot you are, doesn't it!" Snape shouted at Hagrid.

"An' you ain't talking me out of it while y're sick."

"I'm not sick!"

"Now you sit down..."

"Get out of..."

"...and eat your lunch."

"...my office!"

"PUT THAT DOWN!"

Glass shattered against the inside of the door as Snape flung a jar at Hagrid, who sidestepped neatly. Another jar followed, and a beaker, shards of glass flying as each hit, though it was clear that the door rather than Hagrid was now the target. Hagrid watched calmly as item after item was sacrificed to the storm, interfering at last only when Snape turned to the desk to seize and throw the plate of food.

"No. No, lad. Give me that. Y're eating that, not throwing it."

Snape attacked Hagrid then, his fists doing no damage whatsoever, though after a moment Hagrid held his wrists to keep the younger man from hurting himself while Snape kicked and struggled. When he began to weaken, Hagrid steered him to the desk and sat him down in the chair. Snape laid his head on the desk, cushioned on his arms, panting from the exertion.

"Feel better?" Hagrid asked.

"I hate you."

"That's a step in the right direction. Now eat yer lunch."

Snape sat up and stared at the food for the space of several heartbeats. "I don't know why you waste your time on me when I treat you so badly," he said at last.

"I been watching this coming for some time. Ya were gonna blow. Better against me than against Professor McGonagall or a student 'cause ya can't hurt me."

Picking up the fork, Snape began to play with the food. When he finally put some of it into his mouth, Hagrid sat in one of the chairs and leaned back against the counter. "I don't think this is ever going to stop," Snape said. "It just keeps getting worse and worse."

"Ya been through bad times before. Ya got to weather it."

"But always before when things got bad I could at least say there was still something good and clean in the world. Something untouched by trouble. I can't do that anymore. She's gone. It's a cold, dark world, Hagrid."

"Thought she told ya not to stop fighting."

"Do you think that really was her?"

"Don' know. Tell me, what's the worst thing that's happening right now."

"The students. I hate the students. They're all out to make me miserable. They want me fired. I'd leave if I had anywhere to go."

"D' ya hate all of them?"

"Every single one."

"Colfax?"

"Algie? Well, no. Not Algie. He's pretty decent, and besides, he's wrapped up in Quidditch."

"What about the other Slytherin students?"

"On the whole, they're a good group."

"Any Hufflepuffs or Ravenclaws that just mind their own business and do their work?"

"You're right. It isn't all the students. It just feels like all the students."

"Yer problem is, ya got t' get out of here for a bit. I'm goin' t' ask Professor Dumbledore t' cancel yer classes for the afternoon, and me and you 're going somewhere."

"Where?"

"You think about it."

Hagrid left, and In the short time it took for him to return, Snape had changed into more muggle-friendly attire, but reality had also raised its ugly head. "I can't go anywhere," Snape said. when Hagrid walked into the office.

"Why not?"

"The moment I set foot outside Hogwarts, the Ministry types will be after me."

"Doubt it. I'm acting in the capacity of what ya might call a bodyguard. Ain't nobody going t' interfere. Now, where do ya want t' go?"

"I can't. I was warned not to leave Hogwarts. They'll come for me. They'll say I did something wrong while I was outside, and they'll come..." He was locking down again as his sense of danger rose.

Hagrid gripped Snape's arms and peered into his eyes. "Don't do that, lad. Don't shut everyone out. We won't go anywhere, and you just open up again."

"You can't read me."

"Don't have to. I can see the look on yer face. We won't leave Hogwarts, but we'll get out of this castle. Come on down to my place where it's friendlier like."

Snape bundled himself in a warm, hooded cloak and, after checking the door to be sure Hagrid had replaced it properly, went with him into the cold, white world outside. Snow hadn't fallen for a while, but it lay heavily around them, and the cold was like a vise clamping Snape's head. It was good that Hagrid's hut wasn't far. "It wasn't this cold Saturday for the Quidditch match," he commented.

"I suspect Professor Dumbledore had somewhat t' do with that," replied Hagrid, ushering Snape into the hut and then poking at the fire, laying on more wood and getting it blazing. "Yer rooms are mighty cold, too, ya know."

"I'm used to it."

"I think it's a drain, ya know, physically, t' have t' fight the cold when y're feeling poorly. A lot of what ails a man's brain comes from not taking care of the body. Ya ought t' have a good fire in there, and eat proper, and take care of yer appearance..."

That got a derisive snort from Snape. "Me? Appearance? I thought you were supposed to cheer me up."

"You ain't bad looking. Got an interesting face. Roman nose."

"Roman! Don't mock the afflicted. And my poor little head trembling under the weight of it."

Hagrid forged ahead. "Y're not tall, but y're not that short, and y're what they call slender..."

"Skinny. Look at me. Face and hair from my mother, nose and chin from my father, stature and teeth from poor nutrition - the worst of all possible worlds."

"Ever thought of cutting yer hair?"

A trace of sadness flitted across Snape's face. "No. Not now, for certain."

"I give up. Here, make yerself useful." Hagrid pulled out a huge tub of peas. "Help me shell these. The thestrals love the pods. I chop 'em up for winter feed."

They sat in comfortable silence for a while, shelling the peas. The simple, domestic task had a calming effect, and Snape felt some of the locks unfastening, the doors opening, releasing memories that hadn't surfaced in more than a year, overshadowed in recent months by more urgent things. Voices that reflected and expressed his feelings better than he ever could. \emph{Everywhere people stare, each and every day. I can see them laugh at me... How can I even try? I can never win. Hearing them - seeing them - in the state I'm in... Why do the people I care about have to die?}

Hagrid was talking about thestrals and their winter habits, and Snape was listening, at least with half his mind. The other half was free floating, sorting through the mystery of sudden, unexpected death - of cars in ditches, strokes and heart attacks, burning buildings, guns on city streets, and curses on the lips of madmen. \emph{Here I stand, head in hand, turn my face to the wall. If she's gone, I can't go on... But I have to go on. That's what she said. It is a consummation devoutly to be wished, but I have promises to keep, and miles to go before I sleep.}

The meditation did not, could not, ease the bitterness, but it gave Snape order, context, and lifted some of the depression. As Hagrid's soothing voice flowed around him, Snape began to feel he could go on, could face his enemies and detractors and show them he wasn't cowed. Maybe he could never win, but he would give them a fight for their money.

In sudden shock and realization, Snape looked at the pea pod in his hands. "Hagrid," he asked, "how do you get fresh peas in February?"

Peas in February were a trade secret, one that Hagrid steadfastly refused to divulge. "Y're feeling a bit more chipper, though," he said. "Didn't really have t' do anything, just get out of those stone walls."

The two trudged back up the hill shortly before supper, and Hagrid sent Snape to his rooms to tidy up before coming to the Hall. Hagrid went directly into the Hall, which was still mostly empty, the tables not yet laid for the meal. Dumbledore was already at the high table, waiting.

"How is he doing?" Dumbledore asked, "And where did you go?"

"No place. He got the heebie jeebies again and wouldn't leave the grounds. I meet that Scrimgeour fellow in Knockturn Alley, and I'm goin' t' spread him all over the walls. All my hard work falling to pieces. We went t' my place and shelled peas for the thestrals."

"A total change of atmosphere and occupation in an accepting environment. It might have done him good. What did you talk about?"

"I talked about thestrals. He didn't hardly do no talking at all. Didn't seem to be half listening. I sort o' got the feeling he was thinking things through. Kind o' melancholy, but not so brittle, if ya know what I mean."

"Open or closed?"

"Fair open, I think. I could see a ways past his eyes, bit like a normal person for once and..." McGonagall came into the Hall and to her seat next to Dumbledore, effectively changing the conversation.

A few minutes later Snape came into the Hall as well, looking much neater and more presentable than he had that morning. He spoke to several of the Slytherin students, ignored the looks from the other houses, and greeted his fellow teachers at the high table, paying particular attention to McGonagall.

"Excuse me, Professor, but are you by any chance going off grounds this evening? Maybe to town?"

"If by `town' you mean London, no, I'm not. I'm going home to my family. But I'll be in a town if that can help you."

"Perhaps. The larger towns have bookstores open into the evening. I'd like to get a book, but I wouldn't want you to go out of your way."

"And what book would that be?"

"The complete works of William Shakespeare. I imagine it's kind of a standard thing that most book shops carry. It doesn't have to be anything fancy." Snape pulled a twenty-pound note from a pocket. "It wouldn't cost this much, I don't think"

McGonagall scrutinized the note. "Muggle money? How quaint. Well, if I'm near a shop, I'll check."

"Thank you."

The rest of the evening was peaceful. The students went off to the library or their dormitories, the commuting teachers left for home, and the onsite staff retired to the staffroom, where Flitwick eagerly requested - almost demanded - a game of cribbage.

"I think I've created a monster," Snape told him as he went to his own rooms for the board and cards. They played several games, after which Snape suggested leaving the board in the staffroom, which Flitwick considered an excellent idea.

Back in his own rooms for the rest of the evening, Snape first lit a fire in the fireplace and opened the door to his bedroom so that the heat could penetrate there as well. \emph{Hagrid's right. It's one thing to forego a fire on a chilly night, and totally different when it gets this cold. I'm just helping defeat myself.}

He rearranged the furniture in the bedroom as well, placing the bed with the headboard against the wall and extending into the room. It was awkward for moving around the room, but at least when he lay on his side he wouldn't be staring at a wall. \emph{They're not going to crush me. I won't let them beat me down. I'm going to fight.}

At ten he made his usual rounds, taking his time, and just before eleven he contrived to be outside under the moon and the stars. A voice, low but carrying in the cold, dry air, called his name. "Severus, are you waiting for me?" It was McGonagall, wrapped in a heavy cloak, coming up the hill from her weekly evening off.

"Should I be?" Snape asked.

It was the third day of the full moon, and there was plenty of light to see the little package that McGonagall held out to him. "I believe so," she said. "It was most interesting, seeing the inside of a muggle shop and counting muggle money. Here's what's left."

Snape thanked her profusely, took the money and the book, and hurried to his rooms. He already knew where he was going to start. He opened the book to Act I, Scene I of \emph{Hamlet}.

It was hard reading, as Snape struggled through the archaic language trying to decipher the meanings of words like `moiety', `joint-labourer', and `romage'. \emph{I thought I was reasonably intelligent, but I'll need a dictionary to read this play.} Then he came to Hamlet's first soliloquy.

"O, that this too, too solid flesh would melt, thaw, and resolve itself into a dew! Or that the Everlasting had not fix'd his canon 'gainst self-slaughter... How weary, stale, flat, and unprofitable seem to me all the uses of this world... 'tis an unweeded garden that grows to seed; things rank and gross in nature possess it merely. That it should come to this... It is not, nor it cannot come to good; but break, my heart - for I must hold my tongue!"

\emph{Weary, stale, flat, and unprofitable, and he wants to die - that's exactly how I feel right now. The world seems so empty and ugly. And I can't say what I want to say, even if my heart is breaking... How does this man who lived four hundred years ago know what I'm feeling right now?}

Even though it was quite late, Snape continued until the end of the first act, where he made another discovery. \emph{This is a murder mystery! Is that really his father's ghost? Was his father really murdered by his uncle?} It was late, and Snape had to go to bed to be able to teach his classes the next day, but he now had something to pull his thoughts out of black depression - a murder mystery with a character who understood how he felt.

The next morning, Snape took his book to breakfast, where he reread Act I. This was important, since in a murder mystery you needed to catch all the clues, and the language was so hard to understand. That was when he began to notice other things, the first being that people didn't seem to trust Hamlet. Polonius thought Hamlet was trying to seduce his daughter Ophelia, and so did her brother Laertes. And Hamlet talked too much, a strange, almost babbling way of talking when he was trying to hide something. \emph{Is it possible that he's crazy, and there isn't really a ghost? The others saw it too, but it didn't talk to them. What if Hamlet goes after his uncle, but the uncle is really innocent?}

Potions classes were as bad as ever, and Snape had to snap at and admonish students in every session, but he felt no desire to strike anyone because somehow his priorities had shifted and the students had diminished in importance. The material was important, student understanding and performance were important, but their opinions were not. They irritated him, but not enough to wake the demon, and during the whole morning his voice never rose above a conversational tone.

At lunch he was once again deep into the mystery of Hamlet. \emph{Is he really going crazy, or just pretending? And what kind of father is Polonius, to send spies to check on his son?} Then, suddenly, another line touched Severus.

"-Denmark's a prison.

-Then is the world one.

-A goodly one, in which there are many confines, wards, and dungeons, Denmark being one o' the worst.

-We think not so, my lord.

-Why, then, 'tis none to you; for there is nothing either good or bad, but thinking makes it so; to me it is a prison."

\emph{All I have to do is substitute Hogwarts for Denmark, and I could say the same thing.}

Then, Hamlet's plan - to have the players reenact the murder described by the ghost and watch his uncle's reaction. \emph{Now maybe we'll find out if Claudius is really a murderer!}

"I take it," Dumbledore said to McGonagall, "that you got him the book he asked for?"

"It turned out to be quite easy. The girl in the shop knew exactly what it was and got it for me in a minute. I don't think I was five minutes in the shop."

"It certainly seems to be doing good. It has taken him completely out of himself. Such a complete transformation in twenty-four hours! I wonder which one he is reading."

"You could ask."

"Not yet. I do not wish to disturb the process by making him aware that he is being observed. Much better if he considers it a completely private experience. Maybe in a day or two."

Then of course, at supper, Snape hit the speech, Dumbledore's speech, the `sleep of death' speech. `Conscience does make cowards of us all. Dread makes us rather bear those ills we have than fly to others that we know not of.' \emph{I can bear Hogwarts. It's that undiscovered country, the aurors and Azkaban, that keeps me a prisoner here.} It was by no means a new thought. He'd understood that since the day of his trial, but miraculously Shakespeare understood it, too. Understood it and expressed it in words far better than Snape's own.

Momentarily abandoning Hamlet, Snape skimmed the sonnets and found one - his sonnet: "When in disgrace with fortune and men's eyes, I all alone beweep my outcast state, and trouble deaf Heaven with my bootless cries, and look upon myself, and curse my fate... Haply I think on thee... For thy sweet love remembered such wealth brings, that then I scorn to change my state with kings."

Shakespeare was right. If Lily had thought him good enough to be her friend, he could hold that memory, like a shield, against the whole world.

Then, suddenly, Snape hated Hamlet. He didn't hate the play, he hated the character, and sought out Hagrid to explain to him why.

"He's not content with killing the man he thinks murdered his father, he wants to send him to hell. He has an opportunity, while his uncle's praying, but he won't do it because then his uncle might go to heaven, and Hamlet wants him damned. Do you understand the concept of damned, Hagrid?"

"Can't rightly say as I do."

"Well it's forever, it's for eternity. It's until the end of time. It's horrible. And then, he goes right to his mother's room, hears someone behind a curtain, thinks it's his uncle, and kills him without checking to see if he's right. He just saw his uncle praying - why did he think he was behind the curtain? And he doesn't care that he killed Polonius. Do you know what he says about this man he's just killed? He says, `I'll lug the guts into the neighbour room.' The guts! He doesn't even remember he's human!"

"You goin' t' stop reading it, then?"

"Are you kidding! I want to find out if Hamlet gets what he deserves!"

The next morning at breakfast, Snape was so engrossed in Act IV that he scarcely heard the other teachers as they came into the Hall and said good morning. Hagrid, however, wouldn't let the rest of them bother Snape, for next to him was a plate of food, and though his eating was absent-minded, he was eating.

Hagrid moved away from the table as Snape stood, on his way now to his morning classes. "How's it going with that young rapscallion?"

"It's getting a lot more complex. The king really did kill Hamlet's father, but he seems sorry for it and trying to do good, but now that Polonius is dead he's plotting different ways to kill Hamlet. Ophelia's gone mad and drowned, and her brother's come back secretly from France to kill Hamlet. He and the king are working together. Hamlet's decided he has to stop fooling around, get down to business and kill the king. The only nice person is the queen, except Hamlet keeps saying such funny things that it's hard not to like him."

"What's he say?"

"That worms eat dead people, then we use the worms to catch fish, and we eat the fish, and thus a king may progress through the guts of a beggar. Then he tells the king that when a man and a woman get married they become one flesh, so now Hamlet says the king is his mother. The poor king doesn't know what to say when Hamlet tells him `Goodbye, mother' in front of everybody. I'm beginning to like him again."

"I'll be interested in knowing how this one ends. You be sure t' tell me."

Two more Gryffindor students were gone from Wednesday's first session, which contained sixth years from all houses. As Snape moved their former cauldron partners, another Gryffindor student said to a housemate, "I guess they couldn't stand the stench of eating death anymore."

Snape turned slowly and quietly, his anger and bitterness now tightly controlled, his voice soft and caressing. "Have you ever considered, Gregson, the proper function of a maggot?" He stopped by the boy's station, leaning forward slightly, one hand on the desk, the other on the back of Gregson's chair. "We fat all creatures else to fat us, and we fat ourselves for maggots. Your body becomes a very busy place in the grave." His voice now just audible in the silent room, Snape whispered, "We don't eat death, Gregson. Death eats us."

Gregson was white as a sheet as Snape, rigidly calm, moved to the front of the class to begin the lesson. He noted that while the Slytherin students seemed highly amused, the Ravenclaw students were jotting down what he'd said. Hufflepuff students were checking their indexes for potions containing maggots, and the Gryffindors seemed shaken and angry. \emph{Interesting how the personalities of the houses are reflected.} Snape never referred to the incident throughout the rest of the lesson, but it was the best behaved class he'd had all year. 


