% A Difference in the Family: The Snape Chronicles (Rannaro)
% What Of My Soul, Dumbledore?

\chapter{Out of the Depths}

Snape did return to the lion's den that evening. Taken straight to the Dark Lord, he reported on his task.

"Fletcher frequents certain taverns south of the Thames. I'm going to try to contact him tomorrow evening and start cultivating him. It may take a few days to build up his confidence in me enough to start pumping him for information."

"Do not let it take too long," the Dark Lord warned. "We should not like over-caution to defeat us of our victory."

Snape did indeed locate Mundungus Fletcher in a nondescript tavern and, after a moment of consternation on Fletcher's part, bought him a pint. The Confundus charm was fairly easy after that, except that Snape had to concentrate to be sure Fletcher understood.

"You will suggest to the Order of the Phoenix that they use decoys," Snape planted in Fletcher's brain. "Polyjuice Potion. Identical Potters. It is the only thing that might work. You will forget that I have suggested this. You will present it as your own idea. You understand?"

"I understand," Fletcher murmured, and Snape left him to his pint.

After that came the waiting. Nothing much happened for a week and a half except that the Death Eater debate over blood purity became a public topic. On the sixteenth, while enjoying a cup of coffee in a Chelsea shop, Snape noticed in the \emph{Prophet}, which he had concealed behind a copy of the Guardian, that his erstwhile colleague, Professor Burbage, had written a rather impassioned plea for tolerance and wizard\slash muggle cooperation. The thought \emph{I wonder if she knows how brave that is?} flitted through his mind, and then the article was forgotten.

On the twenty-first, it hit. That evening the locket Snape carried began to vibrate, and he opened it as soon as he could find a guarded spot. "Severus," said the tiny portrait of Dumbledore, "you must act at once. Law Enforcement is taken. We got a report two hours ago that Pius Thicknesse began acting strangely during the afternoon, and now our informant has disappeared. We can only assume that Thicknesse has been Imperiused. Moody is trying to contact Scrimgeour, but no success so far. It is imperative that you move now to secure your position."

Snape apparated at once to headquarters only to find that the Dark Lord was not there. "You," the register clerk said, looking relieved. "I'm supposed to contact you. There's a meeting—he just called for it now, not ten minutes ago—at the Malfoy mansion, and he wants you{\el}" Even as they spoke, the mark on Snape's left arm began to tingle.

The sun had already set and the moon, ripe in the third day of its cycle of fullness, was rising, when Snape apparated to the lane that ran next to the grounds of the Malfoy mansion in Wiltshire. The `pop' of his appearance was echoed by another `pop,' and Snape let his wand slip into his hand from the loop in his sleeve, knowing that the other wizard was drawing his wand, too. They paused, and in the moonlight Snape recognized Yaxley. He put his wand away.

"News?" Yaxley asked.

"The best," Snape replied, not one hundred percent certain he'd understood the question. Was Yaxley referring to Snape's news or the Dark Lord's news?

"Thought I might be late," Yaxley confided as they approached the driveway. "It was a little trickier than I expected. But I hope he'll be satisfied. You sound confident that your reception will be good."

Snape contented himself with a nod. As they approached the iron gates, Yaxley raised his arm in salute, and Snape did likewise, realizing the gates had been calibrated to recognize the marks on their arms. The wrought-iron barrier shimmered and let them pass.

Yaxley was clearly more nervous than he wanted to admit, for he suddenly whipped out his wand and pointed it—straight at an albino peacock—then laughed a little at his own jumpiness. "He always did himself well, Lucius. Peacocks{\el}" In the stillness, Snape could hear the trickle of a fountain.

The wheels and gears were spinning in Snape's brain, trying to cover every possibility. Yaxley was in charge of Ministry recruitment, so his presence might have something to do with Thicknesse. But then why was Yaxley worried about being late? Wouldn't he have been one of the first there? \emph{Confidence, Severus. Above all you must show confidence. If this isn't about Thicknesse, it could be about anything. Don't let the sharks smell blood in the water.}

The two men crossed the darkened entry hall and paused before a heavy wooden door. Then Snape reached forward, turned the bronze handle, and they entered.

A split second of overwhelming shock and fear, and then Snape mustered every ounce of control he possessed to maintain the look of calm that had been on his face when he entered the room, the crowded room where every person was watching him and his reactions. He did not look to the center of the room again. Affecting indifference, he waited until the Dark Lord should speak his name. And he tried to lock from his mind the images of the friendly cheerful face of the woman whose body now hung suspended head down from the ceiling above the long meeting table, the woman who for the past ten years had been a coworker, a colleague—the former Hogwarts Professor of Muggle Studies, Charity Burbage.

"Yaxley. Snape. You are very nearly late." The serpentine face shone in the moonlight that now floated through the high windows. The cold, high voice beckoned, no more than the barest hint of a threat behind it. The long, thin hand pointed to the chair on the Dark Lord's right. "Severus, here. Yaxley—beside Dolohov." Then, looking directly at Snape, the Dark Lord said, "So?"

\emph{What game is this?} Snape thought. \emph{He summoned me last. I was meant to arrive late. Even Yaxley knew he should have arrived earlier. Is this about Potter? Or about the Ministry? Or am I being tested now that he's captured Charity? Henry VIII honored those he was about to execute—is that why I sit at his right hand?} Snape kept his face blank and cold.

"My Lord, the Order of the Phoenix intends to move Harry Potter from his current place of safety on Saturday next, at nightfall." It was news. The others at the table shifted and stirred. Snape noticed Draco Malfoy in the middle of them, under the suspended form of the woman who had never taught him. \emph{The boy must be terrified.}

What came next was not unexpected. Murmuring "Saturday{\el} at nightfall," the Dark Lord fixed his red eyes on Snape's black ones and probed, probed deeply and intrusively, and Snape almost defiantly gave him the comfortable rooms in Chelsea and the coffee shop. He also gave him Mundungus Fletcher, but not Dumbledore, Moody, or McGonagall, nor the plan to have multiple Harrys, and the Dark Lord did not see the omission.

"Good. Very good. And this information comes{\el}"

"{\el} from the source we discussed," said Snape. \emph{But you knew that. Yet you chose to demonstrate to everyone at this table that I share confidences with you not shared by anyone else. Does this honor reassure or terrify me?}

Yaxley seemed suddenly to realize he was losing his chance. "My Lord," he said, leaning forward, "I've heard differently. Dawlish, the Auror, let slip that Potter won't be moved until the thirtieth, the night before the boy turns seventeen."

Snape allowed himself to smile, a sign of confidence for the benefit of the others. "My source told me that there are plans to lay a false trail; this must be it. No doubt a Confundus Charm has been placed upon Dawlish. It would not be the first time; he is known to be susceptible."

Yaxley pushed onward. "I assure you, my Lord, Dawlish seemed quite certain."

Relieved beyond measure at the opening Yaxley had unintentionally given him, Snape replied, "If he has been Confunded, naturally he is certain. I assure you, Yaxley, the Auror Office will play no further part in the protection of Harry Potter. The Order believes that we have infiltrated the Ministry."

"The Order's got one thing right, then, eh?" joked one of the wizards, and though others echoed his jibe with smirks and giggles, Snape marveled at his courage—or foolishness.

Yaxley would not be still. "My Lord, Dawlish believes an entire party of Aurors will be used to transfer the boy{\el}" The Dark Lord stopped him.

"Where are they going to hide the boy next?" he inquired of Snape, and Snape knew the largest barrier had been crossed, for he was being addressed as the expert in the matter. Beyond him Professor Burbage swung, unconscious and helpless, but to notice her now was to court death and the destruction of all hope.

"At the home of one of the Order. The place, according to the source, has been given every protection that the Order and Ministry together could provide. I think that there is little chance of taking him once he is there, my Lord, unless, of course, the Ministry has fallen before next Saturday, which might give us the opportunity to discover and undo enough of the enchantments to break through the rest."

The Dark Lord looked down the table. On his command, Yaxley confirmed Dumbledore's suspicions about Pius Thicknesse, spoke of isolating Scrimgeour within the Ministry as the next step in taking over, and added information about the Department of Magical Transport that Snape would pass on at the earliest opportunity. Information that also gave Snape a way to strengthen his position with the Dark Lord.

"The Order is eschewing any form of transport that is controlled or regulated by the Ministry; they mistrust everything to do with the place," Snape told the Dark Lord, and the Dark Lord accepted the statement as true and was pleased. He himself, he told the company, would be there that night to capture Harry Potter.

That was not good news. If the Dark Lord intended to battle the Order in person on the twenty-sixth, then Snape would have no choice but to be there, a prospect with several disadvantages, not the least being the possibility of his own death, ending Dumbledore's plans to protect Hogwarts and any chance of passing his information on to Potter about battling the Dark Lord. And, though he did not intend to harm any of his former colleagues, he was sure that in the confusion of a battle he might have to fight Lupin, or Moody, and while Moody knew, Lupin did not, and Snape would have to fight in earnest. Too, the Order would see him in the Death Eater army, and would know Potter's story to be true—regardless of what the \emph{Prophet} might say—that he, Snape, had indeed killed Dumbledore.

And the Dark Lord was also telling the assembled company that he would have to kill Harry Potter personally.

Snape glanced quickly at Greyback, the Carrows, and Yaxley. Who else had been at Hogwarts that night? Rowle? He fervently hoped they didn't put two and two together and wonder why he, Snape, had told them that same thing nearly two months before the Dark Lord made his decision known.

Two things happened next, both of them shocking though in different ways. The first was a scream, a wailing, that came up through the very floorboards. Snape did not jump or startle as the others did. Being locked down as tightly as he was gave him an advantage there. The Dark Lord sent Pettigrew to silence this second prisoner.

The next was that the Dark Lord demanded Lucius Malfoy's wand, saying he would use it to battle Potter. It was painful to watch the once-proud Malfoy forced to surrender his only weapon and submit to sneers against his loyalty like a disobedient child. \emph{He will humiliate me the same way if ever I fall from grace.}

The great snake Nagini had entered the room (or had it been watching all the time from the shadows?) and slithered its way to its master. Snape was suddenly, if possible, more alert. \emph{Something is happening. He's leading up to something. It's like a play. The first important business, the first act, is over, and here we have a humorous interlude before beginning the second act. Is this about Charity—is it about me, after all?}

It unfolded as if scripted—the impugning of the Malfoy family's devotion and then Bella, predictable, dependable Bella, jumping into the fray to defend the loyalty of her house only to be slapped down with the news that her house had been defiled by the admission of a werewolf into the family. \emph{Blood purity. This is about blood purity. But why is he taunting Bella? No one doubts her loyalty. Why humiliate Bella?}

And then it came, the theme of the second act—"Many of our oldest family trees become a little diseased over time. You must prune yours, must you not, to keep it healthy? Cut away those parts that threaten the health of the rest{\el} cut away the canker{\el} only those of the true blood remain{\el}"

Snape knew. He knew why he'd been informed last to arrive last, knew why the body of Charity Burbage hung over the table, feared that the unseen, wailing prisoner might also be a colleague, a friend—the second act was about him. Snape was being tried, and could not be found wanting.

What had not been sealed before was sealed now. No feeling, no emotion, no hesitation, could be allowed to surface. Snape shut himself utterly down, as cold now as the man testing him. With a tiny movement of Malfoy's wand, the Dark Lord brought Charity Burbage back to consciousness.

"Do you recognize our guest, Severus?" the Dark Lord asked, as all eyes turned to the hanging, twisting prisoner. All eyes but the Dark Lord's, who was staring fixedly, calculatingly, at Snape.

Before Snape could answer, Charity blinked, focused, and recognized him. "Severus! Help me!" she cried as she slowly revolved in her bonds above him.

\emph{I cannot help you. I cannot pity you. I cannot feel the smallest spark of sympathy for you, for he would know instantly. I must find within myself some moment of cold satisfaction to offer up to him, and you must die alone. May it at least be quick.} Snape forced himself to gaze coolly at Charity. "Ah, yes," he replied, and left it at that.

"For those of you who do not know," the Dark Lord said, "we are joined here tonight by Charity Burbage who, until recently, taught at Hogwarts School of Witchcraft and Wizardry{\el} taught the children of witches and wizards all about muggles{\el} how they are no different from us{\el}"

There were taunts and laughs from around the table now as almost all eyes were on the despairing Charity, who again pleaded, "Severus{\el} please{\el} please{\el}" Almost all eyes, but not those of Draco Malfoy, who kept his locked on the surface of the table, nor those of Bella Lestrange, who was now staring at Snape, too. And not those of the Dark Lord, who continued to scrutinize Snape's impassive face with unwavering attention as he detailed Charity's `crimes.'

Charity was weeping now, her pleas silenced, her fate sealed. Snape watched her, icy and calm. The Dark Lord raised his newly acquired wand, hissed, \emph{"Avada Kedavra,"} and Charity's body was allowed to fall to the table. Her ordeal was over.

But not Snape's, not quite, for now the Dark Lord stroked the great snake and murmured, "Dinner, Nagini," and Snape continued to watch, still icy and calm, as Nagini coiled its way to Charity's body, seized her in its powerful jaws, and dragged her from the room. Then he turned in his seat to meet the Dark Lord's red eyes.

"Am I just, Severus?" the Dark Lord whispered, and Snape knew he was meant to be aware of the probe.

"Such should be the fate of all who share her traitorous views. She was a disgrace to the name of witch."

The Dark Lord searched deeply and found no contradiction. He smiled and finally released Snape, addressing the whole group. "Our plans near fruition. The Ministry is under siege, and will soon be ours. The Potter boy will fall into our hands Saturday night. One bastion remains, and it will be ours within the month." He gestured toward Snape. "Tonight I would have you meet and congratulate the next headmaster of Hogwarts."

The hubbub that greeted this announcement almost drowned Bella's anguished cry of "No!" Witches and wizards pressed forward to shake Snape's hand in a general air of celebration. Snape did not celebrate. No smile touched his lips. He was sealed, locked down, and no feeling, no emotion surfaced to mar the impassiveness of his features. No emotion at all.

After the meeting, Snape requested and received permission to return to Chelsea and resume contact with Mundungus Fletcher just in case the plans of the Order changed. He apparated into the Chelsea bedroom and stood there, absolutely still, for several minutes. He had to contact Dumbledore, but struggled for the words to explain what had just happened. Deciding finally that the words would come of themselves once he began talking, he took the locket with its miniature portrait out of his desk drawer. He had not taken it to the meeting, lest it be discovered.

Dumbledore appeared at once. "You are safe," he said, clearly pleased. "What news?"

"Sir, you were correct about Pius Thicknesse. He has been Imperiused. They are planning to control everyone around Minister Scrimgeour first, and then make their move."

"And what else?" asked Dumbledore, a note of suspicion now in his voice.

"The Dark Lord has decided that the best person to propose for Hogwarts would be me."

"Severus, what is wrong? What has happened?"

"I don't understand, sir. Why are you concerned?"

"I have not seen you locked down this tightly since{\el} Severus, I have never seen you locked down quite this tightly. What happened?"

Snape stared into the portrait. Then, his voice cold and withdrawn, he said, "Charity Burbage is dead."

"Merlin! Did you have to watch it?"

"Sir, what would be the point of encompassing such a death and then not avail yourself of the strategic value of having others watch?"

"Severus! Severus, listen to me! I want you to come to Hogwarts at once!"

"That would be unwise, sir. It could jeopardize all our plans."

"I am going to contact Alastor{\el}"

"Also unwise, sir. Such contact, if it became known, would make my position highly unstable."

"Severus{\el}"

Snape closed the locket and placed it back in the desk drawer. Then he removed his shoes and lay down, fully clothed, on top of the bed, his hands folded lightly above his stomach, one ankle crossed over the other. He lay there for some time, eyes open but not really seeing the ceiling above him. There were no images floating in his brain to distress him. He had taken care of that.

\emph{I cannot lower my guard. He can come at any time of day or night, and I have to be ready. I'll never be able to lower my guard again.}

Snape rested, unmoving, through the night, but he did not sleep.

Saturday afternoon found Snape back at headquarters, where he reported to Operations along with the rest who'd been assigned to accompany the Dark Lord.

"What's this?" he asked Bella, examining the piece of cloth she thrust into his hands.

"Hood," she replied. "Standard issue." Then she looked at him with something close to disgust. "You've never gone out into the field, have you? Pathetic."

"Never. My services were needed elsewhere. Why the hoods?"

"To hide our identities. It's more frightening to be faced by an anonymous force than by people you know from other contexts."

"Less likely to be turned over to the Aurors, too."

"Are you questioning my courage?"

"No, of course not. Why ever would I do that?" \emph{And yet}, Snape thought as he fingered the hood, \emph{it does solve one of my problems. With this on, the members of the Order won't be able to identify me. It will make the Hogwarts business easier to deal with.}

They apparated, about thirty of them with the Dark Lord, to Little Whinging in Surrey. There, above the Dursley residence, they were stopped by a force like a wall surrounding the house. The Dark Lord motioned to Snape, and he went at once to his lord's side.

"Why can we not enter?" the Dark Lord inquired, and his tone said that he was not pleased.

Snape looked around at the wide circle of Death Eaters, and then down at the house far below them. "It is not yet Potter's seventeenth birthday," he said. "Prior to that, I believe the protection only ceases the moment he ceases calling the house home. That can't happen until he actually leaves it. At least that is my understanding. Dumbledore never totally confided in me about this aspect of it."

"So we wait, and if you are right, we shall be able to attack after he leaves."

"I believe so, my Lord."

They waited. The sun had set around nine o'clock and the moon would not rise until after midnight. The only light came from the street lamps and the windows of the row upon row of identical houses. Minute after minute ticked by, and Snape could see that some of the others glanced at him, knowing who he was even under the hood, maybe from the unfamiliar and slightly awkward way he sat on his broom. \emph{They suspect I've given them false information. I pray that they're wrong.}

Then they were engulfed by a roar, and Hagrid appeared in their midst astride a motorcycle with a sidecar in which sat Harry Potter. But before anyone could move, others appeared as well—on brooms, but also on thestrals, and everywhere there were Harry Potters. There was a moment's pause as each side recovered from the shock, and then the members of the Order were scattering, speeding for the different points of the compass, and the circle of Death Eaters was forced to split up as well, to give chase.

Snape paused for a second to choose. He was fairly sure that Hagrid would guard the real Harry, for Hagrid was immune to a wide variety of curses and the sidecar was extra protection. The Dark Lord, on the other hand, focused at once on Moody, and though Snape would have liked to watch the back of the only member of the Order who could protect him from the others, he did not want to be near the Dark Lord where the need to show his zeal would be greatest. He chose instead to follow Lupin, and watch Lupin's back. Even though Lupin had never watched his.

They sped upward into the night, and Lupin's `Harry' feinted and dodged with a familiar skill. \emph{A Quidditch player}, Snape thought. \emph{Who might that be? A Weasley? Charlie, Fred, George, and Ron all played Quidditch. Ginny, too, as I recall.} He tried to keep up, but the broom work was hard. As wind and backwash swept over him, the Death Eater hood blew away from Snape's face, but he was enough of an amateur in Operations, that the import of this never occurred to him.

Then another hooded Death Eater swooped by, quicker and more maneuverable on his broom than Snape. His wanded hand came up, and Snape realized he had a clear aim at Lupin's back. He pointed his own wand at the Death Eater's hand and thought, \emph{Sectumsempra!}

He missed. His familiarity with brooms, or lack of it, nearly proved fatal. The cutting curse flew cleanly past the Death Eater and struck `Harry' in the side of the head. "Good one!" cried the Death Eater next to him, revealing by his voice that he was Rookwood. "Did you get him?"

"Flesh wound, I think," replied Snape, then slowed, for Lupin and his `Harry' were now moving beyond Snape's capacity to follow, and he wanted to get back to the starting point to find out what was happening with the others. He let his companion race ahead without him.

Back at the Dursley house, not all was calm and peaceful. A form, a shadow, a body, kicked and twisted in the yard. Snape lowered his broom and dismounted, glancing up at the sky around him to see if any Death Eaters were coming back. Then he approached the struggling body.

It was Moody. It took only the lighting of a Lumos spell to show Snape that Moody had been hit in the face by an Ignis curse. The right side of his skull was charred, the hair singed away. The rest of Moody's body had been broken by the long fall, and yet he was still alive. Barely, but still alive. As Snape dropped to his knees, the enchanted blue eye swirled, made contact, and communicated in silence.

\emph{Get off me, you{\el} boyo?}

\emph{It's me. Can you move?} But Snape already knew he couldn't. Broken bones, ruptured organs—the fall had been cruel.

\emph{Where are they?} There was a desperation in Moody's unspoken voice that Snape had never heard before.

\emph{They'll be back soon. Let me help.}

\emph{No, no. I just always thought I'd go fighting, a wand in my hand. Not Moldyvort's plaything.}

\emph{Tell me what you want, and I'll do it.}

\emph{I couldn't lay that burden on you, boyo.}

Snape let the tip of his wand slip under Moody's jacket, an inch now from Moody's heart. \emph{And watching them kill you wouldn't be a burden? If you wish it, I'll do it.}

\emph{Bless you, boyo. I'll speak a good word for you when you come to the veil.}

The words of the killing curse were nonverbal, the tiny flash of green light hidden by the fabric of Moody's coat. The physical wounds were enough to explain the event, and Snape rose slowly, calm and cool, to await the return of the other Death Eaters and his Lord.

\sbreak

"Dead?" the Dark Lord hissed. "It should have lived to repay the defiance it has shown us."

"Had he fallen from a lesser height, Lord," Snape assured him, "it would have been different. As it was{\el}"

The moon had by now risen, and its light reflected off the blue eye as the Dark Lord sneered down at his fallen enemy. "Bring it, in any case. It can still provide sport, and we know the Lestranges, especially, will be amused." As a precaution, however—or maybe it was a trophy—he took the enchanted eye, leaving an empty socket in its place.

Snape was in charge of the removal of Moody's body, and watched with a bemused smile as the Death Eater operatives bounced it against sidewalk, tree, and stone, then played a modified hoop-and-stick game with the stiff, cartwheeling corpse. He did not try to imagine what they might have done with a live Moody. Such mind games were unnecessary, and interfered with his ability to shut down. Back at headquarters, the body continued to be a foil for fun and entertainment until the naturally progression of decay impaired its integrity. When that happened, it was thrown into the garbage. Snape did not interfere. It was not really Moody, only the house he had once lived in.

Meanwhile, Potter's birthday came, and the Dark Lord eagerly sought the boy's hiding place. Snape, in a less dangerous world, would have wagered his eyeteeth that it was the Weasley home, but nobody pressed him. At least nobody he was interested in wagering with.

But other things were happening as well, and the evening of Potter's birthday coincided with another important staff meeting. Only this meeting turned at once into an Operation as Bella's people handed out hoods and potions. There was plenty of Veritaserum, and other brews to impair will and ensure cooperation, in case the Imperius spells didn't work.

Their destination and their goal was the Ministry of Magic.

That very afternoon, the last cord of the net had been woven into place, and now the head of every department, and every bodyguard that surrounded the Minister, was Imperiused or bribed into the hands of the Dark Lord. Scrimgeour was ripe for plucking, and the Dark Lord wanted to be there for the harvest.

They arrived after midnight at the start of Friday, August first. Snape had no opportunity to contact Dumbledore since he didn't carry the locket with him at all times, and he'd had no chance to return to his laboratory to use it. Scrimgeour would get no warning at all.

The Imperiused heads of departments were called in. Snares were laid for Ministry officials who might try to interfere. Snape spared a brief thought for Arthur Weasley and Nymphadora Tonks, and then remembered this was the day of Bill Weasley's wedding. They would not come in to work, and were therefore safe. It was a small mercy.

Everything had long been in place when Scrimgeour arrived at eight o'clock with his bodyguard. They led him right to the trap in his office, and the doors sealed him from all possibility of aid before he was even aware he was caught.

Scrimgeour's sharp intake of breath was the only satisfaction the Dark Lord got from the Minister's surprise. "I have brought some old friends to visit you, Minister," the Dark Lord sneered, and one by one the circle of Death Eaters pushed back their hoods. Bella and the Lestrange brothers, Dolohov, Mulciber, Rookwood{\el} face after face, and every one had been a prisoner in Azkaban under the care of dementors. Every one except{\el}

"You!" Scrimgeour bellowed as Snape, too, lowered his hood. "You filthy little{\el}" And he lunged for Snape's throat, to be brought up sharply by a casual wave of the Dark Lord's wand.

"You know each other?" The Dark Lord's voice dripped sarcasm as well as surprise. "My, my. Such a small world." He seized Scrimgeour by the hair and forced his eyes around. "Incarceration, shackles, a trial{\el} our poor little potions brewer? Minister, he was barely more than a child. Those who abuse children should be punished. We shall allow Severus first blood, in a manner of speaking."

Snape was locked down and icily calm. "Lord," he said quietly. "I hope I do not disappoint you. You recall I was never in Operations and have never{\el}"

Bella threw back her head with a howl of laughter. "Never?" she shrieked. "Never cast a Cruciatus curse! That'll go high on my list of things you've never done. Almost as high{\el}"

"Bella," the Dark Lord remonstrated with the air of a kindly father, "there is always a first time. We are certain Severus will not disappoint us. Severus?"

Snape drew his wand and stepped forward. His face betrayed no more emotion than if he were about to cast a Wingardium spell on a feather. Scrimgeour followed every move with a look of pure hatred. "You little piece of owl dung," he growled. "You cockroach. And to think a decent man like Albus Dumbledore would ever consider you worth even one hair of his beard."

Snape's wand moved up, almost of its own accord, level with Scrimgeour's heart. \emph{"Crucio,"} Snape said softly, and Scrimgeour dropped to the floor, writhing in pain, for softness can still carry intent.

After several seconds, while Scrimgeour fought to keep from screaming, the Dark Lord raised his hand. "Thank you, Severus. And now it is Bella's turn."

For the rest of the session, stretching into hours, Snape only watched. The survivors of Azkaban were far too greedy for revenge to even notice he wasn't participating. Not content with the simplicity of the Cruciatus curse, they danced Scrimgeour around his office, their curses like knives, whips{\el}

After the first minutes, the Dark Lord began his interrogation, and it centered on one question: Where was Harry Potter? What blood traitor's hovel concealed the Chosen One? Scrimgeour roared his defiance and scorn and refused to answer. They continued. The office was spattered with flecks of blood; the Dark Lord's ire mounted until he joined his Death Eaters and added his power to Scrimgeour's torment as afternoon melted into evening.

And then it was over. Suddenly and unexpectedly over. "NO!" the Dark Lord screamed. "Bring him back! We are not done!" Scrimgeour's limp body lay on the rug, unmoving. "Bring him back! Severus, tell us he is not dead!"

Snape knelt by the fallen Minister. To him it was obvious, but not something that would occur to a Death Eater. "It was his heart," he said. "His heart gave out. He is dead, Lord."

The Dark Lord drove a fist into the top of the desk. "He cheats us! Even now, when his Ministry lies helpless in our hands, he cheats us! Where is Potter?"

The Dark Lord stormed to the door of the Minister's office, his team of Death Eaters fearfully watching him. "Bring them!" he cried to the Death Eaters who came running from different offices. "All the Ministry traitors not already on our side, bring them!"

"Sir," said one Death Eater who had not been with the group questioning Scrimgeour, "most of the rest aren't here." He was trembling in terror, but had to answer. "We wanted to{\el} You said you were not to be disturbed."

"Not here! Not at their posts on a Friday! Where are these slothful, slovenly excuses for workers?"

"Sir, they took the day off. To go to a wedding. Arthur Weasley's son got married today."

"Then take a force to the Weasley home and bring them here!"

All eyes were focused on the Dark Lord. Only Snape, emotionally cut off from the scene because of his defenses, noticed the flicker of movement in a painting on a side wall. A painting he'd thought was empty. The portrait of a little wizard with a toadlike face and one of the long formal wigs of the seventeenth century peered from behind the chair it usually sat on, then scurried back out of the frame.

\emph{Good}, Snape thought. \emph{I don't know whose office he connects with, but this day's work is no longer secret. People who might have been trapped will be warned.}

The Dark Lord was calming now, his face shrewd as he planned the next moves. "We must find Potter," he said, "and we must take care not to lose sources of information through carelessness or anger. We have lost this one,"—he nudged Scrimgeour's body with his foot—"we shall lose no more except by deliberate choice. Interrogate all as to Potter's whereabouts, but do not kill. And do not," he looked significantly at Bella, "drive insane."

Parties of Death Eaters—Death Eaters and tame Ministry workers—were sent out, not just to the Weasley home, but to homes of others known to be associated with the Order of the Phoenix. Still the Dark Lord pondered. He questioned his new servants. "How can we locate one wizard among many?" he asked. "The Ministry does it all the time. How?" He was talking now to Pius Thicknesse, head of Magical Law Enforcement.

"We have dossiers on most people," Thicknesse responded. "The easiest way is a Taboo, if you know a unique habit the person has. Let's say you want a wizard and know he puts treacle in his coffee. That's a very uncommon habit. You place a Taboo on flavoring coffee with treacle, and the next time he does it, the Ministry knows where he is."

"What does Potter do that no one else does?" the Dark Lord asked, then answered his own question. "The boy is arrogant, defiant, insulting. We understand that he commonly speaks our name, which none in the wizarding world do. We shall punish his arrogance. Place a Taboo on the speaking of the name Voldemort."

The Taboo worked. Rowle and Dolohov thought they had Potter cornered in London, but he slipped through their fingers. They were reminded of the consequences of disappointing the Dark Lord. Then the Dark Lord's name was mentioned repeatedly in Grimmauld Place. Potter had fled to Number 12.

Snape was questioned again about how to enter the headquarters of the Order. Thanks to Moody's curses, he could give no information. The Dark Lord scanned and probed him for long, exhausting hours, and was satisfied that the information was no longer there. A guard was set in the square to catch Potter should he ever appear in front of them.

With the Ministry in their hands, the Dark Lord ceased using headquarters, taking up more or less permanent residence in the Malfoy mansion, taking pleasure in toying with Lucius's fears. Snape kept up constant attendance either on the Dark Lord in Wiltshire or at the Ministry. He no longer had the opportunity to be alone in his laboratory where the locket with Dumbledore's portrait remained concealed.

And all through August, the Dark Lord's plans for Snape and for Hogwarts unfolded.

One Ministry employee who came into the Dark Lord's camp immediately and eagerly was Dolores Umbridge. Her obsession with blood purity was as intense as the Dark Lord's and it was a wonder that she'd not been a Death Eater before.

"Good morning, Professor Snape," she said cheerfully when he arrived at the Ministry on the fifteenth, exactly two weeks after the coup. The Board of Governors for Hogwarts was now required to hold its meetings in a Ministry conference room, and Snape was there for his formal interview. Clearly Umbridge intended to sit in on the meeting.

"Good morning," Snape replied. "I trust I am not late."

"Very punctual, in fact. Shall we?"

They entered a wood-paneled room with a long, wide table. The twelve members of the Board looked around when the door opened. They had been standing or sitting in small groups, but now went directly to their seats, ranged along one side of the table. Umbridge marched to a chair at the head and settled into it.

"Professor Snape," said the Chairman of the Board, a stout, businesslike wizard named Sandro McPherson, "there is no need for you to stand. Please, be seated." He indicated a chair that stood alone on the other side of the table where every member of the Board would be able to see Snape's face.

"You come very highly recommended, Professor," McPherson continued. "We have most of the information from your file, though we'd appreciate hearing some of it in your own words. You attended Hogwarts as a student, no?"

"Yes, Mr.~Chairman, from September 1971 until June 1978."

"OWL results?"

"Outstanding in Potions, Charms, Herbology, Astronomy, and Defense against the Dark Arts. Exceeds Expectations in the others."

"Electives?"

"Arithmancy and Ancient Runes."

"Did you ever take Muggle Studies."

"No. I had no interest in Muggle Studies."

A stylishly dressed younger witch, closer to Snape's age, leaned forward. "What is your blood status, Professor? I hope you don't mind my asking."

"Not at all. It is a matter of the gravest concern to anyone who cares about the education of young witches and wizards. I am a half-blood."

"Dear, dear. And which parent was the{\el} you know?"

"My father was a muggle. My mother was pureblood."

"And the bloodlines, both sides if possible."

Snape didn't flicker an eyelash. "Prince, Rossendale, Hewitt{\el}" he began, and continued with a list of pureblood names—provincial, but pureblood. "I fear I cannot do the same for my father's side, which never interested me much. My father and I had a rather strained relationship."

"How many years have you been teaching at Hogwarts?" inquired an older woman.

"September will begin my seventeenth year."

"What administrative experience have you had, Professor?" asked a white-haired wizard.

"I have been head of Slytherin house since my first year. In addition, I was usually the one assigned to familiarize new staff with their duties."

"Why you? Why not the Deputy Headmistress?"

"I presume because Headmaster Dumbledore considered me competent for the task. It always coincided with that period of the year—August—when the Deputy Headmistress had the most work to do concerning the incoming students. Headmaster Dumbledore felt it better to split the labor rather than impose it all on one person."

There were nods around the table. McPherson asked, "Why were you never given the job of Deputy Headmaster?"

"Hogwarts already had a Deputy Headmistress of great administrative competence, a trait common to persons of her cultural background, I have heard. There was never any need to look for another Deputy. The matter never came up." There were smiles then, as it was well known that McPherson was deeply proud of his own Scottish heritage.

Umbridge coughed slightly. "But does Professor McGonagall respect the new laws. It was my understanding she promotes the welfare of{\el} well, mudbloods."

"Professor McGonagall," said Snape carefully, "has great respect for the Ministry, for the Board of Governors, and for the law. She obeys the rules and the law. She does not presume to question or second-guess them. Both the Ministry and the Board told her that it was her duty to integrate persons of muggle background into the school. She followed instructions and did not allow her own prejudices to interfere with her duty. Now that the rules and laws have changed, Professor McGonagall will continue to do her duty."

"Well-spoken!" cried the white-haired wizard, and McPherson looked immensely pleased. Umbridge did not, but she had no vote on the Board. \emph{She has to support me in any case,} Snape thought. \emph{She knows I'm the Dark Lord's choice, even if these others don't.}

"Tell us your understanding of the new laws, Professor," said the younger witch.

"They are there to protect the rights of persons of magical blood from persecution by the nonmagical world. They wish to destroy us, and we must protect ourselves. Persons of nonmagical blood who have usurped the power to perform magic must be identified so that they can be controlled. They must not be allowed to increase their powers, and so must be denied a magical education. Because the wizarding world outside Britain, and unfortunately some of our own magical families, are still wandering in the errors of the past, all children of magical families must be educated at Hogwarts to ensure they learn the truth about muggles. I wish I had known the truth about muggles when I was young. My own witch grandmother was murdered by a muggle mob."

It was done. The rest of the interview was pro forma and involved only the confirmation of small details. McPherson was confident as he shook Snape's hand when it was over. "We have three others to interview, and then the formal review. We'll probably make the decision on the thirtieth and announce it on the thirty-first, but I don't think you have much to worry about. I don't see that any other candidate has your qualifications."

Umbridge waited in the corridor. "I would love it, Professor, if you'd come up to my office for tea and a little chat. You don't have another appointment anywhere, do you?"

Snape did not, and took the elevator with Umbridge up to the first floor. The atmosphere in the Ministry was strange, and many of the workers they encountered seemed anxious and worried. They passed through the waiting room where Umbridge's secretary told her, "No messages," and then Snape got a shock so powerful that it almost broke through his barriers, the barriers that were weaker today because he didn't want to shut down completely in front of the Board. The shock came when he realized that the door to Umbridge's office was decorated by Alastor Moody's enchanted blue eye.

Umbridge followed his gaze, but didn't understand his surprise. "Yes, unusual, isn't it? If someone's in my office, I can look through it and tell immediately if they're hiding something. Very useful. The Minister gave it to me. He said it comes from{\el} him. A token of appreciation for my dedication to the cause."

"And no one deserves it more," said Snape, wondering how it was possible for the Dark Lord to give up his trophy of Moody's death. There had to be more to it.

He watched Umbridge carefully as she put down the cups and poured the tea, and was reasonably satisfied that she hadn't put anything into his. As he sipped the tea, he waited for her to begin. After a moment of silence, she cleared her throat in that irritating way he remembered so well.

"It seems you are the preferred choice of the Board. I think it's not too early to offer congratulations. I wanted to talk to you about the staff at Hogwarts."

"What about the staff at Hogwarts?"

"Well{\el} oh, dear{\el} they're not all exactly, well, reliable, are they?"

"I am afraid I don't know what you're talking about." Snape was not about to let Dolores Umbridge dictate his duties to him. The Dark Lord did that, Dumbledore did that, not her.

"Think, Professor. McGonagall and her streak of rebelliousness, Sprout and her disrespect, and that little Charms teacher{\el} what is he, anyway? And the giant?"

Snape put his cup down and leaned back in his seat. "Of course you faced opposition. When you were there, the Ministry was breaking the law."

"Breaking{\el} ? How could you? How dare you?" Umbridge was sputtering, she was so shocked.

"I must ask you to listen, and to listen carefully. By law, Hogwarts operates under its own charter. It answers to the Ministry in areas where the writ of the Ministry runs, and to the Board for what is under the Board's control. That charter can be changed not by the Ministry or by the Board, but only by decision of the Wizengamot. When the Ministry passes laws concerning the extension or restriction of magic, that is its prerogative. When it tries to control staffing and administration, it is acting illegally. Two years ago, our world was in confusion, no one knew if the Dark Lord was back or not, the Ministry was in conflict with the Headmaster, and the Board was neglecting its role. But the Ministry was still acting in violation of the charter, and the teachers were defending, as best they could, the charter rights of the school. Today there is no such confusion. We're all on the same path, and the path is clear. You and the Ministry control the restriction of magic, and Hogwarts will obey you. But the Board controls administration and staff, and unless and until I receive orders from a superior authority to the contrary, I will be duty bound as Headmaster to uphold and defend the charter of the school."

Snape rose, turned on his heel, and strode from Umbridge's office.

True to McPherson's prediction, the Board of Governors of Hogwarts School of Witchcraft and Wizardry voted on Saturday, August 30, 1997, to appoint Severus Snape Headmaster of the school. He was invited to the Board's chambers in the Ministry at nine o'clock the next morning for the ceremony of instatement and the swearing of his oath, followed by a reception. It was a little rushed, doing it on a weekend, but they wanted him to be able to go to Hogwarts before the students arrived on the Express.

Snape did not look at Umbridge as he raised his right hand and swore to uphold the ancient charter of the school, though he was sure she was seething. He endured the reporters from \emph{The Daily Prophet} with their cameras and predictable questions. He chatted stiffly yet politely at the reception and responded properly to the expressions of congratulation and good wishes for the future. He had one more task appointed to him by the Dark Lord, and near the end of the reception asked McPherson if he might speak briefly to the whole Board.

They adjourned to a conference room where Snape explained that Hogwarts was still short two staff members, a Defense against the Dark Arts instructor and a Muggle Studies teacher. Since the opening of school was the next day, he wanted an emergency confirmation of the appointment of Amycus Carrow to the first job and Alecto Carrow to the second. Since three of the members of the Board had actually proposed Amycus as headmaster not two months earlier, Snape had no trouble getting the confirmation.

At one o'clock that afternoon, Snape and the Carrows apparated to Hogsmeade.

Filch was at the gate to take the little baggage they brought, and then Snape, followed respectfully (for they were under very strict orders from the Dark Lord) by the Carrows, climbed the hill to face the staff, all lined up on the lawn to greet him.

McGonagall, confirmed in her position as Deputy Headmistress and obviously remembering her last meeting with Snape, Moody, and the portrait of Dumbledore, stepped forward.

"Headmaster Snape," she said, stiffly and formally, "on behalf of the staff of Hogwarts School of Witchcraft and Wizardry, permit me to offer our congratulations on your appointment, and to welcome you back to the school. We stand ready to work with you for the good of Hogwarts, its staff and its students."

"Thank you, Professor McGonagall. I'm pleased to be here, and I know we'll all get along fine." He could tell from the guarded expressions on the faces behind her, especially Hagrid's, that they were not going to get along fine, but that everyone had, for the moment, agreed to follow McGonagall's lead. He felt pressure in the sealed places in his brain, pressure behind the locked doors.

"I know you're all very busy getting ready for the students to arrive tomorrow, and I don't want to waste any of your precious time. I'd like to have our first staff meeting, a brief one, right after dinner. Professor McGonagall, would you please show Professor Carrow and Professor Carrow to their rooms and explain tomorrow's duties to them. I'd like to go upstairs. I'll be in my office if anyone needs me."

McGonagall nodded, knowing what he wanted in the office. She and the other teachers dispersed, and Snape climbed slowly to the seventh floor, relieved that it had been easier than he'd feared.

"Password," said the gargoyle.

Snape stopped. He'd never heard the gargoyle speak before. "I'm the Headmaster," he said.

"Set the password," responded the gargoyle.

"Oh. Sorry. The password is{\el}" Snape wanted something Dumbledorish, but he was still locked tightly down, and no thought would come. "The password is Dumbledore," he said finally, resolving to change it to something less obvious when he had the chance. The gargoyle staircase opened and he went up to his office. The pressure in his head was building. He needed to be alone.

It hadn't changed. The desk, the chairs, the strange instruments and contraptions on the tables. It was as if Dumbledore might walk back in at any moment. Except that Dumbledore slumbered in his portrait behind the desk. Snape walked to the desk. With it between them, it was as if the portrait was the headmaster behind his desk and Snape still the teacher.

"Ah," said Dumbledore, blinking his eyes open. "There you are. And about time, too."

"I got here as quickly as was possible."

Dumbledore cocked his head at Snape's tone. "Dear me, Severus, I was not blaming you. You have been doing an excellent job. Excellent."

"Yes," Snape echoed dully. "Excellent." His head throbbed with the pressure.

"But Severus, you should be pleased, proud of what you have accomplished. You have taken the most important step toward protecting the school, the staff, and the students. You have removed every barrier, overcome every obstacle{\el}"

"One of those obstacles was Rufus Scrimgeour."

"I am sorry to hear that," said the portrait of Dumbledore.

"I'm sure you are." The pulse in Snape's temples was like a drumbeat.

"He was a good man. He had his faults of course{\el}"

"The Dark Lord gave me the privilege of starting. I used a Cruciatus curse on him."

"You did what you had to do."

The dam burst. "I did what you made me do!" Snape screamed, and around him astrolabes and globes swept to the floor in a great crashing of copper and crystal. "I watched Charity beg for help, and didn't lift a finger!" Books hurled against the walls and shattered two mirrors. "I killed Alastor Moody, did you know that! I laughed when they disgraced his dead body!" Chairs smashed into the fireplace and the door. "I let them take twelve hours to kill Scrimgeour! Twelve hours!" Chandeliers swung wildly, portraits sprang from the walls, windows burst open, twisting their hinges. Snape grabbed the edge of the heavy desk and upended it, lamps and quills scattering on the floor. Kicking a lamp out of the way, he flung open Dumbledore's wine cabinet and began pitching the bottles at the fireplace with every ounce of strength his thin body could muster. Glass shattered, mead splashed, and when the bottles were gone he started on the glasses. By this time he was screaming again, "Murderer! Murderer! You've damned me! Damned me! I hate you! Damned{\el} damned{\el}"

A large hand took the last glass away, and suddenly Snape was sobbing, his body wracked with pain and grief, and for some reason it was quite natural that Hagrid would be there, easing him to the floor and supporting his shoulders. He buried his face in the sleeve of Hagrid's jacket and continued sobbing, his whole body shaking with the force of the thoughts, the feelings, the memories, that exploded through the locks and seals of his mind.

"Thank you, Hagrid," said Dumbledore calmly. "Was the storm audible outside?"

"Could anyone hear him, you mean? No. I didn't catch what was happening 'til I got t' the office door. I sorta got the feeling it might happen, though. Done it before, once or twice. Never quite as bad as this, I reckon."

"He has been under considerable strain."

"Professor Dumbledore, you got a talent for understatement{\el}" Hagrid looked down at Snape, whose trembling was beginning to weaken, who seemed to be relaxing, going more limp. "I guess you better sit down." To Dumbledore he said, "I'd pour him a glass o' firewhisky, but he seems to have done for the entire stock."

"You may repair some of the damage, if you wish, Hagrid. There is no one here to see but myself."

"Just like you, Albus, to forget everyone else!" exclaimed the portrait of Armando Dippet. "My gracious! Is he always that temperamental?"

Dumbledore sighed. "He swings to extremes. It is a problem both of heredity and nurture, though today it is more a reaction to what he has been through these last two months."

Hagrid helped Snape stand, then guided him to an overturned chair, which Hagrid righted before settling Snape into it. He pulled his ever-present pink umbrella out of his pocket and began clearing up the mess, even able to return most of the liquid to repaired bottles. He poured a rather large amount of firewhisky into the glass his presence had spared.

"You drink this now, lad," he told Snape. "It's medicinal."

Snape did as he was told, then leaned back in the chair, breathing quickly and softly. "Hagrid," he gasped finally. "What brought you here?"

"Impending nuclear meltdown," said Hagrid. "Remember, I was there for the first one when you was thirteen. I can read the signs."

"Thank you," Snape said, beginning to recover. "Does anyone else know?"

"It appears not," said Dumbledore, "shielded as you were from the rest by about seven floors of solid masonry. If it were to happen again during the school term, however, up on the seventh floor like this, Gryffindor house would have a field day with the story."

Snape cradled his forehead with a hand. "It won't happen again," he stated.

"I dare say not. You are now at Hogwarts. You are no longer under the daily control of Riddle. You will no longer be forced to watch or participate in torture and murder. You have a place of your own to go to, and others you can turn to for support. Your situation is now utterly different." He nodded to Hagrid, who took the hint and left them alone in the office.

"You're right. I'm sorry."

"No need to be sorry. I imagine it was even therapeutic. Did you know that all this past month, Harry Potter and his two closest friends have been at 12 Grimmauld Place? Phineas has told me all about it." 


