% A Difference in the Family: The Snape Chronicles (Rannaro)
% Yes, That Is My Job

\chapter{Shadows Rising}

\subsection{Tuesday, August 1, 1995 (three days before the first quarter)}

Professor Severus Snape apparated into the outskirts of Hogsmeade, as he did at the beginning of every August, carrying his Gladstone bag and ready to start a new school year. The fact that this year he was coming in from Croydon, south of London, rather than from Lancashire was irrelevant. There was a curious quality about Snape's mind that allowed it to disconnect from one thing and connect to another so flawlessly that the two areas of his life were completely compartmentalized, separated totally from each other unless he willed otherwise.

"Nine o'clock," said a gruff voice nearby. "I don't think you've ever missed a day."

"Good morning, Moody. Has my status changed, or is this for purely sentimental reasons?"

"Hard to break an old habit is all." Both men were silent for a moment.

"Odd how if you don't have Azkaban to talk about, you have nothing to say," commented Snape when the silence had become too noticeable.

Moody laughed. "Then I'll just wish you a good year teaching. It isn't like we won't have more chances to talk as the year wears on. About less pleasant things."

"True. I suppose I'll be seeing you in London soon. And thank you for the good wishes."

"My pleasure, boyo. Try to stay out of trouble." And with a resounding `pop!' Moody was gone.

"Severus!"

Snape turned and waited as McGonagall caught up to him by the Hogwarts gate. "Morning, Filch," they both said to the caretaker who opened it for them, then walked up the hill side by side.

"Before anything else," McGonagall stated flatly, "I have something I've been wanting to say for a month, and I'm going to say it now. So don't try to stop me."

This sounded foreboding, but Snape just nodded.

"I treated you abominably in June, about Fudge and that dementor. I said unfair, hurtful things, and now when I think what you were about to go off and do that very evening{\el} Well, all I can say is—I'm sorry. Will you forgive me?"

"Forgiven and forgotten long ago. Not to be mentioned again. When did you find out?"

"Last week. I'm in the Order now, too."

"I rather wish you hadn't told me that. Something else to conceal."

"You'd have found out about it soon enough."

Things at Hogwarts seemed perfectly normal. Snape and Flitwick played cribbage after lunch. The inventory of supplies went smoothly. Even the fact that no Defense against the Dark Arts professor had yet been appointed seemed routine. It was as if the events of the past six weeks had never happened.

Until after supper, that is. Then Snape nodded to Dumbledore, Dumbledore nodded back, and Snape quietly made his way down the hill. By the time he reached the gate, it was already open for him, and he slipped through and apparated to Croydon. There, in his new laboratory, in his new lab coat, surrounded by things bubbling and brewing, he continued to make medicines and potions for the Dark Lord's infirmary. \emph{There is a certain surreal quality to this that will take some getting used to.}

It was, however, a routine that was easy to follow. Snape would spend the nights at Hogwarts, the days doing his work as a professor preparing for the school year, and his evenings in Croydon. The routine lasted less than two days.

Snape apparated back to Hogsmeade at eleven o'clock on August 2 and sent a patronus to Dumbledore to open the gate. Once inside, he was met by an answering patronus. `Come to my office at once. Something has happened.'

Surprised and apprehensive, Snape rushed up the hill and climbed the stairs to the headmaster's tower as quickly as he could. Dumbledore was waiting, and McGonagall and Moody were also there. "What happened?" Snape gasped as he tried to catch his breath.

Dumbledore looked grave. "We were rather hoping you could tell us. Harry Potter was attacked by at least two dementors this evening, about two hours ago. In Little Whinging, Surrey. Do you know anything about it?"

It was an uncomfortable moment. The first major crisis since his return to the Dark Lord, and Snape had been outside the circle that planned it. It was not an auspicious introduction to the Order of the Phoenix, and he had a feeling that Moody, and probably the others, would wonder if he'd simply not passed the information along.

"All I knew, and reported, was that they were trying to pull a couple of dementors away from Azkaban. My impression was that they were to be guards. Apparently I was mistaken. I believe I also warned you to watch Potter."

"True on both counts," said Dumbledore with a rueful smile. "And, in fact, Potter was being watched. Or should have been watched. We shall have to take up the matter with Mundungus. I regret that I put you in a position where you felt you had to defend your actions. I fear you have spoiled me, and I was beginning to think you could work miracles."

"No, sir. No miracles."

"So far, Severus, it has been an exciting evening. Mundungus Fletcher abandoned his post watching Potter to take care of some private business. Be sure you entrust nothing vital to him, by the way. It is good we know that now instead of finding it out later. Potter wandered away from home for some time, encountered his cousin Dudley, and the two boys were attacked by dementors not far from their house. Luckily Potter was able to conjure a patronus, and Arabella Figg got a message to me."

"Something else to consider," Moody pointed out. "That Fletcher's back-up at the time was a Squib. Not a good combination."

"True, Alastor. So far tonight I have been to the Ministry to persuade them not to expel Potter or destroy his wand, and I have had to threaten his aunt and force the Dursleys to keep the boy when his uncle wished to throw him out."

"Why do they have to keep him?"

"Ah, Severus, there is magic older than most wizards suspect, and the presence of his family has been protecting Potter for nigh on fourteen years. As long as his home is with them, he is reasonably safe. On a day to day basis, of course."

"Of course."

"When do you next return to London?"

"Tomorrow evening."

"Could you go earlier? We could use the information."

"Not without arousing suspicions. It's better if he believes that I told you I have no access to upper level information. That way, if I talk to people about the things they know, it won't look so much like I'm gathering information for you."

"I see. Well, handle it as you think best."

The next evening Snape returned to Croydon as part of his new routine. He was almost immediately summoned before the Dark Lord. Malfoy and Macnair were there as well.

Red eyes skimmed across the surface of Snape's brain as he knelt before his master. Satisfied, the Dark Lord sat back and began his questioning.

"You have heard of the botched attempt to take the Potter boy."

"Yes, Lord. Dumbledore informed me of it two hours after it happened."

"They were not expecting it?"

"No, Lord."

"Do they not watch him?"

"They have been watching him, but his guard left his post."

"What is the name of this careless enemy who unwittingly aids us?"

"I don't know."

"Why is Potter still at the home of his aunt? Do they not care to protect him better?"

"There is some ancient magic invoked by Dumbledore fourteen years ago that ensures Potter's safety as long as his home is with his family. There is some power attached to the protection of kin{\el}"

"Enough. We are aware of this." The red eyes turned on Malfoy. "Bring Wormtail to us."

They knelt side by side, Snape and Pettigrew, and from Pettigrew's fidgeting it was clear that neither of them knew which was in more trouble, or even why the Dark Lord wished to question them together.

"Look at us," the Dark Lord commanded, and both held their heads up, still and obedient, to permit the eye contact. "Now, Potions Master, tell Wormtail what you have just told us."

Without looking at Pettigrew, Snape repeated his information. "There is an ancient magic, invoked by Dumbledore to keep the Potter boy safe. It involves a kin relationship and seems to be effective whether the protection is given from love or from a sense of duty. If the relative actively chooses to safeguard the boy, he is immune from many kinds of harm. His aunt Petunia agreed to give him a home, from a sense of duty, and as long as he calls that place his home and lives there part of the time, he is guarded."

"Did you know this, Wormtail? Were you aware of this magic, this powerful ancient magic, when you came to us with the location of the child we were seeking? Did you serve Dumbledore then, and lead us into a trap, where the loving protection of the mother would destroy the one who tried to destroy her son?"

As a desperate Pettigrew stammered and groveled, and protested both his innocence and loyalty, Snape felt his whole body growing cold. He watched Pettigrew and the Dark Lord as if from a distance, amazed at his own sudden detachment from the scene. \emph{Could the Dark Lord be right?}

\emph{How ruthless is Dumbledore when the stakes are high enough? When evil is parading in triumph, and your own soldiers are falling into darkness, do you sacrifice one innocent to save thousands of others? Did you step back from being Secret-Keeper for this? Did you support Black in his argument about making Pettigrew the Secret-Keeper for this? Is the Dark Lord right, and the whole thing planned so that the love of a dying mother would channel through her son to destroy your greatest enemy?}

Snape realized that he was staring at Pettigrew with loathing and disgust. The Dark Lord felt it and grimaced in what was meant for a smile.

"Yes, faithful servant, he is loathsome, is he not? But we believe he was sincere in his loyalty. Perhaps he was duped by Dumbledore, but that is an error of judgment, not a breach of faith. You are both dismissed."

Back in his laboratory, Snape found himself feeling dizzy and disoriented. Still in shock, his hands shaking, Snape went to his bookcase and found the little piece of paper he'd put there three days earlier. \emph{Fool! To leave something like this in so obvious a place!} Lighting a Bunsen burner, he rolled the paper into a spill and burned it into nothing.

\emph{Fair is foul, and foul is fair. How does a muggle, a seventeenth century muggle, understand so much about the world of witches and wizards?} There was no doubt in Snape's mind that the Dark Lord was foul, but could he honestly say the same about Dumbledore's being fair? The firm ground of certainty was changing into quicksand, and Snape felt himself sinking.

\emph{What do I know for certain? Surprisingly little. I went to Dumbledore all those years ago because I couldn't stay with the Dark Lord. I assumed that because they were enemies, they were also different. No, that's not fair to Dumbledore. He was good to me. Usually. Did he deceive me? Did he manipulate me into doing something that he knew I would hate to further his own purposes?}

\emph{Do I know that the Dark Lord has deceived us to manipulate us into doing his will? Yes, I know that for a fact. I know because it was done to me. Does Dumbledore deceive and manipulate us into doing his will? It's harder to pinpoint, but I don't think I could say `no' to that question. Does it matter? Don't all people manipulate each other to some extent? Don't I do it, too? At what point does it cease being normal and become evil?}

\emph{Let's say for a moment that Dumbledore wanted the Potter baby to destroy the Dark Lord. He could have fed me that prophecy. He could have ensured Pettigrew became Secret-Keeper. He probably knew already that Pettigrew was working for the Dark Lord. The only thing wrong with the plan from Dumbledore's point of view is that it didn't work. It failed, and the Dark Lord is still here.}

\emph{Does my speculating on this and finding it logical mean that it's true? Clearly not. Just because you have a hypothesis that fits the facts doesn't make the hypothesis right. How can I prove or disprove this hypothesis? What do I look for, what do I need, to show me Dumbledore's true actions?}

There, suddenly—blessedly—the problem became scientific. He had facts, he had a hypothesis that might explain those facts, and now he needed to work out the steps, empirical steps, that would either prove or disprove his ideas.

Noting the time, how late in the evening it was, Snape left his laboratory for the streets of Croydon, and apparated back to Hogwarts.

The next couple of days were odd ones. Snape spent most of his time at Hogwarts and most of his energy on the Croydon headquarters. Finding excuses for being out of his laboratory was not easy, though it helped if he affected an air of being oblivious to the people around him while he moved from one place to another. His ears were open, his eyes were open, and he only worried that the others would suspect he was gathering information because of his too frequent forays into the corridors.

A meeting of the Order of the Phoenix was called for the night of the sixth of August, and Snape apparated there as soon as his duties in Croydon were completed, which was a little before eleven o'clock. The door was opened to him by Molly Weasley, who actually seemed disappointed to see him, and then he was ushered into the parlor, where he found a rather small group. Dumbledore, Hagrid, and Black were among the wizards there, but Moody and Lupin were not, along with several others who were absent. \emph{It's all right. It isn't as if I have a lot to tell them.}

Then suddenly, just as he'd started to give a report, the room began to fill up. Moody, Lupin, Diggle, Vance, Podmore, Doge, and Tonks entered, along with a wizard and a witch introduced as Kingsley Shacklebolt and Hestia Jones. Snape waited patiently while they greeted the others and were seated. The last to enter and seat herself was Molly Weasley.

"We seem to all be here at last," said Dumbledore. "Please proceed, Severus. We have kept you waiting long enough."

Snape started with a description of the organization of headquarters, then went on to more current events.

"Well{\el} we're a bit shorthanded here in{\el} London because Nott's been sent up to Glasgow, Yaxley to Cardiff, and Avery to Lincoln. New cells have been formed there, and they're attracting a decent number of people."

Shacklebolt raised his hand. "Is there a minimum number for a cell?"

"Half a dozen. If you can't get six, it isn't worth the trouble to send someone out. I got the impression that the Cardiff cell was quite small, but that Glasgow could be nearly a dozen, and Lincoln twice that, though some of them will go to York and Norwich when those cells open. The London headquarters is near fifty now, but mostly low rankers, about the level of common workers. The Dark Lord is having trouble getting in people with the status and background for the upper and middle ranks."

"Any idea why that's true?" Moody asked.

"So many of the old upper echelon either died or was shut up in Azkaban. New people, especially educated people, are leery of the Dark Lord until he proves he can be successful. Lots of people are waiting—`on the sidelines,' as the Americans would say."

"Excuse me, Severus," said Dumbledore, "but why so many in the lower levels?"

"There's a lot of discontent. The major complaint I hear is that the Ministry doesn't care about the welfare of the wizard on the street, so to speak. Then, the better educated wizards can find work with the Ministry or with Gringotts, or go into business for themselves, but the poorer ones have trouble even finding muggle jobs. They think the Dark Lord will give them work and a sense of purpose."

"Fudge has a lot to answer for," commented Podmore, and the others agreed.

"Now, tell us about the attack on Potter," Dumbledore continued.

Snape thought for a moment. "That mystifies me. I can't find anyone who was or knows of anyone who was involved in that. That doesn't necessarily mean anything. I'm not in contact with the whole organization by any means, but it's odd that no one knows anything."

Lupin spoke up. "Do you mean it's too secret, that no one has any information?"

"On the contrary, everyone's talking about it. They just don't know who did it."

"And your Dark Lord{\el}" prompted Dumbledore.

"Has said nothing specific. And the two top people just add to the mystery. Malfoy never says anything. He wouldn't divulge his feelings on his own mother's death. But Macnair got defensive when the subject of dementors and Potter came up. He wasn't in on it, and it bothers him,"

More fine points were discussed, and then the meeting was over. Black offered refreshments, but Snape pleaded fatigue, and this time Dumbledore didn't try to stop him. As the parlor emptied into the hall and the dining room, Snape became aware that the place was crawling with Weasleys. Molly, Charlie, Bill, George, Fred—Ron and Ginny had to be there somewhere. Snape was more pleased than ever that he was leaving early.

\emph{All I need is to have to deal with Gred and Forge Weasley. My idea of heaven{\el} not.} With great relief Snape left the house and apparated to Hogwarts, where McGonagall was waiting to let him in.

Over the next few days it gradually became more and more apparent that the daily commute between Hogwarts and Croydon was not going to be practicable. Snape found himself sleeping later and later into the morning and arriving in the Great Hall with barely enough time to grab a bite before breakfast was over. Flitwick was teasing him about getting lazy in his old age, and Sprout began suggesting a list of maladies that started out resembling fatigue and ended either with a funeral or with premature baldness. McGonagall, too, was concerned, but she didn't tease him about it.

"You really should go up and see Madam Pomfrey. You're looking much more peaked than usual. I'm telling you this from self-interest, mind you. It makes me positively tired just looking at you."

Madam Pomfrey was precise in her diagnosis and recommendation. "You've reached a physical and mental limit. It isn't just the ten days since we returned to school, its June and July and then August piled on top of it. Right now you're stretching yourself—you're not getting quite enough sleep, and your eating habits are affected—always a bad sign for you. You're an easy victim for any stray virus that decides it wants you. You could keep on like this indefinitely if all else remains the same. However, school is going to start in three weeks and your workload is going to increase spectacularly. Something's got to change."

Dumbledore agreed, and Snape considered how he was going to handle this when he returned to London.

Snape arrived in Croydon that afternoon rather than waiting until after dinner. He immediately put in a request to speak to Lucius Malfoy. He was told that he could meet with Malfoy at five o'clock.

At a quarter to five, Snape was waiting. Malfoy and Macnair were with the Dark Lord, and Snape was prepared to wait for some time. Luckily he didn't have to, for the two of them walked in together at ten past the hour.

"{\el} more than willing to listen to my point of view. That's what comes of oiling the wheels all these years. A gift here, a donation there, and I have a voice in affairs even if it is unofficial." Malfoy entered first and nodded absently at Snape without interrupting his conversation.

"You buy us more time, Malfoy, and you've done a great service. Nothing like discrediting a witness to make people turn their backs on his story. Think it'll work?"

Malfoy smiled, more of a smirk than a smile. "Old Parliamentary trick. If you have a quorum, you can vote. If certain members arrive late, well{\el}"

"You devious old dog! Best of luck to you!" Macnair, too, nodded to Snape, then left.

"What can I do for you, Severus?" Malfoy lounged comfortably in a chair near the window.

"I'd like to request a change of schedule once school starts. Right now it's no problem taking care of both my work at Hogwarts and my duties here, but come September with classes full time, plus grading papers, plus supervisory duties, I don't think I could handle it. Not and be in any condition to be useful."

"Ah, yes. The daily grind of the secondary school teacher. You do have my sympathy, you know. Working for a living—most tedious. How are your potions coming?"

"Everything will be well stocked by the end of August. The infirmary's half finished now, and operations hasn't requested much. Some of the smaller requisitions I could do in my office at Hogwarts during the autumn term."

"Excellent. I'll inform the Dark Lord. He's most content with your work so far, and the request is a reasonable one. I see no difficulty."

"Thank you, Mr.~Malfoy."

"I'm always pleased to help an old acquaintance. You may go now."

"Yes, sir."

Snape arrived late that night at Hogwarts, and asked to see Dumbledore early the next morning.

Dumbledore was intrigued. "If certain members arrive late{\el} Discrediting a witness{\el} They did not mention what the meeting was about, I suppose?"

"No, sir. It just sounded like Malfoy was going to suggest a tactic that would allow a vote to be taken somewhere before everyone concerned arrived. To force a certain outcome pleasing to the Dark Lord."

"I shall be going down to London tomorrow morning for a little meeting. I may make a small alteration to my plans. Thank you, Severus."

Dumbledore left early for London the following morning, but Snape had no time to speculate on the headmaster's actions since he was almost immediately inundated with orders of eyes. Newt eyes, bat eyes, octopus eyes, and many-faceted bluebottle eyes. Eyes of every size, shape, and color. Fragile things in delicate brine solutions—twenty-four gross of them packed into dry ice in six large cases—each jar had to be examined for damage before storing them in a special locker built out under the lake to keep them cool. It was a major reason why the Potions classroom was in the dungeon.

Snape worked feverishly all day, not even stopping for lunch. He had to work quickly enough that the eyes didn't rise in temperature, and methodically enough that he was sure he'd looked at every one. It was a simple, yet taxing job.

By supper time, Snape was finished. He went to the Great Hall feeling content with the day's work, for the eye shipment was the biggest single job he had getting ready for classes. Dumbledore was back from London, sitting at the Ravenclaw table playing checkers with Flitwick and looking pleased with his day's work, too.

After supper, Snape caught Dumbledore's eye as he was leaving the Hall. Dumbledore rose and followed, though Snape didn't wait for him. As Snape descended the hill, Dumbledore watched, opening and closing the gate into Hogsmeade to allow Snape to apparate to Croydon.

Snape was met at the door to the Croydon headquarters by Macnair himself. "The Dark Lord wants you. Now!"

Macnair seized Snape's arm and pulled him down the stairs and along the underground corridor to the interview room. The room was dark, with a beam of light creating a circle in the middle. There Snape was pushed to his knees, where he waited, frightened now. Malfoy came in and stood behind him, next to Macnair.

Then the Dark Lord appeared.

"You will explain to us now why Dumbledore chose to arrive early for Potter's hearing, and why you chose not to pass this information on."

\emph{What hearing?} The thought flitted uncontrolled across the surface of Snape's brain, and he instantly tried to suppress it. That was an error, for pain—cruel and unyielding—cascaded through him, and he gasped and writhed with the agony of it.

"You will not attempt to hide your thoughts from us."

"Lord, forgive me. I will not again, but I was surprised." The pain receded.

"Bartemius was mistaken in you, we see. You do not have so much control over your thoughts as he believed. Now, you will answer."

"Lord, I know nothing of a hearing. I had no information to pass on." Now the pain started again, small and menacing, a tickle, a promise of what would come if the wrong answer was given.

"You knew he was coming to London."

"Yes, but not why."

"You knew Potter had a hearing at the Ministry this morning to answer charges on the use of magic."

"No, Lord, I did not." The pain began to enlarge and twist inside him like a malevolent worm.

"What use are you to us if you do not know the information we require?"

"Lord, I will try{\el} No!" Snape dropped forward onto his hands, perspiration beading his forehead as the pain notched upward. "Lord, I will{\el} I will get you what you need, only{\el}"

"Only{\el}\,?" repeated the Dark Lord, unrelenting in his torment.

"Only I'm no legilimens. I can't read what you need or what they hide. I stumble in the dark. If you could tell me what I must look for{\el}"

"Enough. Lucius, this one is innocent of betrayal. He did not know, and therefore could not warn. His crime is ignorance. Severus, you will return to your work. When you have completed your tasks, you will go back to Hogwarts, but each night before you do, you will check with Lucius to see if there is anything specific that you must watch for."

"Yes, Lord. Thank you, Lord." And the Dark Lord was gone.

Malfoy helped Snape to his feet. "Hard luck that. He was furious when he heard Dumbledore'd outfoxed Fudge and his plans. I suggest you tell us everything, just to be safe. Tell us if Dumbledore blows his nose."

\sbreak

"I slipped. I can't believe I slipped like that. I could've died. He said Potter had a hearing, and I let my reaction show like any sieve-brained idiot. Then to compound it—I tried to hide it. I'm just thankful that what I released showed him I wasn't hiding something worse."

Dumbledore poured a glass of mead. It was near midnight, and Snape was grateful that the headmaster was willing to sit up and listen. He himself was too hyper to go to bed or even relax.

"It was all for the best, then. Your slip proved your innocence, and he is more convinced than ever that you cannot hide things from him. I would say it worked out quite well."

"Dumb luck! What if the thing I let slip proved my guilt? I wouldn't be here talking to you right now. You can't trust me with anything, sir. I could just as easily give him your secrets{\el}"

"Calm down, Severus. I believe you are making too much of this. Do you remember your first interview with Riddle? You were what? Eighteen? Nineteen?"

"I remember. How do you{\el}\,?"

"You told me. We spent quite a few hours together in Hagrid's hut that day, and you told me many things—I recall you were somewhat distraught—but your account of that interview is one thing I shall never forget."

Snape had drained the glass, too nervous to be aware of what he was doing. Dumbledore refilled it.

"You were young and surrounded by friends who were welcoming you into a fraternity, a fellowship. You burned with devotion, and you opened your mind to him freely and trustingly. And what happened? Without your even being aware, your own mind closed down to him with a completeness that I certainly cannot break through, and I doubt he could either. And it was done without any volition on your part. Involuntary self-protection. Now an occlumens who operates with such unerring instinct is not going to slip and spill fatal information casually. I think something in your brain knew that open honesty at that moment was beneficial. I have complete faith in your ability to shield my little secrets."

The combination of Dumbledore's reassurance, his own fatigue, and the mead had a relaxing effect on Snape. He went down to his own rooms, fell asleep easily, and slept dreamlessly for the rest of the night.

There was another meeting at Grimmauld Place a week later. Snape apparated from Croydon to Kensington Gardens to the nearby alley at about ten-thirty. Black opened the door to his knock and stood aside to let him in. "Snape," he said in greeting.

"Black," was Snape's response. He looked around. Mrs.~Black's portrait was blessedly quiet, and there was change in the air. Much of the smell of mildew and rot was gone. "I see you're getting along with the cleaning."

"It occupies the time."

"I envy you that time. I could use more."

"It isn't by choice."

"Of course not."

Lupin and Molly Weasley came out of the parlor at that moment, and the somewhat barbed conversation ended. They went into the parlor where late refreshments were being served.

"Tea?" said Black. "Maybe a sandwich."

"No, thank you. I had something before I came."

"Just a bite. It's really quite tasty."

"No, really. Please don't put yourself out on my account."

Dumbledore intervened before daggers were drawn. "Gentlemen, I suggest you sit down. We are about to begin, and I am sure we all would like to get business over with as soon as possible. There is a lot to cover, and it is late."

Snape took a seat next to Tonks, while Black leaned against the doorjamb. Each studiously avoided looking at the other during the first part of the meeting.

"Now," said Dumbledore, "there is the matter of the circumstances surrounding the hearing at the Ministry on the question of Harry's using magic illegally."

The assembled wizards and witches nodded in anticipation. All had heard something, and none everything, of the matter.

"First, of course, the very fact that Harry would be arraigned before a tribunal for defending himself from dementors is of concern. The Ministry does not wish to concede the existence of the dementors. They wish to accuse Harry of inventing the threat in order to indulge in a gratuitous display of magic ability in a spot where there were no witnesses except his cousin Dudley. Now Dudley Dursley is well aware that Harry is a wizard, and therefore displays of magic before him do not constitute the serious breach of the law that they would before muggles unaware of our world, and yet the Ministry chose to go to extreme lengths of review of the offense and potential punishment."

There was a general murmur against the Ministry at this, but it was quickly followed by silence.

"Next came the rather blatant attempts on the part of the Ministry to circumvent the process of the law by trying to make Harry miss his hearing on the twelfth and lose by default, and by trying to ensure that he had no legal support nor any witnesses to back him up. An owl was sent to Arthur Weasley advising him of a change in time of the hearing, but it seems to have been intended to miss him, to arrive after he had departed his residence to go to work that morning. The Ministry claim to have sent an owl to me, but it seems never to have arrived. I should now like Severus to give his information."

Having finally realized the fullness of his own role in the previous week's events, Snape spoke up with some confidence. "On the evening of the tenth I had reason to ask to speak with Lucius Malfoy at our{\el} London headquarters. I overheard him say to someone else that they were planning an old Parliamentary trick to force a vote when certain members were sure to arrive late. I informed Professor Dumbledore of this. It seemed to be connected to a strong desire of the Dark Lord to have his return as little publicized as possible while we{\el} they build up strength."

Dumbledore continued. "Lucius Malfoy was present at the Ministry the morning of the twelfth. I would not be surprised to learn that he was there specifically to learn the outcome of Harry's hearing. Severus."

"The evening of the twelfth, when I arrived in{\el} London for routine duties, I was immediately brought before the Dark Lord for interrogation. Specifically, he wished to know why Professor Dumbledore had arrived early for the hearing, and why I hadn't reported his intended early arrival to headquarters."

Tonks turned to Snape, concern in her eyes. "Interrogation?" she whispered. He affected not to hear.

"So now," Dumbledore concluded, "we know the extent of our problem and our danger. It is not just that the Ministry does not wish Potter's story of the return of—excuse me Severus—Voldemort made public. It is that Voldemort is aware of the internal workings of the Ministry, and that he has ways of persuading the Ministry to act according to his wishes."

"Do we have any indication that anyone in the Ministry is actively working for You-Know-Who, or is it just that they're being manipulated?" asked Shacklebolt. Dumbledore nodded to Snape.

"I've heard nothing of one of our{\el} his people being `in' the Ministry. The impression I have is more that we{\el} they have influence, not an actual presence."

"Snape, me boyo," rumbled Moody from a seat near the unlit fireplace, "I suggest you stop fretting about the `usses' and the `thems.' Just say `we,' `us,' and `our.' You got enough to worry about without tippy-toeing around this lot."

Snape smiled wryly and nodded his thanks. A general conversation ensued about how to deal with members of the Ministry, and it was concluded that the Ministry employees among them—specifically Arthur Weasley and Tonks—would try to pinpoint leaks.

As the meeting was breaking up, Snape found himself once again next to Black.

"You know," said Black, "you aren't the only one in this group who's at risk for the work they do."

"I'll remember that," replied Snape, "the next time I'm kneeling in front of the Dark Lord waiting to be punished. Note to self: Black's at risk, too."

"You know I'm not talking about me!"

"Odd, then, that you're the only one to say anything."

"You don't need to rub people's face in it."

"Sorry! Didn't realize that was what I was doing. Should I have said I was brought before the Dark Lord for tea and crumpets? Would that soothe your sensibilities more?"

Dumbledore was suddenly there. "Time to go back to Hogwarts, Severus. Shall we make our apologies and head for home and bed?"

Snape and Black nodded to each other in exaggerated politeness, and Snape followed Dumbledore out of the house.

\sbreak

It was less than a week before the train from King's Cross would arrive, and Snape was in his laboratory setting up a simple distillation apparatus he'd just acquired. During the time that he concentrated on the tubes and clamps, a random thought had surfaced—that he was doing something he loved for someone he despised, and something he hated for someone he respected. \emph{Wouldn't it be easier if the Dark Lord was the headmaster and Dumbledore the rebel? Then I could chuck the teaching job once and for all, and life would be good.} Such thoughts were dangerous luxuries here, though, and he hid it away.

A lower level messenger knocked, then stuck his head around the open door. "The Dark Lord wants you," he said simply, then left without ever having stepped into the room.

Puzzled at the unexpected summons, Snape nonetheless glanced quickly around before leaving to be sure everything there could be left unattended. Then he hurried to the interview chamber.

Malfoy joined him soon after, and together they waited. Neither spoke, since speculation on the Dark Lord's wishes was frowned upon, but Snape took comfort from the fact that Malfoy seemed quite relaxed and untroubled. \emph{So this is probably a new task rather than displeasure over something that's happened.}

The room was large, bare, and dimly lit. Walls, ceiling, and floor were painted black so that there was a sense that it had no dimensions at all. The only furniture was a large throne-like chair where the Dark Lord would appear. Snape hadn't seen the whole room before, since he'd only been there for interrogation when the contained circle of light where he knelt blocked any view of the rest. Today there was no circle of light.

The Dark Lord came. Suddenly he was there, seated in the chair before them. Snape made a movement forward, his first reaction being to kneel, but Malfoy took his arm and indicated he should stand. There was a pause as the Dark Lord surveyed them.

"Lucius tells us you are weak." The statement was like a long hiss, but neutral in its tone.

Unsure what this portended or how to react, Snape said simply, "Yes, Lord."

The red eyes narrowed and the slitted nostrils flared as the Dark Lord chuckled. It was not a pleasant sound. "You were right, Lucius. No protest, no defensiveness, just an honest statement of limitations. Such do not rise in our service, Potions Master, but they are useful tools, and a wise artist takes care of his tools."

No answer was expected to this, and Snape was silent.

"You have asked to be relieved of some of the pressure of your duties. You are too weak to sustain the level of tasks that I have assigned. It is a matter of physical limitation. You are a half-breed?"

"Yes, Lord."

"Honesty is commendable, but weakness must not be coddled. It must be punished to discourage the merely sluggardly. What should your punishment be, Potions Master?"

Confused, Snape replied, "Whatever my Lord thinks is best."

"Even death?"

"Yes, Lord."

"Good. Know this—we do not grant your request to be excused from service because of your weakness."

Struggling to control his disappointment and bewilderment, Snape said only, "Thank you, Lord."

In the pause that followed, the red eyes caught and held his own. Snape felt the scan that flickered over his brain and poked at his thoughts.

"Circumstances have arisen, however," continued the Dark Lord, "that we wish to address by changing your assignment. The Ministry of Magic is displeased with the lack of discipline at Hogwarts. They are sending a functionary to take an active position there, to evaluate the possibility of a total reorganization of the school. This person is not one of our people, but Lucius informs us that her views and beliefs are such that they can play into our hands. You have a delicate job, Severus. You must not let her know that you answer to us, or even that you know we are here. You must support her without appearing to support her too much, so as not to arouse suspicion. And you must report to us everything that happens at Hogwarts. You will cease from this moment your daily attendance here, and you will report once a week, on Saturday evenings."

"Yes, Lord," answered Snape, immensely relieved.

"Lucius, you will brief Severus on details." And then the Dark Lord was gone.

\sbreak

On arrival back at Hogsmeade, Snape sent his patronus with, in addition to asking to be admitted, a request to speak to Dumbledore at once. The gargoyle staircase was open, waiting for him, and Dumbledore had a small plate of sandwiches and tea.

"And maybe a glass of sherry? I hope this is about Dolores Umbridge."

Snape stopped, his hand not quite touching the sherry glass. "You know already? The Dark Lord's information isn't in advance of events as much as he thinks."

"I learned this afternoon, but not from the Ministry. I have people there, too, remember. So both of us are in advance of the official announcement. Is your information firsthand or secondhand?"

"Some of it from the Dark Lord himself. I was called to him, and I have an assignment. Dolores Umbridge, in fact, is my assignment."

"Tell me about the whole interview."

"It was strange. I'd asked Malfoy for permission to go to{\el} London less frequently once the term started, and the Dark Lord called this weakness. He said weakness could not be `coddled,' and I thought he was going to punish me. Instead he denied the request, then gave me the Umbridge assignment and said I wouldn't have to go to{\el} London as frequently. So in effect he granted my request after all."

Dumbledore smiled. "It is good to know he is still vulnerable. Poor Riddle{\el} so insecure in his position that he has to beat it into you that you have no influence on his decisions. `I am not doing this because you asked, Severus, but because I have my own reasons.' Oh, and I have deduced that his headquarters are in the Greater London Metropolitan Area, but not what we traditionally think of as London. One of the outer boroughs, maybe?"

"How{\el}\,?"

"You keep trying to say the name, and all that comes out is London." Dumbledore was gazing placidly into Snape's eyes. "So I would guess it was Barnet{\el} or Harrow{\el} or Hounslow{\el} or Bromley{\el} or Croydon{\el} or—ah! Croydon. See how nicely you shut down—without even trying. Now, tell me more about Umbridge{\el} I am sorry, I have upset you."

"I just never realized before how easy I was to manipulate."

"No, Severus, do not think that. The only reason I was able to see it was because you wanted to tell me. Now, Umbridge."

"They're looking for anything they can find to discredit you or Potter. The two of you are the source of all the rumors about the return of the Dark Lord, and to admit that's happened is political suicide for Fudge and his upper level of administrators. So her job is to get Potter. And you if possible. The Dark Lord wants me to be marginally helpful to her, but not under any circumstances to let her know of his presence. That would stop her from playing into his hands. I doubt she'll trust me, though. Lucius says she's rabid about blood purity. Hates mongrels of any kind. She's particularly looking forward to sacking Hagrid. And I'd keep Flitwick away from her, too."

"I shall keep that in mind. Hagrid is not here at any rate, so that is one less source of friction at the beginning of the term."

"They want her in the Dark Arts job. They're afraid any other instructor might warn the students about the Dark Lord, or at least not stop the students from gossiping and spreading rumors. Part of her job is to prevent them from focusing on him at all. This is one of the things that suits the Dark Lord at this point. Until the organization is set up, anything that keeps the general wizarding world from paying attention to us is an asset."

"Do you have any idea who Riddle's source of information in the Ministry is?"

"None. Except Malfoy, of course. He's spent the last fourteen years building up a network of contacts, and now he's benefiting from all the hard work. He can just about go anywhere in the Ministry and talk to anyone, and no one stops him or is even suspicious of his motives. I'd advise our own people to be very cautious around him. They assume Arthur Weasley is working for you, and Moody, of course, but they don't have any solid information about any of the others. Not in the Ministry."

"Thank you, Severus. This is all most useful. It is past midnight now. We should both of us be getting to bed."

The week's respite that Snape had hoped to have was not to be. On Tuesday the mark on his arm began to throb, and he went at once to Dumbledore.

"I'm being summoned."

"You should leave at once."

"It isn't an urgent summons. More a `come as soon as you can, but don't be obvious' summons. I have no idea why. It could mean I'm in trouble."

"Think of it as a chance to collect more information."

"Very comforting."

The interview was not long, and once again Snape was permitted to stand rather than kneel. He took that as a good sign.

"You brought us a prophecy sixteen years ago."

"Yes, Lord."

"Repeat the prophecy."

"I'm no longer certain I remember the exact phrasing." Pain had already begun, soft and persistent in the center of Snape's being. As he spoke, it prodded him toward the right words. "I think it was, `The one with the strength{\el} power to defeat{\el} vanquish the Dark Lord approaches{\el} Born to them{\el} those who have thrice{\el} defied him, born as the seventh month{\el} dies{\el}'"

"This is not the complete prophecy."

"No. I was interrupted and prevented from hearing the rest."

"Who does know the entire prophecy?"

"Only Dumbledore."

"The seer does not remember her prophecies."

"No, Lord. She is entranced when she speaks, and therefore oblivious to them."

"Has she prophesied since?"

"Once to my knowledge. To predict the return of Petti{\el} of Wormtail to you."

"Does she remember that prophecy?"

"No, Lord."

"Return now to Hogwarts."

"Thank you, Lord."

\sbreak

"So, he was interested in the prophecy."

"Yes. He wanted to know the entire thing, only I don't know it. And he knows that I don't know it. I can't help wondering why he even asked."

"Nonetheless, that he is interested is very valuable information. There are other places he can investigate. It is best you not know of them, but I shall try to have them guarded. Advise me again if you learn of anything."

"Certainly, Headmaster."

\subsection{Friday, September 1, 1995 (the day before the first quarter)}

Early in the morning on September first the summons came again. \emph{He knows the Umbridge woman is arriving today. He knows the students are arriving today. Why does he send for me today?}

Snape went at once to Dumbledore. "Something's happened. It still isn't an urgent summons, but I can't ignore it. I have to go."

Dumbledore looked calm. "The last time it was only for a couple of hours. I dare say you'll be back by lunchtime. Professor Umbridge is not due until just before the feast, so you will miss nothing. Good luck."

The moment Snape entered the Croydon headquarters, he was seized by three Death Eaters he didn't know and his wand taken from him. They then hustled him along the main corridor, down a flight of stairs at the rear of the building, and into a small basement room with a chair, a table, and a dim light in the ceiling. There he waited for three hours, growing more nervous by the minute.

When the door opened, it was only to admit Macnair, followed by the Carrows. Alecto smiled sweetly at Snape and drew an index finger across her throat.

Snape had risen at their entrance, and Macnair took the chair, conjuring two more for Alecto and Amycus. He motioned for Snape to stand at the foot of the table, opposite him, then leaned back with a speculative smirk on his face.

"Slipped up this time, didn't you, Potions Master. He's not happy with you. Not at all, my dear, not at all. You've been talking to people. Telling them things you shouldn't. I wouldn't be surprised if you've seen the sun for the last time."

"I've done nothing wrong."

"No? Mr.~High and Mighty up there in your little kingdom where the rest of us can't go—you think you're better than us. We have your measure now. You've sold us out. You've been selling us out for some time, but now your game is over because now we have proof."

Snape was trying to glimpse behind Macnair's eyes, trying to see some sign of bluffing. His own heart had sped up, and he breathed as if tight bands circled his chest. Something had happened. Something very bad had happened. "The Dark Lord knows I'm faithful."

"The Dark Lord knows you've cheated him of something he wants very much. His anger is great. Your punishment could deflect that anger away from the rest of us. You're not wriggling out of this one, Snake. Ha! If you could, I'd send my own people up to you for wriggling lessons. No, Dumbledore's sold you out, Snake. He used you, and he dumped you, and now you get to pay."

Macnair rose and came to stand beside Snape, his face close, his breath hot on Snape's neck. "And after he finds you guilty, he's giving you to me. I don't like Cruciatus curses, Snakey. They don't linger with you long enough. I break bones. Kneecaps." He ran a finger down Snape's spine. "Remember last time? I bet you were feeling that for a while. Anything I want—I just can't kill you. That pleasure belongs to the Dark Lord. Not that I would want to kill you. Spoils the fun, killing."

On either side of Snape, Alecto and Amycus were grinning. Snape didn't answer. There was nothing to say. \emph{It's about the prophecy. Dumbledore did something with that information, and the Dark Lord knows it could only come from me. He could have warned me. Dumbledore could have warned me{\el}}

A knock at the door, and a Death Eater looked in. "Bring him now," was all he said.

They shoved Snape out the door and pushed him along the narrow corridor to the interview room. \emph{I can't run. I can't fight. Both are signs of guilt. Keep to the story. Nothing wrong. I did nothing wrong.}

There were others there, but Snape couldn't see them beyond the circle of light where he knelt. The Dark Lord appeared and the pain was like the time before—a hint, a promise, a reminder{\el} Red eyes filled his vision.

"We have a mystery for you to unravel, Potions Master. You like mysteries."

Snape let the images cascade into his consciousness: Sherlock Holmes, Hercule Poirot, Peter Wimsey, Brother Cadfael—what could the Dark Lord care about these? The eyes bored deeper, raking through the places where doors had been found before.

"Tell us of the Ministry of Magic."

"They make and enforce the laws{\el}" Snape doubled over suddenly, clutching his stomach.

"No schoolboy lessons. Tell us of the Ministry. What is inside?"

"I've never been anywhere inside except Law Enforcement. Years ago."

"Who works there?"

Snape thought of Fudge and Umbridge, but knew that answer would raise the Dark Lord's anger. "The Weasleys," he blurted out, "Arthur and Percy, Sturgis Podmore{\el}"

"You know of Podmore."

"I told you of him before. I've met him three times."

"Then you will be sorry to hear he is arrested."

Twelve hours later Snape apparated back to Hogsmeade. For a moment he stood next to a tree on the outskirts of town, then his legs buckled and he slid to the ground, leaning his head against its trunk. \emph{I've been here before. Déjà vu all over again.} With some effort he forced himself to study the stars in the night sky.

\emph{Only about nine o'clock. They're in the middle of the feast. I can't send him a message, not there in front of everyone. When? Midnight? Three hours. I have to wait three hours.}

Time ticked by, and Snape drifted in and out of a dreamlike state, a nightmare state, until he heard a woman's voice, "Professor? Professor? Is that you?" She was whispering as if afraid to be overheard.

"Here," Snape said quietly, and she came and knelt beside him. It was Madame Rosmerta from the Three Broomsticks.

"Dumbledore said you might be coming in, and you might need help. Do you think you can stand?"

Snape nodded, and she got him to his feet and through the village to her inn. There she put him onto a cot in the back storeroom. "You just rest a while. I'm going to leave a message for Dumbledore."

A few minutes later she was back with blankets, pillows, tea, hot soup, and bread. Snape accepted them gratefully, managed to eat some of the soup, and then quite suddenly fell asleep on the cot. It had, after all, been a long day.

He woke up before dawn in Dumbledore's office.

\sbreak

"He was going to kill me! Not right away of course, but they had the knives sharpened! Do you have any idea what I just went through? Dragged in front of him, locked in a cell, dragged out again, punished, my head throbbing from the mind probes! Macnair going on in loving detail about what he was going to be allowed to do to me!"

"But you made it. You are with us again. Have a glass of{\el}"

Snape stepped forward and struck the mead from Dumbledore's hand. "Don't treat me like this! I just spent the worst day of my entire life, and you're not going to just kiss it and make it better! You did that to me! When I left here yesterday morning you knew what I was walking into! Good luck, he says! See you at the feast, he says! Were you already planning my funeral?"

"I am sorry. You are right. It was unforgivable."

His eyes narrowing, Snape drew himself to his full height and stared up into Dumbledore's eyes. "Don't you dare try to take my anger away from me, too," he said icily. "I have a right to be angry with you. You can't deny me that."

"You are right, of course. Be angry for as long as it takes you to work this through. And yet you are with us now, so some other decision was reached in your case besides transforming you into Macnair's private playground."

"I'm on probation."

"And what does probation entail?"

"Good, solid, usable information. Something they can use to plan operations that don't turn sour at the last minute. I have to give them someone in the Order. Or something so valuable it's worth the same thing. He's tired of wasting time with me."

"I thought your potions work was valuable on its own. Or your spell work. Or the defense lessons."

"They would be if I was in London all the time. But he's letting me stay here at Hogwarts. He feels it should be worth something."

"What exactly will happen if you do not deliver what he wants?"

"I suppose it depends on the circumstances. This time I was lucky. More than one person had the information that he was interested in the prophecy. It couldn't definitely be narrowed down to any one of us, and he had to weigh future value against the satisfaction of present vengeance. If he hadn't thought I'd be useful, he'd've killed me anyway. If any other leak comes back to me, I'm dead. If I can't get him the information he wants, I'll be called back to London permanently, chained in my laboratory, and worked like a slave. Neither prospect is inviting."

"We shall have to come up with information to give him, then. Do you think information about Professor Umbridge would satisfy him?"

"If it included inside tidbits about the Ministry of Magic, it would be better."

"Good. Let us commence Operation Umbridge. You will like her, Severus. Just the type you love to deflate. Oh, and Severus{\el}"

"Yes, Headmaster?"

"Would you like that glass of mead now?" 


