% A Difference in the Family: The Snape Chronicles (Rannaro)
% – In Principio —


\chapter{Prologue}

\subsection{Thursday, April 9, 1959 (the day after the new moon)}

"Well, look who's here!" Ted Heseltine looked over from the game of darts as the door to the local opened. "If 't ain't the bridegroom! Wha' cha doin' here, Toby? Run outta petrol?" General laughter greeted this comment.

"Shut yer gob, Ted, and watch yer language. Got the missus here."

There was general movement as the men gathered in the local—in that sweet hour between leaving work and going home for supper—realized that the smaller figure behind Toby was the very new Mrs.~Snape. They swept nut shells off the table, dabbed up a bit of spilt ale, and dusted off a chair, for everyone knew that Toby 'd up and married a girl from a country cottage, used to gentler ways than the ones found among the workers in a shabby east Lancashire mill town.

"Beggin' your pardon, Missus," Ted said, offering the now clean seat to the thin, sallow, long-faced woman that Toby'd taken to wife. She was no beauty, but then neither were any of them, and men in their walk of life didn't marry for beauty, but for companionship, a home, and children.

"Thanks," said Mrs.~Snape quietly, and condescended to join them, making her instantly popular with the men.

"Lads!" Toby cried. "Drinks all 'round! This 'ere's m' new wife. Eileen, these are m' mates at the mill, the lads what I spend m' days with." The pints came, and they toasted Toby's wife.

"So Toby, wha' cha doin' back from Blackpool early?" asked Thurstan Garnett. "Y' got another day comin'. Thought you might like to stretch it out{\el} Beggin' your pardon, Missus."

"We come back early," proclaimed Tobias Snape with some drama, "because we been informed we've a house. A dome-ee-sile. End o' Spinner's End, it is, and we're settin' up housekeeping. M' grandad's hired a couple o' men to bring some things from 'is house and m' dad's, and me and 'Leen decided t' take the three days and move in proper. So I ain't back yet, not official. You'll see me at the mill come Monday."

Eileen Snape said nothing as the men exchanged gossip and chatted about the latest news of the job—"fired Fred just like that, and 'im with four kids t' feed"—but she watched their faces as they talked, and her restless eyes took in every detail of the pub. Toby had two more pints and was getting boisterously chummy.

Then it was time to go home—the other men to their wives and to supper—and the little group broke up. Toby and Eileen walked together, hand in hand, through the maze of brick Victorian worker's cottages, soot blackened, the few visible curtains dingy from the grime-filled air. Toby's hobnailed shoes rang loud on the ancient cracked cobblestones as they approached the last little house at the very outskirts of the town, on a street under the shadow of the mill chimney that dominated the whole skyline. The last little house on Spinner's End.

It was dark inside, dark and empty, and their footsteps echoed slightly in the empty rooms. Eileen went directly to the kitchen, where she'd already started preparing supper with one skillet on a coal grate because the gas and electricity hadn't been turned on yet.

Tobias stomped around the little house. The ground floor had a sitting\slash dining room and the kitchen. The upper floor had a large bedroom and a smaller room that Toby planned to divide into a tiny second bedroom and a storage space. There was also a narrow room with a toilet and a sink wedged onto the upper floor sometime in the last fifty years, but no proper bathroom. It was all right. They weren't any la-di-da Londoners. Hot water and soap in a basin was all you really needed. They'd make do.

They camped for supper, eating Eileen's simple meal on two cracked plates while sitting on the floor in the front room. "Could ya ever witch us up a coupla drinks and some posh dessert?" Toby joked, but Eileen frowned.

"You know it doesn't work with food," she said.

"Aye," said Toby. "Seems there's lots it don't work with."

In addition to the skillet and the plates, and two stools in the kitchen, there was one other thing in the house—an old lumpy mattress in the sitting room. The next day they would get some small pieces of furniture, but for tonight this was the bed.

"Come on, 'Leen," Toby coaxed and, even though it was early and the sun barely set, Eileen smiled and joined her very new husband. They were, after all, still on their honeymoon.

\lbreak

\emph{[Many miles away, more than an ocean away, on exactly the same day at almost exactly the same time, the National Aeronautics and Space Administration announced the names of the seven men, the Mercury Seven, who would be the first western pilots to become astronauts in their country's space program. One of them, John Herschel Glenn, Jr., would be the first American in outer space. Neither Tobias Snape nor his new bride, the former Eileen Prince, were ever aware that this had happened, but the coincidence is an interesting one.]}

\lbreak

By the time Eileen woke the next morning, Toby'd left, but he was still with her as she moved around the house. She put on her dressing gown and found a note on a sheet from a tiny pad of paper—`Ye'r the greatest.' Another note was in the tin of tea—`I'm the luckyest man alive.'

Eileen smiled her tight, quiet smile. She wasn't one for talking and had never had many friends, certainly never a beau to go out walking with. Toby made her feel special, important, and he was always telling her sweet things. He did like to go out with his mates of a Friday night, and had a fondness for gin, and sometimes the fondness gave him a ready fist, but these were common traits among working-class men in both small town and big city, and Eileen thought nothing of it.

A knock on the door made her jump. It wasn't Toby—Toby'd walk right in. Eileen didn't want to greet strangers on her doorstep still in her night clothes, so she walked quietly to the front door and, instead of opening it, said, "Who's there?"

"Your mother, 'Leen. Who else are you expecting at seven-thirty on a Friday morning?"

The door opened, and Eileen nodded to her mother and slipped quickly back inside, conscious she was wearing a dressing gown on a public road. "Come in, Mum, and have a cuppa. We got no furniture yet, but at least we got a house. How'd you get here? How'd you know?"

"Believe it or not, that old muggle scoundrel Wensley dropped by yesterday to tell me he'd found a place, and Sam and Emily Dyson are visiting their daughter in Colne, so they gave me a ride." Mrs.~Prince stood in the sitting room looking around at the dingy walls. "It's rather old, isn't it? And small."

"I'll be doing a load of cleaning, that's for sure, and 't ain't big, but it'll be better when the furniture comes, enough for two at any rate."

"Two?" Mrs.~Prince's gaze lingered a moment on Eileen's face. "Are you sure?"

Eileen blushed. It didn't suit her and made her face look blotchy. "Mum, please. We are married. And you can't never be sure."

"We can," Mrs.~Prince replied. "show me the kitchen now, and we'll have that cuppa." She waited until they were sitting and sipping the hot tea before continuing. "There's going to be trouble, 'Leen. It's not just the money, though children are expensive. That man of yours won't stand being second, and babies have a way of grabbing all the attention."

"Toby'll be fine, Mum. He'll be proud t' have fathered a child."

"He'll be jealous. It's bad enough, both of you Moon in Aries, but to get married when it's swinging through Aquarius and now having it in Aries again for this{\el} I never did see a couple so willing to have a fight, with both of you wanting to control everything and him wanting no rivals. You might at least have waited 'til you were settled in."

"We'll be fine, Mum. And you know Toby sets no store by all that{\el}"

The front door opened, and Eileen jumped up to greet her husband. Mrs.~Prince followed more slowly and paused in the kitchen doorway when she saw there were two men in the sitting room. The older of the two, cap already in hand, gave her a nod that was almost a bow.

"Good morning, Constantina. Come to have a peek at the new digs?"

"Good morning, Wensley. I suppose it was good of you to be looking out for them like this."

"Proud to do it, proud to do it. Well, 'Leen, you're looking fit. Got a bit of a glow. Has my grandson been doing his duty? Am I going to be a great-grandfather before I die?"

Toby started to stammer something about waiting until everything was settled with the house and they were sure about the jobs continuing at the mill, then noticed that both Eileen and Mrs.~Prince were very quiet. Wensley Snape had already noticed.

"You got news for us, Constantina?" Wensley asked. "Your people got ways of knowing?"

His mouth still open from an unfinished sentence, Toby turned to his wife of less than a week. "Is it true, 'Leen? D' people like you{\el} D' ye know?"

Eileen nodded. Toby let out a whoop, and began dancing her around the empty sitting room. "A dad!" he bellowed. "A dad! And it'll be a boy, I know it. You've made me the happiest man{\el}"

Then the laborers arrived with furniture gleaned from the houses of several different relatives—sofa and chairs, lamps, table, bed, and all the important things—not many, but enough—to start a home with. As Toby and Eileen busied themselves with telling the workmen where to put these used but serviceable treasures, old Wensley Snape watched Eileen with a keen, almost hungry expression. Constantina Prince was one of the best-known witch healers and potion brewers of the Pendle countryside, and more than anyone else, Wensley had supported Toby in his courtship of her daughter. It was something he'd wanted most of his life.

There are dreams that are never fulfilled, and others that come true. Wensley Snape was lucky in that, of all those near to him, his was the dream that was about to come true. If all went well, in nine months' time, he would have a wizard in the family.
