% A Difference in the Family: The Snape Chronicles (Rannaro)
% Too Much For Granted

\chapter{Multiplying Dangers}

\subsection{Thursday, August 1, 1996 (two days after the full moon)}

What kind of research? was a question that would have to wait until later. For the time being, Snape was hectically busy preparing a full stock of potions—as many as the shelves would hold in the clinic, the laboratory, and field operations—against the time when he could not be at headquarters every day. Then, most suddenly, it was the first of August. Pettigrew went back to Birmingham on a continuous basis, and Snape locked his home in Lancashire to take up more or less permanent residence at Hogwarts for yet another school year.

"Ohio!" called a voice behind him as Snape apparated into the edge of Hogsmeade. It was a most familiar gruff voice. "Strasstree! Aloha! Dog! and{\el} well, I can't pronounce it anyway. Tell me the languages or go to Azkaban."

"Good morning, Moody. Nothing like tradition, is there? Is this a little like `Do not pass GO, do not collect two hundred dollars'?"

"No idea what you're talking about. I have a bet that you can tell me the languages."

"They're greetings. Ohiyo is Japanese. I presume you mean Zdravstui, which is Russian. Aloha is Hawaiian, and Dag, if memory serves, is Dutch. Do you win the bet or lose it, and I thought you had no vacancies in Azkaban."

"We're chock-a-block in Azkaban, but tradition's got to be observed. And you just won me a pocketful of galleons. Hang on{\el} the last one was Boaker Tove. D' you know that one?"

"Hebrew," said Snape, and Moody waved as he disapparated.

Breakfast was under way in the Great Hall, and Slughorn was already there next to Dumbledore. A wave of Dumbledore's hand brought Snape over. "Horace is delighted to have the Dark Arts office and living quarters. He would like to take over the classroom today. Would that be a problem?"

Snape hesitated. \emph{Of course there's a problem. That's my space. I need time to vacate.} But he couldn't say that to Dumbledore with Slughorn sitting there. "No problem at all, Headmaster. I need to clear out a couple of personal things, but that won't delay the move."

"Excellent. The Dark Arts room is just waiting for you to move in."

Snape left breakfast a few minutes before everyone else and went directly to the Potions classroom. He'd been there fifteen years, and a certain amount of private files, supplies, and equipment had made their way into the room. He could hear the rest of the group break up in the Great Hall—there was little time to waste.

\emph{"Peculiaris!"} Snape said with a wave of his wand, making everything that belonged to him invisible to other eyes. It theoretically made everything that belonged to another person invisible to him, but Snape was not concerned about this aspect of the spell. He'd been in this room for fifteen years. Everything in it was either common school property or his personal belongings. Now he could remove what was his own at leisure, without disturbing Slughorn or allowing him to see it.

\sbreak

"And here is the list of supplies that were in the room at the end of the last term, and a preliminary list of things I thought I would order at the beginning of this year. This folder has an inventory of all the equipment that I'm transferring to you, and{\el}"

"Snape, you have got to be the most meticulous Potions master it's ever been my fortune, good or bad, to run across. For the work you're saving me, I thank you."

Snape nodded in response to Slughorn's comment, choosing to treat it, despite the tone, as praise. \emph{It's a good thing you know nothing about modern psychology because if you'd used the word `anal,' I swear I'd have struck you.}

"I still have one or two things in the room, so if you'd wait until tomorrow to change the locks, I'd appreciate it."

"Not a problem, not a problem. Just let me know when you're finished{\el}"

It only took Snape a few trips, while Slughorn was closeted with Dumbledore, to remove all his private possessions from the room. He then removed the Peculiaris spell. The classroom was now entirely Slughorn's, and none of his own responsibility.

And then, without warning, Slughorn was gone.

"Do not worry, Severus. He will be back with us at the beginning of September. He has some things to attend to, and wishes to ride up with the students on the train. You, after all, are acquainted with them all except for the first years. He knows none of them yet."

"What about the eyes?"

"Eyes?"

"Newt eyes{\el} spider eyes{\el} the potions ingredients. They're coming in later this month and have to be{\el}"

"Oh. Well, I am sure that you could handle it{\el} in the spirit of collegiality{\el}"

"Son of a witch!" Snape exploded in fury. "Now he expects me to do his job as well as my own! I swear I'm leaving the eyes out on the lawn to putrefy! I am not taking on his duties so that he can network with the rich and potentially famous!"

"Now, now, Severus. We are talking about school property and school money. I am certain that your basic professionalism{\el}"

"Will be totally eclipsed by my mean-spirited pettiness. Store your own eyes."

In the end, of course, Snape received, inventoried and stored all the potions ingredients that arrived that month for Horace Slughorn. \emph{And he's getting a bill for it, too.}

During the month Snape also made several trips to Birmingham where, no longer chained to his laboratory, he was able to catch up on gossip. There he heard details of the last moments of Igor Karkaroff ('Boring, really. Had the gracelessness to commit suicide. They put up the Dark Mark anyway.'), the attack on Emmeline Vance ('Ran out into the middle of traffic like a sheep. Better for the squad. More publicity.'), and the surprise induction of Draco Malfoy into the ranks of the Death Eaters ('Just honorary I'm told. The boy has to prove himself first.')

All of this was shared with Dumbledore, who was chiefly concerned about Malfoy.

"Nobody's said anything about a task," Snape said over a glass of mead in Dumbledore's office. "I really think only the immediate family knows. My personal feeling is still that it has to do with kidnapping Potter, after which the Dark Lord will kill him. That's what he failed to do last year."

"It does seem nearly as likely as my idea. We shall have to keep a close eye on Harry, and not let him be put into a vulnerable position. Just in case."

\subsection{Sunday, September 1, 1996 (two days before the last quarter moon)}

Then it was the first of September, and the whole staff was prepared for the arrival of the Express. Tables were laid, decorations set up, the house-elves were outdoing themselves, and the teachers were anxiously awaiting the first of the carriages. Snape was looking forward to the moment when Slughorn would start taking care of his own work.

At first the confusion and chaos of the arrival seemed perfectly routine. The heads of houses were out on the lawn shepherding their charges into the Great Hall, and everything was proceeding normally. Then McGonagall cornered Snape. "The others are here, but Harry's missing."

"What?"

"The Weasleys, Granger, Longbottom{\el} they're all here. Potter's missing."

"That's odd. Do the others seem worried or upset?"

"That's the strangest part. They don't seem to care."

Another line of carriages disgorged its passengers. Slughorn was there, and elbowed his way majestically into the Hall. Snape looked quickly around, counting sixth year students. "Malfoy isn't here either. We should tell Dumbledore."

Just then another carriage pulled up on the lawn, and Malfoy stepped out, seeming quite pleased with himself. McGonagall had to meet the first years, so Snape pulled Sprout aside and whispered, "Tell Dumbledore Potter hasn't arrived yet." Then the lawn suddenly cleared of students and professors as everyone entered the castle for the feast.

Snape stayed outside, hesitating in the cool night air. Just as he was about to go in and advise Dumbledore to initiate a search, a sleek silver patronus approached him from the north. It was a patronus Snape didn't recognize, a little like Lupin's but distinct. Then Tonks's voice spoke in his brain. "Come on down to the gate, luv. I got Harry."

Relieved, Snape went into the Great Hall to tell Dumbledore that Potter was safe. Then, picking up a lantern from the entrance hall, he hurried down the hill to the gate. The defenses were less stringent than usual because of the carriages coming onto the grounds, and he was able to open the gates without special permission from Dumbledore. Neither Potter nor Tonks tried to hide their disappointment at seeing him. Potter had blood on his face, but his attitude was one of defiance and outright hatred, as if Snape was responsible for the situation. Tonks offered no explanation, nor did she seem concerned about the blood.

"Well, well, well," Snape said, "Nice of you to turn up, Potter, although you have evidently decided that the wearing of school robes would detract from your appearance."

"I couldn't change, I didn't have my{\el}"

Potter was lying. Students changed into robes long before the train pulled into Hogsmeade and their luggage was taken. Besides, he was holding his invisibility cloak. Something else had happened that Potter was concealing—he'd probably been where he ought not to have been. Snape looked past him at Tonks, whose hostile demeanor was undisguised.

"There is no need to wait, Nymphadora. Potter is quite{\el} safe in my hands."

"I meant Hagrid to get the message," she replied flatly.

\emph{You send a nonspecific patronus to the castle, then because I happen to be the one to receive it, you insult me to my face in front of a student.} Suddenly the meaning of the strange patronus became clear. \emph{I wonder what kind of tales Lupin is telling you—specially tailored to cultivate your sympathy, of course.} Snape began locking the gates again.

"Hagrid was late for the start-of-term feast, just like Potter here, so I took it instead. And incidentally, I was interested to see your new patronus. I think you were better off with the old one. The new one looks weak."

Snape started back up the hill as Potter took his leave of Tonks. The boy was projecting—positively radiating hatred. Snape tried to ignore it, but he was baffled why Potter and Tonks would both act as if he had somehow caused whatever had happened. His own dislike of Potter intensified, and he started to prod, hoping that Potter would lose control and blurt out an explanation.

"Fifty points from Gryffindor for lateness, I think. And, let me see, another twenty for your muggle attire. You know, I don't believe any house has ever been in negative figures this early in the term: We haven't even started pudding. You might have set a record, Potter. I suppose you wanted to make an entrance, did you? And with no flying car available you decided that bursting into the Great Hall halfway through the feast ought to create a dramatic effect."

Potter didn't rise to the bait. They arrived at the castle and paused outside the Great Hall. Potter made a movement towards his cloak, but Snape stopped him. "No cloak. You can walk in so that everyone sees you, which is what you wanted, I'm sure."

Instantly, Potter turned and marched across the Hall to the far side where the Gryffindor table was. Snape watched him, then went up to the staff table to find that the main meal had not yet been cleared away, and that he was at least able to get something to eat. At the Slytherin table, Malfoy was telling some kind of story involving hitting himself in the nose. \emph{Is Malfoy the reason Potter was late? Does this have something to do with Malfoy's task? But if that's so, why does Malfoy think it so funny that Potter's here?}

Dumbledore had risen and was giving his usual opening term speech. The school reacted in surprise to the news that Slughorn would teach Potions, and with greater shock to the information that Snape himself would teach Dark Arts. Potter, obnoxious little toad that he was, even screamed out "No!" at the top of his lungs at the announcement. \emph{And if it had been any other student, or any other professor for that matter, the offender would be immediately taken from the Hall and placed on detention, but I notice neither Dumbledore nor McGonagall seems to regard his behavior as anything but perfectly acceptable.}

The sense of injustice that had sprung to life during Snape's encounter with Tonks and Potter was now expanding into bitterness directed against nearly everyone in the hall. The students' tables buzzed with chatter that Snape knew was about him, and that Dumbledore did nothing to stop, merely waiting patiently until it died down of its own accord. After an admonition to be vigilant and report anything suspicious, and to respect the curfew, Dumbledore sent the students to their dormitories.

With the other heads of houses, Snape spent some time in the Hall getting the students to move. When they'd finally cleared everyone out, and the crowd in the entrance hall was noticeably thinning, Snape heard Dumbledore call his name.

"Yes, Headmaster," he replied, hoping this would not take long. He was suddenly very tired.

Dumbledore steered him back into the Hall where it was more private. "I hope there is nothing causing discord among us," he said calmly. "I understand that you and Nymphadora exchanged words."

"I was under the impression that words were a normal part of a conversation."

"You know what I mean. Did you say something that Nymphadora might have found hurtful?"

"Before or after she told me I had no business being there?"

"Ah," said Dumbledore quietly. "I see there is more here than I at first suspected."

"And while she was complaining about my behavior, did she happen to explain what delayed Potter on the train?"

"No. I was rather hoping you could tell me that."

"Neither Potter nor Tonks felt that any explanation was due to me. They both acted as if my presence was somehow insulting to both of them. I should have left the gate locked."

"Now Severus{\el} They have both been through a rather stressful time. Nymphadora was injured in the fight at the Ministry. She's been in St.~Mungo's. And Harry{\el} well, we older folks often do not realize how hard it must be on a person as young as Harry to lose someone so close to him{\el} Severus?"

Snape was staring down at his hands, fascinated by the fact that the tips of his fingers were trembling beyond his control. It was a moment before he realized that Dumbledore had stopped talking. "I'm sorry, Headmaster. You were saying?"

"No, Severus. I am the one who is sorry. That was unforgivably thoughtless of me. You contain your feelings so well that I sometimes forget{\el} You must have been about the same age, younger{\el} and of course the last year{\el}" Dumbledore studied Snape's face for a moment. "Have you found your loophole?"

"Sir? I thought we were talking about Potter and Tonks."

"Stress sometimes breaks out in the most unpredictable directions{\el} You will pardon me for referring to something personal{\el} but you do have quite a bit to preoccupy you at the moment."

"It had something to do with Malfoy."

"Harry's late arrival?"

"He had his invisibility cloak, and Malfoy was sharing something with his friends about damage to a nose. Potter had blood on his face. Malfoy knows why Potter was late, but Potter doesn't want to accuse Malfoy of anything. That means Potter was where he shouldn't have been, and he got caught. Tonks must have found him."

"That would seem logical. Now, tell me about loopholes."

Snape sat on the edge of the Slytherin table. "There are three parts to the Vow. The first is that I watch over Draco as he attempts to fulfill the Dark Lord's wishes. It's meaningless, since no other action was requested besides watching. The second part, to protect him from harm, contains the phrase `to the best of your ability' which means that if I try to protect him, but don't succeed because of the circumstances, the Vow has been fulfilled. It's the last part that's tricky. The phrase `should it prove necessary' was extended to include `if it seems Draco will fail.' Seems to whom, to me or to Draco? And what's the time frame? If none was specified in the task, it might seem to me that he could succeed during the next ten years. There's even the possibility that no Vow was actually taken on the third part since it referred to a specific task that only one of the parties was able to visualize. Though I don't think I want to risk my life on that being the case."

"So there might be loopholes, but none so certain that we can assume they are there."

"Exactly."

"You will have to find out exactly what it is Draco is supposed to do."

"That will depend to a great extent on Draco."

"I have taken up too much of your time, Severus. You need to get some sleep. I shall try, as much as possible, to reduce the sources of stress."

It was, all things considered, a better end to the day than Snape had been expecting. The bitterness he'd felt against Dumbledore had now abated, and he felt again that he had someone to talk to. Closing off the conversation from his conscious mind, Snape reviewed the following day's plans. For the first time, he was going to be teaching something other than Potions, at least to Hogwarts students. \emph{In some ways, it may be similar to the defense lessons I give the Death Eaters.} The irony of that thought contained a certain symmetry that Snape found pleasing. He slept well that night.

The next day's second lesson was with the sixth year NEWT level students. The classes at this level tended to be smaller, and there was more of a mix of the houses. Snape had found at once that the first floor Dark Arts room made him uncomfortable, and he'd changed it.

First and foremost, he did not like the excessive light. After fifteen years teaching in the dungeon Potions room, the tall windows made Snape feel vulnerable, exposed to danger. In addition, he could not teach sitting at a desk or podium—he had to move around. If he was standing next to the windows, the students wouldn't be able to see his face. He'd be a backlit silhouette. Curtains now covered those windows, and the students' desks were lit by chandeliers.

The other major change was to rid the room of every trace of Dolores Umbridge. Gone were the lace and the flower arrangements, to be replaced by classic prints and woodcuts of different aspects of the Dark Arts, both as teaching aids and as a reminder to the students that what they were studying was of vital importance in a suddenly dangerous world.

Snape, in fact, had three major priorities for the year, the first being the need to impart to the students how dangerous their opponent was and how important to learn to defend themselves. The second was to show them the attraction of the Dark Arts, for no one followed them with the intention of becoming a slave. No, the Dark Arts seduced, entranced, and lured their victims into a quicksand from which it was nearly impossible to escape. It was impossible to battle them effectively unless you understood the attraction. The third priority was to show them the need to cooperate, to band together. One person alone was almost certain to be defeated.

Just before the beginning of class, Snape opened the door and allowed the students assembled outside to enter, a little surprised at how many there were. When they'd settled down, which happened rather quickly, he began.

"I have not asked you to take out your books. I wish to speak to you, and I want your fullest attention. You have had five teachers in this subject so far, I believe. Naturally, these teachers will all have had their own methods and priorities. Given this confusion, I am surprised so many of you scraped an OWL in this subject. I shall be even more surprised if all of you manage to keep up with the NEWT work, which will be much more advanced.

\textooquote The Dark Arts are many, varied, ever-changing, and eternal. Fighting them is like fighting a many-headed monster, which, each time a neck is severed, sprouts a head even fiercer and cleverer than before. You are fighting that which is unfixed, mutating, indestructible{\el}" \emph{Very much like the classical Hydra, which even the hero Hercules was unable to battle alone, but we shall cover that later.}

As he spoke, Snape moved around the class, pointing out illustrations of the effects of certain dark spells and answering questions. It was his first task, however, to introduce the subject of nonverbal spells. McGonagall and Flitwick would both build on what he taught, but the initial lesson was usual dealt with in Dark Arts. "What is the advantage of a nonverbal spell?" Snape asked the class.

Granger's hand shot immediately into the air. The rest of the class sat like lumps, conditioned over the past five years into laziness, knowing that the compulsive Granger would do all their work for them. \emph{I'm going to start calling on students who don't raise their hands, just to keep everyone on their toes. Maybe beginning tomorrow.}

Granger typically gave a memorized textbook answer, which Snape expanded on. "Not all wizards can do this, of course; it is a question of concentration and mind power which some lack." Waves of raw emotion hit Snape as they had the evening before, and he glanced over at Potter and then away. \emph{You may actually turn out to be rather good at this, since it requires the exact opposite talent from occlumency. I wish I knew why you're laboring so hard to let me know you don't like me, though.}

The class split into pairs, given the assignment of trying to cast minor nonverbal jinxes at each other, with the recipient of the jinx trying to repel it nonverbally. The first attempts went about as expected, with most of the students unsuccessful at doing either, only one Slytherin, one Gryffindor, and two Ravenclaws managing it.

Potter was paired, as usual, with Weasley, with the result that Potter was getting no chance to practice at all. Instead of giving up and at least allowing Potter to try, Weasley insisted on straining until his face turned purple while Potter stood idly doing nothing. Exasperated, Snape moved to intervene.

"Pathetic, Weasley. Here{\el} let me show you{\el}"

Turning towards Potter in order to demonstrate the technique to Weasley, Snape was hit suddenly with a resoundingly verbal \emph{"Protego!"} that slammed him back against a desk. As the rest of the class stopped their assignment to watch, Snape forced himself to remember Dumbledore's instructions to treat Potter with kid gloves.

"Do you remember me telling you we are practicing nonverbal spells, Potter?"

"Yes," was Potter's curt reply.

"Yes, sir," Snape reminded him.

"There's no need to call me `sir,' Professor."

\sbreak

"You cannot let him get away with that! It's bad enough that he spends every moment near me projecting violent, hate-filled thoughts, knowing that I can pick them up, but to attack me physically—which I intended to overlook because of the lesson—and then defy me in my own classroom in front of other students—you can't let him get away with that! And if it were any other teacher in this school, you wouldn't!"

"Severus, please try to calm down. There are special circumstances here{\el}"

"That don't apply to Susan Bones, despite her loss, and wouldn't apply to Malfoy or Crabbe if the outcome of that fight had been different, and would also never apply to Flitwick or Trelawney! Just to Potter—and just to me!" Snape suddenly became icily cold. "You want me to resign. Is that what this is all about?"

"Good heavens, no! You of all people are the one I need most to have around me. Please do not think like that."

"Then why did you cancel his detention?"

"That may have been hasty and unthinking on my part. Let us consider it postponed. I do need to confer with Harry, and it needs to be Saturday. Is that better?"

"Yes, sir."

"Clearly not."

"Take him out of my class, sir. Or tell him to stop projecting. One of these days he may come up behind me, and I'm not going to realize it's him, and then you will have a problem."

"I am certain that you are in much better control of your reactions than that." Dumbledore regarded Snape for a moment. "I seem to recall you were quite depressed for a while about your parents' deaths."

"Yes, and I lay in bed staring at the wall for days and days. I don't recall wandering the school mentally threatening my teachers with bodily harm."

"I had thought not to tell you, because I considered it a private matter of Harry's, but I see that it concerns you immediately and intimately{\el} Severus, Harry holds you personally responsible for Sirius Black's death."

The nature of the revelation was so unexpected and bizarre that for a minute or two Snape was unable to respond. Then, "I hope you tried to disabuse him of that notion."

"I did, but without success. He believes you deliberately incited Sirius to go to the Ministry knowing and hoping that he would be killed."

"I tried to talk him out of it."

"I know. Remus told me. Harry believes that you did so in a way that would make Sirius feel you were calling him a coward, and that he was goaded into fighting. And that you are pleased by Sirius's death."

"Then he's more of a fool than I thought, on all counts. Nothing I said would ever goad Sirius into anything except beating me up. And I never wanted anyone dead." Snape stared down at his hands. "Anyone who knew the smallest thing about Sirius would know that the moment he heard a friend of his was in danger{\el} How can Potter even imagine he would have to be goaded? If there's anybody outside of Bella Lestrange or the Dark Lord himself who's responsible for Sirius's death it's{\el}" Snape paused, then looked up again at Dumbledore. "I see. That's the special circumstance."

"It is a lot for a young man to bear. All at once like that."

"He'll have to face it some time. He'll have to accept the consequences of his own decisions and actions some time."

"I am hoping that it will come to him gradually, and that he works it out himself."

"Meanwhile I get to be whipping boy."

"It may work to our advantage."

"How?"

"If ever the three of you face each other—you, Harry, and Tom—all Harry will give up about you is that he hates you, and that you were working to destroy Tom's enemies. It could buy you time."

"As long as Potter doesn't kill me first."

"I think I can give you reasonable assurance that that will not be a problem. Now, since I have you here, I did have a couple of things I was hoping you could research for me."

"I remember. About Fortescue."

"Do you know anything about families named Peverell and Gaunt?"

"No. Well, John of Gaunt, of course. Character in Shakespeare's play Richard II. Speaks the great lines—

\emph{This royal throne of kings, this sceptred isle,}

\emph{{\el} This fortress built by Nature for herself}

\emph{Against infection and the hand of war,}

\emph{This happy breed of men, this little world,}

\emph{This precious stone set in the silver sea,}

\emph{Which serves it in the office of a wall}

\emph{Or as a moat defensive to a house,}

\emph{Against the envy of less happier lands,}

\emph{This blessed plot, this earth, this realm, this England.}

\textooquote It makes a lot of sense when you remember it was written just seven years after the defeat of the Spanish Armada."

Dumbledore was watching Snape with an expression of wondrous amazement. "Spanish Armada? Who was this John of Gaunt?"

"Younger son of Edward III. His son, grandson, and great-grandson were kings. If you count the illegitimate children's descendants, all our kings and queens since come from him, including the present one. His grandson Humphrey married a witch."

"Ah! A witch family named Gaunt?"

"No! The House of Lancaster. Gaunt—Ghent in Belgium—was where John was born. Only Shakespeare thought that people called him that after infancy. And Humphrey never had children. At least not legitimate children. The witch was his mistress before she became his second wife, so there might be something there. Also covered by Shakespeare in{\el} `Henry VI, part one.'"

"And all those years you kept popping down to the theatre in London, I thought it was a waste of time. How wrong I was. Do you think you could check on wizarding families called Gaunt and Peverell? Families important enough to be landed gentry at one time."

"Anything else?"

"Founders of Hogwarts—known artifacts whether believed to still exist or not. And anything connected with the occult or prophecy that Riddle might use to symbolically connect things belonging to any of these people."

"You never ask for anything small, do you?"

"I have great confidence in your resourcefulness. By the way, I take it you are no longer going{\el} wherever{\el} on Saturdays."

"No. Fridays and Sundays, though not both every week. This week I'm going down on Friday. How did you know?"

"You scheduled Harry's detention for Saturday evening. And{\el} wherever{\el} is south of here. Because you are going down."

"Sir, there's almost nothing north of here."

"Do not tell the people of Inverness that. They have a perfectly delightful town, not to mention a world-famous monster{\el} And Severus{\el}\,?"

"Headmaster?"

"Do try to remember about Harry."

"I'll do my best, sir. As soon as he finishes his detention, I'll try to ignore his presence."

"Thank you, Severus."

Friday evening after supper, Snape apparated to Birmingham and, after signing in, went straight to his laboratory to check on the requisitions that had accumulated in the week that he was gone. Headquarters was peaceful, the laboratory quiet and orderly, and Snape found himself wishing he could be there every day, far from the chaos and misguided malice of the adolescent world.

Yaxley came up around eight-thirty to see if Snape wanted to join him for tea. There were a fair number of employees in the cafeteria, but one in particular caught Yaxley's eye. "Watch this," he whispered to Snape, nodding towards a corner and a short wizard with mousey hair sitting there alone. Then turning to the stairs and speaking to empty air, Yaxley said in a fairly normal tone of voice, "Bella! My you're looking well tonight. Care to join us?"

The wizard leapt up so fast that his chair fell over and tea sloshed out of his raised cup all down the front of his robes. Gathering his things helter-skelter, he rushed out of the cafeteria through the clinic and was gone. The others at their tables chuckled softly.

"Who was that?" Snape asked, smiling slightly as he and Yaxley settled at another table.

"Bennett. Used to be at the Cardiff office. Good with memory charms but not much else."

"Sounds like someone I know. What's between him and Bella?"

"Came in on Tuesday with a little lacquered box that had the picture of a greyhound embossed on the lid. Very nice work, but not anything really expensive. Bella had a royal fit! Insisted it was hers and that Bennett was a thief. We had to restrain her from cursing him then and there. He kept saying he bought it from a street peddler. She wants thumbscrews. He's been avoiding her ever since."

"Hard to believe, a street peddler selling Black family possessions. I guess if I were Bella, I'd be angry, too."

"She's looking for the peddler. Apparently he had other things—silverware, cups, scattered items of jewelry{\el} Lucky for him Bennett has no idea who he was."

"How's Bella doing otherwise?"

"Slitting her own throat. She's out to bring you down. Thinks you've elbowed your way in above your proper station. Even went so far as to insinuate that a half-blood—no offense intended—wasn't fit to advise the Dark Lord. Now she wants to check the backgrounds of all the people who seemed relieved when that tactic didn't work. She insists they're `passing' as pure-bloods. Personnel isn't cooperating, though. They don't want the Dark Lord angry at them."

"I leave for a week and the entire place goes to perdition in a hand basket."

A messenger appeared at the door, looked around, and came over to Snape and Yaxley. "Excuse me, sir. He wants to see you."

A grin spread over Yaxley's heavy features at the respectfulness of the tone. "Looks like I'm in the right camp," he said as Snape rose from the table and headed for the interview room.

"Tell us of Slughorn."

"Fatter than ever. As conceited as ever. Still looking for anyone whose connections can get him perquisites."

"Is he closeted with Dumbledore? Is this why he has been brought back?"

"Quite the contrary, they seldom speak. He came briefly in August, left again, returned only with the students on the train, and seems frustrated that Dumbledore won't pay more attention to him. I have the feeling that Dumbledore's had trouble finding instructors. He could get no one for the Dark Arts position, and only Slughorn for any position. Slughorn can't teach anything but Potions, so Dumbledore was forced to move me into Dark Arts."

"Yes, that information pleased us. It is of great strategic benefit. Do not create any suspicion as to your motives or allegiances. We must see that you remain there for a while. In the long run it may be one of our most valuable assets."

"Thank you, Lord."

"Has Slughorn attempted to curry your favor?"

"No, Lord. I have no family connections and am not important enough."

"If he should move to bring you into his circle, you will accept his invitations. You will gain his confidence and get him to trust you."

"Yes, Lord."

Snape didn't return to Hogwarts that night, instead working late at headquarters and then apparating home to Lancashire. There he went through his own extensive library, and the next morning apparated to London to check out several muggle shops that catered to the occult and to hobbies.

Divination was a branch of magic that Snape usually had no patience with, and he certainly didn't want anyone in the wizarding world to think he'd suddenly developed an interest. In any case, many of the divinatory arts were just as well-known to muggles as they were to wizards, and muggles were more inclined to actually analyze what they were doing. Thus he avoided Diagon Alley and the area of Charing Cross Road where the Leaky Cauldron was to concentrate on large bookstores and quaint little shops, and generally pick up several good books and tips on the way.

He also purchased two decks of tarot cards. One was the Rider-Waite-Smith deck that provided the symbolism for most of the others, and the second was a reproduction of an 18th century French deck. Late that afternoon, after studying the decks for several hours, he returned to Hogwarts.

Arriving early to supper, Snape slipped into the seat next to Dumbledore's, forcing Slughorn to move further down. When Dumbledore arrived, Snape laid a card in front of him.

"What is this, Severus?"

"Beautiful, isn't it. It's the two of cups."

"What does it mean?"

"Love. Friendship. Partnership. The Union of Souls."

"It does not sound like Tom."

"Ah, but it also means the reconciling of differences and the merging of opposites. Look at the center symbols. It has three of the four houses of Hogwarts. The lion's head is joined to the eagle's wings. Fire and air merged and sharing a role. The physicality of Gryffindor and the mentality of Ravenclaw. The snakes are Slytherin of course, which would leave Hufflepuff represented by cups if we wanted to draw out the symbolism. So the earth of Hufflepuff becomes the water of the tarot. Slytherin would transform from water to earth, and Gryffindor and Ravenclaw could reverse as well."

"Why did you choose this one?"

"It's the only one where most of the house symbols are on the same card. He tends to see symbolism on the surface rather than digging deep. Look at this one." Snape took back the two and laid down the Magician. "The guide, the leader, the beginning of a new order, the One who merges the energy of heaven and earth. Also the only one with all the symbols of the suits on it: Wands, Swords, Cups, and Coins. And there's a snake, the Worm Ouroboros, the symbol of eternity. And the lemniscate, the symbol of infinity. So if we look at the two of cups and the Magician together, the cup is Hufflepuff, making the coin Slytherin. If Gryffindor and Ravenclaw also switch, then Gryffindor is the sword, and Ravenclaw is the wand. Tell me if this makes any sense to you, because I'm just fooling around with the symbols."

"Actually, it does. Is there anything else?"

"Yes, there is. The original card was much less flattering. The magician was originally a charlatan, a mountebank, trickster, and con artist who deceived by slight of hand. The symbols were just the props of his trade, no eternity or infinity. But the lemniscate was sort of there. It was a large, floppy hat."

"That give us a lot of potential items, does it not?"

"Swords, cups, money, anything inscribed with a pentacle, wands, staffs, snakes, the caduceus—pendants, rings, or anything shaped like or inscribed with any of the above—and hats. Shall I continue with this line of investigation, or are you quite fed up?"

"By all means continue, Severus. It has given me much to think about."

"What exactly am I looking for, sir?"

"Best you not know. That way your insight is not overly restricted or influenced by preconceptions."

Snape collected his cards and went to his own place at the table, allowing a greatly relieved Slughorn to move next to Dumbledore. Since he and Dumbledore had spoken below the level of a whisper, no one in the hall would have heard them. Only McGonagall had a chance to see the cards, but she was talking to Sprout. There are times when actions performed in the midst of a crowd can be the most private.

For the next few days, Snape was reasonably content. There is a lot to be said for reasonable contentedness. By the end of the week, of course, reality set in, propelled by Horace Slughorn.

"We have an entire shipment—a case lot—of flobberworms. Someone has to store them."

"I am sorry, Minerva, I'm not the Potions instructor anymore. Have you spoken to Professor Slughorn about this?"

"Of course I have!" McGonagall seemed positively apoplectic. "He says I should put the crate in the fountain court until he has the time!"

"Then maybe you should."

"Severus Snape, you irritating young whippersnapper! You may think that the loss of two hundred sixty-three galleons worth of flobberworms is nothing, but I assure you{\el}"

"I'll take care of it, Minerva."

It was shortly thereafter that both salvation and retribution entered in the unexpected person of a Gryffindor student named Demelza Robins. She conveyed a message from Slughorn himself requesting that one Harry Potter be released from detention in order to attend a Slughorn soirée that evening.

\emph{Load me with your work and then ask for favors? And not even have the courtesy to come yourself?} It was with great pleasure that Snape sent back word to Slughorn that Potter would not be excused—he would be helping to sort and store Slughorn's flobberworms.

"Oh," said Snape as Robins turned to go, "and we have plenty of protective gloves. Let Potter know he doesn't have to bring his own."

The same Saturday, after he and Potter finished with the flobberworms, Snape apparated to Lancashire. Following an exquisitely pleasant evening home alone, Snape retired to bed, slept in, and then planned his Sunday over a leisurely breakfast.

The point was, of course, that everything was closed on Sundays—the Public Record Office, National Archives, and Family Records Centre at the top of the list. It was the simplest of maneuvers for Snape to apparate in, disable the motion sensors and cameras, and have the entirety of British public records to himself.

Snape, never having been moved to investigate his own family, was forced to stumble his way through the morass of records. One of the first things he discovered was that Gryffindor, Slytherin, Ravenclaw, and Hufflepuff were not family names. They, in fact, preceded most family names by about three to four hundred years, and noble family names by a century. The surnames of the famous founders of Hogwarts were nicknames only, not necessarily received from parents, nor necessarily passed on to offspring.

Another shock was that the word `ancient' when applied to Rome and Greece meant a period over two thousand years in the past, but when applied to British families meant anything prior to the Restoration of Charles II in 1660.

\emph{Which, of course, explains why today there are no wizarding families that bear the names of the founders. And any actual genealogical connection is based on hearsay. Someone told the visitors in 1667 that family tradition maintained a direct link to Godric Gryffindor over sixteen generations. But the actual documentary proof is a tad lacking.}

By the end of a long and trying day, Snape had only a few unsatisfactory pieces of information: that Humphrey, grandson of John of Gaunt had, around 1434, married his former mistress Eleanor Cobham, daughter of Reynold Cobham, son of Reynold Cobham of Kent, subsequent to which her witch identity had been revealed, and that around a hundred years earlier Sir Hugh Peverell of Devonshire had married Elizabeth Cobham, daughter of John Cobham of Devonshire, son of James Cobham of Hoo, Kent.

It was the only connection between the name Gaunt and Peverell that Snape was to find for quite some time.

That evening Snape apparated early to headquarters so that he could sneak in a dinner at a local Pakistani restaurant. He then spent the rest of his time with potions and medicines before he had to apparate back to Hogwarts.

On Monday morning, Snape stopped Dumbledore in the entrance hall. Something had been nagging at him for a week, and he'd remembered what it was.

"Can we speak outside for a moment, Headmaster?"

When they were far enough out onto the lawn that they could not be overheard, Snape stopped. Speaking of the headquarters of the Order wasn't possible in a crowd, however quiet one tried to be.

"Is Grimmauld Place secure, sir?"

"I believe it is. Is there a reason you might think otherwise?"

"One of our people bought a knickknack from a peddler, and Bella claimed it was a family possession. It didn't occur to me earlier, but now I wonder if the things he was selling came out of headquarters. I really don't think we should use the building anymore in any case{\el}"

"Why not?"

"Everybody knows where it is. All the upper echelon used to visit the house socially, and Bella would like to move in now that Sirius is dead. The fact that none of them can any longer find the actual building is a dead giveaway. That means that anyone inside is safe, but people arriving and departing are not. They even tried to kidnap Sirius in the square outside, remember? And now, if someone has access to go in and steal things{\el}" Snape suddenly had to suppress an image of Phina's face that rose unbidden at the memory of the botched operation. He turned to look down the hill.

"I recall, Severus. The information is valuable and the advice sound, as always. I shall keep the matter under consideration. No decision about the place has yet been made. Thank you."

\sbreak

Dumbledore was now gone most of the time. It made little difference to the day-to-day running of the school, which proceeded normally, although there were a few oddities that stood out. One was that Slughorn seemed to feel that Potter was an excellent Potions student.

"Wonderful boy. Takes after his mother in that, I'd say. Seems to have an instinctive grasp of the subject." Slughorn accepted a cup of tea from Sprout in the teachers' staff room.

"I don't recall your ever mentioning Potter's talent, Severus," said Sprout.

"He never deigned to reveal it to me. Are those pumpkin-chocolate chip cookies? May I?"

"Will you look at the sky! There's a storm brewing, I'm sure. Pity that tomorrow's the Hogsmeade outing. The poor students will be drenched. And frozen."

"I notice, Pomona, that you have no such sympathy for me, who must also be out in the wet and the cold shepherding them."

"You're going into Hogsmeade, Severus?" Slughorn commented. "What an excellent opportunity to chat with the students in a relaxed, social atmosphere!"

"Right, Professor. I'm going to chat. Never pass up an opportunity to chat with students, I say."

Sprout was fizzing into her tea, but Slughorn seemed to take Snape's words seriously. "I know this is an imposition on your own enjoyment of the day, Severus, but would you be willing to trade duties with me? I'm supposed to stay here and supervise the first and second years. It's been a while since I was able to visit Hogsmeade."

"I don't know{\el} That trip to Hogsmeade means a lot to me. I am so looking forward to discussing the upcoming Quidditch season with Ron Weasley over butterbeers{\el}"

Snape would have continued and extorted a favor from Slughorn, but Sprout was turning purple, a phenomenon that would soon tip Slughorn off to what he was doing. Better to concede defeat gracefully than to be caught in a subterfuge.

"But it is your first trip in what{\el} fifteen years? Far be it from me to spoil the day for you. I would be happy to exchange the duty and let you go into Hogsmeade tomorrow."

Which was why Snape was still in the Great Hall the following afternoon, finishing a leisurely game of cribbage with Flitwick, when Hagrid burst into the entrance hall and charged up the staircase to the hospital with a student in his arms, bellowing at the top of his lungs, "Snape! Someone get Snape up to Pomfrey! She's been cursed!"

Snape was up and out of the Great Hall in an instant, taking the stairs two at a time to catch up with Hagrid. The student, Bell from Gryffindor, was levitating and convulsing, her body racked with strange spasms that made it difficult for Pomfrey and Hagrid to hold her down and strap her to a bed where they would be able to treat her more easily.

"What caused it?" was Snape's first question.

"Don't know," said Hagrid. "Couple of students was running for the castle as I were going down the hill. They grabbed me and took me to her. She were like this there in the road."

"How high?"

"'Bout six feet."

"Point of contact?"

"Hand, seems like."

Pomfrey was already stripping off the girl's gloves, and Snape seized a tourniquet from the supply cabinet. The contact point was a small spot of skin that was exposed by a hole in the glove. The spot itself was already mortifying, and purple streaks were spreading from it through the capillary system and into the veins of the hand and arm. Snape wrapped the tourniquet near the elbow and tightened it.

"Will that work?" Pomfrey asked. "It looks like it's already spread through her body."

"Nervous system first. That's causing the convulsions." Snape was putting on protective gloves and selecting a tiny knife and a small basin from the instrument drawer. "Now it's entering the bloodstream. That'll kill her. Lucky it was just a small spot, or it would've spread too quickly to stop. She'd already be dead."

As he talked, Snape lanced the contact point and allowed the contaminated blood to flow into the basin. "Get gloves on yourselves. No one comes near this basin that isn't protected. We're going to have to destroy it, the knife, and the gloves before we're finished. Get St.~Mungo's. I can only administer first aid. They have the equipment and medicine to treat her. Hagrid, hold this basin."

Hagrid monitored the seepage of blood from Bell's hand while Snape took his wand and began a low chant around the area of the wrist. McGonagall entered the hospital then, and Pomfrey, having already passed on the medical particulars, turned over to her the business of admitting a team from St.~Mungo's, while she helped Snape with the chanting to slow the progress of the poison.

The team arrived and took Bell to London. One of the medics also took the basin of blood to be analyzed, sealing it in a gelatin-like substance to avoid any accidents in transit.

"Will you be needing the thing that caused it?" McGonagall asked. "I have it here."

"No, Professor," the medic answered. "We've got what we need. We're a hospital. The artifact analysis should be done by the Ministry. We'll be mentioning in our report that it's here."

The first thing the Hogwarts staff did was place the knife and the gloves in a special metal box built through the wall of the hospital wing and incinerate them. Then they put the small bundle McGonagall carried into a small wooden container to ensure none of them touched it.

"How did you get it?"

"The other students gave it to me. I'll be taking statements from all of them as to what happened." McGonagall looked simultaneously angry and frightened.

"At least they had the sense not to try to touch it." Snape gingerly unwrapped the cloth that held the object. It was a necklace. A beautiful necklace of gold and opals. "I know this. It's been for sale at Borgin and Burke's for years. It was still there this summer."

"And what, laddie, were you doing in a place like that this summer?"

"A fine expert in Dark Arts I'd be if I didn't visit Knockturn Alley from time to time. It's a constantly changing market. You have to know what's out there. This one's killed before."

"How do you know?"

"It said so on the sign in the shop. It'd already killed nineteen muggles, or something like that. It cost a huge amount of money, too. Fifteen hundred galleons."

"Why would someone rich enough to buy it want to hurt someone like Katie Bell?" Pomfrey looked around at the other three, clearly mystified.

McGonagall cleared her throat. "The other students said she was going to give it to someone in the castle. They thought perhaps she was under an Imperius curse."

The room seemed suddenly cold to Snape. "Who were the other students?" he asked.

"Potter, Weasley, and Granger."

"They were close enough to witness this?"

"To hear the conversation between Katie and Leanne just before Katie touched the necklace."

"So Bell would probably have seen them, too?"

"Certainly."

"Minerva, when is Professor Dumbledore coming back? I need to talk to him."

"I assume you've already spoken at some length with Professor McGonagall." Snape said as he walked later into Dumbledore's office.

"And with Madam Pomfrey, yes. Madam Pomfrey is, incidentally, extremely pleased that you have the Dark Arts position. She respects your expertise and feels that you respect hers."

"That is kind of her. It's hard to be familiar with Madam Pomfrey's skill over a period of two and a half decades and not be in awe of her."

"Now what is your assessment of these recent events, Severus?"

"I refuse to kill you."

"Severus?"

"Not only that, I refuse to kill anyone right now."

"I beg your pardon? I mean I am pleased to hear that but{\el}" The sight of Snape's raised hand had its effect, and Dumbledore was silent for a moment.

Snape sighed, then walked over to the cabinet where Dumbledore kept his mead and poured himself a glass. "There's a question answered," he said.

"You know one of the most irritating things about you is that you assume others should know what you are thinking. What question has been answered?"

"The Vow. Malfoy has a task to perform that is so immense that the Dark Lord himself has failed at it, and so dangerous that Narcissa is sure that the Dark Lord intends him to die. We knew it wasn't information gathering. It had to be kidnapping, or murder, or something similar. I'll agree it's murder now, because the necklace was intended to kill. There couldn't be a misunderstanding because it was advertised as a killing necklace in Borgin and Burke's.

\textooquote I know the objections, sir. How can we be certain it was Malfoy? Yet the chances of two different people having expensive and powerful plots to harm or kill someone in Hogwarts at the same time is extremely small. I know Malfoy was in the castle under detention. He found some way around it.

\textooquote I think it's clear now that Malfoy is under orders to kill someone at Hogwarts. He purchased the necklace and arranged a way that a totally innocent student could be placed under an Imperius curse to deliver the necklace to its victim. His plan was foiled because his unaware agent accidentally touched the necklace and was cursed herself.

\textooquote The intended victim could not have been Potter. Potter was a few yards from Bell on the road back to Hogwarts, and she could have given it to him there. She didn't. She didn't care that he was there. Who else at Hogwarts has the Dark Lord himself tried and failed to kill? You. The necklace was intended for you. Much as I hate to admit it, you were right all along. Malfoy's mission is to kill you."

Dumbledore nodded in acknowledgment of the analysis, but waited patiently for more. Snape, too, waited, then continued when it was clear Dumbledore wished to hear everything before commenting.

"The third part of the Unbreakable Vow," Snape continued, "is that I would carry out the deed that Draco failed to accomplish. Well, he's failed to accomplish it, and I've announced that I will not fulfill it, and I'm still alive. I would say there's reason to suspect we do have a loophole here."

"Excellent. Very nicely analyzed. I must admit that I am relieved to have it confirmed that I am the target. Better me than another teacher or student. So he has tried and failed, and you are still alive. Maybe this means that Draco has a time frame in which to complete his task. When his time expires, then you die. Maybe it means that as long as Draco still believes he can succeed, we have not reached the point of `fail.' You need to watch out for yourself. This could jump out at you at any moment."

"Whatever the loophole may be, Headmaster, I am quite certain on one point. I'm not going to kill you to complete Malfoy's task."

"You have already agreed to it for quite different reasons. I fail to see how the possibility of helping Draco would cause you to change your mind. I would feel more comfortable if you would agree to abide by my assessment of the situation should we come to a point where immediate decision is necessary."

"Are you asking for an Unbreakable Vow?"

"I would never ask for such a thing."

"Then I agree to abide by your decision."

The following day, Snape left word for Malfoy that he wanted to speak with him in Snape's office at lunch time. Malfoy didn't appear. Instead he sent a message via Crabbe to the effect that he was not feeling well and had gone to the hospital wing to have Madam Pomfrey look at him. Knowing that Malfoy would do precisely that, Snape didn't even bother to check.

\emph{Whether his illness is real or a ruse is irrelevant. He'd find out that I didn't trust him and do his best to avoid me even more. Best wait until there's a pattern he can't deny. Assuming, of course, that he continues to avoid me.}

At Birmingham, Bella started to get pushy. During Snape's Sunday trip down, she spied him in the cafeteria having tea and a scone in a corner, and slipped into the seat across from him. "You used to be a friend of my cousin Regulus, didn't you?"

"We were schoolmates. And colleagues. Do you think it's wise to bring this up here?"

"Ancient history, puppy dog. Did you ever visit him at home?"

"Someone like me? Knowing your aunt as well as you must, you can't possibly think I'd be welcome there."

"You could have passed for pureblood if Regulus was willing to lie for you. Come now, you must have known something of his family, his home life{\el} What was the address of that house now? It seems to have slipped my mind."

"I'm sure I couldn't say."

"And I'd be willing to bet galleons to knuts that's the literal truth. You couldn't—not even if you wanted to. You couldn't say. You couldn't draw it on a map. You couldn't take me there. And that, puppy dog, is the most valuable piece of information I've ever gotten from you."

"Come now Bella, do you think I've forgotten the little side action you initiated back before summer started? None of this is new."

"Oh, yes. Poor Phina. Poor, poor Phina. Do you think about her, puppy dog? Do you lie awake at night whispering her name into your pillow? Do you regret those hours you might have spent with her and didn't?"

"Do you have a point?"

"Someone is stealing what belongs to me. Stealing it out of that house—my house. Under the circumstances, I think I'm justified in thinking this someone works for Dumbledore. Your precious headmaster abets thieves. Now, Mr.~Spy-in-the-Enemy's-Camp, I know you can't tell me where, but you can certainly tell me who. And if you can't, the Dark Lord may be interested in learning why not. After all, what possible reason would you have for concealing that name{\el} unless it was a question of your own personal loyalty?"

"I don't know who it is, Bella."

"Find out."

Bella rose to leave. Just as she stepped away, she turned to face Snape again, as if remembering something that was of marginal importance. "Oh, yes. Leave my nephew alone. He has enough to worry about without being harassed by you."

"I believe his mother is still his legal guardian. Only her wishes and instructions carry any weight with the school."

"I'm not talking about the school. I'm talking about you."

"Are you contemplating taking this issue before the Dark Lord as well?"

Bella glared at Snape, snarling in anger. Then she swept out of the room, leaving him to ponder the dilemma she'd given him.

\emph{She can't go to the Dark Lord about Draco without revealing Narcissa's indiscretion. But she can undermine me with this theft business. Something else to discuss with Dumbledore.}

\sbreak

"Do you think this could seriously compromise your position?" Dumbledore sat calmly at his desk as Snape poked, prodded, and manipulated his right hand. "How does it look?"

"As well as could be expected, I suppose, considering the power of the curse still affecting it. Your fingers wiggle, you feel pinpricks, heat, and cold. The neural system is still there—both sensory and motor control. And the good thing about the tissue damage{\el}"

"It is quite comforting to know there is something good about it."

"Yes. Well, the good thing is that the tissue, for all its blackened appearance, doesn't seem to be dead. It's been four months, and it hasn't sloughed off. It'll never be what it was before you behaved in such a foolish manner, but I'm beginning to think you might have more than a year left. I certainly am not going to number the days until your demise."

"I look forward to living a while longer then, in anticipation of the day when{\el}" Dumbledore chuckled. "I will be able to play the violin?"

Snape glared at Dumbledore. "If you think I'm biting on that one, you're sadly mistaken."

"That is the trouble with wizards who have muggle experience. They have heard all the jokes. Now Arthur Weasley would have walked right into it without the slightest suspicion{\el} What about my other question?"

"It depends on how desperate or angry Bella gets. The names of people who go into headquarters aren't covered by the Fidelius Charm, so finding out the name is a performable task. The Dark Lord will believe that I didn't want to accommodate or take orders from Bella, but he would not accept that I couldn't give him a name if he asked for it."

"And if I were Riddle, I would assume that pure curiosity would lead you to investigate, even if you did not already know. So if you could not tell him when asked, it would be a grave matter."

"Very appropriate choice of words."

"Not intentional, I assure you. When do you go south next?"

"Saturday. After the Quidditch match. I'm doing some more research, and I'll go to headquarters Sunday."

There was a long pause as Snape watched Dumbledore deliberate. Finally, "If you were trying to find out the name for curiosity's sake, how would you go about it?"

"Logically," Snape replied, "methodically. Like everything else."

"I suggest you do that, then. I do not think it would be right for me to give you the name. The person in question has gone into hiding. I shall get word out that it may become more dangerous."

"Thank you, Headmaster."

\sbreak

\emph{A she-wolf with bubble gum-pink fur loped along Oxford street in the rain singing, `I feel pretty, oh so pretty{\el}' She stopped when she saw him. `Do you feel pretty, too?' When he was silent, she added, `It's on the application form, you know.'}

\emph{He shook his head. `I've never been pretty.'}

\emph{`Not be,' the she-wolf laughed, `feel. You have to feel. Feel pretty. Who's the pretty girl in the mirror there{\el}' She turned to continue down Cromwell Road, which he recognized because the Natural History Museum was to the left. `You can apply now,' she said in parting. `They left you a puppy.'}

\emph{There was a little pen of puppies outside Imperial College, and he stood in the queue waiting his turn. Everyone, it seemed, wanted a puppy, and he was afraid they would all be given away before he got to the front of the queue. `Name?' they asked him when he finally made it.}

\emph{`Russ,' he replied.}

\emph{They handed him a puppy with russet fur, which he carried gingerly to the doors into the college. `Name?' he was again asked.}

\emph{`Russ.'}

\emph{`Not you. The puppy.'}

\emph{`I don't know its name,' he admitted.}

\emph{`You can't bring it in if you don't know its name.'}

\emph{`He looked around to see if there was anyone who could help him. Sirius was there, inside the doors, and beside him was a delicate silver doe. `Do you know the name?' he called.}

\emph{`What will you give me if I tell you?' Sirius called back.}

\emph{`Anything.'}

\emph{`Then it must be valuable.'}

Sirius was suddenly gone and Snape was staring at the ceiling of his bedroom, breathing hard as if he'd been running. \emph{Nymphadora's patronus has changed to a wolf. Is that because she's fallen in love with Remus? Potter's patronus is a stag. Was that his father's, too? Does that mean the doe is{\el}\,? But if so, why now? I don't feel any{\el}}

He stopped, pushing the thought behind locks and wards, for the voice of the bubble gum-pink wolf echoed in his brain—\emph{You have to feel. It's on the application form, you know.} 


