% A Difference in the Family: The Snape Chronicles (Rannaro)
% Yes, That Is My Job

\chapter{Mind Games}

\subsection{Saturday, February 17, 1996}

The following Saturday was the Quidditch match between Gryffindor and Hufflepuff. The only interesting thing about it was assessing Ginny Weasley's performance as a Seeker, and watching Potter and the Weasley twins try to conceal their bitter disappointment at not being able to play, that and the spectacular unity and involvement of the Slytherin stands in their drive to knock Gryffindor out of competition.

Louder than the stands of either of the two competing houses, the Slytherins set up a constant roar of `Weasley is our King,' clearly flustering the Gryffindor Keeper, who missed save after save. The new Gryffindor beaters were more of a comedy team than Quidditch players, and the only reason Gryffindor didn't lose by 390 to 80 was Ginny's near miraculous capture of the Snitch, making the score a more respectable 240 to 230. Slytherin was now favored to win the Quidditch Cup. Snape tactfully stayed away from McGonagall for the rest of the afternoon, and didn't mention the word `Quidditch' once at supper.

That evening at Croydon started out normally. Snape spent most of the time in his laboratory, a little disappointed that his training sessions with Phina were now over. \emph{Maybe I should have done something more to show Bella I was interested in her cousin. Maybe her assignment could have be lengthened.}

Snape also paid a couple of visits to the staff lounge, just to see who was there. He was almost hoping to see Peter Pettigrew, thinking that he could start an acquaintance that would eventually allow him to get information about Dumbledore and the Fidelius Charm, or about the Dark Lord's actions just before the death of the Potters, but headquarters was remarkably quiet, and there were few people in the halls, none in the lounge.

Just as Snape was about to leave, that changed. Without warning, the mark on his arm began to sting fiercely. Snape locked the last of his cabinets, shut up the laboratory, and hurried to the interview room. Death Eaters were coming in the main entrance, having apparated from all over the southern district, offices were emptying and soon several dozen people were gathered in the interview room, Bella and Rodolphus Lestrange prominent among them, looking decidedly worried. Malfoy was there, too, his cold face unreadable.

The Dark Lord appeared.

"You will explain how it is that you have misled me."

Bella spoke. "My Lord, we got you inside. It was more than anyone before us was able to accomplish."

"It was not what was promised. Malfoy, you will speak."

"Lord, this is why we must continue to use employees of the Ministry, and the potions of deceit that my staff provide. Only select functionaries of the Ministry know their way around the Department of Mysteries. If we go blundering in without knowing where we're going, we'll be detected, maybe even apprehended."

The Dark Lord turned his crimson gaze on Bella again.

Knowing herself to be under attack, Bella began to look for someone to blame. "Lord, I believe that a great part of our problem was the ineptitude of those who worked on this task before us. They not only failed, they alerted the Ministry to our attempts and made them more alert to our presence."

"Avery," was all that the Dark Lord said.

Snape felt sorry for Avery as his old school colleague stepped forward. \emph{I guess this raid was the reason he was pulled in from Lincoln last Monday. Tough luck if Bella sacrifices him on the altar of her ambition.}

"Lord, we haven't alerted the Ministry. The Ministry still doesn't believe we exist. The only ones who have any idea of our attempts to enter the Department of Mysteries are Dumbledore's people, and they have to use spells of concealment so that the Ministry doesn't know they're there. But if we go in fighting instead of by stealth, and leave unconscious or dead wizards for the Ministry to find the next day, they will know we're there, and we'll be further from our goal than ever."

\emph{Unconscious or dead wizards? Was someone injured tonight? Someone I know?}

"Snape. Tell us of Dumbledore's people."

Stepping forward diffidently, Snape tried to look at neither Bella nor Malfoy. "Lord, the Order's watch on the Department of Mysteries is a routine that they established after the incident with Arthur Weasley in December. One of them is on guard each night. They've become a bit lax about it since nothing has been happening, or at least they had. If I understand correctly, after tonight they'll redouble their watch."

The Dark Lord turned to Bella. "This concerns me, as well. Not only have you failed in your mission, Dumbledore is once again aware of our attempts and will increase his precautions. What has been done with the one we disposed of?"

"We wiped his memory and took him to Devon. We left him bound on the moors. It'll be days before he's found." Bella seemed disappointed that it wasn't worse, but Snape feared the bitter cold of a February night.

"Is this true?" The Dark Lord fixed his gaze on Snape.

"No, Lord. The instant they realize he's not at his post, they'll search for him. Dumbledore can locate any of his people in minutes if he really wants to. They'll recognize the memory spell and know where he was attacked."

"Then he must be killed and his body disposed of."

"I'll go myself," said Bella.

"No, I want you here. Send an operative."

"It will take me only a few minutes to explain where he can be found."

"Good." The Dark Lord turned to the assembled Death Eaters. "If any of you has information that will assist in this task, you will not keep it from us. If any of you conceives of a plan, however poor its chances of success might seem, you will bring it to us at once. You may now go, excepting the Lestranges, Malfoy, and Avery. And you as well Snape, in case we have questions about charms or potions."

"Let me first show my agent where to find Dumbledore's man," Bella asked.

"Lord," Snape said quietly, "may I also go to lock things away in the laboratory. I left there hurriedly at your summons. It would only take five minutes."

"Go, both of you," the Dark Lord replied. "Return quickly."

Snape rushed to the lab. Nothing needed locking down, but now he had a moment alone. He couldn't apparate through the defenses of headquarters or of Hogwarts, but neither of them would stop a patronus. In all his years in the service of the Dark Lord, Snape had never heard anyone allude to using a patronus as a messenger, or of using a patronus at all. He prayed that the idea was so alien to the organization that even if seen, his fox would not be recognized.

Throwing open a window, Snape concentrated. \emph{The one on guard tonight was attacked. They've bound and left him on the Devon moors, but are going now to kill him. You must work fast.} Then silvery Renard sped north on the wings of thought, while Snape rushed back for the Dark Lord's meeting.

In the corridor outside the interview chamber, Snape passed Bella and a tall blond Death Eater. They were walking slowly towards the main entrance where he could apparate once he was outside, Bella still filling him in on the location in Devon.

The meeting was brief, there being no new ideas to review that night. The five of them were put on call, with allowances made for Snape's schedule at Hogwarts. Before they broke up, however, the blond Death Eater returned with bad news. The quarry had escaped. Dumbledore, it seemed, had gotten there first.

Dumbledore didn't speak to Snape that night, nor all Sunday morning, but after lunch he once again brought out the chess board and set it up at the staff table in the Great Hall. By now fully aware of the abysmal level of play, the other teachers left them alone.

\emph{Who was it?}

\emph{Shacklebolt. Good that you got to us. He narrowly avoided frostbite.}

\emph{Did you go?}

\emph{No. Tonks, Lupin, and Moody. Moody found him. Enchanted eyes are a godsend on a moonless night. How did it happen?} For the benefit of the people in the Hall, Dumbledore said, "I'll have your knight in two moves."

\emph{Bella persuaded the Dark Lord to attack the door directly. They disabled Shacklebolt and actually got inside. They found themselves in a room with multiple doors that kept shifting, so the Dark Lord is hardly any closer to what he wants. He's furious, and everyone is walking around like there was broken glass underfoot. He's obsessed. He thinks about it all the time. He has to get that prophecy.}

\emph{How are Harry's lessons going?}

\emph{Useless. Worse than useless. He can't block the smallest probe. He always tries to fight back with spells, which leaves him open all the time. He won't do any exercises, though he lies and says he does. I'm beginning to think that he resents me so much that he's inviting contact with the Dark Lord just to spite me.} "There, no knight for you. Look out for your bishop."

\emph{That is distressing. Do you know the source of this resentment?}

\emph{It seems to have worsened from mild dislike ever since he came into contact with Black. Sometimes when he looks at me, it's like Black looking at me. The same tightness around the eyes, the same backward tilt of the head, the same way he lifts the side of his mouth{\el}}

\emph{We can only keep trying.}

Monday morning brought catastrophe. Owls began inundating Potter with letters, attracting the attention of Umbridge. And then the Quibbler arrived. A few students got the scandal sheet regularly, but this time Miss Lovegood brought a few extra copies. She gave one to Flitwick, and the teachers gathered around. Snape listened for only a few seconds, and was horrified by what he heard.

Potter had given the Quibbler an interview about the return of the Dark Lord, naming the names of Death Eaters. Malfoy was mentioned, as were Crabbe, Goyle, Nott, Avery, Pettigrew, and Macnair. \emph{I hope the Quibbler has good security. The entire editorial staff are now targets.}

By ten o'clock, Educational Decree Number Twenty-seven threatened any student found with a copy of the Quibbler with expulsion, thereby guaranteeing that every student in school would want to read it.

And the owls and letters kept coming.

It was no surprise to Snape that his arm started aching during his first afternoon class. It was a `come tonight' summons, so he caught Dumbledore's eye at supper and flashed a mental message to him. `Good luck' was the silent response.

Once again Snape was on his knees before the Dark Lord, a triumphant Bella now smirking down at him, and Malfoy not allowed in the chamber. Once again subtle pain danced at the corners of his mind, warning of punishment to come if his answers didn't satisfy.

"Potter's actions are part of your assignment. This interview undermines all our efforts at secrecy. Yet you allowed it."

"Lord, it happened outside Hogwarts. The students had an excursion to Hogsmeade. I was not assigned supervisory duties for the excursion."

"Why did you not go anyway?"

"First and second years remain in the castle. Those who don't go to Hogsmeade supervise them." Snape gasped as fire flickered along his spine.

"You hide your failure behind excuses."

Bella smiled. "Macnair wants you all to himself for about five hours. Shall we indulge him?"

There was silence in the chamber as Snape closed his eyes and simply waited. The Dark Lord spoke again.

"You should be punished."

"Yes, Lord."

"Macnair will be given this happy task."

"Yes, Lord."

"If there is any good news to be gleaned from your failure, you will tell us now."

"The Umbridge woman still believes Potter is lying. She's published Decree Twenty-seven. Any student holding a copy of the Quibbler will be expelled."

"This is better. So all is not yet lost. Tell me, Potions Master, can you guarantee that the woman will continue to believe as we wish her to believe?"

"Yes, Lord."

"You speak quickly. Surely you know that you wager high stakes in this game - Macnair is hungry. Bella{\el}"

"Yes, Lord."

"Do you trust that this miserable servant will perform the task he has been given?"

"With the proper oversight, Lord, I do."

"Then he is yours. If he repeats his pitiful failure, you may punish him as you see fit."

"Thank you, Lord," but the Dark Lord was already gone. Bella looked down at Snape, gloating. "You see, puppy dog? I always get what I want. You may stand up now."

Snape rose slowly, his knees stiff from their long contact with the stone floor. Bella twitched a finger, and Snape fell in behind her as she left the chamber. Macnair was waiting in the corridor, and Snape had the distinct impression he was salivating. Bella flirted her way over to him.

"Sorry, Walden," she cooed, "no toys today. I get to play first. Keep your knives sharpened, though. You never know{\el}"

Beckoning again, Bella led Snape to her own office on the second floor. "Sit down, Cursemaster," she said, pointing to a chair. "We're going to talk."

Snape sat while Bella perched on the edge of a large, wide desk. "Let's make sure we understand each other," she said. "You used to help Malfoy, but you screwed up. You didn't keep your eyes on all your little chickens, and one got away from you. Now Malfoy's star is falling, while mine is rising, and I get rewarded with all kinds of perquisites, one of which is you. And to think I wasted Phina's talents on you when you were just ripe for plucking . By the way, didn't you like Phina?"

"She was very attractive."

"But not your type. What is your type, puppy dog? Not me, surely? What about Narcissa? Or maybe Lucius? Is that why the two of you are suddenly so devoted?"

"You know better."

"Do I? You're the subject of quite a bit of gossip, you know. I keep telling them you're like a priest, serving a cause higher than yourself, but most of them think it's just a matter of finding out which way you swing. Macnair even hopes you secretly enjoy being punished. It's his fondest dream."

"I thought we were supposed to be talking about business."

"You are my business, puppy dog. When I say `heel,' you jump to my side. Understand?"

"Yes, ma'am."

Rodolphus stuck his head in. "Having fun, I see. Well, you're just going to have to play later, so pack your toy back to Hogwarts and help me, sweetheart. I need a briefing. I've got a day to learn the ropes up in Manchester, and then Augustus is coming down here."

Bella grinned at Snape. "You know your job. Get back up there and do it, or I may find answers to some of my questions sooner than you'd like."

Snape left quickly, though Rodolphus managed to snag him for a moment in the corridor. "She does love to get her claws into someone, doesn't she? So much better you than me."

Seldom had Snape been so relieved to be back at Hogwarts.

Umbridge had her spy antennae up again, so Dumbledore thought it best to continue to play chess. It was much less suspicious than meeting in either office or going out of the castle for a private stroll. Unfortunately, chess needed time, and on a Tuesday they only had time after supper.

\emph{I was pleased you made it back in one piece.}

\emph{It was touch and go. Seriously. Macnair was drooling. Now I'm on probation, and I belong to Bella Lestrange.}

\emph{You have my sympathy. What is it that you are supposed to do to avoid being chopped into little pieces?} "Ah, Professor Snape, once again your knight is in jeopardy."

"I see it, Headmaster." \emph{I have to make Umbridge believe that Potter is a liar.}

\emph{Not a difficult task. I was afraid it would be much harder.}

\emph{There's more. They're bringing Rookwood in from Manchester today. Something so important that Bella is losing Rodolphus to it. Dolph has to baby-sit Manchester for awhile. She is going to be so antsy.} "Watch your queen-side rook, Headmaster. I'm castle hunting."

Dumbledore pondered his next move. \emph{That is disturbing news. You are probably not aware, but in the time before he went to Azkaban, Rookwood worked for the Ministry{\el} in the Department of Mysteries. We need to know what he tells Riddle. When do you go back next?}

\emph{Not until Saturday, unless I'm called.}

\emph{We must be contented with that, I suppose.} "Check."

Snape found abundant opportunities during the next few days to malign Potter's credibility to Umbridge. The Lady, now totally isolated from the rest of the faculty, hung onto Snape's apparent support like a drowning swimmer.

After a day, Snape noticed he was being observed with some respect by Malfoy, Crabbe, Goyle, and Theodore Nott. Lucius must have told them that I'm working at the Dark Lord's express orders. Looks like he doesn't hold it against me that I've been captured by the Black Queen, or the boys wouldn't be so respectful.

Saturday revealed that the organization had been shaken up again. Rookwood was back in Manchester, Rodolphus was back in London, Avery was in disgrace at headquarters, while Yaxley took over Lincoln. Everyone who'd backed Avery was trying to look inconspicuous, and Malfoy was backtracking and flattering Bella shamefully.

Phina sashayed into Snape's laboratory shortly after he arrived. "Cousin Bella is upset that you didn't go report to her first," she said, then grinned wickedly as Snape hurried out of the laboratory and up the stairs, Phina right behind him.

Bella was pacing her office as Snape rushed in. "It's about time you remembered who was important in your life," she snapped. "What's happening at Hogwarts? Does Umbridge still dance to our tune?"

Snape reported that that was, indeed, the case, at which point Bella seemed to lose interest. "Go back to your beakers and test tubes. Next time remember where you go first."

"Yes, ma'am."

He returned to the laboratory, Phina in tow. She sat quietly in a corner, watching his every move like a hawk, but Snape didn't have the courage at that point to tell her to leave, even though her presence hampered his movements. When it was time for him to go, she blocked the doorway. "No lessons tonight, Professor? Maybe Cousin Bella is right. Maybe I should be jealous of Macnair."

The following Saturday was more of the same. Snape went first to report to Bella, then down to his laboratory where he found a leather-clad Phina swinging a riding crop. "I thought I'd take on Macnair on his own ground," she sneered.

"It's bad enough having Bella torment me, I don't need you, too!"

She smiled. "You mean Mommy's little boy doesn't like being spanked?"

"I hate being spanked!"

"I'm so glad to hear that, because I'm just not the spanking type." She walked over to him, put her arms around his neck, and kissed him, and it was so wonderful to have something even a little bit normal happening in his life at that moment, that Snape kissed her back, willing to do anything she wanted just to keep her there to chase the image of Bella away.

Phina leaned away from him, satisfaction shining in her face. "Take me to dinner?" she said.

It was the best offer Snape 'd had in nearly a month. \emph{Anything to get out of here!}

"I don't know," he said. "How do you feel about garlic?"

"I suppose if we both eat it, it won't matter. Why? Do you have a place in mind?"

"I don't know if it's still there, but around ten years ago I went to this nice Greek place near the Tottenham Court Road tube station{\el}"

"Sounds great. Can I wear this?"

"Only if you want them to call the police."

Phina settled for a long skirt with a peasant style blouse and dangling earrings. Both donned warm coats, checked out with personnel, and apparated to an alley near the tube station. From there it was a short walk to Percy Street and a cozy looking restaurant with an orange and blue marquee. Tables were set on the sidewalk despite the cold, but Snape and Phina went inside.

A small flick of a wand put Snape's name on the reservation list, so they got a table at once. The back of the restaurant was wider than the front, and they sat in the corner where the wide section met the narrower front, shielded from the windows and the door by the jog in the wall.

"So teach me, Potions Master. How does one eat Greek food?"

"The best way is to start with the appetizers, the \emph{mezedes}. A lot of them are like spreads or dips that you eat with pita bread." The restaurant had a mixed plate of \emph{taramosalata}, \emph{houmous}, \emph{tzatziki}, and feta cheese, which Snape suggested as a good introduction to Greek food.

"So what are they?" Phina demanded, but Snape refused to tell her until after she tried them.

"This one is my favorite," Phina declared after trying them all several times. She was pointing to the \emph{houmous}.

"Pureed chickpeas with sesame seed butter and lemon juice. That one is fish eggs, that's yogurt with cucumber and mint, and that's goat cheese. And they just about all have garlic."

Any prejudice Phina had ever had about garlic seemed to be disappearing. She loved the chopped lamb cooked in grapevine leaves and the seafood pilaf, fascinated when Snape told her the rings of slightly chewy meat were squid.

"Why did you come here ten years ago?"

"I got to know London during the Dark Lord's first reign, but after his fall I had to stay at Hogwarts. I hate Hogwarts. So after awhile, on my free evenings I used to come down to London to eat at a restaurant and take in a play. It made me feel a little bit less like I was in prison."

"I didn't know Hogwarts was so bad."

"I suppose just as a place, it isn't. But it wasn't what I wanted to do with my life. And anytime you're forced to stay in a place, you hate it."

"What did you want to do with your life?"

"More like what I'm doing now. Work in a laboratory."

"Why didn't you just leave?"

Fortunately for Snape, the floor show started just then, so Phina's attention was diverted by the Greek dancers. She swayed and clapped to the music, then played an amusing game of trying to keep Snape from looking at the belly dancer.

By the end of the show, they were relaxing over baklava and coffee, talking about the school in France that Phina had attended. They even managed to extend the evening with glasses of amaretto, but by then they both had to admit that it was time to be returning to Croydon. Phina took Snape's arm as they returned to the alley near the tube station and disapparated.

Bella was there almost as soon as the two arrived. "Where have you been," she asked curtly.

"Out," Snape replied, and Phina giggled.

Bella just nodded. Snape didn't need legilimency to deduce from the glint in her eyes that Bella was mentally removing Lucius Malfoy's name from the list of possible rivals. Macnair's, too. "I hope you had a good time," was all she said, and then she went back upstairs.

Snape left Phina at headquarters and apparated back to Hogwarts.

\sbreak

\emph{He was in the interview chamber, staring down at Rookwood kneeling before him{\el}}

\emph{I have been badly advised, it seems.}

\emph{Master, I crave your pardon{\el}}

\emph{I do not blame you, Rookwood. You are sure of your facts?}

\emph{Yes, my Lord, yes{\el} I used to work in the Department after - after all{\el}}

\emph{Avery told me Bode would be able to remove it.}

\emph{Bode could never have taken it, Master{\el} Bode would have known he could not{\el} Undoubtedly that is why he fought so hard against Malfoy's Imperius Curse{\el}}

\emph{Stand up, Rookwood.}

Snape was fighting now, fighting against the vision, fighting against the memory, suddenly locked into something that he didn't want to see, that terrified him.

\emph{I shall need your help. I shall need all the information you can give me.}

\emph{Of course, my Lord, of course{\el} anything{\el}}

\emph{Very well{\el} you may go. Send Avery to me{\el}}

The link was broken, and Snape staggered back, breathing hard. As he stared down at the boy kneeling on the office floor, so similar to the man kneeling in the memory, Snape realized he was shaking. Swallowing quickly he said, "Get up, Potter. That last memory. What was it?" Of course, Snape knew what it was. He needed to find out if Potter knew.

Potter pushed himself to his feet. "I don't know. You mean the one where my cousin tried to make me stand in the toilet?"

"No. I mean the one concerning a man kneeling in the middle of a darkened room{\el}" \emph{A familiar room. A room where I have knelt too many times. Have you seen me kneeling there, Potter?}

"It's{\el} nothing."

Snape tried to read the boy, but Potter was avoiding eye contact. "How do that man and that room come to be inside your head, Potter?"

"It{\el} it was{\el} just a dream I had."

"A dream." \emph{A dream where you enter the Dark Lord's head and look out from his eyes. And when the Dark Lord sleeps, does he dream through your eyes? Is he dreaming of me teaching you occlumency right now?} "You do know why we are here, don't you, Potter? You do know why I am giving up my evenings to this tedious job?" \emph{Not so you can betray me to the Dark Lord on a daily basis.}

"Yes." The hard edge of Potter's defiance shone through his apparent obedience.

"Remind me why we are here, Potter."

"So I can learn occlumency." The green eyes looked everywhere except at Snape. \emph{Is this how Dumbledore used to see me?}

"Correct, Potter. And dim though you may be, I would have thought that after two months' worth of lessons you might have made some progress." Potter was looking at him now, hatred in his eyes. "How many other dreams about the Dark Lord have you had?"

"Just that one."

\emph{Liar. Right now I don't care whether or not you get yourself killed, but I'll be damned if you take me with you.}

"Perhaps you actually enjoy having these visions and dreams, Potter. Maybe they make you feel special - important?"

"No, they don't." Yet the boy's body language belied his words.

"That is just as well, Potter, because you are neither special nor important, and it is not up to you to find out what the Dark Lord is saying to his Death Eaters."

"No," Potter spat back at him, "that's your job, isn't it?"

\emph{You have no clue, do you? You hate me for seeing the images that you broadcast freely, but you have no idea what it's like to have your mind ripped open by brute force. You have no idea what other people are enduring for your sake. Bode dead, Podmore in Azkaban, Weasley lying poisoned in a hospital, Shacklebolt freezing on the Devon moors, all to keep your miserable little self safe. All to keep the Dark Lord from finding a prophecy that could destroy you. What I wouldn't give to be looking into your eyes the moment you realize how many people suffered for you, you ungrateful little piece of{\el}}

"Yes, Potter. That is my job." \emph{And I do my job. As Weasley does his, and Shacklebolt does his, and Dumbledore does his.} "Now, if you are ready, we will start again{\el} One{\el} two{\el} three{\el} \emph{Legilimens!}"

Dementors. All the boy saw were dementors coming closer. It was not what Snape wanted to see, and he tried to change the image, reminding Potter of Dursley, and of the Chang girl. It did no good. It was as if Potter controlled the dementors. Snape had his own memories of dementors and now, as he stared into Lily's eyes, he felt Potter's images and his images merging, joining, opening the doors that he fought to keep closed, opening them to the green eyes{\el}

"\emph{Protego!"} Potter screamed, and the shock wave of the spell hit Snape and flung him back so powerfully that he nearly lost his footing on the stone floor. His wand hand swung upward to flail for balance, and he staggered back against the shelf where the pensieve lay holding his thoughts.

Then Snape felt his own memories drawn up and out from the locked down areas - his parents fighting, always fighting{\el} scenes of cruelty and humiliation from other children{\el} himself, sinking into deep depression after the death of his parents{\el} a vial of slug juice{\el} "ENOUGH!" and Snape's own nonverbal shield struck out, knocking Potter backwards into shelves of jars and bottles, breaking one.

The Reparo spell was instinctive in a potions master, and as the broken jar repaired itself, Snape realized first that Potter was pale and trembling, and then that he himself was as well. He turned now to the pensieve, to straighten it.

"Well, Potter{\el} that was certainly an improvement{\el} I don't remember telling you to use a Shield Charm{\el} but there is no doubt that it was effective{\el}" Over and above the distaste he felt at knowing that Potter had seen thoughts he had always managed to keep private, Snape was cognizant of two immensely important things. The first was that Potter had actually begun to resist him mentally. Not with the Protego spell, but before that, when he refused to show images of Dursley or of Chang. The second was that Potter had read him, used legilimency. It was no simple surface contact - what had been on the surface was dementors. No, this probe had reached deep, and Snape was fairly certain that Potter was not aware of what he'd done.

"Let's try again, shall we?" They took their now familiar positions, the boy clearly more nervous than usual. "On the count of three, then. One{\el} two{\el} three{\el} \emph{Legilimens!}"

It was one of Potter's dreams. They were in a corridor Snape did not recognize, speeding past torchlit stone walls toward a black door{\el} light beckoned through the partly open door{\el} and then - Snape dropped his wand, struggling desperately now to break the contact. He knew Potter's mind, had been touching Potter's mind weekly for two months now, and this was not Potter's mind!

He was inside the Dark Lord's mind as the Dark Lord reviewed his own memory of a day two and a half weeks earlier. This was the Department of Mysteries. These were the doors that blocked him from his goal. He had a plan, and that plan involved Potter. And so he reached out now to Potter's mind, to lure him, to entice him{\el} to intrigue him with the puzzle of the doors{\el} to touch the mind that touched Potter's mind{\el}

In blind panic, Snape struck Potter, knocking him to the ground, and wrenched himself away from the link. Staggering backwards, he banged into the work counter and fell to the floor on his hands and knees. Potter lay, apparently unconscious, on the other side of the room.

\emph{Dear God, did he see me? Did he look through Potter right into me and recognize who he was looking at? Am I a dead man from this moment?} Minutes passed, and no summons blazed on his left arm. Slowly Snape's heartbeat and breathing returned to normal.

Snape pulled himself to his feet and went to check Potter. The boy lay on his back and, despite the fact that he was breathing heavily, seemed to be all right. "Potter?" Snape said quietly. There was no response. "Potter. Potter! POTTER!"

Potter opened his eyes, gazing around the room in bewilderment.

"Explain yourself!"

"I{\el} dunno what happened. I've never seen that before. I mean, I told you, I've dreamed about the door{\el} but it's never opened before{\el}"

\emph{Fool. Fool. He's reaching right past every shield and defense Hogwarts has, right into the midst of us, and you're too precious to try to do anything about it.} "You are not working hard enough! You are lazy and sloppy, Potter, it is small wonder that the Dark Lord{\el}"

Potter's held tilted up and back, the way Black's always did just before an attack. "Can you tell me something, sir? Why do you call Voldemort the Dark Lord, I've only ever Death Eaters call him that{\el}"

Snape gritted his teeth against the stab of pain and then{\el}

A woman screamed outside, from above, from the entrance hall. "What the{\el}?" Snape murmured, listening as other sounds mingled with and replaced the voice. He glanced over at Potter. "Did you see anything unusual on your way down here, Potter?"

Potter shook his head just as another scream pierced through the stone. Snape was out the door in an instant. If something was wrong in the castle, the teachers were needed.

The entrance hall was filling rapidly. Students poured out from the ground floor classrooms where they'd been studying, from the Great Hall where some were finishing supper, from the floors above. Pushing his way through a crowd of Slytherins blocking the dungeon stairs, Snape took in the trunks, the hysterical Trelawney, and the dumpy, smirking figure of Umbridge on the marble staircase and headed for the great oak doors. He had to call Dumbledore, but he couldn't do it where everyone could see.

As it turned out there was no need, for Dumbledore already knew. Snape burst through the doors into the night, where the bright disk of the moon, just past the full, had already risen above the hilly horizon. Its light illumined the lawn, the path up the hill, and the tall figure of Dumbledore striding towards the castle. He was coming from the forest, a fact made obvious by the creature that was following him.

The palomino body and pale blond hair of the centaur shone like gold in the moonlight, but Snape was far more concerned about the powerful hooves that cut into the path with every mighty step. He scooted out of the way of the pair, over to the side and well out of striking distance, the only disadvantage being that he could no longer hear what was happening inside.

\emph{She can't sack Trelawney. Dumbledore has to do something. She can't send Trelawney away. The instant Trelawney walks off these grounds, she's easy prey for the Dark Lord. He wants the prophecy. There are three ways to get the prophecy, and he's trying to break into the Department of Mysteries because he can't touch the other two. But if Trelawney leaves, the Dark Lord doesn't have to break into the Department of Mysteries. All he has to do is break into Trelawney's mind.}

The door into the entrance hall was open, but blocked by the great bulk of the centaur. Snape strained to understand the threads of conversation that filtered out to him. Then it was over, and the crowd in the entrance hall began to drift away. The centaur entered the castle, leaving the doors now free to pass. Snape slipped inside.

Dumbledore was ushering the centaur to the corridor of classrooms on the left that were mostly used as study rooms. Umbridge was stomping up the marble stairs, steaming with rage. Potter was standing by the dungeon stairs, watching the centaur go by, a look of great joy and wonder on his face{\el}

\emph{Potter! I have to talk to Dumbledore about Potter.} Snape walked swiftly across the hall and down the kitchen corridor to the rear staircase. He took the steps two at a time up to the floor where the gargoyle statue was, there to wait until Dumbledore returned, trying to sort out everything that had happened in this very confusing evening.

\sbreak

Snape stood in front of the fire in Dumbledore's office, staring down at his hands. They'd been arguing for half an hour, and Snape felt drained, exhausted, fear and helplessness swirling through his brain like malevolent harpies, prodding, goading, laughing.

Dumbledore came over and laid a hand on his shoulder. "I wish the situation were different," he said gently. "Have you thought of any plans?"

"Yes. Nail the two of clubs to a tree and blow my brains out."

"I would like to hope that things are not that bad."

"If he saw me, they're worse. And you want to keep me where he'll continue to see me. Isn't there anyone else? Someone who doesn't have to walk into his lair every week? Someone who can stay safe at Hogwarts?" \emph{Someone like you?}

"We cannot help it, Severus. The situation exists, and we must deal with it as best we may. Harry must learn occlumency. The bitter truth is, only you can teach it to him."

"He won't learn from me. He refuses."

"He has already learned. He started to block you out today."

"It isn't fast enough or complete enough. The Dark Lord will find me. He may already have found me."

"You have not been summoned."

"Suppose it's a trap, that he's luring me in with a false sense of security, so I'll walk into headquarters unsuspecting on Saturday? Then it'll be too late."

They stood there for awhile, watching the fire as Snape ran scenario after scenario through his head, but none was a solution. It was growing late, so he took his leave and went to his own rooms to go to bed. But not to sleep.

"Y're off yer feed again."

"I'm not hungry, Hagrid. What do you keep doing to your face?"

"'T ain't nothing important. But you got to keep yer strength up. I ain't seen ya so thin since ya was a first year. Have some kipper. Ya always liked kippers."

"I'll tell you what, Hagrid. You stop getting your face all beaten up - then I'll think about eating more." But this was Saturday, and anything as normal as eating was impossible.

Wanting to be alone, Snape returned to his own rooms. For some reason he felt a compulsion to straighten and clean everything. He noted that supplies of powdered lichen and dried marula fruit were running low, and left a note on his desk that they would have to be ordered before the first of May. Another note advised that the potions the fifth years were working on needed to be stirred three times clockwise on Sunday, or they would not be in fit condition to use Monday morning.

Skipping lunch entirely, Snape began drawing up outlines of the material that needed to be covered before the OWLs and NEWTs in June. A separate piece of parchment contained the numbers of a vault at Gringotts and an account at Barclay's. It was only after he noted down that the dark items from his great-grandfather's collection should go to Hogwarts school that Snape fully realized what he was doing.

As he left his office for supper, Snape locked the doors with the set of keys Dumbledore had given him almost fifteen years earlier instead of using the magical locks he'd devised himself. Then he went to supper, where he toyed with a small plate of food while listening politely to Flitwick telling him how poor Sibyll Trelawney was still weeping over her fate three days after being sacked, and to McGonagall about how the weather was making her miserable with her aching bones, and to Sprout about the wilt that was attacking the early sprouting heart's-ease and feverfew.

When Dumbledore left the Hall, Snape rose and followed. "Headmaster," he called softly in the entrance hall. Dumbledore stopped and waited for him. "I thought I would leave a little earlier than usual, if you don't mind opening the shields for me now." Then Snape extended his right hand.

"Of course not," said Dumbledore, looking puzzled and worried as he took the proffered hand. He looked into Snape's eyes, but Snape had shut down, and there was nothing for Dumbledore to see. When their hands separated, Dumbledore was holding the set of keys.

Snape turned and walked through the doors, down the hill, and into Hogsmeade, where he disapparated.

\sbreak

Snape apparated into Croydon several streets away from headquarters and made his way through lines of cars and groups of pedestrians, his pace slowing noticeably the nearer he approached. \emph{Why can't I just walk in as if nothing were wrong? Look at me. My skin is clammy, my mouth is dry, my stomach is tied into knots I never knew existed{\el} This is my punishment for calling Sirius Black a coward{\el}}

A turn to the right, and there it was. The door to headquarters, a short block away. \emph{This is it. There is no other route to take. Whatever lies on the other side of that door must be faced and dealt with. Fear must under no circumstances be allowed to hinder action. I've been hammering into Potter for two months that emotions must be controlled. Practice what you preach, Severus.} Straightening his back, his head high, Snape walked up to the door, raised the latch, and entered.

Three steps into the building and they seized him, Rodolphus on one side and Macnair on the other. "Good boy, showing up early. Dark Lord wants to see you," and they hustled him down the stairs and along the corridor to the interview chamber. Bella was already there, as was Malfoy, as was the Dark Lord.

"He comes? this servant who serves me not," hissed the Dark Lord. "Your memory grows dim. We must refresh it for you. You will kneel."

Even before his knees settled on the floor, the Cruciatus Curse hit. Snape's body arched backward, and then he had no body, only pain that radiated into every corner of his being, obliterating everything else except the echo of screaming{\el}

And then the pain was gone. It had lasted, Snape reckoned as he lay very still on the cold stone floor, but a few seconds. This was not punishment, only a reminder. A rough hand gripped his left shoulder and turned him onto his stomach, so he could push himself back onto his knees. \emph{Angry, but not murderously angry. Steady. Find out what's wrong.}

"What are your tasks, faithless one?"

"To provide your people with potions and charms, and to teach them to defend themselves against enemies."

"And what else?"

"To bring you information about Dumbledore and his followers."

"And what else?"

"To persuade Dolores Umbridge and the Ministry that reports of your return are false, so that we may operate in secrecy."

"And what else?"

Snape was thinking feverishly now. What else had the Dark Lord ever commanded him to do, even if it was not given as a formal task?

"To report on the dreams of Harry Potter."

"What do you know of the dreams of Harry Potter?"

\emph{This is it. He knows.} "He dreams of snakes, and of the Department of Mysteries."

"What has he seen of the Department of Mysteries?"

"A door."

"Has he gone through that door?"

"Yes, and found many other doors."

"Does Potter confide his dreams to you?"

Snape walked through a minefield, and he knew it. A wrong step meant, not death, not yet, but the end of life. "No, Lord, he does not."

"Then how do you know?"

"He confides in Dumbledore, who speaks to{\el} McGonagall." \emph{Who never leaves Hogwarts and is therefore not an easy target.} "She lets things slip from time to time."

"And it did not occur to you that we might want this information at once."

There. That was the transgression. Relief flooded through Snape, while he struggled to turn it into a semblance of misery. Covering his face with his hands he said, "I have failed you, Lord. Punish me."

"That will come. Tell us why Potter does not enter the dream."

Snape was baffled and made no effort to hide it. "Lord, I do not understand."

"We wish him to enter the dream, to seek the prize, to choose a door. He merely watches."

"Forgive my ignorance, Lord, but how can one do more with a dream unless he seeks the real door? And nothing will induce him to leave Hogwarts."

"We are better informed. You will all leave now, except Lucius who will consult with us. Macnair, you will spend a few minutes - a very few minutes - impressing upon this servant why his reports must be timely."

Malfoy flashed a quick smirk of triumph at Bella, and then the four of them - Bella, Rodolphus, Macnair, and Snape - were back in the basement corridor. A door was ajar to a vacant room just ahead, and the three shoved Snape unceremoniously into it.

"I guaranteed your performance to the Dark Lord, puppy dog, and you made me look bad. This doesn't stimulate my maternal instincts." Bella's wand was in her hand.

Snape let his own wand slip from sleeve to hand as well, but Macnair stepped between them with a wicked grin. "Don't forget the Dark Lord, Snape. He gave me a few minutes with you, and if you fight me, you disobey him."

"He didn't give Bella anything."

"Why, Bella, I believe he's right. You'll just have to step outside." The Lestranges retreated and shut the door behind them.

"Don't worry," Macnair chuckled as he took the wand from Snape's now unresisting hand. "I won't do anything fatal - or even permanent. Just give you more to think about for say, a week. Besides, I watched you last June. You thrive on danger. Pain makes you feel more alive. No reason why we can't both enjoy this." He seized Snape's wrist, twisted his arm behind him, and pushed him into the wall. "You do understand that the Dark Lord's business overrides everything else? Say `sir.'"

"Yes, sir."

"And you will bring him every tidbit of information as quickly as you can, not caring about your own safety or convenience?"

"Yes, sir."

"Now for the reminder." The tip of the wand ran slowly down Snape's side. "Something you don't use often. Something you won't really need{\el}" The wand stopped as Macnair whispered \emph{"Ignis - Renes Dextimus!"}

Fire seared the middle of Snape's back, and he cried out once before he slumped to the floor. Macnair tossed his wand beside him. The pain was already subsiding to a sharp ache.

"Don't worry," Macnair said. "You'll notice it for about a week. That should be enough to impress the lesson on your mind. After that you'll be fine. You don't really need more than one kidney anyway." Then he was gone, and Snape was alone in the room. Slowly, gingerly, he got to his feet.

\emph{Fine. The Dark Lord is pissed, and now his sadistic chief executioner is in love with me. Well Dumbledore is going to hear about this. I want a new job. Or at least a raise in pay.}

\sbreak

Dumbledore tapped a finger thoughtfully on the arm of his chair as he watched Madam Pomfrey examine Snape's back. "Have you ever considered the possibility that Macnair may be right," he said after a while.

"Don't you start in on me! I'm getting just a little tired of all this insinuation that I might be sick and twisted!"

"Now, do not get defensive. You do not exactly lead a normative life. And you do have a{\el} tolerance for unpleasant situations exceeding that of any other person of my acquaintance."

"That's because you put me into more unpleasant situations than you do any other person of your acquaintance."

"Only because I know you can tolerate it."

Madam Pomfrey cleared her throat. "He's right about the damage. There isn't much I can do outside of pain killers. It will continue to hurt for about a week, then it will clear up. There's no permanent damage to the kidney. Shall I get you something for the pain?"

"No, that's all right. I can{\el}" Snape stopped and glared at Dumbledore. "On second thought, Madam Pomfrey, I would love something for the pain. I hate pain."

"Here then," she replied, handing him some lozenges. "Two every four hours. And you{\el}" - this was to Dumbledore - "try not to damage him anymore. At least not for a while. I do have other things to attend to."

"Yes, Madam Pomfrey. Of course." The two men waited until the nurse was out of the room. Dumbledore poured mead.

"I am serious, Severus. You have an attitude toward pain that is positively unique in my experience. You neither embrace it nor flee it. You seem to view it as a natural and unavoidable part of existence, to be dealt with on a practical level. And there are times, I swear, when it seems that you regard suffering as a kind of validation. It is no wonder that someone as unsubtle as Walden Macnair misinterprets you."

"You didn't see me today in Croydon. I was terrified. I had to force myself to walk into the building."

"But you did walk into the building. I have never understood why people equate lack of fear with courage. I must remind you that anything is easy if you are not afraid of it. And many times lack of fear is merely an indication of ignorance. No, true courage means being afraid, being horribly afraid, and doing something anyway."

"Lots of people do that. Every day."

"Very few would ask me to cast a Cruciatus Curse just to be sure he could stand up to the pain." When Snape didn't reply, Dumbledore smiled. "You see? Practical. Pain for you is a tool."

"I have never wanted to inflict{\el}"

"No, no, Severus. I mean your pain. Admit it. You used your own willingness to endure pain as a means to inspire Riddle to trust you. It is a rare ability. I should like to think that I could do the same, but I have yet to be put to the test."

"But I don't ever want it to happen again."

"Good. That is healthy. A tool of necessity, never of choice. That is what Macnair does not understand."

They sat for a while in silence. Then Snape changed the subject. "What do you think the Dark Lord meant when he said that he was better informed?"

"I do not know. But this I do know. Harry must never leave Hogwarts except to go to a place equally secure. Riddle has some task for him that requires Harry's physical presence. I do not know what it is, though I can guess from the things that you have told me. No, Severus, we cannot relax our vigilance. At all costs, Harry must not set foot off the grounds of Hogwarts."

The following Saturday was the middle of March. Snape went immediately to Malfoy on arrival in Croydon.

"I just wanted you to know that nothing special happened at Hogwarts since last weekend. I've heard of no changes in Potter's dreams. Should I tell him that myself?"

"No, I'll do it. I'm seeing him in a few minutes. It's only hearing through someone else what he should have heard first that sets him off."

"What if something happens and I don't hear about it?"

"Then you have a rough night." Malfoy watched Snape's face for a moment. "Look, I wouldn't worry too much. You're in a valuable position and you've provided some useful information. He has no one to replace you with. You'd have to out and out betray him to be in real trouble. He's not really that angry. He knows you're loyal. And you get hyper enough about a couple of pinpricks; you're not going to risk real punishment. If you tell him you didn't know something, he'll believe you. He may nudge you to keep you on your toes, but he'll believe you."

"Comforting thought."

"It should be. Avery 'd give his right arm to be as safe in front of the Dark Lord as you are. He's in serious trouble. By the way, when's the next Hogsmeade outing?"

"Two weeks."

"Good. Maybe we can get Potter then."

Snape went cold inside. "I{\el} don't think you will." In response to Malfoy's quizzical look, he explained. "That interview for the Quibbler - it was given in Hogsmeade. In punishment, Umbridge has revoked Potter's Hogsmeade privileges. He can't go there for the rest of the year."

"Ha! Another blow against Bella Lestrange! She was so certain that she could finesse a kidnapping. I have to give this news to the Dark Lord at once. Maybe then he'll listen to my plan."

"Your plan?"

"Best you not know. What you don't know can't throw you to the lions. Or in this case, Macnair."

Working later in his laboratory, Snape registered the sound of someone entering, but didn't immediately turn around.

"You might look at me, you know," said Phina.

"You were conspicuous by your absence last week."

"Last week you were in trouble."

"And what weathervane forecasts `fair' for today?"

"You think I'm very shallow and self-serving, don't you?"

"Not at all. If I were concerned about my health I wouldn't associate with me either."

"You make me laugh. I like that." She moved to a position where she could watch his profile as he mixed a cough medicine for the clinic. "I thought we might go to dinner."

"No, my lovely. You tell Bella I'm not stepping out of observation range of the security guards for all the tea in China."

"I told her you wouldn't bite. Are you always this cautious?"

"Only where my life and health are concerned."

"Suit yourself," said Phina, "but that doesn't mean I won't try again next week."

\sbreak

"Kidnapping?" said Dumbledore later that night. "That is more serious than I thought."

"It's a very good thing that Umbridge already restricted him. If it'd happened after I heard about that, I could be in Avery's position."

"We shall do our best to keep you away from such an unpleasant spot."

"Shouldn't you tell Potter? Maybe it will make him cautious and give him incentive to work on his lessons."

"Now Severus, the boy is only fifteen. He is safe here on the grounds; there is no need to frighten him with this. He has enough to worry about. McGonagall and the other heads of houses, however, need to know that he must not leave Hogwarts under any circumstances. Every other consideration has to be sacrificed to that."

"Headmaster{\el} What's in this prophecy that I don't already know about{\el} that the Dark Lord doesn't already know about{\el} that makes it so dangerous?"

"Best you not know."

Snape accompanied Dumbledore to Grimmauld Place later in the week. Kingsley Shacklebolt opened the door this time. He seemed surprised to see Snape, but offered his hand as soon as they were inside and the door closed. Snape took it.

"I owe you one," Shacklebolt said, and Snape nodded. There was no need to say more.

"Look what the cat dragged in," was Black's muttered comment as they entered the parlor.

Dumbledore glared at him, anger seething in his eyes. "Don't start it, Sirius, or{\el}"

"That's all right, Headmaster," Snape said gently. "I understand the need to appear to be frustrated by inactivity."

Black growled in response, but held his tongue.

After Snape reported on the friction at headquarters between Malfoy and Bella Lestrange, and explained the Dark Lord's desire to kidnap Potter, Dumbledore rose.

"Voldemort - you will excuse me, Severus, but it must be said - Voldemort wishes to obtain the entirety of a prophecy currently stored in the Department of Mysteries. This prophecy was spoken by one person, who does not consciously remember it, heard in its entirety by another, myself, and in part by a third, which is how Voldemort learned of it. That partial knowledge nearly destroyed him fifteen years ago, and he fears to act without knowing the rest. The prophet was Sibyll Trelawney, and she is being housed for her protection and ours at Hogwarts. I am in relatively little danger. There remains the stored prophecy, which cannot be retrieved from the Ministry except by its subject. Hence Voldemort's desire to capture Harry Potter. Like Trelawney, Potter must now at all costs be kept within the grounds of Hogwarts for his own sake and for ours."

The matter was discussed at some length and then the group retired to the kitchen. Snape once again waited for Dumbledore in the parlor. After a few minutes, Black came back in.

"Don't stand up. I won't be long. How are Harry's lessons going?"

"Poorly. Either he has no mental aptitude for this at all, or he is deliberately resisting for reasons of his own."

"Maybe he's just too honest to be a good occlumens."

"Allowing yourself to be swept away by an emotional roller coaster is not the same thing as honesty. And it will not help him fight the Dark Lord."

"Harry's stood up to Voldemort before. He's not afraid."

"Lack of fear in the face of danger is sometimes just stupidity." Snape watched carefully as Black's face began to crimson. "And courage is no shield against legilimency. Potter will stand, wand in hand, bravely facing the Dark Lord, and spilling out through his honest, undisciplined mind every piece of information the Dark Lord needs to accomplish his goals." He paused. "Just like his father."

Black lunged at the seated Snape in fury, but Snape had already read the move and dove for the floor, rolling back onto his feet in one smooth motion just as Dumbledore came through the door.

"It's all right, Headmaster," Snape said calmly, replacing his wand quickly into his sleeve. "Black and I were just debating the relative merits of physical versus mental defenses."

Dumbledore gripped Snape's elbow and steered him out of the house. "Sometimes I think the two of you together are more trouble than Riddle and all his Death Eaters combined."

\sbreak

"He wants to see you," was all Macnair said, then accompanied Snape to the interview room, but without any kind of physical pressure. Malfoy and Avery stood on one side of the room, the Lestranges on the other. Snape stayed back, but in between them, as did Macnair.

The Dark Lord arrived. "Speak, Bella."

"Lord, the quickest way to get our hands on Potter is the Hogsmeade excursion next weekend. We could have operatives at every major gathering point in the town. They would not fail to capture Potter and bring him to you."

"Lucius."

"Lord, is it not still our policy that we must keep our presence secret and out of the public eye? We are strong, but not yet so strong that we can afford to give up our well-planned caution. Even if Bella is right, and Potter can be taken, the kidnapping of a Hogwarts student from the middle of Hogsmeade, in full view of seventy-five percent of the students, would destroy that secrecy. It is, of course, my Lord's decision whether or not the capture of Potter is worth revealing our presence to the entire wizarding world, but I must point out that this should only be done if it has a one hundred percent guarantee of success. Sending even half a dozen of our people into Hogsmeade would alert the populace and the students to our presence regardless of whether they kidnap anyone, and all that we have worked to preserve will be lost{\el}"

"Stop. Severus, you will now speak."

"Lord, the people of Hogsmeade will notice strangers, as will the students. The capture of Potter may well be worth the risk of exposing our operations - I am not competent to speak to that point - but you will not get Potter. Umbridge was furious with Potter about his interview for the Quibbler, and she is obsessed with punishing him. She won't let him out of Hogwarts, and any attempt to kidnap him will fail. He won't be there."

"So you side with Malfoy."

"Lord, I side with no one. I tell you what I know."

"Go then, all of you. Lucius and Bella, we will inform you of our decision."

The six filed out of the interview chamber.

"'Lord, I side with no one.' That's a good line. I'll have to remember that." Macnair was chuckling.

"It's the truth."

"Didn't say it wasn't. It's still a good line." Macnair left them.

Bella crossed over to Snape and hooked a finger under a button on his frock coat. "Puppy dogs shouldn't cross their mistresses," she said quietly.

Malfoy pulled Snape away. "Severus has lab work to do, Bella. Go sharpen your knives somewhere else. And remember - his work is important to the Dark Lord. Don't distract him."

"I wouldn't dream of it."

The arrival of Phina in the laboratory was as predictable as the outcome of a Stalinist election.

Snape didn't even look up from his work. "Bella doesn't believe in following Lucius's advice, does she?"

"What advice?"

"Not to distract me."

"She's not distracting you. I am. I want to go to dinner."

"Tell me, what did you like best about that dinner, the food? the entertainment? the novelty of pretending to be a muggle?"

"I notice you didn't say the company."

"I hate the whole process of being disillusioned, so I tend to skip over it."

"Well, I liked the company and the food the best."

"Do you want to try doing something ordinary and mundane."

"Depends on what it is."

"Go shopping. Bring back shoulder of lamb, onions, garlic, and an assortment of vegetables - anything you like."

"Who's going to cook it?"

"I am."

By the time Phina got back, Snape had two cauldrons set up over flames. As she watched with some trepidation, he cut everything into chunks and added them to one or the other cauldron, then began sprinkling them with powders from a variety of jars.

"What's that stuff?" she finally asked.

"This is cumin." He pointed to the other jars. "Those are ginger, cinnamon, saffron, turmeric{\el}"

"Is this going to be Greek?"

"No. Moroccan."

"I didn't know you could cook."

"What's to know. You add the right ingredients in the right amounts in the right order and heat at the right temperature for the right amount of time. It's just like potion making."

"I never thought about it that way." Phina fidgeted as Snape watched her dispassionately. "Okay," she finally admitted, "I never thought about it at all."

They magicked a low table, pillows, and cushions, and sat on the floor by candlelight, eating Moroccan lamb and vegetables with their fingers, and washing their hands with mint scented water.

"That was wonderful," sighed Phina, and suddenly it seemed quite natural that she should be next to him, reclining on a cushion, teasing him with strands of her hair.

\emph{This is crazy. If Bella catches us, she'll skin us both alive.} But Snape knew that death lay waiting at every turn - in Bella's overarching lust for power, and in Macnair's lust for a more private dominance, in the chance memories sifting through Potter's brain in sleep, and in his own stumblings caused by fatigue or fear. Now, more than anything, Snape wanted life. Life that smiled and giggled up at him from an embroidered pillow. No longer caring about the consequences, Snape folded Phina in his arms and kissed her, his whole being taut and vibrating like the strings of a harp as she melted{\el}

"You SLUT! You TROLLOP! You WHORE!" The door slammed open with a crash that shook the room, Bella screaming at the top of her voice, advancing on the suddenly parted duo like the wrath of a vengeful god. "The fortunes of our whole house hang in the balance, and you DEMEAN yourself with this half-breed FLUNKY, this SERVANT{\el}"

Snape was on his feet, wand in hand, long pent-up frustration boiling over in fury. "Get. Out. Of. My. Lab., you villainous Witch!" To his right, window panes exploded outwards in violent shatterings of glass - cabinet doors burst apart as jars and canisters leapt to the floor - Bunsen burners flared, setting the cauldrons bubbling again, filling the room with the acrid smell of burnt meat. His wand raised, Snape advanced while Bella retreated, dodging beakers, test tubes, cruets, and pipettes as they smashed into the wall behind her, showering her with shards of glass.

Then Bella was out of the room, and Snape turned to Phina. To Phina, whose white face and wide eyes revealed her shock and fear. "I{\el} think{\el} I need to be going now," she said, as she edged towards the door.

There was no point in trying to stop her. Snape watched, hating both Bella and himself, as Phina slipped through the door into the hallway. Then, quickly, she looked back in, sweeping the chaotic destruction with a glance. "Did you really do all that? Wow!"

Snape set about the patient task of repairing the damage. The only other time he remembered losing control like that was at the age of thirteen, and then Dumbledore and Hagrid had been his targets. \emph{Have I truly learned so little in all that time?}


