% A Difference in the Family: The Snape Chronicles (Rannaro)
% Yes, That Is My Job

\chapter{What Is This Thing{\el}}

The following week, the last in May, was utterly routine except{\el}

On Wednesday, after the last afternoon class but before supper, Snape slipped out to the Whomping Willow and through the tunnel to try the spells that Dumbledore had given him. To his satisfaction, they worked. He enjoyed a small libation at the Three Broomsticks before sneaking back into the Shack and returning to Hogwarts.

"You look content about something," McGonagall commented at supper.

"It is merely the look of independence, of freedom from fetters."

"You're quitting and going into private practice."

"No{\el} but that's an excellent idea. `Professor Snape's Private School for Perfectly Scandalous Pranks and Spells.' Think of what you could do with the logo `P.S.P.S. for P.S.P. and S.'"

McGonagall grunted. "It depends on what vowel you put in."

"Spoilsport."

Classes ended, reviewing for exams would take up all of the next week, and on June 1 Snape again went to Croydon. Around nine o'clock, Bella came into the laboratory.

"What do you want?" Snape asked without looking at her.

"My, we are abrupt today. I won't waste your time. I want you to tell the Dark Lord that Malfoy's dream scheme won't work."

"Why should I do that, especially since I have no proof that it won't?"

"They've been working on it for months, and nothing's happened. I'd say that's a pretty fair indicator."

"They don't need me to tell them that."

"We need to act, before it's too late."

"Another piece of unplanned chaos to liven things up? I think the Dark Lord has had his fill for the moment."

"You miss her, don't you?"

Snape paused, because the slight trembling in his hands made it harder to measure the powdered horn. "What I miss or don't miss is none of your concern."

"Black killed her, you know. I can help you get revenge."

"Interesting thought, since there was more than one person there named Black."

Bella was across the space between them in three mad strides, knocking the jar of powder from Snape's hands to smash on the floor and seizing the fabric of his coat. "Who told you! Who told you! It was that rat Gibbon, wasn't it! I'll slit his{\el}"

"Like you did Phina's? How very in character."

It was like dousing Bella with cold water. Carefully she released Snape's coat and brushed imaginary dust from his shoulder with a casual hand. "It's your fault anyway, puppy dog. You taught me the spell."

"No. No, I didn't teach you{\el}"

"Sure you did. All those years ago when you were coaching the dueling classes{\el}"

"Self defense."

"Well, that was one of them. The Digladior. I never got much chance to use it before."

"That's for close range hand-to-hand combat. You can't shoot that across an open space, it's not a thrown spell. You can't aim it. It scatters like birdshot."

"I wanted it to scatter. You hit more targets that way."

"Right. Your own people."

"She got in the way."

"Now it's her fault. My fault, her fault, never your fault is it, Bella? Disobey orders, misuse spells, kill your own{\el}"

"Shut up, Snape!"

"Did you have a pleasant chat with the Dark Lord, Bella? Was he loving and kind to his favorite?"

Bella's wand was out, pointed at Snape's face. "You have a vicious streak in you, Potions Master. No wonder Phina couldn't stomach you. And all along I thought it was just because you were such a cold fish."

Snape looked into Bella's eyes, rather than at the wand. "Yet another act of unplanned chaos? The Dark Lord is going to want to `talk' to you again about disposing of his potions maker without going through proper channels."

"Cold and impersonal. Poor Phina. The one time she managed to start something, I had to walk in and break it up. What a waste of talent. A warm, passionate person can grow tired of plays and restaurants and philosophical pronouncements, you know. But maybe that's all you were ever capable of."

"Not everyone enjoys your love of life, Bella."

Bella relaxed and put her wand away. "Don't pretend, puppy dog. I know you can lose your temper - I've witnessed it. It was one of the most impressive tantrums I've seen in my life. I had high hopes that night that you'd grown up to be a man. Pity."

"Classic queen-side attack. The Lady Macbeth gambit, I believe. It won't work Bella. One of the benefits of all those plays and philosophical pronouncements."

"You're going to sing to my tune."

"Shall I tell the Dark Lord you're trying to persuade me to follow you instead of him?"

"This isn't over." Bella swept from the room, her anger radiating around her.

Snape stood calmly in the laboratory in the wake of Bella's visit, his heart pounding, but not from fear of Bella. \emph{Dear Bella. No subtlety at all. If she'd known the truth, she'd have used it, and to good effect. That she didn't use it means she doesn't know it. Should I tell Dumbledore?}

In the end, since it was no news of an urgent matter, Snape decided not to send to Dumbledore, but rather to wait until a more routine meeting. Instead he returned on schedule to Hogwarts, holding close the new-discovered knowledge that Phina had lied to Bella about him. The intimate evenings at Phina's flat were reported as theater outings and restaurant visits. That was what Bella 'd said, plays and restaurants, plural. The one physical encounter Phina had mentioned was the one Bella knew about anyway.

And Phina's death was an accident. An accident caused by poor judgment and unrestrained recklessness. Criminal negligence. \emph{If I leaned toward self-sacrifice, I might support Bella as the surest and quickest way to destroy the Dark Lord, but a) I do not lean toward self-sacrifice, and b) while quick, the way would also be violent and bloody. Yet for some reason the Dark Lord does take Bella's advice seriously. One can only wonder why.}

\sbreak

The reviewing during the next week was intense. Although the first through fourth and sixth years were still finishing off regular classes, there were five years of review for the fifth years, and two years' worth for the seventh years. It was like this every year before the OWLs and NEWTs, and every year Snape hated it. He worked side by side with his students on a weekly basis and knew what they were capable of. The stress connected with exams never allowed a student's real abilities to shine through. If it were not for the irrational importance the outside world attached to them, the exams would be a waste of time.

The only really good thing about the week was that the common room was full of studying students, and no one was causing any trouble.

By Wednesday it became clear that McGonagall and Umbridge had entered a new stage in their battle of wills. McGonagall was summoned several times to Umbridge's office and `casual' passersby reported argument so intense that they feared the two might come to blows, though the exact words were so distorted by the closed door that none was sure what the disagreement was about.

Snape had a pretty good idea, though. He was not completely surprised when McGonagall stopped by his chair at the end of supper.

"You, Professor, have submitted an order for fangs and claws that is far beyond anything needed by your classes. Please come up to my office at once to either correct what I presume is an error, or explain why I should let the order stand."

Snape followed her meekly up the stairs, knowing there would be no order. When the door was safely shut behind them, McGonagall first searched the office with an anti-spying spell, then whispered, "She wants the defense spells, and with the examiners coming in I can no longer justify not giving them to her. A couple of weeks ago you said you were independent and unfettered. Does that mean you have a way out?"

"I don't know if I should{\el}"

"Listen, Severus. The main reason I've been keeping the spells away from her is to protect your comings and goings. I don't want her to catch you or block your movements. But now we have examiners coming and Dumbledore still isn't back. She's determined to let them in herself, and if I thought I was headmistress I would feel the same. She's getting an injunction from the Ministry of Magic. If I defy it, I can be dismissed."

"Dismissed? If you defy it, you can be arrested. Why didn't you tell me it was getting this serious? Dumbledore showed me two weeks ago how to get in through{\el}"

"Don't you be telling me, now. I don't want any of that kind of information to be tricked out of me. The bottom line is that for the last two weeks you've had an emergency exit from this place, right?"

"Yes."

"Good. When she gives me the injunction, I'll turn over the spells."

Business seemed over, but Snape hesitated. "May I ask you a question?"

"Of course you may ask. I can't say as I'll answer."

"How do the owls get in?"

"You are a shrewd one. Albus explained it when I became deputy, though I must confess I'd never have thought to ask myself. There are two ways. Those coming in from the east could just fly low through the forest. There's no shield there. The centaurs would never permit even Albus to interfere with their territory, but they also guard that side very effectively. There are too many owls from too many families to train them all, however, so the shields have been calibrated to permit their passage."

"You mean you can adjust the shields to block everything except one kind of animal? Or maybe one particular person?"

"Don't you go getting any ideas. The shields are far too big to calibrate to just one individual. It has to be a whole species. I imagine a much smaller screen could be made to allow one person only to pass through."

"What about an owl animagus?"

"I suppose that would breach the defenses. Or ones so small that the shields don't filter them. I am not, however, going to debate with you how many angels can dance on the head of a pin. You can't get through. It's good you have the other way."

Thursday at lunch, Umbridge appeared more pleased than Snape had ever seen her. Clearly the injunction had arrived, had been served, and McGonagall had obeyed.

On Saturday, Snape left the castle after dinner and slipped down the hill to the Whomping Willow, the tunnel, the Shack, and Croydon. When he saw the messenger at the door, he headed directly for the stairs and the interview chamber. The Dark Lord sat calmly enthroned outside the circle of light usually used for interrogations while Malfoy and Bella stood in its center yelling at each other. It was odd to hear Malfoy's voice raised to such a volume, but the moment encapsulated Bella perfectly.

"{\el}foolish, undisciplined behavior{\el}"

"{\el}keeping us locked in the same place, with no progress for{\el}"

Both stopped when Snape entered and all three turned to the Dark Lord.

"Potions Master, do you have frequent occasion to see Sirius Black?"

"Not frequent, Lord, but occasionally."

"Since he returned from Azkaban, have you seen him angry, defiant, or in pain?"

"I saw him surprised and angry, but only for a moment, as I was knocked unconscious by a spell. Since then I have seen him rude and arrogant on several occasions."

"But not as I have described."

"No, Lord."

"Go then. We shall not need you further tonight."

As Snape climbed back up the stairs, a shorter, somewhat dumpy man scurried past him. \emph{I haven't seen him in months. Why would the Dark Lord want to speak tonight to Peter Pettigrew?}

The examiners arrived Sunday evening during dinner. Umbridge arranged a small reception for them in the staffroom, since they had already dined and did not want to cause consternation among the fifth years by suddenly appearing in the Great Hall. When the teachers assembled in the staffroom, Umbridge started to make introductions, only to be interrupted by tiny, wizened little Professor Marchbanks.

"No need, Professor Umbridge, no need. We've been coming here for so many years now, it's beginning to seem like home. Minerva, I hope you are well. Much calmer this year than last, isn't it? School was all agog waiting for the third task. Hardly anyone could concentrate on their OWLs."

Snape waited his turn to greet the four examiners, and old Professor Tofty pulled him aside to ask about some potions work Snape had done for him years earlier. Then the teachers were given their assignments and all retired for the night.

No teacher was allowed to proctor the exam for his or her own subject, so Snape drew the OWLs for Ancient Runes, Arithmancy, and Muggle Studies. It was fairly easy duty this year since none of them were courses taken by the entire fifth year. Proctoring History of Magic, or Transfiguration could be a nightmare.

Croydon was tense again on Saturday. Snape found a pile of orders for medical potions and set to work on what was going to be a very late night of brewing. It was convenient that he could now get in through the Shack, and didn't have to worry about the eleven o'clock curfew.

Around ten o'clock the Dark Lord sent for him. It was a short meeting observed, as now seemed usual, by both Malfoy and Bella.

"Stand before us, Potions master, and look into our eyes."

Snape obeyed, not overly nervous since this had none of the feeling of being a test.

"Show us Sirius Black as he appears today."

Snape allowed images of Black's face to surface in his mind, trying as unobtrusively as possible to make them ones where Black was not angry. Snide, mocking, impatient, all were revealed. The Dark Lord seemed content.

"Now, let us hear his voice."

Again there was a certain selection on Snape's part to keep anger away from the images, so the Dark Lord heard the comment about what the cat dragged in, and inquiries as to Potter's classes, all of which were acceptable and pleasing.

"You may go."

The second week of OWLs continued to go smoothly. The only night of the week when the students were out of the common rooms was Wednesday, when the Astronomy Practical Exam started at eleven o'clock. Snape took advantage of the quiet and went to bed early.

Pounding on the door startled him awake well after midnight. It was Flitwick yelling, "Severus! Severus! Wake up! Quickly!"

Snape pulled on a robe and opened the door. "What{\el}"

"Minerva{\el} Pomfrey needs you{\el} Now, come now{\el} Oh, to think{\el} To Minerva{\el}"

"What's happened to Minerva? Is she sick?"

"Not sick{\el} Stunned{\el} Four - right in the chest{\el} They were sacking Hagrid{\el} She tried to stop them{\el} Outside{\el}"

Snape pushed Flitwick aside and raced for the entrance hall. Out the doors and down the hill he ran, noting that Pomfrey herself had only just arrived at McGonagall's side. Pomfrey knelt, then waved frantically at him, screaming in the warm June night, "She's not breathing! I can't get a pulse!"

There wasn't a second to lose. "How long ago?" Snape demanded as he ran up and dropped to his knees beside McGonagall's still body.

"Three, maybe four minutes, as near as I can tell."

Snape tilted McGonagall's head back, checked her throat, pinched her nose shut and bent to blow air into her mouth. When her lungs had expanded twice, he shifted to push rapidly on her chest about a dozen times, then breathed air into her lungs again. McGonagall shuddered suddenly and gasped in a breath on her own.

Pomfrey checked. "We've got her. Wait a few minutes while she stabilizes." She looked up at Snape, who was sitting back on his heels, head down, panting slightly. "There are some things wands and potions can't do. Tomorrow you're going to teach me that muggle trick."

Madam Pomfrey took over and began conjuring stretchers, for McGonagall was not the only one hurt. Several functionaries from the Ministry of Magic, called in by Umbridge as back-up, had been tossed around bodily by Hagrid. Two were still unconscious, while others had various minor injuries. Several of the seventh years were enlisted to help move the stretchers up the hill.

Inside the castle the rest of the staff, though terribly anxious about McGonagall, had stayed at their duty posts and herded the students back into the common rooms, keeping the corridors quiet.

In the entrance hall, Umbridge seized Snape's sleeve, forcing him to look at her. "Come to my office immediately. I want to talk to you."

"No," Madam Pomfrey said at once. "I need him in the hospital."

Snape brushed away Umbridge's hand. "In a medical emergency, Madam Pomfrey outranks you," he told Umbridge, then turned his back and followed Pomfrey up the stairs, leaving Umbridge to fume.

They laid McGonagall on one of the beds while Pomfrey checked the other two unconscious patients. Returning to McGonagall, she listened to her chest, then motioned Snape to McGonagall's side. "There's some kind of flutter. See what you can read."

Leaning forward, Snape gently opened McGonagall's eyes, ignoring the fact that Umbridge had entered the hospital and was watching them. He was interested to find that part of McGonagall's mind was shut down, and not from injury. He passed it by, as it did not pertain to his business as a healer's assistant. "Some damage to the sternum and ribcage at the point of impact," he said as he searched for information about the heart, "lung tissue{\el} here's the heart. It seems{\el} there's some unusual twitching in the muscles. It's small, but there{\el} right side."

"Ventricular fibrillation. Get St. Mungo's. We'll have to move her." Madam Pomfrey drew her wand and began a low rhythmic chant as she moved the tip in a tiny circle around the area of McGonagall's heart.

Snape turned to Umbridge. "We're getting a medical team in from St. Mungo's Hospital to evacuate her to London. You're going to open the defenses for them."

"I'll do no such thing! You can't order me around."

"No? Watch me." Snape clamped his hand around Umbridge's upper arm and dragged her over to the hospital fireplace. Forcing her onto her knees beside him, he took a handful of floo powder, threw it into the fireplace and said, "St. Mungo's, Emergency Room." A nurse appeared in the green flames.

"Hogwarts school." Snape said. "We have a medical emergency. Patient is female, age seventy, struck in the chest with multiple stun spells{\el}"

"Is this Professor McGonagall?" asked the suddenly anxious nurse.

"Yes. Temporary paralysis to the diaphragm muscles and cardiac arrest. Patient is breathing independently now, but exhibiting signs of ventricular fibrillation. There's a healer keeping the heart stable, but we need a medevac team."

Snape could hear the nurse speaking to others in the emergency room. "Floo transport and apparation are out of the question due to the patient's unstable condition. You'll take two healers and fly her back. Hogwarts," she was talking to Snape again. "We have a team ready to go. Are the defenses open?"

"One moment. I want you to explain to this desk clerk what happens to people who contribute to a death through unprovoked and malicious use of a potentially fatal spell." Snape clutched Umbridge's shoulders and pushed her face into the flame. Though not in direct communication himself, he could hear the nurse say, `Voluntary manslaughter. One to five years in Azkaban, depending on the circumstances.'

Pulling Umbridge back out, Snape told her quietly, "Lower the defenses."

"Yes, Dolores," said a voice behind them. Snape turned to see Professor Tofty standing near the door. "In case you are wondering, I was conducting an exam and witnessed the entire incident from the Astronomy Tower. Do as Professor Snape says."

Umbridge glowered, furious and unwilling, then reluctantly she pulled out her wand, muttering the spell so that the others couldn't hear.

"Just so we understand each other, if the medics run into a barrier now, it's murder," Snape warned her, then said to the nurse. "Hogwarts is open."

He scrambled quickly out of the way, dragging Umbridge back from the fireplace as the medevac team came through. They carried transport brooms and an aerial stretcher, quickly transferred McGonagall to it, and were gone.

"Now," said Umbridge to Snape as she closed the defenses once more, "Now you come to my office."

"How dare you interfere in my running of this school!" Umbridge hissed, whirling on Snape as soon as the door to her office was closed. Snape raised his eyebrows, but said nothing as Umbridge began to pace back and forth. "You have flouted my authority, disobeyed my orders, undermined my position in front of the rest of the staff{\el} How dare you enter into a matter that was none of your business!"

"I suggest you tread with care," Snape finally replied. "Have you any idea what percentage of Britain's wizarding population has learned Transfiguration from Professor McGonagall? I wouldn't worry about your position if I were you. I'd worry about being lynched."

"Silence! You had no right to interfere!"

"I had every right. Madam Pomfrey sent for me as Potions Master and as her medical assistant which, incidentally, is part of my job. Which you would have been aware of if you were doing your job as headmistress."

"Rank, blatant insubordination!"

"Be thankful for it. If Pomfrey and I hadn't been there, there'd be a warrant out for your arrest right now. Your little game was witnessed by the entire fifth year class."

"How do you know that?"

"That's who Tofty was examining up on the Astronomy Tower. If he saw it, they all saw it. Probably before Tofty did. Teenagers have this sixth sense{\el}"

"One more word out of you and I'll dismiss you from staff!"

Snape was silent.

"You're on probation. One step in the wrong direction, Professor, and you are out of Hogwarts and into Azkaban. Do I make myself clear?"

"Yes, ma'am."

"And your weekend jaunts are over. You're confined to the grounds until the end of term."

"Yes, ma'am."

That morning's OWL exam was in Muggle Studies, and Snape reasoned there was no sense trying to get any sleep before the test, so he headed first to his rooms to dress, then down to the Whomping Willow, deriving a certain satisfaction from disobeying Umbridge so soon after receiving her orders.

The Dark Lord chose not to be available at two in the morning, but Macnair was duty officer, so Snape left with him the information that McGonagall had been injured and sent to St. Mungo's. They both agreed that since it didn't directly impact any of the Dark Lord's plans, there was no reason to disturb him against his express wishes.

A few minutes later, Snape was walking back up the hill to the castle.

At breakfast, Snape filled the rest of the teachers in on McGonagall's status. By that time Pomfrey had gotten word that she was out of danger. The teachers agreed it was good that she'd gone to the hospital, both for the extra care and to get her away from Hogwarts and Umbridge.

The Muggle Studies exam went smoothly. Most of the school slept late because of the previous night's excitement, and those who had to be stirring for the test were quiet and subdued. When it was over, Snape returned to his own rooms, hoping to get some sleep before dinner. It was sure to be relatively quiet, since the entire fifth year class was taking their History of Magic OWL.

As he lay fully clothed on the bed, Snape found himself thinking of Phina, of that night in the laboratory when he'd fallen asleep while she massaged his back. He was tired now. His back and his head both ached, and it would feel so nice to have her fingers soothe away the tension and the pain. \emph{Why does everyone I care about have to die?}

It was then that the true wonder of Phina occurred to him - she hadn't awakened his father's demon. She had teased him, mocked him, yelled at him, and defied him, but at no point had he felt the need to control her or to strike her. \emph{Is that proof positive that `love' didn't exist between us, or an indication that something fundamental has changed in my life?} While revolving the question in his mind, Snape fell asleep.

He slept through the beginning of supper, and was again awakened by pounding on his office door. This time it was Draco Malfoy. "Professor? Professor, are you there? Professor Umbridge wants to see you, sir. It's important."

Snape stood up and walked to the door. "Quiet down, Malfoy. What does she want?"

"She's caught Potter and Granger in her office, Professor. Potter was climbing into the fireplace. It looks like he was trying to escape."

"Really?" Snape was trying to imagine why Potter would do such a thing. "What does Professor Umbridge expect of me?"

"I don't know, sir. She just told me to fetch you."

"Very well." Snape locked up the office with slow care, then strolled towards the entrance hall and the stairs. He might have to obey Umbridge, but he wasn't going to do it quickly. Draco stayed ahead of him, trying to encourage him to go faster. \emph{Probably afraid he's missing something.} At the door to Umbridge's office, Draco was still ahead. He entered first, Snape not far behind.

"You wanted to see me, Headmistress?" he said as he walked through the doorway, taking in Potter, Granger, both Weasleys, Longbottom and, even more surprisingly, Lovegood. Potter stood before Umbridge's desk while the others were being restrained by a predictable assortment of students from Snape's own house.

"Ah, Professor Snape. Yes, I would like another bottle of Veritaserum, as quick as you can, please."

\emph{Hoist on your own petard, you ugly witch!} "You took my last bottle to interrogate Potter. Surely you did not use it all? I told you that three drops would be sufficient." Snape was rewarded by the telltale crimson that suffused Umbridge's face.

Her voice simpering, Umbridge coaxed, "You can make some more, can't you?"

"Certainly. It takes a full moon cycle to mature, so I should have it ready for you in around a month."

"A month? A month? But I need it this evening, Snape! I have just found Potter using my fire to communicate with a person or persons unknown!"

"Really?" Snape said, glancing over at Potter. \emph{Tonight. It's tonight and either Malfoy's won and the Dark Lord's concocted a convincing illusion, or Bella's kidnapped Sirius Black.} "Well, it doesn't surprise me. Potter has never shown much inclination to follow school rules."

The boy stared back at him, Lily's eyes meeting his own with steady purpose. Snape saw an image, faint and blurred, of Black on his knees before the Dark Lord, defiant but in pain, and heard the familiar high laughter.

Umbridge was bleating into Snape's ear. "I wish to interrogate him! I wish you to provide me with a potion that will force him to tell me the truth!"

Snape divided his own mind, one side speaking to Umbridge while the other tried to project to Potter. "I have already told you that I have no further stocks of Veritaserum. Unless you wish to poison Potter - and I assure you I would have the greatest sympathy with you if you did - I cannot help you. The only trouble is that most venoms act too fast to give the victim much time for truth-telling{\el}"

To Potter the message was: \emph{I understand. I'll try to contact him}, but Potter wasn't receiving. Instead he was broadcasting words over and over: \emph{Voldemort's got Sirius in the Department of Mysteries{\el}}

Meanwhile, Umbridge was livid. "You are on probation! You are being deliberately unhelpful! I expected better, Lucius Malfoy always speaks most highly of you! Now get out of my office!"

\emph{How dearly I would love to see your face on the day you learn that Malfoy has been playing you like a violin, to his tune, not yours.} Snape bowed a play actor's bow and turned to the door to leave. Then Potter nearly ruined everything.

"He's got Padfoot! He's got Padfoot at the place where it's hidden!"

Snape froze, his hand on the doorknob. The words were so obviously a code that he half expected a paralyzing spell to hit him in the back. Mercifully Umbridge was living up to her image of being a trifle thick.

"Padfoot? What is Padfoot? Where what is hidden? What does he mean, Snape?"

Snape looked around at Potter, projecting a message he was certain the boy was incapable of receiving: \emph{You stupid idiot! If I make it out of this, I'm going to ask Dumbledore for permission to skin you alive and hang your pelt in the staffroom.}

"I have no idea. Potter, when I want nonsense shouted at me I shall give you a Babbling Beverage. And Crabbe, loosen your hold a little, if Longbottom suffocates it will mean a lot of tedious paperwork, and I am afraid I shall have to mention it on your reference if ever you apply for a job."

Closing the door behind him, Snape took a deep breath, then hurried down the stairs to the entrance hall and out into the long, June afternoon that was fading into evening. Supper was half over, but food was the furthest thing from Snape's mind.

As soon as he was sheltered from view by the bushes along the path, Snape drew his wand and sent a patronus skimming south with the message \emph{Potter has seen you in danger. Are you safe? Are you at home?} The message was for Sirius Black, and if Black was in the hands of the Dark Lord in the Department of Mysteries, the Dark Lord would see the patronus and there would be no answer.

The wait seemed to go on forever, but it was really only a few minutes before the ghostly dog brought the reply. \emph{I'm at home and well. Is Harry all right?}

Black deserved an answer. Again the fox traveled south. \emph{He's in trouble for rule-breaking as usual, but otherwise fine. As soon as I can talk to him, I'll pass on your message. Do not send again except in need. Umbridge is watching us.}

With that business taken care of, Snape walked back up to the castle and into the Great Hall. Some of the students had finished supper, so he sat at the foot of the Slytherin table to eat. That way he could keep an eye on movement in the entrance hall.

Thus it was that Snape saw the curious little parade - Granger, Potter, and Umbridge - as they left the castle and headed down the hill. He went outside to watch them, puzzling why they should be going to the Forbidden Forest. He didn't think there was too much to worry about - Umbridge would ensure that Potter never left the grounds, and that was what was important. So Snape waited.

Several minutes later there was a clatter and a rush of students out of the castle, traveling so hurriedly they didn't even notice Snape standing to one side of the entrance steps. It was the Weasleys, Longbottom, and Lovegood, and they were running for the forest.

Curiouser and curiouser. Then Snape remembered the Slytherin students and rushed up the stairs again.

Malfoy was worst hit, his face covered with bats. Bulstrode and Warrington were on the floor, stunned. The others were recovering from various Impediment and Disarming jinxes. Snape helped the students to the hospital wing, grateful that there were no more serious injuries. Then he went to the windows overlooking the forest to watch for the return of Umbridge and the students.

Long minutes ticked by and finally the sun, descending towards its setting, began to tinge the sky with crimson. Snape could wait no longer. Searching for the best way to communicate, patronuses being good only for short messages, he realized that Potter had chosen Umbridge's office because the fireplace there was not being monitored. He ran up the steps to the second floor and entered Umbridge's domain.

It was a strange feeling, not knowing if she would return and catch him as she'd caught Potter, but there was no help for it. Taking a handful of floo powder from the pot Umbridge kept by the hearth, Snape knelt and tossed it into the fireplace, saying, "Twelve Grimmauld Place."

What Snape saw was the kitchen. "Black!" he called. "Sirius Black! Lupin! Moody! Anybody!"

It was Black who answered. "Where's Harry?" he demanded without preamble.

"I'm not sure," Snape answered. "He and Granger led Umbridge into the Forbidden Forest a couple of hours ago. Several of his friends followed them in. They haven't come back yet."

"A couple of hours ago! And you've been sitting there doing nothing!"

"I've been tending to students they attacked, and I've been waiting for them to come back. They're with Umbridge, who can't afford to have anything happen to Potter. And the whole crew of them are pretty fair spell casters themselves. My main concern is that they don't go to London. They haven't got brooms, and they don't know how to apparate, so I think they're safe on that count."

"What's happening in London?"

"Potter saw a vision of you in the Department of Mysteries being tortured by the Dark Lord. I never had the chance to give him your message, so he doesn't know you're safe. I'm afraid he may try to go to London to help you. He has a tendency to do foolish things like that."

"Brave things, you mean. How do you know about this vision?"

"He projected it to me. I tried to project back that I would contact you, but I don't think he knows how to receive. Anyway, I'm going into the forest to look for them, and I wanted you to know what was happening. If he's found a way to go to London, someone should be sent to the Ministry to head him off."

"I'll go myself."

"That isn't wise. You're the bait. If the Dark Lord gets his hands on you, he'll be able to lure Potter anywhere he chooses. I'm going to try to reach Dumbledore now. Someone should stay at headquarters to let him know what's happening. The logical person is you."

"No. If Harry's in trouble, he needs my help. I'm going in. I'll tell everyone here what's happening, but I'm going in."

"That's only playing into the Dark Lord's hands. You of all people need to stay away."

"No! He's James's son! For Chris'sake, Severus, he's Lily's son! And he's the closest thing to my own son I'll ever have. Dammit, I love him!"

For the length of a heartbeat they stared at each other across the green flames, and all the years that stood between them came down to this one moment.

"Good luck," said Severus.

"Thank you," Sirius replied, and was gone.

The floo connection broken, Snape stood and left the office. Since he was going outside anyway, he waited until he was clear of the castle before he directed the patronus to Dumbledore. \emph{Potter gone into forest. May be trying to reach London. Vision of Black held by V. Am going into forest to search now. Full details at number twelve.}

Suddenly, in the gathering darkness, the forest seemed very large. \emph{All I can do is follow their footprints and hope that I find them safe and sound.} As he slipped into the shadow of the trees and lit a Lumos spell, Snape found himself remembering every evil story he'd ever heard about the dangers of the Forbidden Forest. There was no help for it, he had to search. And because of the connection between Potter and the Dark Lord, he had to search alone.

He only hoped that he would find Umbridge and the students well, and be able to return with them to the castle.

What little daylight was left faded, and the dark forest grew darker. Snape had trouble following the path of the students, even though earlier it had seemed as if a herd of buffalo had trampled the undergrowth. He had never gone so deep into the trees before.

Then, suddenly, there was a crash of movement and of powerful bodies around him. Snape froze.

The beings were centaurs. They snorted and pawed the ground, feinting towards him and then pulling back. "You walk where you should not walk, human," one great black one neighed at him.

Snape stood, petrified. He'd watched the palomino, Firenze, enter Hogwarts with Dumbledore, but had never gone close to or spoken with him. These great creatures were enormous, towering over him, their powerful hooves cutting into the turf like knives. Snape wanted no hoof aimed at his head.

"I mean no harm," he said, "and I crave your pardon for coming where I have no right, but I seek our children, young ones led into your land by another human, shorter than I and female."

"The plump mare," snorted the black centaur. "Do you seek her as well?"

Snape thought fast, trying to remember everything he'd ever read about horses in muggle books and magazines. "No, she's an outsider. She came to us trying to take over the herd, and attacked our lead mare. She's stolen the foals, three colts and three fillies."

A chestnut stallion advanced. "What do you wish?"

"To find the foals and return them to the herd. Or at least to know they're safe."

"And your lead mare?"

"Was badly injured, but lives. We are caring for her as best we may."

"Will you take the plump mare as well?"

"If you require it, I will, but none of us wish her to return to the herd."

Stamping hooves shook the earth, and neighing pierced Snape's eardrums. The centaurs moved away, leaving only two to watch him. Snape waited, trying to look submissive, not certain how horses did it.

The chestnut advanced on him again. "Your foals are gone. They found the wingéd ones and mounted them. They have gone south. The mare is with us - you may speak with her, but not take her. There is a moving mountain in the forest, a danger to all sentient creatures, thus you will be silent as you travel with us."

"I will obey the herd guardians of this place."

The centaurs led Snape deeper into the forest while he pondered the information they'd given him. The students had found the `wingéd ones,' which must mean the thestrals. From northern Scotland to London was a few hours' flight by broom or thestral, so there was a very good chance that Black and the other members of the Order would be at the Ministry well before Potter and the students. That was very good news.

What was not good news was the information about the `moving mountain.' Snape had no idea what that could be, and as the centaurs seemed to fear it, he hoped fervently that he would not encounter it.

Deep into the forest they went until they reached a large clearing. Neighs and trumpetings reverberated through the trees as the guards greeted the herd. Other centaurs, mares and foals, lunged at him, pulling up just before hitting him. Snape stood very still, forcing himself not to run in panic.

Umbridge cowered in an open space on one side of the clearing, her hair disheveled and her robes torn. Young centaurs pranced around her, dodging in from time to time to nip at her or snatch and pull her hair. The fillies especially seemed to enjoy this game. Umbridge groveled in terror liked a whipped cur, no trace of her former arrogance left.

"Professor," Snape called as he approached her.

"Snape!" she screamed. "Oh, gad, Snape, get me out of here!"

The chestnut intervened. "You said this mare tried to take control of the herd. Do you follow her, or do you follow your herd leader?"

Snape glanced over at Umbridge, who was now hanging on every word. "I follow our herd leader," he said, and Umbridge moaned.

"This is good. Tell your lead mare that we have her rival. As this is no danger to our own herd, we have not harmed her. We will keep her here until your herd leader is well again and sends for this rebel to chastise her. You will return to your herd now, and you will return alone."

Umbridge pleaded and begged, but Snape had no choice. Not that he really wanted one. "I'll tell McGonagall where you are," he called to Umbridge, and let the centaurs escort him back to Hogwarts.

Midnight came and went, and there was still no word of any kind from London. Snape paced his office like a caged thing, desperate for news. Had Potter arrived in London? Were Black and the other members of the Order able to stop him? Had Dumbledore received his message? And, worst of all thoughts, did the Dark Lord have the prophecy?

Then, in the wee hours of the morning, the mark on Snape's arm seared with a terrible pain, more terrible than the day a year before when the Dark Lord had returned. So intense was the summons that Snape almost forgot where he was and started to apparate from his office, stopping just in time to keep from throwing himself against the shields.

\emph{Shack. I have to get to the Shack. I have to go to London}. There was no room for any other thought, and the summons drove Snape down from the castle to the Willow, where he fumbled desperately for the knot, then ran stumbling and tripping through the tunnel to the Shack. A frantic \emph{Patefacio tugurium} and he was free, apparating at once to Croydon.

Croydon was a madhouse, Death Eaters scurrying like rats, dragging boxes and crates hurriedly packed from rooms that were being gutted. Snape paid no attention, diving for the stairs in panic and racing to the interview chamber, where he threw himself prostrate before the Dark Lord, realizing only then that Bella was already there, lying beside him, moaning in pain.

"You will stand, Potions Master, and you will look at us."

Snape got trembling to his feet and let the Dark Lord search his eyes.

"What do you know of this night?"

"Only that you have summoned me in anger, and the night brought evil to our cause."

"They have failed us, these servants. Failed us and left us with dust. Potter came, but their incompetence has lost the prophecy forever, shattered to pieces in the bowels of the Ministry. And this same incompetence brought our enemies, Dumbledore's Order and even Dumbledore, so that we ourself was forced to reveal our presence to retrieve the smallest crumb from the ashes of so great a debacle."

The Dark Lord pointed a long thin finger at Bella, and she writhed and screamed on the floor.

"Whom have we lost, Potions Master? Who goes tonight to Azkaban?"

"Lord, I do not know. I was not admitted to the planning."

Pain wrapped Snape in fire as the Dark Lord reached out to punish him. "Do not shield yourself in excuses. Defeat for one is defeat for all. Faithless slave," he said to Bella, "tell your fellow servant whom we have lost."

"Malfoy," she gasped, "Macnair{\el} my husband Lestrange and his brother{\el} Rookwood{\el} Dolohov{\el} Avery{\el} Mulciber{\el} Crabbe{\el} Nott{\el} Jugson{\el}"

Snape listened, horrified, as Bella named every first and second rank Death Eater in Britain except for herself. Then the Dark Lord crooked his finger and she screamed again.

"And how many did Dumbledore lose?"

"One, only one{\el}"

"And who will replace those we have lost?" Bella screamed once more, but the Dark Lord no longer paid attention to her. Instead he turned his crimson gaze on the apprehensive Snape. "Who stands above you, Potions Master? Who is there left whose rank outmatches yours?"

It was an answer that terrified Snape, a fate he would have given anything to avoid. "No one, Lord," he replied, and his voice was a hoarse croak.

"So, highest ranking of our advisors, advise us now."

"Lord, why do your servants strip this place as if for departure?"

"It was set up by Malfoy, and he is its secret keeper. We do not trust his strength of will in Azkaban, even though dementors no longer staff it. All the guardians of our branches have been taken."

"Where will we go?"

"It is for you to advise us. Give us an opinion, Potions Master."

"Birmingham, Lord. It's large enough for our whole organization to get lost in, yet far from any of our former centers. But we can't go there now, we have no building to use. Let our people take as much as they can and scatter. When we have a place, you can summon them again."

"Organize it."

"But Lord, I'm expected to be at Hogwarts."

"You have lieutenants."

"No, Lord. My work until now has been solitary. No one follows me."

There was a pause that Snape didn't know how to interpret. When he spoke again, the Dark Lord's voice had changed, lost some of its anger. "You neither follow nor have followers. Who protects you? Who watches your back?"

"I don't go into the field. Why would I need protection, Lord?"

"You are naive." Another pause, and footsteps were heard outside the door. An odd couple came in and knelt before the Dark Lord, short dumpy Peter Pettigrew and a big brutish Death Eater that Snape recognized as Nigel Yaxley.

The Dark Lord pointed again to Bella, and she rose to her knees beside the other two, perspiration beading her face. "This is what I have to give you, Severus. Between them a sorry record of failure, though each has also had some insignificant successes and all long to demonstrate their loyalty. You three will go with Severus now. You will listen to him, advise him to the best of your ability, and follow his instructions. If there is any dispute of the smallest kind, I will accept only Severus's report of what happened. You understand."

"Yes, Lord," the three chorused.

"Severus, I give you access to Malfoy's office. You will stay here until these servants know enough to continue without you. Then you may return to Hogwarts. What you tell Dumbledore I leave to your discretion."

Then the Dark Lord was gone.

As Snape's three new lieutenants rose slowly from their knees, Snape turned to Bella. Somewhat apologetically he asked, "Where is Malfoy's office?"

The spare, austere office was a surprising contrast to the rich luxury of the Malfoy home. Neat and orderly, it reflected the part of Malfoy's personality that was seen most at Croydon, away from family or the political concerns of the Ministry. Snape went at once to the files.

One cabinet contained personnel files, which Snape closed immediately after a brief glance told him what they were. The other contained purely administrative material, blueprints of the building, organizational charts, supply orders, lists of contacts{\el} Snape was amused at Bella's reaction to the mass of meticulously ordered files. It was clear she'd never arranged her own department in any organized way.

"Here. This one is a floor plan of all our departments here, and here's a list of those in charge of the day to day operations in each. Yaxley, do you still have access to Cardiff?"

"No, sir. A new spell was performed when Nott took over."

"Drat. That should have been one of your assignments, to go there and shut down the operation. What about Glasgow; that was Rabastan's. No? Lestrange, you never visited him there? What about Lincoln, Manchester, and Norwich?"

There was no answer. \emph{This is impossible. Five branch offices, and no one in London can enter them. And their secret keepers are all in Azkaban. Why don't I just let the Ministry get the secrets from them?} But that was not an option. The Dark Lord would accept no more loss of personnel or assets, and would punish the one who failed him now, possibly with death. For now, Snape worked for the Dark Lord to the best of his ability.

Snape began a thorough search of every file in the cabinet. He was rewarded almost at once with lists of safe houses all over Britain, from Cornwall and Kent to the Isle of Skye. Pulling the file out and tossing it on the desk, he said, "Go through that. Those are the locations we're dispersing to." Then he saw the narrow folder that was titled simply `notes.'

Inside were five small pieces of note paper, folded in thirds and sealed with paper wafers. On the back of each was written a name: Cardiff - Glasgow - Lincoln - Manchester - Norwich. Malfoy thought of everything.

\emph{Something so valuable and yet so useless. Only one person can look at each note, and then it's gone. And that one person can't be me because I can't go out to the branches now. And it has to be now.} Quietly he handed three of the papers to Yaxley, and two to Bella.

"After we review what needs to be done, Yaxley you go to Norwich, Lincoln, and Cardiff - Lestrange to Manchester and Glasgow - and do the same there. Pettigrew will coordinate the evacuation here."

They spent hours going over the details of packing, and which departments had to be near each other to continue operations, and which branches would use what safe houses, and how communications would be set up to minimize exposure. Then Snape's lieutenants separated, each to his or her assignments. Snape himself went to the Dark Lord with a detailed report of all they had discussed and would do.

It was late afternoon before Snape returned, exhausted, to Hogwarts. In all the time at Croydon, he had not once looked in to observe the packing of his own laboratory. He didn't have the heart.

Students were congregating in small groups around the lawn and in the entrance hall talking animatedly. At first Snape wondered about it, then he remembered it was Friday afternoon and they were free for the weekend. Then he remembered the fifth years had been taking OWLs and they would just have finished with their last exams. Proctoring OWLs seemed ages in the past but it had really been, what? yesterday morning? Part of Snape's brain was telling him he needed to inform McGonagall of something, and another part was saying that it was impossible, though Snape was not sure why. He was too tired to try to find out anything more, having had a total of six hours sleep in the last two and a half days. He made his way quietly to his rooms and lay down, attempting to clear his mind so he could think rationally.

Just as he was drifting off to sleep, a gentle rapping at the door roused him. Dragging himself from the bed, his head now throbbing, Snape opened the door. Dumbledore stood there, smiling benignly.

"Ah, Severus, you have no idea how relieved I was to hear that you had come back in apparent good health. When I returned this morning and found you had left during the night I was concerned, truly concerned. May I come in?"

"Certainly, Headmaster. I'm sorry." Snape stepped aside as Dumbledore entered. He was trying to remember why Dumbledore wasn't supposed to be there, but{\el}

"Are you all right? You look terribly ill. Here, sit down. Let me get you something." Dumbledore conjured coffee and a plate of sandwiches, insisting that Snape eat and drink before asking or answering any questions. The food helped, and Snape began to feel that his brain was working again.

"There. That's better. You're looking more like your old self already. Do you need to see Pomfrey? Did Riddle give you a bad time last night?"

"Bad time? No, I don't think so." Then it started coming back to him. "Something went terribly wrong last night, and we lost the whole upper echelon. Everybody. Except Bella - he brought Bella back. They're all gone. To Azkaban. That's why he put me in charge."

Dumbledore's silence was the silence of a man watching as his ball nears the cup at the end of a ninety-foot putt. "In charge?" he prompted after a moment.

"All the secret keepers are gone. We have to close down the branches{\el} headquarters{\el} and disperse all over Britain. I've been coordinating that. I{\el} Bella works for me now."

"Do you know all the places where your people are dispersing to? Where your next headquarters will be?"

"Yes, but{\el}" Snape stopped and stared at Dumbledore in horror. "You can't. You can't take them out. He'll know it's me. He'll kill me. He'll do worse than kill me. Only three of us know - him, Bella, and me. You can't do this to me!" Snape rose to his feet as he spoke looking around him for a way out of the room, out of the whole situation.

"Easy Severus. Easy. I see you are distraught from the events of the last couple of days. I assure you I shall do nothing that would increase the danger you are in. Sit. Sit down. Good. Now, I have a question I must ask you, nothing about Riddle or your headquarters, so do collect yourself, please."

Snape took several deep breaths and nodded.

"Excellent. Now, do you know where Professor Umbridge is? Harry says he last saw her in the forest, in the company of several of the centaurs."

"Umbridge{\el} Yes, she's still with them. They consider her a renegade for challenging the lead mare, and they're holding her until McGonagall returns."

"Ah. I should be able to handle that."

"Professor? What happened last night? The Dark Lord's people have been taken to Azkaban, and Bella said one of{\el} our people was `lost.' He didn't give more details, and I couldn't ask him or Bella."

"I thought you knew. Harry and his friends went to the Department of Mysteries and were trapped by Death Eaters. There was a fight in which the students performed very well, then members of the Order arrived. We suffered injuries, but{\el} Sirius Black was killed. The prophecy was destroyed. Riddle will never hear it."

"Killed? Sirius Black was killed?"

"I am afraid so."

"He{\el} I{\el} He should have stayed at Grimmauld Place. It was the logical thing to do. I told him{\el}"

"Yes, I know. Lupin told me you'd talked to him and suggested he stay away from the Ministry."

"He wouldn't listen. He had to help Potter."

"That is correct. No one could dissuade him."

Snape sat for awhile, looking at his hands. "Who killed him?"

"Bella Lestrange."

"I see." They were silent for a few moments. "Headmaster, do you need me for anything else? I am really very tired."

"That is all right, Severus. You get some sleep. I have a couple of things I have to do now, in any case. We can talk again tomorrow."

Dumbledore left, and Snape returned to his bedroom.

\sbreak

\emph{He looked into the window at the little dog. `I want it, Mum,' he said, but his mother cuffed him. `They make you weak,' she said. `Anyone who's ever owned one became weak.' Toby came out then with the puppy in his arms. `Every boy needs one, 'Leen,' he said. `You just got to beat 'em now and again.' Eileen struggled to keep the dog away, even though Hagrid was fighting against her, and in the end Eileen won. Toby gave the dog to Sirius.}

\emph{He had to get to the fifth floor because Umbridge moved his Potions class to the fifth floor on account of the OWLs. The staircases kept shifting, though, and he knew he was hours late. There was a boat to take him across the swamp, rowed by Filch, but halfway across he realized it was really Lily. `You were supposed to bring me a puppy,' she said, so he told her Sirius had it. `Well if you can't give it to me, maybe he can give it to Harry,' she replied.}

\emph{The boat landed, and he had to get out because his arm hurt. There was a metal detector at the door into headquarters, searching for the dogs that everyone was trying to bring in. He didn't have a dog, so he got through all right, but they stopped Sirius and sent him to Azkaban because of the dog.}

\emph{He was standing in front of Imperial College. `You can't get in without a dog,' they told him. He was desperate, because Phina was already inside, cradling a little black puppy dog in her arms. `It's easy,' she called to him, `just relax and open your mouth a little and let it happen.' Just then Sirius came up, and he was holding a dog, too. Sirius gave the dog to Potter, then walked into the college and kissed Phina on the forehead. Toby closed the doors. `You're not qualified,' was the last thing he said.}

Snape lay staring up at where the ceiling would be if it were light enough to see the ceiling. \emph{It must be after midnight. Maybe around two in the morning.} He was most intensely aware of his bitter disappointment, as fresh now as the day he first realized he would never enter Imperial College. Then snippets of the dream came back to him, and he tried to assign a rational explanation to the image of Phina and Sirius entering a scientific college when neither knew the least thing about real science.

That was when Snape remembered that Sirius Black was dead - he had a vague recollection that it was Dumbledore who'd told him this. Black was dead. He should be happy, but he wasn't. Instead he felt empty. He closed his eyes and conjured the image of Black's face, so raw with passion and violence. So much like Bella's face, yet so different.

No, he wasn't happy that Black was dead. He didn't feel anything. Just empty. The feeling you get when someone tells you about a car that crashed into a ditch without the driver having a chance to step on the brake. That feeling. Powerless. Empty.

Bella. It was her fault. She'd killed Phina by accident, and now Snape was certain she'd killed Black on purpose. Her own cousin. Not that blood meant anything to Bella, not unless it was flowing across the pavement.

Reckoning that he'd had somewhere close to eight hours' sleep, and no longer tired, Snape rose and dressed, then slipped along silent corridors to the entrance hall and thence outside. He was heading for the steeper paths that fringed the cliff face and led down to the lake shore. The newly crescent moon was gone now, leaving the world starlit and treacherous, but Snape's night vision was good, and he knew the way well.

Lily's rock was there, an unchanging beacon in a turbulent world. Snape settled on the grass beside it, as he'd done so many times, and watched the stars.

\emph{Did I love you, Lily? Sirius saw love as his willingness to face danger for your son. Maybe, back then when the world was young, and you were still alive, I saw danger in the same way. Even last year, when I left this place with the future veiled and uncertain, I still felt a little of the magic of danger - as if I could touch you again when the stakes were high enough. The magic's gone now. I guess as we get older, pain and fear become more real. The only rock I have to cling to now is duty, and sometimes that seems weak and brittle. It would help if I knew I loved you. I suppose if you have to ask the question, the answer is no.}

\emph{So in the end, Sirius was the one, of all of us, the most blessed. He met his fate with clear, open eyes, untroubled by doubt. He knew why he died, and he knew it was worthwhile. Was that how you died? Clear eyed, untroubled by doubt? I have so many doubts, and my vision is blurred.}

Dawn came early to the northern sky, for the solstice had crept up on them while Snape sorted through files in Malfoy's office a scant twenty-four hours earlier. Meditation is for the night hours, for solitude and the company of the stars. With daylight come labor and duty.

Snape rose and brushed grass blades and sand from his robes. Then he walked quietly up the steep path to the castle, almost ready for whatever the day would bring.

One of Snape's first tasks was to invite into his office the children of the Death Eaters who had been taken to Azkaban. Draco Malfoy and Vincent Crabbe were predictably accompanied by Gregory Goyle, while Theodore Nott stood a little apart from them. All of them were aware of what had happened, and Snape felt a little guilty about not speaking with them the previous afternoon, as soon as he returned from Croydon.

"Don't worry too much about your fathers," Snape assured them. With these four he didn't have to hide his dual life. They already knew. "The Dark Lord has indicated to me that Azkaban has lost its dementors. I'm not privy to the details, but they seem to have abandoned the Ministry and returned to him."

Nott began to tremble with relief, and Goyle put a hand on Crabbe's shoulder. Malfoy remained unmoving, though the tight lines of his face relaxed a little.

"What you do now," Snape continued, "is stay here. This is the most secure place until we find out how the Ministry is reacting to what happened. The whole organization is{\el} busy - you will understand that I can't give you details - and the rest of your families will be able to attend to their duties better if they know you're safe."

"Can't we help?" insisted Malfoy. "Can't we do something?"

"No. It's been the Dark Lord's wish since last June that we remain under cover. That order is still in effect. The best way you can obey it is to act normally and give our enemies no opening to attack us until we're ready. Do you understand?"

They nodded. It was the first time that Snape had spoken to them directly of the Dark Lord, and even Malfoy seemed impressed and willing to follow orders.

Breakfast was like entering a different world. The Great Hall was in an uproar, a condition caused by the end of exams, the approaching end of the school year, the removal of Umbridge, and the triumphant return of Dumbledore, who once again presided over the meal from his seat at the high table. As soon as Snape entered the Hall, Dumbledore beckoned him over.

"Thank you for your information yesterday. You will be pleased - well, maybe not pleased, but at least interested - to know that Dolores Umbridge is safe with Madam Pomfrey. It will be some time before she is in any condition to bother us further."

"That is good news, Headmaster. What about Hagrid?"

"He should be back later today. He'll have some explaining to do. Did the centaurs mention to you that there was a strange presence in the forest?"

"They did. A moving mountain, or something like that. What's it got to do with Hagrid?"

"His brother, or rather half-brother, it would appear. Hagrid has been trying to civilize him."

"I see. We have a giant on the grounds. You wouldn't be planning to put a nesting pair of dragons here as well, would you?"

"It is a thought, Severus."

Snape apparated to Croydon early in the afternoon. Most of the offices had been cleared out, and the movement in the corridors seemed more orderly than the day before, probably because everyone now knew that they had somewhere to go.

After clearing the next step with the Dark Lord, Snape began the process of signing out the different departments, first getting from each a complete inventory of what they were taking and then giving instructions on how they should maintain cover, and how they would be contacted when it was time.

By evening Bella and Yaxley were back. The last of the departments was checking out, and the skeleton demolition crew was removing partitions and returning the old building to its previous state. The only things that hadn't been taken out were Malfoy's files and the crates and boxes in the laboratory.

The four of them, Snape, Bella, Pettigrew, and Yaxley, appeared for the last time before the Dark Lord in that interview chamber. Snape presented the Dark Lord with the lists of safe destinations, who staffed them, and with what supplies.

"You have done well. Now find us a new center. We shall contact you to learn of your progress."

"Lord, how may we contact you at need?"

"You may not. What we shall do now is not for you to share. You will go to safe places, perform your tasks, and wait for our call."

"Lord," squeaked Pettigrew, "I have no place to go."

"Severus, you will provide a hiding place for Wormtail. Wormtail, you will assist Severus in any way he requires of you."

"Yes, Lord," both replied.

The Dark Lord was gone, and Snape was saddled with Pettigrew. Together they made their way out to the front entrance. "Wait here," Snape said, and went upstairs without waiting for a response.

One of the demolition crew followed Snape into the laboratory. "We've held off on this room until you approved it," he said. "We didn't want to damage anything."

"Thank you. I'll only be a moment. Do you think you might wait outside until I call you?"

The workman nodded and left, though Snape had the suspicion that he was deeply curious.

What happened next had been carefully prepared that morning by himself and Professor Flitwick. First, the boxes containing the bottles and jars of chemicals and potions ingredients were set to one side. They would remain as they were. It was the boxes of cauldrons and of glassware, of beakers and test tubes, that had to be reduced. That, and most of the equipment. The bulk, rather than the weight, was the problem.

Snape opened the first box of beakers and began using a shrinking spell of Flitwick's. The first beaker kept its size and was lined with a thin layer of special padding. Another beaker was reduced just enough to fit inside the first, and also lined. Successively smaller beakers nested into the first ones until he had seven condensed into the space of one. Then Snape began another nesting group. In this way, he reduced fourteen boxes of various containers down to two. Each box was seven times heavier, but not inordinately heavy.

The mistake many wizards made was to try to make things too small. The concentration of weight over a tiny amount of area tended to crash through floors and demolish staircases. By limiting the scale of reduction, and concentrating especially on boxes of empty vessels that contained mostly air, Snape was able to condense thirty-five cases into eleven. These he bound together and moved downstairs with a levitation spell.

"You can take out the lab now," he told the workman as he left.

Downstairs Snape deposited the cases next to Pettigrew. "Watch these," he ordered, and went next to Malfoy's old office. This was a totally different problem, since it was almost impossible to reduce a mass of paper to any appreciable extent and still have it light enough to transport.

Instead, Snape shredded the paper into boxes. It took up less space, and became illegible in the process. Later the individual sheets could be reconstituted with another spell. It was a combination that Flitwick was particularly proud of. Snape left the file cabinets for the demolition crew.

Rejoining Pettigrew, Snape directed the moving of seventeen boxes out of headquarters and apparated with the first seven to his home in Lancashire. Then he returned to Croydon, where he first checked the progress of the demolition, then joined Pettigrew to apparate together with the remaining ten boxes.

Although returned to its original state, headquarters remained invisible to the general public, since its secret keeper was imprisoned in Azkaban and could not undo the Fidelius Charm.

Once home, there was the problem of Pettigrew. Snape deposited him in the front room, then moved all the boxes to the storeroom next to his own bedroom. He then locked the room with powerful charms. Pettigrew, having spent most of the last fifteen years as a rat in a schoolboy's pocket, was generally proficient in elementary spells, but deficient in advanced ones. Snape was still taking no chances.

Returning downstairs, Snape faced Pettigrew. It was the closest contact the two had ever had in their lives. "I do hope you realize how I feel about this situation."

Pettigrew nodded, swiping his nose with a finger, for all the world like a giant rat cleaning its whiskers. "You don't want me. I'm intruding."

"Just so we understand each other. The hardest part will be the first week, since I have to be at Hogwarts. After that it'll get easier. One, you never leave this house except in my company. There are things about this muggle community you don't know, and a false step could ruin us. Two, you don't go upstairs. I find you've been snooping around in my home, and I'll take you down to the Royal Artillery practice range, have you blown to smithereens, and tell the Dark Lord it was an accident. Got it?"

Snape conjured a cot. "This is your bed. If you prefer, you can use the sofa. There's an extensive library that you have full permission to read. It might do you good. Food will be in the kitchen. I'll try to get back once a day to see that everything's going smoothly. This situation will last for one week. Think you can handle it?"

Pettigrew nodded again, somehow contriving to look more like a rat than ever. Trying to remember that this was not Pettigrew's fault, Snape apparated back to Hogwarts.

The next day was Sunday and, after having slept in, eaten a leisurely breakfast, spent an inordinate amount of time playing cribbage with Flitwick, and retired just before lunch to his office, Snape was once again headed for the Great Hall. The luxury of having two uninterrupted meals in a row was almost too much to bear.

It was also too much to hope for. Stepping out of the dungeons into the entrance hall, Snape was presented with the tableau of Potter, wand drawn, threatening Malfoy, Crabbe, and Goyle, all of them wandless, though Malfoy's hand was near his robes.

\emph{Does this boy never stop?} "Potter!" Snape yelled, freezing all four. "What are you doing, Potter?"

The answer was blatantly defiant. "I'm trying to decide what curse to use on Malfoy, sir."

\emph{The boy's had a rough week. Treat it like a normal infraction of the rules{\el}} "Put that wand away at once. Ten points from Gryff{\el} Ah, I see there are no longer any points left in the Gryffindor hourglass to take away. In that case, Potter, we will simply have to{\el}"

"Add some more?" McGonagall stood in the doorway.

Potter was forgotten at the sound of the well-loved voice. Snape moved forward to take her hand. "Professor McGonagall! Out of St. Mungo's, I see!"

"Yes, Professor Snape, I'm quite as good as new." She then thrust forward her carpetbag and cape. "You two - Crabbe - Goyle - here. Take these up to my office for me."

Having deftly removed two of the students, McGonagall turned to Snape, laughter just barely playing at the corners of her mouth. "Right then. Well, I think Potter and his friends ought to have fifty points apiece for alerting the world to the return of{\el} You-Know-Who! What say you, Professor Snape?"

"What?" It merely countered Umbridge's depredations, but Snape protested for form's sake. "Oh - well - I suppose{\el}"

"So that's fifty each for Potter, the two Weasleys, Longbottom, and Miss Granger."

Snape raised his eyebrows in mock disbelief.

"Oh - and fifty for Miss Lovegood, I suppose," said McGonagall. "Now, you wanted to take ten from Mr. Potter, I think, Professor Snape - so there we are{\el}" The colored baubles moved from section to section of the house hourglasses. "Well, Potter, Malfoy, I think you ought to be outside on a glorious day like this." And with that the confrontation was over, Potter heading out the front door, and Malfoy back to the Slytherin common room.

"How are you, you old tigress you?" asked Snape as the students vanished from the entrance hall. "Is St. Mungo's still standing."

"It was when I departed. I thought I might leave it there, just in case I scraped a knee or got a splinter from a student's wand."

Snape offered McGonagall his arm, and together they went in to lunch.

The year ended, as it always did, with the feast at the end of the week. Snape, who had visited Spinner's End faithfully every day, was thoughtful enough to take some of the food back to Pettigrew so that he could celebrate, too. Beyond that, Snape had no idea what he was going to do with the man while waiting for the Dark Lord's summons. Unless, of course, he found a way to quiz Pettigrew about the events leading up to the disaster at Godric's hollow.

The morning after the feast, the students boarded the Hogwarts Express and returned to King's Cross Station. The teachers, breathing great sighs of relief, straightened their rooms, locked their doors, and went home for the all too brief holiday. This time their departure was tinged by worry about what the future would bring, with the confirmation that He-Who-Must-Not-Be-Named was once again on the loose, but freedom from school was freedom from school, and little could spoil the holiday atmosphere.

Snape expected no vacation. First and foremost, he was now living with Peter Pettigrew, a damper on any occasion. Then, he was expecting the Dark Lord's summons at any time, and had to work to find a new headquarters building before that happened. Finally, Dumbledore had asked him to be on twenty-four hour call. The headmaster implied that he would be searching for something dangerous, and he depended on Snape to be ready to assist him.

So the vacation that was no vacation started, with the Dark Lord in hiding, and Snape more powerful and at the same time more vulnerable than he'd ever been in his life. He was not looking forward to the next school year.


