% A Difference in the Family: The Snape Chronicles (Rannaro)
% The Middle Years

\chapter{Shifting Sands}

\subsection{Wednesday, August 5, 1981}

On Wednesday morning, Flitwick wandered into the Great Hall for breakfast. McGonagall, always the first up and the first downstairs - although, as Flitwick often teased her, this might have something to do with being deputy headmistress with rooms on the first floor instead of up near Gryffindor and Ravenclaw houses on the seventh floor with Flitwick - saw him and waved him over to sit with her.

"We haven't had a chance to chat since the lightning bolt struck, Filius. Do join me for a spot of gossip."

"With pleasure, dear lady," said Flitwick, climbing onto the bench next to her and reaching for eggs, bacon, toast, and tea. "Another shock to your system, I take it. You didn't know about Monday's surprise?"

"Know? I am seriously considering accosting Albus in a crowded corridor, accusing him of trying to drive me from the school through public humiliation, and resigning after an emotionally charged and highly dramatic scene that will shame him before his entire staff."

"Why don't you?" Flitwick said, sipping his tea. "I for one would love to see it."

"Because the scoundrel would only twist it to his own advantage. But you would think he'd at least give me a hint."

"I wish he had, Minerva, because then you would have given me a hint, and I could have told Pomona."

McGonagall stared down at him, a look of feigned horror on her face. "Filius Flitwick! Are you implying that I would spread information of a confidential nature imparted to me in official capacity by the headmaster of this school?"

"Why not? You've done it before." Flitwick suddenly stood up on the bench so that his head was now above McGonagall's. "There's Master Snape. Let's get him in on this."

"Well, I'm not sure{\el}" McGonagall started, but Flitwick was already waving and calling Snape's name.

Snape came over and was pleased to join them. Flitwick let him start eating then asked, "How do you feel about having an auror in Dark Arts?" Black eyes glinted up, then back down at the plate. \emph{Are you nervous about something?} Flitwick thought.

"I suppose under the circumstances it's a wise precaution," Snape answered. "We do live in dangerous times. Best to be prepared."

"I must say, though," said McGonagall, "that I don't envy you at all. Aurors in the school."

"Why should that affect me more than you?" Snape's voice reflected some of his apprehension.

"You're head of Slytherin house! What are you going to do the first time that Scrimgeour person asks to interrogate the students of your house about their parents and their parents' colleagues?"

The look of shock on Snape's face told Flitwick that he hadn't considered this aspect of the situation at all. Flitwick quickly added his own opinion. "I'll tell you what you do, Master Snape. You go right to Professor Dumbledore. You handle the day to day matters of your house, but something that affects school policy goes right to the headmaster. Or to the deputy headmistress," he added slyly.

"There you are," said McGonagall. "I've barely finished my breakfast, and he's heaping me with problems. I've half a mind to suggest that Albus give the position to you and leave me in peace."

There was a lull in the conversation, then Snape said, "I did have a question. It's more of an administrative matter. I need to order supplies, but I don't know how to go about it. Are there forms to fill out?"

"You just make up a list and give it to me," McGonagall answered, only to have Snape pull several sheets of parchment from his robes and lay them on the table. She glanced over the list, written in small, rather cramped handwriting. "You need all of this?" she gasped.

Snape looked embarrassed. "I know it's a lot, but the stores are low, and I don't see how I can get through the year without{\el}" He stopped as McGonagall began to laugh. "I'm sorry. Have I done{\el}"

"No, no," said McGonagall. "It's just that Slughorn was never organized enough to ask me for more than half a month's supplies at a time. Are you telling me this will last you until June and you won't bother me again all year?"

"I think so. I don't want to make any promises, though."

"Laddie, I'm softening to you already. If you gentlemen will excuse me, I'll leave you to talk. I'm off to take care of administrative matters." McGonagall rose and swept from the Hall, leaving Flitwick and Snape at the table.

Flitwick waited until McGonagall was gone, then leaned across the table. "Truth be known, I've been wanting a private chat with you since Saturday. You are the repository of several secrets that have been eating at me for years." Snape's eyebrows shot up, but Flitwick just chuckled. "Two words - green hair. How did you do it? If it's a professional secret, just tell me to mind my own business."

Snape actually smiled. It was a timid, shy smile, but Flitwick was pleased that the young man seemed to be relaxing. "I'm afraid I'll disappoint you, Professor. That one wasn't a charm. It was a potion."

"Even more mysterious. Feeding them a potion in the middle of the Hall when you weren't even there. Now you have to tell me."

"It was a two-part potion. I put the second half in the morning pumpkin juice. The first half was in a box of candy I owled to myself. They took the candy from me, then drank the pumpkin juice less than twenty-four hours later. Green hair."

Flitwick laughed and clapped his hands. "The beauty is, if they hadn't bullied you and taken the candy, nothing would have happened, right? Dumb Gryffindors!"

"They wanted to blame me for it to Professor Dumbledore, but they couldn't without admitting what they'd done."

"Why did you do it?" Flitwick regretted the question at once as he watched the humor in Snape's face fade.

"They{\el} did something to me. If you don't mind, Professor, I'd rather not talk about it."

"That's all right. I don't need to know. I thought it might have been retaliation. Now I have another word for you - bats."

That got them into a discussion of the physiology of vocal cords and the frequency of sound waves, and then they rose from the breakfast table to return to their classrooms and their work. It left Flitwick with a lot to think about, though. \emph{He did that when he was thirteen. Thirteen, and he knew all that about sound waves! What does he know now? And why on earth did the Sorting Hat ever put him into Slytherin? He should have been in my house!}

Severus went from the Great Hall to McGonagall's office to ask for the files on the current Slytherin students. He hadn't intended to start reviewing them this early in the month, but something they'd mentioned at breakfast was now bothering him greatly. McGonagall was pleased to give him the hundred files for his sixty students and the incoming first years. They were in two boxes, and he levitated them down to his office.

It didn't take two minutes before his worst fears were confirmed. There were Death Eater children in Slytherin house, maybe as many as fifteen of them. Their parents worked in the clinic, in supply, in operations. He'd taught spells and self-defense to fathers, mothers, uncles, aunts, cousins, and in one case an older brother. Before the welcoming feast was over on September first, all Slytherin house would know he was a Death Eater.

Flitwick's advice was good, though. This wasn't just his own problem. It was Dumbledore's problem, too. Severus left the dungeon and climbed the stairs to the top of the castle and the entrance to Dumbledore's office. He wasn't sure how to knock, but that was apparently taken care of by some system or spell, for as he stood there the stairway began to move, and he went up to speak to the headmaster.

"I would not be too concerned, Severus. I assumed that many of your students would know as soon as they wrote home to tell their parents who their teachers were. That is of little importance, since those same parents would caution them to secrecy. I do see where the presence of Professor Scrimgeour might complicate things. I would in any case never countenance the interrogation of students."

"One of the things that bothers me is that this didn't occur to me before. How could I not have realized it?"

"My dear boy, you compartmentalize everything. Your brain has been sorting information into sealed sections since you were a baby. You just do not equate Hogwarts with the outside world. They are in separate compartments. You need to consciously focus on these things for your own safety."

"I am going to have to go down to London soon to report. What should I tell him?"

"There is not a lot to tell. About Scrimgeour, of course, and Moody. And the fact that your cover is not secure. He might even caution the parents before the students arrive, so that there will be less gossip."

"I hadn't thought of that. It's a great idea. Professor McGonagall says we get one day a week off. What's my day off?"

"During August, you may come and go as you wish. Once the school year starts, your free evening is on Thursdays."

Thursday turned out to be too far in the future. Almost immediately after Wednesday lunch, Severus's left arm began to sting. It was nothing urgent or really painful, just a gentle nudge, but he went directly to Dumbledore.

"He's calling. I should go to London."

"When?"

"Right now if I can. The longer I delay, the better my excuse will have to be."

"All right. Let me walk you to the gate."

They didn't say much, but Severus appreciated the gesture of concern. As soon as he was through the gate, he apparated to Pendle, and from there to London. Direct apparations were traceable, and he wanted the Dark Lord to know he was being cautious.

He was expected. As Severus signed in, the porter said, "You're to go straight through. He wanted to know when you arrived."

There was no one else in the interview chamber, and the light was soft and diffuse - a conversation rather than an interrogation or punishment. Severus relaxed. The Dark Lord sat in the center and beckoned. "Stand before us," he said.

That he didn't have to kneel was also good. Severus advanced and the Dark Lord searched his eyes. "Tell us now of Hogwarts," the Dark Lord said.

"The Ministry has sent an auror to be a teacher there," Severus said at once, the most important information having to come first.

There was a hiss, then the Dark Lord spoke again. "Continue."

"His name is Rufus Scrimgeour. He came early Monday morning with another auror named Alastor Moody. Moody's returned to the Ministry, but Scrimgeour's still at Hogwarts. I think he plans to commute, though - arrive each morning and return home in the evenings. He's been given the Defense against the Dark Arts job. The other teachers don't like his being there. They're afraid he'll take advantage of his position to investigate them or question the students. They're all, including Dumbledore, opposed to the idea of interrogating students. I don't think they trust the Ministry."

"This discord among our enemies is good news. We shall try to minimize this Scrimgeour's effectiveness. Continue."

"Lord, I am concerned about the security of my own position and my ability to serve you there. Both Scrimgeour and Moody seemed suspicious of me as soon as they heard my name. Moody asked if I knew Dolohov, and said that Dolohov knew me. I took that to mean that Dolohov has been giving the aurors names since he was sent to Azkaban, though that may not be the case. I've also checked the school files and find that several of my future students are from families that serve you. They'll know I'm one of your servants, and word may spread through the school."

"We understand your concern. Our people here will instruct their children in discretion. We shall also investigate this business about Dolohov. It is displeasing to us that he may have divulged our secrets. You must move with caution. As you know, the aurors have been given authority to use Unforgivable curses against our people. You may be facing the Cruciatus curse and Veritaserum."

Severus's eyes widened with the recollection, and he allowed his fear to wash through him. Dropping to his knees, he said, "Lord, I fear my own weakness. I'm not one of your operatives, a soldier in your army - I'm a potions maker, a spell caster, the humblest of your servants. Please, Lord, let me return here where I can serve you without fear of being forced to betray you."

"We desire that you remain at Hogwarts. Your loyalty is of great value to us. Your information is of greater value. Be cautious. Be discreet. Is there something that will minimize the risk of your detection?"

"Once the students arrive, I'll only be allowed off the grounds one evening a week. I've found that this will be Thursday evenings. If I'm summoned on any other day, it will look suspicious. Also, I'll need to be able to tell people what I did with my free time or after a while that will look suspicious, too."

"Come to us then on Thursdays. Your reports should not take long. Then you will have time to create a story for your{\el} colleagues. What reason did you give Dumbledore for coming to us today?"

"I told him I had to go to Diagon Alley to be sure the cauldron shop and the apothecaries had all the necessary equipment our students would be buying, and that the books had arrived at Flourish and Blotts."

"Then you must do what you have told him you would do. Go now. You need not come tomorrow if there is no news. We shall expect you the following Thursday."

It was over. Minutes later Severus was back out on the street in the August sunshine with an entire afternoon to spend in London.

One of the first things Severus did in Diagon Alley was send an owl to Hogwarts telling Dumbledore he would be in London for several hours and that everything was all right, then he went to the cauldron shop and the apothecaries as he'd told the Dark Lord he would.

The business in Diagon Alley took but a few minutes, after which Severus stopped at Barclay's bank to get some muggle money. He'd had the account for several years, since the death of his muggle grandmother, and the sum he'd accumulated there was quite respectable. He didn't withdraw much, enough to buy some books and get a meal.

His first stop was Foyle's bookstore, only a short distance away from the Leaky Cauldron, at least as Severus reckoned distance. In the past he'd loved to just browse through floor after floor of books on every possible topic, but this time he had a purpose. He was looking for a cookbook, one with a recipe for eggs Benedict. This wasn't hard to find, Severus being forced rather to chose from a wide selection of books. What he ended up with, in fact, were two books he'd not come for. The first was a simple instruction book on kitchen terms and basics, the second a two-volume boxed set on the history of food with an accompanying volume containing menus and recipes, neither of which had anything about eggs Benedict.

On the way out of the store, Severus's eye was caught by the magazines, splashed with pictures of royal pomp and circumstance. The Prince of Wales had finally married, at the end of the previous month, and Severus had been too concerned with Death Eater affairs to notice. The photographs reminded him of his younger self leaning out a dormer window of the Blacks' London residence watching guests arrive in formal attire. He decided to buy one of the magazines, then noticed the picture on another.

It looked liked a funny little airplane, with stubby wings jutting out from its tail, but Severus knew what it was. It was an orbital spacecraft, a spacecraft meant to leave earth and reenter, and then be used again. He flipped through the magazine to the article. \emph{April twelfth. The Americans sent the shuttle up on April twelfth and I missed that one, too.} Severus purchased both magazines.

This gave him an idea. Returning to the Leaky Cauldron, he waited for several minutes to speak to Tom, the barkeep. "You're the tutor chap, aren't you?" Tom said when he got to Severus. "Haven't seen you come in here for quite a while."

"I haven't been here," Severus admitted, "and I won't be around much in the future either. I've got a job up at Hogwarts."

Tom nodded his head, looking pleased. "That's a piece of luck for you now, isn't it? Good position, a little security. What can I get you?"

Severus decided to splurge. "A glass of mead," he said. "And I'd like to ask you something else as well."

"Go ahead," said Tom.

Taking a sip of his mead first, Severus plunged in with what was sure to be an odd request. "If I had a muggle newspaper delivered to the Cauldron every day, could you send it up to Hogwarts by owl?"

"What do you want with a muggle newspaper?"

"These days you have to avail yourself of all sources of information."

"You doing this for Dumbledore?"

"I'll be passing it on to him."

"Sure, as long as you're paying for the service."

That done, Severus had to arrange for delivery, buying a copy of the Guardian and then apparating to their offices, but it was something he was able to accomplish in about half an hour.

It was now early evening. Severus wandered through the streets around Leicester Square until he found a little restaurant that seemed interesting, but not too unusual. He didn't want to eat too much strange food on his first excursion. He sat at a corner table, observing the one table with other customers without actually staring at them, and checked the menu, finally ordering something called beef Stroganoff.

The dish was delicious, especially the sour cream sauce, and Severus took out his cookbook to find what was in it, discovering to his surprise that the book included tomato paste in the recipe, but there was no hint of tomato in the food he was eating. Not certain what to do, but intensely curious, he finally asked the waiter, showing him the cookbook. To his great surprise, the chef came out to talk to him.

"I didn't mean to bother you," Severus apologized.

"That's all right. It's early. We're not busy yet." He explained how different chefs prepared things to their own tastes and that as long as certain basics were there - in this case beef, onions, mushrooms, sour cream, and dry mustard - sliced and cooked by a certain method, there could be infinite variations on beef Stroganoff.

Severus returned to Hogwarts fired with the magic of cooking, every bit as complex and exact - and yet how much more personal - a science as potion making.

"There you are!" called Sprout as Severus passed the open door of the teachers' staff room, just to the left of the steps leading down to the dungeons and his own rooms. "We were wondering where you were. Is everything all right?"

Severus came over and stood in the doorway, thankful that the twin guardian gargoyles didn't challenge him. "I had to check a couple of things in Diagon Alley and thought I might make an afternoon of it."

"And evening," said Sprout. "Looks like you bought something."

It was an invitation to come in and open the bag, so Severus did, showing them the two cookbooks, the magazines, and the copy of the Guardian. "I should start getting the newspaper in a couple of days," he said.

"Well, if that's what you like to read, dear," responded Sprout, picking up one of the magazines. "Who's this lovely couple?"

"He's the son of the Queen," Severus explained. "Just got married last month."

"So this is fancy muggle clothing. You know, it's quite elegant in a way. Minerva, look at this blue gown."

"What's this?" Flitwick asked, looking at the pictures of the Columbia.

"It's a scientific vehicle. It goes into space."

"Didn't know you were interested in things like that."

"I used to follow all the moon shots when I was a student." Severus noted that Flitwick seemed not to understand, so he elaborated. "The muggles in America were sending rockets to the moon. People were walking on the moon."

"How clever. Was it cheese?"

"Sadly, no. Just rocks and dust."

Flitwick glanced over at the two women, who were examining and commenting on the clothes in the other magazine. "Don't mean to offend, but word has it you grew up in a muggle family."

"Sort of," Severus admitted. "My mother stopped using magic at home, and my dad was a muggle."

"I don't mind telling you it can get boring here in the evenings. Slughorn was no fit company for anyone but himself, and I don't always share the ladies' interests. While Mullein was here we had interesting conversations almost every night, but now sometimes we do, and sometimes we don't. Futhark comes down from time to time, but all he wants to talk about are runes. And when those two, Pince, Pomfrey, Hooch, and Trelawney get together{\el} well, I'm a little lost. What do muggles do for entertainment?"

"My dad and I used to play cards. Cribbage mostly."

"What's that?"

"It's a two player card game where you peg points according to what you hold in your hand. It's like a race to see who can go around the track on a board first. The math is simple, but the combinations can be complex."

"Could you teach me this game?"

"I'd love to. I haven't played a cribbage game since{\el}" Severus paused, then went on. "Well, not since my dad died. Hold on. I'll get the board."

Picking up everything except the magazine with the wedding photographs, Severus hurried to his rooms and collected the cribbage board with its pegs and deck of cards. The rest of the evening was quite pleasant, showing Flitwick how to cut for deal, who got the crib, why thirty-one was twice as good as thirty, how a pair gave you two points but three of a kind gave you six, why it was important who counted first, and why nineteen was the lowest hand you could have.

And then, in the perfect example of beginner's luck, Flitwick skunked him. Twice.

They went to bed after midnight.

\subsection{Thursday, August 6, 1981}

After breakfast the next morning, Professor McGonagall called Snape over to speak with her before he went to his office. "Yes, ma'am?" he said, smoothly and politely as he approached, all respect and diffidence.

"Now that you're finished with those supplies you were working so hard at, I thought I might show you around the school - I can tell you things you have to watch out for, explain some of your duties, and show you places the students never see."

"I'd appreciate that very much, ma'am. It's kind of you to spend so much time on me. When would be most convenient for you?"

"I thought perhaps in an hour. Would you meet me at nine in the entrance hall?"

"With pleasure, ma'am."

McGonagall watched him go, smooth and quiet. Smooth. That was the perfect word for him. \emph{You got to Flitwick last night with that card game,} thought McGonagall, \emph{and you'll find a way to Sprout soon enough, I can tell. You're trying to get to me by buttering me up, but you'll find I don't fall so easily. You may not be as bad as I thought, but I'll still wager you're no saint either.}

When McGonagall left her office and walked to the marble staircase at nine, Snape was already waiting at its foot. "Come up with me, then," she called. "We'll start at the top and work our way down."

McGonagall talked as they climbed the stairs. "One of your most important duties, outside of teaching, of course, is to see the children don't get into trouble. Curfew is our biggest weapon, but you'd be amazed at how creative the little darlings can be. Fortunately, we haven't had a pregnancy in the last few years, but that's due to constant vigilance."

There was no response from Snape, so McGonagall looked behind her to find that he was blushing again. She adopted a stern face. "Surely you knew as a student that your classmates were engaged in extracurricular activities? Well, it's your duty to break them up. We owe that to their parents."

"You mean I have to interrupt{\el}"

"You have to hunt them down, chase them out, and deduct points from their houses. Be ruthless." She didn't ask if Snape had ever snuck off to a hidden part of the castle with a girl. She didn't have to. The look on his face was answer enough. \emph{You're more innocent than I thought, laddie. At least about some things.}

"At night, Flitwick is responsible for the seventh floor - Gryffindor and Ravenclaw. Sprout handles the ground areas - Hufflepuff and Slytherin. Dumbledore and I check in between. You help us, but you also help Hagrid with the exterior areas. Filch takes over after eleven and roves. By eleven you're usually free to go to bed, since the prefects should have accounted for everyone in their houses by then. In an emergency, the other resident staff are Trelawney, Futhark (though not on weekends), Hooch, Pince, and Pomfrey, but they don't have regular patrol duties."

Every floor had a small staff washroom with an adjoining rest area. "Just in cast you suddenly feel that if you don't get a moment of peace and quiet you're going to commit murder. And the children will drive you to that point from time to time. The key to survival in the jungle is knowing where your safe areas are."

"I never realized these existed," Snape said when McGonagall showed him the rest area on the sixth floor.

"Of course not. They're here to allow us to escape from the students. What use would they be if the students knew where they were?"

The fifth floor had the storeroom. "Anything you want to put away here that you'd like on the grounds, but don't want to have cluttering your room, you can put here." McGonagall showed Snape his own store area, which so far held just the boxes and bags he'd carried his things in. "And if there's something you need, we have extra furniture here as well." The whole back end of the store area was filled with chairs, tables, desks, bookcases, even a couple of beds.

The teachers' bathroom was on the third floor. It was a large, elegant room faced in marble with a great rectangular tub, a little like a small pool, sunk into the floor. Around the tub were faucets that provided water and bubble bath of different temperatures and fragrances. Huge towel racks held warm towels. A large window looked out over the lake.

"Most of the teachers have smaller tubs, sinks, and basins in their own rooms," McGonagall said, "so we use this only when we feel the need for some luxury, but Slughorn was in here almost every day. He never could get enough luxury, though I understand, too, that the Potions rooms are the smallest and coldest in the castle, so there was some excuse for it."

It was fascinating to watch Snape's reaction to the bathroom, for he seemed almost frightened by its grandeur and openness. He touched the towel rack with tentative fingers, but made no effort to explore further, and when McGonagall showed him the lockers where he could put his clothes while bathing, he began to blush furiously, his embarrassment so acute that McGonagall felt sorry for him.

At lunch, McGonagall sought out Dumbledore. When the two of them sat together in one of the corners of the Great Hall, the others understood that they were discussing school business and left them alone.

"Bee in your bonnet?" Dumbledore asked.

McGonagall was watching the other side of the hall, where Snape had come in with the cribbage board and cards, and he and Flitwick sat down to play. Turning, she realized that Dumbledore knew she'd been observing them.

"Is there something I should know about Professor Snape," she asked, filling her plate and beginning to eat. "I mean, is there anything wrong with him that could affect his teaching or the operation of this school?"

"Whatever do you mean, Minerva? Has Severus said or done something amiss?"

"Done? No. Said{\el} it's more what he doesn't say. And what he doesn't do. He's been here six days, eating with us, joining us last evening in the staff room, and he hasn't said one word about himself outside of his job here and buying books yesterday in London. And that he played cards with his father. Did you know he's been avoiding Scrimgeour? Just a few minutes ago he was coming to the Hall, saw Scrimgeour, and walked back into the dungeons before Scrimgeour could see him."

"Anything else?" Dumbledore appeared quite serious, but McGonagall could hear the smile in his voice.

"In addition to that, I do not believe I have ever met a more painfully prudish person in my life. You should have seen him, Albus, when I talked about stopping students' trysting, or about using the staff bathroom. It was all very straightforward and matter-of-fact, but I swear he was about to sink through the floor with embarrassment. It isn't natural. There's something wrong there."

"I would prefer not discussing anyone's private affairs, though I can see how you might be concerned for the school. Let me assure you that he will not be a problem."

"Are you so sure?" McGonagall's voice had dropped to a whisper, even though none of the other teachers was near. "You didn't see him, Albus. I swear it was abnormal for a young man of his age."

Dumbledore sighed. "This is in strictest confidence, Minerva, headmaster to deputy headmistress. I shall not go into detail, but prior to his parents' deaths, Severus's home life was sufficiently unpleasant that it left scars, and I am not speaking of emotional scars, though I am certain those are there as well."

McGonagall stared at Dumbledore in horror, forcing herself not to glance across the hall at Snape and Flitwick. "That wee bit-bit of a thing?"

"Indeed. Before he came to us. I discovered it in his second year. He managed through seven years at Hogwarts to avoid any situation where someone else might see the scars. I would not be surprised if he does what he can to avoid seeing them himself. I hope that allays some of your concerns."

McGonagall nodded, for if what Dumbledore said was true, it was surprising that Master Snape had coped as well as he had under the social pressure of a school like Hogwarts.

"Good," said Dumbledore. "Now, if you will excuse me, Minerva, I have some things to attend to."

McGonagall sat alone after that, thinking. \emph{It was the openness and sense of exposure, poor lad. No wonder he was uncomfortable. It would explain the lack of girlfriends, too, the shying away from physical intimacy. And why he's reluctant to talk about himself or his family.} She felt her heart swell with maternal protectiveness. \emph{And to think that I suspected him of more sinister motives. Minerva McGonagall, you should be ashamed of yourself!}

Getting up from the table, McGonagall crossed the hall to return to her own rooms, pausing as she did so by the two playing cribbage. She watched the game for a few minutes, then smiled as she asked, "Who's winning?"

August passed quickly. Severus received his supplies and spent a pleasant couple of days putting them away, needing more cabinets from the storeroom on the fifth floor in order to have room for all of them. Desks were cleaned and arranged, equipment set up, and lessons prepared. His office, too, was in order, and he brought books from home for the bookcase. On one of his weekly trips to London, he discovered a new series of murder mysteries, the fourth volume only just published, that set him researching the twelfth century to find out how much of the background was true.

Severus was also getting to know his students, or at least as much as one can know from a file. He knew their classes and their academic abilities, who was on the Quidditch team and who got detention nearly every week, and which parents wrote constantly asking for special treatment for their children. He was beginning to look forward to the start of school.

Even the other teachers seemed to like him including, unexpectedly, Professor McGonagall. Indeed, if it hadn't been for the brooding presence of Rufus Scrimgeour, Severus might almost have thought of his life as happy.

"Do I frighten you, Professor Snape?"

"No, sir."

"Then I would appreciate it if you would look at me. I realize these interviews are unusual and outside the normal routine of Hogwarts, but I find it, frankly, irritating to have to talk to someone whose face I can't see."

"Yes, sir."

Severus looked at Scrimgeour, not exactly into his eyes, but a little past his left ear at the picture of the Minister of Magic on the wall behind him.

"Your full name is Severus Snape?" It may or may not have been intentional, but Scrimgeour sounded like the police homicide detective in a television program Severus had seen as a child.

"Yes, sir."

Scrimgeour noted the question and its answer on a piece of parchment. "Parents?"

"Tobias Snape and Eileen Prince." Severus paused, then added, "Both deceased."

"You're a half-blood then." Scrimgeour seemed to relax a little. "Not exactly top drawer - for the other side, I mean."

"No, sir{\el} uh{\el} yes, sir."

"How long have you been teaching at Hogwarts?"

"This is my first year. I was hired at the beginning of this month."

"Aren't you a bit young for a Hogwarts professor? Normally Professor Dumbledore requires more experience."

"I understand Professor Slughorn retired rather suddenly. You'd have to ask Professor Dumbledore about that, though. I really don't know myself. But I did have an Outstanding on my Potions NEWT, and I've been tutoring since I was thirteen."

"That's what Dumbledore said. I understand it's the only work you've had since you graduated. Could you give me the names of some of your pupils?"

"Names?" Severus said. "Why would you need their names?"

"We just want to be able to verify your statement. It's routine. We might not even contact them. It depends on the Ministry, really. I just need them for my report."

"I'd really rather not give you any names, at least not until I've had a chance to contact people and ask permission."

"How many pupils are we talking about?"

"I'm not sure."

Scrimgeour looked up from his parchment. "Come now. It was just a couple of weeks ago that you were seeing them regularly and collecting payment. Just run through the list in your mind and give me a number."

Severus looked down at his hands. The problem was, of course, that the tutoring hadn't been in Potions - it had been in self defense. And the pupils weren't paying him - the Dark Lord was. Anything he told Scrimgeour could be proven false. What was the penalty for lying to an auror conducting an official investigation?

"I'm sorry, sir. I've never been in a position like this before. I'd like to help, and I know I'm supposed to answer your questions, but I also have a responsibility to my{\el} my clients. I'd appreciate it if you could give me some time to talk to them, or at least ask for advice on my conflicting duties{\el}"

"You want to talk to a lawyer? I'm conducting a routine check into Hogwarts personnel, and you want to talk to a lawyer?"

"No. No, that's not{\el}" Severus felt his face paling and hoped Scrimgeour didn't notice. "Just, maybe Professor Dumbledore. If I could speak with Professor Dumbledore{\el}"

"That's all right, Professor Snape. I don't need to ask any more questions. I'll just note for the record that in a routine interview you were unwilling to provide information. I'm certain no one at the Ministry will even notice. You may go now."

"Yes, sir. Thank you, sir."

Severus rose and left the Dark Arts office. His hands were trembling slightly, and he felt weak. \emph{I need to learn to face times like that. I need to have the answers ready. How do I know the answers if I don't know what the questions are going to be?} He returned to his own rooms, thinking of what he might have said, should have said, already preparing for the next time.

He went straight to Dumbledore.

"I think he knows. I'm sure he knows. It was like a cat playing with a mouse. Dolohov. Dolohov told them. That's what the other one said, the one that went back to London. He said Dolohov knew me."

"Calm down, Severus. This cannot have been the worst of your experiences. After all, you have faced down Voldemort himself{\el} Oh, dear. I am sorry. Does it hurt badly?"

"Not terribly. It's a little like an electric shock."

"How would you know what an electric shock feels like?"

Severus paused in his pacing and glanced over at Dumbledore, sitting at his desk in the tower office. "I stuck a fork in an electric outlet when I was five." He smiled a little at the memory. "Mum had hysterics, but Dad thought it was funny. After he made sure I was all right, of course."

"Such a wealth of experience you have, Severus, growing up in the muggle world. I have a friend in the Ministry who would love to meet and talk with you. If he knew about you, of course. Fascinated with muggles. Now, where were we? Ah! We must have some other way to refer to{\el} him. I refuse to go through life saying `What's his name,' and you cannot take the other sobriquet. Maybe something classical - Mephistopheles, or some such thing. Do you have any suggestions?"

"Moriarty?" Severus said without thinking, then remembered that he spoke to a wizard. "Sorry, sir. Muggle reference."

"The Napoleon of Crime? Would that then make you Dr. Watson, my dear Severus? Note how I flatter myself by assuming you meant me to represent the incomparable Sherlock."

"Who better, sir? With Professor Scrimgeour standing in as Gregson."

"Not Lestrade?"

"Too pompous. Lestrade at least admitted Holmes was smarter, and kept coming back for help."

"I shall defer to the expert, Severus. Gregson it shall be. There, see? You can laugh at the incident. Well, maybe not laugh, but at least smile. Do not worry about Rufus Scrimgeour. He knows nothing and can learn nothing, and even if he could, he would have to go through me to get to you. You are perfectly safe here at Hogwarts. They will not touch you."

"Thank you, sir." There was another pause, then Severus said tentatively, "May I ask you about something else?"

"Certainly. Why waste this splendid opportunity?"

"What's happening with Lily?"

Dumbledore leaned back in his chair. "I have been wondering when you would get back to her. It has been over half a month, and you have been so circumspect, so cautious, as if there were nothing in the world but potions ingredients, inventories, and student files."

"I'm sorry, sir. It's none of my business."

"You mistake me, Severus. Whose else's business would it be, besides Lily's herself - and James's? I have people who owe their lives to the fact that you consider Lily to be your business. No, I am simply commenting on how you have been able to bottle it up so well over such a span of time. I commend you."

"And Lily, sir?"

"Is well. For the moment they are in hiding. They have found a place well away from anywhere that Volde{\el} Moriarty might look. They are preparing to perform a Fidelius Charm to protect the house. I believe I already told you that they have considered me for the Secret Keeper. Once that is done, Lily will be quite secure. You have nothing to worry about."

"It's good to know. That I have nothing to worry about. Except Scrimgeour, of course." Severus was looking at his hands again. "Sir, what's the worst they could do to me? Could they send me to Azkaban?"

"Good heavens, no! Azkaban is for serious criminals, not for fourth-level potions brewers and gymnastics instructors."

"Gymnastics! I don't teach{\el}"

"You teach people how to fall down. That is gymnastics. You teach a few other things as adjuncts to falling down, but I gather they are peripheral."

"Sir, falling down is just preliminary to{\el}"

"Severus, do you want Rufus Scrimgeour to think you are important? If it comes to it, you teach people how to fall down."

Severus nodded, understanding. "Yes, sir," he said.

\subsection{Thursday, August 20, 1981 (two days before the last quarter)}

By the third week of August, all of the teachers were aware that the newspaper Professor Snape received by owl every morning was not \emph{The Daily Prophet}. At first they'd been curious about the pictures that didn't move and the weather forecasts, but the novelty soon faded, and he was generally left alone to read it. Cribbage was relegated to lunch or the evening, Flitwick having decided he wasn't sharp enough in the morning to have a chance of beating Snape.

"Anything happening in the world?"

Severus looked up from the article he was reading. Professor Kettleburn clearly wanted to sit and talk, so he folded the paper and gestured to the bench opposite him. "Please join me, Professor. The news isn't very cheerful anyway. It seems the Americans shot down two Libyan fighter planes in the Mediterranean."

"That sounds serious." Kettleburn helped himself to sausages and toast.

"Just a difference of opinion over where Libya ends and international waters start. What can I do for you, Professor?"

"To put it briefly, young man, what are your plans for Quidditch?"

"I don't play Quidditch."

"No, but Slytherin does, and a lot of us are hoping to see someone challenge Gryffindor's iron grip on the Quidditch cup."

"What have you got against Gryffindor?" Severus was intrigued at the idea that inter-house rivalry extended to the whole staff.

"Not a thing. Hufflepuff myself, though. I just want the matches to get more exciting. Put a little spice into it. More sporting, if you get my meaning. Are you a betting man?"

"No, not really. I don't even go to Quidditch games. Was Gryffindor winning all those years I was in school?"

"Pretty much. Don't get me wrong, they've had some great teams, and they do tend to get players willing to take risks. That's the Gryffindor mentality. Old Slughorn, now, he rather thought of being on the Slytherin team as a reward for the rich and famous."

"Even I can see that's not the way to get a topnotch team." Severus sipped his coffee pensively. "What would I have to do?" he asked after a moment.

"That's the spirit! Take charge and come out fighting!" Kettleburn's voice became conspiratorial. "Now look, your captain and half the team were seventh years, so now they're gone. You get to pick the new captain. Doesn't have to be one of the old players - could be someone completely new. Have tryouts. Be there to show them the old system of favorites is out and skill is in. Learn the game and take an interest. The team 'll appreciate it and play better for you. The first game of the season is always Gryffindor-Slytherin. You probably won't be able to beat them with a new team, but you could at least make them sit up and take notice."

Severus nodded as Kettleburn rose to leave, his breakfast finished. "Thank you for the advice, sir. You've given me some ideas."

"Glad to hear it, Snape. Keep me posted. I'm real interested in learning how the team shapes up."

"Are you a betting man, sir?"

Kettleburn laughed as he turned away, "Why do you think I was over here talking to you?"

A week before the students arrived, Severus wandered over to the greenhouses where Professor Sprout was sorting through supplies of pots and soil. She was wearing a large apron and heavy gloves, and muttering about mandrakes.

"What can I do for you?" she called as soon as she saw him. "People don't usually visit my little domain. It's good to have some company."

"It's a nice place. I always liked the Herbology classes. My grandmother grew all her own herbs, though she didn't have a greenhouse, so she couldn't raise the more exotic ones. Actually, there were a few specific ones I was curious to see if you had."

Sprout straightened up, hands on hips. "Go ahead and ask."

Severus pulled out a list. "Rosemary, bay, oregano, thyme, sage{\el}"

"Whoa, there. What potion are you making with those?"

"No potion. I was thinking of doing some of my own cooking, and these are herbs I might need."

Sprout was intrigued, and she and Severus spent the rest of the afternoon planning a small kitchen herb garden just for him.

\emph{Monday, August 31, 1981 (two days before the new moon)}

"I say," said Snape decisively, examining the contents of his goblet, "that the Sorting Hat is the biggest con game in the Wizarding World."

"Do tell?" Sprout replied, adding some more mead to his glass. It was the last evening of August, and the heads of houses were mourning their final hours of freedom. Sprout had just made the enchanting discovery that Master Snape had trouble holding his liquor, and she was experimenting with just how talkative she could make him before McGonagall came to his rescue.

"Of course. We have four houses with fourteen dormitories each, for seven years of boys and seven years of girls. Each dormitory has five beds. Every year we bring in twenty boys and twenty girls, and defying all odds on random chance, each year we get five boys and five girls per house. The Hat may actually be sorting at the beginning of the alphabet, but you get down to the Zs, and they go to the house that still has an empty slot. If your last name is Zoltan, you have no choice at all."

"It can't be that bad, Severus," said McGonagall. "I'm sure the Hat sorts them all very conscientiously."

"Then the admission process is rigged. Students usually go in the same house as their parents, right? So you select students by what house their parents were in and voila! Sorting done before they ever get on the train."

"You forget that I handle admissions. If what you say is true, I would have to know about it."

"Maybe you do, and you're not admitting it."

Sprout ducked her head down to hide a quickly stifled laugh and put a finger to her lips as warning to the shocked Flitwick. Neither of them ever dared challenge McGonagall.

"Are you calling me a liar, boy?" McGonagall's eyes narrowed, and her voice grew cold. She turned to poke the fire, the night being chill and the motion well adapted to concealing the expression on her face.

"Why is it that whenever I make a point against you my age suddenly becomes an element of the debate? You're a lot like my grandmother, you know. She used the same \emph{ad hominem} arguments{\el}"

"I am not your grandmother!" McGonagall snapped as she spun to face him, just in time to catch a glimpse of the mead bottle disappearing into Sprout's robes. Ignoring Snape, she advanced on the unlucky Sprout. "Are you getting that poor lad drunk? Setting him on me like a hound on a bear? Give me that bottle!"

Sprout handed her the mead, and McGonagall took it and Snape's goblet, replacing it with a cup of coffee. "You drink that, child. It's better for you. And now that I think about it, being compared to Constantina Rossendale is not such a bad thing."

Snape took the coffee without complaint. Sprout wanted to focus the conversation on Snape's hitherto hidden family, but McGonagall refused to take advantage of his temporary vulnerability and firmly changed the subject.

"Do you remember what you have to do tomorrow, Severus?" she asked, sitting next to the fire and arranging her robes neatly over her feet.

"Yes. I go out onto the lawn with you three when the carriages come up the hill. Basically we herd the older students into the Hall as quickly as possible so that everyone's in place before Hagrid comes up from the boat dock with the first years. Then I keep an eye on Slytherin house to make sure no one causes any trouble during the feast. By the way, where do I sit?"

"End of the board, right in front of the Slytherin table. It's where Slughorn sat as well. Normally the Dark Arts professor is next to you, but we'll have to see what Dumbledore wants. He may prefer the Ministry wallah next to him." McGonagall motioned to Sprout, who refilled Snape's cup, this time with coffee.

"I certainly hope so," said Snape. "That man makes me nervous with all his questions."

"Has he been questioning you? What about?"

Snape was suddenly alert and wary. "He said he was doing a routine check of the whole staff. You mean he didn't ask you any questions?"

"Nary a one," McGonagall replied. "You, Flitwick?" but Flitwick shook his head.

"He asked me a few," said Sprout, "about where'd I'd been before I came to Hogwarts and things like that. And he talked to Sibyll, I know because she got all huffy about it. I think it was just the newer teachers, the ones they haven't known for years."

Severus relaxed again, relieved that he hadn't been singled out. School was about to start, and he had enough to think about without having to worry unnecessarily about Rufus Scrimgeour into the bargain.

\subsection{Tuesday, September 1, 1981}

Lunch was served later than usual on September first since there would be no supper, and the Welcoming Feast would not start until after eight o'clock. All the last minute checks of the dormitories and common rooms were over and Severus spent the rest of the afternoon going over what he had to say to the students in his house the following morning. By six-thirty he and all the other teachers were in the Great Hall, waiting for news that the train had arrived.

"I am so nervous," Severus confided in Flitwick. "This does get easier as the years pass, doesn't it?"

"A little bit," replied Flitwick, "but that feeling never completely vanishes. It's the unknown, Severus. We are facing the unknown. One-seventh of it at least. But you know some of them."

"I know nearly half of them, though not well. And they know me. It's going to be interesting."

Then word came that the train was in. "They'll be loading the carriages now," said McGonagall. "Places everyone."

The heads of houses, Hooch, Kettleburn, and Futhark went out onto the lawn. The others were spread through the entrance hall and Great Hall to usher the students to their seats. If they did it right, the students would never realize they were surrounded by shepherds. Severus never had when he was a student.

Down at the bottom of the hill the great gates opened, and the carriages began their ascent. That was when Severus got his biggest shock of the night. "What are those creatures pulling the carriages?" he gasped to McGonagall. The creatures in question were like horses with wings, but with skeletal black bodies, dragonish heads, and glowing white eyes.

"Those are thestrals," McGonagall told him. "They've always been there."

"I never saw them before," Severus whispered. "Is it because I'm a teacher?"

"No, dear. Didn't you take Care of Magical Creatures in school?"

"Only the first year. Then I switched to Arithmancy and Ancient Runes."

"Then I suggest you look it up later, or ask Kettleburn. Here they come! Look lively now, everyone!"

The carriages were upon them, disgorging students in a total chaos of legs, wheels, voices{\el} Following the example of the others, Severus maintained a constant litany of "This way, up the steps, please, you know where you're supposed to go, quickly now, inside before the feast starts, this way, up the steps, please{\el}"

"Hey, Snape!" yelled an almost familiar voice. "What're you doing back here? I thought you were shut of this place years ago!"

Severus turned to see Algernon Colfax, considerably taller than he'd been in third year when Severus had tutored him in Potions and Charms. It had to be the rarified atmosphere of seventh year that made Algie think he could address someone four years ahead of him in such a familiar way, but Algie had always had more than his fair share of self-confidence.

"Hey, yourself," said Severus, "but watch your mouth. I'm on the detention\slash demerit side of the table now, and my eye's on you. And it's `Professor Snape' for your information."

"Ooooo!" exclaimed Algie. "Does that mean Gryffindor falls this year?"

Severus looked keenly at Algie in the light from the carriage lamps. Algie was, in some ways, like him. Not quite famous enough, not quite rich enough, to merit Slughorn's attention. But a good chap and a decent student - and better than decent on a broom{\el}

"There are falls, and there are falls. No curses or hexes, not on my watch, but how are you at Quidditch?"

Algie's eyes widened in surprise. "I am, without a doubt, the world's greatest beater{\el} But Slughorn would never{\el}" He eyed Severus suspiciously, then it hit him. "No! NO! You're head of house! I don't believe it! Chris! Marlie! Look who's head of house instead of old Slughorn!" Algie was waving at a couple of classmates, Christopher Tobin and Marlene Kingsford, and attracting way too much attention.

"Shh! You're not supposed to find out until later. You want me to look bad in front of the others?"

"You? Look bad? Not you, Cursemaster. And if you're revamping the Quidditch team, I'll be your loyal slave for the entire year."

"Good. I'll hold you to that. Now get inside where you belong. And Algie{\el} it's Professor Snape to you. Don't forget it."

Once the carriages were empty and the students in the Hall finding their seats, Severus and the others entered the castle to join the rest of the teachers, Severus first hurrying into the dungeon area where he'd left his professorial robe. He'd chosen black, a bit like the academic gown worn at a traditional university and, now properly attired, walked into the Hall and to his place at the high table.

To Severus's great relief, Scrimgeour was indeed sitting at Dumbledore's left. Kettleburn was next to Severus. Kettleburn had just managed a quick, "All right so far" when Dumbledore tapped his glass with a spoon and the Hall quieted down. Almost immediately, the great doors swung open and Professor McGonagall entered, crossing half the width of the Hall before turning to walk down the center row, a train of first years following in her wake, eyes wide with wonder.

"Remember your sorting?" Kettleburn asked.

"All too well," Severus replied, and left it at that. This Sorting held no surprises. The house tables erupted in cheers with each new member, and the names Severus expected to enter Slytherin did so with an almost boring predictability. When only three children were left, Severus leaned towards Kettleburn and whispered, "The girl will be in Hufflepuff, as will one of the boys. The other boy will be Ravenclaw."

Kettleburn grinned. "I see you can count. I used to make bets, but the others won't take them anymore."

"Speaking of which, I may have found a beater. If he's as good as he thinks he is."

"Ah, this promises to be a good year."

The last three were sorted into Hufflepuff and Ravenclaw, then Dumbledore rose to introduce the two new professors. Scrimgeour got a polite round of applause; Severus got cheers from Slytherin house, some applause from the other houses, and a general murmur among the older students, especially the seventh years who had more to remember about him. At the Slytherin table, students whose parents staffed the Dark Lord's headquarters were exchanging glances and whispering. \emph{Now we find out if the Dark Lord put the fear into them and their parents.}

Part way through the feast, Severus left the dais to speak to his prefects. All of them were students whose faces, if not their names, had been known to him in seventh year. They all seemed genuinely pleased that the new head of house remembered them.

Then the feast was over, Dumbledore gave a few advisory notices, and the prefects escorted the students to their dormitories. The school year was under way. The professors, tired and anxious to get a good night's sleep before orientation began the following morning, wished each other good night, and Severus followed the students of Slytherin house into the dungeons.

He did not, therefore, notice the speculative expression on McGonagall's face as he exited the Great Hall. \emph{So smooth. So polite. So young and innocent,} McGonagall was thinking. \emph{So tell me, Master Butter-Wouldn't-Melt-In-My-Mouth, whose death did you witness in the last three years that today allows you to see thestrals?}

The next morning at nine o'clock, Severus entered the Slytherin common room to face all seventy of his students. He hadn't exactly memorized his speech, though he had worked on how the different elements would flow together. Before he began, however, Severus realized that a large number of the older students were taller than he was. He had the prefects move a small bench to a position where he could stand on it and be seen and heard by everyone.

First, Severus welcomed the students to Slytherin, spoke briefly of Salazar Slytherin, the founder of the house, and of famous former members. He then outlined the rules, both the `don't's - teasing, hexing, fighting, cheating - and the `do's - studying and living together as a family.

"Currently Slytherin fluctuates between second and fourth place among the houses, depending on the year. We haven't won the House cup in five years, or the Quidditch cup in seven. That's going to change. I'll be monitoring your academic performance, and students having trouble in their classes will have to get tutoring help. Students who lose us points through misbehavior -" without being aware of it, Severus had slipped into a rather good imitation of the Dark Lord "- will be{\el} disciplined. There will be no leniency and no exceptions."

"Not fair!" called out one seventh year boy. "You got into enough trouble when you were a student!"

"And you, Reginald Fenloper, will not repeat my mistakes. Do you happen to remember what happened to Benjamin Osgood?"

The unfortunate Fenloper's eyes widened, and he grew visibly paler. The older students and the Death Eater children nodded knowingly. The new head of house had a reputation for curses and powerful contacts. It would take a brave student to run afoul of him.

"Another area where we can and will improve is Quidditch. I need to appoint a new captain, and as far as I'm concerned, every position on the team is open to the best players. We start tryouts next week. We may not take the Quidditch cup this year, while our new team learns to work together, but if we assemble the right team and we all pull together, Gryffindor's days are numbered."

His speech out of the way, Severus let the prefects conduct the first year orientation while he began his interviews.

The interviews were incredibly tedious. Hour after hour of the same questions, the same answers, the same concerns and problems{\el} It was mind-numbing. Then, on Friday, classes began.

"Don't just dump it in, Carson. Why do you think your parents went to the expense of buying scales?"

"One of you three sent a stinging hex against Pomeroy, and if I don't find out which one, you're all on detention."

"I hope that gesture means you admire Wilkins's taste in music, because if it doesn't I'm taking points from your house."

"Wooden spoon. Do you see here where you stir it with a wooden spoon? Do I have to teach remedial reading as well as Potions?"

"Addison, put that wand away before I take it away."

"Marconi, put that wand away "

"Put that wand{\el}"

A crisis of the soul will send us back to our childhood roots. In Severus's case, it sent him back to Hagrid's hut.

"They are absolute little monsters! They don't care about the material, they will not study, they will not do assignments, they care only for the number of points they will make, they are noisy, they are rude{\el} Nothing is worth this!"

"I thought you taught people before," Hagrid said calmly.

"I did. But I taught people who wanted to learn. They wanted to learn so much, they were paying extra money for it."

"So now you got the ones whose parents are paying the extra money. 'Cept the parents ain't here."

"Fine. What am I supposed to do?"

"They're kids. You got to either entertain them or scare them."

"Entertain them?"

"Then you got to scare them."

Young Professor Snape stalked threateningly into his next Potions class preceded by a nonverbal thunderclap spell that reverberated off the walls and sent students scurrying to their desks with their hands over their ears. "Now that I have your attention," he said in a quiet, menacing voice, "recess is over. The next student who pulls out a wand in this classroom will be fed to Hagrid's grindylows. And I assure you it will be six weeks before your parents even notice that you are missing. Longer before they care. Do I make myself clear?"

He had fewer problems after that.

McGonagall was cornered in the staff room.

"Why me? Why am I the one stuck with the worst combination in every single class! Never, never should you put Slytherin and Gryffindor together, and that's what I get all the time!"

"Don't exaggerate, Severus. You don't have them every class, only half the classes. The other half is Ravenclaw\slash Hufflepuff. That should be a good combination."

"It doesn't compensate. Nobody else gets that combination, and in hour-and-a-half classes with potentially dangerous chemicals to boot. Most of you have forty-five minutes at a time with only one house. Sprout has Slytherin\slash Ravenclaw and Gryffindor\slash Hufflepuff, Sinistra has Slytherin\slash Hufflepuff. We could at least alternate years. I could have Slytherin\slash Gryffindor for first, third, and fifth, and Sprout could have them for second and fourth."

"I'm quite content with the way things are," said Sprout. "I think you just have to learn to cope."

"Besides," added McGonagall, "Hooch and Kettleburn get Gryffindor and Slytherin together."

"You are not going to fob me off with distortions and inaccuracies. Flying only lasts a few weeks, and not all the students take Magical Creatures, so the classes are smaller and in any case he doesn't get first and second years. I am still the only one who gets the classes from hell every single day from September to June!"

McGonagall smiled sweetly. "It's tradition, dear. And there's not a thing you can do about it."

It was a measure of how miserable Severus was that the bright spot in his week was Quidditch.

The Slytherin Quidditch tryouts in the second week of school attracted a large crowd, many of them not Slytherin students. The members of the other houses' Quidditch teams were there, as were the heads of houses themselves and several other teachers who were interested in Quidditch. In addition, the stands were full of students of all houses.

Some twenty-five students were trying out for the seven team positions. Partly because Severus preferred the bludgers, and partly for Algie's sake, he decided to start with candidates for the two Beaters. Even Severus with his limited experience could tell after twenty minutes that Algie Colfax and Chris Tobin were far and away his best choices. Both were seventh years, which made the next step easy.

"Remember, I'm also looking for a Quidditch captain. Let's see how you do in the job. Take over the tryouts while I watch how you handle yourselves."

From then until sunset, Algie and Chris were in charge. From the first minute it was clear not only how keen they were on Quidditch, but how long they'd been hoping for this moment. It's a rare day when someone gets the opportunity to live the daydreams and fantasies of six long years, and Algie wasn't going to waste the chance. By the time they were ready to go in to supper, he had his team. Except for himself and Chris, they were all third, fourth, and fifth years, which augured well for the future.

Severus gathered the Slytherin team around him. "I'm making Colfax the captain. Any objections?" There were none, and the team, already beginning to act like a united group, went up to supper together, discussing training schedules and game strategy.

Kettleburn and McGonagall came over to chat for a moment. "A good looking bunch of players," said Kettleburn. "Care to place your first bet, Minerva? I say Slytherin outscores Gryffindor with the Quaffle, and Gryffindor's only chance to win is to catch the Snitch before Slytherin has them down by more than a hundred fifty."

"It's a bet!" exclaimed McGonagall, "and the easiest galleon I ever won. And you, young man. I thought you weren't interested in Quidditch."

"I'm not," said Severus, "but I'm interested in my house."

"Then the gauntlet is down," McGonagall said. "It's you against me now, and may the best house win."

Saturday, October 17, 1981 (three days before the last quarter moon)

After supper on the third Saturday in October, Hagrid stopped Severus on his way down into the dungeons.

"Good you're still here, Professor Snape. Professor Dumbledore's sent for me, and he asked me to bring you along, too."

Upstairs in Dumbledore's office, the news was good. "This evening Hagrid and I are going into the west country to visit James and Lily. Everything is well with them, and they have nearly completed the preparations for the Fidelius Charm. We shall be making the final adjustments. If all goes according to schedule, it should be performed next week. I shall not mention to them that you are here. It is probably best that they not know. Not yet at any rate. There is nothing you can do, but I thought you might like to know for your own peace of mind."

\subsection{Saturday, October 24, 1981 (three days before the new moon)}

The fourth Saturday in October was set for the first Hogsmeade excursion. Severus was scheduled to supervise, and at breakfast asked for a review of his duties.

"It isn't hard," said McGonagall. "In fact, generally it's as much fun for the staff as for the students. You just make sure there are no fights and that none of the students troubles the local residents. You remember getting out to Hogsmeade, don't you?"

"Not really," Severus answered. "I didn't use to go." He paused, wondering how much of a response she expected, then volunteered, "I was never interested in candy or in jokes and tricks. Not the kind you buy in shops at any rate."

McGonagall's sudden sympathetic expression told Severus she'd remembered that as a boy he never had enough money. He changed the subject, and they discussed other matters. Dumbledore was not at breakfast that morning, and Severus assumed he'd already left to take care of the business at Lily's home, but said nothing to anyone about it.

Peace of mind was hardly an adequate expression for the way Severus felt that afternoon in Hogsmeade. He was walking on air. Lily would be safe. She had a good place to raise her son, in the clean air of the west country where Mr.~Arrogance would have to learn to live quietly and where Lily would feel almost at home. Dumbledore would be secret keeper and Hagrid would be watchdog. Severus could endure any amount of Slytherin-Gryffindor squabbling if Lily was safe.

The next day, without divulging any details, Dumbledore let Severus know that the Fidelius charm had been performed. Lily's home was now protected even from a chance view by a passing stranger. Hagrid was going down that day to visit, but Hagrid's knowing the secret jeopardized nothing.

Severus was happy. Lily was safe and life was good.

\subsection{Thursday, October 29, 1981 (Two days after the new moon)}

The following Thursday, late in the afternoon, Severus made his usual trip to London. His weekly reports to the Dark Lord were short and dull. Scrimgeour had not yet gotten Dumbledore's permission to interview students, so he arrived, taught his classes, and returned home every evening. Nothing was discussed in staff meetings that wasn't school business. The sons and daughters of the Dark Lord's Death Eaters were being circumspect and discreet{\el}

This Thursday was different. When Severus finished his report, the Dark Lord said, "And now we have a reward for you, in recognition of what you have done and of the value we set upon your future usefulness to us. Kneel, and uncover your arm." With wand instead of hot iron, the Dark Lord gently touched and altered the mark on Severus's left arm, elaborating and enlarging the design. When he was done, the mark was that of the third level, one of the inner circles. Severus was rising in the Dark Lord's service.

Then the Dark Lord asked, "Has Dumbledore spoken of the child of the prophecy?"

"No, Lord. He never talks of it or of the child."

"He will soon. When he does, note each word, for we are eager to hear what the wise wizard says."

"Yes, Lord."

Once outside on the streets of London, Severus puzzled about his instructions a little, but reasoned that the Dark Lord undoubtedly knew that the Potters had gone into hiding and hoped to get some clue of their whereabouts through a chance remark of Dumbledore's. He made a mental note to tell Dumbledore of the comment.

This evening, however, Severus had decided on something special. He was still exploring the area around Leicester Square, and had finally resolved to see a play. What better place to begin his theater experience than at St.~Martin's with Agatha Christie's \emph{The Mousetrap}? That meant an early dinner, since he would have to apparate back to Hogwarts as soon as the play was over.

Severus dined in a little Indian restaurant, another daring experiment that left him fascinated with the foods and spices so different from what he'd grown up with, then wandered around Leicester Square until seven-thirty, when he went to the theater, nearby in West Street. The play didn't start until eight o'clock, but Severus wanted to spend the time observing and learning from the other theatergoers.

The play itself was delightful and enthralling as the little group of strangers at a guest house, snow bound and isolated, tried to identify the murderer in their midst. Severus had the pleasure of being surprised by the ending and, after joining the enthusiastic applause, apparated back north, his head full of footlights, curtain calls, and the joys of being an actor.

Back at Hogwarts, he reported to Dumbledore.

"He expected me to speak about James and Lily? How odd." Dumbledore stared into the fire crackling in the fireplace of his office, its flames casting dancing shadows on the walls.

"Not exactly, sir. He said you would speak of the child. He said he was eager to hear your words, your precise words, and he called you a `wise wizard,' though I had the impression he was speaking sarcastically."

"Very odd indeed. I shall send a message to the Potters to be cautious, though it is hard to imagine them being more cautious than they are already. Did Moriarty seem to be aware that a Fidelius charm had been cast?"

"No, sir. He made no mention of it, or anything that might have been an allusion. He's just expecting you to have something to say about the child."

"All right. You get to bed. I shall meditate on this puzzle. Good night, Severus."

"Good night, sir."

\subsection{Saturday, October 31, 1981}

% FIX \emph
\emph{(Note that my time sequence here is very different from the norm. I later revised it for another story, but decided to keep my earlier version here.)}

On Friday, after going his rounds in the school to be sure everything was in order, Severus went to bed around eleven o'clock, as usual. Two hours later, he was shocked from his sleep by a stab of pain that pulsed up through his left arm and radiated out from his shoulder. He was out of bed in an instant, but the pain was as suddenly gone as it had come.

First lighting a lamp, Severus pushed up his sleeve and examined the skull and snake mark branded into his arm. It appeared perfectly normal. \emph{What was that? It felt like he was calling all of us urgently, then suddenly changed his mind. Should I go? I'd have to get Filch to let me out, and that would look suspicious. He knows I can only leave on Thursdays, so I have an excuse.}

Severus then thought of Dumbledore, debating with himself whether or not to wake the headmaster. Deciding to err on the side of caution, he went up to Dumbledore's office, was admitted, and described what had happened. After verifying that the pain had vanished almost instantly, Dumbledore thanked him and sent him back to bed.


